### 2023-07-11 src/tex/ms.tex
[showyourwork] paper draft
Signed-off-by: nstarman <nstarman@users.noreply.github.com>

% Define document class

\PassOptionsToPackage{table}{xcolor}

\documentclass[twocolumn]{aastex631}
\usepackage{showyourwork}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{todonotes}

\newcommand{\mrm}[1]{\mathrm{#1}}
\newcommand{\mbs}[1]{\boldsymbol{#1}}
\newcommand{\mbf}[1]{\mathbf{#1}}
\newcommand{\mbb}[1]{\mathbb{#1}}
\newcommand{\mfk}[1]{\mathfrak{#1}}
\newcommand{\mcal}[1]{\mathcal{#1}}
\newcommand{\unit}[1]{[\text{#1}]}

\newcommand{\nth}[1]{{#1}_{\mrm{n}}}
\newcommand{\fth}[1]{{#1}_{\mrm{f}}}
\newcommand{\qth}[1]{{#1}_{\mrm{q}}}

\newcommand{\pdf}{P}
\newcommand{\cdf}{\Phi}

\newcommand{\Exp}[1]{e^{#1}}
\newcommand{\Erf}[1]{\mathrm{erf}\left(#1\right)}

\newcommand{\sigobs}{{\sigma_*}}
\newcommand{\JN}[1]{{\textcolor{red}{JN: #1}}}

\NewDocumentCommand \dif {o m} {
	\IfNoValueTF{#1}
		{ \mathrm{d}{#2} }
		{ \mathrm{d}^{#1}{\!#2} }
}

% Begin!
\begin{document}

% Title
\title{Characterizing Stellar Streams by ML}

% Author list
\author{Nathaniel Starkman}
\author{Jacob Nibauer}
\author{Jo Bovy}
\author{Jeremy Webb}

% Abstract with filler text
\begin{abstract}
    Stellar stream membership likelihoods with ML. It works!
\end{abstract}

\section{Introduction} \label{sec:intro}

    [Content Here]

    \

    Paper Map:
    \begin{enumerate}
        \item Intro
        \item Method \begin{enumerate}
            \item Fig 1: Overall explainer figure that illustrates the method with Neural networks, and norm flow for CMD
            \item Fig 2: Bayesian graphical model
            \item Test On Synthetic Stream:
            \item Some sort of plot demonstrating successful recovery
        \end{enumerate}
        \item Application / Results \begin{enumerate}
            \item Test case GD-1: \begin{enumerate}
                \item CMD norm flow background
                \item Fig: Stream phi1 phi2 top panel and histograms of each dimension below GD-1
                \item Some plot in phi1-phi2 that shows density variations
            \end{enumerate}
            \item Test case Pal-5 \begin{enumerate}
                \item CMD norm flow background
                \item Fig: Stream phi1 phi2 top panel and histograms of each dimension below Pal 5
                \item Some plot in phi1-phi2 that shows density variations
            \end{enumerate}
        \end{enumerate}
        \item Conclusion
        \item Appendix
    \end{enumerate}

% section introduction (end)

\section{Method} \label{sec:method}

    Stellar streams

    \subsection{Likelihood Setup}\label{sub:likelihood_setup}

        \begin{figure}
        \centering
        \includegraphics[scale=0.5]{figures-not-syw/DAG_StreamDensity.pdf}
        \caption{Fill in.}
        \label{fig: DAG}
        \end{figure}

        We model the stream and background as functions continuous in some affine parameter. In principle this parameter can be anything. Though it might seem the best parameter is the stream's arc length, the most common, easiest, and practical parameter is the longitude -- $w_{\cdot, j\equiv0} \equiv \phi_1$ -- in some stream-oriented reference frame \citep[for details see][section 2]{2023MNRAS.522.5022S}.

        We model the likelihood for a single star as
        \begin{align} \label{eq:general_model}
            \pdf(\nth{\mbs{w}}, \nth{\mbs{m}} | \mbs{\theta})
                &= \sum_{q} \ f_q(w_{i, 0}) \pdf(\nth{\mbs{w}}|\mbs{\theta},q_i\!=\!q) \pdf(\nth{\mbs{m}}|\mbs{\theta},q_i\!=\!q)
        \end{align}
        where we have assumed that $\nth{\mbs{w}}$ and $\nth{\mbs{m}}$ are conditionally independent, and that the mixture weights $f$ are normalized s.t. $\sum_q f(w_{i,0}) = 1$. We discuss the mixture weights further in \autoref{sub:mixture_weight}

        Assuming the measurement of each star is independent, the total log-likelihood is a sum over all stars:
        \begin{equation}
            \ln\mcal{L}\left(\{(\nth{\mbs{w}},\nth{\mbs{m}})\} | \mbs{\theta}\right) = \sum_i  \ln \pdf(\nth{\mbs{w}}, \nth{\mbs{m}} | \mbs{\theta}).
        \end{equation}

        It will prove convenient to distinguish the models for $q=0,1$ as the \textit{background} and \textit{stream} models, respectively. In this notation:

        \begin{multline}
            \pdf(\nth{\mbs{w}}, \nth{\mbs{m}} | \mbs{\theta}) 
            = \\\phantom{+} \ \quad f \quad\ P^{(S)}(\nth{\mbs{w}}|\mbs{\theta}) P^{(S)}(\nth{\mbs{m}}|\mbs{\theta})  \\
            \quad + (1-f) P^{(B)}(\nth{\mbs{w}}|\mbs{\theta}) P^{(B)}(\nth{\mbs{m}}|\mbs{\theta}), \nonumber
        \end{multline}

        The probablity of a being a stream member is then simply
        \begin{equation}\label{eq:membership_prob}
            \pdf\left(S | \mbs{w}_n, \mbs{m}_n, \mbs{\theta} \right) = \frac{f P^{(S)}(\nth{\mbs{w}}|\mbs{\theta}) P^{(S)}(\nth{\mbs{m}}|\mbs{\theta}) }{ \pdf(\nth{\mbs{w}}, \nth{\mbs{m}} | \mbs{\theta})}.
        \end{equation}
    Hereafter, when we refer to ``membership probability," Eq.~\ref{eq:membership_prob} provides the formal definition. 
    %\newpage

    \subsection{Determination of the Mixture Weight} \label{sub:mixture_weight}
        The mixture weight $f_q(w_{i,0})$ as used in Eq.~\ref{eq:general_model} is characterized as the fraction of stars belonging to the mixture component $q$ over an increment $[w_{i,0}, w_{i,0} + \dif{w_{i,0}}]$. Thus, the mixture weight encodes information about the linear density of the stream, which has been shown to depend on substructure in the galaxy (CITE-x). The dependence of the mixture weight on the linear density is captured by the expression
        \begin{equation}\label{eq:fraction_param}
            f_q\left(w_{i,0}\right) = \frac{N_q\left(\phi_1\right)}{N_{\rm tot}\left(\phi_1\right)},
        \end{equation}
        where $N_q\left(\phi_1\right)$ is the number of stars in component $q$ within an interval $[\phi_1, \phi_1 + \dif{\phi_1}]$, and 
        $N_{\rm tot}$ is the total number of stars in the same band (including those in component $q$). The linear  density for component $q$ is then entirely specified by the function $N_q(\phi_1)$.

        The mixture model specified in \S-X only models the weight parameter $f_q$, and not the components of the ratio in \autoref{eq:fraction_param}. However, the linear density $N_q(\phi_1)$ can be readily obtained from $f_q$, provided that $N_{\rm tot}\left(\phi_1\right)$ can be calculated. Importantly, this function does not depend on the parameters of the on-stream or off-stream model. Instead, $N_{\rm tot}(\phi_1)$ is simply the number of stars in a small $\phi_1$ increment. We therefore model $N_{\rm tot}\left(\phi_1\right)$ as a post-processing step using a single normalzing flow in $\phi_1$.

        In particular, for a given field the distribution of $\phi_1$ coordinates is specified by the set $\{\phi_{1,i}\}_i$. A normalizng flow is trained to this dataset, and will satisfy $\int d\phi_1 P_{\phi_i}(\phi_1) = 1$ by construction. In order to re-weight the normalizing flow to obtain $N_{\rm tot}(\phi_1)$, we simply rescale $P_{\phi}(\phi_1)$ by $N_{\rm tot,0}$, which is the total number of stars in the field considered. We can then obtain the linear stream density with
        \begin{equation}
            N_q\left(\phi_1\right) = f_q N_{\rm tot} \left(\phi_1\right)  = f_q \left[N_{\rm tot,0} P_{\phi_1}\left(\phi_1\right) \right] .
        \end{equation}

    \subsection{Astrometric Model} \label{sub:astrometric_model}

        \subsubsection{On-Stream} \label{ssub:astrometric_model_on_stream}

            The astrometric track is modeled with a neural network in each phase space dimension, parameterized as a function of $\phi_1$. The neural network output for a single stream component is the mean location of the stream track in each dimension, $\mbs{\mu}_w(\phi_1 | q_i)$, and its associated covariance matrix $\mbs{\Sigma}_w(\phi_1 | q_i)$. The probability for the data is then
            \begin{equation}
                \pdf^{(S)}(\nth{\mbs{w}} | \mbs{\theta}, \phi_{1,i}, q_i) = \mcal{N}\left(\nth{\mbs{w}} | \mbs{\mu}_w\left(\phi_{1,i} | q_i \right), \mbs{\Sigma}_w\left(\phi_{1,i} | q_i \right) \right),
            \end{equation}
            where $\mbs{\theta}$ is the set of neural network parameters that define $\mbs{\mu}_w$ and $\mbs{\Sigma}_w$.
            In the simplest case, we take $\mbs{\Sigma}_w$ to be diagonal, consisting of both intrinsic dispersion for each dimension of $\mbs{w}$ and the data uncertainties added in quadrature.

            In practice, we work with truncated Gaussians, where the truncation is set by the size of the field in each astrometric dimension. This ensures that the probability density is zero wherever there is no data. Details of the truncated Gaussian are included in \autoref{app:distributions}.

        \subsubsection{Off-stream} \label{ssub:astrometric_model_off_stream}

            We now outline the off-stream astrometric model. We take a similar approach to the on-stream astrometric model discussed in \S\ref{ssub:astrometric_model_on_stream}, though we typically do not characterize the backgrounds with a Gaussian distribution. Instead, we utilize a range of distributions (i.e., exponential, skew-normal) discussed in \autoref{app:distributions}. The parameters of the user-specified background distributions are themselves neural network outputs, such that any $\phi_1$ ``slice" of the background should be characterized by some analytic density, but the evolution of the backgrounds with $\phi_1$ can be complex.

            Let $\mbs{\theta}_{B,j}(\phi_1)$ represent the neural network which outputs a vector of parameters characterizing the background distribution at a given $\phi_1$ for astrometric dimension $j$. The number of outputs for the background model is equal to $\Sigma_{j>0} \mathrm{dim}\left(\mbs{\theta}_{B,j}\right)$ (where $j=0$ corresponds to $\phi_1$, which we do not model). At a given $\phi_1$, the probability density for the astrometric dimension $j>0$ is $\pdf^{(B)}_j\left(\mbs{w}_{n,j} | \mbs{\theta}, \mbs{\theta}_{B,j}, \phi_1 \right)$. We treat each background component as independent, allowing us to write the likelihood as a product over the astrometric dimensions:
            \begin{equation}
                \pdf^{(B)}\left(\mbs{w}_n | \mbs{\theta}, \phi_1 \right) = \prod_{j>0} \pdf_j^{(B)}\left(\mbs{w}_{n,j} | \mbs{\theta}, \mbs{\theta}_{B,j}, \phi_1 \right).
            \end{equation}

    %\newpage

    \subsection{Photometric Model} \label{sub:photometric_model}

        \subsubsection{On-Stream} \label{sub:photometric_model_on_stream}
            In photometric coordinates we model the stream as a single-population isochrone with the possibility of a non-zero distance gradient. We accomplish this by modeling the distance of the isochrone as a neural network output, parametrized as a function of $\phi_1$. The result is a distance track along the stream, estimated from the variation in its isochrone with $\phi_1$.

            At any given $\phi_1$, the isochrone is modeled in absolute magnitudes
            and parameterized by the unit-normalized stellar mass, labeled $\gamma$. For example, increasing $\gamma$ corresponds to movement up the main sequence towards the red giant branch. We denote the isochrone as $\mcal{I(\gamma)}$. The intrinsic dipsersion around the isochrone is $\Sigma_\mcal{I}(\gamma)$. Since the isochrone is in absolute magnitudes, but the data are in apparent magnitudes,
            it is necessary to shift the isochrone by a distance modulus to the predicted distance of the stream, labeled  $\mu(\nth{\phi_1})$.

            For the $n$-th star, the photometric model is:

            \begin{multline}
                P^{(S)}(\mbs{m_i}, \gamma; \mbs{\theta}(\nth{\phi_1}), \nth{\phi_1}) 
                \\ \sim \mcal{N}(\nth{\mbs{m}}; \{\mcal{I(\gamma)} + \mu(\nth{\phi_1}), \sqrt{\Sigma_{\mcal{I}}^2(\gamma) + \Sigma_\mu^2(\nth{\phi_1}) + \Sigma_i^2} \}) \\ \times\pdf(\gamma, \nth{\phi_1}),
            \end{multline}

            where $\pdf(\gamma)$ encodes both the present-day mass function of the stream, as well as the observational constraints (e.g. $g < 22$ mag).

            We are interested in the total probability (at some $\phi_1$) and so integrate over $\gamma$ to find:
            \begin{small}
            \begin{multline}
                P^{(S)}(\nth{\mbs{m}}; \mbs{\theta}(\nth{\phi_1}), \nth{\phi_1}) = \\\int\limits_{\gamma=0}^{1} \mcal{N}(\mbs{m}; \{\mcal{I(\gamma)} + \mu(\nth{\phi_1}), \sqrt{\Sigma_{\mcal{I}}^2(\gamma) + \Sigma_\mu^2(\nth{\phi_1}) + \Sigma_i^2} \}) \pdf(\gamma) \rm{d}\gamma.
            \end{multline}\end{small}
            Then, for a given $\phi_1$ we can obtain a distribution over the distance modulus using 
            \begin{equation}
                \mu_{\rm sample}\left(\phi_1\right) \sim \mathcal{N}\left(\mu(\phi_1), \Sigma^2_\mu(\phi_1) \right) \quad\unit{mag}.
            \end{equation}
            For each sample, we can convert the distance-modulus distribution to the distance track using 
            \begin{equation}
                \rm{dist}\left(\phi_1\right) = 10^{\frac{1}{5}\mu_{\rm sample}(\phi_1)+1} \quad\unit{pc}.
            \end{equation}

        \subsubsection{Off-stream} \label{sub:photometric_model_off_stream}
            In this section we introduce our model for the distribution of backgrounds in photometric coordinates.

            In general, the distribution of stars in color (i.e., $g-r$) and magnitude (i.e., $g$) is a complicated function of location in the galaxy. Even within a field centered on the stream of interest, the color-magnitude diagram (CMD) is a combination of stellar populations distributed over a range in distances. Because of this, we do not expect an analytic density to provide a realistic description of the data. In this work we take a data-driven approach, and represent the CMD using a normalizing flow model.

            Normalizing flows provide a flexible description of a probability density, by transforming samples generated from a simple base distribution (i.e., a Gaussian) to the more complicated target distribution. The transformations are typically non-linear outputs of a neural neural network, whose parameters are optimized until the target density accurately characterizes the data. The neural network transformation is differentiable, so that jacobian factors can be combined to ensure that the the target distribution remains a valid probability density (i.e., integrates to one).

            Our implementation is as follows. For a given stream, we restrict the data to some field characterized by a polygon drawn around the stream. Because our density modeling is aimed at stream characterization rather than discovery, we assume that the stream is sufficiently well known so that it can be masked out as a simple cut in (e.g.) $\phi1-\phi_2$ coordinates. With the stream masked out, we then fit a normalizing flow to the photometric data. Because the background CMD can evolve with $\phi_1$, we fit a \emph{conditional} normalizing flow, $q_{\rm flow}(\mathbf{m}|\phi_1)$, so that the color-magnitude diagram is conditionally dependent on position along the stream. In practice, we model magntiudes and not colors (i.e., $\mathbf{m} = (g,r)$ rather than $g \ \mathrm{and} \ g-r$. Otherwise, the two arguments will always be covariate). Our central assumption with this model is that the distribution of colors and magnitudes for background stars in the masked region are quantitatively similar to those in the unmasked region. For a sufficiently narrow mask we expect this to be the case, and find that this assumption does not introduce bias for the streams considered in this work.

            Once the normalizing flow, $q_{\rm flow}\left(\mathbf{m} | \phi_1\right)$, is fit to the data, its parameters are fixed while the other components of the model begin training. Therefore, the normalizing flow can be rapidly trained and computed as a pre-processing step.

            The specific architecture of the photometric normalizing flow are discussed in \S-X.

    % subsection likelihood_setup (end)

    % \vspace{10pt}

    % \subsection[Astrometric Background]{Astrometric Background: pieces of $P^{(B)}(\mbs{w})$} \label{sub:background_astrometric}

    %     When looking for a stellar stream, the highly complex Galaxy is the background. There are numerous approaches to modeling a complex structure, from a mix of very simple models to a single highly flexible model, like a basis function expansion or ML network.
    %     We aim towards the mix of simple models, but use more flexible models as needed. In this section we describe the various models used when modeling the background, in different coordinates of the phase space.

        % \subsubsection{Flat Background} \label{ssub:flat_background}

        %     The simplest possible background is the flat background.
        %     Perhaps surprisingly, the Galaxy around GD-1 is well modeled by a flat distribution in the $\phi_2(\phi_1)$ phase space.
        %     For a domain $x \in [a, b]$ the normalized PDF is given by
        %     \begin{align}
        %         \pdf(x|a,b) &= \frac{1}{b-a} & \text{and} \\
        %         \ln \pdf(x | a, b) &= -\ln\left({b-a}\right)
        %     \end{align}
        %     where $a,b$ are the $\phi_2$ bounds of the data selection box.

        % % subsubsection flat_background (end)

        % \subsubsection{Exponential-like Background} \label{ssub:exponential_background}

        %     In many coordinate axes, the distribution of the background data is better described by an exponential distribution.
        %     The unit-normalized exponential distribution in the domain $[a, b]$ ($a \neq b$) is given by:
        %     \begin{equation}\label{eq:exp_distr}
        %         f(x) = \frac{m \Exp{-m (x - a))}}{1 - \Exp{-m(b - a)}}.
        %     \end{equation}
        %     However for $m \rightarrow 0$, which describes the flat distribution (\autoref{ssub:flat_background}), this functional form can be numerically unstable, particularly with lower bit precision numerics like \texttt{float32} data-types. In the context of ML, the numerical instability is problematic when employing parameter drop-out for $m$. While for parameter dropout this might be avoided by re-parameterizing to $m+\epsilon$, the numerical instability remains and may be encountered later, creating a difficult-to-diagnose \texttt{NaN}. 
        %     For both compatibility with the flat distribution and for practical reasons we modify the above distribution and approximate the exponential distribution with a 3rd order expansion around $m=0$ when $|m| < \epsilon$, for some small $\epsilon$.

        % % subsubsection exponential_background (end)

        %% PLOT HERE OF ALL THE BACKGROUNDS?? **

    % subsection astrometric background (end)

        % Let $\Omega$ be the independent variable in $\mbf{w}$.

        % $\pdf(m_i | ) \rm{KDE(\mbf{m}_i|\omega_{i} )}$

    % subsection photmetric background (end)

        \begin{figure}
            \script{mock/plot/photometric_background_selection.py}
            \centering
            \includegraphics[width=1\linewidth]{figures/mock/photometric_background_selection.pdf}
            \caption{Caption: TO-DO need to show this with a ground truth (e.g. show true weight in top panel).}
            \label{fig:mock_data_photometric_background_selection}
        \end{figure}

        \begin{figure*}
            \script{mock/plot/results.py}
            \centering
            \includegraphics[width=1\linewidth]{figures/mock/results.pdf}
            \caption{Caption: TO-DO need to show this with a ground truth (e.g. show true weight in top panel).}
            \label{fig:mock_data_result}
        \end{figure*}

\section{Model Implementation}

    \subsection{Network Architecture}

        \begin{enumerate}
            \item A network per model component, e.g. one for the weights, one for the stream track and width, one for the background distribution.
        \end{enumerate}

    \subsection{Astrometric Stream}

        \subsubsection{Track Region Prior} \label{sub:track_region_prior}

            The overall track of the stream is known, so it makes sense to give this information to the system. However, we don't want the prior to dominate the results on small scales. A good balance between these two goals is to have a prior that only influences the track on large scales.
            We introduce the ``split" Gaussian prior, which is a Gaussian split at the peak and pieced back together with a flat region connecting the halves. 
            It is smooth up to the first derivative, so works well in an auto-grad setting.
            The unnormalized PDF is described by:
            \begin{small}
            \begin{equation}
                \pdf(x,\mu,\sigma,w) \propto  \frac{1}{\sigma \sqrt{2 \pi}} \begin{cases} 
                   \Exp{-\frac{1}{2}\left(\frac{x-(\mu-w)}{\sigma}\right)^2} & \phantom{\mu - w <}\ x < \mu - w \\
                    1 & \mu - w \leq x < \mu + w \\
                    \Exp{-\frac{1}{2}\left(\frac{x-(\mu+w)}{\sigma}\right)^2} & \mu + w < x
                \end{cases}.
            \end{equation}\end{small}

            Since this prior is equi-probable in the region $\mu - w < x < \mu + w$, the  impact is to encourage the stream to fall anywhere within this region. 
            It is convenient to reparametrize, with $\tau = \frac{1}{\sigma}$.
            \begin{small}
            \begin{equation}
                \ln \pdf(x,\mu,w) \propto \tau \begin{cases} 
                    -\left(x-(\mu-w)\right)^2 & \phantom{\mu - w <}\ x < \mu - w \\
                    0 & \mu - w \leq x < \mu + w \\
                    -\left(x-(\mu+w)\right)^2 & \mu + w \leq x
                \end{cases},
            \end{equation}\end{small}
            where the additive normalization is 
            $-\ln\left(\sqrt{\frac{\pi}{\tau}} \left(\frac{1}{2}\text{erf}\left(2 \sqrt{\tau } w\right)+1\right)\right)$

            % The total log-probability over all the

            % \begin{equation}
            %     \ln\mcal{L}\left(\{(\nth{\mbs{w}},\nth{\mbs{m}})\} | \mbs{\theta}\right) = \sum_i  \pdf(\nth{\mbs{w}}, \nth{\mbs{m}} | \mbs{\theta}).
            % \end{equation}

        % subsection track_region_prior

% section method (end)

%\newpage
\section{Results} \label{sec:results}

    In this section we present an application of our model to a synthetic stream with known ground truths, and demonstrate the model's ability to characterize stream density variations and membership probabilities in an unsupervised manner. We then apply the method to real stellar streams in \S-X (GD-1) and \S-Y (Pal-5).

    \subsection{Test on a Synthetic Stream}\label{sub:simple_mock_data}

        In this section we apply our model to a synethic stream in order to demonstrate an accurate recovery of stream members and density variations.

        We generate synthetic observations by sampling points from a third degree polynomial \JN{check this} with a constant scatter. Density variations are then simulated by evaluating the stream density with two Gaussian distributions centered at different values of $\phi_1$ with random amplitudes (which sum to $1$) and widths. Stream stars are then removed using random sampling, weighted by their likelihood of belonging to the density. The background astrometric  points in are generated from exponential distributions at each $\phi_1$. The number of stream stars is \JN{X}, while the number of background stars is \JN{Y}.

        The synthetic stream is also simulated in magnitudes using a 12~Gyr isochrone with [Fe/H] = -1.35~dex. The isochrone truncates just short of the giant branch, and sampled from uniformly (i.e., the initial mass function, $P(\gamma)$, is uniform). The background photometric coordinates are generated as a 2-dimensional Gaussian with non-zero covariance. The distance modulus is derived from a polynomial parallax track with uniform thickness. Thus, the synthetic data scenario described here generates a mock stream in astrometric coordinates and photometric coordinates, with density variations, a distance gradient which is consistent in parallax and distance modulus (i.e., magnitudes), all superimposed over a noisy field of background points in each astrometric and photometric dimension.

        The result of applying our density model to the synthetic data is illustrated in Fig.~\ref{fig:mock_data_result}. The top panel shows the weight parameter that controls membership probability as a function of $\phi_1$. The dashed curve represents the output of our data-driven model, while the solid curve is the ground truth. \JN{todo: maybe the kde should be a histogram}, the second panel shows the stream and background in the $(\phi_1,\phi_2)$ plane, and the third panel shows the stream and background in the $(\phi_1,\varpi)$ plane. Points are color-coded according to their membership probability (Eq.~X) \JN{would be good to remove the $\sigma$ bands in this plot.} The weight parameter clearly shows that the model has captured the two prominent density variations along the stream. The are additional variations  mostly around the edges of the stream, though re-sampling the neural network weights with dropout reveals that these variations represent regions of higher model uncertainty.

        We find that the stream is successfully recovered in both astrometric and photometric coordinates, with $x\%$ stream stars being recovered with membership probability greater than $y$. The false positive rate (i.e., stars misidentified as stream members) for this test is found to be $z\%$ when cutting on this threshold.

        In the bottom two rows of Fig.~\ref{fig:mock_data_result} we illustrate the synthetic data color-coded by stream membership probability (top) and background membership probability (background) for different $\phi_1$ slices. Importantly, the photometric portion of the mixture model successfully identifies the stream in magnitude space, showing a high stream membership probability where the stream is present, and a low probability ($\sim 0$) where the stream is absent.

    % subsection test_on_a_synthetic_stream (end)

    \subsection{Results on GD-1} \label{sub:gd1}

        We now apply our density modeling approach to the stellar stream GD-1. We discuss the data selection in \S\ref{ssub:gd1_data} and results in \S\ref{ssub:trained_gd1}.

        \subsubsection{Data Selection} \label{ssub:gd1_data}
            We utilize data from {\it Gaia} DR3 for the astrometric coordinates of each star, and Pan-STARRS1 to obtain more accurate color information. We adopt broad cuts on the cross-matched data to limit the field to a region known to contain GD-1. We perform these rough cuts by requiring \JN{fill in what the cuts are and reference proper motion figure and CMD figure.}

            The result is a field populated by \JN{x} stars, from which we would like to identify stream members.

        \subsubsection{Model Specification}\label{sec:GD_1_ModelSpecification}

            We model GD-1 as a three-component mixture consisting of a main stream component, a spur, and background. In order to guide our model towards GD-1, we set down 4 ``control points" along GD-1's main track, and 3 control points along the spur (illustrated in \JN{x}). These control points act as gaussian priors on the model. We set the Gaussian error on these control points to large values, so that their influence on the model is not dominant. Indeed, we find that the value of the control points is to help reduce training time, since otherwise it will take the flexible density model longer time to converge to the actual stream.

            The weight parameter is also set to truncate to $0$ at $\phi_1 < X$ and $\phi_1 > Y$. This ensures that we do not model stream stars that fall

        \subsubsection{Trained Density Model}\label{ssub:trained_gd1}

            In this section we present results from our model applied to real {\it Gaia} and Pan-STARRS data of GD-1.

            We visualize the performance of our model in identifying stream stars and characterizing the astrometric background with Fig.~\ref{fig:gd1-background}. The top panel shows the stream in $\phi_1$, $\phi_2$ coordinates, color-coded by membership probability (derived from Eq.~\ref{eq:membership_prob}). The following three rows represent background distributions in $\phi_2, \mu_{\phi_1}, \rm{\ and} \ \mu_{\rm phi_2}$, respectively taken at different $\phi_1$ increments centered on the red lines. The $\phi_1$ increments are roughly $\sim X$ in size.

            The blue lines over-plotted represent the best fit model at the given $\phi_1$ slice. We find that the backgrounds are typically well characterized by the distributions adopted (described in \S-x). We can also see from Fig.~\ref{fig:gd1-background}
            that the stream and spur components appear to be well characterized.

            Our ability to recover the stream is demonstrated further in Fig.~\ref{fig:gd1-astrometrics}. In this figure, we only plot stars if their membership probability is greater than \JN{X}. The result is a ``gold" catalog of probable stream and spur members, extending over $X$-degrees in $\phi_1$. We find the expected gap around $\phi_1 \sim -20~\rm{deg}$, which has been proposed to be the location of the dissolved progenitor (CITE).

            Our model also fits the distribution of stream stars in the CMD. These fits are illustrated in Fig.~\ref{fig:gd1-cmds}, where the CMD for the population in a given $\phi_1$ band is plotted, color-coded by stream membership probability. For the on-stream regions, the isochrone appears to provide a decent description of the stream, though there is room for further improvements (discussed in \S-x). However, we note that the stream's presence and absence in the isochrone is well captured by the mixture weight, which is a neural network output.

            Additionally, the distance modulus is also a neural network output, conditioned on $\phi_1$. This allows us to obtain a distance modulus at each $\phi_1$ along the stream. The distance modulus track and (converted) distance track are illustrated in Fig.~\ref{fig:gd1-distance_modulus}. The left panel shows the distance modulus (in magnitudes), while the right shows the corresponding distance track. Importantly, the prior on the distance track is that the stream must fall between $[4,40]~\rm{kpc}$. Thus, our ability to recover the distance to GD-1 without substantial bias provides a useful indicator that our color-magnitude model combined with the astrometric model provide an adequate description of the data. \JN{more on this...}

            \begin{figure*}[h]
                \script{gd1/plot/data_selection.py}
                \centering
                \includegraphics[width=1\linewidth]{figures/gd1/data_selection.pdf}
                \caption{Caption}
                \label{fig:gd1-data_selection}
            \end{figure*}

            \begin{figure*}[h]
                \script{gd1/plot/results.py}
                \centering
                \includegraphics[width=1\linewidth]{figures/gd1/results.pdf}
                \caption{CAPTION}
                TODO:
                \begin{itemize}
                    \item Add plot of the stream linear density
                    \item Reduce the distance between the plot sections
                    \item Color palette for the spur
                    \item more subtle stream MLE path
                    \item weight 5th and 95th percentile distribution
                    \item rerun model with larger pmphi2 sigma
                    \item add the isochrones to the cmd plots
                \end{itemize}
                \label{fig:gd1-results}
            \end{figure*}

            \begin{figure*}
                \centering
                \includegraphics[scale=0.8]{figures-not-syw/gd1/gd1_heatmap_density_KDE2.pdf}
                \caption{Caption}
                \label{fig:gd1-heatmap}
            \end{figure*}

            \input{output/gd1_members.tex}

    % subsection gd1 (end)

% section results (end)

\section{acknowledgements}

    We would like to thank the Academy.

    \url{https://github.com/nstarman/stellar_stream_density_ml_paper/}

\bibliography{bib}

\appendix

\section{Notation} \label{app:notation}

    \begin{itemize}
        \item Full Data
            \begin{itemize}
                \item $\mbf{D} \in \mbb{R}^{(N, F^{(d)})}$ is the data matrix
                \item indexed with index sets $\mrm{n} \in \mbs{I_N} \equiv \{0, ..., N\} \in \mbb{Z^+}$ for the measurements and $\mrm{f} \in \mbs{I_F}  \equiv \{0, ..., F^{(d)}\} \in \mbb{Z^+}$ for the features.
                \item $d_{\mrm{nf}}$ elements of the $n$-th measurement of the $f$-th feature.
                \item $\nth{\mbs{d}}$ row-vector of all features.
                \item  $\mbf{D}$ is split into astrometric and photometric coordinates $\mbf{D} = \{\mbf{W}, \mbf{M}\}$, in that order of features. $F^{(w)} + F^{(m)} = F$, where $F^{(w)}, F^{(m)}$ are defined below.
            \end{itemize}
        \item Astrometric Data
            \begin{itemize}
                \item $\mbf{W} \in \mathbb{R}^{(N, F^{(w)})}$ is the astrometric data matrix
                \item indexed with index the same $N$ as the full data and $\mrm{f} \in \mbs{I_{F^{(w)}}} \equiv \{0, ..., F^{(w)}\} \in \mathbb{Z^+}$ for the astrometric features, where $F^{(w)} \leq F$.
                \item $w_{\mrm{nf}}$ elements of the $n$-th measurement of the $f$-th astrometric feature.
                \item $\nth{\mbs{w}}$ row-vector of all astrometric features.
                \item The first (index 0) feature column, $w_{\cdot,0}$ of $\mbf{W}$ (and $\mbf{D}$) is $\phi_1$.
            \end{itemize}
        \item Photometric Data
            \begin{itemize}
                \item $\mbf{M} \in \mathbb{R}^{(N, F^{(m)})}$ is the photometric data matrix
                \item indexed with index the same $N$ as the full data and $\mrm{f} \in \mbs{I_{F^{(m)}}} \equiv \{0, ..., F^{(m)}\} \in \mathbb{Z^+}$ for the photometric features, where $F^{(m)} \leq F$.
                \item $m_{\mrm{nf}}$ elements of the $n$-th measurement of the $f$-th photometric feature.
                \item $\nth{\mbs{m}}$ row-vector of all photometric features.
            \end{itemize}
        \item Mixture Models
            \begin{itemize}
                \item index set over the models: $\mrm{q} \in \mbs{I_Q} \equiv \{0, ..., Q \} \in \mbb{Z^+}$ 
            \end{itemize}
        \item $\pdf(...)$ is a PDF and $\cdf(...)$ it's CDF.
        % \item $\pi(...)$ is a prior
        \item $\mcal{L}$ is a likelihood.
    \end{itemize}

\section{Theory of Mixture Density Networks (MDNs} \label{app:theory_of_mixture_density_networks}

    Mixture Density Networks (MDNs) are a generalization over mixture models, where the weights and model parameters may be functions, rather than scalars, as in normal mixture models. Generalizing to functional parameters allows the model to capture variation over those parameters that is not possible with scalar-valued models.

    For the MDN we take $d_{\cdot, 0} \equiv x_{\cdot}$ (indexed from 0), which is the first feature column of $\mbf{D}$, as the `independent' coordinate over which the MDN parameters are functions. In the context of streams $d_{\cdot, 0} = x$ is $\phi_1$ the longitude coordinate in a reference frame rotated such that the stream is aligned along $\phi_1$.

    The PDF of the MDN is

    \begin{equation} \label{eq:general_mixture_network}
        \pdf(\nth{\mbs{d}} | \mbs{\theta}(\nth{x}))
        = \sum_{\mrm{q} \in \mbs{I_Q}} \ \qth{f}(\nth{x}) \qth{P}(\nth{d}|\qth{\mbs{\theta}}(\nth{x}),q\!=\!\mrm{q})
    \end{equation}
    The mixture weights $\qth{f}$ are normalized s.t.

    \begin{equation}
        \sum_{\mrm{q}} \qth{f}(\nth{x}) = 1 \qquad \forall \nth{x}
    \end{equation}
    In practice this is enforced by defining
    \begin{equation}
        f_{\mrm{q} = b}(\nth{x}) = 1 - \sum_{\rm{q}\in \mbs{I_Q}\backslash b} \qth{f}(\nth{x})
    \end{equation}
    for some ``background" index $b \in \mbs{I_Q}$.

    Assuming the measurement of each datum is independent, the total log-likelihood is a sum over all data:
    \begin{equation}
        \ln\mcal{L}\left(\mbf{D} | \mbs{\theta}(\mbs{x})\right) = \sum_{n \in \mbs{I_N}} \ln \left[ \sum_{q\in\mbs{I_Q}} \qth{P}\left(\nth{\mbs{d}} | \qth{\mbs{\theta}}(x_n)\right) \right].
    \end{equation}

    The full posterior distribution includes the priors.

    \todo[inline]{TODO}

\section{Probability Distributions} \label{app:distributions}

    A variety of probability distributions are used when modeling the stream and Galactic background. This appendix presents relevant mathematical details of these distributions.
    In particular, observational errors are modeled as Gaussian distributions, which requires modifying each distribution to account for the Gaussian noise.

    \vspace{10pt}

    Let $x \sim X$ be distributed as some specified distribution
    and $\delta \sim \Delta \equiv \mcal{N}(0, \sigma_*)$ as an independent, centered Gaussian.
    An observation $Y$ is distributed as
    \begin{equation}
        Z = X + \Delta,
    \end{equation}
    Which is a convolution of the PDFs.
    \begin{align}  \label{eq:general_convolution}
        \pdf_Z(x; \mbs{\theta}, \sigma)
            & \equiv (\pdf_X(x; \mbs{\theta}) * \mcal{N}(x; 0, \sigma)) \\
            &= \int_{-\infty}^{\infty} \rm{d}\tau \, \pdf(x; \mbs{\theta})\mcal{N}(x-\tau; 0, \sigma)
    \end{align}

    In the following subsections we work through the distributions $\pdf(x,\mbs{\theta})$ and the convolutions with $\mcal{N}(x,0,\sigobs)$.

    \vspace{5pt}
    \subsection{Flat Distribution} \label{sub:flat_distribution}

        The simplest distribution is that of the univariate uniform distribution.
        For a domain $x \in [a, b]$ the PDF is given by
        \begin{equation}\label{eq:pdf_flat_univariate}
            P_{\mcal{U}}(x|a,b) = \begin{cases}
                (b-a)^{-1} & a < x \leq b \\
                0 & \text{else}
            \end{cases}
        \end{equation}
        where $a,b$ are the bounds.

        In practice, the bounds $a,b$ are the bounds of the observation window, creating a subset of a larger field.
        Suppose the larger field is uniformly distributed in a region larger than the bounds $a, b$, ie. $P_{\mcal{U}}(x|\alpha,\beta)$.
        Let each observed datum $x_n$ in the field have Gaussian error $\sigobs_n$,
        then the PDF of the uniform-Gaussian-convolved distribution is given by:

        \begin{equation}
            \pdf_{(\mcal{U}*\mcal{N})}(x; \alpha, \beta, \sigobs) = \begin{cases}
                \pdf_\mcal{U}(x; \alpha, \beta) \left( \cdf_{\mcal{N}}(x; \alpha, \sigobs) - \cdf_{\mcal{N}}(x; \beta, \sigobs) \right) & \alpha \leq x \leq \beta \\
                0 & \text{else}
            \end{cases}
        \end{equation}

        We then truncate this distribution to the observed field $(a, b]$
        \begin{equation} \label{eq:pdf_flat_univariate_convolved_error_full}
            \pdf_{(\mcal{U}*\mcal{N})}(x | a < X \leq b; \alpha, \beta, \sigobs)
        \end{equation}
        in the normal fashion: setting $\pdf_{(\mcal{U}*\mcal{N})} = 0$ when $x < a, x > b$ and normalizing $\pdf_{(\mcal{U}*\mcal{N})}$ within $(a,b]$. The truncated distribution is tractable but unwieldy. The distribution can be simplified enormously if two conditions hold: first, $\alpha \ll a, b \ll \beta$, the observed field is a small subset of the full field; and second, 
        $\sigobs \ll |\alpha - a|$ and $\sigobs \ll |\beta - b|$, the errors are smaller than the observation window size compared to the full field.
        In this case, the distribution reduces back to the uniform distribution!

        Therefore, for all cases considered in this work \eqref{eq:pdf_flat_univariate_convolved_error_full} becomes:

        \begin{equation}\label{eq:pdf_flat_univariate_convolved_error}
            \pdf_{(\mcal{U}*\mcal{N})}(x | a < X \leq b; \alpha, \beta, \sigobs) \cong P_{\mcal{U}}(x|a,b)
        \end{equation}

    \vspace{10pt}
    \subsection{Truncated Exponential Distribution} \label{sub:exponential_distribution}

        The univariate exponential distribution is:
        \begin{equation} \label{eq:pdf_exp_univariate}
            \pdf_{\mcal{E}}(x; \lambda) = \begin{cases}
                m \Exp{-\lambda x} & x \in [0, \infty) \\
                0 & x < 0
            \end{cases}
        \end{equation}

        The support of this distribution, $[0, \infty)$, rarely matches the support of the data. We generalize to the unit-normalized, truncated, univariate exponential distribution in the domain $(a, b]$:
        \begin{equation} \label{eq:pdf_truncexp_univariate}
            \pdf_{\mcal{E}_T}(x; \lambda, a, b) = \begin{cases}
                \frac{\lambda \Exp{-\lambda \, (x - a))}}{1 - \Exp{-\lambda(b - a)}} & a < x \leq b \\
                0 & \text{else},
            \end{cases}
        \end{equation}
        for bounds $x \in (a,b]$. However, as $\lambda \rightarrow 0$, which describes the flat distribution (\autoref{sub:flat_distribution}), this functional form can be numerically unstable. It is therefore practical to define $\pdf_{\mcal{E}}(x; |\lambda| < \epsilon, a, b) \cong P_{\mcal{U}}(x; a,b)$.

        Let each observed datum $x_n$ in the field have Gaussian error $\sigobs_n$,
        then the PDF of the Exponential-convolved-with-a-Gaussian distribution is given by:

        \begin{equation}
            \pdf_{\mcal{E}\cdot\mcal{N}}(x;m,a,\sigma_*) = \frac{m  e^{\frac{1}{2} \lambda  \left(2 b+\lambda  \sigma _*^2-2 x\right)}}{e^{\lambda  (b-a)}-1} = \pdf_{\mcal{E}}(x;\lambda,a) \ \Exp{\frac{1}{2}\lambda^2 \sigma_*^2},
        \end{equation}
        where the function is no longer truncated, since a Gaussian is not compact.

        We impose the same observation field $(a, b]$ and truncate $\pdf_{\mcal{E}\cdot\mcal{N}}(x | a < X \leq b;m,a,\sigma_*)$.
        We note the normalization, which is the CDF evaluated at $a, b$, cancels the factor
        $\Exp{\frac{1}{2}\lambda^2 \sigma_*^2}$. Following thtough, the truncated convolved distribution is identical to the original distribution.

        \begin{equation}
            \pdf_{(\mcal{E}\cdot\mcal{N})_T}x | a < X \leq b;m,a,\sigma_*) \equiv \pdf_{\mcal{E}}(x; \lambda, a, b)
        \end{equation}

    \vspace{10pt}
    \subsection{Normal Distribution}

        The properties of the Normal distribution are well known. For completeness we state

        \begin{equation}
            P_X(x; \mu, \sigma) = \mcal{N}(\mu, \sigma).
        \end{equation}

        With the inclusion of observational errors the distribution becomes

        \begin{equation}
            P_{\mcal{N}\cdot\mcal{N}}(x; \mu, \sigma, \sigobs) = \mcal{N}(\mu, \sqrt{\sigma^2 + \sigobs^2}).
        \end{equation}

        The Normal distribution is not compact, with non-zero value over all $x$. In an observational window $(a,b]$ the PDF is truncated, giving

        \begin{equation}
            P_{\mcal{N}_T}(x; \mu, \sigma, a, b) = \begin{cases}
                \frac{\mcal{N}(x, \mu, \sigma)}{\Phi_\mcal{N}(b; \mu, \sigma) - \Phi_\mcal{N}(a; \mu, \sigma)} & a < x \leq b \\
                0 & \text{else}
            \end{cases}
        \end{equation}

        Note that the observation-window-truncation is performed on the full distribution, which includes the observational errors, if present.
        Therefore, let $\tilde{\sigma}^2 \equiv \sigma^2+\sigma_*^2$

        \begin{equation}
            P_{(\mcal{N}\cdot\mcal{N})_T}(x; \mu, \tilde{\sigma}, a, b) = P_{\mcal{N}_T}(x; \mu, \tilde{\sigma}, a, b)
        \end{equation}

    \vspace{10pt}
    \subsection{Skew-Normal Distribution}

        The PDF of the skew-normal distribution is given by

        \begin{equation}
            \pdf_{SN}(x;\mu,\sigma,\alpha) = 2\pdf_{\mcal{N}}(x;\mu,\sigma)\cdf_{\mcal{N}}(\alpha x;\mu,\sigma).
        \end{equation}

        Despite the popularity of this distribution we are not aware of any work showing the convolution of the skew-normal distribution with a centered Gaussian. Moreover, our Mathematica (v13.2) does not successfully perform this convolution. Consequently we present a step-by-step derivation of $P_{X\cdot\mcal{N}}$.

        \autoref{eq:general_convolution} establishes that convolutions of PDFs are an integral operation. Integrals are often challenging and it is useful to recast a problem in different terms. Rather that working with PDFs of distributions we can instead consider the moment-generating function (MGF) corresponding to the PDF's distribution. Like the PDF, the MGF uniquely determines a distribution, so a MFG uniquely maps to a PDF. Also, 
        for the MGF of two distributions the convolutions is a multiplication, not an integral.
        Therefore, for the convolution of two PDFs their MGFs are multiplied and if the product is the MGF of a known distribution, the corresponding PDF is the convolution of the two original PDFs.

        The MGF of the Normal distribution is

        \begin{equation} \label{eq:mgf_normal}
            M_{\mcal{N}}(t) = \Exp{\frac{\sigma_*^2 t^2}{2}}
        \end{equation}

        And the MGF of the skew-normal is

        \begin{equation} \label{eq:mgf_skewnormal}
            M_{S\mcal{N}}(t) = 2 * \Exp{\mu t + \frac{\sigma^2 t^2}{2}} \cdf(\sigma \delta t), \quad \delta = \frac{\alpha}{\sqrt{1 + \alpha^2}}.
        \end{equation}

        The product of the two MGF is

        \begin{equation}
            M_{S\mcal{N}*\mcal{N}}(t) = M_{S\mcal{N}}(t) * M_{\mcal{N}}(t) = 2 * \Exp{\mu t + \frac{(\sigma^2 + \sigma_*^2) t^2}{2}} \cdf(\sigma \delta t).
        \end{equation}
        We rewrite $\tilde\sigma^2 = \sigma^2 + \sigma_*^2$, and $\tilde{\sigma} \tilde{\delta} = \sigma \delta$.

        \begin{equation}
            M_{S\mcal{N}*\mcal{N}}(t) = 2 * \Exp{\mu t + \frac{\tilde{\sigma}^2 t^2}{2}} \cdf_{\mcal{N}}(\tilde{\sigma} \tilde{\delta} t)
        \end{equation}
        This has the same form as the skew-normal, only with $\sigma \rightarrow \tilde\sigma$ and $\delta \rightarrow \tilde\delta$.

        Therefore the PDF of the convolved distribution is

        \begin{equation}
            \pdf_{S\mcal{N}\cdot\mcal{N}}(x;\mu,\sigma,\alpha) = 2\pdf_{\mcal{N}}(x;\mu,\tilde{\sigma})\cdf_{\mcal{N}}(\tilde{\alpha} x;\mu,\tilde{\sigma})
        \end{equation}
        where $\tilde\sigma^2 = \sigma^2 + \sigma_*^2$ and $\tilde{\alpha} = \frac{\tilde{\delta}}{\sqrt{1-\tilde{\delta}^2}}$, $\tilde{\delta} = \frac{\sigma}{\tilde{\sigma}}\delta$.

        The truncation of this distribution to the range $(a, b]$ is

       \begin{equation}
            \pdf_{S\mcal{N}_T}(x; \mu, \sigma, \alpha, a, b)
                = \begin{cases}
                    \frac{\pdf_{S\mcal{N}}(x; \mu, \tilde\sigma, \tilde\alpha)}{\cdf_{S\mcal{N}}(b; \mu, \tilde\sigma, \tilde\alpha) - \cdf_{S\mcal{N}}(a; \mu, \tilde\sigma, \tilde\alpha)} & a < x \leq b \\
                    0 & \text{else}
                \end{cases}
        \end{equation}
        where
        \begin{equation}
            \cdf_{S\mcal{N}}(x; \mu, \sigma) = \frac{1}{2} \text{erfc}\left(\frac{\mu -x}{\sqrt{2} \sigma }\right)-2 T\left(\frac{x-\mu }{\sigma },\alpha \right)
        \end{equation}
        where $T$ is Owen's T distribution.

\section{Plots} \label{app:developing_plots}

    \begin{figure*}
        \centering
        \includegraphics[scale=0.7]{figures-not-syw/gd1/tot_stream_and_spur_prob.png}
        \caption{Caption}
        \label{fig:gd1-astrometrics}
    \end{figure*}

    \begin{figure*}
        \centering
        \includegraphics[scale=0.8]{figures-not-syw/gd1/Unknown.png}
        \caption{Caption}
        \label{fig:gd1-distance_modulus}
    \end{figure*}

    \begin{figure}
        \centering
        \includegraphics[scale=0.6]{figures-not-syw/gd1/Unknown-2.png}
        \caption{Caption}
        \label{fig:gd1-cmd}
    \end{figure}

    \begin{figure*}
        \centering
        \includegraphics[scale=0.6]{figures-not-syw/gd1/Unknown-4.png}
        \caption{Caption}
        \label{fig:gd1-cmds}
    \end{figure*}

\end{document}

### 2023-07-11 src/scripts/brutus/download_mist_file.py

@@ -1,0 +1,36 @@
+"""Mist files for brutus."""
+
+import pathlib
+import shutil
+import sys
+
+import brutus.utils
+
+# Add the parent directory to the path
+sys.path.append(pathlib.Path(__file__).parent.parent.as_posix())
+# isort: split
+
+import paths  # noqa: E402
+
+##############################################################################
+
+try:
+    snkmkp = snakemake.params
+except NameError:
+    snkmkp = {"load_from_static": True}
+
+
+if snkmkp["load_from_static"]:
+    shutil.copyfile(
+        paths.static / "brutus" / "MIST_1.2_iso_vvcrit0.0.h5",
+        paths.data / "brutus" / "MIST_1.2_iso_vvcrit0.0.h5",
+        follow_symlinks=True,
+    )
+    sys.exit(0)
+
+brutus.utils.fetch_isos(target_dir=paths.data / "brutus", iso="MIST_1.2_vvcrit0.0")
+shutil.copyfile(
+    paths.data / "brutus" / "MIST_1.2_iso_vvcrit0.0.h5",
+    paths.static / "brutus" / "MIST_1.2_iso_vvcrit0.0.h5",
+    follow_symlinks=True,
+)

### 2023-07-11 src/scripts/dustmaps/download_dustmaps.py

@@ -1,0 +1,39 @@
+"""Mist files for brutus."""
+
+import pathlib
+import shutil
+import sys
+
+import dustmaps.bayestar
+import dustmaps.config
+
+# Add the parent directory to the path
+sys.path.append(pathlib.Path(__file__).parent.parent.as_posix())
+# isort: split
+
+import paths  # noqa: E402
+
+##############################################################################
+# Parameters
+
+try:
+    snkmkp = snakemake.params
+except NameError:
+    snkmkp = {"load_from_static": True}
+
+
+##############################################################################
+
+
+DUSTMAPS_DIR = paths.data / "dustmaps"
+DUSTMAPS_DIR.mkdir(exist_ok=True)
+
+dustmaps.config.config["data_dir"] = DUSTMAPS_DIR.as_posix()
+
+if snkmkp["load_from_static"]:
+    shutil.copyfile(
+        paths.static / "dustmaps" / "bayestar2019.h5",
+        DUSTMAPS_DIR / "bayestar" / "bayestar2019.h5",
+    )
+else:
+    dustmaps.bayestar.fetch(version="bayestar2019")

### 2023-07-11 src/scripts/gd1/data/1-query_data.py

@@ -1,0 +1,203 @@
+"""Query data from Gaia, crossmatched with PS-1."""
+
+import shutil
+import sys
+from itertools import combinations, pairwise
+from pathlib import Path
+
+import asdf
+import astropy.coordinates as coords
+import astropy.units as u
+import matplotlib.pyplot as plt
+import numpy as np
+from astroquery.gaia import Gaia
+from astroquery.utils.tap.model.job import Job
+from tqdm import tqdm
+
+# isort: split
+from frames import gd1_frame as frame
+
+sys.path.append(Path(__file__).parent.parent.parent.as_posix())
+# isort: split
+
+import paths  # noqa: E402
+
+##############################################################################
+# Parameters
+
+GAIA_LOGIN = Path(paths.static / "gaia.login").expanduser()
+SAVE_LOC = paths.data / "gd1" / "gaia_ps1_xm_polygons.asdf"
+
+try:
+    snkmkp = snakemake.params
+except NameError:
+    snkmkp = {"load_from_static": True}
+
+
+if snkmkp["load_from_static"]:
+    shutil.copyfile(paths.static / "gd1" / "gaia_ps1_xm_polygons.asdf", SAVE_LOC)
+    sys.exit(0)
+
+
+##############################################################################
+
+
+PHI1_EDGES = np.arange(-100, 30 + 10, 10) * u.deg
+PHI2_BOUNDS = (-9, 5) * u.deg
+PLX_BOUNDS = (-10, 1.0) * u.milliarcsecond
+BP_RP_BOUNDS = (-1, 3) * u.mag
+GMAG_BOUNDS = (0, 50) * u.mag
+IMAG_BOUNDS = (0, 50) * u.mag
+
+
+def a_as_b(cols: dict[str, str | None], prefix: str) -> str:
+    """Convert a dictionary of column names to a string of "a as b" pairs."""
+    return ", ".join(
+        tuple(prefix + (k if v is None else f"{k} as {v}") for k, v in cols.items())
+    )
+
+
+gaia_cols = {
+    "source_id": None,
+    "ra": None,
+    "ra_error": None,
+    "dec": None,
+    "dec_error": None,
+    "parallax": None,
+    "parallax_error": None,
+    "pmra": None,
[…]

### 2023-07-11 src/scripts/gd1/data/2-combine_data.py

@@ -1,0 +1,161 @@
+"""Combine data fields into one dataset."""
+
+import contextlib
+import shutil
+import sys
+from pathlib import Path
+
+import asdf
+import astropy.coordinates as coords
+import astropy.units as u
+import dustmaps.bayestar
+import gala.coordinates as gc
+import numpy as np
+from astropy.table import QTable, vstack
+
+# isort: split
+from frames import gd1_frame as frame
+
+sys.path.append(Path(__file__).parent.parent.parent.as_posix())
+# isort: split
+
+import paths  # noqa: E402
+
+##############################################################################
+# Parameters
+
+SAVE_LOC = paths.data / "gd1" / "gaia_ps1_xm.asdf"
+
+try:
+    snkmkp = snakemake.params
+except NameError:
+    snkmkp = {"load_from_static": False}
+
+
+##############################################################################
+
+if snkmkp["load_from_static"]:
+    shutil.copyfile(paths.static / "gd1" / "gaia_ps1_xm.asdf", SAVE_LOC)
+    sys.exit(0)
+
+# -----------------------------------------------------------------------------
+# Initial combination
+
+af = asdf.open(paths.data / "gd1" / "gaia_ps1_xm_polygons.asdf", mode="r")
+
+combined = vstack(af.search("polygon-*").nodes, metadata_conflicts="silent")
+
+# correct metadata
+combined.meta.pop("query")
+combined.meta["frame"] = f"{frame.__class__.__module__}.{frame.__class__.__name__}"
+
+# correct unit and data types
+combined["ps1_g"].unit = u.mag
+
+combined.write(SAVE_LOC, format="asdf")
+
+del combined
+af.close()
+
+# -----------------------------------------------------------------------------
+
+table = QTable.read(SAVE_LOC)
+
+# ---------------------------------------
+# Astrometrics
+
+c_icrs = coords.SkyCoord(
+    ra=table["ra"],
+    dec=table["dec"],
+    distance=coords.Distance(
+        parallax=table["parallax"] << u.arcsecond, allow_negative=True
+    ),
[…]

### 2023-07-11 src/scripts/gd1/data/3.2-phot_edges.py

@@ -1,0 +1,48 @@
+"""Setup."""
+
+import sys
+from pathlib import Path
+
+import asdf
+import brutus.filters
+import brutus.seds
+import numpy as np
+import shapely
+
+# isort: split
+
+sys.path.append(Path(__file__).parent.parent.parent.as_posix())
+# isort: split
+
+import paths  # noqa: E402
+
+##############################################################################
+
+
+# Build isochrone
+mags, _, _ = brutus.seds.Isochrone(
+    filters=brutus.filters.ps[:-2],  # (g, r)
+    nnfile=(paths.data / "brutus" / "nn_c3k.h5").resolve(),
+    mistfile=(paths.data / "brutus" / "MIST_1.2_iso_vvcrit0.0.h5").resolve(),
+).get_seds(
+    eep=np.linspace(202, 600, 5000),
+    apply_corr=True,
+    feh=-1.35,
+    dist=7.8e3,
+    loga=np.log10(12e9),
+)
+mags = mags[np.all(np.isfinite(mags), axis=1)]
+
+isochrone = shapely.LineString(np.c_[mags[:, 0] - mags[:, 2], mags[:, 0]])
+iso_tight = isochrone.buffer(0.1)
+iso_medium = isochrone.buffer(0.3)
+iso_loose = isochrone.buffer(0.5)
+
+
+af = asdf.AsdfFile()
+af["isochrone"] = np.c_[isochrone.xy]
+af["isochrone_tight"] = np.c_[iso_tight.exterior.xy]
+af["isochrone_medium"] = np.c_[iso_medium.exterior.xy]
+af["isochrone_loose"] = np.c_[iso_loose.exterior.xy]
+af.write_to(paths.data / "gd1" / "isochrone.asdf")
+af.close()

### 2023-07-11 src/scripts/gd1/frames.py

@@ -1,0 +1,12 @@
+"""Setup."""
+
+from __future__ import annotations
+
+import astropy.coordinates as coords
+import gala.coordinates as gc
+
+##############################################################################
+
+
+galactocentric_frame = coords.Galactocentric()
+gd1_frame = gc.GD1Koposov10()

### 2023-07-11 src/scripts/gd1/model/0-spur_control_points.py

@@ -1,0 +1,31 @@
+"""Plot results."""
+
+import sys
+from pathlib import Path
+
+import astropy.units as u
+from astropy.table import QTable
+
+sys.path.append(Path(__file__).parent.parent.parent.as_posix())
+# isort: split
+
+import paths  # noqa: E402
+
+##############################################################################
+
+
+# Values from Price-Whelan and Bonaca 2018
+table = QTable(
+    # fmt: off
+    rows=[
+        [-35.0 * u.deg, 1.3 * u.deg, 0.85 * u.deg, -12.95 * u.mas / u.yr, 3 * u.mas / u.yr],  # noqa: E501
+        [-30.0 * u.deg, 1.3 * u.deg, 0.85 * u.deg, -12.6 * u.mas / u.yr, 3 * u.mas / u.yr],  # noqa: E501
+        [-20 * u.deg, 1.5 * u.deg, 0.85 * u.deg, -11.5 * u.mas / u.yr, 5 * u.mas / u.yr],  # noqa: E501
+    ],
+    # fmt: on
+    names=("phi1", "phi2", "w_phi2", "pm_phi1", "w_pm_phi1"),
+    units=(u.deg, u.deg, u.deg, u.mas / u.yr, u.mas / u.yr),
+    meta={},
+)
+
+table.write(paths.data / "gd1" / "spur_control_points.ecsv", overwrite=True)

### 2023-07-11 src/scripts/gd1/model/0-stream_control_points.py

@@ -1,0 +1,34 @@
+"""Plot results."""
+
+import sys
+from pathlib import Path
+
+import astropy.units as u
+from astropy.table import QTable
+
+sys.path.append(Path(__file__).parent.parent.parent.as_posix())
+# isort: split
+
+import paths  # noqa: E402
+
+##############################################################################
+
+
+table = QTable(
+    # fmt: off
+    rows=[
+        [-80.0 * u.deg, -2.24 * u.deg, 1.75 * u.deg, -9.9 * u.mas / u.yr, 0.75 * u.mas / u.yr],  # noqa: E501
+        [-70.0 * u.deg, -1.3 * u.deg, 1.75 * u.deg, -11.1 * u.mas / u.yr, 0.75 * u.mas / u.yr],  # noqa: E501
+        [-60.0 * u.deg, -0.8 * u.deg, 1.75 * u.deg, -12.5 * u.mas / u.yr, 0.75 * u.mas / u.yr],  # noqa: E501
+        [-50.0 * u.deg, -0.0 * u.deg, 1.75 * u.deg, -13.3 * u.mas / u.yr, 0.75 * u.mas / u.yr],  # noqa: E501
+        [-40.0 * u.deg, -0.0 * u.deg, 1.75 * u.deg, -13.3 * u.mas / u.yr, 0.75 * u.mas / u.yr],  # noqa: E501
+        [-30.0 * u.deg, -0.0 * u.deg, 1.75 * u.deg, -12.6 * u.mas / u.yr, 0.75 * u.mas / u.yr],  # noqa: E501
+        [-20.0 * u.deg, 0.09 * u.deg, 1.75 * u.deg, -11.5 * u.mas / u.yr, 0.75 * u.mas / u.yr],  # noqa: E501
+    ],
+    # fmt: on
+    names=("phi1", "phi2", "w_phi2", "pm_phi1", "w_pm_phi1"),
+    units=(u.deg, u.deg, u.deg, u.mas / u.yr, u.mas / u.yr),
+    meta={},
+)
+
+table.write(paths.data / "gd1" / "stream_control_points.ecsv", overwrite=True)

### 2023-07-11 src/scripts/gd1/model/1-info.py

@@ -1,0 +1,157 @@
+"""Plot results."""
+
+import sys
+from pathlib import Path
+
+import asdf
+import astropy.units as u
+import numpy as np
+from astropy.table import QTable
+
+# isort: split
+import stream_ml.pytorch as sml
+
+sys.path.append(Path(__file__).parent.parent.parent.as_posix())
+# isort: split
+
+import paths  # noqa: E402
+
+##############################################################################
+
+snkmkp = snakemake.params  # noqa: F821
+
+
+##############################################################################
+
+# Read tables
+table = QTable.read(paths.data / "gd1" / "gaia_ps1_xm.asdf")
+masks = QTable.read(paths.data / "gd1" / "masks.asdf")
+
+# Info file
+af = asdf.AsdfFile()
+
+# -----------------------------------------------------------------------------
+# Mask
+# TODO! move this to the data files
+
+sel = (
+    (table["parallax"] > 0 * u.milliarcsecond)  # FIXME! allow negative parallax
+    & masks[snkmkp["pm_mask"]]
+    & masks[snkmkp["phot_mask"]]
+    & ~np.isnan(table["g0"])
+    & ~np.isnan(table["ps1_g_error"])
+    & ~np.isnan(table["r0"])
+    & ~np.isnan(table["ps1_r_error"])
+)
+table = table[sel]
+
+# Save mask
+af["mask"] = sel
+
+
+# ----------------------------------------------------
+# Data
+
+af["renamer"] = {
+    "source_id": "id",
+    # ------
+    "ra": "ra",
+    "ra_error": "ra_err",
+    "dec": "dec",
+    "dec_error": "dec_err",
+    "parallax": "plx",
+    "parallax_error": "plx_err",
+    "pmra": "pmra",
+    "pmra_error": "pmra_err",
+    "pmdec": "pmdec",
+    "pmdec_error": "pmdec_err",
+    "ra_dec_corr": "ra_dec_corr",
+    "ra_parallax_corr": "ra_plx_corr",
+    "ra_pmra_corr": "ra_pmra_corr",
+    "ra_pmdec_corr": "ra_pmdec_corr",
+    "dec_parallax_corr": "dec_plx_corr",
+    "dec_pmra_corr": "dec_pmra_corr",
[…]

### 2023-07-11 src/scripts/gd1/model/2-train_flow.py

@@ -1,0 +1,70 @@
+"""Train photometry background flow."""
+
+import sys
+from pathlib import Path
+
+import torch as xp
+import torch.utils.data as td
+from torch import optim
+from tqdm import tqdm
+
+import stream_ml.pytorch as sml
+
+# isort: split
+from data import data
+from define_model import background_photometric_model as bkg_flow
+
+# Add the parent directory to the path
+sys.path.append(Path(__file__).parent.parent.as_posix())
+# isort: split
+
+import paths  # noqa: E402
+
+# =============================================================================
+# Load Data
+
+try:
+    snkmkp = snakemake.params
+except NameError:
+    snkmkp = {
+        "load_from_static": True,
+        "epochs": 1_000,
+    }
+
+if snkmkp["load_from_static"]:
+    bkg_flow.load_state_dict(xp.load(paths.static / "gd1" / "flow_model.pt"))
+    xp.save(bkg_flow.state_dict(), paths.data / "gd1" / "flow_model.pt")
+
+    sys.exit(0)
+
+
+# =============================================================================
+# Train
+
+off_stream = (data["phi2"] < -1.5) | (data["phi2"] > 2)
+
+coord_names = (*bkg_flow.indep_coord_names, *bkg_flow.coord_names)
+dataset = td.TensorDataset(data[coord_names].array[off_stream])
+loader = td.DataLoader(dataset=dataset, batch_size=500, shuffle=True, num_workers=0)
+optimizer = optim.Adam(bkg_flow.parameters(), lr=1e-3)
+
+# Turn on gradients for training
+object.__setattr__(bkg_flow, "with_grad", True)  # noqa: FBT003
+
+for _epoch in tqdm(range(snkmkp["epochs"])):
+    for _step, (data_cur_,) in enumerate(loader):
+        data_cur = sml.Data(data_cur_, names=coord_names)
+
+        optimizer.zero_grad()
+
+        mpars = bkg_flow.unpack_params(bkg_flow(data_cur))
+        loss = -bkg_flow.ln_posterior_tot(mpars, data_cur)
+
+        loss.backward()
+        optimizer.step()
+
+# Turn off gradients for usage later
+object.__setattr__(bkg_flow, "with_grad", False)  # noqa: FBT003
+
+xp.save(bkg_flow.state_dict(), paths.data / "gd1" / "flow_model.pt")
+xp.save(bkg_flow.state_dict(), paths.static / "gd1" / "flow_model.pt")

### 2023-07-11 src/scripts/gd1/model/3-train_model.py

@@ -1,0 +1,112 @@
+"""Train photometry background flow."""
+
+import sys
+from pathlib import Path
+
+import torch as xp
+import torch.utils.data as td
+from torch import optim
+from tqdm import tqdm
+
+import stream_ml.pytorch as sml
+
+# isort: split
+from data import data, where
+from define_model import model
+
+# Add the parent directory to the path
+sys.path.append(Path(__file__).parent.parent.as_posix())
+# isort: split
+
+import paths  # noqa: E402
+
+# =============================================================================
+
+try:
+    snkmkp = snakemake.params
+except NameError:
+    snkmkp = {
+        "load_from_static": False,
+        "epochs": 1_000,
+    }
+
+if snkmkp["load_from_static"]:
+    model.load_state_dict(xp.load(paths.static / "gd1" / "model.pt"))
+    xp.save(model.state_dict(), paths.data / "gd1" / "model.pt")
+
+    sys.exit(0)
+
+
+# =============================================================================
+# Training Parameters
+
+EPOCHS = 1250 * 10
+BATCH_SIZE = int(len(data) * 0.075)
+
+LEARNING_RATE = 1e-3
+WEIGHT_DECAY = 1e-8
+
+dataset = td.TensorDataset(
+    data.array,  # data
+    where.array,  # TRUE where NOT missing
+)
+
+loader = td.DataLoader(
+    dataset=dataset,
+    batch_size=BATCH_SIZE,
+    shuffle=True,
+    num_workers=0,
+    drop_last=True,  # drop rando last for better plotting
+)
+
+optimizer = optim.Adam(
+    list(model.parameters()), lr=LEARNING_RATE, weight_decay=WEIGHT_DECAY
+)
+
+scheduler = optim.lr_scheduler.ConstantLR(optimizer, factor=0.1)  # constant 1e-4
+
+
+# =============================================================================
+# Train
+
+num_steps = len(loader.dataset) // loader.batch_size
+epoch: int = 0
+epoch_iterator = tqdm(
+    range(EPOCHS),
+    dynamic_ncols=True,
+    postfix={"lr": f"{scheduler.get_last_lr()[0]:.2e}", "loss": f"{0:.2e}"},
+)
+for _epoch in epoch_iterator:
+    for _step, (step_arr, step_where_) in enumerate(loader):
+        # Prepare
+        step_data = sml.Data(step_arr, names=data.names)
+        step_where = sml.Data(step_where_, names=data.names[1:])
+
+        # Forward Step
[…]

### 2023-07-11 src/scripts/gd1/model/4-likelihoods.py

@@ -1,0 +1,111 @@
+"""Get Likelihoods."""
+
+import sys
+from pathlib import Path
+
+import numpy as np
+import torch as xp
+from astropy.table import QTable
+from tqdm import tqdm
+
+# Add the parent directory to the path
+sys.path.append(Path(__file__).parent.parent.parent.as_posix())
+# isort: split
+
+from gd1.model.data import data, table, where  # noqa: E402
+from gd1.model.define_model import model  # noqa: E402
+from helper import manually_set_dropout  # noqa: E402
+
+import paths  # noqa: E402
+
+# =============================================================================
+
+# Load model
+model.load_state_dict(xp.load(paths.data / "gd1" / "model.pt"))
+model = model.eval()
+
+
+# =============================================================================
+# Variations
+
+N = 250
+
+stream_probs = xp.empty((len(data), N))
+spur_probs = xp.empty((len(data), N))
+with xp.no_grad():
+    model.train()
+    manually_set_dropout(model, 0.15)
+
+    for i in tqdm(range(N), total=N):
+        mpars = model.unpack_params(model(data))
+        stream_lik = model.component_posterior(
+            "stream", mpars, data, stream_astrometric_where=where
+        )
+        spur_lik = model.component_posterior(
+            "spur", mpars, data, spur_astrometric_where=where
+        )
+        bkg_lik = model.component_posterior(
+            "background", mpars, data, background_astrometric_where=where
+        )
+        tot_lik = model.posterior(
+            mpars,
+            data,
+            stream_astrometric_where=where,
+            spur_astrometric_where=where,
+            background_astrometric_where=where,
+        )
+
+        stream_probs[:, i] = stream_lik / tot_lik
+        spur_probs[:, i] = spur_lik / tot_lik
+
+stream_prob_percentiles = np.c_[
+    np.percentile(stream_probs, 5, axis=1),
+    np.percentile(stream_probs, 95, axis=1),
+]
+spur_prob_percentiles = np.c_[
+    np.percentile(spur_probs, 5, axis=1),
+    np.percentile(spur_probs, 95, axis=1),
+]
+
+model.eval()
+manually_set_dropout(model, 0.0)
+
+
+# =============================================================================
+# MLE
+
+with xp.no_grad():
+    mpars = model.unpack_params(model(data))
+
[…]

### 2023-07-11 src/scripts/gd1/model/data.py

@@ -1,0 +1,49 @@
+"""Import data."""
+
+import sys
+from pathlib import Path
+
+import asdf
+import torch as xp
+from astropy.table import QTable
+
+import stream_ml.pytorch as sml
+
+# isort: split
+# Add the parent directory to the path
+sys.path.append(Path(__file__).parent.parent.parent.as_posix())
+# isort: split
+
+import paths  # noqa: E402
+
+# =============================================================================
+# Load data and model
+
+with asdf.open(
+    paths.data / "gd1" / "info.asdf", lazy_load=False, copy_arrays=True
+) as af:
+    sel = af["mask"]
+    names = tuple(af["names"])
+    renamer = af["renamer"]
+
+table = QTable.read(paths.data / "gd1" / "gaia_ps1_xm.asdf")[sel]
+
+data = sml.Data.from_format(
+    table, fmt="astropy.table", names=names, renamer=renamer
+).astype(xp.Tensor, dtype=xp.float32)
+
+where = sml.Data(
+    (~xp.isnan(data.array)[:, 1:]),  # True where NOT missing
+    names=data.names[1:],
+)
+
+# TODO: it would be nice to keep this as NaN
+data.array[xp.isnan(data.array)] = 0.0  # set missing data to zero
+
+
+# -----------------------------------------------------------------------------
+
+pth = paths.data / "gd1" / "data.tmp"
+if not pth.exists():
+    with pth.open("w") as f:
+        f.write("hack for snakemake")

### 2023-07-11 src/scripts/gd1/plot/data_selection.py

@@ -1,0 +1,287 @@
+"""Train photometry background flow."""
+
+import sys
+from pathlib import Path
+from typing import Any
+
+import asdf
+import astropy.units as u
+import matplotlib as mpl
+import matplotlib.pyplot as plt
+import numpy as np
+from astropy.table import QTable, Row
+
+# isort: split
+# Add the parent directory to the path
+sys.path.append(Path(__file__).parent.parent.parent.as_posix())
+# isort: split
+
+import paths  # noqa: E402
+
+###############################################################################
+# Load stuff
+
+# Matplotlib style
+plt.style.use(paths.scripts / "paper.mplstyle")
+
+table = QTable.read(paths.data / "gd1" / "gaia_ps1_xm.asdf")
+masks_table = QTable.read(paths.data / "gd1" / "masks.asdf")
+
+pm_edges = QTable.read(paths.data / "gd1" / "pm_edges.ecsv")
+pm_edges.add_index("label", unique=True)
+
+with asdf.open(
+    paths.data / "gd1" / "isochrone.asdf", lazy_load=False, copy_arrays=True
+) as af:
+    isochrone = af["isochrone"]
+    iso_medium = af["isochrone_medium"]
+
+
+###############################################################################
+
+_mask = (
+    # position cuts
+    (table["phi1"] > -80 * u.deg)
+    & (table["phi1"] < 10 * u.deg)
+    & (table["phi2"] > -4 * u.deg)
+    & (table["phi2"] < 2 * u.deg)
+)
+
+
+def _sel_patch(row: Row, k1: str, k2: str, **kwargs: Any) -> mpl.patches.Rectangle:
+    """Add a Rectangular patch to the plot."""
+    rec = mpl.patches.Rectangle(
+        (row[k1 + "_min"].value, row[k2 + "_min"].value),
+        row[k1 + "_max"].value - row[k1 + "_min"].value,
+        row[k2 + "_max"].value - row[k2 + "_min"].value,
+        **kwargs
+    )
+    rec.set_facecolor((*rec.get_facecolor()[:-1], 0.05))
+
+    return rec
+
+
[…]

### 2023-07-11 src/scripts/helper.py

@@ -1,0 +1,32 @@
+"""Exposes common paths useful for manipulating datasets and generating figures."""
+
+from scipy.interpolate import CubicSpline
+from torch import nn
+
+from stream_ml.core import ModelAPI
+from stream_ml.core.typing import Array, ArrayNamespace
+from stream_ml.core.utils.funcs import pairwise_distance
+from stream_ml.pytorch.builtin.compat import FlowModel
+
+
+def isochrone_spline(mags: Array, *, xp: ArrayNamespace[Array]) -> CubicSpline:
+    """Return a spline interpolating the isochrone's coordinates."""
+    pdist = pairwise_distance(mags, axis=0, xp=xp)
+    gamma = xp.concatenate((xp.asarray([0]), pdist.cumsum()))
+    gamma = gamma / gamma[-1]  # gamma in [0, 1]
+    return CubicSpline(gamma, mags)
+
+
+def manually_set_dropout(model: ModelAPI, p: float) -> tuple[ModelAPI]:
+    """Manually set dropout.
+
+    For use when pytorch ``.eval()`` doesn't work
+    """
+    for m in model.children():
+        if isinstance(m, nn.Dropout):
+            m.p = p
+        elif isinstance(m, FlowModel):
+            pass
+        else:
+            manually_set_dropout(m, p)
+    return model

### 2023-07-11 src/scripts/mock/model/define_model.py

@@ -1,0 +1,233 @@
+"""Train photometry background flow."""
+
+import sys
+from pathlib import Path
+
+import asdf
+import numpy as np
+import torch as xp
+from nflows.distributions.normal import ConditionalDiagonalNormal
+from nflows.flows.base import Flow
+from nflows.transforms.autoregressive import MaskedAffineAutoregressiveTransform
+from nflows.transforms.base import CompositeTransform
+from nflows.transforms.permutations import ReversePermutation
+from scipy.interpolate import CubicSpline
+from torch import nn
+
+import stream_ml.pytorch as sml
+from stream_ml.core.utils.funcs import pairwise_distance
+from stream_ml.pytorch.builtin import Parallax2DistMod
+from stream_ml.pytorch.params import ModelParameter, ModelParameters
+from stream_ml.pytorch.params.bounds import ClippedBounds, SigmoidBounds
+from stream_ml.pytorch.params.scaler import StandardLnWidth, StandardLocation
+
+# Add the parent directory to the path
+sys.path.append(Path(__file__).parent.parent.parent.as_posix())
+# isort: split
+
+import paths  # noqa: E402
+
+# =============================================================================
+# Load Data
+
+with asdf.open(
+    paths.data / "mock" / "data.asdf", lazy_load=False, copy_arrays=True
+) as af:
+    stream_abs_mags = af["stream_abs_mags"]
+
+    data = sml.Data(**af["data"]).astype(xp.Tensor, dtype=xp.float32)
+    scaler = sml.utils.StandardScaler(**af["scaler"]).astype(
+        xp.Tensor, dtype=xp.float32
+    )
+    object.__setattr__(scaler, "names", tuple(scaler.names))
+    coord_bounds = {k: tuple(v) for k, v in af["coord_bounds"].items()}
+
+
+# =============================================================================
+# Make Data
+
+coord_astrometric_names = ("phi2", "parallax")
+coord_photometric_names = ()
+phot_names = ("g", "r")
+coord_names = coord_astrometric_names + coord_photometric_names
+
+coord_astrometric_bounds = {k: coord_bounds[k] for k in coord_astrometric_names}
+coord_photometric_bounds = {k: coord_bounds[k] for k in coord_photometric_names}
+phot_bounds = {k: coord_bounds[k] for k in phot_names}
+
+
[…]

### 2023-07-11 src/scripts/mock/plot/photometric_background_selection.py

@@ -1,0 +1,59 @@
+"""Train photometry background flow."""
+
+import sys
+from pathlib import Path
+
+import asdf
+import matplotlib.pyplot as plt
+import numpy as np
+import torch as xp
+
+import stream_ml.pytorch as sml
+
+# isort: split
+# Add the parent directory to the path
+sys.path.append(Path(__file__).parent.parent.parent.as_posix())
+# isort: split
+
+import paths  # noqa: E402
+
+# =============================================================================
+
+plt.style.use(paths.scripts / "paper.mplstyle")
+
+
+with asdf.open(
+    paths.data / "mock" / "data.asdf", lazy_load=False, copy_arrays=True
+) as af:
+    data = sml.Data(**af["data"]).astype(xp.Tensor, dtype=xp.float32)
+    off_stream = np.array(af["off_stream"], dtype=bool)
+
+# =============================================================================
+
+fig, axs = plt.subplots(2, 1, figsize=(4, 4))
+
+axs[0].plot(
+    data["phi1"][off_stream],
+    data["phi2"][off_stream],
+    ls="none",
+    marker=",",
+    ms=1,
+    color="k",
+    rasterized=True,
+)
+axs[0].set_xlabel(r"$\phi_1 \ $ [$\degree$]")
+axs[0].set_ylabel(r"$\phi_2 \ $ [$\degree$]")
+axs[0].set_aspect(2)
+axs[0].grid(visible=True, which="both", axis="y")
+axs[0].grid(visible=True, which="major", axis="x")
+
+axs[1].scatter(
+    data["g-r"][off_stream], data["g"][off_stream], s=0.5, color="k", rasterized=True
+)
+axs[1].set_xlabel(r"$g-r \ $ [mag]")
+axs[1].set_ylabel(r"$g \ $ [mag]")
+axs[1].set_aspect("auto")
+axs[1].grid(visible=True, which="major")
+
+fig.tight_layout()
+fig.savefig(paths.figures / "mock" / "photometric_background_selection.pdf")

### 2023-07-11 src/scripts/paths.py

@@ -1,0 +1,26 @@
+"""Exposes common paths useful for manipulating datasets and generating figures."""
+from pathlib import Path
+
+# Absolute path to the top level of the repository
+root = Path(__file__).resolve().parents[2].absolute()
+
+# Absolute path to the `src` folder
+src = root / "src"
+
+# Absolute path to the `src/data` folder (contains datasets)
+data = src / "data"
+
+# Absolute path to the `src/static` folder (contains static images)
+static = src / "static"
+
+# Absolute path to the `src/scripts` folder (contains figure/pipeline scripts)
+scripts = src / "scripts"
+
+# Absolute path to the `src/tex` folder (contains the manuscript)
+tex = src / "tex"
+
+# Absolute path to the `src/tex/figures` folder (contains figure output)
+figures = tex / "figures"
+
+# Absolute path to the `src/tex/output` folder (contains other user-defined output)
+output = tex / "output"

### 2023-07-11 src/tex/ms.tex
[showyourwork] paper
Signed-off-by: nstarman <nstarman@users.noreply.github.com>

@@
 \usepackage{showyourwork}
-\usepackage{amsmath}
+\usepackage{amsmath, amssymb}
+\usepackage{gensymb}
 \usepackage{xcolor}
 \usepackage{booktabs}
-\usepackage{todonotes}
-
+\usepackage{dsfont}
+\usepackage[inline]{enumitem}
+\usepackage{cleveref}
+\usepackage{transparent}
+\usepackage{array}
+\usepackage{float}
+
+% Change the section names
+\renewcommand{\sectionautorefname}{\S\!}%
+\renewcommand{\subsectionautorefname}{\S\!\!}%
+\renewcommand{\subsubsectionautorefname}{\S\!}%
+\renewcommand{\equationautorefname}{Eq.}
+\renewcommand{\tableautorefname}{Table}
+\renewcommand{\figureautorefname}{Fig.}
+
+\newcommand{\code}[1]{\textsc{#1}}
+\newcommand{\package}[1]{\code{#1}}
+\newcommand{\stream}[1]{#1}
+\newcommand{\dataarchive}[1]{\textit{#1}}
+\newcommand{\Gaia}{\dataarchive{Gaia}}
+\newcommand{\PanStarrs}{\dataarchive{Pan-STARRS1}}
+
+% Math fonts
 \newcommand{\mrm}[1]{\mathrm{#1}}
@@
 \newcommand{\mcal}[1]{\mathcal{#1}}
-\newcommand{\unit}[1]{[\text{#1}]}
-
-\newcommand{\nth}[1]{{#1}_{\mrm{n}}}
-\newcommand{\fth}[1]{{#1}_{\mrm{f}}}
-\newcommand{\qth}[1]{{#1}_{\mrm{q}}}
-
-\newcommand{\pdf}{P}
-\newcommand{\cdf}{\Phi}
-
+
+% Math symbols
 \newcommand{\Exp}[1]{e^{#1}}
 \newcommand{\Erf}[1]{\mathrm{erf}\left(#1\right)}
-
-\newcommand{\sigobs}{{\sigma_*}}
-\newcommand{\JN}[1]{{\textcolor{red}{JN: #1}}}
-
 \NewDocumentCommand \dif {o m} {
@@
 
+% Statistics
+\newcommand{\pdf}{p}
+\newcommand{\cdf}{P}
+\newcommand{\likelihood}{\mcal{L}}
+\newcommand{\prior}{\mcal{\pi}}
+\newcommand{\posterior}{p}
+
+% Labels
+\newcommand{\nth}[1]{{#1}_{\mrm{n}}}  % measurement
+\newcommand{\fth}[1]{{#1}_{\mrm{f}}}  % feature
+\newcommand{\qth}[1]{{#1}_{\mrm{q}}}  % model index
+\newcommand{\unit}[1]{[\text{#1}]}
+
+\newcommand{\smallcomponent}[2]{#2^{\scriptscriptstyle (#1)}}
+\newcommand{\cmp}[2]{\smallcomponent{#1}{#2}}
+\newcommand{\Scmp}[1]{\cmp{S}{#1}}
+\newcommand{\Bcmp}[1]{\cmp{B}{#1}}
+\newcommand{\astroM}[1]{{#1}_w}
+\newcommand{\photoM}[1]{\smallcomponent{m}{#1}}
+\newcommand{\chemoM}[1]{\smallcomponent{z}{#1}}
+
+\newcommand{\Spdf}{\Scmp{\pdf}}
+\newcommand{\Bpdf}{\Bcmp{\pdf}}
+
+\newcommand{\parallax}{\varpi}
+\newcommand{\sigobs}{{\sigma_*}}
+
+\defcitealias{Ibata+2021}{I21}
+
 % Begin!
@@
 % Title
-\title{Characterizing Stellar Streams by ML}
+\title{Stream Members Only:\\ Data-Driven Characterization of Stellar Streams with Mixture Density Networks}
 
 % Author list
-\author{Nathaniel Starkman}
-\author{Jacob Nibauer}
-\author{Jo Bovy}
-\author{Jeremy Webb}
-
-% Abstract with filler text
+\author[0000-0003-3954-3291]{Nathaniel Starkman}
+\altaffiliation{Co-first author.}
+\affiliation{David A Dunlap Department of Astronomy and Astrophysics, University of Toronto, 50 St. George St, Toronto ON M5S 3H4, Canada}
+
+\author[0000-0001-8042-5794]{Jacob Nibauer}
+\altaffiliation{Co-first author.}
+\affiliation{Department of Astrophysical Sciences, Princeton University, 4 Ivy Ln, Princeton, NJ 08544, USA}
+
+\author[0000-0001-6855-442X]{Jo Bovy}
+\affiliation{David A Dunlap Department of Astronomy and Astrophysics, University of Toronto, 50 St. George St, Toronto ON M5S 3H4, Canada}
+
+\author[0000-0003-3613-0854]{Jeremy J. Webb}
+\affiliation{Department of Science, Technology and Society, York University, 4700 Keele St, Toronto ON M3J 1P3, Canada}
+
+\author[0000-0001-6584-6144]{Kiyan Tavangar}
+\affiliation{Department of Astronomy, Columbia University, 538 West 120th Street, New York, NY 10027, USA}
+
+\author[0000-0003-0872-7098]{Adrian Price-Whelan}
+\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA}
+
+\author[0000-0002-7846-9787]{Ana Bonaca}
+\affiliation{The Observatories of the Carnegie Institution for Science, 813 Santa Barbara Street, Pasadena, CA 91101, USA}
+
+\correspondingauthor{Nathaniel Starkman}
+\email{n.starkman@mail.utoronto.ca}
+
+\shortauthors{Starkman and Nibauer et al.}
+
 \begin{abstract}
-    Stellar stream membership likelihoods with ML. It works!
+
+    Stellar streams are sensitive probes of the Milky Way's gravitational
+    potential. The mean track of a stream constrains global properties of the
+    potential, while its fine-grained surface density constrains galactic
+    substructure. A precise characterization of streams from potentially noisy
+    data marks a crucial step in inferring galactic structure, including the
+    dark matter, across orders of magnitude in mass scales. Here we present a
+    new method for constructing a smooth probability density model of stellar
+    streams using all of the available astrometric and photometric data. To
+    characterize a stream's morphology and kinematics, we utilize mixture
+    density networks to represent its on-sky track, width, stellar number
+    density, and kinematic distribution. We model the photometry for each stream
+    as a single-stellar population, with a distance track that is simultaneously
+    estimated from the stream's inferred distance modulus (using photometry) and
+    parallax distribution (using astrometry). We use normalizing flows to
+    characterize the distribution of background stars. We apply the method to
+    the stream \stream{GD-1}, and the tidal tails of \stream{Palomar 5}. For
+    both streams we obtain a catalog of stellar membership probabilities that
+    are made publicly available.  Importantly, our model is capable of handling
+    data with incomplete phase-space observations, making our method applicable
+    to the growing census of Milky Way stellar streams. When applied to a
+    population of streams, the resulting membership probabilities from our model
+    form the required input to infer the Milky Way's dark matter distribution
+    from the scale of the stellar halo down to subhalos.
+
 \end{abstract}
@@
 
-    [Content Here]
-
-    \
-
-    Paper Map:
-    \begin{enumerate}
-        \item Intro
-        \item Method \begin{enumerate}
-            \item Fig 1: Overall explainer figure that illustrates the method with Neural networks, and norm flow for CMD
-            \item Fig 2: Bayesian graphical model
-            \item Test On Synthetic Stream:
-            \item Some sort of plot demonstrating successful recovery
-        \end{enumerate}
-        \item Application / Results \begin{enumerate}
-            \item Test case GD-1: \begin{enumerate}
-                \item CMD norm flow background
-                \item Fig: Stream phi1 phi2 top panel and histograms of each dimension below GD-1
-                \item Some plot in phi1-phi2 that shows density variations
-            \end{enumerate}
-            \item Test case Pal-5 \begin{enumerate}
-                \item CMD norm flow background
-                \item Fig: Stream phi1 phi2 top panel and histograms of each dimension below Pal 5
-                \item Some plot in phi1-phi2 that shows density variations
-            \end{enumerate}
-        \end{enumerate}
-        \item Conclusion
-        \item Appendix
-    \end{enumerate}
+    Stellar streams are the disrupted remnants of globular clusters and
+    satellite galaxies, and their census has grown extensively in the Milky Way
+    thanks to all-sky astrometric missions like \Gaia{}
+    \citep{GaiaCollaboration+2016, GaiaCollaboration+2023} and low-surface
+    brightness photometric surveys (e.g., \citealt{Ibata+1998,
+    GrillmairDionatos2006, Shipp+2018, Ibata+2021}).  The formation of streams
+    can be traced back to a progenitor (a globular cluster or satellite galaxy)
+    whose stars are gradually lost to the tidal field of the host galaxy. The
+    stars extend along a series of similar orbits, called tidal tails, which can
+    sometimes span several tens of degrees across the sky. The orbital proximity
+    of stars belonging to a stream makes them sensitive tracers of the mass
+    distribution of galaxies, sourced by both the baryonic and dark matter
+    components.
+
+    The average properties of a stream (e.g., the mean position and velocity
+    track of the tidal tails) can be used to reconstruct the global dark matter
+    distribution of the stellar halo (e.g., \citealt{Johnston+1999, Bonaca+2014,
+    Bovy2014, Bovy+2016, Nibauer+2022, Koposov+2023}), while local variations in
+    the stream track and surface density encode information about the stream's
+    progenitor \citep{Kupper+2012, Sanders+2013, Price-Whelan+2014}, encounters
+    with baryonic structures such as the stellar bar (e.g., \citealt{Erkal+2017,
+    Pearson+2017}), and non-luminous structures like dark matter subhalos (e.g.,
+    \citealt{Ibata+2002, Johnston+2002, Carlberg+2012-74820C, Bovy+2017,
+    Bonaca+2019, Hermans+2021}).
+
+    While several methods have been developed to model stream properties as a
+    function of global halo characteristics (e.g., the mass distribution,
+    flattening; \citealt{Johnston+1999, Binney2008, Koposov+2010,
+    SandersBinney2013, Bovy2014, Nibauer+2022}) and local substructures (e.g.,
+    the bar's pattern speed and the mass of subhalo perturbers;
+    \citealt{Antoja+2014, Hattori+2016, Price-Whelan+2016, Bovy+2017,
+    Pearson+2017, Bonaca+2019}), these methods often rely on the existence of a
+    homogenized stream-tracer population that characterizes a given stream
+    across each of the observable phase-space dimensions.  Additionally, because
+    even the fine-grained properties of streams are influenced by the detailed
+    mass distribution of its host galaxy, it is important to propagate errors
+    both in measurement uncertainty and membership uncertainty (i.e., which
+    stars belong to the stream versus the background) when attempting to model a
+    stream. Otherwise, a poorly characterized stream could bias constraints on,
+    e.g., the total mass of the galaxy, the dark matter halo shape, and the mass
+    of subhalo perturbers.  In order to generate more precise constraints on the
+    structure of the galaxy, it is therefore imperative that a statistically
+    sound and homogenized catalog of stellar streams is produced.
+
+    While streams are well described in action-angle coordinates
+    \citep[e.g.][]{Bovy2014} or (restricted) $N$-body simulations
+    \citep[e.g.][]{Dehnen+2004}, these methods rely on prior assumptions about
+    the galaxy and its underlying gravitational potential.  Therefore, it is
+    necessary to devise data-driven methods to characterize stellar streams
+    without appealing to strong prior assumptions about the galaxy's structure.
+
+    There are a few previous works which have modeled stellar streams in this
+    context. \citet{Patrick+2022} developed the method introduced by
+    \citet{Erkal+2017}, which is a data-driven, spline-based method for modeling
+    the photometric properties and on-sky positions of previously identified
+    streams. Their method works by fitting the stream's stellar surface density
+    with a series of splines, capturing both surface brightness variations along
+    the stream and changes in the position of the stream track and width. Their
+    method also utilizes an isochrone fit to a given stream, from which a
+    distance modulus can be derived. While this method is very successful at
+    characterizing the photometric properties of a stream, it does not consider
+    the kinematic dimensions which have become increasingly well-measured with
+    successive data releases from \Gaia{}, as well as targeted observations.
+    From a population of RR Lyrae stars, \citet{Price-Whelan+2019} utilized a
+    mixture model to fit the globular cluster stream Pal-5 in the space of
+    proper motions and heliocentric distances.  The mixture modeling approach
+    enables a simultaneous fit to both the stream and background density,
+    allowing for a cleaner selection of stream stars. However, the track of the
+    stream in on-sky coordinates is not fit. The method identified 27 RR Lyrae
+    stars consistent with being members of the stream. While useful for
+    determining the average properties of a stream (e.g., its mean distance
+    track), a limited population of RR Lyrae stars are not sufficient to capture
+    the small-scale properties of streams expected to inform constraints on,
+    e.g., a population of perturbers in the galaxy.
+
+    Other methods for extracting stellar streams from the data include
+    matched-filter algorithms, where over-densities in color-magnitude space are
+    inspected as possible clusters undergoing tidal stripping
+    \citep{Grillmair+1995, GrillmairJohnson2006, Shipp+2018}.  While the
+    matched-filter technique has been extremely successful in stream discovery,
+    it is not equipped to characterize streams at the level of detail necessary
+    to inform precise constraints on the potential of the galaxy and its
+    substructure.
+
+    In order to address the need for a flexible model of stellar streams both in
+    photometric and kinematic spaces, in this work we develop a new method for
+    characterizing streams and quantifying the membership probability of
+    possible stream stars. Our approach provides several key advantage over
+    previous stream modeling efforts, specifically in its ability to jointly
+    model the kinematic and photometric properties of streams simultaneously
+    using a flexible model.  Furthermore, our method is well-suited to fitting
+    streams with only partial or incomplete phase-space or photometric
+    observations, enabling a full characterization of streams insofar as the
+    available data allows.
+
+    \paragraph{Paper organization}
+
+        The paper is organized as follows.  In \autoref{sec:method} we introduce
+        our method for characterizing stream tracks and computing stellar
+        membership probabilities.  We discuss initial data processing in
+        \autoref{sub:method:framing_the_data} and build a probabilistic
+        framework to model the stream and background in
+        \autoref{sub:method:likelihood_setup}-\autoref{sub:methods:priors}.  In
+        \autoref{sec:results_mock} we apply our method to simulated data to
+        demonstrate the model with a known ground truth dataset, then to the
+        stellar streams \stream{GD-1} (\autoref{sec:results_gd1}) and
+        \stream{Pal\,5} (\autoref{sec:results_pal5}).  We compare our model to
+        other methods in \autoref{sec:discussion}.  We conclude in
+        \autoref{sec:conclusions}, discussing the results of this work and
+        future directions.
 
@@
 
+\newpage
 \section{Method} \label{sec:method}
 
-    Stellar streams
-
-    \subsection{Likelihood Setup}\label{sub:likelihood_setup}
-
-        \begin{figure}
+    Below, we offer a concise overview of our approach, followed by a more
+    in-depth technical explanation in subsequent sections.  We start, in
+    \autoref{sub:method:framing_the_data}, by transforming the astrometric data
+    into a stream-oriented on-sky reference frame ($\phi_1, \phi_2, \parallax,
+    \mu_{\phi_1}^*, \mu_{\phi_2}, v_r)$, for each stream.  In this frame, the
+    stream track lies along $\phi_1$, and the stream density may be described by
+    distributions in the other parameters as injective functions of $\phi_1$
+    (called conditional distributions).  Likewise, the background of the
+    Galactic field may be described with $\phi_1$-conditioned distributions.  We
+    will also model the stream in photometric coordinates.  Additional features,
+    e.g.  metallicity, can also be modeled along the stream and background as
+    functions of $\phi_1$, though we leave this to a future work.
+
+    The distributions for the stream and background are collected in a single
+    mixture model that describes the entire field.  We take the parameters of
+    the mixture model --- the mixture weights and component distribution
+    parameters --- to be general (continuous) functions of $\phi_1$, the
+    conditioning variable. This is done using a feed-forward neural network that
+    takes $\phi_1$, the conditioning variable, as its input and outputs the
+    parameter value(s) that characterize the distribution of stars at a $\phi_1$
+    ``slice".  Mixture models of conditional probability distributions using
+    neural networks are called Mixture Density Networks (MDNs)
+    \citep{Bishop+1994}.  Since the model coefficients may evolve with $\phi_1$,
+    MNDs are well suited to characterize streams (and the background) with all
+    their variations in position, width, and linear density.
+
+    % sub: framing_the_data (end)
+
+    \subsection{Framing the Data} \label{sub:method:framing_the_data}
+
+        As a stream progenitor orbits the Galactic center of mass, its path can
+        be approximated locally as an elliptical segment. The associated arms of
+        the stream generally align closely with its orbital plane.  As viewed
+        from a Galactocentric reference frame, the stream approximately assumes
+        the form of a great circle enabling a 1:1 mapping from some phase
+        parameter to a unique position along the stream. Thus in a `stream'
+        oriented frame the rotated longitudinal and latitudinal coordinates
+        ($\phi_1, \phi_2$) align with the stream such that the stream's phase is
+        $\phi_1$ and $\phi_2 \simeq 0$.
+
+        While it would be ideal to characterize streams in this Galactocentric
+        frame, transformation to the frame requires knowledge of the distance to
+        the Galactic center  \citep{GRAVITY2018, BennettBovy2019, Leung+2022},
+        the solar motion around the Galactic center, and accurate distances to
+        field stars (among other uncertain quantities). In a heliocentric frame,
+        e.g. the standard ICRS\footnote{International Celestial Reference
+        System} \citep{ICRS1997}, projection effects can obscure the shape of a
+        stream leading to a non-trivial stream track. Therefore in a
+        heliocentric frame, there is no assurance of effecting a rotation like
+        in the Galactocentric frame that would similarly align the stream in an
+        observer's coordinates such that $\phi_2(\phi_1) \approx 0$.
+        Thankfully, most streams are adequately distant from both the Galactic
+        center and the observer, or exhibit orientations such that a rotation a)
+        can be established or b) holds valid. For most of the best-studied
+        globular cluster streams -- \stream{GD-1}, \stream{Palomar 5},
+        \stream{Jhelum}, etc. -- this holds true. However for some streams of
+        dwarf galaxies, like the Magellanic and Sagittarius streams which each
+        wrap around the Milky Way \citep{Newberg+2002, Majewski+2003,
+        WannierWrixon1972}, no such transformation is possible. More generally,
+        a stream's ``sky"-projected path may be kinked, e.g. by subhalo
+        interactions, such that it is a many-to-one function in $\phi_1$.
+
+        In this work we consider the vast majority of streams that can be
+        described as an injective function, $\phi_2(\phi_1)$.  Since we are
+        examining known streams this transformation is known \textit{a priori},
+        or may be constructed during pre-processing
+        \citep[see][\S2.1]{Starkman+2023}.  We note that, with sufficient prior
+        knowledge, many-to-one functions may be broken into injective segments
+        and their connection constrained by a prior. Thus the methods developed
+        here may be extended and applied even to wrapped and kinked streams.
+        However, we leave extending the model framework to a future work.
+
+    \subsection{Likelihood Setup}\label{sub:method:likelihood_setup}
+
+        \begin{figure*}
+            \script{pgm.py}
             \centering
-        \includegraphics[scale=0.5]{figures-not-syw/DAG_StreamDensity.pdf}
-        \caption{Fill in.}
-        \label{fig: DAG}
-        \end{figure}
-
-        We model the stream and background as functions continuous in some affine parameter.
-In principle this parameter can be anything.
-Though it might seem the best parameter is the stream's arc length, the most common, easiest, and practical parameter is the longitude -- $w_{\cdot, j\equiv0} \equiv \phi_1$ -- in some stream-oriented reference frame \citep[for details see][section 2]{2023MNRAS.522.5022S}.
-
-        We model the likelihood for a single star as
-        \begin{align} \label{eq:general_model}
+            \includegraphics[scale=0.6]{figures/pgm.pdf}
+            \caption{%
+                Probabilistic Graphical Models (PGMs) of the Mixture Density
+                Networks used in this work.
+                %
+                \textbf{Left}: A PGM of the stream model. The full dataset
+                $x_n^{obs}$ is the aggregation of the observed astrometry
+                $w_n^{obs}$ and photometry $m_n^{obs}$, along with the
+                corresponding observational errors. We model the data as a
+                mixture of Gaussians (in astrometry + distance modulus), with
+                the Gaussians indexed by $q$. The weight $\alpha$ determines the
+                weighted contribution of each Gaussian to each datum. All models
+                are conditioned on $\phi_1$.
+                %
+                \textbf{Right}: a PGM of the background model. The data are
+                identical to that of the stream, however the model is not a
+                mixture of Gaussians, but of a variety of distributions. We
+                further distinguish between trainable distribution parameters
+                (circles) and fixed distributions (points), like a pre-trained
+                normalizing flow background model, explained in further detail
+                in \autoref{sub:method:pre-training_distributions}. Alike to the
+                stream model, all background models are conditioned on $\phi_1$.
+                % 
+            }
+            \label{fig:PGM}
+        \end{figure*}
+
+        Mixture models are a statistical method to represent a population as a
+        set of a sub-populations specified by probability distributions.  These
+        distributions are characterized by their parameters and the mixture by a
+        corresponding set of mixture coefficients. Scalar mixture models may be
+        extended to model completely general conditional distributions by making
+        the distribution parameters and mixture coefficients into functions of a
+        conditional input \citep{McLachlanBasford1989}.  Mixture Density
+        Networks (MDNs) are a machine learning method to implement these general
+        mixture models, taking the parameters and coefficients to be the outputs
+        of feed-forward neural networks and as such, general continuous
+        functions \citep{Bishop1994}.  Functional parameters allow the model to
+        capture variation over those parameters that is not possible with
+        scalar-valued models. Moreover, by using neural networks the inferred
+        functional forms are ``model-free" and driven entirely by the data.
+
+        For the MDN we take $x_{\cdot, 0}$, the first feature column of the data
+        $\{\mbf{x}\}$, as the `independent' coordinate over which the MDN
+        parameters are conditioned. In the context of streams $x_{\cdot, 0}
+        \equiv \phi_1$ is the longitude coordinate in a reference frame rotated
+        such that the stream is aligned along $\phi_1$. The parameters of the
+        stream, the background field, and the mixing coefficients of the two are
+        now general data-driven continuous functions along $\phi_1$.
+
+        The PDF of a general MDN is
+        \begin{equation} \label{eq:general_mixture_network}
+            \!\!\! \pdf(\nth{\mbs{x}} | \mbs{\theta}(\phi_1))
+            \!=\! \sum_{\mrm{q} \in \mbs{I_Q}} \! \qth{f}(\phi_1) \cmp{q}{\pdf}\left(\nth{\mbs{x}}|\qth{\mbs{\theta}}(\phi_1)\right),
+        \end{equation}
+        where $\cmp{q}{\pdf}$ is the PDF of the $q$-th model and $f_q$ its
+        mixing coefficient for all $q$ models in the set of models indexed by
+        $\mbs{I_Q}$. $\mbs{\theta}$ is the $\phi_1$-conditional output of the
+        feed-forward neural network, and $\nth{\mbs{x}}$ the data on the $n$-th
+        star in $\{\mbs{x}\}$, not including $\phi_1$. For convenience we drop
+        the implied subscript $n$ in $\phi_1$, the explicit notation of
+        $\mbs{\theta}$'s dependence on $\phi_1$, and the index set $\mbs{I}_X$
+        in summations over its elements $x$.
+
+        The mixture coefficients $\qth{f}$ are normalized such that
+        \begin{equation} \label{eq:mixture_weight_sum}
+            \sum_{\mrm{q}} \qth{f}(\phi_1) = 1, \qquad \forall \phi_1
+        \end{equation}
+        In practice this is enforced by defining a background
+        \begin{equation} \label{eq:mixture_weight_normalization}
+            f_{b}(\phi_1) = 1 - \sum_{\rm{q}\in \mbs{I_Q}\backslash \{b\}} \qth{f}(\phi_1),
+        \end{equation}
+        the summation over all models except for some ``background" index $b \in
+        \mbs{I_Q}$.  In the context of Galactic streams the ``foreground" is the
+        stream itself, while the background is the Galaxy --- bulge, bar, disc,
+        halo --- and additional structures, like globular clusters and dwarf
+        galaxies, that are not associated with the stream itself.  We discuss
+        the mixture weights further in \autoref{sub:method:mixture_weight}.
+
+        In this work we consider primarily astrometric and photometric data,
+        (notated $\{\mbs{w}\}$ and $\{\mbs{m}\}$, respectively), but note that
+        the MDN framework may be extended to arbitrary feature dimensions.
+        Assuming the conditional independence of the astrometry and
+        photometry\footnote{ For \Gaia{} data this is true in practice but not
+        in detail: there exist small correlations between the astrometric and
+        photometric data.}, we split each model into linearly separable
+        astrometric and photometric models $\cmp{q}{\pdf} = \cmp{q,w}{\pdf}
+        \cmp{q,m}{\pdf}$.
+
+        The likelihood for a single star then becomes, simplifying from
+        \autoref{eq:general_mixture_network},
+        \begin{equation} \label{eq:general_model}
+            \!\!\!\!\! \pdf(\nth{\mbs{w}}, \! \nth{\mbs{m}} | \mbs{\theta})
+                \!=\! \sum_{q} \! f_q(\phi_1) \cmp{q,w}{\pdf}(\nth{\mbs{w}}|\mbs{\theta}) \cmp{q,m}{\pdf}(\nth{\mbs{m}}|\mbs{\theta})
+        \end{equation}
+
+        Assuming the measurement of each star is independent, the total
+        log-likelihood is a sum over all stars:
+        \begin{equation} \label{eq:general_likelihood}
+            \ln\mcal{L}\left(\{\nth{\mbs{w}},\nth{\mbs{m}}\} | \mbs{\theta}\right) = \sum_n \ln \pdf(\nth{\mbs{w}}, \nth{\mbs{m}} | \mbs{\theta}).
+        \end{equation}
+
+        It will prove convenient to distinguish the models for $q$ as the
+        \textit{background} and \textit{stream} models, respectively. In this
+        notation:
+        \begin{align} \label{eq:stream_and_bkg_prob}
             \pdf(\nth{\mbs{w}}, \nth{\mbs{m}} | \mbs{\theta})
-                &= \sum_{q} \ f_q(w_{i, 0}) \pdf(\nth{\mbs{w}}|\mbs{\theta},q_i\!=\!q) \pdf(\nth{\mbs{m}}|\mbs{\theta},q_i\!=\!q)
+            =& \phantom{+} \qquad f \phantom{+} \Spdf(\nth{\mbs{w}}|\mbs{\theta}) \Spdf(\nth{\mbs{m}}|\mbs{\theta}) \\
+            & + (1-f) \Bpdf(\nth{\mbs{w}}|\mbs{\theta}) \Bpdf(\nth{\mbs{m}}|\mbs{\theta}), \nonumber
         \end{align}
-        where we have assumed that $\nth{\mbs{w}}$ and $\nth{\mbs{m}}$ are conditionally independent, and that the mixture weights $f$ are normalized s.t.
-$\sum_q f(w_{i,0}) = 1$.
-We discuss the mixture weights further in \autoref{sub:mixture_weight}
-
-        Assuming the measurement of each star is independent, the total log-likelihood is a sum over all stars:
+        where we have dropped the $(w), (m)$ superscript as the model types are
+        evident from their inputs. We applied
+        \autoref{eq:mixture_weight_normalization} to require only a single
+        mixture coefficient.  Note that the stream and background PDFs can
+        consist of further components. This will become important for our
+        characterization of the stream \stream{GD-1}, which appears spatially
+        bifurcated. We note this as an implementation detail since all
+        stream-related components (cold, extra-tidal, perturbed) and all other
+        components (stellar halo, globular clusters, etc) may be grouped into
+        multi-component \autoref{eq:stream_and_bkg_prob} \textit{stream} and
+        \textit{background} models.  The stream and background models are
+        included graphically in \autoref{fig:PGM}, where the left plot shows the
+        stream model, and the right the background.
+
+        The probability of a being a stream member is then simply
+        \begin{equation}\label{eq:membership_prob}
+            \pdf\!\left(S | \nth{\mbs{w}}, \nth{\mbs{m}}, \mbs{\theta} \right)
+            = \frac{f \Spdf(\nth{\mbs{w}}|\mbs{\theta}) \Spdf(\nth{\mbs{m}}|\mbs{\theta}) }{ \pdf(\nth{\mbs{w}}, \nth{\mbs{m}} | \mbs{\theta})}.
+        \end{equation}
+
+        Hereafter, when we refer to ``membership probability,"
+        \autoref{eq:membership_prob} provides the formal definition. We nuance
+        this definition by considering missing feature dimensions in the
+        following subsection.
+
+    \subsection{Missing Phase-Space Observations}
+    \label{sub:method:missing_data}
+
+        Streams have a diversity of measurement coverage: several have full 6-D
+        astrometrics as well as photometry and chemical abundances available
+        \citep[e.g.,][]{Koposov+2019, Antoja+2020, Li+2022}, while most have
+        partial coverage, lacking some feature dimensions.  Most streams
+        detected by \Gaia \citep{Gaia2016, Gaia2023}, for instance, have proper
+        motions but not radial velocities nor high signal-to-noise parallax
+        measurements.  Follow-up surveys, like \dataarchive{S5} \citep{Li+2019},
+        add many feature dimensions, however only for a select set of streams.
+        Given the diversity of coverage it is important that the likelihood
+        model -- \autoref{eq:membership_prob} -- account for missing data.
+
+        The method of treatment of missing data depends on the cause for that
+        data to be missing.  Broadly, there are two categories of causes:
+        randomness and systematics.  Consider a dataset with all features
+        measured but with a random subset of features masked.  One possible
+        approach is to attempt to impute the missing features, then feed the
+        full-featured data to the likelihood model. Alternatively, the
+        likelihood model might use only the present features, ignoring those
+        missing. If however, features are missing for systematic reasons, due to
+        a selection function, then this approach will introduce systematic bias.
+        The way to avoid bias where the data is incomplete due to the selection
+        function is to know that selection function. Otherwise the probabilities
+        will not be properly normalized.  Selection functions are often very
+        challenging to characterize, so it is routine and convenient to simply
+        cut the data where the effects of the selection function become
+        significant.  Not including such affected data moves the contribution of
+        the selection function from a prior to the evidence.  Our models compute
+        likelihoods under a specific dataset, and \autoref{eq:membership_prob}
+        is a ratio of the probabilities, so the removed selection functions are
+        not expected to be impactful.
+
+        We adopt the approach of modeling the data masks as randomly-distributed
+        and not systematic. We do not impute missing data, instead the per-star
+        likelihood is modeled with a distribution with the same dimensionality
+        as the data vector.  For example, a star with a 6D astrometric
+        measurement will be modeled with a full 6D distribution, while a star
+        missing its radial velocity measurement will be modeled with a
+        dimensionally-reduced (5D) form of the 6D distribution. Using
+        dimensionally reduced distributions ensure that missing phase-space
+        dimensions do not amplify nor suppress the likelihood.  Notwithstanding,
+        we include a quality flag on our calculations indicating the number of
+        missing features.  We leave incorporating priors on the data mask
+        distribution to future work.
+
+    % sub: missing_phase_space_observations (end)
+
+    \subsection{Pre-training distributions} 
+    \label{sub:method:pre-training_distributions}
+
+        In \autoref{sub:method:likelihood_setup} we set up the general
+        mathematical framework of MDNs, then specified the models on two axes:
+        the component and the data type. Broadly, the components are stream
+        versus background and the data types are astrometric and photometric.
+        For some components, e.g. the stream, the data density will be well fit
+        by an analytic function.  For others, no analytic density provides a
+        realistic description of the data. In this work we take a data-driven
+        approach, and represent non-analytic distributions using a normalizing
+        flow model.
+
+        Normalizing flows provide a flexible description of a probability
+        density, by transforming samples generated from a simple base
+        distribution (i.e., a Gaussian) to the more complicated target
+        distribution \citep{EstebanVanden2010, Rippel2013, RezendeMohamed2015}.
+        The transformations are typically non-linear outputs of a neural
+        network, whose parameters are optimized until the target density
+        accurately characterizes the data. The neural network transformation is
+        differentiable, so that jacobian factors can be combined to ensure that
+        the target distribution remains a valid probability density (i.e.,
+        integrates to one) \citep{Kobyzev+2019}.  For the neural networks we
+        regularize the data (minus the mean, divided by the standard deviation
+        per feature column); thus we correct the overall normalization of the
+        flow by the product of the jacobian of the regularization operation.
+
+        Our implementation is as follows. For a given stream, we restrict the
+        data to some field characterized by a polygon drawn around the stream.
+        Because our density modeling is aimed at stream characterization rather
+        than discovery, we assume that the stream is sufficiently well known so
+        that it can be masked out as a simple cut in (e.g.) $\phi_1-\phi_2$
+        coordinates. With the stream masked out, we then fit a normalizing flow
+        to the data. Because the distribution can evolve with $\phi_1$, we fit a
+        \emph{conditional} normalizing flow, $q_{\rm flow}(\mathbf{x}|\phi_1)$.
+        Our central assumption with this model is that the distribution for
+        background stars in the masked region are quantitatively similar to
+        those in the unmasked region. For a sufficiently narrow mask we expect
+        this to be the case, and find that this assumption does not introduce
+        bias for the streams considered in this work.
+
+        Once the normalizing flow, $q_{\rm flow}\left(\mathbf{x} |
+        \phi_1\right)$, is fit to the data, its parameters are fixed while the
+        other components of the model begin training. Therefore, the normalizing
+        flow can be rapidly trained and computed as a pre-processing step.
+
+        It is easy to evaluate the log-likelihood of a normalizing flow at a
+        point $\mbs{x}$ when all feature dimensions are present. When one (or
+        more) feature dimension is missing, however, evaluating the marginal
+        log-likelihood involves integrals over the flow. While the procedure is
+        straightforward it is computationally expensive. As an alternative, we
+        conservatively set the log-likelihood to $0$, the maximum value,
+        overemphasizing the flow's contribution to the background model.
+        Conceptually, up-weighting the background model decreases the
+        false-positive rate in stream membership identification, at the cost of
+        increasing the false-negative rate.  Another approach, which we leave to
+        a future work, is to construct normalizing flows of each marginal
+        distribution, e.g. $q_{\rm flow}\left(\{x_i\}_{i \in \mbs{I}_F, i \neq
+        {j, k}} | x_j, x_k, \phi_1\right)$, and select for each $\nth{\mbs{x}}$
+        the correct flow given the present features.
+
+    % sub: pre-training_distributions (end)
+
+    \vspace{10pt}
+    \subsection{Determination of the Mixture Weight} \label{sub:method:mixture_weight}
+
+        The mixture weight $f_q(\phi_1)$ as used in \autoref{eq:general_model}
+        is characterized as the fraction of stars belonging to the mixture
+        component $q$ over an increment $[\phi_1, \phi_1 + \dif{\phi_1}]$. Thus,
+        the mixture weight encodes information about the linear density of the
+        stream, which has been shown to depend on substructure in the galaxy
+        \citep{Siegal-GaskinsValluri2009, Yoon+2011}. The dependence of the
+        mixture weight on the linear density is captured by the expression
+        \begin{equation}\label{eq:fraction_param}
+            f_q\left(\phi_1\right) = \frac{n_q\left(\phi_1\right)}{n_{\rm tot}\left(\phi_1\right)},
+        \end{equation}
+        where $n_q\left(\phi_1\right)$ is the number density of stars in
+        component $q$ (i.e., the number of stars belonging to component $q$ per
+        $\phi_1$ interval), and $n_{\rm tot}$ is the total number density of
+        stars in the same interval (including those in component $q$). The
+        linear  density for component $q$ is then entirely specified by the
+        function $n_q(\phi_1)$.
+
+        The mixture model specified in \autoref{eq:general_model} only models
+        the weight parameter $f_q$, and not the components of the ratio in
+        \autoref{eq:fraction_param}. However, the linear density $n_q(\phi_1)$
+        can be readily obtained from $f_q$, provided that $n_{\rm
+        tot}\left(\phi_1\right)$ can be calculated. Importantly, this function
+        does not depend on the parameters of the on-stream or off-stream model.
+        Instead, $n_{\rm tot}(\phi_1)$ is simply proportional to the number of
+        stars in a small $\phi_1$ increment. We therefore model $n_{\rm
+        tot}\left(\phi_1\right)$ as a post-processing step using a single
+        normalizing flow in $\phi_1$.
+
+        In particular, for a given field the distribution of $\phi_1$
+        coordinates is specified by the set $\{\phi_1\}_f$. A normalizing flow
+        is trained to this dataset, and will satisfy $\int d\phi_1
+        P_{\phi_f}(\phi_1) = 1$ by construction.  We can then obtain the linear
+        stream density with
         \begin{equation}
-            \ln\mcal{L}\left(\{(\nth{\mbs{w}},\nth{\mbs{m}})\} | \mbs{\theta}\right) = \sum_i  \ln \pdf(\nth{\mbs{w}}, \nth{\mbs{m}} | \mbs{\theta}).
+            n_q\left(\phi_1\right) = f_q\!\left(\phi_1\right) \, n_{\rm tot}\!\left(\phi_1\right)  \equiv f_q\!\left(\phi_1\right) P_{\phi_1}\!\!\left(\phi_1\right) .
         \end{equation}
 
-        It will prove convenient to distinguish the models for $q=0,1$ as the \textit{background} and \textit{stream} models, respectively. In this notation:
-
-        \begin{multline}
-            \pdf(\nth{\mbs{w}}, \nth{\mbs{m}} | \mbs{\theta}) 
-            = \\\phantom{+} \ \quad f \quad\ P^{(S)}(\nth{\mbs{w}}|\mbs{\theta}) P^{(S)}(\nth{\mbs{m}}|\mbs{\theta})  \\
-            \quad + (1-f) P^{(B)}(\nth{\mbs{w}}|\mbs{\theta}) P^{(B)}(\nth{\mbs{m}}|\mbs{\theta}), \nonumber
+    % subsection: determination_of_the_mixture_weight (end)
+
+    \subsection{Astrometric Model} \label{sub:method:astrometric_model}
+
+        \subsubsection{On-Stream} \label{ssub:method:astrometric_model:on_stream}
+
+            The N-dimensional astrometric track is modeled with a single neural
+            network, parameterized as a function of $\phi_1$.  The neural
+            network output for a single stream component is the mean location of
+            the stream track in each dimension, $\astroM{\mbs{\mu}}(\phi_1)$,
+            and its associated covariance matrix
+            $\astroM{\mbs{\Sigma}}(\phi_1)$. The probability for the data is
+            then
+            \begin{equation}
+                \cmp{S,w}{\pdf}(\nth{\mbs{w}} | \mbs{\theta})
+                \!= \mcal{N}_F \big(\nth{\mbs{w}} | \astroM{\mbs{\mu}}\!(\phi_1), {\cmp{w}{\nth{\mbs{\Sigma}}}}^2 \! + \!  \astroM{\mbs{\Sigma}}^2\!\left(\phi_1\right) \!\big),
+            \end{equation}
+            where $\astroM{\mbs{\theta}}$ is the set of neural network
+            parameters that define $\astroM{\mbs{\mu}}$ and
+            $\astroM{\mbs{\Sigma}}$; and $\cmp{w}{\nth{\mbs{\Sigma}}}$ the data
+            uncertainties.  In the simplest case, we take
+            $\cmp{w}{\nth{\mbs{\Sigma}}}, \astroM{\mbs{\Sigma}}$ to be diagonal,
+            consisting of both intrinsic dispersion for each dimension of
+            $\mbs{w}$ and the data uncertainties added in quadrature. The data
+            uncertainties $\cmp{w}{\nth{\mbs{\Sigma}}}$ are elements of
+            $\mbs{\delta}\mbf{W}$, the dataset of astrometric uncertainties.
+
+            In practice, we work with truncated Gaussians, where the truncation
+            is set by the size of the field in each astrometric dimension.
+            Details of the truncated Gaussian are included in
+            \autoref{app:sub:normal_distribution}. Truncating to the field
+            ensures that the probability density is zero wherever there is no
+            data. This has an added benefit of correctly normalizing the
+            Gaussian distribution, which is not compact (has non-zero
+            probability over all space) and would otherwise not integrate to one
+            within the field.
+
+            As a MDN, we implement the Gaussian distribution parameters with a
+            multi-layered feed-forward neural network. The number of layers
+            required depends on the maximum dimensionality of the Gaussian, and
+            whether the neural network employs regularization techniques like
+            dropout. We use alternating layers of linear and tanh units. Details
+            of the network architecture are discussed in
+            \autoref{sub:methods:model_implementation}.
+
+            If a particular observation has missing phase-space coordinate(s) $f_k$, we reduce
+            the dimensionality of the Gaussian to that of the data-vector.
+            Namely, for $\mbs{I}_{\tilde{F}} \equiv \mbs{I}_{F} \backslash
+            \{f_k\}$
+            \begin{align}
+                \nth{\tilde{\mbf{w}}} &\mapsto \nth{\tilde{\mbf{w}}} = \{ w_{n,f} | f\in \mbs{I}_{\tilde{F}}\}, \nonumber\\
+                \astroM{\mbs{\mu}} &\mapsto \astroM{\tilde{\mbs{\mu}}} = \{ \mu_{f} | f\in \mbs{I}_{\tilde{F}}\}, \nonumber\\
+                \astroM{\mbs{\Sigma}} &\mapsto \astroM{\tilde{\mbs{\Sigma}}} = \{ \Sigma_{i,j} | i,j \in \mbs{I}_{\tilde{F}} \}, & \nonumber
+                \intertext{such that,}
+                \Spdf(\nth{\mbs{w}} & | \astroM{\mbs{\theta}}(\phi_1))
+                    \mapsto \Spdf(\nth{\tilde{\mbs{w}}} | \astroM{\tilde{\mbs{\theta}}} (\phi_1))\,.
+            \end{align}
+
+        % ssub: on_stream (end)
+
+        \subsubsection{Off-stream}
+
+            \label{ssub:method:astrometric_model:off_stream} We now outline the
+            off-stream astrometric model. We take a similar approach to the
+            on-stream astrometric model discussed in
+            \autoref{ssub:method:astrometric_model:on_stream}, though we
+            typically do not characterize the backgrounds with a Gaussian
+            distribution. Instead, we utilize a range of distributions (i.e.,
+            exponential, skew-normal) discussed in \autoref{app:distributions}.
+            The parameters of the user-specified background distributions are
+            themselves neural network outputs, such that any $\phi_1$ ``slice"
+            of the background should be characterized by some analytic density,
+            but the evolution of the backgrounds with $\phi_1$ can be complex.
+            Details of the network architecture are discussed in
+            \autoref{sub:methods:model_implementation}.
+
+            Let $\Bcmp{\fth{\mbs{\theta}}}(\phi_1)$ represent the neural network
+            which outputs a vector of parameters characterizing the background
+            distribution at a given $\phi_1$ for astrometric dimension $f$. The
+            number of outputs for the background model is equal to
+            $\mathrm{dim}\left(\fth{\Bcmp{\mbs{\theta}}}\right)$ (where $f=0$
+            corresponds to $\phi_1$, which we do not model). At a given
+            $\phi_1$, the probability density for the astrometric dimension
+            $f>0$ is $\Bcmp{\fth{\pdf}}\left(\mbs{w}_{n,f} |
+            \Bcmp{\fth{\mbs{\theta}}}(\phi_1) \right)$. We treat each background
+            component dimension as independent, allowing us to write the
+            likelihood as a product over the astrometric dimensions:
+            \begin{equation} \label{eq:astrometric_model_off_stream_probability}
+                \pdf^{(B)}\left(\nth{\mbs{w}} | \mbs{\theta}(\phi_1) \right) = \prod_{f\in \mbs{I}_{\tilde{F}}} \pdf_f^{(B)}\left(\mbs{w}_{n,f} | \Bcmp{\fth{\mbs{\theta}}}(\phi_1) \right)\,,
+            \end{equation}
+            where $\mbs{I}_{\tilde{F}}$ is the set of indices of the features,
+            omitting missing phase space dimensions.
+
+        % ssub:method:astrometric_model:off_stream (end)
+
+    % sub: astrometric_model (end)
+
+    \subsection{Photometric Model} \label{sub:method:photometric_model}
+
+        \subsubsection{On-Stream} \label{ssub:method:photometric_model:on_stream}
+
+            In photometric coordinates we model the stream as a
+            single-population isochrone with the possibility of a non-zero
+            distance gradient. We accomplish this by modeling the distance of
+            the isochrone as a neural network output, parameterized as a
+            function of $\phi_1$. The result is a distance track along the
+            stream, estimated from the variation in its isochrone with $\phi_1$.
+
+            At any given $\phi_1$, the isochrone is modeled in absolute
+            magnitudes and parameterized by the normalized stellar mass, labeled
+            $\gamma \in (0, 1]$, in the modeled mass range. For example,
+            increasing $\gamma$ corresponds to movement up the main sequence
+            towards the red giant branch. We denote the isochrone as
+            $\mcal{I(\gamma)}$, and \package{StreamMapper} permits any such
+            distribution. The intrinsic dispersion around the isochrone is
+            $\Sigma_\mcal{I}(\gamma)$. Since the isochrone is in absolute
+            magnitudes, but the data are in apparent magnitudes, it is necessary
+            to shift the isochrone by a distance modulus to the predicted
+            distance of the stream, labeled  $\mu(\phi_1)$, with intrinsic
+            stream distance variation $\sigma_\mu(\gamma)$.
+
+            For the $n$-th star, the photometric model is:
+            \begin{multline} \label{eq:photometric_probability_point}
+                \cmp{S,m}{\pdf}(\mbs{m_i}, \gamma | \mbs{\theta}(\phi_1)) 
+                \\ \sim \mcal{N}(\nth{\mbs{m}} | \{\mcal{I(\gamma)} + \mu(\phi_1), \mbs{\Sigma}_{\mcal{I}}^2(\gamma) + \mathds{1} \sigma_\mu^2(\phi_1) + {\cmp{m}{\nth{\mbs{\Sigma}}}}^2 \}) \\ \times \prior(\gamma, \nth{\mbs{m}}, \phi_1),
             \end{multline}
 
-        The probablity of a being a stream member is then simply
-        \begin{equation}\label{eq:membership_prob}
-            \pdf\left(S | \mbs{w}_n, \mbs{m}_n, \mbs{\theta} \right) = \frac{f P^{(S)}(\nth{\mbs{w}}|\mbs{\theta}) P^{(S)}(\nth{\mbs{m}}|\mbs{\theta}) }{ \pdf(\nth{\mbs{w}}, \nth{\mbs{m}} | \mbs{\theta})}.
+            where $\cmp{m}{\nth{\mbs{\Sigma}}}$ is the data covariance and
+            $\prior(\gamma, \nth{\mbs{m}}, \phi_1)$ encodes both the present-day
+            mass function of the stream, as well as any observational
+            constraints (e.g., $g < 20$ mag).
+
+            For a given star, we are interested in its probability of belonging
+            to the stream's isochrone. Therefore, we marginalize over $\gamma$
+            to find:
+            \begin{small}
+            \begin{align} \label{eq:photometric_probability}
+                &\cmp{S,m}{\pdf}(\nth{\mbs{m}} | \mbs{\theta}(\phi_1)) = \\
+                &\ \int\limits_{\gamma=0}^{1} \mcal{N}(\nth{\mbs{m}} | \{\mcal{I(\gamma)} + \mu(\phi_1), \mbs{\Sigma}_{\mcal{I}}^2(\gamma) + \mathds{1}\sigma_\mu^2(\phi_1) + {\cmp{m}{\nth{\mbs{\Sigma}}}}^2 \}) \nonumber
+                \\
+                &\qquad \times \prior(\gamma, \nth{\mbs{m}} | \phi_1) \rm{d}\gamma. \nonumber
+            \end{align}
+            \end{small}
+            Then, for a given $\phi_1$ we can obtain a distribution over the
+            distance modulus using 
+            \begin{align}
+                \mu_{\rm sample}\left(\phi_1\right) \sim \mathcal{N}\left(\mu(\phi_1), \sigma^2_\mu(\phi_1) \right). %& \quad\unit{mag$^{-1}$}.
+            \end{align}
+            For each sample, we can convert the distance-modulus distribution
+            (and error) to the distance track using 
+            \begin{align}
+                \rm{dist}\left(\phi_1\right) &= 10^{\frac{1}{5}\mu_{\rm sample}(\phi_1)+1} & \quad\unit{pc}, \\
+                \delta \rm{dist}(\phi_1) &\simeq \frac{\ln{10}}{5} \rm{dist}(\phi_1) \ \sigma_\mu(\phi_1) & \quad\unit{pc}.
+            \end{align}
+
+            Let $\cmp{S,m}{\mbs{\theta}}(\phi_1)$ represent the feed-forward
+            neural network which outputs a vector of parameters characterizing
+            the stream's photometric distribution at a given $\phi_1$. The
+            network has 2 outputs -- $\mu, \sigma_\mu$ -- as we only consider
+            the distance track of the isochrone, holding fixed stellar
+            population parameters internal to modeling the isochrone, such as
+            its age and metallicity.  In principle we might include parameters
+            of the isochrone in the model, now $\mcal{I}(\mbs{\theta}, \gamma)$,
+            where $\theta = {a, Z, ...}$ and any other generating parameters of
+            the isochrone.  However, at a detailed level stellar streams are
+            generally poorly fit by theoretical isochrones, at least ones with
+            realistic ages and metallicities.  Consequently including the age
+            and metallicity as model parameters does not meaningfully contribute
+            to constraining results on the stream's stellar population.
+            Moreover, age and metallicity are partially degenerate with the
+            distance modulus, working counter to the goal of fitting a distance
+            track to the stream. An alternate approach is to use data-driven
+            isochrones instead of theoretic ones.   \package{StreamMapper}
+            allows any isochrone from any theoretic or data-driven library to be
+            used, so long as the isochrone may be described as a curve
+            $\mcal{I}(\gamma, \phi_1)$ with dispersion
+            $\Sigma_{\mcal{I}}(\gamma, \phi_1)$. In this work we use MIST
+            \citep{Dotter2016, Choi+2016} isochrones for their convenience, but
+            recognize their limitations as compared to data-driven isochrones.
+            We defer using data-driven isochrones and constraining ages and
+            metallicities to a future work.
+
+            The photometric probability, \autoref{eq:photometric_probability},
+            encodes the photometric distribution -- the ``track" -- of the
+            isochrone model, as well as the relative probability of points along
+            the track. The latter is the term $\prior(\gamma, \nth{\mbs{m}} |
+            \phi_1)$, which describes all priors on both the isochrone as well
+            as survey constraints and selection effects. We assume that the
+            properties of the isochrone are conditionally independent from
+            observational constraints; namely
+            \begin{equation} \label{eq:isochrone_prior_components}
+                \prior(\gamma, \nth{\mbs{m}} | \phi_1) = \prior_{\cal{I}}(\gamma | \phi_1) \prior_{obs}(\nth{\mbs{m}} | \phi_1)
             \end{equation}
-    Hereafter, when we refer to ``membership probability," Eq.~\ref{eq:membership_prob} provides the formal definition. 
-    %\newpage
-
-    \subsection{Determination of the Mixture Weight} \label{sub:mixture_weight}
-        The mixture weight $f_q(w_{i,0})$ as used in Eq.~\ref{eq:general_model} is characterized as the fraction of stars belonging to the mixture component $q$ over an increment $[w_{i,0}, w_{i,0} + \dif{w_{i,0}}]$.
-Thus, the mixture weight encodes information about the linear density of the stream, which has been shown to depend on substructure in the galaxy (CITE-x).
-The dependence of the mixture weight on the linear density is captured by the expression
-        \begin{equation}\label{eq:fraction_param}
-            f_q\left(w_{i,0}\right) = \frac{N_q\left(\phi_1\right)}{N_{\rm tot}\left(\phi_1\right)},
+            where $\prior_{\mcal{I}}$ and $\prior_{obs}$ are the isochrone and
+            observational priors, respectively.
+
+            The second term in \autoref{eq:isochrone_prior_components} --
+            $\prior_{obs}(\nth{\mbs{m}} | \phi_1)$ -- encodes all observational
+            effects in the photometric dataset. Some effects are easily modeled,
+            e.g. instruments have well-characterized magnitude limits, both
+            faint and bright. Other effects are not easily modeled, e.g, complex
+            location-dependent completeness issues \citep{GaiaCompleteness}.
+            Accounting for the completeness is very challenging. In practice we
+            avoid the contribution of completeness to $\prior_{obs}$, masking
+            data for which it is relevant. \Gaia, for instance, is complete from
+            $12 < G < 17$ and has high completeness up to $G \approx 20$, thus
+            we mask $G > 20$.  The masks are easily modeled as magnitude limits
+            and replace the complex completeness model in $\prior_{obs}$.
+            \autoref{sub:method:missing_data} explains how masking is
+            implemented in the models, though in this case every feature is
+            masked, not only a few feature dimensions. With every featured
+            masked, the photometric model in
+            \autoref{eq:photometric_probability} reduces from an
+            $F_m$-dimensional Gaussian to a 0-D Gaussian, which is a null
+            distribution and does not enter into the likelihood.  In photometric
+            coordinates completeness depends on a stars apparent magnitude;
+            viewed in astrometric coordinates, the completeness cannot be
+            described so simply. \Gaia, for instance has scanning law residuals
+            in the density field. When photometric coordinates are masked due to
+            completeness, we do not mask the corresponding  astrometric
+            features, so that the stars membership probability is determined
+            solely by the astrometric model. This practice allows us to include
+            stars with good astrometric measurements, not penalizing those stars
+            for which the photometric model is insufficient.  We examine the
+            results to confirm that the scan pattern does not impact the
+            membership distribution.
+
+            The first term in \autoref{eq:isochrone_prior_components} --
+            $\prior_{\mcal{I}}$ -- encodes the point-wise amplitude of the
+            isochrone.  Physically, this amplitude is the the present-day mass
+            function (PDMF). The PDMF $\prior_{\cal{I}}(\gamma, \phi_1)$ is a
+            joint distribution, depending on $\gamma$ since it is the
+            $\gamma$-dependent distribution amplitude, and also on $\phi_1$.
+            This latter dependence is confusingly termed the ``mass function of
+            the stream", which is the expected variation in the stellar mass
+            distrubion along the stream, arising due to e.g. mass segregation in
+            the progenitor \citep{WebbBovy2022}. To date this variation along
+            the stream has not been observed, so in practice we drop the
+            $\phi_1$ dependence -- $\prior_{\cal{I}}(\gamma, \phi_1) =
+            \prior_{\cal{I}}(\gamma)$ -- assuming that the PDMF is constant
+            along the stream.
+
+            In the
+            \href{https://github.com/GalOrrery/stream_mapper-pytorch}{\package{StreamMapper}}
+            we offer a few ansatz for the PDMF, though any user-defined function
+            may be used instead. The default assumption, known to be
+            non-physical, is a uniform distribution over $\gamma$.  Similarly
+            non-physical are truncated uniform distributions, considering only a
+            segment of the isochrone, e.g. the main sequence turnoff (MSTO). We
+            include also a Kroupa initial mass function (IMF)
+            \citep{Kroupa2001}. The Kroupa IMF, and all physically-motivated
+            IMFs, have a much larger fraction of low-mass stars than high-mass
+            stars, the latter being less likely to form.  This is observed in
+            streams, particularly their progenitors. However the Kroupa IMF, and
+            most out-of-the-box IMFs, are poor fits to the observed PDMF as
+            stream progenitors like globular clusters are extremely old
+            ($\sim10$ Gyr) and may be dynamically evolved
+            \citep{GrillmairSmith2001} while an IMF is the zero-age
+            distribution.  How then should the PDMF $\prior_{\cal{I}}$ be
+            treated?  One approach to the PDMF is to use a more informed
+            distribution, for example time-evolving an IMF, either analytically
+            or by simulation, to the age of the stream's stellar population.
+            However, for many streams, e.g. those lacking known progenitors, the
+            PDMF is observationally poorly constrained.  In short, using any
+            fixed distribution is simple in implementation, however the choice
+            of distribution is not.
+
+            Rather than using a fixed \textit{a priori} ansatz, another approach
+            to the PDMF is to incorporate it into the model, parameterized by
+            some distribution and fit simultaneously to the distance modulus and
+            other $\cmp{m}{\mbs{\theta}}$.  We find this, like incorporating $a,
+            Z$ into the isochrone model, to be interesting avenues by which to
+            develop the model. However the resulting significant increase in
+            model flexibility necessitates careful regulation, and we leave this
+            to a future work.
+
+            The last approach to the issue of the PDMF, and the one we take in
+            this work, is to render it unimportant.  With fixed age,
+            metallicity, and other isochrone model parameters, the primary
+            purpose of the isochrone is to allow the model to determine the
+            distance modulus of the stream. For this, only a portion of the
+            stream need be modeled.  For streams with observable main sequence
+            turn-offs, like \stream{GD-1} in \Gaia, this portion of the
+            isochrone has both many stars and a relatively small range in
+            masses. Thus, we restrict the mass range of the isochrone such that
+            we are modeling only a region of interest over which the PDMF does
+            not meaningfully contribute to the final result.
+
+        % ssub: on_stream (end)
+
+        \subsubsection{Linking to Astrometrics: the Distance Modulus and the Parallax} \label{ssub:method:linking_to_astrometrics}
+
+            By modeling jointly the astrometrics and photometrics we may tie
+            together components of the models.  In particular, the distance
+            modulus in the photometric model and the parallax in the astrometric
+            model are both measures of the distance track of the stream. We
+            model in the same coordinates as the data, and thus prefer parallax
+            and distance modulus over the distance for each model type.  We
+            introduce a prior to connect these components of the models:
+            \begin{align}
+                \prior(\{\mu_I, \mu_\parallax \} | \phi_1) &= \delta( \rm{dist}(\mu_I) - \rm{dist}(\parallax) )(\phi_1), \label{eq:distance_track_prior}
+            \end{align}
+            where $\delta$ is the Dirac delta function \citep{Dirac1947}, and
+            enforces that the distance modulus track and parallax track must be
+            equal (when converted to the actual distance) as a function of
+            $\phi_1$.  The widths are similarly constrained. The distance and
+            first-order error conversion are given by
+            \begin{align}
+                \mu_I(\parallax) &= 10 - 5\log_{10}(\parallax) \\
+                \sigma_I(\sigma_\parallax)  &\approxeq \frac{5}{\ln{10}} \mu_I \lvert\sigma_\parallax\rvert.
+            \end{align}
+
+            In practice, at the distance of many streams the errors in the
+            parallaxes are of order 1 and we exclude the feature from the model.
+
+        % ssub: linking_to_astrometrics (end)
+
+        \subsubsection{Off-stream}
+        \label{sub:method:photometric_model:off_stream}
+
+            The distribution of background stars in color (i.e., $g-r$) and
+            magnitude (i.e., $g$) is a complicated function of location in the
+            galaxy. Even within a field centered on the stream of interest, the
+            color-magnitude diagram (CMD) is a combination of stellar
+            populations distributed over a range in distances. Because of this,
+            we do not find an analytic density that describes the data and use
+            instead a normalizing flow, discussed in
+            \autoref{sub:method:pre-training_distributions}.  Because the
+            background CMD can evolve with $\phi_1$, we fit a \emph{conditional}
+            normalizing flow, $q_{\rm flow}(\mathbf{m}|\phi_1)$, so that the
+            color-magnitude diagram is conditionally dependent on position along
+            the stream. In practice, we model magnitudes and not colors (i.e.,
+            $\mathbf{m} = (g,r)$ rather than $g \ \mathrm{and} \ g-r$.
+            Otherwise, the two arguments will always be covariate). The
+            normalizing flow approach makes modeling the photometry relatively
+            straightforward.
+
+            In photometry the intrinsic width of stellar streams tends to be
+            quite small, with correspondingly small $\sigma_\mu$ (see
+            \autoref{eq:photometric_probability}). Therefore the effective
+            region of the isochrone model is well determined and we do not find
+            the marginal log-likelihood approach discussed in
+            \autoref{sub:method:pre-training_distributions} to be impactful.
+
+        % ssub: off_stream (end)
+
+    % sub: photometric_model (end)
+
+    \subsection{Priors} \label{sub:methods:priors}
+
+        In \autoref{sub:method:likelihood_setup} we introduced the likelihood
+        setup. In \autoref{ssub:method:photometric_model:on_stream} we added
+        priors in the form of the isochrone's PDMF and photometric observational
+        constraints. In this section we introduce and develop more priors that
+        are important for training our Bayesian Mixture Density Network.
+
+        \subsubsection{Parameter Bounds} \label{ssub:methods:priors:parameter_bounds}
+
+            For each parameter in $\mbs{\theta}$ of the model we implement
+            priors on its range.  Uninformative, e.g. uniform $\mcal{U}(a, b)$,
+            priors are often assumed where little is known about a parameter
+            (except that $(a,b]$ contain the correct $\theta$ and its
+            distribution). Where more is known about $\theta$, for instance that
+            it is a categorical, more informative priors like the Dirichlet
+            distribution \citep{Christopher2016} may be used. Our code,
+            \package{StreamMapper}, permits any user-defined prior, and we
+            include $\mcal{U}(a, b)$.  The default choice of prior and bounds
+            $\mcal{U}$ set to the limits of the dataset in each feature
+            dimension.
+
+            We implement a hard-coded uniform prior on a neural network output
+            by applying a scaled logistic function of the form
+            \begin{equation}\label{eq:scaled_logistic}
+                  \sigma(x, \{a,b\}) = a + (b - a) * \sigma(x)
             \end{equation}
-        where $N_q\left(\phi_1\right)$ is the number of stars in component $q$ within an interval $[\phi_1, \phi_1 + \dif{\phi_1}]$, and 
-        $N_{\rm tot}$ is the total number of stars in the same band (including those in component $q$). The linear  density for component $q$ is then entirely specified by the function $N_q(\phi_1)$.
-
-        The mixture model specified in \S-X only models the weight parameter $f_q$, and not the components of the ratio in \autoref{eq:fraction_param}.
-However, the linear density $N_q(\phi_1)$ can be readily obtained from $f_q$, provided that $N_{\rm tot}\left(\phi_1\right)$ can be calculated.
-Importantly, this function does not depend on the parameters of the on-stream or off-stream model.
-Instead, $N_{\rm tot}(\phi_1)$ is simply the number of stars in a small $\phi_1$ increment.
-We therefore model $N_{\rm tot}\left(\phi_1\right)$ as a post-processing step using a single normalzing flow in $\phi_1$.
-
-        In particular, for a given field the distribution of $\phi_1$ coordinates is specified by the set $\{\phi_{1,i}\}_i$.
-A normalizng flow is trained to this dataset, and will satisfy $\int d\phi_1 P_{\phi_i}(\phi_1) = 1$ by construction.
-In order to re-weight the normalizing flow to obtain $N_{\rm tot}(\phi_1)$, we simply rescale $P_{\phi}(\phi_1)$ by $N_{\rm tot,0}$, which is the total number of stars in the field considered.
-We can then obtain the linear stream density with
+            Therefore, we pair every parameter bound with a matching bound in
+            the network architecture. Further details of this practice are
+            explained \autoref{app:nns_and_priors}.
+
+            The parameter bounds may be independent of $\phi_1$, as is implicit
+            to the above discussion, or conditionally dependent and vary as any
+            user-defined function of $\phi_1$.  Alternatively, prior parameters
+            may be separated into pieces, dealing with different modeling needs,
+            e.g. defining broad parameter bounds as was done in this section.
+            We introduce a different piece subsequently.
+
+        % ssub:methods:priors:parameter_bounds (end)
+
+        \subsubsection{Priors on the Stream Track} \label{sub:methods:priors:track_region_prior}
+
+            We now discuss how our model incorporates known information about
+            the track of the stream.  Our density modeling is aimed at
+            characterization of \textit{known} streams, not stream discovery.
+            From previous studies, the broad track of a stream is known for
+            significant portions of its length \citep[e.g. see the atlas
+            in][]{Mateu2022}. It makes sense, then, to provide this information
+            to the model. Care must be taken that this prior information does
+            not dominate the model.  We introduce a ``guide'' prior to encourage
+            the stream model to pass through a user-defined guide region, while
+            also remaining compatible with the data.  We use a ``split''-Normal
+            prior: a Gaussian split and separated at the peak and pieced back
+            together with a flat region connecting the halves.  The
+            un-normalized PDF is given by:
             \begin{equation}
-            N_q\left(\phi_1\right) = f_q N_{\rm tot} \left(\phi_1\right)  = f_q \left[N_{\rm tot,0} P_{\phi_1}\left(\phi_1\right) \right] .
+                \pdf(x,\mu,\sigma,w) \propto \begin{cases} 
+                   \Exp{-\frac{1}{2}\left(\frac{x-(\mu-w)}{\sigma}\right)^2} & \phantom{\mu - w <}\ x < \mu - w \\
+                    1 & \mu - w \leq x < \mu + w \\
+                    \Exp{-\frac{1}{2}\left(\frac{x-(\mu+w)}{\sigma}\right)^2} & \mu + w < x
+                \end{cases}.
             \end{equation}
-
-    \subsection{Astrometric Model} \label{sub:astrometric_model}
-
-        \subsubsection{On-Stream} \label{ssub:astrometric_model_on_stream}
-
-            The astrometric track is modeled with a neural network in each phase space dimension, parameterized as a function of $\phi_1$.
-The neural network output for a single stream component is the mean location of the stream track in each dimension, $\mbs{\mu}_w(\phi_1 | q_i)$, and its associated covariance matrix $\mbs{\Sigma}_w(\phi_1 | q_i)$.
-The probability for the data is then
+            Since the derivative at the peak of a Gaussian is $0$, the piecewise
+            PDF is smooth up to the first derivative and can be used with
+            gradient-based optimizers.
+
+            The Gaussian portions of the prior encourage the network towards the
+            central region $\mu - w < x < \mu + w$. Because the prior is
+            equi-probable in the guided region, the stream may lie anywhere as
+            preferred by the data and the stream model.  It is convenient to
+            parameterize, with $\tau = \frac{1}{\sigma}$. Namely,
+            \begin{small}
             \begin{equation}
-                \pdf^{(S)}(\nth{\mbs{w}} | \mbs{\theta}, \phi_{1,i}, q_i) = \mcal{N}\left(\nth{\mbs{w}} | \mbs{\mu}_w\left(\phi_{1,i} | q_i \right), \mbs{\Sigma}_w\left(\phi_{1,i} | q_i \right) \right),
+                \ln \pdf(x,\mu, \tau, w) \propto \tau
+                \begin{cases} 
+                    -\left(x-(\mu-w)\right)^2 & \phantom{\mu - w <}\ x < \mu - w \\
+                    0 & \mu - w \leq x < \mu + w \\
+                    -\left(x-(\mu+w)\right)^2 & \mu + w \leq x
+                \end{cases},
             \end{equation}
-            where $\mbs{\theta}$ is the set of neural network parameters that define $\mbs{\mu}_w$ and $\mbs{\Sigma}_w$.
-            In the simplest case, we take $\mbs{\Sigma}_w$ to be diagonal, consisting of both intrinsic dispersion for each dimension of $\mbs{w}$ and the data uncertainties added in quadrature.
-
-            In practice, we work with truncated Gaussians, where the truncation is set by the size of the field in each astrometric dimension.
-This ensures that the probability density is zero wherever there is no data.
-Details of the truncated Gaussian are included in \autoref{app:distributions}.
-
-        \subsubsection{Off-stream} \label{ssub:astrometric_model_off_stream}
-
-            We now outline the off-stream astrometric model.
-We take a similar approach to the on-stream astrometric model discussed in \S\ref{ssub:astrometric_model_on_stream}, though we typically do not characterize the backgrounds with a Gaussian distribution.
-Instead, we utilize a range of distributions (i.e., exponential, skew-normal) discussed in \autoref{app:distributions}.
-The parameters of the user-specified background distributions are themselves neural network outputs, such that any $\phi_1$ ``slice" of the background should be characterized by some analytic density, but the evolution of the backgrounds with $\phi_1$ can be complex.
-
-            Let $\mbs{\theta}_{B,j}(\phi_1)$ represent the neural network which outputs a vector of parameters characterizing the background distribution at a given $\phi_1$ for astrometric dimension $j$.
-The number of outputs for the background model is equal to $\Sigma_{j>0} \mathrm{dim}\left(\mbs{\theta}_{B,j}\right)$ (where $j=0$ corresponds to $\phi_1$, which we do not model).
-At a given $\phi_1$, the probability density for the astrometric dimension $j>0$ is $\pdf^{(B)}_j\left(\mbs{w}_{n,j} | \mbs{\theta}, \mbs{\theta}_{B,j}, \phi_1 \right)$.
-We treat each background component as independent, allowing us to write the likelihood as a product over the astrometric dimensions:
-            \begin{equation}
-                \pdf^{(B)}\left(\mbs{w}_n | \mbs{\theta}, \phi_1 \right) = \prod_{j>0} \pdf_j^{(B)}\left(\mbs{w}_{n,j} | \mbs{\theta}, \mbs{\theta}_{B,j}, \phi_1 \right).
-            \end{equation}
-
-    %\newpage
-
-    \subsection{Photometric Model} \label{sub:photometric_model}
-
-        \subsubsection{On-Stream} \label{sub:photometric_model_on_stream}
-            In photometric coordinates we model the stream as a single-population isochrone with the possibility of a non-zero distance gradient.
-We accomplish this by modeling the distance of the isochrone as a neural network output, parametrized as a function of $\phi_1$.
-The result is a distance track along the stream, estimated from the variation in its isochrone with $\phi_1$.
-
-            At any given $\phi_1$, the isochrone is modeled in absolute magnitudes
-            and parameterized by the unit-normalized stellar mass, labeled $\gamma$.
-For example, increasing $\gamma$ corresponds to movement up the main sequence towards the red giant branch.
-We denote the isochrone as $\mcal{I(\gamma)}$.
-The intrinsic dipsersion around the isochrone is $\Sigma_\mcal{I}(\gamma)$.
-Since the isochrone is in absolute magnitudes, but the data are in apparent magnitudes,
-            it is necessary to shift the isochrone by a distance modulus to the predicted distance of the stream, labeled  $\mu(\nth{\phi_1})$.
-
-            For the $n$-th star, the photometric model is:
-
-            \begin{multline}
-                P^{(S)}(\mbs{m_i}, \gamma; \mbs{\theta}(\nth{\phi_1}), \nth{\phi_1}) 
-                \\ \sim \mcal{N}(\nth{\mbs{m}}; \{\mcal{I(\gamma)} + \mu(\nth{\phi_1}), \sqrt{\Sigma_{\mcal{I}}^2(\gamma) + \Sigma_\mu^2(\nth{\phi_1}) + \Sigma_i^2} \}) \\ \times\pdf(\gamma, \nth{\phi_1}),
-            \end{multline}
-
-            where $\pdf(\gamma)$ encodes both the present-day mass function of the stream, as well as the observational constraints (e.g. $g < 22$ mag).
-
-            We are interested in the total probability (at some $\phi_1$) and so integrate over $\gamma$ to find:
-            \begin{small}
-            \begin{multline}
-                P^{(S)}(\nth{\mbs{m}}; \mbs{\theta}(\nth{\phi_1}), \nth{\phi_1}) = \\\int\limits_{\gamma=0}^{1} \mcal{N}(\mbs{m}; \{\mcal{I(\gamma)} + \mu(\nth{\phi_1}), \sqrt{\Sigma_{\mcal{I}}^2(\gamma) + \Sigma_\mu^2(\nth{\phi_1}) + \Sigma_i^2} \}) \pdf(\gamma) \rm{d}\gamma.
-            \end{multline}\end{small}
-            Then, for a given $\phi_1$ we can obtain a distribution over the distance modulus using 
-            \begin{equation}
-                \mu_{\rm sample}\left(\phi_1\right) \sim \mathcal{N}\left(\mu(\phi_1), \Sigma^2_\mu(\phi_1) \right) \quad\unit{mag}.
-            \end{equation}
-            For each sample, we can convert the distance-modulus distribution to the distance track using 
-            \begin{equation}
-                \rm{dist}\left(\phi_1\right) = 10^{\frac{1}{5}\mu_{\rm sample}(\phi_1)+1} \quad\unit{pc}.
-            \end{equation}
-
-        \subsubsection{Off-stream} \label{sub:photometric_model_off_stream}
-            In this section we introduce our model for the distribution of backgrounds in photometric coordinates.
-
-            In general, the distribution of stars in color (i.e., $g-r$) and magnitude (i.e., $g$) is a complicated function of location in the galaxy.
-Even within a field centered on the stream of interest, the color-magnitude diagram (CMD) is a combination of stellar populations distributed over a range in distances.
-Because of this, we do not expect an analytic density to provide a realistic description of the data.
-In this work we take a data-driven approach, and represent the CMD using a normalizing flow model.
-
-            Normalizing flows provide a flexible description of a probability density, by transforming samples generated from a simple base distribution (i.e., a Gaussian) to the more complicated target distribution.
-The transformations are typically non-linear outputs of a neural neural network, whose parameters are optimized until the target density accurately characterizes the data.
-The neural network transformation is differentiable, so that jacobian factors can be combined to ensure that the the target distribution remains a valid probability density (i.e., integrates to one).
-
-            Our implementation is as follows.
-For a given stream, we restrict the data to some field characterized by a polygon drawn around the stream.
-Because our density modeling is aimed at stream characterization rather than discovery, we assume that the stream is sufficiently well known so that it can be masked out as a simple cut in (e.g.) $\phi1-\phi_2$ coordinates.
-With the stream masked out, we then fit a normalizing flow to the photometric data.
-Because the background CMD can evolve with $\phi_1$, we fit a \emph{conditional} normalizing flow, $q_{\rm flow}(\mathbf{m}|\phi_1)$, so that the color-magnitude diagram is conditionally dependent on position along the stream.
-In practice, we model magntiudes and not colors (i.e., $\mathbf{m} = (g,r)$ rather than $g \ \mathrm{and} \ g-r$.
-Otherwise, the two arguments will always be covariate).
-Our central assumption with this model is that the distribution of colors and magnitudes for background stars in the masked region are quantitatively similar to those in the unmasked region.
-For a sufficiently narrow mask we expect this to be the case, and find that this assumption does not introduce bias for the streams considered in this work.
-
-            Once the normalizing flow, $q_{\rm flow}\left(\mathbf{m} | \phi_1\right)$, is fit to the data, its parameters are fixed while the other components of the model begin training.
-Therefore, the normalizing flow can be rapidly trained and computed as a pre-processing step.
-
-            The specific architecture of the photometric normalizing flow are discussed in \S-X.
-
-    % subsection likelihood_setup (end)
-
-    % \vspace{10pt}
-
-    % \subsection[Astrometric Background]{Astrometric Background: pieces of $P^{(B)}(\mbs{w})$} \label{sub:background_astrometric}
-
-    %     When looking for a stellar stream, the highly complex Galaxy is the background.
-There are numerous approaches to modeling a complex structure, from a mix of very simple models to a single highly flexible model, like a basis function expansion or ML network.
-    %     We aim towards the mix of simple models, but use more flexible models as needed.
-In this section we describe the various models used when modeling the background, in different coordinates of the phase space.
-
-        % \subsubsection{Flat Background} \label{ssub:flat_background}
-
-        %     The simplest possible background is the flat background.
-        %     Perhaps surprisingly, the Galaxy around GD-1 is well modeled by a flat distribution in the $\phi_2(\phi_1)$ phase space.
-        %     For a domain $x \in [a, b]$ the normalized PDF is given by
-        %     \begin{align}
-        %         \pdf(x|a,b) &= \frac{1}{b-a} & \text{and} \\
-        %         \ln \pdf(x | a, b) &= -\ln\left({b-a}\right)
-        %     \end{align}
-        %     where $a,b$ are the $\phi_2$ bounds of the data selection box.
-
-        % % subsubsection flat_background (end)
-
-        % \subsubsection{Exponential-like Background} \label{ssub:exponential_background}
-
-        %     In many coordinate axes, the distribution of the background data is better described by an exponential distribution.
-        %     The unit-normalized exponential distribution in the domain $[a, b]$ ($a \neq b$) is given by:
-        %     \begin{equation}\label{eq:exp_distr}
-        %         f(x) = \frac{m \Exp{-m (x - a))}}{1 - \Exp{-m(b - a)}}.
-        %     \end{equation}
-        %     However for $m \rightarrow 0$, which describes the flat distribution (\autoref{ssub:flat_background}), this functional form can be numerically unstable, particularly with lower bit precision numerics like \texttt{float32} data-types.
-In the context of ML, the numerical instability is problematic when employing parameter drop-out for $m$.
-While for parameter dropout this might be avoided by re-parameterizing to $m+\epsilon$, the numerical instability remains and may be encountered later, creating a difficult-to-diagnose \texttt{NaN}.
-        %     For both compatibility with the flat distribution and for practical reasons we modify the above distribution and approximate the exponential distribution with a 3rd order expansion around $m=0$ when $|m| < \epsilon$, for some small $\epsilon$.
-
-        % % subsubsection exponential_background (end)
-
-        %% PLOT HERE OF ALL THE BACKGROUNDS?? **
-
-    % subsection astrometric background (end)
-
-        % Let $\Omega$ be the independent variable in $\mbf{w}$.
-
-        % $\pdf(m_i | ) \rm{KDE(\mbf{m}_i|\omega_{i} )}$
-
-    % subsection photmetric background (end)
+            \end{small}
+            where the additive normalization is
+            \\
+            $-\ln\left(\sqrt{\frac{\pi}{\tau}}
+            \left(\frac{1}{2}\text{erf}\left(2 \sqrt{\tau }
+            w\right)+1\right)\right)$.  In this form we see that $\tau$ may be
+            increased to strengthen the prior and encourage $\theta$ to lie
+            within the desired region. It is important that the region be set
+            large enough that we may be confident the prior is not driving the
+            final result on small scales. As an added measure, it may useful to
+            turn off this prior after the stream lies within the desired guides
+            and the learning rate of the optimizer is low enough that the model
+            does not escape the solution minima.
+
+        % sub:methods:priors:track_region_prior (end)
+
+    % sub:methods:priors (end)
+
+    \subsection{Model Implementation} \label{sub:methods:model_implementation}
+
+        In previous sections we discussed the mathematical implementation of
+        each component of the Mixture Density Network. Here we make brief
+        remarks on the code implementation in \package{StreamMapper} and the
+        architecture of the neural networks.
+
+        The neural networks are all multi-layer perceptrons (MLP; built with the
+        \package{PyTorch} stack \citep{Pytorch2019}. We wrap the network
+        \texttt{pytorch.Module} in a custom framework, allowing the Bayesian
+        likelihood, prior, evidence, etc. to be bundled with the network's
+        forward step. This framework allows for a high degree of modularity.
+        Component models, e.g. the stream model, of the mixture are easily added
+        to (and moved from) as items in the larger mixture model. Probability
+        methods understand how to traverse the mixture model, calling and
+        combining the appropriate methods of the constituent models, so it
+        unnecessary to write custom loss functions.  Another benefit of the
+        modular framework is the ease of building and experimenting with
+        different mixture models. Furthermore, each model component may be saved
+        and serialized separately from the other components, allowing for
+        portability of the components between models.  For example, if a stream
+        has a prominent extra-tidal feature, e.g. the spur of \stream{GD-1}
+        \citep{Bonaca+2019}, a fiducial model of just the main stream may be
+        trained, then the stream (and background) model components may be saved
+        and used as the initialization to the stream (and background) of a more
+        complete model that includes the spur.  By using a modular framework,
+        the architecture of each neural network may be chosen to best-suit its
+        modeling needs: e.g. thin networks for simply varying components.  On
+        the other hand, large networks can have useful emergent phenomenon, e.g.
+        understanding covariate structures, that cannot be (or are unknown how
+        to be) replicated with multiple smaller networks. We choose to use the
+        smaller and more tailored models, finding their balance of performance
+        and reduced training time well-suited for this work.
+
+        The models permit user-defined priors to be passed at model
+        instantiation.  Priors specific to a single model are contained on that
+        model, while priors connecting two (or more) models are held on the
+        mixture model object. As an example of the latter, see
+        \autoref{ssub:method:linking_to_astrometrics}, which connects the
+        distance component of the astrometric and photometric stream models.
+
+        The specific architecture of the neural network(s) is set and determined
+        by the user. So long as the network has the correct number of inputs
+        (e.g. one for $\phi_1$) and outputs (one per parameter), any
+        feed-forward network may be used.  Our default choice, and for which we
+        provide a helper function, is an MLP with a sequence of \texttt{Linear}
+        \!\!\textrightarrow \texttt{Tanh} \!\!\textrightarrow \texttt{Dropout}
+        (hereafter \texttt{LTD}) blocks.  Dropout layers are used to prevent
+        network co-adaptation and over-fitting. Dropout works by randomly
+        zeroing out nodes in the network, decreasing the importance of any
+        single node, encouraging instead emergent patterns across the network
+        \citep{GalGhahramani2015}.  One model for which the \texttt{LTD} network
+        cannot be used is the normalizing flow used in the photometric
+        background model (\autoref{sub:method:photometric_model:off_stream}).
+        Here we use the \package{zuko} package for normalizing flows, with a
+        conditional diagonal normal base distribution and composite transform
+        network of a reverse permutation and masked affine auto-regressive
+        transform layers. As noted in our data availability statement, all the
+        codes used in this paper are bundled by
+        \href{https://github.com/showyourwork/showyourwork}{\package{showyourwork}}
+        \citep{Luger+2021} in a public repository. We will describe for each
+        stream model specifics relevant to that stream but refer readers to the
+        publicly-available code itself for more implementation details.
+
+% sec:method (end)
+
+\section{Results: Mock} \label{sec:results_mock}
+
+    In this section we present an application of our model to a synthetic stream
+    with known ground truths, and demonstrate the model's ability to
+    characterize stream density variations and membership probabilities in an
+    unsupervised manner.
+
+    \subsection{Data Simulation} \label{sub:results_mock:data}
+
+        We generate synthetic stream observations by sampling from simple
+        algebraic forms.  In $\phi_1$ we sample from a uniform distribution.
+        Non-Poissonian density variations, like gaps, are introduced by adding
+        to the uniform distribution two Gaussian distributions centered at
+        different values of $\phi_1$ with negative amplitudes and random widths.
+        Stream stars are then sampled from this uniform-plus-gaps mixture
+        distribution.  In $\phi_2$ we sample from a quadratic in $\phi_1$ with
+        normally-distributed $0.15^{\degree}$ scatter.  The distances are
+        uniformly sampled from $7$ to $15$ kpc in a linear function in $\phi_1$
+        with normally-distributed $0.25 \ \rm{kpc}$ scatter, then transformed to
+        the parallax $\parallax$. Even though the stream width is constant in
+        the distance the width in parallax is not, which will be used to
+        demonstrate that we can recover $\phi_1$ dependent distributions.  The
+        number of stream stars is $\variable{output/mock/nstream_variable.txt}$.
+        $\variable{output/mock/nbackground_variable.txt}$ background astrometric
+        points are generated by sampling from uniform distributions in each
+        coordinate.
+
+        The synthetic stream's photometry is also simulated using a
+        \variable{output/mock/isochrone_age_variable.txt}\unskip, [Fe/H] =
+        \variable{output/mock/isochrone_feh_variable.txt} MIST isochrone
+        \citep[using][]{brutus}. The isochrone is truncated just short of the
+        giant branch, and is sampled from assuming a stream mass function
+        similar to \stream{Pal\,5} \citep{GrillmairSmith2001} as well as with an
+        intrinsic uniform 0.2~dex scatter orthogonal to the isochrone track.
+
+        The isochrone is shifted by the stream's distance modulus, which is
+        derived from the astrometric distance track.  The background photometric
+        coordinates are generated as a 2-dimensional Gaussian with non-zero
+        covariance. The background is illustrative, if not realistic, in that it
+        is a distribution about which we care very little beyond our ability to
+        fit with a model.  Thus, the synthetic data scenario described here, and
+        presented in \autoref{fig:mock_data_photometric_background_selection},
+        generates a mock stream in astrometric coordinates and photometric
+        coordinates, with density variations, a distance gradient which is
+        consistent in parallax and distance modulus (i.e., magnitudes), all
+        superimposed over a $\sim 10$ times larger noisy field of background
+        points in each astrometric and photometric dimension.
+
+    \subsection{Model Specification} \label{sub:results_mock:model}
 
@@
             \includegraphics[width=1\linewidth]{figures/mock/photometric_background_selection.pdf}
-            \caption{Caption: TO-DO need to show this with a ground truth (e.g. show true weight in top panel).}
+            \caption{
+                %
+                \textbf{Top panel:} Astrometric coordinates ($\phi_1$, $\phi_2$)
+                for the mock data set.  Light blue points are the stream and
+                background within an ``on"-stream region. Black points are in
+                the ``off"-stream region used to train the background
+                photometric model.
+                %
+                \textbf{Bottom panel:} Photometric coordinates for the mock data
+                set.  Black points are in the ``off"-stream region from the
+                region defined in the astrometric coordinates.  Light blue
+                points are the stream and background from the on-stream region.
+                The stream's isochrone is apparent as an overdensity around
+                (g-r, g)$\ \approx (0, 20)$.  The background is an arbitrary
+                Gaussian distribution from which the stream must be separated.
+                %
+            }
             \label{fig:mock_data_photometric_background_selection}
@@
 
-        \begin{figure*}
+        \begin{figure*}[!h]
             \script{mock/plot/results.py}
             \centering
-            \includegraphics[width=1\linewidth]{figures/mock/results.pdf}
-            \caption{Caption: TO-DO need to show this with a ground truth (e.g. show true weight in top panel).}
+            \includegraphics[width=0.9\linewidth]{figures/mock/results.pdf}
+            \caption{%
+                Illustration of the model's performance in recovering a stream
+                from synthetic observations. The \textbf{top panel} shows the
+                stream mixture coefficient $f(\phi_1)$ (dashed red line)
+                predicted by the model, overplotted on the true stream fraction
+                (black-outlined histogram).
+                %
+                In the \textbf{middle two rows} we also show the $\phi_2$ and
+                parallax, $\parallax$, tracks as a function of $\phi_1$ and
+                their associated widths (labeled as $\sigma_{\phi_2}$ and
+                $\sigma_{\parallax}$, respectively). The true values for these
+                quantities are shown in gray, while our model prediction and
+                uncertainty is show by the dashed red curve and red band, and by
+                the color of the data points (color-coded by membership
+                probability). The model does an excellent job at identifying the
+                ground truth stream stars.
+                %
+                In the \textbf{bottom three rows} we demonstrate our ability to
+                separate the stream from the background both astrometrically and
+                photometrically. Histograms are shown for each model component
+                (black for the ground truth, blue for the background, red for
+                the stream), in 4 $\phi_1$ ranges across the data set.  The
+                height of the histogram is the probability-weighted density for
+                the collection of stars in each bin. There is nearly perfect
+                agreement for the number of stars belonging to each model
+                component as a function of $\phi_1$. In the bottom row we show
+                photometric plots for each model component in the same 4
+                $\phi_1$ ranges across the data set. Points are color-coded by
+                stream membership probability. 
+                %
+            }
             \label{fig:mock_data_result}
@@
 
-\section{Model Implementation}
-
-    \subsection{Network Architecture}
-
-        \begin{enumerate}
-            \item A network per model component, e.g. one for the weights, one for the stream track and width, one for the background distribution.
-        \end{enumerate}
-
-    \subsection{Astrometric Stream}
-
-        \subsubsection{Track Region Prior} \label{sub:track_region_prior}
-
-            The overall track of the stream is known, so it makes sense to give this information to the system.
-However, we don't want the prior to dominate the results on small scales.
-A good balance between these two goals is to have a prior that only influences the track on large scales.
-            We introduce the ``split" Gaussian prior, which is a Gaussian split at the peak and pieced back together with a flat region connecting the halves. 
-            It is smooth up to the first derivative, so works well in an auto-grad setting.
-            The unnormalized PDF is described by:
-            \begin{small}
-            \begin{equation}
-                \pdf(x,\mu,\sigma,w) \propto  \frac{1}{\sigma \sqrt{2 \pi}} \begin{cases} 
-                   \Exp{-\frac{1}{2}\left(\frac{x-(\mu-w)}{\sigma}\right)^2} & \phantom{\mu - w <}\ x < \mu - w \\
-                    1 & \mu - w \leq x < \mu + w \\
-                    \Exp{-\frac{1}{2}\left(\frac{x-(\mu+w)}{\sigma}\right)^2} & \mu + w < x
-                \end{cases}.
-            \end{equation}\end{small}
-
-            Since this prior is equi-probable in the region $\mu - w < x < \mu + w$, the  impact is to encourage the stream to fall anywhere within this region. 
-            It is convenient to reparametrize, with $\tau = \frac{1}{\sigma}$.
-            \begin{small}
-            \begin{equation}
-                \ln \pdf(x,\mu,w) \propto \tau \begin{cases} 
-                    -\left(x-(\mu-w)\right)^2 & \phantom{\mu - w <}\ x < \mu - w \\
-                    0 & \mu - w \leq x < \mu + w \\
-                    -\left(x-(\mu+w)\right)^2 & \mu + w \leq x
-                \end{cases},
-            \end{equation}\end{small}
-            where the additive normalization is 
-            $-\ln\left(\sqrt{\frac{\pi}{\tau}} \left(\frac{1}{2}\text{erf}\left(2 \sqrt{\tau } w\right)+1\right)\right)$
-
-            % The total log-probability over all the
-
-            % \begin{equation}
-            %     \ln\mcal{L}\left(\{(\nth{\mbs{w}},\nth{\mbs{m}})\} | \mbs{\theta}\right) = \sum_i  \pdf(\nth{\mbs{w}}, \nth{\mbs{m}} | \mbs{\theta}).
-            % \end{equation}
-
-        % subsection track_region_prior
-
-% section method (end)
-
-%\newpage
-\section{Results} \label{sec:results}
-
-    In this section we present an application of our model to a synthetic stream with known ground truths, and demonstrate the model's ability to characterize stream density variations and membership probabilities in an unsupervised manner.
-We then apply the method to real stellar streams in \S-X (GD-1) and \S-Y (Pal-5).
-
-    \subsection{Test on a Synthetic Stream}\label{sub:simple_mock_data}
-
-        In this section we apply our model to a synethic stream in order to demonstrate an accurate recovery of stream members and density variations.
-
-        We generate synthetic observations by sampling points from a third degree polynomial \JN{check this} with a constant scatter.
-Density variations are then simulated by evaluating the stream density with two Gaussian distributions centered at different values of $\phi_1$ with random amplitudes (which sum to $1$) and widths.
-Stream stars are then removed using random sampling, weighted by their likelihood of belonging to the density.
-The background astrometric  points in are generated from exponential distributions at each $\phi_1$.
-The number of stream stars is \JN{X}, while the number of background stars is \JN{Y}.
-
-        The synthetic stream is also simulated in magnitudes using a 12~Gyr isochrone with [Fe/H] = -1.35~dex.
-The isochrone truncates just short of the giant branch, and sampled from uniformly (i.e., the initial mass function, $P(\gamma)$, is uniform).
-The background photometric coordinates are generated as a 2-dimensional Gaussian with non-zero covariance.
-The distance modulus is derived from a polynomial parallax track with uniform thickness.
-Thus, the synthetic data scenario described here generates a mock stream in astrometric coordinates and photometric coordinates, with density variations, a distance gradient which is consistent in parallax and distance modulus (i.e., magnitudes), all superimposed over a noisy field of background points in each astrometric and photometric dimension.
-
-        The result of applying our density model to the synthetic data is illustrated in Fig.~\ref{fig:mock_data_result}.
-The top panel shows the weight parameter that controls membership probability as a function of $\phi_1$.
-The dashed curve represents the output of our data-driven model, while the solid curve is the ground truth.
-\JN{todo: maybe the kde should be a histogram}, the second panel shows the stream and background in the $(\phi_1,\phi_2)$ plane, and the third panel shows the stream and background in the $(\phi_1,\varpi)$ plane.
-Points are color-coded according to their membership probability (Eq.~X) \JN{would be good to remove the $\sigma$ bands in this plot.} The weight parameter clearly shows that the model has captured the two prominent density variations along the stream.
-The are additional variations  mostly around the edges of the stream, though re-sampling the neural network weights with dropout reveals that these variations represent regions of higher model uncertainty.
-
-        We find that the stream is successfully recovered in both astrometric and photometric coordinates, with $x\%$ stream stars being recovered with membership probability greater than $y$.
-The false positive rate (i.e., stars misidentified as stream members) for this test is found to be $z\%$ when cutting on this threshold.
-
-        In the bottom two rows of Fig.~\ref{fig:mock_data_result} we illustrate the synthetic data color-coded by stream membership probability (top) and background membership probability (background) for different $\phi_1$ slices.
-Importantly, the photometric portion of the mixture model successfully identifies the stream in magnitude space, showing a high stream membership probability where the stream is present, and a low probability ($\sim 0$) where the stream is absent.
-
-    % subsection test_on_a_synthetic_stream (end)
-
-    \subsection{Results on GD-1} \label{sub:gd1}
-
-        We now apply our density modeling approach to the stellar stream GD-1. We discuss the data selection in \S\ref{ssub:gd1_data} and results in \S\ref{ssub:trained_gd1}.
-
-        \subsubsection{Data Selection} \label{ssub:gd1_data}
-            We utilize data from {\it Gaia} DR3 for the astrometric coordinates of each star, and Pan-STARRS1 to obtain more accurate color information.
-We adopt broad cuts on the cross-matched data to limit the field to a region known to contain GD-1.
-We perform these rough cuts by requiring \JN{fill in what the cuts are and reference proper motion figure and CMD figure.}
-
-            The result is a field populated by \JN{x} stars, from which we would like to identify stream members.
-
-        \subsubsection{Model Specification}\label{sec:GD_1_ModelSpecification}
-
-            We model GD-1 as a three-component mixture consisting of a main stream component, a spur, and background.
-In order to guide our model towards GD-1, we set down 4 ``control points" along GD-1's main track, and 3 control points along the spur (illustrated in \JN{x}).
-These control points act as gaussian priors on the model.
-We set the Gaussian error on these control points to large values, so that their influence on the model is not dominant.
-Indeed, we find that the value of the control points is to help reduce training time, since otherwise it will take the flexible density model longer time to converge to the actual stream.
-
-            The weight parameter is also set to truncate to $0$ at $\phi_1 < X$ and $\phi_1 > Y$. This ensures that we do not model stream stars that fall
-
-        \subsubsection{Trained Density Model}\label{ssub:trained_gd1}
-
-            In this section we present results from our model applied to real {\it Gaia} and Pan-STARRS data of GD-1.
-
-            We visualize the performance of our model in identifying stream stars and characterizing the astrometric background with Fig.~\ref{fig:gd1-background}.
-The top panel shows the stream in $\phi_1$, $\phi_2$ coordinates, color-coded by membership probability (derived from Eq.~\ref{eq:membership_prob}).
-The following three rows represent background distributions in $\phi_2, \mu_{\phi_1}, \rm{\ and} \ \mu_{\rm phi_2}$, respectively taken at different $\phi_1$ increments centered on the red lines.
-The $\phi_1$ increments are roughly $\sim X$ in size.
-
-            The blue lines over-plotted represent the best fit model at the given $\phi_1$ slice.
-We find that the backgrounds are typically well characterized by the distributions adopted (described in \S-x).
-We can also see from Fig.~\ref{fig:gd1-background}
-            that the stream and spur components appear to be well characterized.
-
-            Our ability to recover the stream is demonstrated further in Fig.~\ref{fig:gd1-astrometrics}.
-In this figure, we only plot stars if their membership probability is greater than \JN{X}.
-The result is a ``gold" catalog of probable stream and spur members, extending over $X$-degrees in $\phi_1$.
-We find the expected gap around $\phi_1 \sim -20~\rm{deg}$, which has been proposed to be the location of the dissolved progenitor (CITE).
-
-            Our model also fits the distribution of stream stars in the CMD.
-These fits are illustrated in Fig.~\ref{fig:gd1-cmds}, where the CMD for the population in a given $\phi_1$ band is plotted, color-coded by stream membership probability.
-For the on-stream regions, the isochrone appears to provide a decent description of the stream, though there is room for further improvements (discussed in \S-x).
-However, we note that the stream's presence and absence in the isochrone is well captured by the mixture weight, which is a neural network output.
-
-            Additionally, the distance modulus is also a neural network output, conditioned on $\phi_1$.
-This allows us to obtain a distance modulus at each $\phi_1$ along the stream.
-The distance modulus track and (converted) distance track are illustrated in Fig.~\ref{fig:gd1-distance_modulus}.
-The left panel shows the distance modulus (in magnitudes), while the right shows the corresponding distance track.
-Importantly, the prior on the distance track is that the stream must fall between $[4,40]~\rm{kpc}$.
-Thus, our ability to recover the distance to GD-1 without substantial bias provides a useful indicator that our color-magnitude model combined with the astrometric model provide an adequate description of the data.
-\JN{more on this...}
-
-            \begin{figure*}[h]
+        We select on-stream and off-stream regions using the known $\phi_1,
+        \phi_2$ range of the mock stream.  The upper panel of
+        \autoref{fig:mock_data_photometric_background_selection} shows these
+        selections in blue and black, respectively.  The lower panel shows the
+        on and off-stream selections in photometric coordinates.  In this space
+        it is apparent that the on-stream region has two populations, drawn from
+        the isochrone and from background points included in the simple $\phi_1,
+        \phi_2$ box.  In contrast, the off-stream region has only the the
+        background population.  We use the off-stream population to train a
+        conditional normalizing flow (see
+        \autoref{sub:method:pre-training_distributions}) on the magnitudes $g$
+        and $r$ and conditioned on $\phi_1$.  The normalizing flow is now a
+        non-parametric distribution characterizing the photometric background,
+        including its variation over $\phi_1$.  For this mock stream the
+        flexibility of the normalizing flow greatly exceeds necessity: the
+        background is drawn from a $\phi_1$-invariant multivariate normal,
+        essentially the base distribution of the normalizing flow.  It is
+        therefore no surprise that the trained normalizing flow provides an
+        excellent characterization of the background.  We will later see that
+        the flow performs similarly well on complex distributions.  Having
+        trained the background photometric model we proceed to build and train
+        the full model.
+
+        Per \autoref{eq:stream_and_bkg_prob} the stream is an independent
+        addition of both astrometric and photometric models.  In astrometrics
+        the stream is a Gaussian track in $\phi_2$ and parallax $\parallax$,
+        using the model defined in
+        \autoref{ssub:method:astrometric_model:on_stream}.  We use a 4-layer
+        \texttt{LTD} with overall shape ($\phi_1$ input, 4 outputs), where the 4
+        outputs are $[\mu_{\phi_2}, \sigma_{\phi_2}, \mu_{\parallax},
+        \sigma_{\parallax}](\phi_1)$.  The network is small, but sufficiently
+        large to permit 15\% dropout and retain robust predictions.  The
+        photometric model is a distance modulus-shifted isochrone, using the
+        model outlined in  \autoref{ssub:method:photometric_model:on_stream}. We
+        use the same isochrone parameters as were used to simulate the stream,
+        including the \citet{GrillmairSmith2001} mass function.  For this mock
+        stream, we demonstrate simultaneous astrometric and photometric
+        modeling, linking the distance modulus and parallax track, as explained
+        in \autoref{ssub:method:linking_to_astrometrics}.
+
+        The total background model has two pieces, an astrometric and a
+        photometric model.  As a pre-training phase the photometric normalizing
+        flow model was fitted to an off-stream selection and is now held fixed.
+        The astrometric model is split in two components, the first is a uniform
+        distribution in $\phi_2$, and the second is an exponential distribution
+        for $\parallax$.  The uniform distribution does not have any parameters,
+        and thus no neural network.  The exponential distribution has only the
+        slope parameter and we use a 3-layer \texttt{LTD} with shape (1, 32, 1)
+        and 15\% dropout. Background and stream are combined in a mixture model
+        whose mixture parameters are a 4-layer (1, 64, 1) \texttt{LTD} network.
+        We train the mixture model with an \texttt{AdamW} optimizer with
+        learning rate of $5\times10^{-3}$ and a scheduler to periodically and
+        temporarily increase the learning rate, encouraging the optimizer
+        towards better minima.
+
+    \newpage
+    \subsection{Trained Density Model} \label{sub:results_mock:results}
+
+% sec: results_gd1 ---
+    \begin{figure*}[ht]
         \script{gd1/plot/data_selection.py}
@@
         \includegraphics[width=1\linewidth]{figures/gd1/data_selection.pdf}
-                \caption{Caption}
+        \caption{%
+            Data selections for \stream{GD-1}, within the data cube described in
+            \autoref{sub:results_gd1:data}.
+            %
+            \textbf{Row 1:}
+            Proper motion and photometric selections.  
+            The proper motion selection is the $[\mu_{\phi_1},
+            \mu_{\phi_2}](\phi_1)$ curve from \citetalias{Ibata+2021} (dashed
+            black line) buffered by $6$ and $3$ mas/yr, respectively (blue
+            curves defining the bottom left and top-right of the shaded
+            rectangular region). Viewed without $\phi_1$ we see the
+            $\mu_{\phi_1}, \mu_{\phi_2}$ ``phase''-like diagram. The photometric
+            selection is based on a 12 Gyr, [Fe/H] = -1.2 MIST isochrone,
+            buffered by 0.3 mag to select the stream. The data is cut at
+            $G\leq20$, before applying the isochrone selection.
+            %
+            \textbf{Rows 2 \& 3:}
+            Applying the combination of astrometric and photometric selections,
+            plotted for astrometric coordinates $\phi_2, \parallax,
+            \mu_{\phi_1}, \mu_{\phi_2}$.  The proper motions are plotted
+            relative to \citetalias{Ibata+2021}. Using a log-density coloring,
+            the stream is identifiable in all phase-space coordinates except
+            $\parallax$ where the errors are significant.  }
         \label{fig:gd1-data_selection}
     \end{figure*}
-
-            \begin{figure*}[h]
-                \script{gd1/plot/results.py}
+% --- sec: results_gd1 (end)
+
+        The result of applying our density model to the synthetic data is
+        illustrated in \autoref{fig:mock_data_result}. The top panel shows the
+        weight parameter that controls membership probability as a function of
+        $\phi_1$. The dashed curve represents the output of our data-driven
+        model, while the histogram is the ground truth. The second panel shows
+        the stream and background in the $(\phi_1,\phi_2)$ plane, and the third
+        panel shows the stream and background in the $(\phi_1,\parallax)$ plane.
+        Points are color-coded according to their membership probability
+        \autoref{eq:membership_prob}. The weight parameter clearly shows that
+        the model has captured the two prominent density variations along the
+        stream.  There are additional variations, mostly around the edges of the
+        stream, though re-sampling the neural network weights with dropout
+        reveals that these variations represent regions of higher model
+        uncertainty.
+
+        We find that the stream is successfully recovered in both astrometric
+        and photometric coordinates, with
+        $>99\%$ %$\variable{output/mock/ncorrect_variable.txt}\%$ 
+        of stream stars being recovered with membership probability greater than
+        $80\%$.  In the bottom two rows of \autoref{fig:mock_data_result} we
+        illustrate the synthetic data color-coded by stream membership
+        probability (top) and background membership probability (background) for
+        different $\phi_1$ slices. Importantly, the photometric portion of the
+        mixture model successfully identifies the stream in magnitude space,
+        showing a high stream membership probability where the stream is
+        present, and a low probability ($\sim 0$) where the stream is absent.
+        The false positive rate (i.e., stars misidentified as stream members)
+        for this test is found to be $<0.1\%$ (3 stars) when cutting on the 80\%
+        membership probability threshold.
+
+% sec: results  (end)
+
+\section{Results: GD-1} \label{sec:results_gd1}
+
+    We now apply our method for stream characterization to the stellar stream
+    \stream{GD-1}, initially discovered by \citet{GrillmairDionatos2006}.
+    Previous work has identified several density variations along \stream{GD-1}
+    \citep{deBoer+2018}, including a bifurcation that can be modeled by an
+    encounter with a dense dark matter subhalo \citep{Bonaca+2019, Webb+2019}.
+    Characterizing the detailed density fluctuations of this stream is therefore
+    important for constraining a population of perturbers.  We discuss the data
+    selection in \autoref{sub:results_gd1:data}, model specifics in
+    \autoref{sub:results_gd1:model}, and the results in
+    \autoref{sub:results_gd1:results}.
+
+    \subsection{Data Selection} \label{sub:results_gd1:data}
+
+        We utilize data from \Gaia{} DR3 for the astrometric coordinates of each
+        star.  To obtain more accurate color information, we cross-match the
+        \Gaia{} field on \PanStarrs{} \citep{PanSTARRS1} using \Gaia's provided
+        \texttt{Best-neighbors} catalog.  To limit the field to a region known
+        to contain \stream{GD-1} we adopt broad cuts on the cross-matched data.
+        We perform these rough cuts by requiring the data lie within the
+        phase-space cube:
+        \begin{itemize}
+            \setlength\itemsep{0em}
+            \item $\phi_1 \in [-100, 40] \ \rm{deg}$,
+            \item $\phi_2 \in [-9, 5] \ \rm{deg}$,
+            \item $\parallax \in [-10, 1] \ \rm{mas}$,
+            \item $G_{\rm BP} \in [-1, 3] \ \rm{mag}$
+            \item $g, r \in [0, 50] \ \rm{mag}$, %, and not \texttt{null},
+        \end{itemize}
+        where we use \package{gala}'s \citep{gala, galav1.3} \code{GD1Koposov10}
+        frame \citep{Koposov+2010} to define $\phi_1$, $\phi_2$, and associated
+        proper motions.  For downloading purposes we split the query into 32
+        sub-regions in even $\phi_1$ increments.  Stream-specific coordinates
+        ($\phi_1, \phi_2$) are not included in \Gaia.  One could embed the
+        coordinate transform in the ADQL \citep{ADQL2.0}, or define great-circle
+        arcs in ICRS \citep{ICRS1997}. Since only rough cuts are required and
+        since the sub-region boxes are sufficiently small for a reasonable
+        flat-sky approximation  we simply translate the ($\phi_1, \phi_2$) boxes
+        to ICRS.  We correct the \PanStarrs{} photometry for dust extinction
+        using the \textit{Bayestar19} \citep{Green+2019} models in the
+        \package{dustmaps} package \citep{Green2018}.  \textit{Bayestar19} is a
+        three-dimensional dust map of the Milky Way for which we use \Gaia's
+        position and parallax distance information. We note that the extinction
+        has very little dependence on the distance past $\approx 8 \ \rm{kpc}$.
+        For stars with missing parallax measurements we assume a distance of
+        $8.5 \ \rm{kpc}$, a typical distance to the stream, thus increasing
+        potential membership probability. Adopting a slightly lower or higher
+        fiducial distance does not significantly change the results of our
+        analysis. We include the 1$\sigma$ errors as a source of uncertainty in
+        $\mbs{\Sigma}_n$, the per-star photometric uncertainty.  We also correct
+        the parallax for the zero-point using the
+        \href{https://pypi.org/project/gaiadr3-zeropoint/}{\code{gaiadr3-zeropoint}}
+        package, which implements the findings from \cite{Lindegren+2021}.  The
+        result is a field populated by \variable{output/gd1/ndata_variable.txt}
+        stars, from which we would like to identify stream members.
+
+        We create data masks for a higher signal-to-noise selection around
+        \stream{GD-1}.  The two mask types, proper motion and photometric, are
+        shown in \autoref{fig:gd1-data_selection}. For the proper motions we use
+        \citet{Ibata+2021} (hereafter \citetalias{Ibata+2021}) as the reference
+        for the known track of the stream. We select all all stars with
+        $\mu_{\phi_1}^*, \mu_{\phi_2}$ within 6 mas/yr of the track, as a
+        function of $\phi_1$. In \autoref{fig:gd1-data_selection} the proper
+        motion data are shown as the difference from the \citetalias{Ibata+2021}
+        track.  In photometric coordinates we define a mask around a $12 \
+        \rm{Gyr}$, [Fe/H] = $-1.2$ isochrone at a distance of $7.8 \ \rm{kpc}$.
+        The selection region is a $0.3 \ \rm{mag}$ orthogonal buffer around the
+        MIST isochrone \citep[using][]{brutus}, which is illustrated in the
+        2nd-from-the-top-left plot in \autoref{fig:gd1-data_selection}. The
+        buffered isochrone selection is wide enough to contain \stream{GD-1}
+        over its full distance gradient, including the ``typical" distance of
+        8.5 kpc used in the photometric correction.  In addition, to avoid
+        detailed modeling of the completeness as a term in $\prior_{obs}$ (from
+        \autoref{eq:isochrone_prior_components}) we mask out photometry with $G
+        > 20$.  With combinations of these masks the stream has much larger
+        signal-to-noise, though is still only a small percent of the total data.
+
+    \subsection{Model Specification}\label{sub:results_gd1:model}
+
+        \begin{figure}
+            \script{gd1/plot/photometric_background_selection.py}
             \centering
-                \includegraphics[width=1\linewidth]{figures/gd1/results.pdf}
-                \caption{CAPTION}
-                TODO:
+            \includegraphics[width=1\linewidth]{figures/gd1/photometric_background_selection.pdf}
+            \vspace{-20pt}
+            \caption{%
+                The on and off-stream selection.
+                % 
+                \textbf{Top panel:} Astrometric coordinates ($\phi_1$,
+                $\phi_2$).  Light blue points are the stream and background
+                within an on-stream region. Black points are in the off-stream
+                region used to train the background photometric model. Note this
+                plot is generated from a reduced field with a tighter proper
+                motion cut to aid in visually identifying the stream.  The
+                proper motion cut is $-15 < \mu_{\phi_1}^* < -10$, $-4.5 <
+                \mu_{\phi_2} < -2$ [mas/yr].
+                %
+                \textbf{Bottom panel:} CMD of the astrometric selection above.
+                The stream's isochrone is apparent as an overdensity.
+                %
+            }
+            \label{fig:gd1-photometric_background_selection}
+        \end{figure}
+
+        The modeling framework, detailed in section \autoref{sec:method}, is
+        modular, allowing many model components to be combined, nested, added to
+        the mixture, and linked via priors.  The model we require for
+        \stream{GD-1} is similar to the model built for the mock stream in
+        \autoref{sub:results_mock:model}, but has additional components for
+        \stream{GD-1}'s spur.  In this section we will discuss how the total
+        model is built, noting similarities to the example mocks-stream model.
+
+        All full stream models necessarily include a background model, which we
+        model in both astrometric and photometric spaces.  The photometric
+        background is too complex to capture with simple analytic distributions.
+        Instead, we train a normalizing flow on the magnitudes $g, r$,
+        conditioned on $\phi_1$. We refer readers to
+        \autoref{sub:method:pre-training_distributions} for discussion of the
+        photometric distribution and how a normalizing flow can characterize
+        this complex distribution, including its variation over $\phi_1$.  The
+        flow's flexibility, while necessary in this context, also poses a
+        problem: the flow captures the stream as easily as the background.
+        Consequently we select on-stream and off-stream regions using the known
+        $\phi_1,\phi_2$ range of the stream, as shown in the upper panel of
+        \autoref{fig:gd1-photometric_background_selection}.  In the lower panel
+        we plotted this selection in photometric coordinates, where an isochrone
+        is apparent in the on-stream selection.  The normalizing flow is trained
+        on the off-stream selection, and will be fixed (not trainable, nor
+        contribute to the gradient) when incorporated into the larger model.
+
+        Unlike for the photometry, the astrometric background could be (mostly)
+        fit with simple analytic distributions.  This is true if the selected
+        field is large enough -- the distribution in each coordinate is
+        approximately a skew-normal or a similarly tailed exponential-type
+        function. However by defining a higher signal-to-noise field around the
+        \citet{Ibata+2021} stream track in $\mu_{\phi_1}^*, \mu_{\phi_2}$, the
+        background in these coordinates is no longer well described by an
+        exponential distribution. Similarly, for much of the extent of
+        \stream{GD1's} field the parallax is well modeled by a truncated
+        skew-normal distribution, $\parallax \sim \rm{TruncSkew}\mcal{N}(\mu,
+        \Sigma; a, b)$, however for $\phi_1 \in [-100, -60]$ this does not hold.
+        Rather than splitting the model at a somewhat arbitrary $\phi_1$ or
+        interpolating between two distributions we instead fit the astrometry
+        with a $\phi_1$-conditioned normalizing flow. The background model is
+        characterized by:
+
         \begin{itemize}
-                    \item Add plot of the stream linear density
-                    \item Reduce the distance between the plot sections
-                    \item Color palette for the spur
-                    \item more subtle stream MLE path
-                    \item weight 5th and 95th percentile distribution
-                    \item rerun model with larger pmphi2 sigma
-                    \item add the isochrones to the cmd plots
+            \setlength\itemsep{0em}
+            \item $\phi_2, \sim \rm{TruncExp}(\lambda; a, b)$: a truncated
+                exponential distribution (see
+                \autoref{app:sub:exponential_distribution}).  The distribution
+                has 1 slope parameter.
+            \item $\mu_{\phi_1}^*, \mu_{\phi_2}, \varpi \sim q_{\rm flow}$: a 3
+                argument , one context feature ($\phi_1$) normalizing flow
+                trained on an off-stream selection (see
+                \autoref{fig:gd1-photometric_background_selection} for that
+                selection). Though discussed in the context of a photometric
+                background, \autoref{sub:method:pre-training_distributions}
+                details how these flows are constructed and trained.
         \end{itemize}
-                \label{fig:gd1-results}
+
+        We model the main stream of \stream{GD-1} similarly to the mock stream
+        -- as an independent addition of both astrometric and photometric
+        models.  The astrometric model for the stream is a 5-dimensional
+        Gaussian in a Gaussian track in $\phi_2, \parallax, \mu_{\phi_1},
+        \mu_{\phi_2}, \parallax$, using the model defined in
+        \autoref{ssub:method:astrometric_model:on_stream}.  The parameter
+        network's 10 outputs are $\mbs{\theta} = [\mu_{\phi_2}, \sigma_{\phi_2},
+        \mu_\parallax, \sigma_\parallax, \mu_{\mu_{\phi_1}^*},
+        \sigma_{\mu_{\phi_1}^*}, \mu_{\mu_{\phi_2}}, \sigma_{\mu_{\phi_2}},
+        \mu_\parallax, \sigma_\parallax](\phi_1)$.  In testing the network is
+        sufficiently large to permit 15\% dropout and retain robust predictions.
+
+        The stream's photometric model is a distance modulus-shifted isochrone,
+        using the model from \autoref{ssub:method:photometric_model:on_stream}.
+        We use a $12 \ \rm{Gyr}$, [Fe/H]$ = -1.2$ MIST isochrone with no assumed
+        intrinsic dispersion.  \stream{GD-1}'s true spectroscopic metallicity is
+        [Fe/H]$\lesssim-2$, but there is enough degeneracy in age and
+        metallicity that the chosen isochrone empirically matches the CMD locus
+        and is useful in this modeling context.  Using the method described in
+        \autoref{ssub:method:linking_to_astrometrics} the distance modulus track
+        is set by the parallax track in the astrometric model. Thus the
+        on-stream photometric model has no independent parameters and
+        consequently no neural network.
+
+        \variable{output/gd1/control_points.tex}
+
+        We model the spur of \stream{GD-1} as a separate component to the main
+        stream. The spur has an identical model as the stream: a 5-D astrometric
+        Gaussian and isochrone in the photometry. Owing to their common origin,
+        we impose the prior that the spur and stream share the same isochrone.
+        The parallax is also shared, motivated by initial findings, and that
+        there were too few stars to robustly detect any deviations.
+
+        \variable{output/gd1/member_table_select.tex}
+
+        The parameter phase-space is large and a random initialization will take
+        significant time to converge towards the stream track. This initial
+        training is unnecessary as the rough stream track is known \textit{a
+        priori}.  To guide the astrometric model towards the known
+        \stream{GD-1}, we set down guides (see
+        \autoref{sub:methods:priors:track_region_prior}) along \stream{GD-1}'s
+        main track and on the spur.  We set the width of these guides to large
+        values, so that their influence on the model is not dominant. Indeed, we
+        find that the value of the guides is to help reduce training time, since
+        otherwise it will take the flexible density model much longer to
+        converge to the actual stream.  We include all the track regions in
+        \autoref{tab:gd1_track_prior}.
+
+        All the component models are tied together into a mixture model.  The
+        singular weight parameter network is a \texttt{LTD} network with 15\%
+        dropout.  The stream weights are in the range $\ln f \in [-10, 0]$,
+        while the spur weights are $\ln f \in [-10, 0]$ and set to 0 for $\phi_1
+        < -45, -15 < \phi_1$.  By \autoref{eq:mixture_weight_normalization} the
+        background brings the cumulative weight to one, normalizing the mixture.
+
+    \subsection{Trained Density Model}\label{sub:results_gd1:results}
+
+        \begin{figure*}[ht]
+            \script{gd1/plot/results_full.py}
+            \centering
+            \includegraphics[width=0.83\linewidth]{figures/gd1/results_full.pdf}
+            \caption{%
+                The model for \stream{GD-1}, including both a thin-stream and
+                spur component.  For comparison we include the tracks from
+                \citet{Price-WhelanBonaca2018} and \citet{Ibata+2021}. Note how
+                the model largely agrees with the latter track in all
+                astrometric dimensions.
+                %
+                \textbf{Panel 1: }%
+                    The stream mixture coefficients $f(\phi_1)$ predicted by the
+                    model, colored by the stream and spur membership likelihood.
+                %
+                \textbf{Panel 2: }
+                    $\phi_2(\phi_1)$ over the full range of $\phi_1$. The data
+                    color and transparency are set by the model's
+                    50th-percentile stream and spur probability. We include the
+                    error bars for stars with $>75\%$ membership probability.
+                    The predicted 50th-percentile track $\pm$ width is
+                    over-plotted (red band), along with the 90\% confidence
+                    region (broader red band).  The 5th to 95th percentile
+                    variation in the width is shown  in the adjoining top plot.
+                %
+                \textbf{Panel 3 \& 4: }%
+                    $\parallax(\phi_1)$ and $d(\phi_1)$ over the full range of
+                    $\phi_1$. The $\parallax$ is tied to the photometry -- see
+                    \autoref{fig:gd1-results-panels}.
+                %
+                \textbf{Panel 5 \& 6: }%
+                    The proper motions $\Delta \mu_{\phi_1^*}, \Delta
+                    \mu_{\phi_2}$ shown relative to the galstreams track (black
+                    dashed line). The model convolves observational errors with
+                    the stream width, but the large fractional errors make the
+                    determination difficult.   }
+            \label{fig:gd1-results-full}
         \end{figure*}
 
-            \begin{figure*}
+        \begin{figure*}[t]
+            \script{gd1/plot/results_panels.py}
             \centering
-                \includegraphics[scale=0.8]{figures-not-syw/gd1/gd1_heatmap_density_KDE2.pdf}
-                \caption{Caption}
+            \includegraphics[width=1\linewidth]{figures/gd1/results_panels.pdf}
+            \caption{%
+                Photometric coordinate $(g, r)$ plots for each model component
+                in 4 $\phi_1$ ranges across the data set. Over-plotted is the
+                model isochrone, shifted to the mean distance of the track
+                within the selected $\phi_1$ range. Importantly this means we do
+                not expect the mean isochrone to exactly match the distribution
+                of points. See \autoref{fig:gd1-results-full} for the match of
+                the distance gradient to the data and prior literature results.
+                %
+            }
+            \label{fig:gd1-results-panels}
+        \end{figure*}
+
+        In this section we present results from our model applied to real {\it
+        Gaia} and Pan-STARRS data of \stream{GD-1}.  We visualize the
+        performance of our model in identifying stream stars in
+        \autoref{fig:gd1-results-full}, and illustrate our photometric fit in
+        \autoref{fig:gd1-results-panels}. In \autoref{tab:gd1_member_table} we
+        provide a selection of \stream{GD-1} member stars. The full catalog is
+        available online at
+        \href{https://zenodo.org/records/10211410}{zenodo:10211410}. Lastly,
+        \autoref{fig:gd1-heatmap} is a membership probability-weighted density
+        heatmap of the \stream{GD-1} stream derived from our fit.
+
+        In \autoref{fig:gd1-results-full}, the top panels shows the fraction of
+        stars belonging to the stream (red) and spur (yellow) as a function of
+        $\phi_1$. The second panel illustrates the stream in $\phi_1$, $\phi_2$
+        coordinates, color-coded by the membership probability for the stream
+        and spur components (derived from \autoref{eq:membership_prob}). The
+        following rows represent the other astrometric dimensions for the stream
+        and spur components, with the distance track obtained through our
+        photometric model (visualized in \autoref{fig:gd1-results-panels} and
+        discussed below). The red and yellow bands represent model predictions
+        for the main stream and spur, respectively. The points with thick error
+        bars represent control points (discussed in
+        \autoref{sub:results_gd1:model}) for the stream and spur components,
+        which are priors on the location of the stream and spur components
+        across the astrometric dimensions. The control points in the parallax
+        panel represent the reliable parallax and distance modulus estimates
+        from \citet{deBoer+2020}. The actual data points are color-coded by the
+        maximum membership probability of belonging to any of the three model
+        components (i.e., maximum of the main stream, spur, or background
+        components). For stars with membership probability greater than $75\%$,
+        we also plot their astrometric errorbars from \Gaia{} as the thin red
+        lines.
+
+        Because the neural networks are trained with dropout, we can estimate
+        the modeling uncertainty in our fits to each stream with a Monte Carlo
+        procedure \citep{GalGhahramani2015}. Namely, by incorporating dropout
+        during both neural network training and inference, the distribution of
+        model outputs represents the posterior predictive distribution,
+        marginalized over the neural network parameters. An estimate of this
+        distribution is shown in the weight parameter of
+        \autoref{fig:gd1-results-full}, represented as the red (main stream) and
+        yellow (spur) bands. For the astrometric dimensions, our model predicts
+        a mean track, and a standard deviation. Error bands are estimated by
+        incorporating dropout with a rate of 15\%. Each of the panels in
+        \autoref{fig:gd1-results-full} shows the track mean and width,
+        calculated from the 50th percentile of the posterior predictive
+        distribution for both quantities. Plotted behind that is the 90\%
+        credible region of the track mean. We note that the credible region of
+        the mean alone is generally larger than that of the $\mu \pm \sigma$
+        50th-percentile ridge. This highlights the importance of exploring the
+        full posterior of parameters, not only a Maximum Likelihood Estimation
+        (MLE) or posterior ridge-line.
+
+        Our model finds \variable{output/gd1/nstream/nstream_variable.txt}stars
+        that belong to the main stream component with membership probability
+        greater than
+        \variable{output/gd1/nstream/minimum_membership_probability.txt} at the
+        \variable{output/gd1/nstream/posterior_percentile.txt} percentile in the
+        membership posterior distribution. For the spur component, there are
+        \variable{output/gd1/nspur/nspur_variable.txt} stars with the same
+        membership probability threshold at the same percentile of the posterior
+        distribution.  A tabulation of the astrometry, photometry, and
+        membership posterior distribution for each star is included in
+        \autoref{tab:gd1_member_table}. The full table may be found on the
+        paper's
+        \href{https://github.com/nstarman/stellar_stream_density_ml_paper}{GitHub
+        repository}. \autoref{tab:gd1_member_table} gives the MLE prediction,
+        but also samples the 5th-95th percentile of the posterior distribution
+        of the likelihood using the dropout method. The variation in the 90\%
+        credible region in the track means there can be significant variation in
+        a star's estimated membership probability.
+
+        The extent of the main stream in $\phi_1$ is roughly $80~\rm{deg}$, and
+        the angular extent of the spur is roughly $15~\rm{deg}$. The distance
+        track (bottom panel) places the stream in the range of $6-10~\rm{kpc}$,
+        with an upwards concavity as a function of $\phi_1$. This result is
+        consistent with other works, which find a similar distance to
+        \stream{GD-1} using other techniques \citep{deBoer+2020, Ibata+2021}.
+        Importantly, our distance estimate is not hard-coded to fall in this
+        range: we allow for the stream track to fall anywhere within
+        $[4,40]~\rm{kpc}$, with a broad prior around previous literature
+        estimates. The similarity of our inferred distance track compared to
+        other works indicates that our photometric model is performing
+        satisfactorily.
+
+        We also recover the well-known underdensity gaps along the stream around
+        $\phi_1 \approx -40, -20 \ \rm{and } -5~\rm{deg}$ (seen best in
+        \autoref{fig:gd1-heatmap}). The $-20\degree$ feature was first reported
+        by \citet{CarlbergGrillmair2013}, and is one location hypothesized for
+        the dissolved stream progenitor. \citet{WebbBovy2019} suggests the
+        $-40\degree$ gap might be  the progenitor location.  The recovery of
+        this density fluctuation from a joint model in astrometric and
+        photometric coordinates developed here argues that the feature is indeed
+        intrinsic to the stream and not an artifact of the data.
+
+        The spur is a distinct component of our model, independent in its weight
+        and all astrometric dimensions except $\parallax$ which is shared with
+        the \stream{GD-1} main stream through the photometric model. The model
+        finds a non-negligible spur feature, with a peak fractional weight
+        approaching the thin stream. As corroboration, the proper motion of the
+        spur closely agrees with the thin stream. The alignment of these
+        dimensions is not hard-coded in our model. The width of the spur in
+        proper motion is very thin, thinner even than the stream.  However with
+        the large observational errors and low number density of the spur it is
+        difficult to attribute this to a physical difference between the two
+        systems. In contrast, the small errors in $\phi_2$ indicate the spur's
+        width diverges from the thin stream at $\phi_1 > -35 \ \rm{deg}$,
+        whereas the width is similar at lower $\phi_1$. There are numerous
+        mechanisms by which a stream's width may vary \citep[e.g.  epicyclic
+        effects as in][]{Ibata+2020}, so differences between the spur and stream
+        are both notable and expected.
+
+        \stream{GD-1} has other observed tidal features, namely the ``blob''
+        \citep{Price-WhelanBonaca2018}, which is a very diffuse component
+        enclosing the thin stream. When fitting our model to \stream{GD-1} with
+        a more stringent proper motion cut, we are able to recover the blob. In
+        a more crowded field, the stream makes up only a few percent of the
+        total number of stream stars, so diffuse features like the blob are not
+        separated from the background. We could, perhaps, guide the model
+        towards the blob by adding an additional mixture distribution that is
+        specialized to diffuse components around the thin stream. Because the
+        aim of the current paper is to introduce and demonstrate our method, we
+        defer a more detailed fit of the diffuse extra-tidal structure of Milky
+        Way streams to future work.
+
+        We note that the model-predicted track does not always closely align
+        with the predicted member stars or our notion of a slowly-evolving
+        stream. This misalignment is most evident in $\mu_{\phi_1^*}$, where the
+        track has a sharp turn up at $\phi_1 \sim -65 \ \rm{deg}$ and then
+        flattens out. There are a number of contributing factors. First, the
+        observational uncertainties are large enough that this flattening is
+        consistent with the data. Second, we do not enforce the stream track to
+        be smooth with $\phi_1$ -- our fits are dictated by the data.  Last,
+        examining 2D slices when fitting in high dimensional spaces can be
+        misleading \citep{Aggarwal+2002}. Unsurprisingly, the raw membership
+        probabilities for each model component provide a more accurate
+        representation of the stream's 6d phase-space distribution than any
+        phase-space slice could, as may be seen in \autoref{fig:gd1-heatmap}. We
+        discuss the smoothed stream model determined solely by membership
+        probabilities at the end of this section.
+
+        We highlight the performance of our photometric model in
+        \autoref{fig:gd1-results-panels}. In this figure, we color-code each
+        star by its membership probability (top row; same as
+        \autoref{fig:gd1-results-full}), and in the bottom row we visualize the
+        performance of our photometric model in bands of $\phi_1$. Our model
+        isochrone, which shifts vertically due to our distance modulus estimate,
+        is shown in green (we plot the mean-distance isochrone in each $\phi_1$
+        band). Because our model preforms a joint fit in photometry and
+        astrometry, the most probable stream members do not need to fall exactly
+        along the isochrone.  Still, the likely stream members are
+        overwhelmingly distributed as might be expected from a single-stellar
+        population.  Even the more diffuse tails of the stream can be seen in
+        the CMD distribution, where they still roughly follow a single-stellar
+        population.
+
+        With membership probabilities for each component of the stream estimated
+        from both astrometry and photometry, it is possible to quickly construct
+        a custom representation of the stream's phase-space density. We
+        illustrate this in  \autoref{fig:gd1-heatmap}, which shows a Gaussian
+        kernel density estimate (KDE) of bandwidth $0.1 \ \rm{deg}$ (or mas/yr)
+        fit to the model. The primary overdensities at $\phi_1 = (-50, -30, -10)
+        \ \rm{deg}$ are all visible in $\phi_2$. The gap at $20 \ \rm{deg}$ is
+        prominent in all features, but the gap at $-40$ is less visible in
+        proper motions, since the spur shares the stream's proper motions and
+        thus contributes to the density in those coordinates. This highlights
+        the importance of constructing a multidimensional smooth density model
+        of streams.
+
+        \begin{figure}[ht]
+            \script{gd1/plot/smooth_likelihood.py}
+            \centering
+            \hspace{-25 pt}\includegraphics[width=1.05\linewidth]{figures/gd1/smooth_likelihood.pdf}
+            \caption{%
+                Smoothed KDE model of \stream{GD-1}'s member stars, weighted by
+                their membership probability. The KDE has a bandwidth of $0.1 \
+                \rm{deg}$ (or mas/yr).  In $\phi_2$ the spur is clearly visible
+                in the KDE.  The gaps at $-20\degree$ are prominent in both
+                $\phi_2$ and $\mu_{\phi_1}$.  The gap at $-40\degree$ is most
+                prominent in $\phi_2$.
+                %
+            }
             \label{fig:gd1-heatmap}
+        \end{figure}
+
+% sub: gd1 (end)
+
+\section{Results: Palomar 5} \label{sec:results_pal5}
+
+    We now apply the method to the stellar stream \stream{Palomar 5}.
+    Historically lengths of the stream have been found with matched filter
+    photometric techniques, like with the discovery in \citet{Odenkirchen+2001}.
+    Post-\Gaia{} the stream was also observed by filtering kinematically
+    \cite[e.g.,][]{Starkman+2019, Ibata+2021}.  However at $\sim 20 \ \rm{kpc}$,
+    the \stream{Pal\,5} main sequence is not observed by \Gaia{}, making a high
+    signal-to-noise astrometric detection challenging.  We discuss the data
+    selection in \autoref{sub:results_pal5:data}, model specifics in
+    \autoref{sub:results_pal5:model}, and the results in
+    \autoref{sub:results_pal5:results}.
+
+    \begin{figure*}[ht]
+        \script{pal5/plot/data_selection.py}
+        \centering
+        \includegraphics[width=1\linewidth]{figures/pal5/data_selection.pdf}
+        \caption{%
+            Data selections for \stream{Pal\,5}, within the data cube described
+            in \autoref{sub:results_pal5:data}.
+            %
+            \textbf{Row 1:}
+            Proper motion and photometric selections.  \stream{Pal\,5} is
+            apparent in the proper motions as a small overdensity. The
+            photometric selection is based on a 12 Gyr, [Fe/H] = -1.2 MIST
+            isochrone, buffered by 0.3 dex. The photometry is also cut to
+            \Gaia{}'s $G\leq20$ mag, before applying the isochrone selection.
+            %
+            \textbf{Rows 2 \& 3:}
+            Applying the combination of astrometric and photometric selections,
+            plotted for astrometric coordinates $\phi_2, \parallax,
+            \mu_{\phi_1}, \mu_{\phi_2}$.  The stream is an identifiable
+            overdensity in only $\phi_2$ and errors dominate all other
+            coordinates.  }
+        \label{fig:pal5-data_selection}
     \end{figure*}
 
-            \input{output/gd1_members.tex}
-
-    % subsection gd1 (end)
-
-% section results (end)
-
+    \subsection{Data Selection} \label{sub:results_pal5:data}
+
+        We construct a \Gaia{} DR3 - \PanStarrs{} crossmatched field very
+        similarly to the procedure outlined in \autoref{sub:results_gd1:data}
+        for \stream{GD-1}.  To limit the field to a region containing
+        \stream{Pal\;5} we adopt broad cuts on the data by requiring the data
+        lie within the phase-space cube:
+        \begin{itemize}
+            \setlength\itemsep{0em}
+            \item $\phi_1 \in [-20, 20] \ \rm{deg}$,
+            \item $\phi_2 \in [-5, 10] \ \rm{deg}$,
+            \item $\parallax \in [-10, 1] \ \rm{mas}$,
+            \item $\rm{G-R} \in [-0.5, 1.2] \ \rm{mag}$
+            \item $g, r \in [0, 30] \ \rm{mag}$,
+        \end{itemize}
+        where we use \package{gala}'s \code{Pal5PriceWhelan18} frame
+        \citep{Price-Whelan+2019} to define $\phi_1$, $\phi_2$, and associated
+        proper motions.  Using the \textit{Bayestar19} maps we correct the
+        \PanStarrs{} photometry for dust extinction.  For stars without distance
+        information we assume a distance of $20 \ \rm{kpc}$, a typical distance
+        to the stream \citep{Harris1996, Odenkirchen2003, Grillmair2006,
+        Ibata+2016, Price-Whelan+2019} and thus increasing the probability of
+        the star being considered a member.  The 1$\sigma$ dust correction
+        errors are included by quadrature in $\mbs{\Sigma}_n$, the per-star
+        photometric uncertainty. We also correct the parallax for the \Gaia\
+        zero-point as in \autoref{sub:results_gd1:data}.  The result is a field
+        populated by \variable{output/pal5/ndata_variable.txt} stars, from which
+        we would like to identify stream members.
+
+        Within the broad selection cuts, we create more specific data masks.  In
+        particular we mask concentrated over-densities, like the globular
+        cluster \stream{M5}, that are not associated with \stream{Pal\;5}.  In
+        \autoref{fig:pal5-data_selection} we show the proper motion and
+        photometric masks, with \stream{M5} already filtered out.  The proper
+        motion mask extends from $\mu_{\phi_1}$ and $\mu_{\phi_2} \in (-4, -1)$
+        [mas/yr].  The photometric mask is defined by a $0.15 \ \rm{mag}$ buffer
+        around a $[\rm{Fe}/{H}] = -1.3$, $11.5 \ \rm{Gyr}$ isochrone. It is the
+        shape of the isochrone which is important, not the physical reality of
+        the metallicity nor age, discussed in further detail in
+        \autoref{ssub:method:photometric_model:on_stream}.  In addition, to
+        avoid detailed modeling of the completeness as a term in $\prior_{obs}$
+        (from \autoref{eq:isochrone_prior_components}) we mask out photometry
+        with $G > 20$.  With combinations of these masks the stream has much
+        larger signal-to-noise, though is still only a small fraction of the
+        total data.
+
+        The reduced dataset, with all specific masks applied, is included below
+        the data mask plots in \autoref{fig:pal5-data_selection}. In $\phi_2$,
+        $\mu_{\phi_1}^*$, and $\mu_{\phi_2}$ the \stream{Pal\,5} progenitor is
+        clearly visible. Only in $\phi_2$ is the stream visible, and then only
+        for a few degrees around the progenitor. The distance of \stream{Pal\,5}
+        means most $\parallax$ measurements have $\sim 100\%$ errors, so neither
+        the stream nor even the progenitor are evident.
+
+    % sub data_selection (end)
+
+    \vspace{-6pt}
+    \subsection{Model Specification} \label{sub:results_pal5:model}
+
+        In this section we discuss how the total \stream{Pal\,5} model is built,
+        using the modular modeling framework from \autoref{sec:method}.  We
+        model the stream of \stream{Pal\;5} as a single Gaussian component
+        conditioned on $\phi_1$. As a function of $\phi_1$, the astrometric
+        stream density is a 3-dimensional Gaussian in $\phi_2, \mu_{\phi_1},
+        \mu_{\phi_2}$, using the model defined in
+        \autoref{ssub:method:astrometric_model:on_stream}.  The parameter
+        network is a 5-layer \texttt{LTD} where the 6 outputs are $\mbs{\theta}
+        = [\mu_{\phi_2}, \sigma_{\phi_2}, \mu_{\mu_{\phi_1}^*},
+        \sigma_{\mu_{\phi_1}^*}, \mu_{\mu_{\phi_2}},
+        \sigma_{\mu_{\phi_2}}](\phi_1)$.  In testing, the network is
+        sufficiently large to permit 15\% dropout and retain robust predictions.
+        At $\sim 20 \ \rm{kpc}$ any \Gaia{}-crossmatched data is not
+        photometrically deep enough to contain the main sequence nor its turn
+        off. Thus we do not model the stream photometrically. We only use
+        photometric cuts to remove some background. Similarly, we do not include
+        the parallax as the errors are too large for the parallax to contribute
+        to the model.
+
+        \begin{figure}[ht]
+            \script{pal5/plot/photometric_background_selection.py}
+            \centering
+            \includegraphics[width=1\linewidth]{figures/pal5/photometric_background_selection.pdf}
+            \caption{%
+                \textbf{Top panel:} Astrometric coordinates ($\phi_1$,
+                $\phi_2$).  Light blue points are the stream and background
+                within an ``on"-stream region. Black points are in the
+                ``off"-stream region used to train the background photometric
+                model. The \stream{M5} cluster is masked as a black circle
+                cutting into the on-stream selection at $\phi_1\sim-1\degree$.
+                %
+                \textbf{Bottom panel:} CMD plot of the astrometric selection
+                above. The stream's isochrone is somewhat apparent, but the
+                background contamination is large.
+                %
+            }
+            \label{fig:pal5-photometric_background_selection}
+        \end{figure}
+
+        To avoid a large convergence time, we use as a prior the known stream
+        track, in this case \package{galstream}'s \citep{Mateu2022}
+        implementation of \stream{Pal\,5} from \citet{Ibata+2021}. From the
+        track, we set down guides (see
+        \autoref{sub:methods:priors:track_region_prior}) regularly spaced in
+        $\phi_1$. We include all the guides in \autoref{tab:pal5_track_prior}.
+        We don't place guides in the other coordinates, except at the location
+        of the progenitor, because the stream is not visible and the models
+        disagree on the proper motions (see \autoref{fig:pal5-data_selection},
+        top left plot).  The progenitor is an exception, both visible
+        kinematically and also extremely well measured
+        \citep{VasilievBaumgardt2021}, and we place a tight kinematic prior on
+        the stream track at the location of the progenitor.  The guide priors
+        are visible in \autoref{fig:pal5-results-full}.
+        \variable{output/pal5/control_points.tex}
+
+        The background is fit with an analytic distribution and a normalizing
+        flow:
+        \begin{itemize}
+            \setlength\itemsep{0em}
+            \item $\phi_2 \sim \rm{TruncExp}(\lambda; a, b)$: a truncated
+                exponential distribution (see
+                \autoref{app:sub:exponential_distribution}).  The distribution
+                has 1 parameter and we use a \texttt{LTD} neural network with
+                15\% dropout.
+            \item $\mu_{\phi_1}, \mu_{\phi_2} \sim q_{\rm flow}$: a two feature,
+                one context feature normalizing flow trained on an off-stream
+                selection (see
+                \autoref{fig:pal5-photometric_background_selection} for that
+                selection). \autoref{sub:method:pre-training_distributions}
+                details how these flows are constructed and trained.
+        \end{itemize}
+
+        All the component models are tied together into a mixture model.  The
+        weight parameter network is the usual \texttt{LTD} with 15\% dropout.
+        The stream weights are in the range $\ln{f_{\rm stream}} \in [-10, 0]$
+        and set to $-\infty$ for $\phi_1 \notin [-10^\circ, 10^\circ]$. By
+        \autoref{eq:mixture_weight_normalization} the background  brings the
+        cumulative weight to one, normalizing the mixture.
+
+    % sub model_specification (end)
+
+    \subsection{Trained Density Model} \label{sub:results_pal5:results}
+
+        \begin{figure*}[ht]
+            \script{pal5/plot/results_full.py}
+            \centering
+            \includegraphics[width=0.85\linewidth]{figures/pal5/results_full.pdf}
+            \caption{%
+                The model for \stream{Pal\,5}.  For comparison we include the
+                tracks from \citet{Price-Whelan+2019} and \citet{Ibata+2021}.
+                %
+                \textbf{Panel 1: }%
+                The stream mixture coefficients $f(\phi_1)$ predicted by the
+                model, colored by the stream membership likelihood. The
+                stream fraction and number density drop to nearly $0$ for $\phi_1 > 5 \
+                \rm{deg}$, making the track dominated by low-number
+                statistics.
+                %
+                \textbf{Panel 2: }
+                $\phi_2(\phi_1)$ over the full range of $\phi_1$. The data color
+                and transparency are set by the model's 50th-percentile stream
+                probability. We include the error bars for stars with $>75\%$
+                membership probability. The predicted 50th-percentile track
+                $\pm$ width is over-plotted (red band), along with the 90\%
+                confidence region (broader red bend). The 5th to 95th percentile
+                variation in the width is shown in the adjoining top plot.
+                %
+                \textbf{Panel 3: }%
+                $\parallax(\phi_1)$ and $d(\phi_1)$ over the full range of
+                $\phi_1$.
+                %
+                \textbf{Panel 4 \& 5: }%
+                The proper motions $\mu_{\phi_1^*}, \mu_{\phi_2}$. The model
+                convolves observational errors with the stream width, but the
+                large fractional errors make the determination difficult. The
+                track is largely consistent with 0 width driven by small number
+                statistics.  }
+            \label{fig:pal5-results-full}
+        \end{figure*}
+
+        \begin{figure*}[htp]
+            \script{pal5/plot/results_panels.py}
+            \centering
+            \includegraphics[width=1\linewidth]{figures/pal5/results_panels.pdf}
+            \caption{%
+                Photometric coordinate $(g, r)$ plots for each model component
+                in 5 $\phi_1$ ranges across the data set, centered on the
+                \stream{Pal\,5} progenitor.
+                %
+                On either side of the progenitor we strongly detect the stream
+                for $\approx 5\degree$ and tentatively for an additional
+                $\approx 5\degree$. The leading arm (positive $\phi_1$) track
+                for $\phi_1 > 5\degree$ is consistent with
+                \citet{Starkman+2019}. We do not detect any fanning of the
+                stream, but given the shallow photometry, this is expected.
+                %
+            }
+            \label{fig:pal5-results-panels}
+        \end{figure*}
+
+        \variable{output/pal5/member_table_select.tex}
+
+        Our fit to \stream{Pal\,5} and its tidal tails is illustrated in
+        \autoref{fig:pal5-results-full}. In the top panel we plot the stream
+        fraction and its uncertainty, estimated by applying dropout during
+        inference and evaluation of our model. The model clearly identifies the
+        progenitor cluster $(\phi_1 = 0)$.
+
+        The membership probability of stream stars is illustrated in subsequent
+        panels of \autoref{fig:pal5-results-full}, with guide points and their
+        widths shown in red. The leading and trailing arms of the stream are
+        clearly identified in our fits, with high membership probability on
+        either side of the cluster. Our model prefers a thin on-sky morphology
+        for \stream{Pal\,5}'s tidal tails, with an angular width of the stream
+        (parameterized by $\ln{\sigma_{\phi_2}}$) around $\sim 0.1~\rm{deg}$.
+        This is contrary to our fit of \stream{GD-1} in
+        \autoref{fig:gd1-results-full}, where we find a more appreciable width
+        of $\sim 0.2~\rm{deg}$ and above.  This inferred width is consistent
+        with \stream{Pal\,5} being more distant than \stream{GD-1}, though we
+        expect a thin inferred width for \stream{Pal\,5} since we do not model
+        the stream in photometric coordinates. When photometry is available, we
+        expect that our photometric model provides substantial constraining
+        power in characterizing the stream, since diffuse parts of the tidal
+        tails in on-sky angular coordinates remain tightly clustered in the CMD.
+        This clustering is seen in our \stream{GD-1} fits
+        (\autoref{fig:gd1-results-panels}), where even the more extended parts
+        of the stream remain clustered in the CMD.
+
+        The parallax, proper motion tracks, and their widths are also shown in
+        \autoref{fig:pal5-results-full}. The red vertical lines represent the
+        astrometric errors in each dimension, shown only for stars with
+        membership probability greater than $75\%$. The errors are large
+        compared to the width of the best fit stream track (shown as the red
+        band). The track is a valid minimum to our loss function: because our
+        model incorporates the large astrometric uncertainties, small variations
+        to the estimated width of the stream in each dimension do not produce
+        substantial changes to the loss function. Thus, a narrow stream in the
+        kinematic dimensions provides a valid fit to the stream given the data
+        at hand.
+
+        We also note that the track of the stream shown as the red band in each
+        dimension appears to have an abrupt change in direction around $\phi_1
+        \approx 7^\circ$. This also represents the region with the lowest stream
+        fraction, as seen in the top panel of \autoref{fig:pal5-results-full}.
+        In low stream fraction regions, the model is uncertain about the track
+        of the stream since only a few stars contribute to the on-stream fit.
+        The track changes highlight the importance of utilizing the membership
+        probabilities of individual stars when analyzing any given stream, since
+        membership probabilities incorporate information on the stream fraction
+        while the mean stream-track alone does not provide this information.
+
+        In \autoref{fig:pal5-results-panels} we again show the data in
+        $\phi_1-\phi_2$ coordinates, color-coded by membership probabilities in
+        the top panel (same colorbar as in \autoref{fig:pal5-results-full}). In
+        the bottom panels we plot the CMD of the data in bands of $\phi_1$. As
+        discussed, our fit to \stream{Pal\,5} does not incorporate information
+        from the CMD.  Thus, the bottom row represents a data-driven isochrone
+        for \stream{Pal\,5} and its tidal tails, obtained by fitting the
+        stream's astrometric overdensity. Indeed, the highest probability
+        regions of the CMD appear qualitatively similar to a standard isochrone,
+        with an extended and clustered sequence. The main sequence appears to be
+        missing, which is expected given our cut at $G = 20~\rm{mag}$, below
+        which the main sequence of \stream{Pal\,5} resides \citep{Bonaca+2020}.
+        The similarity of the color-magnitude distribution of \stream{Pal\,5}'s
+        tidal tails to the red end of a standard isochrone highlights the
+        validity of our astrometric membership model, since a photometric fit
+        was never performed.
+
+        The stream solution, i.e. the per-star membership likelihood, is a
+        posterior distribution. \autoref{fig:pal5-results-full} and
+        \autoref{fig:pal5-results-panels} show the membership likelihood
+        evaluated at the $50$th percentile of this distribution, per star. In
+        \autoref{fig:pal5-heatmap} we sample over the full distribution and
+        smooth by a 0.1~deg (or mas/yr) kernel to produce a smooth
+        representation of the stream. As a consequence of the sampling we see
+        the model's stream solution extends beyond the $\approx \pm5\degree$
+        shown previously.  Though the model certainty and individual membership
+        likelihoods are low, the stream path matches closely with findings in
+        deeper photometric catalogues, like \citet{Ibata+2017}.
+
+        \begin{figure}[ht]
+            \script{pal5/plot/smooth_likelihood.py}
+            \centering
+            \hspace{-25pt}\includegraphics[width=1.05\linewidth]{figures/pal5/smooth_likelihood.pdf}
+            \caption{%
+                Smoothed KDE model of the stream's member stars, weighted by
+                their membership probability. The KDE has a bandwidth of $0.1 \
+                \rm{deg}$ (or mas/yr). We exclude the progenitor to limit the
+                density range and better display the diffuse tidal tails. The
+                stream extends from $-12$ to $10$ degrees in this plot, which
+                appears longer than in \autoref{fig:pal5-results-full} and
+                \autoref{fig:pal5-results-panels}. Those show the membership
+                likelihood at the $50$th-percentile of its distribution. This
+                figure samples over the full posterior, showing the contribution
+                of less-likely members.
+                %
+            }
+            \label{fig:pal5-heatmap}
+        \end{figure}
+
+        While \Gaia{} alone is not photometrically capable of observing the main
+        sequence of \stream{Pal\,5}'s tidal tails, the modeling framework we
+        present here is capable of operating on outer-joined datasets. This
+        allows us to easily combine deep photometric data with kinematics from,
+        e.g., \Gaia{}.  We leave that to a future work, though expect that a
+        simultaneous model in photometry and astrometry would help identify the
+        more diffuse parts of the stream, which become washed out in our
+        astrometric fit due to the substantial number of background stars.
+        Still, this section highlights the capability of our model when applied
+        to a noisy field with a diffuse stream.
+
+    % sub trained_density_model
+
+% section pal5 (end)
+
+\section{Discussion} \label{sec:discussion}
+
+    We now provide a discussion of the methods presented in the paper, focusing
+    on limitations of our approach in \autoref{sec:limitations} and comparison
+    to existing methods in \autoref{sub:comparison}. In
+    \autoref{sub:future_surveys} we discuss prospects for applying our method to
+    existing and future datasets.
+
+    \subsection{Caveats and Limitations}\label{sec:limitations}
+
+        We now highlight the limitations of our method, and areas for potential
+        improvement.
+
+        First, our usage of neural networks ensures that our method is
+        expressive, and capable of describing a diverse range of stream
+        morphologies all under one framework. At the same time, neural network
+        training is computationally expensive, and takes a long time on a local
+        device. Our fits to \stream{GD-1} and \stream{Pal\,5} presented in this
+        work were performed on a local computer without GPU support, though
+        training time takes on the order of a few hours per stream. This can be
+        improved substantially with the use of GPUs.
+
+        Second, our fits to \stream{GD-1} in \S\ref{sec:results_gd1} rely on a
+        theoretical isochrone. While the stream does appear to be decently
+        characterized by a theoretical isochrone, there is room for improvement.
+        Especially considering that globular clusters do not always follow
+        simple single-stellar population (see, e.g., \citealt{MiloneMarino2022}
+        for a review of this subject), it is worth considering whether more
+        data-driven approaches can be used to model the photometry of a stream
+        without imposing tight priors on the stellar population.
+
+        Third, we have used a combination of analytic distributions and more
+        flexible machine learning methods like normalizing flows to describe the
+        distribution of background stars. However, the field of the Galaxy is
+        complicated, in all coordinates. The analytic distributions in our
+        modeling (specifically the $\phi_2$ background distributions) are
+        clearly approximate. While the analytic distributions might be made more
+        complex, the alternative is to substitute for non-parameteric flexible
+        models. We have postponed this to future work, since the analytic
+        backgrounds provide a decent description in the fields of \stream{GD-1}
+        and \stream{Pal\,5}. However, this might not be the case for other
+        streams. Constructing flexible background models will therefore provide
+        further improvement over our method.
+
+        Fourth, the number density of stars belonging to a stream is determined
+        by several interesting physical processes. These include (e.g.)
+        epicyclic overdensities, the orbital phase of the stream, and
+        interactions with galactic substructure. Our model constrains the
+        stellar number density along any given stream, and can therefore be used
+        to infer the underlying mechanism(s) responsible for the stream’s
+        density. However, all observational surveys are subject to selection
+        effects. In order to determine the nature and reality of a stream’s
+        density fluctuations, selection effects must be accounted for. For the
+        case of \Gaia{}, there is ongoing work to model the survey’s selection
+        function \citep{Cantat-Gaudin+2023}. Our model provides the first step,
+        which is to characterize the observations.  With additional work, the
+        selection function may be incorporated into our model and fits as a
+        prior on the data.  Doing so will enable a more robust analysis of each
+        stream's linear density, allowing us to make more definitive conclusions
+        about its intrinsic structure. We defer this to future work
+
+        Finally, our method is suited for characterizing streams rather than
+        detecting them. Thus, some amount of supervised work is required to
+        reduce the data down to a clean enough selection of stars so that our
+        model can converge to a high likelihood solution. Crucially, the field
+        must contain not only stream stars but also enough background stars to
+        model that component well and distinguish stream from background. As a
+        rule of thumb, it is best if the stream is at least a few percent of the
+        total data, preferably even 10\%. Better background models permit this
+        fraction to be pushed down further.  If the field is too noisy and
+        control points cannot be reliably placed, our method might not be able
+        to characterize the stream of interest.  This also applies to streams
+        with bifurcated features like GD-1's spur component. To model these
+        additional features we must add a separate mixture component. A more
+        data-driven approach to characterize previously unknown or diffuse
+        extensions to a stream would mark a substantial improvement over our
+        current implementation. We leave this to future work.
+
+    \subsection{Comparison to Existing Methods} \label{sub:comparison}
+
+        There are several existing methods for the detection of stellar streams,
+        and some existing work on detailed stream characterization. Here we
+        briefly overview the existing methods, and highlight commonalities and
+        differences between the results of our work and previous studies.
+
+        Currently, the matched filter is the most common method for detecting
+        and characterizing streams (e.g., \citealt{Rockosi+2002, Grillmair2014,
+        Bonaca+2012, Jethwa+2018, Shipp+2018}).  The method works by selecting a
+        stellar population in the CMD (i.e., from a metal-poor isochrone) and
+        searching for a stellar overdensity in the astrometric data. The
+        approach has proved successful for stream detection, but to a lesser
+        extent for characterization. From the matched filter approach alone,
+        stream membership probabilities are not obtained and there is
+        substantial contamination from background stars. While the approach can
+        provide an excellent coarse-grained description of a given stream, it
+        does not provide a density model in astrometry and photometry.
+
+        To a good approximation streams are expected to roughly trace a stellar
+        orbit. The STREAMFINDER algorithm exploits this physical expectation
+        \citep{STREAMFINDER}, by integrating orbits in a trial Galactic
+        potential and identifying stellar overdensities that appear to coincide
+        with segments of the trial orbits. While the method has identified many
+        stream candidates, using these streams for potential reconstruction is
+        circular in reasoning. That is, the detection and characterization of
+        these streams is conditioned on a choice of the potential. The method we
+        present here does not make assumptions about the gravitational
+        potential, nor do we enforce physical assumptions about the dynamics of
+        each stream.
+
+        This work represents one machine learning-based approach for stream
+        characterization. Another method is presented in \citet{Shih+2022}, VIA
+        MACHINAE, which uses conditional density estimation and a linear feature
+        detector to discover streams and identify probable members. While the
+        method is promising for stream discovery, its intended use is not for
+        detailed characterization (as stated in \citealt{Shih+2022}). Our work
+        has the opposite intent: the method presented is not designed to detect
+        streams, rather, it is well-suited for characterizing streams that fall
+        within some predefined field. Thus, our method can be used for
+        characterizing the VIA MACHINAE candidates, and obtaining more robust
+        membership probabilities.
+
+        In \citet{Patrick+2022} the stellar density of 13 tidal streams is
+        modeled in on-sky positions and color-magnitude coordinates. The
+        morphology of each stream is characterized by a series of splines, which
+        are themselves a function of $\phi_1$. This method was originally
+        developed in \citet{Erkal+2017}.  Importantly, \citet{Patrick+2022}
+        performs a fit in $\phi_1-\phi_2$ and photometry, similar to our work.
+        The photometric approach in \citet{Patrick+2022} relies on generating
+        mock stellar populations in the CMD, selecting probable stream stars,
+        modeling the $\phi_1-\phi_2$ distribution for those stars, and then
+        refining the CMD fit based on the $\phi_1-\phi_2$ fit. This approach is
+        therefore similar to a matched filter analysis. The model does not
+        currently incorporate kinematic information, though the work could be
+        extended. The improvement of our work is that we do not require an
+        iterative fit to the CMD and astrometry: we handle both spaces through a
+        joint likelihood without simulating mock-observations. Additionally, we
+        can easily incorporate kinematic information and data with missing
+        phase-space dimensions.
+
+        We also highlight upcoming work from the CATS Collaboration 2023 (in
+        prep.), which provides a spline-based characterization of streams
+        implemented in the \package{Jax} library \citep{jax2018github}. The
+        \package{Jax} backend ensures that fitting the model to a stream is very
+        fast (on the order of minutes), and also has the capability of
+        incorporating kinematic data with missing phase-space dimensions. The
+        method does not currently model the color-magnitude distribution of a
+        stream, but relies on a loose photometric selection. The photometric
+        model in this work could be extended to the spline-based method,
+        allowing for a joint astrometric and photometric model than can be
+        rapidly fit to the stream of interest.
+
+        In total, having multiple methods to characterize streams and their
+        membership probabilities is advantageous. As the volume of tidal
+        features continues to grow, it will become important to fit different
+        models to the same stream, in order to evaluate whether certain features
+        or density variations are real versus spurious artifacts from the
+        adopted method. Considering the information encoded about perturbations
+        in the small-scale density fluctuations along a given stream, a
+        posterior distribution over models will help capture systematic errors
+        in our description of streams and the field of perturbations that give
+        rise to their density.
+
+    % sub: comparison (end)
+
+    \subsection{Combining Information from Present and Future Surveys} \label{sub:future_surveys}
+
+        Streams have been primarily discovered and characterized using
+        photometric searches and matched filter methods (e.g.,
+        \citealt{Rockosi+2002, Grillmair2014, Bonaca+2012, Jethwa+2018,
+        Shipp+2018}).  \Gaia{} has enabled a more precise localization of
+        streams, thanks to their  compact kinematic distribution relative to a
+        field of background stars.  On the other hand, \Gaia{} is not
+        photometrically deep ($G\lesssim 21$) and therefore is less sensitive to
+        diffuse streams in the outer Milky Way halo.  Current and upcoming
+        surveys --- e.g., DES \citep{Abbott+2018, Abbott+2021}, \textit{Euclid}
+        \citep{Laureijs+2011}, Rubin \citep{Ivezic+2019}, \textit{Roman}
+        \citep{Spergel+2013} --- do and will probe much deeper photometrically
+        than \Gaia{} can detect.  From the more distant stellar halo
+        \citep{Shipp+2018} to extragalactic systems
+        \citep{Martinez-Delgado+2008, Demirjian+2020, Roman+2023}, these
+        missions will reveal many new tidal features. Since \Gaia{} cannot be
+        used for these streams, kinematic information will be rare, requiring
+        dedicated followup observations.
+
+        In this work we build mixture models (specifically MDNs) to characterize
+        streams using all of the existing photometric and astrometric data for a
+        given field. Looking to \autoref{fig:gd1-results-full} and
+        \autoref{fig:pal5-results-full}, the proper motion components of the
+        model are among the most information-rich and contribute significantly
+        to the model. What then are the prospects for using this work with
+        streams discovered with data from DES, \textit{Euclid}, Rubin, etc?
+        There are two categories of streams these surveys will observe. The
+        first is streams that partially appear in \Gaia{} but are deeper in
+        these surveys; \stream{Pal\,5} is an example, with its main sequence
+        below the \Gaia{} observation limit. Our method permits missing
+        phase-space dimensions, therefore allowing ``outer''-joined catalogues
+        mixing \Gaia{} and photometrically deeper surveys. In this scenario the
+        stream track in proper motions and parallaxes (and possibly radial
+        velocities) communicate and are mutually constrained with the
+        photometric tracks. The second category is streams entirely missing from
+        \Gaia{}, where the data is on-sky positions ($\phi_1$, $\phi_2$),
+        photometry ($\mbs{m}$), and potentially metallicities. Even in this
+        limited data regime,  our stream characterization framework is
+        applicable. The  normalizing flow background model with a tightly
+        constrained stream isochrone model can be flexibly applied to any
+        stream, allowing for a characterization of the tidal feature insofar as
+        the available data allows.
+
+        The ability to simultaneously model the on-sky and photometric
+        distribution of a stream makes this approach a quantitative and Bayesian
+        form of a matched filter analysis. For this reason, our method is
+        readily applicable to the wealth of data expected from upcoming surveys,
+        including both streams discovered in the Milky Way and extragalactic
+        tidal features. While the present work is concerned with the former
+        case, similar methods to the approach developed here may be applied to
+        extragalactic tidal features, 1000s of which are expected to be
+        discovered with Rubin \citep{Ivezic+2019} and \textit{Roman}
+        \citep{Spergel+2013}. With a density model of an extragalactic tidal
+        feature, the gravitational potential of external galaxies can be
+        constrained (e.g., \citealt{Fardal+2013, Pearson+2022, Nibauer+2023}).
+        We leave an extension of our method to extragalactic streams to future
+        work.
+
+    % sub: future_surveys (end)
+
+\section{Summary and Conclusion} \label{sec:conclusions}
+
+    We have constructed and demonstrated a new method for characterizing stellar
+    streams, given all of the astrometric and photometric data available. We
+    model a stream in astrometric coordinates using mixture density networks,
+    allowing for a flexible representation of diverse stream morphologies under
+    a single modeling framework. Additionally, our astrometric fit does not rely
+    on assumptions about the gravitational potential. Our simultaneous
+    photometric model treats each stream as a single-stellar population,
+    generated from a theoretical isochrone. The distance modulus along the
+    stream is itself a function of $\phi_1$, allowing us to tie photometric
+    information to parallax measurements along the stream. This tie enables a
+    reconstruction of stellar stream distance tracks that are compatible with
+    photometry and astrometry by construction. A joint model in astrometric and
+    photometric coordinates also naturally allows for more spatially diffuse
+    regions of a stream to be detected. Additionally, our background model
+    relies on a combination of analytic densities and normalizing flows, each of
+    which are modular in \package{StreamMapper} and readily adaptable to a given
+    field.
+
+    The combination of a flexible stream and background model allows us to
+    obtain robust stream-membership probabilities for each star in a given
+    field. This enables the generation of statistical samples for stream stars,
+    informed by astrometry and photometry. We apply the method to the stream
+    \stream{GD-1} and the tidal tails of \stream{Palomar 5}, generating
+    membership catalogs for both streams that are publicly available at
+    \href{https://zenodo.org/records/10211410}{zenodo:10211410}. Our
+    characterization of \stream{GD-1} reveals a significant detection of the
+    stream's main component as well as the ``spur" component, which represents a
+    bifurcation from the main stream.  We also recover density variations and
+    gaps along the stream that have been previously observed. Our fit to
+    \stream{Pal\,5} demonstrates the performance of our model on a more diffuse
+    stream with low signal-to-noise measurements.  The inclusion of deeper
+    photometric data for \stream{Pal\,5} will enable a more extended view of the
+    stream.
+
+    Our method represents a new avenue to characterize the growing census of
+    stellar streams discovered in the Milky Way. While most streams have been
+    roughly characterized with matched filter algorithms, a statistical and
+    homogeneous determination of stream-membership probabilities for each star
+    has not been performed or made publicly available. A homogeneous catalog of
+    stellar streams and stellar membership probabilities will therefore
+    represent a substantial step forward for modeling the Galaxy, since both the
+    global track of a stream and its small-scale density distribution are
+    sensitive to the Milky Way's gravitational potential.
+
+    Especially when considering the small-scale perturbation history of a stream
+    predicted by $\Lambda\rm{CDM}$, the inclusion or exclusion of stream stars
+    can make a substantial difference in our inference of the perturbers.
+    Constructing catalogs with membership probabilities as we do in this work
+    provides a crucial step forward to making our inference of, e.g., dark
+    matter subhalos in the Galaxy more robust. Equipped with membership
+    probabilities, one is finally able to propagate the uncertainty in our
+    determination of the ``on-stream data" through to the posterior distribution
+    of model parameters (e.g., those characterizing the subhalo mass function).
+    Thus, our works provides a new technique to generate samples of stream stars
+    using all of the existing kinematic and photometric data, from which models
+    for the Milky Way and its potential can be constrained in a statistically
+    sound manner.
+
+% section comparison_to_other_methods (end)
+
+\newpage
 \section{acknowledgements}
 
-    We would like to thank the Academy.
-
-    \url{https://github.com/nstarman/stellar_stream_density_ml_paper/}
-
+    NS acknowledges support from the Natural Sciences and Engineering Research
+    Council of Canada (NSERC) - Canadian Graduate Scholarships Doctorate Program
+    [funding reference number 547219 - 2020].  NS received partial support from
+    NSERC (funding reference number RGPIN-2020-04712) and from an Ontario Early
+    Researcher Award (ER16-12-061; PI Bovy).
+
+    JN is supported by a National Science Foundation Graduate Research
+    Fellowship, Grant No. DGE-2039656. Any opinions, findings, and conclusions
+    or recommendations expressed in this material are those of the author(s) and
+    do not necessarily reflect the views of the National Science Foundation.
+
+    Both NS and JN would like to thank the
+    \href{https://stellarstreams.org/streams22/}{Community Atlas of Tidal
+    Streams 2022} conference for starting the discussions that led to this work.
+    We thank Joshua Speagle for conversations and suggestions that were crucial
+    to the development of the photometric model. We also thank Shirley Ho and
+    Miles Cranmer for insightful discussions and comments.
+
+    This work has made use of data from the European Space Agency (ESA) mission
+    \Gaia{} (\url{https://www.cosmos.esa.int/gaia}), processed by the \Gaia{}
+    Data Processing and Analysis Consortium (DPAC,
+    \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the
+    DPAC has been provided by national institutions, in particular the
+    institutions participating in the \Gaia{} Multilateral Agreement.
+
+    The data availability statement is modified from one provided to
+    ShowYourWork by Mathieu Renzo.
+
+    \paragraph{Software (alphabetical)}
+
+        \package{asdf} \citep{Greenfield+2015}, %
+        \package{astropy} \citep{Astropy2013, Astropy2018, Astropy2022}, %
+        \package{astroquery} \citep{Astroquery2019}, %
+        \package{brutus} \citep{brutus}, %
+        \package{Matplotlib} \citep{Hunter2007}, %
+        \package{NumPy} \citep{Harris+2020}, %
+        \package{Pytorch} \citep{Pytorch2019}, %
+        \package{SciPy} \citep{Scipy2020}, %
+        \package{ShowYourWork} \citep{Luger+2021}, %
+        \package{zuko} \citep{zuko}. %
+
+\newpage
+\section*{Data Availability} \label{sec:data_availability}
+
+    This study was carried out using the reproducibility software
+    \href{https://github.com/showyourwork/showyourwork}{\showyourwork}
+    \citep{Luger+2021}, which uses continuous integration to programmatically
+    download the data, perform the analyses, create the figures, and compile the
+    manuscript. Each figure caption contains two links: one to the dataset used
+    in the corresponding figure, and the other to the script used to make the
+    figure. The datasets are stored at
+    \href{https://zenodo.org/records/10211410}{zenodo:10211410}. The git
+    repository associated with this study is publicly available at
+    \href{https://github.com/nstarman/stellar_stream_density_ml_paper}{nstarman/stellar\_stream\_density\_ml\_paper}.
+    The open-source code base developed for this project is
+    \href{https://github.com/GalOrrery/stream_mapper-pytorch}{\package{StreamMapper}}.
+
+% section data_availability (end)
+
+\newpage
 \bibliography{bib}
@@
 
-\section{Notation} \label{app:notation}
-
-    \begin{itemize}
-        \item Full Data
-            \begin{itemize}
-                \item $\mbf{D} \in \mbb{R}^{(N, F^{(d)})}$ is the data matrix
-                \item indexed with index sets $\mrm{n} \in \mbs{I_N} \equiv \{0, ..., N\} \in \mbb{Z^+}$ for the measurements and $\mrm{f} \in \mbs{I_F}  \equiv \{0, ..., F^{(d)}\} \in \mbb{Z^+}$ for the features.
-                \item $d_{\mrm{nf}}$ elements of the $n$-th measurement of the $f$-th feature.
-                \item $\nth{\mbs{d}}$ row-vector of all features.
-                \item  $\mbf{D}$ is split into astrometric and photometric coordinates $\mbf{D} = \{\mbf{W}, \mbf{M}\}$, in that order of features.
-$F^{(w)} + F^{(m)} = F$, where $F^{(w)}, F^{(m)}$ are defined below.
-            \end{itemize}
-        \item Astrometric Data
-            \begin{itemize}
-                \item $\mbf{W} \in \mathbb{R}^{(N, F^{(w)})}$ is the astrometric data matrix
-                \item indexed with index the same $N$ as the full data and $\mrm{f} \in \mbs{I_{F^{(w)}}} \equiv \{0, ..., F^{(w)}\} \in \mathbb{Z^+}$ for the astrometric features, where $F^{(w)} \leq F$.
-                \item $w_{\mrm{nf}}$ elements of the $n$-th measurement of the $f$-th astrometric feature.
-                \item $\nth{\mbs{w}}$ row-vector of all astrometric features.
-                \item The first (index 0) feature column, $w_{\cdot,0}$ of $\mbf{W}$ (and $\mbf{D}$) is $\phi_1$.
-            \end{itemize}
-        \item Photometric Data
-            \begin{itemize}
-                \item $\mbf{M} \in \mathbb{R}^{(N, F^{(m)})}$ is the photometric data matrix
-                \item indexed with index the same $N$ as the full data and $\mrm{f} \in \mbs{I_{F^{(m)}}} \equiv \{0, ..., F^{(m)}\} \in \mathbb{Z^+}$ for the photometric features, where $F^{(m)} \leq F$.
-                \item $m_{\mrm{nf}}$ elements of the $n$-th measurement of the $f$-th photometric feature.
-                \item $\nth{\mbs{m}}$ row-vector of all photometric features.
-            \end{itemize}
-        \item Mixture Models
-            \begin{itemize}
-                \item index set over the models: $\mrm{q} \in \mbs{I_Q} \equiv \{0, ..., Q \} \in \mbb{Z^+}$ 
-            \end{itemize}
-        \item $\pdf(...)$ is a PDF and $\cdf(...)$ it's CDF.
-        % \item $\pi(...)$ is a prior
-        \item $\mcal{L}$ is a likelihood.
-    \end{itemize}
-
-\section{Theory of Mixture Density Networks (MDNs} \label{app:theory_of_mixture_density_networks}
-
-    Mixture Density Networks (MDNs) are a generalization over mixture models, where the weights and model parameters may be functions, rather than scalars, as in normal mixture models.
-Generalizing to functional parameters allows the model to capture variation over those parameters that is not possible with scalar-valued models.
-
-    For the MDN we take $d_{\cdot, 0} \equiv x_{\cdot}$ (indexed from 0), which is the first feature column of $\mbf{D}$, as the `independent' coordinate over which the MDN parameters are functions.
-In the context of streams $d_{\cdot, 0} = x$ is $\phi_1$ the longitude coordinate in a reference frame rotated such that the stream is aligned along $\phi_1$.
-
-    The PDF of the MDN is
-
-    \begin{equation} \label{eq:general_mixture_network}
-        \pdf(\nth{\mbs{d}} | \mbs{\theta}(\nth{x}))
-        = \sum_{\mrm{q} \in \mbs{I_Q}} \ \qth{f}(\nth{x}) \qth{P}(\nth{d}|\qth{\mbs{\theta}}(\nth{x}),q\!=\!\mrm{q})
-    \end{equation}
-    The mixture weights $\qth{f}$ are normalized s.t.
-
-    \begin{equation}
-        \sum_{\mrm{q}} \qth{f}(\nth{x}) = 1 \qquad \forall \nth{x}
-    \end{equation}
-    In practice this is enforced by defining
-    \begin{equation}
-        f_{\mrm{q} = b}(\nth{x}) = 1 - \sum_{\rm{q}\in \mbs{I_Q}\backslash b} \qth{f}(\nth{x})
-    \end{equation}
-    for some ``background" index $b \in \mbs{I_Q}$.
-
-    Assuming the measurement of each datum is independent, the total log-likelihood is a sum over all data:
-    \begin{equation}
-        \ln\mcal{L}\left(\mbf{D} | \mbs{\theta}(\mbs{x})\right) = \sum_{n \in \mbs{I_N}} \ln \left[ \sum_{q\in\mbs{I_Q}} \qth{P}\left(\nth{\mbs{d}} | \qth{\mbs{\theta}}(x_n)\right) \right].
-    \end{equation}
-
-    The full posterior distribution includes the priors.
-
-    \todo[inline]{TODO}
-
 \section{Probability Distributions} \label{app:distributions}
 
-    A variety of probability distributions are used when modeling the stream and Galactic background. This appendix presents relevant mathematical details of these distributions.
-    In particular, observational errors are modeled as Gaussian distributions, which requires modifying each distribution to account for the Gaussian noise.
+    A variety of probability distributions are used when modeling the stream and
+    Galactic background. This appendix presents relevant mathematical details of
+    these distributions.  In particular, observational errors are modeled as
+    Gaussian distributions, which requires modifying each distribution to
+    account for the Gaussian noise.
 
@@
 
-    Let $x \sim X$ be distributed as some specified distribution
-    and $\delta \sim \Delta \equiv \mcal{N}(0, \sigma_*)$ as an independent, centered Gaussian.
-    An observation $Y$ is distributed as
+    Let $x \sim X$ be distributed as some specified distribution and $\delta
+    \sim \Delta \equiv \mcal{N}(0, \sigma_*)$ as an independent, centered
+    Gaussian.  An observation $Y$ is distributed as
     \begin{equation}
@@
 
-    In the following subsections we work through the distributions $\pdf(x,\mbs{\theta})$ and the convolutions with $\mcal{N}(x,0,\sigobs)$.
+    In the following subsections we work through the distributions
+    $\pdf(x,\mbs{\theta})$ and the convolutions with $\mcal{N}(x,0,\sigobs)$.
 
@@
 
-        The simplest distribution is that of the univariate uniform distribution.
-        For a domain $x \in [a, b]$ the PDF is given by
-        \begin{equation}\label{eq:pdf_flat_univariate}
+        The simplest distribution is that of the univariate uniform
+        distribution.  For a domain $x \in [a, b]$ the PDF is given by
+        \begin{equation} \label{eq:pdf_flat_univariate}
             P_{\mcal{U}}(x|a,b) = \begin{cases}
@@
 
-        In practice, the bounds $a,b$ are the bounds of the observation window, creating a subset of a larger field.
-        Suppose the larger field is uniformly distributed in a region larger than the bounds $a, b$, ie. $P_{\mcal{U}}(x|\alpha,\beta)$.
-        Let each observed datum $x_n$ in the field have Gaussian error $\sigobs_n$,
-        then the PDF of the uniform-Gaussian-convolved distribution is given by:
-
-        \begin{equation}
+        In practice, the bounds $a,b$ are the bounds of the observation window,
+        creating a subset of a larger field.  Suppose the larger field is
+        uniformly distributed in a region larger than the bounds $a, b$, ie.
+        $P_{\mcal{U}}(x|\alpha,\beta)$.  Let each observed datum $x_n$ in the
+        field have Gaussian error $\sigobs_n$, then the PDF of the
+        uniform-Gaussian-convolved distribution is given by:
+
+        \begin{equation} \label{eq:flat_distribution}
             \pdf_{(\mcal{U}*\mcal{N})}(x; \alpha, \beta, \sigobs) = \begin{cases}
@@
         \end{equation}
-        in the normal fashion: setting $\pdf_{(\mcal{U}*\mcal{N})} = 0$ when $x < a, x > b$ and normalizing $\pdf_{(\mcal{U}*\mcal{N})}$ within $(a,b]$.
-The truncated distribution is tractable but unwieldy.
-The distribution can be simplified enormously if two conditions hold: first, $\alpha \ll a, b \ll \beta$, the observed field is a small subset of the full field; and second,
-        $\sigobs \ll |\alpha - a|$ and $\sigobs \ll |\beta - b|$, the errors are smaller than the observation window size compared to the full field.
-        In this case, the distribution reduces back to the uniform distribution!
-
-        Therefore, for all cases considered in this work \eqref{eq:pdf_flat_univariate_convolved_error_full} becomes:
+        in the normal fashion: setting $\pdf_{(\mcal{U}*\mcal{N})} = 0$ when $x
+        < a, x > b$ and normalizing $\pdf_{(\mcal{U}*\mcal{N})}$ within $(a,b]$.
+        The truncated distribution is tractable but unwieldy. The distribution
+        can be simplified enormously if two conditions hold: first, $\alpha \ll
+        a, b \ll \beta$, the observed field is a small subset of the full field;
+        and second, $\sigobs \ll |\alpha - a|$ and $\sigobs \ll |\beta - b|$,
+        the errors are smaller than the observation window size compared to the
+        full field.  In this case, the distribution reduces back to the uniform
+        distribution!
+
+        Therefore, for all cases considered in this work
+        \eqref{eq:pdf_flat_univariate_convolved_error_full} becomes:
 
@@
     \vspace{10pt}
-    \subsection{Truncated Exponential Distribution} \label{sub:exponential_distribution}
+    \subsection{Truncated Exponential Distribution} \label{app:sub:exponential_distribution}
 
@@
 
-        The support of this distribution, $[0, \infty)$, rarely matches the support of the data.
-We generalize to the unit-normalized, truncated, univariate exponential distribution in the domain $(a, b]$:
+        The support of this distribution, $[0, \infty)$, rarely matches the
+        support of the data. We generalize to the unit-normalized, truncated,
+        univariate exponential distribution in the domain $(a, b]$:
         \begin{equation} \label{eq:pdf_truncexp_univariate}
@@
         \end{equation}
-        for bounds $x \in (a,b]$.
-However, as $\lambda \rightarrow 0$, which describes the flat distribution (\autoref{sub:flat_distribution}), this functional form can be numerically unstable.
-It is therefore practical to define $\pdf_{\mcal{E}}(x; |\lambda| < \epsilon, a, b) \cong P_{\mcal{U}}(x; a,b)$.
-
-        Let each observed datum $x_n$ in the field have Gaussian error $\sigobs_n$,
-        then the PDF of the Exponential-convolved-with-a-Gaussian distribution is given by:
+        for bounds $x \in (a,b]$. However, as $\lambda \rightarrow 0$, which
+        describes the flat distribution (\autoref{sub:flat_distribution}), this
+        functional form can be numerically unstable. It is therefore practical
+        to define $\pdf_{\mcal{E}}(x; |\lambda| < \epsilon, a, b) \cong
+        P_{\mcal{U}}(x; a,b)$.
+
+        Let each observed datum $x_n$ in the field have Gaussian error
+        $\sigobs_n$, then the PDF of the Exponential-convolved-with-a-Gaussian
+        distribution is given by:
 
@@
         \end{equation}
-        where the function is no longer truncated, since a Gaussian is not compact.
-
-        We impose the same observation field $(a, b]$ and truncate $\pdf_{\mcal{E}\cdot\mcal{N}}(x | a < X \leq b;m,a,\sigma_*)$.
-        We note the normalization, which is the CDF evaluated at $a, b$, cancels the factor
-        $\Exp{\frac{1}{2}\lambda^2 \sigma_*^2}$. Following thtough, the truncated convolved distribution is identical to the original distribution.
+        where the function is no longer truncated, since a Gaussian is not
+        compact.
+
+        We impose the same observation field $(a, b]$ and truncate
+        $\pdf_{\mcal{E}\cdot\mcal{N}}(x | a < X \leq b;m,a,\sigma_*)$.  We note
+        the normalization, which is the CDF evaluated at $a, b$, cancels the
+        factor $\Exp{\frac{1}{2}\lambda^2 \sigma_*^2}$. Following thtough, the
+        truncated convolved distribution is identical to the original
+        distribution.
 
@@
     \vspace{10pt}
-    \subsection{Normal Distribution}
-
-        The properties of the Normal distribution are well known. For completeness we state
+    \subsection{Normal Distribution} \label{app:sub:normal_distribution}
+
+        The properties of the Normal distribution are well known. For
+        completeness we state
 
         \begin{equation}
-            P_X(x; \mu, \sigma) = \mcal{N}(\mu, \sigma).
+            P_X(x; \mu, \sigma) = \mcal{N}(x; \mu, \sigma).
         \end{equation}
@@
         \begin{equation}
-            P_{\mcal{N}\cdot\mcal{N}}(x; \mu, \sigma, \sigobs) = \mcal{N}(\mu, \sqrt{\sigma^2 + \sigobs^2}).
+            P_{\mcal{N}\cdot\mcal{N}}(x; \mu, \sigma, \sigobs) = \mcal{N}(x; \mu, \sqrt{\sigma^2 + \sigobs^2}).
         \end{equation}
 
-        The Normal distribution is not compact, with non-zero value over all $x$. In an observational window $(a,b]$ the PDF is truncated, giving
+        The Normal distribution is not compact, with non-zero value over all
+        $x$. In an observational window $(a,b]$ the PDF is truncated, giving
 
@@
             P_{\mcal{N}_T}(x; \mu, \sigma, a, b) = \begin{cases}
-                \frac{\mcal{N}(x, \mu, \sigma)}{\Phi_\mcal{N}(b; \mu, \sigma) - \Phi_\mcal{N}(a; \mu, \sigma)} & a < x \leq b \\
+                \frac{\mcal{N}(x; \mu, \sigma)}{\Phi_\mcal{N}(b; \mu, \sigma) - \Phi_\mcal{N}(a; \mu, \sigma)} & a < x \leq b \\
                 0 & \text{else}
@@
 
-        Note that the observation-window-truncation is performed on the full distribution, which includes the observational errors, if present.
+        Note that the observation-window-truncation is performed on the full
+        distribution, which includes the observational errors, if present.
         Therefore, let $\tilde{\sigma}^2 \equiv \sigma^2+\sigma_*^2$
@@
 
-    \vspace{10pt}
-    \subsection{Skew-Normal Distribution}
-
-        The PDF of the skew-normal distribution is given by
-
-        \begin{equation}
-            \pdf_{SN}(x;\mu,\sigma,\alpha) = 2\pdf_{\mcal{N}}(x;\mu,\sigma)\cdf_{\mcal{N}}(\alpha x;\mu,\sigma).
-        \end{equation}
-
-        Despite the popularity of this distribution we are not aware of any work showing the convolution of the skew-normal distribution with a centered Gaussian.
-Moreover, our Mathematica (v13.2) does not successfully perform this convolution.
-Consequently we present a step-by-step derivation of $P_{X\cdot\mcal{N}}$.
-
-        \autoref{eq:general_convolution} establishes that convolutions of PDFs are an integral operation.
-Integrals are often challenging and it is useful to recast a problem in different terms.
-Rather that working with PDFs of distributions we can instead consider the moment-generating function (MGF) corresponding to the PDF's distribution.
-Like the PDF, the MGF uniquely determines a distribution, so a MFG uniquely maps to a PDF.
-Also,
-        for the MGF of two distributions the convolutions is a multiplication, not an integral.
-        Therefore, for the convolution of two PDFs their MGFs are multiplied and if the product is the MGF of a known distribution, the corresponding PDF is the convolution of the two original PDFs.
-
-        The MGF of the Normal distribution is
-
-        \begin{equation} \label{eq:mgf_normal}
-            M_{\mcal{N}}(t) = \Exp{\frac{\sigma_*^2 t^2}{2}}
-        \end{equation}
-
-        And the MGF of the skew-normal is
-
-        \begin{equation} \label{eq:mgf_skewnormal}
-            M_{S\mcal{N}}(t) = 2 * \Exp{\mu t + \frac{\sigma^2 t^2}{2}} \cdf(\sigma \delta t), \quad \delta = \frac{\alpha}{\sqrt{1 + \alpha^2}}.
-        \end{equation}
-
-        The product of the two MGF is
-
-        \begin{equation}
-            M_{S\mcal{N}*\mcal{N}}(t) = M_{S\mcal{N}}(t) * M_{\mcal{N}}(t) = 2 * \Exp{\mu t + \frac{(\sigma^2 + \sigma_*^2) t^2}{2}} \cdf(\sigma \delta t).
-        \end{equation}
-        We rewrite $\tilde\sigma^2 = \sigma^2 + \sigma_*^2$, and $\tilde{\sigma} \tilde{\delta} = \sigma \delta$.
-
-        \begin{equation}
-            M_{S\mcal{N}*\mcal{N}}(t) = 2 * \Exp{\mu t + \frac{\tilde{\sigma}^2 t^2}{2}} \cdf_{\mcal{N}}(\tilde{\sigma} \tilde{\delta} t)
-        \end{equation}
-        This has the same form as the skew-normal, only with $\sigma \rightarrow \tilde\sigma$ and $\delta \rightarrow \tilde\delta$.
-
-        Therefore the PDF of the convolved distribution is
-
-        \begin{equation}
-            \pdf_{S\mcal{N}\cdot\mcal{N}}(x;\mu,\sigma,\alpha) = 2\pdf_{\mcal{N}}(x;\mu,\tilde{\sigma})\cdf_{\mcal{N}}(\tilde{\alpha} x;\mu,\tilde{\sigma})
-        \end{equation}
-        where $\tilde\sigma^2 = \sigma^2 + \sigma_*^2$ and $\tilde{\alpha} = \frac{\tilde{\delta}}{\sqrt{1-\tilde{\delta}^2}}$, $\tilde{\delta} = \frac{\sigma}{\tilde{\sigma}}\delta$.
-
-        The truncation of this distribution to the range $(a, b]$ is
-
-       \begin{equation}
-            \pdf_{S\mcal{N}_T}(x; \mu, \sigma, \alpha, a, b)
-                = \begin{cases}
-                    \frac{\pdf_{S\mcal{N}}(x; \mu, \tilde\sigma, \tilde\alpha)}{\cdf_{S\mcal{N}}(b; \mu, \tilde\sigma, \tilde\alpha) - \cdf_{S\mcal{N}}(a; \mu, \tilde\sigma, \tilde\alpha)} & a < x \leq b \\
-                    0 & \text{else}
-                \end{cases}
-        \end{equation}
-        where
-        \begin{equation}
-            \cdf_{S\mcal{N}}(x; \mu, \sigma) = \frac{1}{2} \text{erfc}\left(\frac{\mu -x}{\sqrt{2} \sigma }\right)-2 T\left(\frac{x-\mu }{\sigma },\alpha \right)
-        \end{equation}
-        where $T$ is Owen's T distribution.
-
-\section{Plots} \label{app:developing_plots}
-
-    \begin{figure*}
-        \centering
-        \includegraphics[scale=0.7]{figures-not-syw/gd1/tot_stream_and_spur_prob.png}
-        \caption{Caption}
-        \label{fig:gd1-astrometrics}
-    \end{figure*}
-
-    \begin{figure*}
-        \centering
-        \includegraphics[scale=0.8]{figures-not-syw/gd1/Unknown.png}
-        \caption{Caption}
-        \label{fig:gd1-distance_modulus}
-    \end{figure*}
-
-    \begin{figure}
-        \centering
-        \includegraphics[scale=0.6]{figures-not-syw/gd1/Unknown-2.png}
-        \caption{Caption}
-        \label{fig:gd1-cmd}
-    \end{figure}
-
-    \begin{figure*}
-        \centering
-        \includegraphics[scale=0.6]{figures-not-syw/gd1/Unknown-4.png}
-        \caption{Caption}
-        \label{fig:gd1-cmds}
-    \end{figure*}
+\newpage
+\section{Pairing Neural Networks with Priors} \label{app:nns_and_priors}
+
+    In modeling, the choices of priors are important, not only for the
+    information they adds to a model, but also for how optimizers explore
+    parameter spaces. Simple optimizers, like MCMC, propose a parameter vector
+    then compute its likelihood given the data \citep{HoggForeman-Mackey2018}.
+    Priors with compact support  $\theta \sim \mcal{D}((a, b])$, e.g.
+    $\mcal{U}(a, b)$, may be very dangerous as the optimizer can be initialized
+    in a region with zero probability and has no means but blind luck to find
+    the region of support -- the region with non-zero likelihood. More
+    sophisticated optimizers, like gradient-based descent \citep{cauchy_2009},
+    are susceptible to a similar initialization problem, allowing
+    zero-probability regions, but requiring at least a non-zero gradient to make
+    informed updates to the optimizers state.  Outside the support the gradient
+    can be zero.  With MDNs, model parameters are neural network outputs. Unlike
+    for conventional models where an informed initial parameter state may be
+    chosen by hand, it is impractical and undesirable to initialize by hand a
+    neural network's output by setting all its internal weights. One might
+    imagine accomplishing a desired initial output by pre-training the network
+    with a toy model that forces convergence on a set output vector.  However,
+    neural networks are highly non-linear in their response to internal state
+    changes (a desirable property). It is quite possible that when switching
+    from the toy to real model's loss function the pre-trained network is in a
+    local probability island from which the global optimum is unreachable.  
+    Therefore, with the MDN neural networks, initialization is mostly
+    for checking the dependence of the results on the initial state --
+    though even this dependence may instead be done using parameter
+    dropout. Rather than focusing on initializing to a particular
+    parameter vector, for neural networks it is instead important that
+    the initial state, whatever it is, has non-zero probability (or
+    non-zero gradient, depending on the optimizer).  Neural networks
+    have some intrinsic phase-space range that depends on the
+    architecture of the network. Therefore the network architecture must
+    be chosen such that the outputs match well with the priors. For
+    example, with a uniform prior $\theta \sim \mcal{U}(a,b)$, the
+    network should be restricted such that $\theta \in (a, b]$, e.g. by
+    ending the network's $\theta$ channel with a scaled logistic
+    function.
 

### 2023-07-11 src/scripts/__init__.py

@@ -1,0 +1,3 @@
+"""Scripts."""
+
+from .mpl_colormaps import *  # noqa: F403

### 2023-07-11 src/scripts/brutus/download_mist_file.py

@@ -1,0 +1,36 @@
+"""Download MIST files for brutus."""
+
+import shutil
+import sys
+from typing import Any
+
+import brutus.utils
+from showyourwork.paths import user as user_paths
+
+paths = user_paths()
+
+##############################################################################
+
+snkmk: dict[str, Any]
+try:
+    snkmk = dict(snakemake.params)
+except NameError:
+    snkmk = {"load_from_static": True, "save_to_static": False}
+
+
+if snkmk["load_from_static"] and (paths.static / "brutus").exists():
+    shutil.copyfile(
+        paths.static / "brutus" / "MIST_1.2_iso_vvcrit0.0.h5",
+        paths.data / "brutus" / "MIST_1.2_iso_vvcrit0.0.h5",
+        follow_symlinks=True,
+    )
+    sys.exit(0)
+
+brutus.utils.fetch_isos(target_dir=paths.data / "brutus", iso="MIST_1.2_vvcrit0.0")
+
+if snkmk["save_to_static"]:
+    shutil.copyfile(
+        paths.data / "brutus" / "MIST_1.2_iso_vvcrit0.0.h5",
+        paths.static / "brutus" / "MIST_1.2_iso_vvcrit0.0.h5",
+        follow_symlinks=True,
+    )

### 2023-07-11 src/scripts/brutus/download_nn_file.py

@@ -1,0 +1,37 @@
+"""Download Nerual Network files for brutus."""
+
+import shutil
+import sys
+from typing import Any
+
+import brutus.utils
+from showyourwork.paths import user as user_paths
+
+paths = user_paths()
+
+##############################################################################
+
+snkmk: dict[str, Any]
+try:
+    snkmk = dict(snakemake.params)
+except NameError:
+    snkmk = {"load_from_static": True, "save_to_static": False}
+
+
+if snkmk["load_from_static"] and (paths.static / "brutus").exists():
+    shutil.copyfile(
+        paths.static / "brutus" / "nn_c3k.h5",
+        paths.data / "brutus" / "nn_c3k.h5",
+        follow_symlinks=True,
+    )
+    sys.exit(0)
+
+
+brutus.utils.fetch_nns(target_dir=paths.data / "brutus", model="c3k")
+
+if snkmk["save_to_static"]:
+    shutil.copyfile(
+        paths.data / "brutus" / "nn_c3k.h5",
+        paths.static / "brutus" / "nn_c3k.h5",
+        follow_symlinks=True,
+    )

### 2023-07-11 src/scripts/dustmaps/download_dustmaps.py

@@ -1,0 +1,42 @@
+"""Download dust maps."""
+
+import shutil
+from typing import Any
+
+import dustmaps.bayestar
+import dustmaps.config
+from showyourwork.paths import user as user_paths
+
+paths = user_paths()
+
+##############################################################################
+# Parameters
+
+snkmk: dict[str, Any]
+try:
+    snkmk = dict(snakemake.params)
+except NameError:
+    snkmk = {"load_from_static": True, "save_to_static": False}
+
+
+##############################################################################
+
+
+DUSTMAPS_DIR = paths.data / "dustmaps"
+DUSTMAPS_DIR.mkdir(exist_ok=True)
+
+dustmaps.config.config["data_dir"] = DUSTMAPS_DIR.as_posix()
+
+if snkmk["load_from_static"] and (paths.static / "dustmaps").exists():
+    shutil.copyfile(
+        paths.static / "dustmaps" / "bayestar2019.h5",
+        DUSTMAPS_DIR / "bayestar" / "bayestar2019.h5",
+    )
+else:
+    dustmaps.bayestar.fetch(version="bayestar2019")
+
+if snkmk["save_to_static"]:
+    shutil.copyfile(
+        DUSTMAPS_DIR / "bayestar" / "bayestar2019.h5",
+        paths.static / "dustmaps" / "bayestar2019.h5",
+    )

### 2023-07-11 src/scripts/dustmaps/ps1_corrections.py

@@ -1,0 +1,20 @@
+"""Save file of PS-1 exctinction coefficients."""
+
+import json
+
+from showyourwork.paths import user as user_paths
+
+paths = user_paths()
+
+# From Table 1 of Green et al. (2019)
+# https://arxiv.org/pdf/1905.02734.pdf
+factors = {
+    "g": 3.158,
+    "r": 2.617,
+    "i": 1.971,
+    "z": 1.549,
+    "y": 1.263,
+}
+
+with (paths.data / "dustmaps" / "ps1_corrections.json").open(mode="w") as f:
+    json.dump(factors, f)

### 2023-07-11 src/scripts/gd1/data/1-query_data.py

@@ -1,0 +1,243 @@
+"""Query data from Gaia, crossmatched with PS-1."""
+
+import shutil
+import sys
+from itertools import combinations, pairwise
+from pathlib import Path
+from typing import Any
+
+import asdf
+import astropy.coordinates as coords
+import astropy.units as u
+import matplotlib.pyplot as plt
+import numpy as np
+from astroquery.gaia import Gaia
+from astroquery.utils.tap.model.job import Job
+from showyourwork.paths import user as user_paths
+from tqdm import tqdm
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+from scripts.gd1.frames import gd1_frame as frame
+from scripts.helper import a_as_b
+
+##############################################################################
+# Parameters
+
+SAVE_LOC = paths.data / "gd1" / "gaia_ps1_xm_polygons.asdf"
+
+snkmk: dict[str, Any]
+try:
+    snkmk = dict(snakemake.params)
+except NameError:
+    snkmk = {"load_from_static": True, "save_to_static": True}
+
+
+if snkmk["load_from_static"] and (paths.static / "gd1").exists():
+    shutil.copyfile(paths.static / "gd1" / "gaia_ps1_xm_polygons.asdf", SAVE_LOC)
+    sys.exit(0)
+else:
+    GAIA_LOGIN = Path(paths.static / "gaia.login").expanduser()
+    Gaia.login(credentials_file=GAIA_LOGIN, verbose=False)
+
+Gaia.ROW_LIMIT = -1  # no limit
+
+##############################################################################
+
+
+PHI1_EDGES = (
+    np.concatenate((np.arange(-100, -80, 2), np.arange(-80, 30 + 5, 5))) * u.deg
+)
+PHI2_BOUNDS = (-9, 5) * u.deg
+PLX_BOUNDS = (-10, 1.0) * u.milliarcsecond
+BP_RP_BOUNDS = (-1, 3) * u.mag
+GMAG_BOUNDS = (0, 30) * u.mag
+IMAG_BOUNDS = (0, 30) * u.mag
+
+
+gaia_cols = {
+    "source_id": None,
+    # Astrometry
[…]

### 2023-07-11 src/scripts/gd1/data/2-combine_data.py

@@ -1,0 +1,208 @@
+"""Combine GD-1's data fields into one dataset."""
+
+import contextlib
+import json
+import shutil
+import sys
+from typing import Any
+
+import asdf
+import astropy.units as u
+import dustmaps.bayestar
+import gala.coordinates as gc
+import numpy as np
+from astropy.coordinates import ICRS, Distance, SkyCoord
+from astropy.table import QTable, vstack
+from showyourwork.paths import user as user_paths
+from zero_point import zpt
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+from scripts.gd1.frames import gd1_frame as frame
+
+##############################################################################
+# Parameters
+
+SAVE_LOC = paths.data / "gd1" / "gaia_ps1_xm.asdf"
+
+snkmk: dict[str, Any]
+try:
+    snkmk = dict(snakemake.params)
+except NameError:
+    snkmk = {"load_from_static": True, "save_to_static": False}
+
+
+##############################################################################
+
+if snkmk["load_from_static"] and (paths.static / "gd1").exists():
+    shutil.copyfile(paths.static / "gd1" / "gaia_ps1_xm.asdf", SAVE_LOC)
+    sys.exit(0)
+
+# -----------------------------------------------------------------------------
+# Initial combination
+
+af = asdf.open(paths.data / "gd1" / "gaia_ps1_xm_polygons.asdf", mode="r")
+
+combined = vstack(af.search("polygon-*").nodes, metadata_conflicts="silent")
+
+# correct metadata
+combined.meta.pop("query")
+combined.meta["frame"] = f"{frame.__class__.__module__}.{frame.__class__.__name__}"
+
+# correct unit and data types
+combined["ps1_g"].unit = u.mag
+
+combined.write(SAVE_LOC, format="asdf")
+
+del combined
+af.close()
+
+# -----------------------------------------------------------------------------
+
+table = QTable.read(SAVE_LOC)
+
+# ---------------------------------------
[…]

### 2023-07-11 src/scripts/gd1/data/2.5-variable_ndata.py

@@ -1,0 +1,12 @@
+"""Save the number of stars in the GD-1 stream."""
+
+
+from astropy.table import QTable
+from showyourwork.paths import user as user_paths
+
+paths = user_paths()
+
+table = QTable.read(paths.data / "gd1" / "gaia_ps1_xm.asdf")
+
+with (paths.output / "gd1" / "ndata_variable.txt").open("w") as f:
+    f.write(f"{len(table):,}")

### 2023-07-11 src/scripts/gd1/data/3-phot_edges.py

@@ -1,0 +1,54 @@
+"""Define the photometric data mask boundaries for GD-1."""
+
+from dataclasses import asdict
+
+import asdf
+import astropy.units as u
+import brutus.filters
+import brutus.seds
+import numpy as np
+import shapely
+from astropy.coordinates import Distance
+from showyourwork.paths import user as user_paths
+
+import stream_mapper.pytorch as sml
+
+paths = user_paths()
+
+##############################################################################
+
+filters = brutus.filters.ps[:-2]  # (g, r)
+
+# Build isochrone
+abs_mags, _, _ = brutus.seds.Isochrone(
+    filters=filters,
+    nnfile=(paths.data / "brutus" / "nn_c3k.h5").resolve(),
+    mistfile=(paths.data / "brutus" / "MIST_1.2_iso_vvcrit0.0.h5").resolve(),
+).get_seds(
+    eep=np.linspace(202, 600, 5000),
+    apply_corr=True,
+    feh=-1.2,
+    # feh=-1.35,
+    # dist=7.8e3,
+    dist=10,
+    loga=np.log10(12e9),
+)
+abs_mags = abs_mags[np.all(np.isfinite(abs_mags), axis=1)]
+mags_data = sml.Data(abs_mags, names=[n.removeprefix("PS_") for n in filters])
+
+app_mags = abs_mags + Distance(7.8 * u.kpc).distmod.value
+isochrone = shapely.LineString(np.c_[app_mags[:, 0] - app_mags[:, 2], app_mags[:, 0]])
+# iso_tight = isochrone.buffer(0.1)
+iso_medium = isochrone.buffer(0.3)
+# iso_loose = isochrone.buffer(0.5)
+
+
+af = asdf.AsdfFile()
+af["isochrone_data"] = asdict(mags_data)
+af["isochrone_data"].pop("_n2k")
+# Masks
+af["isochrone_"] = np.c_[isochrone.xy]
+af["isochrone_medium"] = np.c_[iso_medium.exterior.xy]
+
+af.write_to(paths.data / "gd1" / "isochrone.asdf")
+af.close()

### 2023-07-11 src/scripts/gd1/data/3-pm_edges.py

@@ -1,0 +1,39 @@
+"""Define the proper motion data mask boundaries for GD-1."""
+
+import sys
+
+import astropy.units as u
+import galstreams
+from astropy.table import QTable
+from showyourwork.paths import user as user_paths
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+from scripts.gd1.frames import gd1_frame
+from scripts.helper import make_vertices
+
+##############################################################################
+
+mws = galstreams.MWStreams()
+gd1 = mws["GD-1-I21"]
+gd1_sc = gd1.track.transform_to(gd1_frame)[::100]
+
+
+path_pmphi1_tight = make_vertices(gd1_sc.phi1.degree, gd1_sc.pm_phi1_cosphi2.value, 4)
+path_pmphi2_tight = make_vertices(gd1_sc.phi1.degree, gd1_sc.pm_phi2.value, 2)
+
+path_pmphi1_medium = make_vertices(gd1_sc.phi1.degree, gd1_sc.pm_phi1_cosphi2.value, 6)
+path_pmphi2_medium = make_vertices(gd1_sc.phi1.degree, gd1_sc.pm_phi2.value, 3)
+
+table = QTable()
+table["phi1"] = path_pmphi1_tight[:, 0] * u.deg
+table["pm_phi1_cosphi2_tight"] = path_pmphi1_tight[:, 1] * u.mas / u.yr
+table["pm_phi2_tight"] = path_pmphi2_tight[:, 1] * u.mas / u.yr
+table["pm_phi1_cosphi2_medium"] = path_pmphi1_medium[:, 1] * u.mas / u.yr
+table["pm_phi2_medium"] = path_pmphi2_medium[:, 1] * u.mas / u.yr
+
+table.write(paths.data / "gd1" / "pm_edges.ecsv", overwrite=True)

### 2023-07-11 src/scripts/gd1/data/4-masks.py

@@ -1,0 +1,116 @@
+"""Define data masks for GD-1."""
+
+import shutil
+import sys
+
+import asdf
+import astropy.units as u
+import galstreams
+import matplotlib.path as mpath
+import numpy as np
+from astropy.table import QTable
+from showyourwork.paths import user as user_paths
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+from scripts.gd1.frames import gd1_frame
+from scripts.helper import make_path, make_vertices
+
+##############################################################################
+# PARAMETERS
+
+SAVE_LOC = paths.data / "gd1" / "masks.asdf"
+
+snkmk: dict[str, bool]
+try:
+    snkmk = snakemake.params
+except NameError:
+    snkmk = {"load_from_static": True, "save_to_static": False}
+
+
+if snkmk["load_from_static"] and (paths.static / "gd1").exists():
+    shutil.copyfile(paths.static / "gd1" / "masks.asdf", SAVE_LOC)
+
+    sys.exit(0)
+
+# Gaia Data
+table = QTable.read(paths.data / "gd1" / "gaia_ps1_xm.asdf")
+
+
+##############################################################################
+# Masks
+
+masks_table = QTable()
+
+# =============================================================================
+# Proper motion
+
+# Mask edges
+pm_edges = QTable.read(paths.data / "gd1" / "pm_edges.ecsv")
+
+# Tight
+path_pmphi1 = make_path(pm_edges["phi1"], pm_edges["pm_phi1_cosphi2_tight"])
+path_pmphi2 = make_path(pm_edges["phi1"], pm_edges["pm_phi2_tight"])
+
+masks_table["pm_tight"] = path_pmphi1.contains_points(
+    np.c_[table["phi1"].value, table["pm_phi1"].value]
+) & path_pmphi2.contains_points(np.c_[table["phi1"].value, table["pm_phi2"].value])
+
+# Medium
+path_pmphi1 = make_path(pm_edges["phi1"], pm_edges["pm_phi1_cosphi2_medium"])
+path_pmphi2 = make_path(pm_edges["phi1"], pm_edges["pm_phi2_medium"])
+
+masks_table["pm_medium"] = path_pmphi1.contains_points(
+    np.c_[table["phi1"].value, table["pm_phi1"].value]
+) & path_pmphi2.contains_points(np.c_[table["phi1"].value, table["pm_phi2"].value])
+
+
[…]

### 2023-07-11 src/scripts/gd1/frames.py

@@ -1,0 +1,7 @@
+"""Frames."""
+
+import astropy.coordinates as coords
+import gala.coordinates as gc
+
+galactocentric_frame = coords.Galactocentric()
+gd1_frame = gc.GD1Koposov10()

### 2023-07-11 src/scripts/gd1/model.py

@@ -1,0 +1,547 @@
+"""GD-1 Model."""
+
+import sys
+from dataclasses import KW_ONLY, dataclass, replace
+from math import inf
+from typing import Any
+
+import asdf
+import astropy.units as u
+import numpy as np
+import torch as xp
+import zuko
+from astropy.table import QTable
+from showyourwork.paths import user as user_paths
+
+import stream_mapper.pytorch as sml
+from stream_mapper.core import ModelAPI
+from stream_mapper.core.setup_package import WEIGHT_NAME
+from stream_mapper.core.typing import ArrayNamespace
+from stream_mapper.core.utils import within_bounds
+from stream_mapper.pytorch import Data, IndependentModels, MixtureModel, Params
+from stream_mapper.pytorch.builtin import Exponential
+from stream_mapper.pytorch.params import ModelParameter, ModelParameters, set_param
+from stream_mapper.pytorch.params.bounds import SigmoidBounds
+from stream_mapper.pytorch.params.scaler import StandardLnWidth, StandardLocation
+from stream_mapper.pytorch.prior import Prior
+from stream_mapper.pytorch.typing import Array, NNModel
+from stream_mapper.pytorch.utils import StandardScaler
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+from scripts.helper import isochrone_spline
+
+##############################################################################
+# Setup
+
+# Load data
+distance_cp = QTable.read(paths.data / "gd1" / "control_points_distance.ecsv")
+gd1_cp_ = QTable.read(paths.data / "gd1" / "control_points_stream.ecsv")
+spur_cp = QTable.read(paths.data / "gd1" / "control_points_spur.ecsv")
+
+
+@dataclass(frozen=True, repr=False)
+class UpWeight(Prior[Array]):
+    """Force the weight to be larger than a threshold."""
+
+    threshold: float
+
+    _: KW_ONLY
+    component: str = "spur"
+    lower: float = -inf
+    upper: float = inf
+    lamda: float = 100_000
+    array_namespace: ArrayNamespace[Array] = xp
+
+    def __post_init__(self, *args: Any, **kwargs: Any) -> None:
+        wgt_name = f"{self.component}.ln-weight"
+        self._wgt_name: str
+        object.__setattr__(self, "_wgt_name", wgt_name)
+
+        super().__post_init__(*args, **kwargs)
+
[…]

### 2023-07-11 src/scripts/gd1/models/1-train_background_astrometric_flow.py

@@ -1,0 +1,239 @@
+"""Train parallax background flow."""
+
+import sys
+from dataclasses import replace
+from typing import Any
+
+import galstreams
+import matplotlib.pyplot as plt
+import numpy as np
+import torch as xp
+import torch.utils.data as td
+from matplotlib.cm import ScalarMappable
+from matplotlib.gridspec import GridSpec
+from scipy.interpolate import InterpolatedUnivariateSpline
+from showyourwork.paths import user as user_paths
+from torch import optim
+from tqdm import tqdm
+
+import stream_mapper.pytorch as sml
+from stream_mapper.core import Data
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+from scripts.gd1.datasets import data, off_stream, where
+from scripts.gd1.frames import gd1_frame
+from scripts.gd1.model import make_model
+from scripts.mpl_colormaps import stream_cmap1 as cmap_stream
+
+model_without_grad = make_model()["background"]["astrometric"]["else"]
+
+# =============================================================================
+# Load Data
+
+snkmk: dict[str, Any]
+try:
+    snkmk = dict(snakemake.params)
+except NameError:
+    snkmk = {
+        "load_from_static": False,
+        "save_to_static": False,
+        "epochs": 2_500,
+        "diagnostic_plots": True,
+    }
+
+save_path = paths.data / "gd1"
+save_path.mkdir(parents=True, exist_ok=True)
+(save_path / "astro_flow").mkdir(parents=True, exist_ok=True)
+
+static_path = paths.static / "gd1"
+static_path.mkdir(parents=True, exist_ok=True)
+
+if snkmk["load_from_static"] and (paths.static / "gd1").exists():
+    # Load from static
+    model_without_grad.load_state_dict(
+        xp.load(static_path / "background_astrometric_model.pt")
+    )
+
+    # Save to data
+    xp.save(
+        model_without_grad.state_dict(),
+        save_path / "background_astrometric_model.pt",
+    )
+
+    sys.exit(0)
+
+figure_path = paths.scripts / "gd1" / "_diagnostics" / "astro_flow"
+figure_path.mkdir(parents=True, exist_ok=True)
+
+
+mws = galstreams.MWStreams()
[…]

### 2023-07-11 src/scripts/gd1/models/2-train_background_photometry_flow.py

@@ -1,0 +1,143 @@
+"""Train photometry background flow."""
+
+import sys
+from dataclasses import replace
+from typing import Any
+
+import matplotlib.pyplot as plt
+import numpy as np
+import torch as xp
+import torch.utils.data as td
+from showyourwork.paths import user as user_paths
+from torch import optim
+from tqdm import tqdm
+
+import stream_mapper.pytorch as sml
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+from scripts.gd1.datasets import data, off_stream, where
+from scripts.gd1.model import make_model
+
+model_without_grad = make_model()["background"]["photometric"]
+
+# =============================================================================
+# Load Data
+
+snkmk: dict[str, Any]
+try:
+    snkmk = dict(snakemake.params)
+except NameError:
+    snkmk = {
+        "load_from_static": False,
+        "save_to_static": True,
+        "epochs": 2_000,
+        "diagnostic_plots": True,
+    }
+
+save_path = paths.data / "gd1"
+save_path.mkdir(parents=True, exist_ok=True)
+(save_path / "phot_flow").mkdir(parents=True, exist_ok=True)
+
+static_path = paths.static / "gd1"
+static_path.mkdir(parents=True, exist_ok=True)
+
+if snkmk["load_from_static"] and (paths.static / "gd1").exists():
+    model_without_grad.load_state_dict(
+        xp.load(static_path / "background_photometry_model.pt")
+    )
+    xp.save(
+        model_without_grad.state_dict(),
+        save_path / "background_photometry_model.pt",
+    )
+    sys.exit(0)
+
+
+figure_path = paths.scripts / "gd1" / "_diagnostics" / "phot_flow"
+figure_path.mkdir(parents=True, exist_ok=True)
+
+# =============================================================================
+# Train
+
+# Make a copy of the model with gradients
+# The network is shared with the original model
+model = replace(model_without_grad, with_grad=True)
+
+# Prerequisites for training
+coord_names = model.indep_coord_names + model.coord_names
+dataset = td.TensorDataset(
+    data[coord_names].array[off_stream],
+    where[coord_names].array[off_stream],
+)
+loader = td.DataLoader(
+    dataset=dataset,
+    batch_size=int(len(data) * 0.075),
+    shuffle=True,
+    num_workers=0,
+    drop_last=True,
+)
+optimizer = optim.AdamW(model.parameters(), lr=1e-3)
+
[…]

### 2023-07-11 src/scripts/gd1/models/3-control_points_distance.py

@@ -1,0 +1,50 @@
+"""GD-1 distance control points."""
+
+
+import astropy.units as u
+import numpy as np
+from astropy.coordinates import Distance
+from astropy.table import QTable
+from showyourwork.paths import user as user_paths
+
+paths = user_paths()
+
+##############################################################################
+
+
+table = QTable(
+    # fmt: off
+    rows=[
+        [-70.0 * u.deg, 14.5 * u.mag, 0.3],
+        [-40.0 * u.deg, 14.4 * u.mag, 0.3],
+        [0.0 * u.deg, 15 * u.mag, 0.3],
+    ],
+    # fmt: on
+    names=("phi1", "distmod", "w_distmod"),
+    units=(u.deg, u.mag, u.mag),
+    meta={},
+)
+
+# Convert to parallax
+table["parallax"] = Distance(distmod=table["distmod"]).parallax
+table["w_parallax"] = (
+    np.abs(
+        (Distance(distmod=table["distmod"] + table["w_distmod"]).parallax)
+        - (Distance(distmod=table["distmod"] - table["w_distmod"]).parallax)
+    )
+    / 2
+    * 1.1
+)
+
+# Convert to distance
+table["distance"] = Distance(distmod=table["distmod"])
+table["w_distance"] = (
+    np.abs(
+        (Distance(distmod=table["distmod"] + table["w_distmod"]))
+        - (Distance(distmod=table["distmod"] - table["w_distmod"]))
+    )
+    / 2
+)
+
+# Save
+table.write(paths.data / "gd1" / "control_points_distance.ecsv", overwrite=True)

### 2023-07-11 src/scripts/gd1/models/3-control_points_spur.py

@@ -1,0 +1,27 @@
+"""GD1 spur control points."""
+
+
+import astropy.units as u
+from astropy.table import QTable
+from showyourwork.paths import user as user_paths
+
+paths = user_paths()
+
+##############################################################################
+
+
+# Values from Price-Whelan and Bonaca 2018
+table = QTable(
+    # fmt: off
+    rows=[
+        [-35.0 * u.deg, 1.3 * u.deg, 0.85 * u.deg, -12.95 * u.mas / u.yr, 2.0 * u.mas / u.yr],  # noqa: E501
+        [-30.0 * u.deg, 1.3 * u.deg, 0.85 * u.deg, -12.6 * u.mas / u.yr, 2.0 * u.mas / u.yr],  # noqa: E501
+        [-20 * u.deg, 1.5 * u.deg, 0.85 * u.deg, -11.5 * u.mas / u.yr, 2.0 * u.mas / u.yr],  # noqa: E501
+    ],
+    # fmt: on
+    names=("phi1", "phi2", "w_phi2", "pm_phi1", "w_pm_phi1"),
+    units=(u.deg, u.deg, u.deg, u.mas / u.yr, u.mas / u.yr),
+    meta={},
+)
+
+table.write(paths.data / "gd1" / "control_points_spur.ecsv", overwrite=True)

### 2023-07-11 src/scripts/gd1/models/4-train_model.py

@@ -1,0 +1,220 @@
+"""Train GD-1 model."""
+
+import re
+import sys
+import warnings
+from typing import Any
+
+import matplotlib.pyplot as plt
+import numpy as np
+import torch as xp
+import torch.utils.data as td
+from showyourwork.paths import user as user_paths
+from torch import optim
+from tqdm import tqdm
+
+import stream_mapper.pytorch as sml
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+from scripts.gd1.datasets import data, where
+from scripts.gd1.model import make_model
+from scripts.gd1.models.helper import diagnostic_plot
+from scripts.helper import manually_set_dropout
+
+# =============================================================================
+# Initial set up
+
+snkmk: dict[str, Any]
+try:
+    snkmk = dict(snakemake.params)
+except NameError:
+    snkmk = {
+        "load_from_static": False,
+        "save_to_static": False,
+        "diagnostic_plots": True,
+        # training
+        "weight_decay": 1e-8,
+        "lr": 1e-3,
+        "T_high": 10_000,
+        "T_spur": 1,
+        "T_post_spur": 999,
+        "T_refine": 500,
+    }
+snkmk["epochs"] = (
+    snkmk["T_high"] + snkmk["T_spur"] + snkmk["T_post_spur"] + snkmk["T_refine"]
+)
+
+model = make_model()
+
+save_path = paths.data / "gd1"
+save_path.mkdir(parents=True, exist_ok=True)
+(save_path / "models").mkdir(parents=True, exist_ok=True)
+
+static_path = paths.static / "gd1"
+static_path.mkdir(parents=True, exist_ok=True)
+
+if snkmk["load_from_static"] and (paths.static / "gd1").exists():
+    model.load_state_dict(xp.load(static_path / "model.pt"))
+    xp.save(model.state_dict(), save_path / "model.pt")
+
+    sys.exit(0)
+
+diagnostic_path = paths.scripts / "gd1" / "_diagnostics" / "models"
+diagnostic_path.mkdir(parents=True, exist_ok=True)
+
+# =============================================================================
+# Load saved model components
+
+model["background"]["astrometric"]["else"].load_state_dict(
+    xp.load(save_path / "background_astrometric_model.pt")
+)
+model["background"]["photometric"].load_state_dict(
[…]

### 2023-07-11 src/scripts/gd1/models/6-variable_nspur.py

@@ -1,0 +1,22 @@
+"""write variable 'nspur_variable.txt' to disk."""
+
+from astropy.table import QTable
+from showyourwork.paths import user as user_paths
+
+paths = user_paths()
+
+save_path = paths.data / "gd1"
+save_path.mkdir(parents=True, exist_ok=True)
+
+output_path = paths.output / "gd1" / "nspur"
+output_path.mkdir(parents=True, exist_ok=True)
+
+# =============================================================================
+# Load Data
+
+lik_tbl = QTable.read(save_path / "membership_likelhoods.ecsv")
+
+is_strm = (lik_tbl["spur (50%)"] > 0.80) & (lik_tbl["spur.ln-weight"].mean(1) > -6)
+
+with (output_path / "nspur_variable.txt").open("w") as f:
+    f.write(f"${sum(is_strm):d}$")

### 2023-07-11 src/scripts/gd1/models/6-variable_nspur_probability.py

@@ -1,0 +1,11 @@
+"""write variable 'nspur_variable.txt' to disk."""
+
+from showyourwork.paths import user as user_paths
+
+paths = user_paths()
+
+output_path = paths.output / "gd1" / "nspur"
+output_path.mkdir(parents=True, exist_ok=True)
+
+with (output_path / "minimum_membership_probability.txt").open("w") as f:
+    f.write(r"$80\%$")

### 2023-07-11 src/scripts/gd1/models/6-variable_nstream.py

@@ -1,0 +1,22 @@
+"""write variable 'nstream_variable.txt' to disk."""
+
+from astropy.table import QTable
+from showyourwork.paths import user as user_paths
+
+paths = user_paths()
+
+save_path = paths.output / "gd1"
+save_path.mkdir(parents=True, exist_ok=True)
+
+output_path = paths.output / "gd1" / "nstream"
+output_path.mkdir(parents=True, exist_ok=True)
+
+# =============================================================================
+# Load Data
+
+lik_tbl = QTable.read(paths.data / "gd1" / "membership_likelhoods.ecsv")
+
+is_strm = (lik_tbl["stream (50%)"] > 0.80) & (lik_tbl["stream.ln-weight"].mean(1) > -6)
+
+with (output_path / "nstream_variable.txt").open("w") as f:
+    f.write(f"${sum(is_strm):d}$")

### 2023-07-11 src/scripts/gd1/models/6-variable_nstream_percentile.py

@@ -1,0 +1,11 @@
+"""write variable 'nstream_variable.txt' to disk."""
+
+from showyourwork.paths import user as user_paths
+
+paths = user_paths()
+
+output_path = paths.output / "gd1" / "nstream"
+output_path.mkdir(parents=True, exist_ok=True)
+
+with (output_path / "posterior_percentile.txt").open("w") as f:
+    f.write(r"$50$th")

### 2023-07-11 src/scripts/gd1/models/6-variable_nstream_probability.py

@@ -1,0 +1,11 @@
+"""write variable 'nstream_variable.txt' to disk."""
+
+from showyourwork.paths import user as user_paths
+
+paths = user_paths()
+
+output_path = paths.output / "gd1" / "nstream"
+output_path.mkdir(parents=True, exist_ok=True)
+
+with (output_path / "minimum_membership_probability.txt").open("w") as f:
+    f.write(r"$80\%$")

### 2023-07-11 src/scripts/gd1/plot/data_selection.py

@@ -1,0 +1,242 @@
+"""Plot the data masks."""
+
+import sys
+
+import asdf
+import astropy.units as u
+import galstreams
+import matplotlib.pyplot as plt
+import numpy as np
+import shapely.geometry as sg
+import shapely.ops as so
+from astropy.table import QTable
+from matplotlib.colors import LogNorm
+from scipy.interpolate import InterpolatedUnivariateSpline
+from showyourwork.paths import user as user_paths
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+from scripts.gd1.frames import gd1_frame
+from scripts.helper import make_path
+
+###############################################################################
+# Load stuff
+
+# Matplotlib style
+plt.style.use(paths.scripts / "paper.mplstyle")
+
+# Load data
+table = QTable.read(paths.data / "gd1" / "gaia_ps1_xm.asdf")
+masks_table = QTable.read(paths.data / "gd1" / "masks.asdf")
+
+pm_edges = QTable.read(paths.data / "gd1" / "pm_edges.ecsv")
+
+# Load isochrone
+with asdf.open(
+    paths.data / "gd1" / "isochrone.asdf", lazy_load=False, copy_arrays=True
+) as af:
+    isochrone = af["isochrone_medium"]
+
+# Load galstreams
+mws = galstreams.MWStreams()
+gd1 = mws["GD-1-I21"]
+gd1_sc = gd1.track.transform_to(gd1_frame)[::100]
+
+# spline of lit tracks
+spline_pmphi1 = InterpolatedUnivariateSpline(
+    gd1_sc.phi1.value, gd1_sc.pm_phi1_cosphi2.value
+)
+spline_pmphi2 = InterpolatedUnivariateSpline(gd1_sc.phi1.value, gd1_sc.pm_phi2.value)
+
+# Lit tracks
+_lit1_kw = {"c": "k", "ls": "--", "alpha": 0.6}
+
+###############################################################################
+
+
+path_pm = make_path(pm_edges["pm_phi1_cosphi2_medium"], pm_edges["pm_phi2_medium"])
+
+_mask = (
[…]

### 2023-07-11 src/scripts/gd1/plot/photometric_background_selection.py

@@ -1,0 +1,138 @@
+"""Plot the photometry background flow."""
+
+import sys
+
+import asdf
+import astropy.units as u
+import matplotlib.pyplot as plt
+import numpy as np
+from astropy.table import QTable
+from scipy.stats import gaussian_kde
+from showyourwork.paths import user as user_paths
+
+import stream_mapper.pytorch as sml
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+# =============================================================================
+
+# Load data
+table = QTable.read(paths.data / "gd1" / "gaia_ps1_xm.asdf")
+masks = QTable.read(paths.data / "gd1" / "masks.asdf")
+
+# Make Mask
+pm_tight_mask = (
+    (table["pm_phi1"] > -15 * u.mas / u.yr)
+    & (table["pm_phi1"] < -10 * u.mas / u.yr)
+    & (table["pm_phi2"] > -4.5 * u.mas / u.yr)
+    & (table["pm_phi2"] < -2 * u.mas / u.yr)
+)
+completeness_mask = table["gaia_g"] < 20 * u.mag
+
+sel = (
+    pm_tight_mask
+    & completeness_mask
+    & masks["low_phi2"]
+    & ~np.isnan(table["g0"])
+    & ~np.isnan(table["r0"])
+    & (table["phi1"] > -80 * u.deg)
+    & (table["phi1"] < 10 * u.deg)
+)
+
+# Apply mask
+table = table[sel]
+masks = masks[sel]
+
+# Get off-stream selection
+off_stream = ~masks["offstream"]
+
+# Turn into sml.Data
+with asdf.open(
+    paths.data / "gd1" / "info.asdf", lazy_load=False, copy_arrays=True
+) as af:
+    names = tuple(af["names"])
+    renamer = af["renamer"]
+data = sml.Data.from_format(table, fmt="astropy.table", names=names, renamer=renamer)
+where = sml.Data((~np.isnan(data.array)), names=data.names)
+
+# =============================================================================
+
+bw_method = 0.05
+background_kde = gaussian_kde(
+    np.c_[data["g"][off_stream], data["r"][off_stream]].T,
+    bw_method=bw_method,
+)
[…]

### 2023-07-11 src/scripts/gd1/plot/results_full.py

@@ -1,0 +1,1228 @@
+"""Plot the trained GD1 model."""
+
+from __future__ import annotations
+
+import copy as pycopy
+import sys
+
+import astropy.units as u
+import galstreams
+import matplotlib.pyplot as plt
+import numpy as np
+import torch as xp
+from astropy.coordinates import Distance
+from astropy.table import QTable
+from matplotlib.cm import ScalarMappable
+from matplotlib.gridspec import GridSpec
+from matplotlib.legend_handler import HandlerTuple
+from matplotlib.lines import Line2D
+from scipy.interpolate import InterpolatedUnivariateSpline
+from showyourwork.paths import user as user_paths
+from tqdm import tqdm
+
+from stream_mapper.core import WEIGHT_NAME, Params
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+from scripts.gd1.datasets import data
+from scripts.gd1.frames import gd1_frame as frame
+from scripts.gd1.model import make_model
+from scripts.helper import (
+    color_by_probable_member,
+    manually_set_dropout,
+    p2alpha,
+    recursive_iterate,
+)
+from scripts.mpl_colormaps import stream_cmap1 as cmap_stream
+from scripts.mpl_colormaps import stream_cmap2 as cmap_spur
+
+# =============================================================================
+# Load data
+
+# Matplotlib style
+plt.style.use(paths.scripts / "paper.mplstyle")
+
+# Load control points
+stream_cp = QTable.read(paths.data / "gd1" / "control_points_stream.ecsv")
+spur_cp = QTable.read(paths.data / "gd1" / "control_points_spur.ecsv")
+distance_cp = QTable.read(paths.data / "gd1" / "control_points_distance.ecsv")
+
+# Load model
+model = make_model()
+model = pycopy.deepcopy(model)
+model.load_state_dict(xp.load(paths.data / "gd1" / "model.pt"))
+model = model.eval()
+
[…]

### 2023-07-11 src/scripts/gd1/plot/results_panels.py

@@ -1,0 +1,231 @@
+"""Plot Phi1-binned panels of the trained model."""
+
+import sys
+
+import asdf
+import matplotlib as mpl
+import matplotlib.pyplot as plt
+import numpy as np
+import torch as xp
+from astropy.table import QTable
+from matplotlib.gridspec import GridSpec
+from showyourwork.paths import user as user_paths
+from tqdm import tqdm
+
+import stream_mapper.visualization as smlvis
+from stream_mapper.core import Data, Params
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+from scripts.gd1.datasets import data
+from scripts.gd1.model import make_model
+from scripts.helper import (
+    color_by_probable_member,
+    manually_set_dropout,
+    p2alpha,
+    recursive_iterate,
+)
+from scripts.mpl_colormaps import stream_cmap1 as cmap1
+from scripts.mpl_colormaps import stream_cmap2 as cmap2
+
+# =============================================================================
+# Load data
+
+# Matplotlib style
+plt.style.use(paths.scripts / "paper.mplstyle")
+
+# isochrone data
+with asdf.open(
+    paths.data / "gd1" / "isochrone.asdf", "r", lazy_load=False, copy_arrays=True
+) as af:
+    isochrone_data = Data(**af["isochrone_data"])
+
+# Load model
+model = make_model()
+model.load_state_dict(xp.load(paths.data / "gd1" / "model.pt"))
+model = model.eval()
+
+# Load results from 4-likelihoods.py
+lik_tbl = QTable.read(paths.data / "gd1" / "membership_likelhoods.ecsv")
+bkg_prob = np.array(lik_tbl["bkg (50%)"])
+stream_prob = np.array(lik_tbl["stream (50%)"])
+stream_wgt = np.array(lik_tbl["stream.ln-weight"])
+spur_prob = np.array(lik_tbl["spur (50%)"])
+spur_wgt = np.array(lik_tbl["spur.ln-weight"])
+allstream_prob = np.array(lik_tbl["allstream (50%)"])
+
+# =============================================================================
+# Cut down
+
+keep = data["phi1"] < 10  # [deg]
+data = data[keep]
+bkg_prob = bkg_prob[keep]
[…]

### 2023-07-11 src/scripts/gd1/plot/smooth_likelihood.py

@@ -1,0 +1,146 @@
+"""Plot GD1 Likelihoods."""
+
+import sys
+
+import matplotlib.pyplot as plt
+import numpy as np
+import torch as xp
+from matplotlib.cm import ScalarMappable
+from matplotlib.gridspec import GridSpec
+from scipy import stats
+from showyourwork.paths import user as user_paths
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+from scripts.gd1.datasets import data, where
+from scripts.gd1.model import make_model
+
+# =============================================================================
+
+# Matplotlib style
+plt.style.use(paths.scripts / "paper.mplstyle")
+
+# Load model
+model = make_model()
+model.load_state_dict(xp.load(paths.data / "gd1" / "model.pt"))
+model = model.eval()
+
+with xp.no_grad():
+    mpars = model.unpack_params(model(data))
+
+    stream_lnlik = model.component_ln_likelihood("stream", mpars, data, where=where)
+    spur_lnlik = model.component_ln_likelihood("spur", mpars, data, where=where)
+    tot_lnlik = model.ln_likelihood(mpars, data, where=where)
+
+tot_stream_prob = np.exp(np.logaddexp(stream_lnlik, spur_lnlik) - tot_lnlik)
+
+nddata = data.astype(np.ndarray)
+
+# =============================================================================
+# Plot
+
+fig = plt.figure(figsize=(6, 4.5))
+
+gs = GridSpec(
+    4,
+    1,
+    figure=fig,
+    height_ratios=(1, 5, 5, 5),
+    hspace=0.15,
+    left=0.12,
+    right=0.98,
+    top=0.94,
+    bottom=0.1,
+)
+cmap = plt.get_cmap()
+
+# ---------------------------------------------------------------------------
+# Colormap
+
+ax0 = fig.add_subplot(gs[0, :])
+cbar = fig.colorbar(ScalarMappable(cmap=cmap), cax=ax0, orientation="horizontal")
+cbar.ax.xaxis.set_ticks_position("top")
[…]

### 2023-07-11 src/scripts/gd1/table/control_points.py

@@ -1,0 +1,137 @@
+"""Plot GD1 Likelihoods."""
+
+import sys
+from io import StringIO
+
+import numpy as np
+from astropy.table import QTable, Table
+from astropy.units import Quantity
+from showyourwork.paths import user as user_paths
+
+from stream_mapper.core.typing import Array
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+(paths.output / "gd1").mkdir(exist_ok=True, parents=True)
+
+# =============================================================================
+
+cps_stream = QTable.read(paths.data / "gd1" / "control_points_stream.ecsv")
+cps_spur = QTable.read(paths.data / "gd1" / "control_points_spur.ecsv")
+cps_dist = QTable.read(paths.data / "gd1" / "control_points_distance.ecsv")
+
+
+def low_high(vs: Array, es: Array) -> list[str]:
+    """Process to +/- error string."""
+    vs = Quantity(vs).value
+    es = Quantity(es).value
+    return [
+        (
+            "${\\color{gray}\\big(}_{"
+            + lower
+            + "}^{"
+            + ("" if len(lower) == len(upper) else "\\phantom{+}")
+            + upper
+            + "}{\\color{gray}\\big)}$"
+            if not np.isnan(v)
+            else ""
+        )
+        for v, lower, upper in (
+            (v, f"{v - e:0.2f}", f"{v + e:0.2f}") for v, e in zip(vs, es, strict=True)
+        )
+    ]
+
+
+table = Table()
+
+table["component"] = ["stream"] * len(cps_stream) + ["spur"] * len(cps_spur)
+table[r"$\phi_1 \,[\rm{\degree}]$"] = np.concatenate(
+    (cps_stream["phi1"], cps_spur["phi1"])
+)
+table[r"$\phi_2 \,[\rm{\degree}]$"] = low_high(
+    cps_stream["phi2"], cps_stream["w_phi2"]
+) + low_high(cps_spur["phi2"], cps_spur["w_phi2"])
+table[r"$\mu_{\phi_1} \,[\frac{\rm{mas}}{\rm{yr}}]$"] = low_high(
+    cps_stream["pm_phi1"], cps_stream["w_pm_phi1"]
+) + low_high(cps_spur["pm_phi1"], cps_spur["w_pm_phi1"])
+table[r"$\mu \,[\rm{mag}]$"] = " " * 74
[…]

### 2023-07-11 src/scripts/gd1/table/member_table_select.py

@@ -1,0 +1,250 @@
+"""Plot GD1 Likelihoods."""
+
+import sys
+from io import StringIO
+
+import numpy as np
+from astropy.table import QTable
+from numpy.lib.recfunctions import structured_to_unstructured
+from showyourwork.paths import user as user_paths
+
+from stream_mapper.core.typing import Array
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+from scripts.gd1.datasets import table as data_table
+
+(paths.output / "gd1").mkdir(exist_ok=True, parents=True)
+rng = np.random.default_rng(42)
+
+# =============================================================================
+
+member_liks = QTable.read(paths.data / "gd1" / "membership_likelhoods.ecsv")
+
+sel = (member_liks["stream (95%)"] > 0.8) | (member_liks["spur (95%)"] > 0.8)
+
+# Select some rows
+rows = []
+# we work within the table selection
+strm_mle = member_liks["stream (MLE)"][sel]
+spur_mle = member_liks["spur (MLE)"][sel]
+# 1 row with highest probability
+rows.append(np.argmax(strm_mle))
+# 5 rows with a probability > 0.9
+prob_idx = np.where(strm_mle > 0.9)[0]
+subselect = rng.choice(np.arange(len(prob_idx)), size=5, replace=False, shuffle=False)
+rows.extend(prob_idx[subselect])
+# 4 rows with a probability < 0.75
+prob_idx = np.where(strm_mle < 0.75)[0]
+subselect = rng.choice(np.arange(len(prob_idx)), size=4, replace=False, shuffle=False)
+rows.extend(prob_idx[subselect])
+# 1 row with highest probability > 0.99
+rows.append(np.argmax(spur_mle))
+# 1 rows with a probability > 0.9 and low stream probability
+prob_idx = np.where(
+    (strm_mle < 0.75) & (spur_mle > 0.9) & (spur_mle != spur_mle.max())
+)[0]
+subselect = rng.choice(np.arange(len(prob_idx)), size=1, replace=False, shuffle=False)
+rows.extend(prob_idx[subselect])
+# # 3 rows with non-zero joint probability  # TODO
+# prob_idx = np.where((strm_mle > 0.1) & (spur_mle > 0.6))[0]
[…]

### 2023-07-11 src/scripts/helper.py

@@ -1,0 +1,120 @@
+"""Exposes common paths useful for manipulating datasets and generating figures."""
+
+from __future__ import annotations
+
+from collections.abc import Mapping
+from functools import partial
+from typing import TYPE_CHECKING, Any
+
+import astropy.units as u
+import matplotlib.path as mpath
+import numpy as np
+import torch as xp
+from scipy.interpolate import CubicSpline
+from torch import nn
+
+from stream_mapper.core.utils import pairwise_distance
+from stream_mapper.pytorch.builtin.compat._flow import _FlowModel
+
+if TYPE_CHECKING:
+    from types import FunctionType
+
+    from matplotlib.colors import LinearSegmentedColormap
+
+    from stream_mapper.core import ModelAPI, Params
+    from stream_mapper.core.typing import Array, ArrayNamespace
+
+
+def p2alpha(p: Array, /, minval: float = 0.1) -> Array:
+    """Convert probability to alpha."""
+    out = minval + (1 - minval) * np.where(  # avoid NaN for p=0
+        p == p.max(), 1, (p - p.min()) / (p.max() - p.min())
+    )
+    return np.clip(out, minval, 1)
+
+
+def color_by_probable_member(
+    *pandcmaps: tuple[Array, LinearSegmentedColormap]
+) -> np.ndarray:
+    """Color by the most probable member."""
+    # probabilities
+    ps = np.stack(tuple(p[0] for p in pandcmaps), 1)
+    # colors
+    cs = np.stack(tuple(cmap(p) for p, cmap in pandcmaps), 0)
+    # color by most probable
+    return cs[np.argmax(ps, 1), np.arange(len(ps))]
+
+
+def isochrone_spline(mags: Array, *, xp: ArrayNamespace[Array]) -> CubicSpline:
+    """Return a spline interpolating the isochrone's coordinates."""
+    pdist = pairwise_distance(mags, axis=0, xp=xp)
+    gamma = xp.concatenate((xp.asarray([0]), pdist.cumsum(0)))
+    gamma = gamma / gamma[-1]  # gamma in [0, 1]
+    return CubicSpline(gamma, mags)
+
+
+def manually_set_dropout(model: ModelAPI, p: float) -> tuple[ModelAPI]:
+    """Manually set dropout.
+
+    For use when pytorch ``.eval()`` doesn't work
+    """
+    for m in model.children():
+        if isinstance(m, nn.Dropout):
+            m.p = p
[…]

### 2023-07-11 src/scripts/mock/data/2-variable_isochrone_age.py

@@ -1,0 +1,15 @@
+"""write variable 'isochrone_age_variable.txt' to disk."""
+
+import asdf
+from showyourwork.paths import user as user_paths
+
+paths = user_paths()
+(paths.output / "mock").mkdir(parents=True, exist_ok=True)
+
+# =============================================================================
+# Load Data
+
+with asdf.open(
+    paths.data / "mock" / "data.asdf", lazy_load=False, copy_arrays=True
+) as af, (paths.output / "mock" / "isochrone_age_variable.txt").open("w") as f:
+    f.write(f"{af['isochrone_age'].value:g} {af['isochrone_age'].unit}")

### 2023-07-11 src/scripts/mock/data/2-variable_isochrone_feh.py

@@ -1,0 +1,15 @@
+"""write variable 'isochrone_feh_variable.txt' to disk."""
+
+import asdf
+from showyourwork.paths import user as user_paths
+
+paths = user_paths()
+(paths.output / "mock").mkdir(parents=True, exist_ok=True)
+
+# =============================================================================
+# Load Data
+
+with asdf.open(
+    paths.data / "mock" / "data.asdf", lazy_load=False, copy_arrays=True
+) as af, (paths.output / "mock" / "isochrone_feh_variable.txt").open("w") as f:
+    f.write(f"{af['isochrone_feh']:g}~dex")

### 2023-07-11 src/scripts/mock/model.py

@@ -1,0 +1,242 @@
+"""Train photometry background flow."""
+
+import sys
+from collections.abc import Callable
+from dataclasses import dataclass
+
+import asdf
+import numpy as np
+import torch as xp
+import zuko
+from scipy.interpolate import CubicSpline
+from showyourwork.paths import user as user_paths
+
+import stream_mapper.pytorch as sml
+from stream_mapper.core import WEIGHT_NAME
+from stream_mapper.core.typing import ArrayNamespace
+from stream_mapper.pytorch.builtin import Parallax2DistMod
+from stream_mapper.pytorch.params import ModelParameter, ModelParameters
+from stream_mapper.pytorch.params.bounds import ClippedBounds, SigmoidBounds
+from stream_mapper.pytorch.params.scaler import StandardLnWidth, StandardLocation
+from stream_mapper.pytorch.typing import Array
+
+paths = user_paths()
+
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+from scripts.helper import isochrone_spline
+
+# =============================================================================
+# Load Data
+
+with asdf.open(
+    paths.data / "mock" / "data.asdf", lazy_load=False, copy_arrays=True
+) as af:
+    stream_abs_mags = af["stream_abs_mags"]
+    gamma_mass = af["gamma_mass"]
+
+    data = sml.Data(**af["data"]).astype(xp.Tensor, dtype=xp.float32)
+    where = sml.Data(**af["where"]).astype(xp.Tensor, dtype=xp.bool)
+    scaler = sml.utils.StandardScaler(**af["scaler"]).astype(
+        xp.Tensor, dtype=xp.float32
+    )
+    object.__setattr__(scaler, "names", tuple(scaler.names))
+    coord_bounds = {k: tuple(v) for k, v in af["coord_bounds"].items()}
+
+
+# =============================================================================
+# Make Data
+
+coord_astrometric_names = ("phi2", "parallax")
+coord_photometric_names = ()
+phot_names = ("g", "r")
+coord_names = coord_astrometric_names + coord_photometric_names
+
+coord_astrometric_bounds = {k: coord_bounds[k] for k in coord_astrometric_names}
+coord_photometric_bounds = {k: coord_bounds[k] for k in coord_photometric_names}
+phot_bounds = {k: coord_bounds[k] for k in phot_names}
+
+
[…]

### 2023-07-11 src/scripts/mock/models/1-train_flow.py

@@ -1,0 +1,135 @@
+"""Train photometry background flow."""
+
+import sys
+from dataclasses import replace
+from typing import Any
+
+import asdf
+import matplotlib.pyplot as plt
+import torch as xp
+import torch.utils.data as td
+from showyourwork.paths import user as user_paths
+from torch import optim
+from tqdm import tqdm
+
+import stream_mapper.pytorch as sml
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+from scripts.mock.model import bkg_flow as model_without_grad
+from scripts.mock.model import flow_coords
+
+# =============================================================================
+# Parameters
+
+snkmk: dict[str, Any]
+try:
+    snkmk = dict(snakemake.params)
+except NameError:
+    snkmk = {
+        "load_from_static": False,
+        "save_to_static": True,
+        "diagnostic_plots": True,
+        "epochs": 400,
+        "lr": 1e-3,
+    }
+
+
+if snkmk["load_from_static"] and (paths.static / "mock").exists():
+    model_without_grad.load_state_dict(
+        xp.load(paths.static / "mock" / "background_photometry_model.pt")
+    )
+    xp.save(
+        model_without_grad.state_dict(),
+        paths.data / "mock" / "background_photometry_model.pt",
+    )
+
+    sys.exit(0)
+
+
+# =============================================================================
+# Load Data
+
+with asdf.open(
+    paths.data / "mock" / "data.asdf", lazy_load=False, copy_arrays=True
+) as af:
+    table = af["table"]
+
+    data = sml.Data(**af["data"]).astype(xp.Tensor, dtype=xp.float32)
+    where = sml.Data(**af["where"]).astype(xp.Tensor, dtype=bool)
+    scaler = sml.utils.StandardScaler(**af["scaler"]).astype(
+        xp.Tensor, dtype=xp.float32
+    )
+
+    off_stream = af["off_stream"]
+
+figure_path = paths.scripts / "mock" / "_diagnostics" / "flow"
+figure_path.mkdir(parents=True, exist_ok=True)
+
+# =============================================================================
+# Training Parameters
+
+# Turn on gradients for training
+model = replace(model_without_grad, with_grad=True)
+
+data_offstream: sml.Data = data[off_stream]
+where_offstream: sml.Data = where[off_stream]
+
+loader = td.DataLoader(
+    dataset=td.TensorDataset(
[…]

### 2023-07-11 src/scripts/mock/models/2-train_model.py

@@ -1,0 +1,183 @@
+"""Train photometry background flow."""
+
+import sys
+from typing import Any
+
+import asdf
+import matplotlib.pyplot as plt
+import torch as xp
+import torch.utils.data as td
+from showyourwork.paths import user as user_paths
+from torch import optim
+from tqdm import tqdm
+
+import stream_mapper.pytorch as sml
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+from scripts import helper
+from scripts.mock.model import model
+from scripts.mock.models.helper import diagnostic_plot
+
+# =============================================================================
+# Parameters
+
+snkmk: dict[str, Any]
+try:
+    snkmk = dict(snakemake.params)
+except NameError:
+    snkmk = {
+        "load_from_static": False,
+        "save_to_static": False,
+        "diagnostic_plots": True,
+        "init_T": 500,
+        "T_0": 500,
+        "n_T": 3,
+        "final_T": 1_000,
+        "eta_min": 1e-4,
+        "lr": 5e-3,
+    }
+snkmk["epochs"] = snkmk["init_T"] + snkmk["T_0"] * snkmk["n_T"] + snkmk["final_T"]
+
+
+if snkmk["load_from_static"] and (paths.static / "mock").exists():
+    model.load_state_dict(xp.load(paths.static / "mock" / "model.pt"))
+    xp.save(model.state_dict(), paths.data / "mock" / "model.pt")
+
+    sys.exit(0)
+
+# =============================================================================
+# Load Data
+
+with asdf.open(
+    paths.data / "mock" / "data.asdf", lazy_load=False, copy_arrays=True
+) as af:
+    data = sml.Data(**af["data"]).astype(xp.Tensor, dtype=xp.float32)
+    where = sml.Data(**af["where"]).astype(xp.Tensor, dtype=xp.bool)
+    scaler = sml.utils.StandardScaler(**af["scaler"]).astype(
+        xp.Tensor, dtype=xp.float32
+    )
+    table = af["table"]
+
+# ensure the folders exist
+(paths.data / "mock").mkdir(exist_ok=True, parents=True)
+(paths.static / "mock").mkdir(exist_ok=True, parents=True)
+diagnostic_path = paths.scripts / "mock" / "_diagnostics" / "models"
+diagnostic_path.mkdir(parents=True, exist_ok=True)
[…]

### 2023-07-11 src/scripts/mock/plot/photometric_background_selection.py

@@ -1,0 +1,72 @@
+"""Train photometry background flow."""
+
+
+import asdf
+import matplotlib.pyplot as plt
+import numpy as np
+import torch as xp
+from showyourwork.paths import user as user_paths
+
+import stream_mapper.pytorch as sml
+
+paths = user_paths()
+
+
+# =============================================================================
+
+plt.style.use(paths.scripts / "paper.mplstyle")
+
+
+with asdf.open(
+    paths.data / "mock" / "data.asdf", lazy_load=False, copy_arrays=True
+) as af:
+    data = sml.Data(**af["data"]).astype(xp.Tensor, dtype=xp.float32)
+    where = sml.Data(**af["where"]).astype(xp.Tensor, dtype=xp.bool)
+    off_stream = np.array(af["off_stream"], dtype=bool)
+
+# =============================================================================
+
+fig, axs = plt.subplots(2, 1, figsize=(4, 4))
+
+# Plot the astrometric background selection
+axs[0].plot(
+    data["phi1"][off_stream],
+    data["phi2"][off_stream],
+    ls="none",
+    marker=",",
+    ms=1,
+    color="k",
+)
+axs[0].plot(
+    data["phi1"][~off_stream],
+    data["phi2"][~off_stream],
+    ls="none",
+    marker=",",
+    ms=1,
+    color="tab:blue",
+    alpha=0.25,
+)
+axs[0].set_xlabel(r"$\phi_1 \ $ [$\degree$]")
+axs[0].set_ylabel(r"$\phi_2 \ $ [$\degree$]")
+axs[0].set_aspect(2)
+axs[0].grid(visible=True, which="both", axis="y")
+axs[0].grid(visible=True, which="major", axis="x")
+axs[0].set_rasterization_zorder(100)
+
+# Plot the photometric background selection
+axs[1].scatter(data["g-r"][off_stream], data["g"][off_stream], s=0.5, color="k")
+axs[1].scatter(
+    data["g-r"][~off_stream],
+    data["g"][~off_stream],
+    s=0.5,
+    color="tab:blue",
+    alpha=0.25,
+)
+axs[1].set_xlabel(r"$g-r \ $ [mag]")
+axs[1].set_ylabel(r"$g \ $ [mag]")
+axs[1].set_aspect("auto")
+axs[1].grid(visible=True, which="major")
+axs[1].set_rasterization_zorder(100)
+
+fig.tight_layout()
+fig.savefig(paths.figures / "mock" / "photometric_background_selection.pdf")

### 2023-07-11 src/scripts/mock/plot/results.py

@@ -1,0 +1,525 @@
+"""Train photometry background flow."""
+
+import sys
+
+import asdf
+import matplotlib as mpl
+import matplotlib.pyplot as plt
+import numpy as np
+import torch as xp
+from matplotlib.gridspec import GridSpec
+from showyourwork.paths import user as user_paths
+from tqdm import tqdm
+
+import stream_mapper.pytorch as sml
+import stream_mapper.visualization as smlvis
+from stream_mapper.core import WEIGHT_NAME
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+from scripts.helper import manually_set_dropout, p2alpha, recursive_iterate
+from scripts.mock.model import model
+
+# =============================================================================
+
+# Matplotlib style
+plt.style.use(paths.scripts / "paper.mplstyle")
+
+# Load model
+model.load_state_dict(xp.load(paths.data / "mock" / "model.pt"))
+
+# Load data
+with asdf.open(paths.data / "mock" / "data.asdf") as af:
+    data = sml.Data(**af["data"]).astype(xp.Tensor, dtype=xp.float32)
+    where = sml.Data(**af["where"]).astype(xp.Tensor, dtype=xp.bool)
+    stream_table = af["stream_table"]
+    table = af["table"]
+    n_stream = af["n_stream"]
+    n_background = af["n_background"]
+
+# =============================================================================
+# Likelihood
+
+# Also evaluate the model with dropout on
+with xp.no_grad():
+    # turn dropout on
+    model = model.train()
+    manually_set_dropout(model, 0.15)
+    # evaluate the model
+    ldmpars = [model.unpack_params(model(data)) for i in tqdm(range(100))]
+    # Mpars
+    dmpars = sml.params.Params(
+        recursive_iterate(ldmpars, ldmpars[0], reduction=lambda x: x)
+    )
+
+    # turn dropout back off
+    manually_set_dropout(model, 0)
+    model = model.eval()
+
+# Evaluate model
+with xp.no_grad():
+    manually_set_dropout(model, 0)
[…]

### 2023-07-11 src/scripts/mock/stats/variable_falseident.py

@@ -1,0 +1,52 @@
+"""write variable 'isochrone_age_variable.txt' to disk."""
+
+import sys
+
+import asdf
+import torch as xp
+from showyourwork.paths import user as user_paths
+
+import stream_mapper.pytorch as sml
+from stream_mapper.core import WEIGHT_NAME
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+from scripts.mock.model import model
+from scripts.mock.models import helper
+
+(paths.output / "mock").mkdir(parents=True, exist_ok=True)
+
+# =============================================================================
+# Load Data
+
+# Load model
+model.load_state_dict(xp.load(paths.data / "mock" / "model.pt"))
+
+# Load data
+with asdf.open(paths.data / "mock" / "data.asdf") as af:
+    data = sml.Data(**af["data"]).astype(xp.Tensor, dtype=xp.float32)
+    where = sml.Data(**af["where"]).astype(xp.Tensor, dtype=xp.bool)
+    table = af["table"]
+
+
+# Evaluate model
+with xp.no_grad():
+    helper.manually_set_dropout(model, 0)
+    mpars = model.unpack_params(model(data))
+
+    stream_lik = model.component_posterior("stream", mpars, data, where=where)
+    tot_lik = model.posterior(mpars, data, where=where)
+
+stream_prob = stream_lik / tot_lik
+stream_prob[(stream_prob > 0.4) & (mpars[(f"stream.{WEIGHT_NAME}",)] < -4)] = 0
+# nstream = int(sum(stream_prob > 0.8))
+
+numstream = sum(table["label"] == "stream")
+falseident = (sum(stream_prob.numpy() > 0.8) - numstream) / numstream * 100
+
+with (paths.output / "mock" / "falseident_variable.txt").open("w") as f:
+    f.write(f"{falseident:2g}")

### 2023-07-11 src/scripts/mock/stats/variable_ncorrect.py

@@ -1,0 +1,53 @@
+"""write variable 'isochrone_age_variable.txt' to disk."""
+
+import sys
+
+import asdf
+import torch as xp
+from showyourwork.paths import user as user_paths
+
+import stream_mapper.pytorch as sml
+from stream_mapper.core import WEIGHT_NAME
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+from scripts.mock.model import model
+from scripts.mock.models import helper
+
+(paths.output / "mock").mkdir(parents=True, exist_ok=True)
+
+# =============================================================================
+# Load Data
+
+# Load model
+model.load_state_dict(xp.load(paths.data / "mock" / "model.pt"))
+
+# Load data
+with asdf.open(paths.data / "mock" / "data.asdf") as af:
+    data = sml.Data(**af["data"]).astype(xp.Tensor, dtype=xp.float32)
+    where = sml.Data(**af["where"]).astype(xp.Tensor, dtype=xp.bool)
+    table = af["table"]
+
+
+# Evaluate model
+with xp.no_grad():
+    helper.manually_set_dropout(model, 0)
+    mpars = model.unpack_params(model(data))
+
+    stream_lik = model.component_posterior("stream", mpars, data, where=where)
+    tot_lik = model.posterior(mpars, data, where=where)
+
+stream_prob = stream_lik / tot_lik
+stream_prob[(stream_prob > 0.4) & (mpars[(f"stream.{WEIGHT_NAME}",)] < -4)] = 0
+# nstream = int(sum(stream_prob > 0.8))
+
+true_stream = table["label"] == "stream"
+ncorrect = sum((stream_prob.numpy() > 0.8) & true_stream) / true_stream.sum() * 100
+
+
+with (paths.output / "mock" / "ncorrect_variable.txt").open("w") as f:
+    f.write(f"{ncorrect:g}")

### 2023-07-11 src/scripts/mpl_colormaps.py

@@ -1,0 +1,99 @@
+"""Matplotlib colormaps."""
+
+from __future__ import annotations
+
+__all__: tuple[str, ...] = ()
+
+import matplotlib as mpl
+import numpy as np
+from matplotlib.colors import LinearSegmentedColormap
+
+# ============================================================================
+
+stream_cmap1 = LinearSegmentedColormap(
+    "Stream1",
+    {
+        "red": np.array(
+            [
+                [0.0, 0.0, 0.0],
+                [0.25, 0.0, 0.0],
+                [0.5, 1.0, 1.0],
+                [0.75, 1.0, 1.0],
+                [1.0, 0.5, 0.5],
+            ]
+        ),
+        "green": np.array(
+            [
+                [0.0, 0.0, 0.0],
+                [0.25, 0.0, 0.0],
+                [0.5, 0.75, 0.75],
+                [0.75, 0.0, 0.0],
+                [1.0, 0.0, 0.0],
+            ]
+        ),
+        "blue": np.array(
+            [
+                [0.0, 0.3, 0.3],
+                [0.25, 1.0, 1.0],
+                [0.5, 1.0, 1.0],
+                [0.75, 0.0, 0.0],
+                [1.0, 0.0, 0.0],
+            ]
+        ),
+        "alpha": np.array(
+            [
+                [0.0, 1.0, 1.0],
+                [0.25, 1.0, 1.0],
+                [0.5, 1.0, 1.0],
+                [0.75, 1.0, 1.0],
+                [1.0, 1.0, 1.0],
+            ]
+        ),
+    },
+)
+mpl.colormaps.register(cmap=stream_cmap1)
+
+# ============================================================================
+
+stream_cmap2 = LinearSegmentedColormap(
+    "Stream2",
+    {
+        "red": np.array(
+            [
+                [0.0, 0.0, 0.0],
+                [0.25, 0.0, 0.0],
+                [0.5, 0.5, 0.5],
+                [0.75, 1, 1],
+                [1.0, 0.5, 0.5],
+            ]
+        ),
+        "green": np.array(
+            [
+                [0.0, 0.0, 0.0],
+                [0.25, 0.0, 0.0],
+                [0.5, 0.75, 0.75],
+                [0.75, 1, 1],
+                [1.0, 0.5, 0.5],
+            ]
+        ),
+        "blue": np.array(
+            [
+                [0.0, 0.3, 0.3],
[…]

### 2023-07-11 src/scripts/pal5/data/1-query_data.py

@@ -1,0 +1,238 @@
+"""Query data from Gaia, crossmatched with PS-1."""
+
+import shutil
+import sys
+from itertools import combinations, pairwise
+from pathlib import Path
+from typing import Any
+
+import asdf
+import astropy.coordinates as coords
+import astropy.units as u
+import matplotlib.pyplot as plt
+import numpy as np
+from astroquery.gaia import Gaia
+from astroquery.utils.tap.model.job import Job
+from showyourwork.paths import user as user_paths
+from tqdm import tqdm
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+from scripts.helper import a_as_b
+from scripts.pal5.frames import pal5_frame as frame
+
+##############################################################################
+# Parameters
+
+snkmk: dict[str, Any]
+try:
+    snkmk = dict(snakemake.params)
+except NameError:
+    snkmk = {"load_from_static": True, "save_to_static": False}
+
+SAVE_LOC = paths.data / "pal5" / "gaia_ps1_xm_polygons.asdf"
+
+if snkmk["load_from_static"] and (paths.static / "pal5").exists():
+    shutil.copyfile(paths.static / "pal5" / "gaia_ps1_xm_polygons.asdf", SAVE_LOC)
+    sys.exit(0)
+
+# Log into Gaia for the query
+GAIA_LOGIN = Path(paths.static / "gaia.login").expanduser()
+Gaia.login(credentials_file=GAIA_LOGIN, verbose=False)
+
+Gaia.ROW_LIMIT = -1  # no limit
+
+##############################################################################
+
+
+PHI1_EDGES = np.arange(-20, 20 + 5, 5) * u.deg
+PHI2_BOUNDS = (-5, 10) * u.deg
+PLX_BOUNDS = (-10, 1) * u.milliarcsecond
+G_R_BOUNDS = (-0.5, 1.2) * u.mag
+GMAG_BOUNDS = (0, 30) * u.mag
+IMAG_BOUNDS = (0, 30) * u.mag
+
+
+gaia_cols = {
+    "source_id": None,
+    "ra": None,
+    "ra_error": None,
[…]

### 2023-07-11 src/scripts/pal5/data/2-combine_data.py

@@ -1,0 +1,206 @@
+"""Combine data fields into one dataset."""
+
+import contextlib
+import json
+import shutil
+import sys
+from typing import Any
+
+import asdf
+import astropy.units as u
+import dustmaps.bayestar
+import gala.coordinates as gc
+import numpy as np
+from astropy.coordinates import ICRS, Distance, SkyCoord
+from astropy.table import QTable, vstack
+from showyourwork.paths import user as user_paths
+from zero_point import zpt
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+from scripts.pal5.frames import pal5_frame as frame
+
+##############################################################################
+# Parameters
+
+snkmk: dict[str, Any]
+try:
+    snkmk = dict(snakemake.params)
+except NameError:
+    snkmk = {"load_from_static": True, "save_to_static": False}
+
+SAVE_LOC = paths.data / "pal5" / "gaia_ps1_xm.asdf"
+
+if snkmk["load_from_static"] and (paths.static / "pal5").exists():
+    shutil.copyfile(paths.static / "pal5" / "gaia_ps1_xm.asdf", SAVE_LOC)
+    sys.exit(0)
+
+##############################################################################
+
+# -----------------------------------------------------------------------------
+# Initial combination
+
+af = asdf.open(paths.data / "pal5" / "gaia_ps1_xm_polygons.asdf", mode="r")
+
+combined = vstack(af.search("polygon-*").nodes, metadata_conflicts="silent")
+
+# correct metadata
+combined.meta.pop("query")
+combined.meta["frame"] = f"{frame.__class__.__module__}.{frame.__class__.__name__}"
+
+# correct unit and data types
+combined["ps1_g"].unit = u.mag
+
+combined.write(SAVE_LOC, format="asdf")
+
+del combined
+af.close()
+
+# -----------------------------------------------------------------------------
+
+table = QTable.read(SAVE_LOC)
+
+# ---------------------------------------
+# Astrometrics
+
[…]

### 2023-07-11 src/scripts/pal5/data/2.5-variable_ndata.py

@@ -1,0 +1,11 @@
+"""Combine data fields into one dataset."""
+
+from astropy.table import QTable
+from showyourwork.paths import user as user_paths
+
+paths = user_paths()
+
+table = QTable.read(paths.data / "pal5" / "gaia_ps1_xm.asdf")
+
+with (paths.output / "pal5" / "ndata_variable.txt").open("w") as f:
+    f.write(f"{len(table):,}")

### 2023-07-11 src/scripts/pal5/data/3-phot_edges.py

@@ -1,0 +1,116 @@
+"""Define the photometric data mask boundaries for GD-1."""
+
+import sys
+from dataclasses import asdict
+
+import asdf
+import astropy.units as u
+import brutus.filters
+import brutus.seds
+import numpy as np
+import shapely
+from astropy.coordinates import Distance
+from astropy.table import QTable
+from matplotlib import pyplot as plt
+from showyourwork.paths import user as user_paths
+
+import stream_mapper.pytorch as sml
+
+paths = user_paths()
+
+try:
+    snkmk = snakemake.params
+except NameError:
+    snkmk = {
+        "diagnostic_plots": True,
+    }
+
+
+##############################################################################
+
+filters = brutus.filters.ps[:-2]  # (g, r)
+
+# Build isochrone
+# From https://arxiv.org/pdf/1910.00592.pdf
+# 11.5 Gyr MIST isochrone with [Fe/H] = -1.3 (Choi et al. 2016) between 20 < g < 23.7
+abs_mags, _, _ = brutus.seds.Isochrone(
+    filters=filters,
+    nnfile=(paths.data / "brutus" / "nn_c3k.h5").resolve(),
+    mistfile=(paths.data / "brutus" / "MIST_1.2_iso_vvcrit0.0.h5").resolve(),
+).get_seds(
+    eep=np.linspace(202, 600, 5000),
+    apply_corr=True,
+    feh=-1.3,
+    dist=10,  # absolute magnitudes
+    loga=np.log10(11.5e9),
+)
+abs_mags = abs_mags[np.all(np.isfinite(abs_mags), axis=1)]
+mags_data = sml.Data(abs_mags, names=tuple(n.removeprefix("PS_") for n in filters))
+
+af = asdf.AsdfFile()
+af["isochrone_data"] = asdict(mags_data)
+af["isochrone_data"].pop("_n2k")
+
+
+# Shift to distance of Palomar 5
+# Palomar 5 has a distance gradient, so it's important that a simple
+# photometric selection is wide enough to capture the full stream, including
+# the more distant parts. See the diagnostic plot below.
+app_mags = abs_mags + Distance(20 * u.kpc).distmod.value
+isochrone = shapely.LineString(app_mags[:, :2])
[…]

### 2023-07-11 src/scripts/pal5/data/3-pm_edges.py

@@ -1,0 +1,27 @@
+"""PM-edges."""
+
+import astropy.units as u
+from astropy.table import QTable
+from showyourwork.paths import user as user_paths
+
+paths = user_paths()
+
+##############################################################################
+
+table = QTable(
+    rows=[
+        ["med_icrs", *(-4, -1) * u.mas / u.yr, *(-4, -1) * u.mas / u.yr],
+    ],
+    names=("label", "pm_ra_min", "pm_ra_max", "pm_dec_min", "pm_dec_max"),
+    dtype=(str, float, float, float, float),
+    units=(None, u.mas / u.yr, u.mas / u.yr, u.mas / u.yr, u.mas / u.yr),
+    meta={
+        "pm_ra_min": "$\\mu_{\\phi_1}\\cos{\\phi_2}$, not reflex corrected",
+        "pm_ra_max": "$\\mu_{\\phi_1}\\cos{\\phi_2}$, not reflex corrected",
+        "pm_dec_min": "$\\mu_{\\phi_2}$, not reflex corrected",
+        "pm_dec_max": "$\\mu_{\\phi_2}$, not reflex corrected",
+    },
+)
+table.add_index("label", unique=True)
+
+table.write(paths.data / "pal5" / "pm_edges.ecsv", overwrite=True)

### 2023-07-11 src/scripts/pal5/data/4-off_field.py

@@ -1,0 +1,25 @@
+"""Off-stream selection."""
+
+import sys
+
+import galstreams
+import numpy as np
+import shapely.geometry as sg
+from showyourwork.paths import user as user_paths
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+from scripts.pal5.frames import pal5_frame
+
+###############################################################################
+
+pal5 = galstreams.MWStreams()["Pal5-PW19"]
+track = pal5.track.transform_to(pal5_frame)
+footprint = sg.LineString(np.c_[track.phi1.degree, track.phi2.degree]).buffer(1.5)
+
+with paths.data / "pal5" / "footprint.npz" as f:
+    np.savez_compressed(f, footprint=footprint.exterior.xy)

### 2023-07-11 src/scripts/pal5/data/5-masks.py

@@ -1,0 +1,278 @@
+"""Setup."""
+
+import shutil
+import sys
+
+import asdf
+import galstreams
+import matplotlib as mpl
+import matplotlib.path as mpath
+import numpy as np
+from astropy import units as u
+from astropy.coordinates import SkyCoord
+from astropy.table import QTable
+from matplotlib import pyplot as plt
+from showyourwork.paths import user as user_paths
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+
+from scripts.pal5.frames import pal5_frame as frame
+
+##############################################################################
+# PARAMETERS
+
+SAVE_LOC = paths.data / "pal5" / "masks.asdf"
+
+try:
+    snkmk = snakemake.params
+except NameError:
+    snkmk = {
+        "load_from_static": True,
+        "save_to_static": False,
+        "diagnostic_plots": True,
+    }
+
+
+if snkmk["load_from_static"] and (paths.static / "pal5").exists():
+    shutil.copyfile(paths.static / "pal5" / "masks.asdf", SAVE_LOC)
+
+    sys.exit(0)
+
+
+##############################################################################
+# Read tables
+
+# Gaia Data
+table = QTable.read(paths.data / "pal5" / "gaia_ps1_xm.asdf")
+
+c_pal5_icrs = SkyCoord(
+    ra=table["ra"], dec=table["dec"], pm_ra_cosdec=table["pmra"], pm_dec=table["pmdec"]
+)
+c_pal5 = c_pal5_icrs.transform_to(frame)
+
+
+##############################################################################
+# Masks
+
+masks_table = QTable()
+
+# =============================================================================
+# Off-stream selection
+# Applying this mask to the data table will remove the off-stream region.
+
+footprint = np.load(paths.data / "pal5" / "footprint.npz")["footprint"]
+
+masks_table["off_stream"] = mpath.Path(footprint.T, readonly=True).contains_points(
+    np.c_[table["phi1"].to_value("deg"), table["phi2"].to_value("deg")]
+)
+
[…]

### 2023-07-11 src/scripts/pal5/datasets.py

@@ -1,0 +1,59 @@
+"""Pal-5 DataSets."""
+
+import asdf
+import astropy.units as u
+import numpy as np
+import torch as xp
+from astropy.table import QTable
+from showyourwork.paths import user as user_paths
+
+import stream_mapper.pytorch as sml
+
+paths = user_paths()
+
+# =============================================================================
+# Load data table
+
+with asdf.open(
+    paths.data / "pal5" / "info.asdf", lazy_load=False, copy_arrays=True
+) as af:
+    sel = af["mask"]
+    names = tuple(af["names"])
+    renamer = af["renamer"]
+
+table = QTable.read(paths.data / "pal5" / "gaia_ps1_xm.asdf")[sel]
+masks = QTable.read(paths.data / "pal5" / "masks.asdf")[sel]
+
+
+# TODO: where should this go?
+# We set photoometrics with G_gaia > 20 to NaN
+completeness_mask = table["gaia_g"] > 20 * u.mag
+table["g0"][completeness_mask] = np.nan
+table["r0"][completeness_mask] = np.nan
+table["i0"][completeness_mask] = np.nan
+table["z0"][completeness_mask] = np.nan
+table["y0"][completeness_mask] = np.nan
+
+
+# =============================================================================
+# Make Data object
+
+data = sml.Data.from_format(
+    table, fmt="astropy.table", names=names, renamer=renamer
+).astype(xp.Tensor, dtype=xp.float32)
+
+# True where NOT missing
+where = sml.Data(~xp.isnan(data.array), names=data.names)
+
+# TODO: it would be nice to keep this as NaN.
+# Need to set missing data to some value, even though it's ignored, for the
+# gradient. Maybe can use zuko's MaskedMLP?
+data.array[~where.array] = xp.asarray(
+    np.repeat(np.nanmedian(data.array, axis=0, keepdims=True), len(data), axis=0)
+)[~where.array]
+
+# =============================================================================
+# Off-stream selection
+# This will select the off-stream region (it's the opposite of the mask).
+
+off_stream = ~masks["off_stream"]

### 2023-07-11 src/scripts/pal5/model.py

@@ -1,0 +1,322 @@
+"""Plot results."""
+
+import sys
+from dataclasses import replace
+
+import asdf
+import torch as xp
+import zuko
+from astropy.table import QTable
+from showyourwork.paths import user as user_paths
+
+import stream_mapper.pytorch as sml
+from stream_mapper.core import WEIGHT_NAME
+from stream_mapper.pytorch.params import ModelParameter, ModelParameters
+from stream_mapper.pytorch.params.bounds import SigmoidBounds
+from stream_mapper.pytorch.params.scaler import StandardLnWidth, StandardLocation
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+
+##############################################################################
+
+pal5_cp = QTable.read(paths.data / "pal5" / "control_points_stream.ecsv")
+
+with asdf.open(paths.data / "pal5" / "info.asdf", mode="r") as af:
+    renamer = af["renamer"]
+    scaler = sml.utils.StandardScaler(**af["scaler"]).astype(
+        xp.Tensor, dtype=xp.float32
+    )
+    all_coord_bounds = {k: tuple(v) for k, v in af["coord_bounds"].items()}
+
+astro_coords = ("phi2", "pmphi1", "pmphi2")
+astro_coord_errs = ("phi2_err", "pmphi1_err", "pmphi2_err")
+astro_coord_bounds = {k: v for k, v in all_coord_bounds.items() if k in astro_coords}
+
+phot_coords = ("g", "r")
+phot_coord_errs = ("g_err", "r_err")
+phot_coord_bounds = {k: v for k, v in all_coord_bounds.items() if k in phot_coords}
+
+coord_names = astro_coords + phot_coords
+coord_bounds: dict[str, tuple[float, float]] = {
+    k: v for k, v in all_coord_bounds.items() if k in coord_names
+}
+
+
+##############################################################################
+# Background
+
+# -----------------------------------------------------------------------------
+# Astrometry
+
+background_phi2_model = sml.builtin.Exponential(
+    net=sml.nn.sequential(
+        data=1, hidden_features=16, layers=2, features=len(coord_names), dropout=0.0
+    ),
+    data_scaler=scaler,
+    coord_names=("phi2",),
+    coord_err_names=("phi2_err",),
[…]

### 2023-07-11 src/scripts/pal5/models/0-info.py

@@ -1,0 +1,140 @@
+"""Pal-5 Model Info."""
+
+from dataclasses import asdict
+
+import asdf
+import numpy as np
+from astropy.table import QTable
+from showyourwork.paths import user as user_paths
+
+# isort: split
+import stream_mapper.pytorch as sml
+
+paths = user_paths()
+
+##############################################################################
+
+try:
+    snkmk = snakemake.params
+except NameError:
+    snkmk = {
+        "pm_mask": "pm_med_icrs",
+        "phot_mask": "phot_15",
+    }
+
+
+##############################################################################
+
+# Read tables
+table = QTable.read(paths.data / "pal5" / "gaia_ps1_xm.asdf")
+masks = QTable.read(paths.data / "pal5" / "masks.asdf")
+
+# Info file
+af = asdf.AsdfFile()
+
+# -----------------------------------------------------------------------------
+# Mask
+# TODO: move this to the data files
+
+sel = (
+    masks["M5"]
+    & masks["things"]
+    & masks["things2"]
+    & masks[snkmk["pm_mask"]]
+    & masks[snkmk["phot_mask"]]
+    & masks["phi1_subset"]
+)
+
+table = table[sel]
+
+# Save mask
+af["mask_info"] = {"pm_mask": snkmk["pm_mask"], "phot_mask": snkmk["phot_mask"]}
+af["mask"] = sel
+
+
+# ----------------------------------------------------
+# Data
+
+af["renamer"] = {
+    "source_id": "id",
+    # ------
+    "ra": "ra",
+    "ra_error": "ra_err",
+    "dec": "dec",
+    "dec_error": "dec_err",
+    "parallax": "plx",
+    "parallax_error": "plx_err",
+    "pmra": "pmra",
+    "pmra_error": "pmra_err",
+    "pmdec": "pmdec",
+    "pmdec_error": "pmdec_err",
+    "ra_dec_corr": "ra_dec_corr",
+    "ra_parallax_corr": "ra_plx_corr",
+    "ra_pmra_corr": "ra_pmra_corr",
+    "ra_pmdec_corr": "ra_pmdec_corr",
+    "dec_parallax_corr": "dec_plx_corr",
+    "dec_pmra_corr": "dec_pmra_corr",
+    "dec_pmdec_corr": "dec_pmdec_corr",
+    "parallax_pmra_corr": "plx_pmra_corr",
[…]

### 2023-07-11 src/scripts/pal5/models/1-control_points_stream.py

@@ -1,0 +1,112 @@
+"""Plot results."""
+
+import sys
+
+import astropy.units as u
+import galstreams
+import numpy as np
+from astropy.coordinates import Distance
+from astropy.table import QTable
+from interpolated_coordinates import InterpolatedSkyCoord
+from matplotlib import pyplot as plt
+from showyourwork.paths import user as user_paths
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+from scripts.pal5.datasets import data, masks
+from scripts.pal5.frames import pal5_frame as frame
+
+###############################################################################
+# Parameters
+
+try:
+    snkmk = snakemake.params
+except NameError:
+    snkmk = {
+        "diagnostic_plots": True,
+    }
+
+
+###############################################################################
+
+table = QTable(
+    np.empty((11, 7)),
+    names=("phi1", "phi2", "w_phi2", "distance", "w_distance", "distmod", "w_distmod"),
+    units=(u.deg, u.deg, u.deg, u.kpc, u.kpc, u.mag, u.mag),
+)
+
+# Adding in regularly spaced points from :mod:`galstreams`
+allstreams = galstreams.MWStreams(implement_Off=True)
+pal5 = allstreams["Pal5-I21"]
+track = pal5.track.transform_to(frame)[::-1]
+itrack = InterpolatedSkyCoord(track, affine=track.phi1)
+
+x = np.linspace(track.phi1.min(), track.phi1.max(), len(table) - 1)
+nans = np.full_like(x.value, np.nan)
+
+#       ([progenitor], [stream])
+table["phi1"] = np.concatenate(([0], x)) << u.deg
+
+# phi2
+table["phi2"] = np.concatenate(([0], itrack(x).phi2)) << u.deg
+table["w_phi2"] = np.concatenate(([0.1], np.full_like(x.value, 1))) << u.deg
+# distance
+table["distance"] = np.concatenate(([np.nan], itrack(x).distance)) << u.kpc
+table["w_distance"] = np.concatenate(([np.nan], np.full_like(x.value, 1.5))) << u.kpc
+# -> distmod
[…]

### 2023-07-11 src/scripts/pal5/models/2-train_background_pm_flow.py

@@ -1,0 +1,170 @@
+"""Train photometry background flow."""
+
+import sys
+from dataclasses import replace
+from typing import Any
+
+import galstreams
+import matplotlib.pyplot as plt
+import numpy as np
+import torch as xp
+import torch.utils.data as td
+from showyourwork.paths import user as user_paths
+from torch import optim
+from tqdm import tqdm
+
+import stream_mapper.pytorch as sml
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+from scripts.pal5.datasets import data, off_stream, where
+from scripts.pal5.frames import pal5_frame as frame
+from scripts.pal5.model import background_pm_model as model_without_grad
+
+# =============================================================================
+# Load Data
+
+snkmk: dict[str, Any]
+try:
+    snkmk = dict(snakemake.params)
+except NameError:
+    snkmk = {
+        "load_from_static": False,
+        "save_to_static": False,
+        "epochs": 2_000,
+        "diagnostic_plots": True,
+    }
+
+if snkmk["load_from_static"] and (paths.static / "pal5").exists():
+    # Load the model from the static directory
+    model_without_grad.load_state_dict(
+        xp.load(paths.static / "pal5" / "background_pm_model.pt")
+    )
+    # Save the model to the data directory
+    xp.save(
+        model_without_grad.state_dict(),
+        paths.data / "pal5" / "background_pm_model.pt",
+    )
+    sys.exit(0)
+
+
+figure_path = paths.scripts / "pal5" / "_diagnostics" / "pm_flow"
+figure_path.mkdir(parents=True, exist_ok=True)
+
+# Training steps save directory
+(paths.data / "pal5" / "pm_flow").mkdir(parents=True, exist_ok=True)
+
+if snkmk["diagnostic_plots"]:
+    allstreams = galstreams.MWStreams(implement_Off=True)
+    pal5PW19 = allstreams["Pal5-PW19"].track.transform_to(frame)
+    pal5I21 = allstreams["Pal5-I21"].track.transform_to(frame)
+
+# =============================================================================
+# Train
+
+# Make a copy of the model with gradients
+# The network is shared with the original model
+model = replace(model_without_grad, with_grad=True)
+
+# Prerequisites for training
[…]

### 2023-07-11 src/scripts/pal5/models/4-likelihoods.py

@@ -1,0 +1,111 @@
+"""Get Likelihoods."""
+
+import copy as pycopy
+import sys
+
+import numpy as np
+import torch as xp
+from astropy.table import QTable
+from showyourwork.paths import user as user_paths
+from tqdm import tqdm
+
+from stream_mapper.core import Params
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+
+from scripts.helper import manually_set_dropout, recursive_iterate
+from scripts.pal5.datasets import data, table, where
+from scripts.pal5.model import model
+
+# =============================================================================
+# Load model
+
+model = pycopy.deepcopy(model)
+model.load_state_dict(xp.load(paths.data / "pal5" / "model.pt"))
+model = model.eval()
+
+
+# =============================================================================
+# Variations
+
+N = 250
+
+stream_weights = np.empty((len(data), N))
+stream_probs = np.empty((len(data), N))
+bkg_probs = np.empty((len(data), N))
+with xp.no_grad():
+    # turn dropout on
+    model = model.train()
+    manually_set_dropout(model, 0.15)
+    # evaluate the model
+    ldmpars = [model.unpack_params(model(data)) for _ in tqdm(range(N))]
+    # mpars
+    dmpars = Params(recursive_iterate(ldmpars, ldmpars[0], reduction=lambda x: x))
+
+    for i, mpars in enumerate(ldmpars):
+        # Postprocess
+        clean = np.ones(len(data), dtype=bool)
+
+        # Weights
+        stream_weights[:, i] = mpars["stream.ln-weight",]
+        stream_weights[~clean, i] = -100
+
+        stream_lnlik = model.component_ln_posterior("stream", mpars, data, where=where)
+        bkg_lnlik = model.component_ln_posterior("background", mpars, data, where=where)
+        # tot_lnlik = model.ln_posterior(mpars, data, where=where)  # TODO
+        tot_lnlik = xp.logaddexp(stream_lnlik, bkg_lnlik)
+
+        # Store, applying the postprocessing
+        bkg_probs[:, i] = xp.exp(bkg_lnlik - tot_lnlik)
+        bkg_probs[~clean, i] = 1
+
[…]

### 2023-07-11 src/scripts/pal5/models/__init__.py

@@ -1,0 +1,1 @@
+"""Pal5 Model."""

### 2023-07-11 src/scripts/pal5/models/helper.py

@@ -1,0 +1,416 @@
+"""Helper function."""
+# ruff: noqa: ERA001
+
+
+import sys
+from math import inf
+
+import asdf
+import galstreams
+import matplotlib as mpl
+import matplotlib.pyplot as plt
+import numpy as np
+import torch as xp
+from astropy.table import QTable
+from matplotlib.gridspec import GridSpec
+from showyourwork.paths import user as user_paths
+
+import stream_mapper.visualization as smlvis
+from stream_mapper.core import WEIGHT_NAME, ModelAPI
+from stream_mapper.pytorch import Data
+from stream_mapper.visualization.background import (
+    exponential_like_distribution as exp_distr,
+)
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+from scripts.helper import color_by_probable_member, p2alpha
+from scripts.mpl_colormaps import stream_cmap1 as cmap1
+from scripts.pal5.datasets import masks
+from scripts.pal5.frames import pal5_frame as frame
+
+# =============================================================================
+# Configuration
+
+# Matplotlib style
+plt.style.use(paths.scripts / "paper.mplstyle")
+
+
+# =============================================================================
+# Load data
+
+# galstreams
+allstreams = galstreams.MWStreams(implement_Off=True)
+pal5I21 = allstreams["Pal5-I21"].track.transform_to(frame)
+pal5PW19 = allstreams["Pal5-PW19"].track.transform_to(frame)
+
+# Control points
+pal5_cp = QTable.read(paths.data / "pal5" / "control_points_stream.ecsv")
+
+# Isochrone data
+with asdf.open(
+    paths.data / "pal5" / "isochrone.asdf", "r", lazy_load=False, copy_arrays=True
+) as af:
+    isochrone_data = Data(**af["isochrone_data"])
+
+# Progenitor
+progenitor_prob = np.zeros(len(masks))
+progenitor_prob[~masks["Pal5"]] = 1
+
+
+# =============================================================================
+
+
+def diagnostic_plot(model: ModelAPI, data: Data, where: Data) -> plt.Figure:
+    """Plot the model."""
+    # Evaluate model
[…]

### 2023-07-11 src/scripts/pal5/plot/data_selection.py

@@ -1,0 +1,252 @@
+"""Train photometry background flow."""
+
+from typing import Any
+
+import asdf
+import astropy.units as u
+import galstreams
+import matplotlib as mpl
+import matplotlib.pyplot as plt
+import numpy as np
+from astropy.table import QTable, Row
+from matplotlib.colors import LogNorm
+from showyourwork.paths import user as user_paths
+
+import stream_mapper.pytorch as sml
+
+paths = user_paths()
+
+###############################################################################
+# Load stuff
+
+# Matplotlib style
+plt.style.use(paths.scripts / "paper.mplstyle")
+
+table = QTable.read(paths.data / "pal5" / "gaia_ps1_xm.asdf")
+masks_table = QTable.read(paths.data / "pal5" / "masks.asdf")
+
+# Load PM edges
+pm_edges = QTable.read(paths.data / "pal5" / "pm_edges.ecsv")
+pm_edges.add_index("label", unique=True)
+
+# Load complete mask
+with asdf.open(
+    paths.data / "pal5" / "info.asdf", lazy_load=False, copy_arrays=True
+) as af:
+    mask = af["mask"]
+
+# Isochrone
+with asdf.open(
+    paths.data / "pal5" / "isochrone.asdf", lazy_load=False, copy_arrays=True
+) as af:
+    isochrone_data = sml.Data(**af["isochrone_data"])
+    isochrone_15 = af["isochrone_15"]
+
+# Apply phi1 mask
+table = table[masks_table["phi1_subset"]]
+mask = mask[masks_table["phi1_subset"]]
+masks_table = masks_table[masks_table["phi1_subset"]]  # has to be last
+
+# shortcut bounds
+p1min = table["phi1"].min().value
+p1max = table["phi1"].max().value
+p2min = table["phi2"].min().value
+p2max = table["phi2"].max().value
+
+# Lit tracks
+_lit1_kw = {"c": "k", "ls": "--", "alpha": 0.6}
+_lit2_kw = {"c": "k", "ls": ":", "alpha": 0.6}
+
+# galstreams
+allstreams = galstreams.MWStreams(implement_Off=True)
+pal5I21 = allstreams["Pal5-I21"].track
[…]

### 2023-07-11 src/scripts/pal5/plot/photometric_background_selection.py

@@ -1,0 +1,104 @@
+"""Train photometry background flow."""
+
+import sys
+
+import matplotlib.pyplot as plt
+import numpy as np
+from matplotlib.ticker import FormatStrFormatter
+from scipy.stats import gaussian_kde
+
+# isort: split
+from showyourwork.paths import user as user_paths
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+from scripts.pal5.datasets import data, off_stream
+
+data = data.astype(np.ndarray)
+
+# =============================================================================
+
+bw_method = 0.05
+background_kde = gaussian_kde(
+    np.c_[data["g"][off_stream], data["r"][off_stream]].T,
+    bw_method=bw_method,
+)
+positions = np.c_[data["g"][~off_stream], data["r"][~off_stream]]
+stream_kde = gaussian_kde(positions.T, bw_method=bw_method)
+
+# =============================================================================
+
+plt.style.use(paths.scripts / "paper.mplstyle")
+
+fig, axs = plt.subplots(2, 1, figsize=(4, 4))
+
+# -------------------------------------------------
+# Phi1-phi2
+
+axs[0].set(
+    xlabel=(r"$\phi_1 \ $ [deg]"),
+    ylabel=(r"$\phi_2 \ $ [deg]"),
+    rasterization_zorder=0,
+)
+axs[0].hist2d(
+    data["phi1"][off_stream],
+    data["phi2"][off_stream],
+    cmap="gray",
+    bins=300,
+    zorder=-10,
+)
+axs[0].plot(
+    data["phi1"][~off_stream],
+    data["phi2"][~off_stream],
+    ls="none",
+    marker=",",
+    ms=1e-2,
+    color="tab:blue",
+    alpha=0.5,
+    zorder=-5,
+)
+axs[0].grid(visible=True, which="both", axis="y")
+axs[0].grid(visible=True, which="major", axis="x")
+
+# -------------------------------------------------
+# Photometric
+
+axs[1].set(
+    xlabel=(r"$g-r \ $ [mag]"),
+    ylabel=(r"$g \ $ [mag]"),
+    aspect="auto",
+    xlim=(0, 0.8),
+    rasterization_zorder=0,
+)
+axs[1].scatter(
+    data["g"][off_stream] - data["r"][off_stream],
[…]

### 2023-07-11 src/scripts/pal5/plot/results_full.py

@@ -1,0 +1,680 @@
+"""Plot the trained pal5 model."""
+
+from __future__ import annotations
+
+import copy as pycopy
+import sys
+
+import galstreams
+import matplotlib.pyplot as plt
+import numpy as np
+import torch as xp
+from astropy.table import QTable
+from matplotlib.cm import ScalarMappable
+from matplotlib.gridspec import GridSpec
+from matplotlib.legend_handler import HandlerTuple
+from matplotlib.lines import Line2D
+from showyourwork.paths import user as user_paths
+from tqdm import tqdm
+
+import stream_mapper.pytorch as sml
+from stream_mapper.core import WEIGHT_NAME
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+from scripts.helper import manually_set_dropout, p2alpha, recursive_iterate
+from scripts.mpl_colormaps import stream_cmap1 as cmap_stream
+from scripts.pal5.datasets import data, masks
+from scripts.pal5.frames import pal5_frame as frame
+from scripts.pal5.model import model
+
+# =============================================================================
+# Load data
+
+# Matplotlib style
+plt.style.use(paths.scripts / "paper.mplstyle")
+
+# Control points
+stream_cp = QTable.read(paths.data / "pal5" / "control_points_stream.ecsv")
+
+# Load model
+model = pycopy.deepcopy(model)
+model.load_state_dict(xp.load(paths.data / "pal5" / "model.pt"))
+model = model.eval()
+
+# Load results from 4-likelihoods.py
+lik_tbl = QTable.read(paths.data / "pal5" / "membership_likelhoods.ecsv")
+stream_prob = np.array(lik_tbl["stream (50%)"])
+stream_lnwgt = np.array(lik_tbl["stream.ln-weight"])
+
+# Progenitor
+progenitor_prob = np.zeros(len(masks))
+progenitor_prob[~masks["Pal5"]] = 1
+
+# galstreams
+allstreams = galstreams.MWStreams(implement_Off=True)
+pal5I21 = allstreams["Pal5-I21"].track.transform_to(frame)
[…]

### 2023-07-11 src/scripts/pal5/plot/smooth_likelihood.py

@@ -1,0 +1,158 @@
+"""Plot pal5 Likelihoods."""
+
+import copy
+import sys
+
+import matplotlib.pyplot as plt
+import numpy as np
+import torch as xp
+from matplotlib.cm import ScalarMappable
+from matplotlib.gridspec import GridSpec
+from scipy import stats
+from showyourwork.paths import user as user_paths
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+from scripts.pal5.datasets import data, masks, where
+from scripts.pal5.model import model
+
+# =============================================================================
+
+# Matplotlib style
+plt.style.use(paths.scripts / "paper.mplstyle")
+
+# Load model
+model = copy.deepcopy(model)
+model.load_state_dict(xp.load(paths.data / "pal5" / "model.pt"))
+model = model.eval()
+
+# Evaluate likelihood
+with xp.no_grad():
+    mpars = model.unpack_params(model(data))
+
+    stream_lnlik = model.component_ln_likelihood("stream", mpars, data, where=where)
+    tot_lnlik = model.ln_likelihood(mpars, data, where=where)
+
+tot_stream_prob = np.exp(stream_lnlik - tot_lnlik)
+
+nddata = data.astype(np.ndarray)
+
+# Cut out the progenitor
+nddata_prog = nddata[~masks["Pal5"]]
+nddata = nddata[masks["Pal5"]]
+
+tot_stream_prob_prog = tot_stream_prob[~masks["Pal5"]]
+tot_stream_prob = tot_stream_prob[masks["Pal5"]]
+
+# =============================================================================
+# Plot
+
+fig = plt.figure(figsize=(6, 4.5))
+
+gs = GridSpec(
+    4,
+    1,
+    figure=fig,
+    height_ratios=(1, 5, 5, 5),
+    hspace=0.15,
+    left=0.085,
+    right=0.98,
+    top=0.94,
+    bottom=0.1,
+)
+cmap = plt.get_cmap()
+
+# ---------------------------------------------------------------------------
+# Colormap
+
+ax0 = fig.add_subplot(gs[0, :])
[…]

### 2023-07-11 src/scripts/pal5/table/control_points.py

@@ -1,0 +1,109 @@
+"""Pal5 control points."""
+
+import sys
+from io import StringIO
+
+import numpy as np
+from astropy.table import QTable, Table
+from astropy.units import Quantity
+from showyourwork.paths import user as user_paths
+
+from stream_mapper.core.typing import Array
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+(paths.output / "pal5").mkdir(exist_ok=True, parents=True)
+
+# =============================================================================
+
+cps_stream = QTable.read(paths.data / "pal5" / "control_points_stream.ecsv")
+
+
+def low_high(vs: Array, es: Array) -> list[str]:
+    """Process to +/- error string."""
+    vs = Quantity(vs).value
+    es = Quantity(es).value
+    return [
+        (
+            "${\\color{gray}\\big(}_{"
+            + lower
+            + "}^{"
+            + ("" if len(lower) == len(upper) else "\\phantom{+}")
+            + upper
+            + "}{\\color{gray}\\big)}$"
+            if not np.isnan(v)
+            else ""
+        )
+        for v, lower, upper in (
+            (v, f"{v - e:0.2f}", f"{v + e:0.2f}") for v, e in zip(vs, es, strict=True)
+        )
+    ]
+
+
+table = Table()
+
+table[r"$\phi_1 \,[\rm{\degree}]$"] = cps_stream["phi1"].value
+table[r"$\phi_2 \,[\rm{\degree}]$"] = low_high(cps_stream["phi2"], cps_stream["w_phi2"])
+table[r"$\mu_{\phi_1} \,[\frac{\rm{mas}}{\rm{yr}}]$"] = low_high(
+    cps_stream["pmphi1"], cps_stream["w_pmphi1"]
+)
+table[r"$\mu_{\phi_2} \,[\frac{\rm{mas}}{\rm{yr}}]$"] = low_high(
+    cps_stream["pmphi2"], cps_stream["w_pmphi2"]
+)
+table.sort(r"$\phi_1 \,[\rm{\degree}]$")
+
+# -----------------------------------------------------------------------------
+# Write the table
+
+preamble = r"""
+\centering
+\setlength{\tabcolsep}{0pt}
+\newcommand\capitem{\\$\phantom{+}\ast$\ }
+"""
+
+caption = r"""%
+    Stream Track Regions Priors for Pal\,5: %
[…]

### 2023-07-11 src/scripts/pal5/table/member_table_full.py

@@ -1,0 +1,163 @@
+"""Plot Pal5 Likelihoods."""
+
+import sys
+
+import numpy as np
+from astropy.table import QTable
+from numpy.lib.recfunctions import structured_to_unstructured
+from showyourwork.paths import user as user_paths
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+from scripts.pal5.datasets import table as data_table
+
+(paths.output / "pal5").mkdir(exist_ok=True, parents=True)
+rng = np.random.default_rng(42)
+
+# =============================================================================
+
+member_liks = QTable.read(paths.data / "pal5" / "membership_likelhoods.ecsv")
+
+sel = member_liks["stream (95%)"] > 0.8
+
+table = QTable()
+table[r"\texttt{source\_id}"] = data_table["source_id"][sel]
+
+# Astrometry
+table[r"$\alpha$ [$\mathrm{{}^{\circ}}$]"] = data_table["ra"][sel].to_value("deg")
+table[r"$\delta$ [$\mathrm{{}^{\circ}}$]"] = data_table["dec"][sel].to_value("deg")
+table[r"$\mu_{\alpha}^{*}$ [$\frac{\rm{mas}}{\rm{yr}}$]"] = [
+    f"${v:0.2f} \\pm {e:0.2f}$"
+    for v, e in zip(
+        data_table["pmra"][sel].to_value("mas/yr"),
+        data_table["pmra_error"][sel].to_value("mas/yr"),
+        strict=True,
+    )
+]
+table[r"$\mu_{\delta}$ [$\frac{\rm{mas}}{\rm{yr}}$]"] = [
+    rf"${v:0.2f} \pm {e:0.2f}$"
+    for v, e in zip(
+        data_table["pmdec"][sel].to_value("mas/yr"),
+        data_table["pmdec_error"][sel].to_value("mas/yr"),
+        strict=True,
+    )
+]
+
+# Photometry
+table["g [mag]"] = [
+    rf"${v:0.2f} \pm {e:0.2f}$"
+    for v, e in zip(
+        data_table["g0"][sel].to_value("mag"),
+        data_table["ps1_g_error"][sel].to_value("mag"),
+        strict=True,
+    )
+]
+table["r [mag]"] = [
+    rf"${v:0.2f} \pm {e:0.2f}$"
+    for v, e in zip(
[…]

### 2023-07-11 src/scripts/pal5/table/member_table_select.py

@@ -1,0 +1,205 @@
+"""Plot Pal5 Likelihoods."""
+
+import sys
+from io import StringIO
+
+import numpy as np
+from astropy.table import QTable
+from numpy.lib.recfunctions import structured_to_unstructured
+from showyourwork.paths import user as user_paths
+
+from stream_mapper.core.typing import Array
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+from scripts.pal5.datasets import table as data_table
+
+(paths.output / "pal5").mkdir(exist_ok=True, parents=True)
+rng = np.random.default_rng(42)
+
+# =============================================================================
+
+member_liks = QTable.read(paths.data / "pal5" / "membership_likelhoods.ecsv")
+
+sel = member_liks["stream (95%)"] > 0.8
+
+# Select some rows
+rows = []
+# we work within the table selection
+strm_mle = member_liks["stream (50%)"][sel]
+# 1 row with highest probability
+rows.append(np.argmax(strm_mle))
+# 5 rows with a probability > 0.9
+prob_idx = np.where(strm_mle > 0.9)[0]
+subselect = rng.choice(np.arange(len(prob_idx)), size=5, replace=False, shuffle=False)
+rows.extend(prob_idx[subselect])
+
+
+def process_lines(vs: Array, es: Array) -> list[str]:
+    """Process to value +/- error string."""
+    return [
+        (rf"${v:0.2f} \pm {e:0.2f}$" if not np.isnan(v) else "---")
+        for v, e in zip(vs, es, strict=True)
+    ]
+
+
+table = QTable()
+# yada yada the source_id column
+table[r"\texttt{source\_id}"] = ["---"] * len(rows)
+
+# Astrometry
+table[r"$\alpha$ [$\mathrm{{}^{\circ}}$]"] = data_table["ra"][sel][rows].to_value("deg")
+table[r"$\delta$ [$\mathrm{{}^{\circ}}$]"] = data_table["dec"][sel][rows].to_value(
+    "deg"
+)
+table[r"$\mu_{\alpha}^{*}$ [$\frac{\rm{mas}}{\rm{yr}}$]"] = process_lines(
+    data_table["pmra"][sel][rows].to_value("mas/yr"),
+    data_table["pmra_error"][sel][rows].to_value("mas/yr"),
+)
[…]

### 2023-07-11 src/scripts/pgm.py

@@ -1,0 +1,201 @@
+"""Plot Stream PGM."""
+
+import sys
+
+import daft
+import matplotlib.pyplot as plt
+from showyourwork.paths import user as user_paths
+
+paths = user_paths()
+
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+
+# Matplotlib style
+plt.style.use(paths.scripts / "paper.mplstyle")
+
+# Colors.
+w_color = {"ec": "tab:blue"}
+m_color = {"ec": "#f89406"}
+
+# =============================================================================
+# Stream Model
+
+# Instantiate the PGM.
+pgm = daft.PGM()
+
+# Astrometric Nodes
+pgm.add_node(
+    "stream_sigma_w,obs", r"$\Sigma_n^{(w)}$", 2, 2, fixed=True, plot_params=w_color
+)
+pgm.add_node(
+    "stream_w,obs", r"$w_n^{\rm obs}$", 3, 2, observed=True, plot_params=w_color
+)
+
+pgm.add_node(
+    "stream_mu_w,model", r"$\mu^{(w)}}$", 2, 3, observed=False, plot_params=w_color
+)
+pgm.add_node(
+    "stream_sigma_w,model", r"$\Sigma^{(w)}$", 3, 3, observed=False, plot_params=w_color
+)
+
+#   Add in the edges.
+pgm.add_edge("stream_sigma_w,obs", "stream_w,obs")
+pgm.add_edge("stream_mu_w,model", "stream_w,obs")
+pgm.add_edge("stream_sigma_w,model", "stream_w,obs")
+
+# Photometric Nodes
+pgm.add_node(
+    "stream_sigma_m,obs", r"$\Sigma_n^{(m)}$", 5, 2, fixed=True, plot_params=m_color
+)
+pgm.add_node(
+    "stream_m,obs", r"$m_n^{\rm obs}$", 4, 2, observed=True, plot_params=m_color
+)
+
+pgm.add_node(
+    "stream_mu_m,model", r"$\mu^{(m)}$", 4, 3, observed=False, plot_params=m_color
+)
+pgm.add_node(
+    "stream_sigma_m,model", r"$\Sigma^{(m)}$", 5, 3, observed=False, plot_params=m_color
+)
+
+#   Add in the edges.
[…]

### 2023-07-28 src/tex/ms.tex
[showyourwork] overleaf sync

--- 2023-07-11 src/tex/ms.tex
@@
 
-            The astrometric track is modeled with a neural network in each phase space dimension, parameterized as a function of $\phi_1$.
+            The astrometric track is modeled with a neural network, encompassing each phase space dimension, parameterized as a function of $\phi_1$.
 The neural network output for a single stream component is the mean location of the stream track in each dimension, $\mbs{\mu}_w(\phi_1 | q_i)$, and its associated covariance matrix $\mbs{\Sigma}_w(\phi_1 | q_i)$.
@@
             \begin{equation}
-                \pdf^{(S)}(\nth{\mbs{w}} | \mbs{\theta}, \phi_{1,i}, q_i) = \mcal{N}\left(\nth{\mbs{w}} | \mbs{\mu}_w\left(\phi_{1,i} | q_i \right), \mbs{\Sigma}_w\left(\phi_{1,i} | q_i \right) \right),
+                \pdf^{(S)}(\nth{\mbs{w}} | \mbs{\theta}, \phi_{1,i}, q_i) = \mcal{N}\big(\nth{\mbs{w}} | \mbs{\mu}_w\left(\phi_{1,i} | q_i \right), \mbs{\Sigma}_w\left(\phi_{1,i} | q_i \right) \big),
             \end{equation}
@@
             \end{equation}
+
+            \todo[inline]{TODO:}
+            \begin{enumerate}
+                \item Not including isochrone parameters, e.g. age and metallicity
+                \item integrating over $\gamma$ the model assumes a PDMF, e.g. Kroupa
+            \end{enumerate}
+
+            By integrating over $\gamma$ the model is not sensitive to
 
@@
             \item A network per model component, e.g. one for the weights, one for the stream track and width, one for the background distribution.
+            \item MLP for the components - lin / tanh + dropout
+            \item Normalizing flow - specific pieces
         \end{enumerate}
+
+        \begin{table}
+            \centering
+            \caption{MLP structure}
+            \begin{tabular}{@{}ccc@{}}
+            \toprule
+            Layer & Shape & Param \# \\
+            \midrule
+            Linear & (1, 3) & 1  \\
+            Tanh & (2, 3) & 1  \\
+            Dropout & (2, 3) & 0  \\
+            \bottomrule
+            \end{tabular}
+        \end{table}
 

### 2023-07-29 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
+            \begin{figure}
+                \script{gd1/plot/photometric_background_selection.py}
+                \centering
+                \includegraphics[width=1\linewidth]{figures/gd1/photometric_background_selection.pdf}
+                \caption{Caption}
+                \label{fig:gd1-photometric_background_selection}
+            \end{figure}
+
             \begin{figure*}[h]
-                \script{gd1/plot/results.py}
+                \script{gd1/plot/results_full.py}
                 \centering
-                \includegraphics[width=1\linewidth]{figures/gd1/results.pdf}
+                \includegraphics[width=1\linewidth]{figures/gd1/results_full.pdf}
                 \caption{CAPTION}
@@
                 \end{itemize}
-                \label{fig:gd1-results}
+                \label{fig:gd1-results-full}
+            \end{figure*}
+
+            \begin{figure*}[h]
+                \script{gd1/plot/results_panels.py}
+                \centering
+                \includegraphics[width=1\linewidth]{figures/gd1/results_panels.pdf}
+                \caption{CAPTION}
+                \label{fig:gd1-results-panels}
             \end{figure*}
@@
             \begin{figure*}
+                \script{gd1/plot/smooth_likelihood.py}
                 \centering
-                \includegraphics[scale=0.8]{figures-not-syw/gd1/gd1_heatmap_density_KDE2.pdf}
+                \includegraphics[scale=0.8]{figures/gd1/smooth_likelihood.pdf}
                 \caption{Caption}

### 2023-08-11 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
+% Change the section names
+\renewcommand{\sectionautorefname}{\S\!}%
+\renewcommand{\subsectionautorefname}{\S\!\!}%
+\renewcommand{\subsubsectionautorefname}{\S\!}%
+\renewcommand{\equationautorefname}{Eq.}
+
+\newcommand{\package}[1]{\textsc{#1}}
+\newcommand{\stream}[1]{#1}
+\newcommand{\dataarchive}[1]{\texttt{#1}}
+
+% Math fonts
 \newcommand{\mrm}[1]{\mathrm{#1}}
@@
 
+% Statistics
+\newcommand{\pdf}{\mcal{P}}
+\newcommand{\cdf}{\mfk{P}}
+\newcommand{\likelihood}{\mcal{L}}
+\newcommand{\prior}{\mcal{\pi}}
+\newcommand{\posterior}{p}
+
+% Labels
+\newcommand{\nth}[1]{{#1}_{\mrm{n}}}  % measurement
+\newcommand{\fth}[1]{{#1}_{\mrm{f}}}  % feature
+\newcommand{\qth}[1]{{#1}_{\mrm{q}}}  % model index
+\newcommand{\unit}[1]{[\text{#1}]}
+
+\newcommand{\cmp}[2]{#2^{(#1)}}
+\newcommand{\smallcomponent}[2]{#2^{\scriptscriptstyle (#1)}}
+\newcommand{\astroM}[1]{\smallcomponent{w}{#1}}
+\newcommand{\photoM}[1]{\smallcomponent{m}{#1}}
+\newcommand{\chemoM}[1]{\smallcomponent{z}{#1}}
+
+\newcommand{\sigobs}{{\sigma_*}}
+
+\newcommand{\JN}[1]{{\textcolor{red}{JN: #1}}}
+
 % Begin!
@@
 % Author list
-\author{Nathaniel Starkman}
-\author{Jacob Nibauer}
+\author{Nathaniel Starkman \& Jacob Nibauer}
 \author{Jo Bovy}
 \author{Jeremy Webb}
+\author{Ana Bonaca}
 
@@
 
-    [Content Here]
-
-    \
-
-    Paper Map:
+    \todo[inline]{Rephrase ---}
+
+    \begin{quotation}
+
+        A stellar stream is the association of stars tidally stripped from a common
+        progenitor system that orbits in an underlying galactic gravitational field
+        \citep{Johnston1998, HelmiWhite1999}. Stream progenitors are gravitationally
+        bound systems, such as satellite dwarf galaxies or star clusters
+        \citep{Odenkirchen2001, Majewski2003}. In the absence of external interactions
+        these systems are stable, though still capable of mass loss driven by internal
+        processes \citep{Hills1975, HeggieHut2003}, e.g. relaxation and binary
+        interactions. Considering external interactions, these progenitor systems may
+        be disrupted: completely, as in the merger events that formed the Galactic
+        stellar halo \citep{Lynden-Bell1967, Searle1978}; or partially, such as tidal
+        disruption forming a stellar stream.
+
+        In the approximation of a smooth galactic gravitational field, the
+        progenitor's extent is limited to the tidal radius. Through processes internal
+        and external, progenitor stars can achieve sufficient energy to bring them
+        beyond the tidal boundary, thus ``escaping'' into the galactic field. Escape
+        primarily occurs at both an inner and outer saddle point of the combined
+        potential -- e.g. the L2 and L3 Lagrange points for a spherical galactic field
+        \citep{Ross1997, Fukushige2000, BinneyTremaine2008}. Generally, the initial
+        phase space position of the escaped star is very similar to that of the
+        progenitor: the configuration position is the tidal boundary and the star has
+        a low peculiar velocity. Since both the escaped star and its progenitor orbit
+        in the same underlying galactic potential and have similar phase space
+        positions their orbits are similar \citep{BinneyTremaine2008}. Given
+        sufficient time the phase space separation will increase and an escaped star
+        will lead or trail the position of the progenitor, depending on the location
+        from which it escaped. Therefore, a collection of tidally stripped stars will
+        form extended structures, aka tails or streams, that are few to thousands of
+        parsecs in length \citep{Johnston1998, HelmiWhite1999, Bovy2014}.
+
+        To be a coherent, observable structure the peculiar velocity dispersion of
+        escaped stars relative to the progenitor must be relatively low, but does vary
+        from system to system. Stars in kinematically hot streams (e.g. from
+        progenitors with larger kinematic dispersions) have more dissimilar orbits
+        from each other and the progenitor than do stars in cold streams, with smaller
+        dispersions \citep{Johnston1998, Hendel2015}. The orbit of a star depends on
+        its phase space position and the gravitational potential; therefore measuring
+        a star's position and velocity and observing its orbit reveals the local
+        potential, which is normally dominated by the Galaxy (primarily the dark
+        matter halo at large distances) \citep{Gibbons2014}. However, an orbit is
+        impractical to observe on human timescales. Cold streams offer a workaround.
+        Like measuring one star at many points in one orbit over an extended period,
+        streams are many stars measured at different points along approximately one
+        orbit at the same time. Therefore stellar streams are one of the most
+        promising means to study the Galactic gravitational potential: the stellar
+        components as well as the dark matter \citep{Johnston2016}.
+
+        On the observational front there has been a large concerted effort in the
+        field to find new stellar streams \citep[for an extensive list of known
+        Galactic streams see][]{Mateu2022}, extend the detected extents of known
+        streams \citep[e.g. for \stream{Palomar 5} alone:][]{Rockosi2002, Ibata2017,
+        Grillmair2006, Carlberg2012, StarkmanEtAl2019}, and increase the general
+        purity of stream catalogs.
+
+    \end{quotation}
+
+    \todo[inline]{--- Rephrase}
+
+    \paragraph{Review of detection methods}
+
+        Identifying streams of globular of clusters is a challenging task.
+Streams are very low signal-to-noise structures spread over comparatively large regions of the sky.
+They live in a vast background of field stars.
+
+        Historically streams were detected by matched-filter techniques
+        % Add citations
+        You took an isochrone and shifted it by a distance modulus until a stream stood out in longitude and latitude as an extended overdensity structure.
+
+        With the advent of Gaia, we gained access to detailed astrometric data. For most streams this
+
+        poses a challenging task due to their intricate and diffuse nature
+        from large-scale surveys is challenging due to the complex and overlapping distributions of stars in different regions of the sky; disentangling members from the vast background of field stars
+
         \begin{enumerate}
-        \item Intro
-        \item Method \begin{enumerate}
-            \item Fig 1: Overall explainer figure that illustrates the method with Neural networks, and norm flow for CMD
-            \item Fig 2: Bayesian graphical model
-            \item Test On Synthetic Stream:
-            \item Some sort of plot demonstrating successful recovery
+            \item Streamfinder \citep{2018MNRAS.477.4063M}. This method requires the potential
+            \item VIA MACHINAE \citep{2022MNRAS.509.5992S}
+            \item Kiyan and Adrian
+            \item Matched Filter
+            \item Gaia stuff: Adrian and Ana and Sara et al
+            \item Uniform Modeling of 12 Stellar stream \citep{PatrickEtAl2022}. Only on phi1, phi2, and CMD. Their CMD method is more sophisticated. Worth discussing.
         \end{enumerate}
-        \item Application / Results \begin{enumerate}
-            \item Test case GD-1: \begin{enumerate}
-                \item CMD norm flow background
-                \item Fig: Stream phi1 phi2 top panel and histograms of each dimension below GD-1
-                \item Some plot in phi1-phi2 that shows density variations
+
+    Review of available data:
+    \begin{enumerate}
+        \item Gaia.
+Streams in Gaia have on-sky positions and proper motions, and parallaxes, though for most streams the parallax errors are prohibitively large.
+Likewise, most streams in Gaia do not have good radial velocity measurements.
+The photometry is generally poor, generally necessitating cross-matching with other datasets.
+        \item S5. This is a much smaller dataset. It has deeper photometry and radial velocity measurements.
     \end{enumerate}
-            \item Test case Pal-5 \begin{enumerate}
-                \item CMD norm flow background
-                \item Fig: Stream phi1 phi2 top panel and histograms of each dimension below Pal 5
-                \item Some plot in phi1-phi2 that shows density variations
-            \end{enumerate}
-        \end{enumerate}
-        \item Conclusion
-        \item Appendix
-    \end{enumerate}
+
+    \paragraph{Paper organization}
+
+        The paper is organized as follows.
+        In \autoref{sec:method} we introduce our method for characterizing stream tracks and computing stellar membership.
+        We discuss the data in \autoref{sub:framing_the_data} and build a probabilistic framework to model the stream and background in \autoref{sub:likelihood_setup}-\autoref{sub:priors}.
+        In \autoref{sec:results} we apply our method,
+        % TODO: rephrase the mock data
+        first to simulated data (\autoref{sub:mock_data}) to demonstrate the model with a known ground truth dataset,
+        then to the stellar streams \stream{GD-1} (\autoref{sub:gd1}) and \stream{Pal\,5} (\autoref{sub:pal5}).
+        We compare our approach to characterizing stellar streams to other methods in \autoref{sec:comparison}.
+        We conclude in \autoref{sec:conclusions}, discussing the results of this work and future directions.
 
@@
 
-    Stellar streams
+    We now introduce our method for characterizing stellar stream tracks and computing stream membership likelihoods from N-D phase-space measurements.
+    % TODO: rephrase following sentence
+    We develop a flexible Bayesian model framework, using Mixture Density Networks, that allows arbitrary numbers of phase-space dimensions to be incorporated in the model and permits missing phase-space observations.
+
+    % \subsection*{}  Conceptual Description
+
+        Below, we offer a concise overview of our approach, followed by a more in-depth technical explanation in subsequent sections.
+
+        \paragraph{one orbit and a single population}
+
+            Stellar streams consist of stars that are tidally disrupted from a progenitor system.
+            To a first approximation, the stars occupy a single orbit, that of their progenitor.
+            Additionally, as stars formed in the progenitor they retain its photometric and chemical characteristics: which for globular clusters means following an isochrone.
+            In this simplistic picture, astrometrically characterizing a stream requires only finding it's orbit.
+Member stars fall directly on the orbit and the isochrone, making membership likelihood determination trivial.
+
+            % Observational errors complicate this picture.
+Instead of a certain membership calculation, we must build a probabilistic model, assigning a likelihood that an observed star falls along the stream's orbit.
+
+        \paragraph{similar orbits and a somewhat noisy population}
+
+            Occupying a single orbit implies that streams remain a point in action space, and having a common origin would thus not become extended structure. This is not true.
+            Differences in stream stars' orbits from the progenitor's arise from various factors including internal dynamics of the progenitor and the host Galactic potential.
+
+            An intrinsic width, in configuration and kinematic space.
+
+            Centered on a track, not an orbit.
+
+            This defines an astrometric phase-space hyper-tube \cite{2018MNRAS.477.4063M}, with a distribution radial to the track.
+
+            Instead of characterizing the stream by its orbit, we characterize it by it's track and the distribution around that track.
+            Computing membership likelihoods now requires fitting the track and distribution. This cannot be
+            done without then also fitting the field of stars in which the stream lives, since the stream 
+            and field cannot be clearly separated.
+
+        \paragraph{gaps orbits and a somewhat noisy population}
+
+            This is still a simplistic picture of streams.
+
+            Perturbations to the Galactic potential, in the form of time evolution and non-axisymmetry, as well as substructure can disrupt the stellar stream. 
+            Even most perturbations don't ruin the idea of the phase-space hypertube. They either drop the mixture weight (rephrase, not yet introduced) to 0 or change the width of the hypertube.
+
+        % TODO: significantly expand on this
+
+        \paragraph{Modeling approach}
+
+            We take a Bayesian approach modeling the stream and background distribution.
+
+            Mixture model are a general formalism for modelling arbitrary conditional density functions.
+
+            In this case we want to model the density function, conditioned on the location along the track.
+
+            However, previously we discussed how stream will vary along the track, with changes in the width and possible gaps.
+            Also observational effects, e.g the distance gradient changes the on-sky width (should this be mentioned earlier?)
+
+            We can take the parameters of the mixture model -- the mixing coefficients and component distribution parameters -- to be general (continuous) functions of the conditioning variable.
+            We do this by modelling the parameters as This is achieved outputs of a feed-forward neural network that takes the conditioning variable as its input.
+This is called a Mixture Density Network (MDN)
+
+    % subsection framing_the_data (end)
+
+    \subsection{Framing the Data} \label{sub:framing_the_data}
+
+        The hypertube idea is connected to orbits.
+        One might think then that a variable like the phase-angle or the arc-length, or any variable that directly sweeps along the stream would be best to use as the conditioning variable.
+        This is not the case for a number of reasons (see \cite{StarkmanEtAl2023} for some discussion on this topic), not least of which is that we do not have any of these quantities.
+We do not know the stream track, it's what we want to know.
+
+        Instead we will approach this in the standard way: by parameterizing the stream along its the longitude -- $w_{\cdot, j\equiv0} \equiv \phi_1$ -- in a stream-oriented reference frame.
+        $\phi_1$ becomes our conditioning variable.
+
+        \begin{quotation}
+            The stream is projected from its initial reference frame, e.g. ICRS
+            \citep{ICRS1997}, into a rotated on-sky frame, with longitude $\phi_1$ and
+            latitude $\phi_2$, such that the stream extends along $\phi_1$. In this frame
+            the stream may be fit by a low-order polynomial as a function of $\phi_1$
+            \citep[e.g.][]{Bonaca2020}. Similar, if more sophisticated, methods swap tools
+            like univariate splines \citep[e.g.][]{Erkal2017, Bonaca2018} for the
+            low-order polynomials. Using a coordinate dimension, here $\phi_1$, as the
+            independent variable works for many streams, as $\phi_1$ sweeps monotonically
+            along the stream. For example \stream{GD-1} is straight for over 80 degrees
+            \citep{Webb2019, Price-Whelan2018}.
+        \end{quotation}
+
+        There are known to be issues with this...
+
+        \begin{quotation}
+            However, this is not true in general: a
+            stream's path can become kinked by subhalo interactions, or curved on the
+            celestial sphere in an observer's reference frame, or like the Magellanic
+            stream wrap multiple times around the Milky Way \citep{Wannier1972}. When a
+            stream track is not a function, methods fitting $\phi_2(\phi_1)$ fail.
+        \end{quotation}
+
+        We leave extending the model framework to phase-wrapped, doubled-backed paths, etc to a future work.
 
@@
         \centering
-        \includegraphics[scale=0.5]{figures-not-syw/DAG_StreamDensity.pdf}
+        \includegraphics[scale=0.5]{static/DAG_StreamDensity.pdf}
         \caption{Fill in.}
@@
         \end{figure}
-
-        We model the stream and background as functions continuous in some affine parameter.
-In principle this parameter can be anything.
-Though it might seem the best parameter is the stream's arc length, the most common, easiest, and practical parameter is the longitude -- $w_{\cdot, j\equiv0} \equiv \phi_1$ -- in some stream-oriented reference frame \citep[for details see][section 2]{2023MNRAS.522.5022S}.
 
@@
         \end{align}
-        where we have assumed that $\nth{\mbs{w}}$ and $\nth{\mbs{m}}$ are conditionally independent, and that the mixture weights $f$ are normalized s.t.
-$\sum_q f(w_{i,0}) = 1$.
-We discuss the mixture weights further in \autoref{sub:mixture_weight}
-
-        Assuming the measurement of each star is independent, the total log-likelihood is a sum over all stars:
+        where we have assumed that $\nth{\mbs{w}}$ and $\nth{\mbs{m}}$ are
+        conditionally independent, and that the mixture weights $f$ are
+        normalized s.t. $\sum_q f(w_{i,0}) = 1$.  We discuss the mixture weights
+        further in \autoref{sub:mixture_weight}.
+
+        Assuming the measurement of each star is independent, the total
+        log-likelihood is a sum over all stars:
         \begin{equation}
@@
 
-        It will prove convenient to distinguish the models for $q=0,1$ as the \textit{background} and \textit{stream} models, respectively. In this notation:
-
-        \begin{multline}
+        It will prove convenient to distinguish the models for $q=0,1$ as the
+        \textit{background} and \textit{stream} models, respectively. In this
+        notation:
+
+        \begin{align}
             \pdf(\nth{\mbs{w}}, \nth{\mbs{m}} | \mbs{\theta})
-            = \\\phantom{+} \ \quad f \quad\ P^{(S)}(\nth{\mbs{w}}|\mbs{\theta}) P^{(S)}(\nth{\mbs{m}}|\mbs{\theta})  \\
-            \quad + (1-f) P^{(B)}(\nth{\mbs{w}}|\mbs{\theta}) P^{(B)}(\nth{\mbs{m}}|\mbs{\theta}), \nonumber
-        \end{multline}
+            =& \phantom{+} \qquad f \phantom{+} P^{(S)}(\nth{\mbs{w}}|\mbs{\theta}) P^{(S)}(\nth{\mbs{m}}|\mbs{\theta}) \\
+            & + (1-f) P^{(B)}(\nth{\mbs{w}}|\mbs{\theta}) P^{(B)}(\nth{\mbs{m}}|\mbs{\theta}), \nonumber
+        \end{align}
 
@@
         \end{equation}
-    Hereafter, when we refer to ``membership probability," Eq.~\ref{eq:membership_prob} provides the formal definition. 
-    %\newpage
+
+        Hereafter, when we refer to ``membership probability,"
+        \autoref{eq:membership_prob} provides the formal definition.
+
+        \paragraph{missing phase-space observations}
+
+            Streams have a diversity of measurement coverage: several have full 6-D astrometrics as well as photometrics and chemical abundances available \citep[e.g.,][]{Koposov2019, 2020A&A...635L...3A, 2022ApJ...928...30L}, while most have partial coverage, lacking feature dimensions.
+            % TODO: terminology ND-phase-space vs feature columns
+            Most streams in \dataarchive{Gaia} {\color{red} [cite]}, for instance, have proper motions but not radial velocities nor reliable parallax measurements.
+Followup surveys, like \dataarchive{S5} {\color{red} [cite]}, add many feature dimensions, however only for a select set of streams.
+Given the diversity of coverage it is important that the likelihood model can deal with missing data.
+
+            The method of treatment of missing data depends on the cause for that data to be missing.
+            Broadly, there are two categories of causes: randomness and systematics.
+            Consider a dataset with all features measured but with a random subset of features masked.
+            One possible approach is to attempt to impute the missing features, then feed the full-featured data to the likelihood model.
+Alternatively, the likelihood model might use only the present features, ignoring those missing.
+If however, features are missing for systematic reasons, then this approach can introduce systematic bias.
+Consider a star too far away to measure it's parallax distance or radial velocity.
+This is a systematic reason and this information should be incorporated into any model as a prior.
+Not doing so, the data imputation approach might predict too-close distances.
+Likewise, using only present features in the likelihood model misses that the star is likely very distant.
+
+            {\color{red} Sentence explaining why we ignore features regardless.}
+            We include a quality flag on our calculations, indicating the number of missing features.
+
+            The per-star likelihood is modelled with a distribution with the same dimensionality as the data vector.
+            For example, a star with a 6D astrometric measurement will be modelled with a full 6D distribution, while a star missing its radial velocity measurement, will be modelled with a 5D dimensionally-reduced form of the 6D distribution.
+Using dimensionally reduced distributions ensure that missing phase-space dimensions do not amplify nor suppress the likelihood.
+
+    % subsection likelihood_setup (end)
 
     \subsection{Determination of the Mixture Weight} \label{sub:mixture_weight}
-        The mixture weight $f_q(w_{i,0})$ as used in Eq.~\ref{eq:general_model} is characterized as the fraction of stars belonging to the mixture component $q$ over an increment $[w_{i,0}, w_{i,0} + \dif{w_{i,0}}]$.
+        The mixture weight $f_q(\phi_1)$ as used in \autoref{eq:general_model} is characterized as the fraction of stars belonging to the mixture component $q$ over an increment $[\phi_1, \phi_1 + \dif{\phi_1}]$.
 Thus, the mixture weight encodes information about the linear density of the stream, which has been shown to depend on substructure in the galaxy (CITE-x).
@@
 
-        In particular, for a given field the distribution of $\phi_1$ coordinates is specified by the set $\{\phi_{1,i}\}_i$.
-A normalizng flow is trained to this dataset, and will satisfy $\int d\phi_1 P_{\phi_i}(\phi_1) = 1$ by construction.
+        In particular, for a given field the distribution of $\phi_1$ coordinates is specified by the set $\{\nth{\phi_{1}}\}_f$.
+A normalizng flow is trained to this dataset, and will satisfy $\int d\phi_1 P_{\phi_f}(\phi_1) = 1$ by construction.
 In order to re-weight the normalizing flow to obtain $N_{\rm tot}(\phi_1)$, we simply rescale $P_{\phi}(\phi_1)$ by $N_{\rm tot,0}$, which is the total number of stars in the field considered.
@@
             The astrometric track is modeled with a neural network, encompassing each phase space dimension, parameterized as a function of $\phi_1$.
-The neural network output for a single stream component is the mean location of the stream track in each dimension, $\mbs{\mu}_w(\phi_1 | q_i)$, and its associated covariance matrix $\mbs{\Sigma}_w(\phi_1 | q_i)$.
+The neural network output for a single stream component is the mean location of the stream track in each dimension, $\astroM{\mbs{\mu}}(\phi_1)$, and its associated covariance matrix $\astroM{\mbs{\Sigma}}(\phi_1)$.
 The probability for the data is then
             \begin{equation}
-                \pdf^{(S)}(\nth{\mbs{w}} | \mbs{\theta}, \phi_{1,i}, q_i) = \mcal{N}\big(\nth{\mbs{w}} | \mbs{\mu}_w\left(\phi_{1,i} | q_i \right), \mbs{\Sigma}_w\left(\phi_{1,i} | q_i \right) \big),
-            \end{equation}
-            where $\mbs{\theta}$ is the set of neural network parameters that define $\mbs{\mu}_w$ and $\mbs{\Sigma}_w$.
-            In the simplest case, we take $\mbs{\Sigma}_w$ to be diagonal, consisting of both intrinsic dispersion for each dimension of $\mbs{w}$ and the data uncertainties added in quadrature.
+                \pdf^{(S)}(\nth{\mbs{w}} | \astroM{\mbs{\theta}}(\nth{\phi_{1}})) = \mcal{N}_F \big(\nth{\mbs{w}} | \astroM{\mbs{\mu}} \left(\nth{\phi_{1}} \right), \astroM{\mbs{\Sigma}} \left(\nth{\phi_{1}}\right) \big),
+            \end{equation}
+            where $\mbs{\theta}$ is the set of neural network parameters that define $\astroM{\mbs{\mu}}$ and $\astroM{\mbs{\Sigma}}$.
+            In the simplest case, we take $\astroM{\mbs{\Sigma}}$ to be diagonal, consisting of both intrinsic dispersion for each dimension of $\mbs{w}$ and the data uncertainties added in quadrature.
 
             In practice, we work with truncated Gaussians, where the truncation is set by the size of the field in each astrometric dimension.
-This ensures that the probability density is zero wherever there is no data.
-Details of the truncated Gaussian are included in \autoref{app:distributions}.
+Details of the truncated Gaussian are included in \autoref{app:sub:normal_distribution}.
+Truncating to the field ensures that the probability density is zero wherever there is no data.
+This has an added benefit of correctly normalizing the Gaussian distribution, which is not compact (has non-zero probability over all space) and would otherwise not integrate to one within the field.
+
+            As a MDN, we implement the Gaussian distribution parameters with a multi-layered feed-forward neural network.
+The number of layers required depends on the maximum dimensionality of the Gaussian, and whether the neural network employs regularization techniques like dropout.
+We use alternating layers of linear and tanh units.
+Details of the network architecture are discussed in \autoref{sub:model_implementation}.
+
+            In the presence of missing phase-space coordinate $f_k$ we reduce the dimensionality of the Gaussian to that of the data-vector.
+Namely, for $\mbs{I}_{\tilde{F}} = \mbs{I}_{F} \backslash f_k$
+            \begin{align}
+                \nth{\tilde{\mbf{w}}} &\mapsto \nth{\tilde{\mbf{w}}} = \{ w_{n,f}\}_{f\in \mbs{I}_{\tilde{F}}}, \nonumber\\
+                \astroM{\mbs{\mu}} &\mapsto \astroM{\tilde{\mbs{\mu}}} = \{ \mu_{f}\}_{f\in\mbs{I}_{\tilde{F}}}, \nonumber\\
+                \astroM{\mbs{\Sigma}} &\mapsto \astroM{\tilde{\mbs{\Sigma}}} = \{ \Sigma_{i,j}\}_{i,j \in \mbs{I}_{\tilde{F}}}, & \nonumber
+                \intertext{such that,}
+                \pdf^{(S)}(\nth{\mbs{w}} & | \astroM{\mbs{\theta}}(\nth{\phi_{1}}))
+                    \mapsto \pdf^{(S)}(\nth{\tilde{\mbs{w}}} | \astroM{\tilde{\mbs{\theta}}} (\nth{\phi_{1}})).
+            \end{align}
 
@@
             We now outline the off-stream astrometric model.
-We take a similar approach to the on-stream astrometric model discussed in \S\ref{ssub:astrometric_model_on_stream}, though we typically do not characterize the backgrounds with a Gaussian distribution.
+We take a similar approach to the on-stream astrometric model discussed in \autoref{ssub:astrometric_model_on_stream}, though we typically do not characterize the backgrounds with a Gaussian distribution.
 Instead, we utilize a range of distributions (i.e., exponential, skew-normal) discussed in \autoref{app:distributions}.
 The parameters of the user-specified background distributions are themselves neural network outputs, such that any $\phi_1$ ``slice" of the background should be characterized by some analytic density, but the evolution of the backgrounds with $\phi_1$ can be complex.
-
-            Let $\mbs{\theta}_{B,j}(\phi_1)$ represent the neural network which outputs a vector of parameters characterizing the background distribution at a given $\phi_1$ for astrometric dimension $j$.
-The number of outputs for the background model is equal to $\Sigma_{j>0} \mathrm{dim}\left(\mbs{\theta}_{B,j}\right)$ (where $j=0$ corresponds to $\phi_1$, which we do not model).
-At a given $\phi_1$, the probability density for the astrometric dimension $j>0$ is $\pdf^{(B)}_j\left(\mbs{w}_{n,j} | \mbs{\theta}, \mbs{\theta}_{B,j}, \phi_1 \right)$.
+Details of the network architecture are discussed in \autoref{sub:model_implementation}.
+
+            Let $\fth{\cmp{B}{\mbs{\theta}}}(\phi_1)$ represent the neural network which outputs a vector of parameters characterizing the background distribution at a given $\phi_1$ for astrometric dimension $f$.
+The number of outputs for the background model is equal to $\mathrm{dim}\left(\fth{\cmp{B}{\mbs{\theta}}}\right)$ (where $f=0$ corresponds to $\phi_1$, which we do not model).
+At a given $\phi_1$, the probability density for the astrometric dimension $f>0$ is $\fth{\pdf^{(B)}}\left(\mbs{w}_{n,f} | \fth{\cmp{B}{\mbs{\theta}}}(\phi_1) \right)$.
 We treat each background component as independent, allowing us to write the likelihood as a product over the astrometric dimensions:
-            \begin{equation}
-                \pdf^{(B)}\left(\mbs{w}_n | \mbs{\theta}, \phi_1 \right) = \prod_{j>0} \pdf_j^{(B)}\left(\mbs{w}_{n,j} | \mbs{\theta}, \mbs{\theta}_{B,j}, \phi_1 \right).
-            \end{equation}
+            \begin{equation} \label{eq:astrometric_model_off_stream_probability}
+                \pdf^{(B)}\left(\nth{\mbs{w}} | \mbs{\theta}(\phi_1) \right) = \prod_{f\in \mbs{I}_{\tilde{F}}} \pdf_f^{(B)}\left(\mbs{w}_{n,f} | \fth{\cmp{B}{\mbs{\theta}}}(\phi_1) \right).
+            \end{equation}
+            Where $\mbs{I}_{\tilde{F}}$ is the set of indices of the features, omitting missing phase space dimensions.
 
@@
                 \item integrating over $\gamma$ the model assumes a PDMF, e.g. Kroupa
+                \item generic details of neural network, e.g Table 1
+                \item introducing parallax
+                \item how we reduce dimensionality.
             \end{enumerate}
-
-            By integrating over $\gamma$ the model is not sensitive to
 
@@
 
+            \todo[inline]{TODO:}
+            \begin{enumerate}
+                \item Overview of the architecture
+                \item How one would reduce the dimensionalty.
+            \end{enumerate}
+
     % subsection likelihood_setup (end)
@@
             \includegraphics[width=1\linewidth]{figures/mock/results.pdf}
-            \caption{Caption: TO-DO need to show this with a ground truth (e.g. show true weight in top panel).}
+            \caption{Caption: .}
+            TODO:
+            \begin{enumerate}
+                \item Get rid of the dropout in the plot
+                \item the linear density in the stream-fraction plot
+            \end{enumerate}
             \label{fig:mock_data_result}
@@
 
-\section{Model Implementation}
-
-    \subsection{Network Architecture}
-
-        \begin{enumerate}
-            \item A network per model component, e.g. one for the weights, one for the stream track and width, one for the background distribution.
-            \item MLP for the components - lin / tanh + dropout
-            \item Normalizing flow - specific pieces
-        \end{enumerate}
-
-        \begin{table}
-            \centering
-            \caption{MLP structure}
-            \begin{tabular}{@{}ccc@{}}
-            \toprule
-            Layer & Shape & Param \# \\
-            \midrule
-            Linear & (1, 3) & 1  \\
-            Tanh & (2, 3) & 1  \\
-            Dropout & (2, 3) & 0  \\
-            \bottomrule
-            \end{tabular}
-        \end{table}
-
-    \subsection{Astrometric Stream}
-
-        \subsubsection{Track Region Prior} \label{sub:track_region_prior}
+    \subsection{Priors} \label{sub:priors}
+
+        \subsubsection{Bounding Boxes}
+
+        \subsubsection{Region Prior} \label{sub:track_region_prior}
+
+            Region priors encourage the model to pass through a user-defined control region, while also remaining compatible with the data.
 
@@
 
-            % The total log-probability over all the
-
-            % \begin{equation}
-            %     \ln\mcal{L}\left(\{(\nth{\mbs{w}},\nth{\mbs{m}})\} | \mbs{\theta}\right) = \sum_i  \pdf(\nth{\mbs{w}}, \nth{\mbs{m}} | \mbs{\theta}).
-            % \end{equation}
-
-        % subsection track_region_prior
+    \subsection{Linking Coordinates: Combining the Distance Modulus with the Parallax Track}
+
+        \todo[inline]{TODO:}
+        \begin{enumerate}
+            \item Discuss how to connect the distance modulus to the parallax.
+            \item First-order error propagation to set width DM to width parallax.
+        \end{enumerate}
+
+    \subsection{Model Implementation, aka the code} \label{sub:model_implementation}
+
+        \todo[inline]{TODO:}
+
+        \begin{enumerate}
+            \item A network per model component, e.g. one for the weights, one for the stream track and width, one for the background distribution.
+            \item MLP for the components - lin / tanh + dropout
+            \item Normalizing flow - specific pieces
+            \item Architecture in the Appendix
+        \end{enumerate}
+
+        \begin{table}
+            \centering
+            \caption{MLP structure}
+            \begin{tabular}{@{}rrcl@{}}
+            \toprule
+            & Layer & Shape & Param \# \\
+            \midrule
+            & Linear & (None, 1, F) & 1  \\
+            & Tanh & (None, 1, F) & 1  \\
+            & Dropout & (None, 1, F) & 0  \\
+            & Linear & (None, 1, F) & 1  \\
+            \bottomrule
+            \end{tabular}
+        \end{table}
+
+        Dropout layers were used to prevent network co-adaptation and over-fitting.
+Droput works by randomly zeroing out nodes in the network, decreasing the importance of single nodes versus emergent patterns across the  network.
 
@@
     In this section we present an application of our model to a synthetic stream with known ground truths, and demonstrate the model's ability to characterize stream density variations and membership probabilities in an unsupervised manner.
-We then apply the method to real stellar streams in \S-X (GD-1) and \S-Y (Pal-5).
-
-    \subsection{Test on a Synthetic Stream}\label{sub:simple_mock_data}
+We then apply the method to real stellar streams in \autoref{sub:gd1} and \autoref{sub:pal5}.
+
+    \subsection{Test on a Synthetic Stream} \label{sub:mock_data}
 
@@
 
-        The result of applying our density model to the synthetic data is illustrated in Fig.~\ref{fig:mock_data_result}.
+        The result of applying our density model to the synthetic data is illustrated in \autoref{fig:mock_data_result}.
 The top panel shows the weight parameter that controls membership probability as a function of $\phi_1$.
@@
 
-        In the bottom two rows of Fig.~\ref{fig:mock_data_result} we illustrate the synthetic data color-coded by stream membership probability (top) and background membership probability (background) for different $\phi_1$ slices.
+        In the bottom two rows of \autoref{fig:mock_data_result} we illustrate the synthetic data color-coded by stream membership probability (top) and background membership probability (background) for different $\phi_1$ slices.
 Importantly, the photometric portion of the mixture model successfully identifies the stream in magnitude space, showing a high stream membership probability where the stream is present, and a low probability ($\sim 0$) where the stream is absent.
@@
 
-        We now apply our density modeling approach to the stellar stream GD-1. We discuss the data selection in \S\ref{ssub:gd1_data} and results in \S\ref{ssub:trained_gd1}.
+        We now apply our density modeling approach to the stellar stream GD-1. We discuss the data selection in \autoref{ssub:gd1_data} and results in \autoref{ssub:trained_gd1}.
 
@@
 
-            We visualize the performance of our model in identifying stream stars and characterizing the astrometric background with Fig.~\ref{fig:gd1-background}.
-The top panel shows the stream in $\phi_1$, $\phi_2$ coordinates, color-coded by membership probability (derived from Eq.~\ref{eq:membership_prob}).
+            We visualize the performance of our model in identifying stream stars and characterizing the astrometric background with \autoref{fig:gd1-results-full} and \autoref{fig:gd1-results-panels}.
+In \autoref{fig:gd1-results-full} The top panel shows the stream in $\phi_1$, $\phi_2$ coordinates, color-coded by membership probability (derived from \autoref{eq:membership_prob}).
 The following three rows represent background distributions in $\phi_2, \mu_{\phi_1}, \rm{\ and} \ \mu_{\rm phi_2}$, respectively taken at different $\phi_1$ increments centered on the red lines.
@@
 We find that the backgrounds are typically well characterized by the distributions adopted (described in \S-x).
-We can also see from Fig.~\ref{fig:gd1-background}
+We can also see from \autoref{fig:gd1-results-panels}
             that the stream and spur components appear to be well characterized.
 
-            Our ability to recover the stream is demonstrated further in Fig.~\ref{fig:gd1-astrometrics}.
+            Our ability to recover the stream is demonstrated further in \autoref{fig:gd1-results-full}.
 In this figure, we only plot stars if their membership probability is greater than \JN{X}.
@@
             Our model also fits the distribution of stream stars in the CMD.
-These fits are illustrated in Fig.~\ref{fig:gd1-cmds}, where the CMD for the population in a given $\phi_1$ band is plotted, color-coded by stream membership probability.
+These fits are illustrated in \autoref{fig:gd1-results-panels}, where the CMD for the population in a given $\phi_1$ band is plotted, color-coded by stream membership probability.
 For the on-stream regions, the isochrone appears to provide a decent description of the stream, though there is room for further improvements (discussed in \S-x).
@@
 This allows us to obtain a distance modulus at each $\phi_1$ along the stream.
-The distance modulus track and (converted) distance track are illustrated in Fig.~\ref{fig:gd1-distance_modulus}.
+The distance modulus track and (converted) distance track are illustrated in \autoref{fig:gd1-results-full}.
 The left panel shows the distance modulus (in magnitudes), while the right shows the corresponding distance track.
@@
                     \item Add plot of the stream linear density
-                    \item Reduce the distance between the plot sections
                     \item Color palette for the spur
                     \item more subtle stream MLE path
-                    \item weight 5th and 95th percentile distribution
                     \item rerun model with larger pmphi2 sigma
@@
                 \caption{CAPTION}
+                TODO:
+                \begin{itemize}
+                    \item Add plot of the stream linear density
+                    \item Color palette for the spur
+                    \item add the isochrones to the cmd plots
+                \end{itemize}
                 \label{fig:gd1-results-panels}
@@
 
-            \input{output/gd1_members.tex}
+            \variable{output/gd1_members.tex}
 
@@
 
+    \subsection{Palomar 5} \label{sub:pal5}
+
+        Content
+
+    % subsection pal5 (end)
+
 % section results (end)
 
+\section{Comparison to Other Methods} \label{sec:comparison}
+
+    \subsection[STREAMFINDER]{\cite{2018MNRAS.477.4063M}}
+
+    % subsection streamfinder (end)
+
+    \subsection{VIA MACHINAE}{\cite{2022MNRAS.509.5992S}}
+
+    % subsection via_machinae (end)
+
+    \subsection[Uniform Modeling of 13 Stellar Streams]{\cite{PatrickEtAl2022}}
+
+    % subsection uniform_modeling_of_13_stellar_streams (end)
+
+\section{Conclusions} \label{sec:conclusions}
+
+% section comparison_to_other_methods (end)
+
 \section{acknowledgements}
@@
 
-    \url{https://github.com/nstarman/stellar_stream_density_ml_paper/}
+    \GitHubURL
+
+    \todo[inline]{reword}
+    "This study was carried out using the reproducibility software
+    \href{https://github.com/showyourwork/showyourwork}{\showyourwork}
+    \citep{Luger2021}, which leverages continuous integration to
+    programmatically download the data from
+    \href{https://zenodo.org/}{zenodo.org}, create the figures, and
+    compile the manuscript. Each figure caption contains two links: one
+    to the dataset stored on zenodo used in the corresponding figure,
+    and the other to the script used to make the figure (at the commit
+    corresponding to the current build of the manuscript). The git
+    repository associated to this study is publicly available at
+    \url{https://github.com/mathren/CE_accretors}, and the release
+    v.2.1 allows anyone to re-build the entire manuscript. The datasets
+    are stored at \url{https://doi.org/10.5281/zenodo.7343715}, including
+    the template setup to recreate them using MESA (version 15140 and
+    the software development kit \texttt{x86\_64-linux-20.12.1}) and
+    the scripts used to produce the figures."
+
+    \paragraph{Software (alphabetical)}
+
+        \package{asdf} \citep{Greenfield2015},
+        \package{astropy} \citep{Astropy2013, Astropy2018, Astropy2022},
+        \package{astroquery} \citep{Astroquery2019},
+        \package{Matplotlib} \citep{Hunter2007},
+        \package{NumPy} \citep{Harris2020},
+        \package{Pytorch} \citep{Pytorch2019},
+        \package{SciPy} \citep{Scipy2020},
+
+\section*{Data Availability} \label{sec:data_availability}
+
+    This study was carried out using the reproducibility software
+    \href{https://github.com/showyourwork/showyourwork}{\showyourwork}
+    \citep{Luger2021}, which uses continuous integration to
+    programmatically download the data, perform the analyses, create the
+    figures, and compile the manuscript. Each figure caption contains two links:
+    one to the dataset used in the corresponding figure, and the other to the
+    script used to make the figure. The datasets are stored at
+    \todo[inline]{zenodo url}. The git repository associated
+    with this study is publicly available at \GitHubURL.
+
+% section data_availability (end)
 
@@
 
-    \begin{itemize}
-        \item Full Data
-            \begin{itemize}
-                \item $\mbf{D} \in \mbb{R}^{(N, F^{(d)})}$ is the data matrix
-                \item indexed with index sets $\mrm{n} \in \mbs{I_N} \equiv \{0, ..., N\} \in \mbb{Z^+}$ for the measurements and $\mrm{f} \in \mbs{I_F}  \equiv \{0, ..., F^{(d)}\} \in \mbb{Z^+}$ for the features.
-                \item $d_{\mrm{nf}}$ elements of the $n$-th measurement of the $f$-th feature.
-                \item $\nth{\mbs{d}}$ row-vector of all features.
-                \item  $\mbf{D}$ is split into astrometric and photometric coordinates $\mbf{D} = \{\mbf{W}, \mbf{M}\}$, in that order of features.
-$F^{(w)} + F^{(m)} = F$, where $F^{(w)}, F^{(m)}$ are defined below.
-            \end{itemize}
-        \item Astrometric Data
-            \begin{itemize}
-                \item $\mbf{W} \in \mathbb{R}^{(N, F^{(w)})}$ is the astrometric data matrix
-                \item indexed with index the same $N$ as the full data and $\mrm{f} \in \mbs{I_{F^{(w)}}} \equiv \{0, ..., F^{(w)}\} \in \mathbb{Z^+}$ for the astrometric features, where $F^{(w)} \leq F$.
-                \item $w_{\mrm{nf}}$ elements of the $n$-th measurement of the $f$-th astrometric feature.
-                \item $\nth{\mbs{w}}$ row-vector of all astrometric features.
-                \item The first (index 0) feature column, $w_{\cdot,0}$ of $\mbf{W}$ (and $\mbf{D}$) is $\phi_1$.
-            \end{itemize}
-        \item Photometric Data
-            \begin{itemize}
-                \item $\mbf{M} \in \mathbb{R}^{(N, F^{(m)})}$ is the photometric data matrix
-                \item indexed with index the same $N$ as the full data and $\mrm{f} \in \mbs{I_{F^{(m)}}} \equiv \{0, ..., F^{(m)}\} \in \mathbb{Z^+}$ for the photometric features, where $F^{(m)} \leq F$.
-                \item $m_{\mrm{nf}}$ elements of the $n$-th measurement of the $f$-th photometric feature.
-                \item $\nth{\mbs{m}}$ row-vector of all photometric features.
-            \end{itemize}
-        \item Mixture Models
-            \begin{itemize}
-                \item index set over the models: $\mrm{q} \in \mbs{I_Q} \equiv \{0, ..., Q \} \in \mbb{Z^+}$ 
-            \end{itemize}
-        \item $\pdf(...)$ is a PDF and $\cdf(...)$ it's CDF.
-        % \item $\pi(...)$ is a prior
-        \item $\mcal{L}$ is a likelihood.
-    \end{itemize}
-
-\section{Theory of Mixture Density Networks (MDNs} \label{app:theory_of_mixture_density_networks}
-
-    Mixture Density Networks (MDNs) are a generalization over mixture models, where the weights and model parameters may be functions, rather than scalars, as in normal mixture models.
-Generalizing to functional parameters allows the model to capture variation over those parameters that is not possible with scalar-valued models.
-
-    For the MDN we take $d_{\cdot, 0} \equiv x_{\cdot}$ (indexed from 0), which is the first feature column of $\mbf{D}$, as the `independent' coordinate over which the MDN parameters are functions.
-In the context of streams $d_{\cdot, 0} = x$ is $\phi_1$ the longitude coordinate in a reference frame rotated such that the stream is aligned along $\phi_1$.
+    In this work we use multiple data sets and a variety of mathematical tools to analyze the data, including machine learning algorithms and statistical models.
+    For clarity and to connect related components of the models used in this work, a consistent mathematical notation is crucial. Here we establish the notation and symbols used throughout this work.
+    \autoref{table:symbol_table} enumerates the symbols used for the statistical models and the different datasets, e.g. distinguishing astrometric from photometric data.
+
+    \begin{table}
+    \centering
+    \caption{Symbol Table}
+    \label{table:symbol_table}
+    \begin{tabular}{p{0.35\linewidth} p{0.6\linewidth}}
+    Symbol                         & Explanation \\
+    \toprule
+    % -----------------------------------------------------------------------------
+    \\
+    \multicolumn{2}{l}{\textbf{Datasets}:} \\
+    \midrule
+    % -------------------------------------------------
+    \multicolumn{2}{l}{\textbf{Full Data}:}  \vspace{5pt} \\
+    $\mbf{X} \in \mbb{R}^{(N, F+1)}$ & Full dataset.  \\
+    $N$ & The number of independent measurements (aka stars) in the dataset.  \\
+    $F$ & The number of measured features, e.g.
+$(\alpha, \delta, \varpi, \mu_{\alpha^*}, \mu_\delta, v_r, g, r)$,  not including the the `independent' feature over which the others are conditioned.
+\\
+    $\mrm{n} \in \mbs{I_N} \equiv \{1, ..., N\} \in \mbb{Z^+}$ & Index into the set of measurements $\mbf{X}$. \\
+    $\mrm{f} \in \mbs{I_F}  \equiv \{1, ..., F\} \in \mbb{Z^+}$ & Index into the set of features of $\mbf{X}$. $ f=0$ is the `independent' feature.\\
+    $x_{\mrm{n,f}}$ & $n$-th measurement of the $f$-th feature of $\mbf{X}$. \\
+    $\nth{\mbs{x}}$ & $n$-th row-vector of all features. \\
+    % -------------------------------------------------
+    \\
+    \multicolumn{2}{l}{\textbf{Astrometric Data}:}  \vspace{5pt} \\
+    $\mbf{W} \in \mathbb{R}^{(N, F_w + 1)}$ & Full astrometric dataset. \\
+    $\mrm{f_w} \in \mbs{I_{F_w}} \equiv \{1, ..., F_w\} \in \mathbb{Z^+}$ & Index into the set of astrometric features. $f_w = 0$ is the `independent' feature.\\
+    $w_{\mrm{n,f_w}}$ & $n$-th measurement of the $f_w$-th feature of $\mbf{W}.$\\
+    $\nth{\mbs{w}}$ & $n$-th row-vector of all astrometric features. \\
+    $\phi_1 \equiv w_{\cdot,0}$ & The `independent' (index 0) feature column on which the models are conditioned.\\
+    % -------------------------------------------------
+    \\
+    \multicolumn{2}{l}{\textbf{Photometric Data}:}  \vspace{5pt} \\
+    $\mbf{M} \in \mathbb{R}^{(N, F_m)}$ & Full photometric dataset. \\
+    $\mrm{f_m} \in \mbs{I_{F_m}} \equiv \{1, ..., F_m\} \in \mathbb{Z^+}$ & Index into the set of photometric features. \\
+    $m_{\mrm{n,f_m}}$ & $n$-th measurement of the $f_m$-th feature of $\mbf{M}$. \\
+    $\nth{\mbs{m}}$ & $n$-th row-vector of all features. \\
+    % -----------------------------------------------------------------------------
+    \\
+    \multicolumn{2}{l}{\textbf{Statistics}:} \\
+    \midrule
+    $\pdf(...)$ & The PDF of the distribution. \\
+    $\cdf(...)$ & The CDF corresponding to $\pdf(...)$. \\
+    $\mbs{\theta} = \{\theta_f\}_f$ & The vector of a distribution's parameters. \\
+    $\mcal{L}(\nth{\mbf{x}}, \mbs{\theta}(\phi_1))$ & The likelihood of the data given the parameters. \\
+    $Q$ & The number of models in a mixture model. \\
+    $\mrm{q} \in \mbs{I_Q} \equiv \{1, ..., Q \} \in \mbb{Z^+}$ & Index into the set of $Q$ models. \\
+    % -------------------------------------------------
+    \\
+    \end{tabular}
+    \end{table}
+
+    We use $\tilde{F}$ to indicate that there a missing features, e.g. radial velocities.
+    The index set $\mbs{I}_F \mapsto \mbs{I}_{\tilde{F}} = \{1, ..., k-1, k+1, ... \}$ where $k$ is the index of the missing feature.
+
+% section notation (end)
+
+\section{Theory of Mixture Density Networks (MDNs)} \label{app:theory_of_mixture_density_networks}
+
+    Mixture models (MMs) are a statistical method to represent a population as a set of a sub-populations specified by probability distributions.
+These distributions are characterized by their parameters and mixture by a corresponding set of mixture weights.
+Mixture Density Networks (MDNs)
+    are a machine learning method to combine a MM with neural networks, increasing the flexibility of the model.
+An MDN replaces the scalar distribution parameters of the MM with neural networks, allowing the distribution parameters and mixture weights to vary as smooth functions \citep{Bishop1994}.
+Functional parameters allows the model to capture variation over those parameters that is not possible with scalar-valued models.
+Moreover, by using neural networks the inferred functional forms are ``model-free" and driven entirely by the data.
+
+    % Quote from https://mikedusenberry.com/mixture-density-networks
+    % A mixture density network (MDN) is an interesting model formalism built within the general framework of neural networks and probability theory for working on supervised learning problems in which the target variable cannot be easily approximated by a single standard probability distribution.
+Essentially an MDN allows one to model a conditional probability distribution as a mixture of distributions, in which the individual distributions and the corresponding mixture coefficients are parameterized by functions of the inputs
+
+    For the MDN we take $x_{\cdot, 0} \equiv x_{\cdot}$ (indexed from 0), which is the first feature column of $\mbf{X}$, as the `independent' coordinate over which the MDN parameters are conditioned.
+In the context of streams $x_{\cdot, 0} \equiv \phi_1$ is the longitude coordinate in a reference frame rotated such that the stream is aligned along $\phi_1$.
 
@@
     \begin{equation} \label{eq:general_mixture_network}
-        \pdf(\nth{\mbs{d}} | \mbs{\theta}(\nth{x}))
-        = \sum_{\mrm{q} \in \mbs{I_Q}} \ \qth{f}(\nth{x}) \qth{P}(\nth{d}|\qth{\mbs{\theta}}(\nth{x}),q\!=\!\mrm{q})
-    \end{equation}
-    The mixture weights $\qth{f}$ are normalized s.t.
-
-    \begin{equation}
-        \sum_{\mrm{q}} \qth{f}(\nth{x}) = 1 \qquad \forall \nth{x}
+        \pdf(\nth{\mbs{x}} | \mbs{\theta}(\phi_1))
+        = \sum_{\mrm{q} \in \mbs{I_Q}} \ \qth{f}(\phi_1) \qth{P}(\nth{x}|\qth{\mbs{\theta}}(\phi_1),q\!=\!\mrm{q})
+    \end{equation}
+    The mixture coefficients $\qth{f}$ are normalized s.t.
+    \begin{equation}
+        \sum_{\mrm{q}} \qth{f}(\phi_1) = 1 \qquad \forall \phi_1
     \end{equation}
@@
     \begin{equation}
-        f_{\mrm{q} = b}(\nth{x}) = 1 - \sum_{\rm{q}\in \mbs{I_Q}\backslash b} \qth{f}(\nth{x})
+        f_{b}(\phi_1) = 1 - \sum_{\rm{q}\in \mbs{I_Q}\backslash b} \qth{f}(\phi_1)
     \end{equation}
@@
 
-    Assuming the measurement of each datum is independent, the total log-likelihood is a sum over all data:
-    \begin{equation}
-        \ln\mcal{L}\left(\mbf{D} | \mbs{\theta}(\mbs{x})\right) = \sum_{n \in \mbs{I_N}} \ln \left[ \sum_{q\in\mbs{I_Q}} \qth{P}\left(\nth{\mbs{d}} | \qth{\mbs{\theta}}(x_n)\right) \right].
+    Assuming the measurement of each datum is independent, the likelihood is a sum over all data:
+    \begin{equation}
+        \mcal{L}\left(\mbf{x}_n | \mbs{\theta}(\phi_1)\right) = \sum_{q\in\mbs{I_Q}} \qth{P}\left(\nth{\mbs{x}} | \qth{\mbs{\theta}}(\phi_1)\right).
     \end{equation}
@@
 
-    \todo[inline]{TODO}
+    \begin{equation}
+        \ln\posterior\left(\mbf{X} | \mbs{\theta}(\mbs{x})\right) = \ln\mcal{L}\left(\mbf{X} | \mbs{\theta}(\mbs{x})\right) +  \sum_{n \in \mbs{I_N}} \ln \left[ \sum_{q\in\mbs{I_Q}} \qth{\prior}\left(\qth{\mbs{\theta}}(\mbf{x}_n)\right) \right].
+    \end{equation}
 
@@
     \vspace{10pt}
-    \subsection{Normal Distribution}
+    \subsection{Normal Distribution} \label{app:sub:normal_distribution}
 
@@
         \autoref{eq:general_convolution} establishes that convolutions of PDFs are an integral operation.
-Integrals are often challenging and it is useful to recast a problem in different terms.
+Integrals are often intractable, but the problem is solvable if recast in different terms.
 Rather that working with PDFs of distributions we can instead consider the moment-generating function (MGF) corresponding to the PDF's distribution.
 Like the PDF, the MGF uniquely determines a distribution, so a MFG uniquely maps to a PDF.
-Also,
-        for the MGF of two distributions the convolutions is a multiplication, not an integral.
+For the MGF of two distributions the convolutions is a multiplication, not an integral.
         Therefore, for the convolution of two PDFs their MGFs are multiplied and if the product is the MGF of a known distribution, the corresponding PDF is the convolution of the two original PDFs.
@@
         \end{equation}
-        where $T$ is Owen's T distribution.
-
-\section{Plots} \label{app:developing_plots}
-
-    \begin{figure*}
-        \centering
-        \includegraphics[scale=0.7]{figures-not-syw/gd1/tot_stream_and_spur_prob.png}
-        \caption{Caption}
-        \label{fig:gd1-astrometrics}
-    \end{figure*}
-
-    \begin{figure*}
-        \centering
-        \includegraphics[scale=0.8]{figures-not-syw/gd1/Unknown.png}
-        \caption{Caption}
-        \label{fig:gd1-distance_modulus}
-    \end{figure*}
-
-    \begin{figure}
-        \centering
-        \includegraphics[scale=0.6]{figures-not-syw/gd1/Unknown-2.png}
-        \caption{Caption}
-        \label{fig:gd1-cmd}
-    \end{figure}
-
-    \begin{figure*}
-        \centering
-        \includegraphics[scale=0.6]{figures-not-syw/gd1/Unknown-4.png}
-        \caption{Caption}
-        \label{fig:gd1-cmds}
-    \end{figure*}
+        where $T$ is Owen's T distribution \citep{Owen_1956}.
+
+% \section{Plots} \label{app:developing_plots}
+
+%     \begin{figure*}
+%         \centering
+%         \includegraphics[scale=0.7]{figures-not-syw/gd1/tot_stream_and_spur_prob.png}
+%         \caption{Caption}
+%         \label{fig:gd1-astrometrics}
+%     \end{figure*}
+
+%     \begin{figure*}
+%         \centering
+%         \includegraphics[scale=0.8]{figures-not-syw/gd1/Unknown.png}
+%         \caption{Caption}
+%         \label{fig:gd1-distance_modulus}
+%     \end{figure*}
+
+%     \begin{figure}
+%         \centering
+%         \includegraphics[scale=0.6]{figures-not-syw/gd1/Unknown-2.png}
+%         \caption{Caption}
+%         \label{fig:gd1-cmd}
+%     \end{figure}
+
+%     \begin{figure*}
+%         \centering
+%         \includegraphics[scale=0.6]{figures-not-syw/gd1/Unknown-4.png}
+%         \caption{Caption}
+%         \label{fig:gd1-cmds}
+%     \end{figure*}
 

### 2023-08-14 src/tex/ms.tex
[showyourwork] overleaf sync
[showyourwork] DAG
Signed-off-by: nstarman <nstarman@users.noreply.github.com>

@@
 \usepackage{booktabs}
+\usepackage{dsfont}
 \usepackage{todonotes}
@@
 \newcommand{\dataarchive}[1]{\texttt{#1}}
+\newcommand{\Gaia}{\dataarchive{Gaia}}
+\newcommand{\gaia}{\dataarchive{gaia}}
 
@@
 
-\newcommand{\cmp}[2]{#2^{(#1)}}
 \newcommand{\smallcomponent}[2]{#2^{\scriptscriptstyle (#1)}}
-\newcommand{\astroM}[1]{\smallcomponent{w}{#1}}
+\newcommand{\cmp}[2]{\smallcomponent{#1}{#2}}
+\newcommand{\Scmp}[1]{\cmp{S}{#1}}
+\newcommand{\Bcmp}[1]{\cmp{B}{#1}}
+\newcommand{\astroM}[1]{{#1}_w}
 \newcommand{\photoM}[1]{\smallcomponent{m}{#1}}
@@
 
+\newcommand{\Spdf}{\Scmp{\pdf}}
+\newcommand{\Bpdf}{\Bcmp{\pdf}}
+
 \newcommand{\sigobs}{{\sigma_*}}
 
-\newcommand{\JN}[1]{{\textcolor{red}{JN: #1}}}
+\newcommand{\TODO}[1]{{\textcolor{red}{#1}}}
+\newcommand{\JN}[1]{\TODO{#1}}
 
@@
 \section{Introduction} \label{sec:intro}
-
-    \todo[inline]{Rephrase ---}
+    Stellar streams are the disrupted remnants of globular clusters and satellite galaxies, and their census has grown extensively in the Milky Way thanks to all-sky astrometric missions like {\it Gaia} and low-surface brightness photometric surveys (\JN{cite}).
+The formation of streams can be traced back to a progenitor cluster (i.e., a satellite galaxy or globular cluster), whose stars are gradually lost to the tidal field of the host galaxy and extend along a series of similar orbits producing tidal tails which can sometimes span many tens of degrees across the sky.
+This orbital proximity of stars belonging to a stream makes them sensitive detectors of the mass distribution of galaxies, sourced by both the baryonic and dark matter components across a large range of mass-scales.
+
+    The average properties of a stream (e.g., the mean position and velocity track of the tidal tails) can be used to reconstruct the global dark matter distribution of the stellar halo (e.g., \JN{cite}), while local variations in the stream track and surface density encode information about the stream's encounters with baryonic structures such as (e.g.) the stellar bar (\JN{cite}), and non-luminous structures like dark matter subhalos (\JN{cite}).
+
+    While several methods have been developed to model stream properties as a function of global halo properties (e.g., flattening and orientation;\JN{cite}) and local substructures (e.g., the bar's pattern speed and the mass of subhalo perturbers; \JN{cite}), these methods and insights often rely on the existence of a homogenized stream-tracer population that characterizes the stream across each of the observable phase-space dimensions.
+Additionally, because even the fine-grain properties of streams are influenced by the detailed mass distribution of galaxies, it is important to propagate errors both in measurement uncertainty and membership uncertainty (i.e., which stars belong to the stream versus the background) when attempting to model the galaxy.
+Otherwise, a stream that has been poorly characterized could bias constraints on (e.g.) the total mass of the galaxy, the dark matter halo shape, and the mass of subhalo perturbers.
+In order to generate more precise constraints on the structure of the galaxy, it is therefore imperative that a statistically sound and homogenized catalog of stellar streams is produced so that theoretical models for the gravitational potential of the galaxy across a large range of spatial scales can be constrained.
 
@@
 
+    \paragraph{one orbit and a single population}
+
+        Stellar streams consist of stars that are tidally disrupted from a progenitor system.
+        To a first approximation, the stars occupy a single orbit, that of their progenitor.
+        Additionally, as stars formed in the progenitor they retain its photometric and chemical characteristics: which for globular clusters means following an isochrone.
+        In this simplistic picture, astrometrically characterizing a stream requires only finding it's orbit.
+Member stars fall directly on the orbit and the isochrone, making membership likelihood determination trivial.
+
+        % Observational errors complicate this picture.
+Instead of a certain membership calculation, we must build a probabilistic model, assigning a likelihood that an observed star falls along the stream's orbit.
+
+    \paragraph{similar orbits and a somewhat noisy population}
+
+        Occupying a single orbit implies that streams remain a point in action space, and having a common origin would thus not become extended structure. This is not true.
+        Differences in stream stars' orbits from the progenitor's arise from various factors including internal dynamics of the progenitor and the host Galactic potential.
+
+        An intrinsic width, in configuration and kinematic space.
+
+        Centered on a track, not an orbit.
+
+        This defines an astrometric phase-space hyper-tube \cite{2018MNRAS.477.4063M}, with a distribution radial to the track.
+
+        Instead of characterizing the stream by its orbit, we characterize it by it's track and the distribution around that track.
+        Computing membership likelihoods now requires fitting the track and distribution. This cannot be
+        done without then also fitting the field of stars in which the stream lives, since the stream 
+        and field cannot be clearly separated.
+
+    \paragraph{gaps orbits and a somewhat noisy population}
+
+        This is still a simplistic picture of streams.
+
+        Perturbations to the Galactic potential, in the form of time evolution and non-axisymmetry, as well as substructure can disrupt the stellar stream. 
+        Even most perturbations don't ruin the idea of the phase-space hypertube. They either drop the mixture weight (rephrase, not yet introduced) to 0 or change the width of the hypertube.
+
     \paragraph{Review of detection methods}
@@
 
-        \paragraph{one orbit and a single population}
-
-            Stellar streams consist of stars that are tidally disrupted from a progenitor system.
-            To a first approximation, the stars occupy a single orbit, that of their progenitor.
-            Additionally, as stars formed in the progenitor they retain its photometric and chemical characteristics: which for globular clusters means following an isochrone.
-            In this simplistic picture, astrometrically characterizing a stream requires only finding it's orbit.
-Member stars fall directly on the orbit and the isochrone, making membership likelihood determination trivial.
-
-            % Observational errors complicate this picture.
-Instead of a certain membership calculation, we must build a probabilistic model, assigning a likelihood that an observed star falls along the stream's orbit.
-
-        \paragraph{similar orbits and a somewhat noisy population}
-
-            Occupying a single orbit implies that streams remain a point in action space, and having a common origin would thus not become extended structure. This is not true.
-            Differences in stream stars' orbits from the progenitor's arise from various factors including internal dynamics of the progenitor and the host Galactic potential.
-
-            An intrinsic width, in configuration and kinematic space.
-
-            Centered on a track, not an orbit.
-
-            This defines an astrometric phase-space hyper-tube \cite{2018MNRAS.477.4063M}, with a distribution radial to the track.
-
-            Instead of characterizing the stream by its orbit, we characterize it by it's track and the distribution around that track.
-            Computing membership likelihoods now requires fitting the track and distribution. This cannot be
-            done without then also fitting the field of stars in which the stream lives, since the stream 
-            and field cannot be clearly separated.
-
-        \paragraph{gaps orbits and a somewhat noisy population}
-
-            This is still a simplistic picture of streams.
-
-            Perturbations to the Galactic potential, in the form of time evolution and non-axisymmetry, as well as substructure can disrupt the stellar stream. 
-            Even most perturbations don't ruin the idea of the phase-space hypertube. They either drop the mixture weight (rephrase, not yet introduced) to 0 or change the width of the hypertube.
-
-        % TODO: significantly expand on this
-
-        \paragraph{Modeling approach}
-
         We take a Bayesian approach modeling the stream and background distribution.
@@
 
-        The hypertube idea is connected to orbits.
-        One might think then that a variable like the phase-angle or the arc-length, or any variable that directly sweeps along the stream would be best to use as the conditioning variable.
-        This is not the case for a number of reasons (see \cite{StarkmanEtAl2023} for some discussion on this topic), not least of which is that we do not have any of these quantities.
-We do not know the stream track, it's what we want to know.
+        {\color{red} Assume we know a stream track}
 
@@
 
+        \IfFileExists{static/DAG_StreamDensity.pdf}{
             \begin{figure}
@@
                 \caption{Fill in.}
-        \label{fig: DAG}
+                \label{fig:DAG}
             \end{figure}
-
-        We model the likelihood for a single star as
-        \begin{align} \label{eq:general_model}
-            \pdf(\nth{\mbs{w}}, \nth{\mbs{m}} | \mbs{\theta})
-                &= \sum_{q} \ f_q(w_{i, 0}) \pdf(\nth{\mbs{w}}|\mbs{\theta},q_i\!=\!q) \pdf(\nth{\mbs{m}}|\mbs{\theta},q_i\!=\!q)
-        \end{align}
-        where we have assumed that $\nth{\mbs{w}}$ and $\nth{\mbs{m}}$ are
-        conditionally independent, and that the mixture weights $f$ are
-        normalized s.t. $\sum_q f(w_{i,0}) = 1$.  We discuss the mixture weights
-        further in \autoref{sub:mixture_weight}.
+        }{
+        }
+
+        Mixture models (MMs) are a statistical method to represent a population as a set of a sub-populations specified by probability distributions.
+These distributions are characterized by their parameters and the mixture by a corresponding set of mixture coefficients.
+Scalar mixture models may be extended to model completely general conditional distributions by making the distribution parameters and mixture coefficients functions of a conditional input \citep{McLachlan1989MixtureM}.
+        Mixture Density Networks (MDNs) are a machine learning method to implement these general MM, taking the parameters and coefficients to be the outputs of feed-forward neural networks and as such, general continuous functions \citep{Bishop1994}.
+Functional parameters allows the model to capture variation over those parameters that is not possible with scalar-valued models.
+Moreover, by using neural networks the inferred functional forms are ``model-free" and driven entirely by the data.
+
+        For the MDN we take $x_{\cdot, 0}$, which is the first feature column of the data $\mbf{X}$, as the `independent' coordinate over which the MDN parameters are conditioned.
+In the context of streams $x_{\cdot, 0} \equiv \phi_1$ is the longitude coordinate in a reference frame rotated such that the stream is aligned along $\phi_1$.
+The parameters of the stream, the background field, and the mixing coefficients of the two are now general data-driven continuous functions along $\phi_1$.
+        {\color{cyan} \\ connecting to intro...
+
+            The hypertube idea is connected to orbits.
+            One might think then that a variable like the phase-angle or the arc-length, or any variable that directly sweeps along the stream would be best to use as the conditioning variable.
+            This is not the case for a number of reasons (see \cite{StarkmanEtAl2023} for some discussion on this topic), not least of which is that we do not have any of these quantities.
+We do not know the stream track, it's what we want to know.
+        }
+
+        The PDF of a general MDN is
+        \begin{equation} \label{eq:general_mixture_network}
+            \!\!\! \pdf(\nth{\mbs{x}} | \mbs{\theta}(\phi_1))
+            \!=\! \sum_{\mrm{q} \in \mbs{I_Q}} \! \qth{f}(\phi_1) \cmp{q}{\pdf}(\nth{\mbs{x}}|\qth{\mbs{\theta}}(\phi_1))
+            % \prior(\nth{\mbs{x}}, \phi_1)
+        \end{equation}
+        where $\pdf_q$ is the PDF of the $q$-th model and $f_q$ its mixing coefficient for all $q$ models in the set of models indexed by $\mbs{I_Q}$.
+$\mbs{\theta}$ is the $\phi_1$-conditional output of the feed-forward neural network, and $\nth{\mbs{x}}$ the data on the $n$-th star in $\mbs{X}$, not including $\phi_1$.
+For convenience we drop the implied subscript $n$ in $\phi_1$.
+A full detailing of notation and symbols is included in \autoref{app:notation}.
+For convenience we drop the explicit notation of $\mbs{\theta}$'s dependence on $\phi_1$ and the index set $\mbs{I}_X$ in summations over its elements $x$.
+
+        The mixture coefficients $\qth{f}$ are normalized s.t.
+        \begin{equation}
+            \sum_{\mrm{q}} \qth{f}(\phi_1) = 1 \qquad \forall \phi_1
+        \end{equation}
+        In practice this is enforced by defining
+        \begin{equation} \label{eq:mixture_weight_normalization}
+            f_{b}(\phi_1) = 1 - \sum_{\rm{q}\in \mbs{I_Q}\backslash \{b\}} \qth{f}(\phi_1),
+        \end{equation}
+        the summation over all models except for some ``background" index $b \in \mbs{I_Q}$.
+        We discuss the mixture weights further in \autoref{sub:mixture_weight}.
+
+        In this work we consider primarily astrometric and photometric data, (notated $\mbs{W}$ and $\mbs{M}$, respectively, as detailed in \autoref{app:notation}), but note that the MDN framework may be extended to arbitrary feature dimensions.
+        Assuming the conditional independence of the astrometry and photometry,
+        we split each model into linearly separable astrometric and photometric models $\cmp{q}{\pdf} = \cmp{q,w}{\pdf} \cmp{q,m}{\pdf}$ .
+
+        The likelihood for a single star then becomes, simplifying from \autoref{eq:general_mixture_network},
+        \begin{equation} \label{eq:general_model}
+            \!\!\!\!\! \pdf(\nth{\mbs{w}}, \! \nth{\mbs{m}} | \mbs{\theta})
+                \!=\! \sum_{q} \! f_q(\phi_1) \cmp{q,w}{\pdf}(\nth{\mbs{w}}|\mbs{\theta}) \cmp{q,m}{\pdf}(\nth{\mbs{m}}|\mbs{\theta})
+        \end{equation}
 
@@
         log-likelihood is a sum over all stars:
-        \begin{equation}
-            \ln\mcal{L}\left(\{(\nth{\mbs{w}},\nth{\mbs{m}})\} | \mbs{\theta}\right) = \sum_i  \ln \pdf(\nth{\mbs{w}}, \nth{\mbs{m}} | \mbs{\theta}).
-        \end{equation}
-
-        It will prove convenient to distinguish the models for $q=0,1$ as the
+        \begin{equation} \label{eq:general_likelihood}
+            \ln\mcal{L}\left(\{\nth{\mbs{w}},\nth{\mbs{m}}\} | \mbs{\theta}\right) = \sum_n \ln \pdf(\nth{\mbs{w}}, \nth{\mbs{m}} | \mbs{\theta}).
+        \end{equation}
+
+        It will prove convenient to distinguish the models for $q$ as the
         \textit{background} and \textit{stream} models, respectively. In this
         notation:
-
-        \begin{align}
+        \begin{align} \label{eq:stream_and_bkg_prob}
             \pdf(\nth{\mbs{w}}, \nth{\mbs{m}} | \mbs{\theta})
-            =& \phantom{+} \qquad f \phantom{+} P^{(S)}(\nth{\mbs{w}}|\mbs{\theta}) P^{(S)}(\nth{\mbs{m}}|\mbs{\theta}) \\
-            & + (1-f) P^{(B)}(\nth{\mbs{w}}|\mbs{\theta}) P^{(B)}(\nth{\mbs{m}}|\mbs{\theta}), \nonumber
+            =& \phantom{+} \qquad f \phantom{+} \Scmp{P}(\nth{\mbs{w}}|\mbs{\theta}) \Spdf(\nth{\mbs{m}}|\mbs{\theta}) \\
+            & + (1-f) \Bpdf(\nth{\mbs{w}}|\mbs{\theta}) \Bpdf(\nth{\mbs{m}}|\mbs{\theta}), \nonumber
         \end{align}
-
-        The probablity of a being a stream member is then simply
+        where we have dropped the $(w), (m)$ superscript as the model types are evident from their inputs.
+We applied \autoref{eq:mixture_weight_normalization} to require only a single mixture coefficient.
+        Of course, if more components are included in the mixture then \autoref{eq:stream_and_bkg_prob} becomes the more general \autoref{eq:general_model}.
+However, this an implementation detail as any more complex model, e.g a model including a cold stream, extra-tidal features, the background stellar halo, and field globular clusters may be rearranged such that all stream-related components (cold or extra-tidal) and all other components (stellar halo and globular clusters) are grouped into multi-component \textit{stream} and \textit{background} models which themselves adhere to a \autoref{eq:general_model}-type relation.
+
+        The probability of a being a stream member is then simply
         \begin{equation}\label{eq:membership_prob}
-            \pdf\left(S | \mbs{w}_n, \mbs{m}_n, \mbs{\theta} \right) = \frac{f P^{(S)}(\nth{\mbs{w}}|\mbs{\theta}) P^{(S)}(\nth{\mbs{m}}|\mbs{\theta}) }{ \pdf(\nth{\mbs{w}}, \nth{\mbs{m}} | \mbs{\theta})}.
+            \pdf\left(S | \nth{\mbs{w}}, \nth{\mbs{m}}, \mbs{\theta} \right) = \frac{f \Spdf(\nth{\mbs{w}}|\mbs{\theta}) \Spdf(\nth{\mbs{m}}|\mbs{\theta}) }{ \pdf(\nth{\mbs{w}}, \nth{\mbs{m}} | \mbs{\theta})}.
         \end{equation}
@@
         Hereafter, when we refer to ``membership probability,"
-        \autoref{eq:membership_prob} provides the formal definition.
-
-        \paragraph{missing phase-space observations}
-
-            Streams have a diversity of measurement coverage: several have full 6-D astrometrics as well as photometrics and chemical abundances available \citep[e.g.,][]{Koposov2019, 2020A&A...635L...3A, 2022ApJ...928...30L}, while most have partial coverage, lacking feature dimensions.
+        \autoref{eq:membership_prob} provides the formal definition. We nuance this definition by considering missing feature dimensions in the following subsection.
+
+    \subsection{Missing Phase-Space Observations} \label{sub:missing_data}
+
+        Streams have a diversity of measurement coverage: several have full 6-D astrometrics as well as photometrics and chemical abundances available \citep[e.g.,][]{Koposov2019, 2020A&A...635L...3A, 2022ApJ...928...30L}, while most have partial coverage, lacking some feature dimensions.
         % TODO: terminology ND-phase-space vs feature columns
-            Most streams in \dataarchive{Gaia} {\color{red} [cite]}, for instance, have proper motions but not radial velocities nor reliable parallax measurements.
+        Most streams in \gaia {\color{red} [cite]}, for instance, have proper motions but not radial velocities nor reliable parallax measurements.
 Followup surveys, like \dataarchive{S5} {\color{red} [cite]}, add many feature dimensions, however only for a select set of streams.
-Given the diversity of coverage it is important that the likelihood model can deal with missing data.
+Given the diversity of coverage it is important that the likelihood model -- \autoref{eq:membership_prob} -- account for missing data.
 
@@
 Likewise, using only present features in the likelihood model misses that the star is likely very distant.
-
-            {\color{red} Sentence explaining why we ignore features regardless.}
-            We include a quality flag on our calculations, indicating the number of missing features.
-
-            The per-star likelihood is modelled with a distribution with the same dimensionality as the data vector.
-            For example, a star with a 6D astrometric measurement will be modelled with a full 6D distribution, while a star missing its radial velocity measurement, will be modelled with a 5D dimensionally-reduced form of the 6D distribution.
+        The effects of mask systematics are mitigated by not including such data,
+        moving the contribution of the systematics from a prior to the evidence.
+        Our models compute likelihoods under a specific dataset, and \autoref{eq:membership_prob} is a ratio of the probabilities, so the removed systematics are not expected to be impactful.
+
+        We adopt the approach of modeling the data masks as randomly-distributed and not systematic.
+We do not impute missing data, instead the per-star likelihood is modelled with a distribution with the same dimensionality as the data vector.
+        For example, a star with a 6D astrometric measurement will be modelled with a full 6D distribution, while a star missing its radial velocity measurement will be modelled with a dimensionally-reduced (5D) form of the 6D distribution.
 Using dimensionally reduced distributions ensure that missing phase-space dimensions do not amplify nor suppress the likelihood.
+        Notwithstanding, we include a quality flag on our calculations indicating the number of missing features.
+        We leave incorporating priors on the data mask distribution to future work.
 
@@
 
-        In particular, for a given field the distribution of $\phi_1$ coordinates is specified by the set $\{\nth{\phi_{1}}\}_f$.
+        In particular, for a given field the distribution of $\phi_1$ coordinates is specified by the set $\{\phi_1\}_f$.
 A normalizng flow is trained to this dataset, and will satisfy $\int d\phi_1 P_{\phi_f}(\phi_1) = 1$ by construction.
@@
             \begin{equation}
-                \pdf^{(S)}(\nth{\mbs{w}} | \astroM{\mbs{\theta}}(\nth{\phi_{1}})) = \mcal{N}_F \big(\nth{\mbs{w}} | \astroM{\mbs{\mu}} \left(\nth{\phi_{1}} \right), \astroM{\mbs{\Sigma}} \left(\nth{\phi_{1}}\right) \big),
-            \end{equation}
-            where $\mbs{\theta}$ is the set of neural network parameters that define $\astroM{\mbs{\mu}}$ and $\astroM{\mbs{\Sigma}}$.
+                \cmp{S,w}{\pdf}(\nth{\mbs{w}} | \mbs{\theta}) \!
+= \mcal{N}_F \big(\nth{\mbs{w}} | \astroM{\mbs{\mu}}\!(\phi_1), {\cmp{w}{\nth{\mbs{\Sigma}}}}^2 \!
++ \!
+\astroM{\mbs{\Sigma}}^2\!\left(\phi_1\right) \!\big),
+            \end{equation}
+            where $\astroM{\mbs{\theta}}$ is the set of neural network parameters that define $\astroM{\mbs{\mu}}$ and $\astroM{\mbs{\Sigma}}$; and $\cmp{w}{\nth{\mbs{\Sigma}}}$ the data uncertainties.
             In the simplest case, we take $\astroM{\mbs{\Sigma}}$ to be diagonal, consisting of both intrinsic dispersion for each dimension of $\mbs{w}$ and the data uncertainties added in quadrature.
+The data uncertainties $\cmp{w}{\nth{\mbs{\Sigma}}}$ are drawn from $\mbs{\delta}\mbf{W}$, the dataset of astrometric uncertainties (see \autoref{app:notation}).
 
@@
             In the presence of missing phase-space coordinate $f_k$ we reduce the dimensionality of the Gaussian to that of the data-vector.
-Namely, for $\mbs{I}_{\tilde{F}} = \mbs{I}_{F} \backslash f_k$
+Namely, for $\mbs{I}_{\tilde{F}} = \mbs{I}_{F} \backslash \{f_k\}$
             \begin{align}
-                \nth{\tilde{\mbf{w}}} &\mapsto \nth{\tilde{\mbf{w}}} = \{ w_{n,f}\}_{f\in \mbs{I}_{\tilde{F}}}, \nonumber\\
-                \astroM{\mbs{\mu}} &\mapsto \astroM{\tilde{\mbs{\mu}}} = \{ \mu_{f}\}_{f\in\mbs{I}_{\tilde{F}}}, \nonumber\\
-                \astroM{\mbs{\Sigma}} &\mapsto \astroM{\tilde{\mbs{\Sigma}}} = \{ \Sigma_{i,j}\}_{i,j \in \mbs{I}_{\tilde{F}}}, & \nonumber
+                \nth{\tilde{\mbf{w}}} &\mapsto \nth{\tilde{\mbf{w}}} = \{ w_{n,f} | f\in \mbs{I}_{\tilde{F}}\}, \nonumber\\
+                \astroM{\mbs{\mu}} &\mapsto \astroM{\tilde{\mbs{\mu}}} = \{ \mu_{f} | f\in \mbs{I}_{\tilde{F}}\}, \nonumber\\
+                \astroM{\mbs{\Sigma}} &\mapsto \astroM{\tilde{\mbs{\Sigma}}} = \{ \Sigma_{i,j} | i,j \in \mbs{I}_{\tilde{F}} \}, & \nonumber
                 \intertext{such that,}
-                \pdf^{(S)}(\nth{\mbs{w}} & | \astroM{\mbs{\theta}}(\nth{\phi_{1}}))
-                    \mapsto \pdf^{(S)}(\nth{\tilde{\mbs{w}}} | \astroM{\tilde{\mbs{\theta}}} (\nth{\phi_{1}})).
+                \Spdf(\nth{\mbs{w}} & | \astroM{\mbs{\theta}}(\phi_1))
+                    \mapsto \Spdf(\nth{\tilde{\mbs{w}}} | \astroM{\tilde{\mbs{\theta}}} (\phi_1)) = \mcal{N}_{\tilde{F}}.
             \end{align}
+
+        % ssub: on_stream (end)
 
@@
 
-            Let $\fth{\cmp{B}{\mbs{\theta}}}(\phi_1)$ represent the neural network which outputs a vector of parameters characterizing the background distribution at a given $\phi_1$ for astrometric dimension $f$.
-The number of outputs for the background model is equal to $\mathrm{dim}\left(\fth{\cmp{B}{\mbs{\theta}}}\right)$ (where $f=0$ corresponds to $\phi_1$, which we do not model).
-At a given $\phi_1$, the probability density for the astrometric dimension $f>0$ is $\fth{\pdf^{(B)}}\left(\mbs{w}_{n,f} | \fth{\cmp{B}{\mbs{\theta}}}(\phi_1) \right)$.
+            Let $\Bcmp{\fth{\mbs{\theta}}}(\phi_1)$ represent the neural network which outputs a vector of parameters characterizing the background distribution at a given $\phi_1$ for astrometric dimension $f$.
+The number of outputs for the background model is equal to $\mathrm{dim}\left(\fth{\Bcmp{\mbs{\theta}}}\right)$ (where $f=0$ corresponds to $\phi_1$, which we do not model).
+At a given $\phi_1$, the probability density for the astrometric dimension $f>0$ is $\Bcmp{\fth{\pdf}}\left(\mbs{w}_{n,f} | \Bcmp{\fth{\mbs{\theta}}}(\phi_1) \right)$.
 We treat each background component as independent, allowing us to write the likelihood as a product over the astrometric dimensions:
             \begin{equation} \label{eq:astrometric_model_off_stream_probability}
-                \pdf^{(B)}\left(\nth{\mbs{w}} | \mbs{\theta}(\phi_1) \right) = \prod_{f\in \mbs{I}_{\tilde{F}}} \pdf_f^{(B)}\left(\mbs{w}_{n,f} | \fth{\cmp{B}{\mbs{\theta}}}(\phi_1) \right).
+                \pdf^{(B)}\left(\nth{\mbs{w}} | \mbs{\theta}(\phi_1) \right) = \prod_{f\in \mbs{I}_{\tilde{F}}} \pdf_f^{(B)}\left(\mbs{w}_{n,f} | \Bcmp{\fth{\mbs{\theta}}}(\phi_1) \right).
             \end{equation}
@@
 
-    %\newpage
+        % ssub: off_stream (end)
+
+    % sub: astrometric_model (end)
 
@@
             At any given $\phi_1$, the isochrone is modeled in absolute magnitudes
-            and parameterized by the unit-normalized stellar mass, labeled $\gamma$.
+            and parameterized by the normalized stellar mass, labeled $\gamma \in (0, 1]$, in the modeled mass range.
 For example, increasing $\gamma$ corresponds to movement up the main sequence towards the red giant branch.
@@
 Since the isochrone is in absolute magnitudes, but the data are in apparent magnitudes,
-            it is necessary to shift the isochrone by a distance modulus to the predicted distance of the stream, labeled  $\mu(\nth{\phi_1})$.
+            it is necessary to shift the isochrone by a distance modulus to the predicted distance of the stream, labeled  $\mu(\phi_1)$, with intrinsic stream distance variation $\sigma_\mu(\gamma)$.
 
             For the $n$-th star, the photometric model is:
-
-            \begin{multline}
-                P^{(S)}(\mbs{m_i}, \gamma; \mbs{\theta}(\nth{\phi_1}), \nth{\phi_1}) 
-                \\ \sim \mcal{N}(\nth{\mbs{m}}; \{\mcal{I(\gamma)} + \mu(\nth{\phi_1}), \sqrt{\Sigma_{\mcal{I}}^2(\gamma) + \Sigma_\mu^2(\nth{\phi_1}) + \Sigma_i^2} \}) \\ \times\pdf(\gamma, \nth{\phi_1}),
+            \begin{multline} \label{eq:photometric_probability_point}
+                \cmp{S,m}{P}(\mbs{m_i}, \gamma | \mbs{\theta}(\phi_1)) 
+                \\ \sim \mcal{N}(\nth{\mbs{m}} | \{\mcal{I(\gamma)} + \mu(\phi_1), \mbs{\Sigma}_{\mcal{I}}^2(\gamma) + \mathds{1} \sigma_\mu^2(\phi_1) + {\cmp{m}{\nth{\mbs{\Sigma}}}}^2 \}) \\ \times \prior(\gamma, \nth{\mbs{m}}, \phi_1),
             \end{multline}
 
-            where $\pdf(\gamma)$ encodes both the present-day mass function of the stream, as well as the observational constraints (e.g. $g < 22$ mag).
+            where $\cmp{m}{\nth{\mbs{\Sigma}}}$ is the data covariance and $\prior(\gamma, \nth{\mbs{m}}, \phi_1)$ encodes both the present-day mass function of the stream, as well as any observational constraints (e.g.
+$g < 20$ mag).
 
@@
             \begin{small}
-            \begin{multline}
-                P^{(S)}(\nth{\mbs{m}}; \mbs{\theta}(\nth{\phi_1}), \nth{\phi_1}) = \\\int\limits_{\gamma=0}^{1} \mcal{N}(\mbs{m}; \{\mcal{I(\gamma)} + \mu(\nth{\phi_1}), \sqrt{\Sigma_{\mcal{I}}^2(\gamma) + \Sigma_\mu^2(\nth{\phi_1}) + \Sigma_i^2} \}) \pdf(\gamma) \rm{d}\gamma.
-            \end{multline}\end{small}
+            \begin{align} \label{eq:photometric_probability}
+                &\cmp{S,m}{P}(\nth{\mbs{m}} | \mbs{\theta}(\phi_1)) = \\
+                &\ \int\limits_{\gamma=0}^{1} \mcal{N}(\nth{\mbs{m}} | \{\mcal{I(\gamma)} + \mu(\phi_1), \mbs{\Sigma}_{\mcal{I}}^2(\gamma) + \mathds{1}\sigma_\mu^2(\phi_1) + {\cmp{m}{\nth{\mbs{\Sigma}}}}^2 \}) \nonumber
+                \\
+                &\qquad \times \prior(\gamma, \nth{\mbs{m}}, \phi_1) \rm{d}\gamma. \nonumber
+            \end{align}
+            \end{small}
             Then, for a given $\phi_1$ we can obtain a distribution over the distance modulus using 
-            \begin{equation}
-                \mu_{\rm sample}\left(\phi_1\right) \sim \mathcal{N}\left(\mu(\phi_1), \Sigma^2_\mu(\phi_1) \right) \quad\unit{mag}.
-            \end{equation}
-            For each sample, we can convert the distance-modulus distribution to the distance track using 
-            \begin{equation}
-                \rm{dist}\left(\phi_1\right) = 10^{\frac{1}{5}\mu_{\rm sample}(\phi_1)+1} \quad\unit{pc}.
-            \end{equation}
-
-            \todo[inline]{TODO:}
+            \begin{align}
+                \mu_{\rm sample}\left(\phi_1\right) \sim \mathcal{N}\left(\mu(\phi_1), \sigma^2_\mu(\phi_1) \right) & \quad\unit{mag}.
+            \end{align}
+            For each sample, we can convert the distance-modulus distribution (and error) to the distance track using 
+            \begin{align}
+                \rm{dist}\left(\phi_1\right) &= 10^{\frac{1}{5}\mu_{\rm sample}(\phi_1)+1} & \quad\unit{pc}, \\
+                \delta \rm{dist}(\phi_1) &\simeq \frac{\ln{10}}{5} \rm{dist}(\phi_1) \ \sigma_\mu(\phi_1) & \quad\unit{pc}.
+            \end{align}
+
+            Let $\cmp{S,m}{\mbs{\theta}}(\phi_1)$ represent the feed-forward neural network which outputs a vector of parameters characterizing the stream's photometric distribution at a given $\phi_1$.
+The network has 2 outputs -- $\mu, \Sigma_\mu$ -- as we only consider the distance track of the isochrone, holding fixed stellar population parameters internal to modeling the isochrone, such as its age and metallicity.
+            In principle we might include parameters of the isochrone in the model, now $\mcal{I}(\mbs{\theta}, \gamma)$, where $\theta = {a, Z, ...}$ and any other generating parameters of the isochrone.
+            % FIXME! DO this Likewise, the dust map may be treated as a prior and it's errors incorporated into the data errors.
+            However, stellar streams are generally poorly fit by theoretic isochrones, at least ones with realistic ages and metallicities.
+            Consequently including the age and metallicity as model parameters
+            does not meaningfully contribute to constraining results on the stream's stellar population.
+Moreover, age and metallicity are partially degenerate with the distance modulus.
+An alternate approach is to use data-driven isochrones instead of theoretic ones.
+In some forms of this approach the age and metallicity are not meaningful quantities.
+In others, e.g.
+with a suite of models or a trained emulator, the data-driven isochrones might have realistic ages and metallicities and thus meaningfully contribute to the model.
+            % Is this true? re-read Uniform Modeling of 13 streams
+            We defer this to a future work.
+
+            The photometric probability, \autoref{eq:photometric_probability} includes the term $\prior(\gamma, \nth{\mbs{m}}, \phi_1)$, which encodes all priors on both the isochrone as well as observational constraints.
+It is safe to assume that the properties of the isochrone are conditionally independent from observational constraints; namely
+            \begin{equation} \label{eq:isochrone_prior_components}
+                \prior(\gamma, \nth{\mbs{m}}, \phi_1) = \prior_{\cal{I}}(\gamma, \phi_1) \prior_{obs}(\nth{\mbs{m}}, \phi_1)
+            \end{equation}
+            where $\prior_{\cal{I}}$ and $\prior_{obs}$ are the isochrone and observational priors, respectively.
+            \autoref{eq:photometric_probability} already encodes the photometric distribution -- the ``track" -- of the isochrone model at each point along the track, but not the amplitudes, the relative probability of points.
+Physically, this amplitude is the the present-day mass function (PDMF).
+We include the PDMF as $\prior_{\cal{I}}(\gamma, \phi_1)$.
+$\prior_{\cal{I}}$ is a joint distribution, depending on $\gamma$ since it is the $\gamma$-dependent distribution amplitude, and also on $\phi_1$.
+This latter dependence is confusing termed the ``mass function of the stream", which is the expected variation in the average stellar mass along the stream, due to e.g.
+mass segregation in the progenitor \TODO{[cite]}.
+To date this effect has not been observed \TODO{[cite?]}, so in practice we drop the $\phi_1$ dependence -- $\prior_{\cal{I}}(\gamma, \phi_1) = \prior_{\cal{I}}(\gamma)$ -- assuming that the PDMF is constant along the stream.
+
+            \todo[inline]{More on the PDMF}
             \begin{enumerate}
-                \item Not including isochrone parameters, e.g. age and metallicity
-                \item integrating over $\gamma$ the model assumes a PDMF, e.g. Kroupa
-                \item generic details of neural network, e.g Table 1
-                \item introducing parallax
-                \item how we reduce dimensionality.
+                \item problems with just a Kroupa -- it's not present day
+                \item could parameterize a more general distribution and fit for the PDMF
+                \item we are interested in the photometric model for a number of reasons, but an important one is that we can fit the distance modulus of the stream, for this only a subsection of the isochrone is needed.
+The best section is the MS turnoff.
+                Consequently, if we focus on the MS turnoff then the variation in the PDMF is much smaller and we can use a flat distribution. (Maybe need a plot demonstrating this?)
             \end{enumerate}
+
+            The second term in \autoref{eq:isochrone_prior_components} -- $\prior_{obs}(\nth{\mbs{m}}, \phi_1)$ -- encodes all observational effects in the photometric dataset. In particular we are
+
+            \todo[inline]{discussion of the $\prior_{obs}(\nth{\mbs{m}}, \phi_1)$}
+
+            \begin{enumerate}
+                \item survey completeness is challenging.
+We pre-select the dataset so that we don't need to concern ourselves with this.
+For Gaia this means cutting $G_{ \Gaia} > 20$.
+Our discussion of the PDMF emphasizes why this isn't a problem for the isochrone.
+                \item we don't actually cut the data, but apply a mask.
+\autoref{sub:missing_data} explains how this is done.
+In this case ALL the photometric feature dimensions are masked.
+This means that the on-stream component is a track of 0-dimensional Gaussians, which means it doesn't enter into the probability.
+Any astrometric data enters the astrometric model, so the membership likelihood of these stars is driven entirely by the astrometric model.
+            \end{enumerate}
+
+            \todo[inline]{Dust}
+            We use \package{dustmaps} Bayestar 19 for the dust modeling. We treat it as known. Include as a source of error in $\Sigma_n$
+
+        % ssub: on_stream (end)
+
+        \subsubsection{Linking to Astrometrics: the Distance Modulus and the Parallax}
+
+            % TODO: rephrase
+            By modeling jointly the astrometrics and photometrics we may tie together components of the models.
+            In particular, the distance modulus in the photometric model and the parallax in the astrometric model are both measures of the distance track of the stream.
+
+            We introduce a prior to connect these components of the model:
+            \begin{align}
+                \prior(\{\mu_I, \mu_\varpi \} | \phi_1) &= \delta( \rm{dist}(\mu_I) - \rm{dist}(\varpi) )(\phi_1), \label{eq:distance_track_prior}
+                % \prior(\{\sigma_I, \sigma_\varpi \}(\phi_1)) &= \delta( \rm{dist}(\mu_I) - \rm{dist}(\varpi) )(\phi_1) \label{eq:distance_width_prior}
+            \end{align}
+            where $\delta$ is the Dirac delta function, and simply expresses that the distance modulus track and parallax track must be equal (when converted to the actual distance) as a function of $\phi_1$.
+            The widths are similarly constrained.
+
+            % TODO: include the specific functions?
+            % \begin{align}
+            %     \mu_I(\varpi) &= 10 - 5\log_{10}(\varpi) \\
+            %     \sigma_I(\sigma_\varpi) &= \TODO{\text{write down the equation}}
+            % \end{align}
+
+            \todo[inline]{expand on this}
+
+            In practice, at the distance of many streams the parallaxes are informative and are excluded from most models.
+            % TODO!
 
@@
 
-            In general, the distribution of stars in color (i.e., $g-r$) and magnitude (i.e., $g$) is a complicated function of location in the galaxy.
+            In general, the distribution of stars in color (i.e., $g-r$) and magnitude (i.e., $g$) is a complicated function of location in the galaxy \TODO{(e.g.
+[cite])}.
 Even within a field centered on the stream of interest, the color-magnitude diagram (CMD) is a combination of stellar populations distributed over a range in distances.
@@
 The transformations are typically non-linear outputs of a neural neural network, whose parameters are optimized until the target density accurately characterizes the data.
-The neural network transformation is differentiable, so that jacobian factors can be combined to ensure that the the target distribution remains a valid probability density (i.e., integrates to one).
+The neural network transformation is differentiable, so that jacobian factors can be combined to ensure that the the target distribution remains a valid probability density (i.e., integrates to one) \TODO{[cite]}.
 
@@
 
-            The specific architecture of the photometric normalizing flow are discussed in \S-X.
-
-            \todo[inline]{TODO:}
-            \begin{enumerate}
-                \item Overview of the architecture
-                \item How one would reduce the dimensionalty.
-            \end{enumerate}
-
-    % subsection likelihood_setup (end)
+            % The specific architecture of the photometric normalizing flow are discussed in \autoref{sub:model_implementation}. But
+            It is easy to evaluate the log-likelihood a normalizing flow at a point $\mbs{m}$ when all feature dimensions are present.
+When one (or more) feature dimension is missing, however, evaluating the marginal log-likelihood involves integrals over the flow.
+While the procedure is straightforward procedure, it is computationally expensive.
+As an alternative, we conservatively set the log-likelihood to $0$, the maximum value, overemphasizing the flow's contribution to the background model.
+Conceptually, up-weighting the background model decreases the false-positive rate in stream membership identification, at the
+            cost of increasing the false-negative rate.
+However, the intrinsic width of stellar streams tends to be quite small, with correspondingly small $\sigma_\mu$ (see \autoref{eq:photometric_probability}); thus the effective region of the isochrone model is well determined and we do not find the marginal log-likelihood approach to be impactful.
+Another approach, which we leave to a future work, is to construct normalizing flows of each marginal distribution, e.g.
+$q_{\rm flow}\left(\{m_i\}_{i \in \mbs{I}_F, i \neq {j, k}} | m_j, m_k, \phi_1\right)$, and select for each $\nth{\mbs{m}}$ the correct flow given the missing features.
+
+        % ssub: off_stream (end)
+
+    % sub: photometric_model (end)
 
@@
 
-    % \subsection[Astrometric Background]{Astrometric Background: pieces of $P^{(B)}(\mbs{w})$} \label{sub:background_astrometric}
+    % \subsection[Astrometric Background]{Astrometric Background: pieces of $\Bcmp{P}(\mbs{w})$} \label{sub:background_astrometric}
 
@@
 
+        \todo[inline]{intro sentences}
+
         \subsubsection{Bounding Boxes}
@@
             $-\ln\left(\sqrt{\frac{\pi}{\tau}} \left(\frac{1}{2}\text{erf}\left(2 \sqrt{\tau } w\right)+1\right)\right)$
-
-    \subsection{Linking Coordinates: Combining the Distance Modulus with the Parallax Track}
-
-        \todo[inline]{TODO:}
-        \begin{enumerate}
-            \item Discuss how to connect the distance modulus to the parallax.
-            \item First-order error propagation to set width DM to width parallax.
-        \end{enumerate}
 
@@
 The background astrometric  points in are generated from exponential distributions at each $\phi_1$.
-The number of stream stars is \JN{X}, while the number of background stars is \JN{Y}.
+The number of stream stars is \variable{mock/nstream_variable.txt}, while the number of background stars is \JN{Y}.
 
@@
         \subsubsection{Data Selection} \label{ssub:gd1_data}
+
+            \begin{enumerate}
+                \item Gaia data.
+                    \begin{enumerate}
+                        \item box size
+                        \item selection criteria
+                    \end{enumerate}
+                \item crossmatched with panstarrs1
+                \item extinction corrected with bayestar2019
+            \end{enumerate}
+
             We utilize data from {\it Gaia} DR3 for the astrometric coordinates of each star, and Pan-STARRS1 to obtain more accurate color information.
@@
 
-            \variable{output/gd1_members.tex}
+            \variable{output/gd1_select_members.tex}
 
@@
 
-\section{Comparison to Other Methods} \label{sec:comparison}
-
-    \subsection[STREAMFINDER]{\cite{2018MNRAS.477.4063M}}
+\section{Discussion}
+
+    \subsection{Comparison to Other Methods} \label{sec:comparison}
+
+        \subsubsection[STREAMFINDER]{\cite{2018MNRAS.477.4063M}}
+
+            Assumes a potential
 
@@
 
-    \subsection{VIA MACHINAE}{\cite{2022MNRAS.509.5992S}}
+        \subsubsection{VIA MACHINAE}{\cite{2022MNRAS.509.5992S}}
+
+            Only astrometric.
 
@@
 
-    \subsection[Uniform Modeling of 13 Stellar Streams]{\cite{PatrickEtAl2022}}
+        \subsubsection[Uniform Modeling of 13 Stellar Streams]{\cite{PatrickEtAl2022}}
+
+            Doesn't do simultaneous modeling.
 
@@
 
-    \GitHubURL
-
-    \todo[inline]{reword}
-    "This study was carried out using the reproducibility software
-    \href{https://github.com/showyourwork/showyourwork}{\showyourwork}
-    \citep{Luger2021}, which leverages continuous integration to
-    programmatically download the data from
-    \href{https://zenodo.org/}{zenodo.org}, create the figures, and
-    compile the manuscript. Each figure caption contains two links: one
-    to the dataset stored on zenodo used in the corresponding figure,
-    and the other to the script used to make the figure (at the commit
-    corresponding to the current build of the manuscript). The git
-    repository associated to this study is publicly available at
-    \url{https://github.com/mathren/CE_accretors}, and the release
-    v.2.1 allows anyone to re-build the entire manuscript. The datasets
-    are stored at \url{https://doi.org/10.5281/zenodo.7343715}, including
-    the template setup to recreate them using MESA (version 15140 and
-    the software development kit \texttt{x86\_64-linux-20.12.1}) and
-    the scripts used to produce the figures."
+    The data availability statement is modified from
 
@@
     \todo[inline]{zenodo url}. The git repository associated
-    with this study is publicly available at \GitHubURL.
+    with this study is publicly available at \GitHubURL{}.
 
@@
     \autoref{table:symbol_table} enumerates the symbols used for the statistical models and the different datasets, e.g. distinguishing astrometric from photometric data.
+
+    \TODO{position the table here}
 
@@
     \multicolumn{2}{l}{\textbf{Full Data}:}  \vspace{5pt} \\
-    $\mbf{X} \in \mbb{R}^{(N, F+1)}$ & Full dataset.  \\
+    $\mbf{X} \in \mbb{R}^{(N, F+1)}$ & The full dataset, including all measurements (rows) and features (columns).  \\
+    $\mbs{\delta}\mbf{X} \in \mbb{R}^{(N, F+1)}$ & The full set of uncertainties in $\mbf{X}$, e.g. Gaussian $\sigma_{n,f}$ and correlation terms $\sigma_{n,(f_i, f_j)}$.\\
     $N$ & The number of independent measurements (aka stars) in the dataset.  \\
@@
 \\
-    $\mrm{n} \in \mbs{I_N} \equiv \{1, ..., N\} \in \mbb{Z^+}$ & Index into the set of measurements $\mbf{X}$. \\
-    $\mrm{f} \in \mbs{I_F}  \equiv \{1, ..., F\} \in \mbb{Z^+}$ & Index into the set of features of $\mbf{X}$. $ f=0$ is the `independent' feature.\\
-    $x_{\mrm{n,f}}$ & $n$-th measurement of the $f$-th feature of $\mbf{X}$. \\
-    $\nth{\mbs{x}}$ & $n$-th row-vector of all features. \\
+    $\mrm{n} \in \mbs{I_N} \equiv \{1, ..., N\} \in \mbb{Z^+}$ & Index into the set of measurements $\mbf{X}$ (and $\mbs{\delta}\mbf{X}$), i.e. the $n$-th star. \\
+    $\mrm{f} \in \mbs{I_F}  \equiv \{1, ..., F\} \in \mbb{Z^+}$ & Index into the set of features of $\mbf{X}$  (and $\mbs{\delta}\mbf{X}$). $ f=0$ is the `independent' feature.\\
+    $(\delta)x_{\mrm{n,f}}$ & $n$-th star with $f$-th feature in $(\mbs{\delta})\mbf{X}$. \\
+    $(\mbs{\delta})\nth{\mbs{x}}$ & $n$-th star as a row vector of all features of $(\mbs{\delta})\mbf{X}$. \\
+
     % -------------------------------------------------
@@
     $\mbf{W} \in \mathbb{R}^{(N, F_w + 1)}$ & Full astrometric dataset. \\
-    $\mrm{f_w} \in \mbs{I_{F_w}} \equiv \{1, ..., F_w\} \in \mathbb{Z^+}$ & Index into the set of astrometric features. $f_w = 0$ is the `independent' feature.\\
-    $w_{\mrm{n,f_w}}$ & $n$-th measurement of the $f_w$-th feature of $\mbf{W}.$\\
-    $\nth{\mbs{w}}$ & $n$-th row-vector of all astrometric features. \\
-    $\phi_1 \equiv w_{\cdot,0}$ & The `independent' (index 0) feature column on which the models are conditioned.\\
+    $\mrm{f_w} \in \mbs{I_{F_w}} \equiv \{1, ..., F_w\} \in \mathbb{Z^+}$ & Index into the set of astrometric features. $f_w = f = 0$ is the `independent' feature.\\
+    $w_{\mrm{n,f_w}}$ & $f_w$-th astrometric feature of the $n$-th star in $\mbf{W}.$\\
+    $\nth{\mbs{w}}$ & $n$-th star as a row-vector of all astrometric features. \\
+    $\phi_1 \equiv w_{\cdot,0}$ & The `independent' (index 0) feature column on which the models are conditioned.
+For convenience $\phi_1$ is used instead of $\nth{\phi_1}$ (or $w_{n,0}$) except where the $n$ subscript cannot be inferred from context.\\
     % -------------------------------------------------
@@
     $\mrm{q} \in \mbs{I_Q} \equiv \{1, ..., Q \} \in \mbb{Z^+}$ & Index into the set of $Q$ models. \\
+    $\mrm{b} \in \mbs{I_Q}$ & The index of the background model in the set of $Q$ models.
     % -------------------------------------------------
@@
 
-\section{Theory of Mixture Density Networks (MDNs)} \label{app:theory_of_mixture_density_networks}
-
-    Mixture models (MMs) are a statistical method to represent a population as a set of a sub-populations specified by probability distributions.
+% \section{Theory of Mixture Density Networks (MDNs)} \label{app:theory_of_mixture_density_networks}
+
+%     Mixture models (MMs) are a statistical method to represent a population as a set of a sub-populations specified by probability distributions.
 These distributions are characterized by their parameters and mixture by a corresponding set of mixture weights.
 Mixture Density Networks (MDNs)
-    are a machine learning method to combine a MM with neural networks, increasing the flexibility of the model.
+%     are a machine learning method to combine a MM with neural networks, increasing the flexibility of the model.
 An MDN replaces the scalar distribution parameters of the MM with neural networks, allowing the distribution parameters and mixture weights to vary as smooth functions \citep{Bishop1994}.
@@
 
-    % Quote from https://mikedusenberry.com/mixture-density-networks
-    % A mixture density network (MDN) is an interesting model formalism built within the general framework of neural networks and probability theory for working on supervised learning problems in which the target variable cannot be easily approximated by a single standard probability distribution.
+%     % Quote from https://mikedusenberry.com/mixture-density-networks
+%     % A mixture density network (MDN) is an interesting model formalism built within the general framework of neural networks and probability theory for working on supervised learning problems in which the target variable cannot be easily approximated by a single standard probability distribution.
 Essentially an MDN allows one to model a conditional probability distribution as a mixture of distributions, in which the individual distributions and the corresponding mixture coefficients are parameterized by functions of the inputs
 
-    For the MDN we take $x_{\cdot, 0} \equiv x_{\cdot}$ (indexed from 0), which is the first feature column of $\mbf{X}$, as the `independent' coordinate over which the MDN parameters are conditioned.
+%     For the MDN we take $x_{\cdot, 0} \equiv x_{\cdot}$ (indexed from 0), which is the first feature column of $\mbf{X}$, as the `independent' coordinate over which the MDN parameters are conditioned.
 In the context of streams $x_{\cdot, 0} \equiv \phi_1$ is the longitude coordinate in a reference frame rotated such that the stream is aligned along $\phi_1$.
 
-    The PDF of the MDN is
-
-    \begin{equation} \label{eq:general_mixture_network}
-        \pdf(\nth{\mbs{x}} | \mbs{\theta}(\phi_1))
-        = \sum_{\mrm{q} \in \mbs{I_Q}} \ \qth{f}(\phi_1) \qth{P}(\nth{x}|\qth{\mbs{\theta}}(\phi_1),q\!=\!\mrm{q})
-    \end{equation}
-    The mixture coefficients $\qth{f}$ are normalized s.t.
-    \begin{equation}
-        \sum_{\mrm{q}} \qth{f}(\phi_1) = 1 \qquad \forall \phi_1
-    \end{equation}
-    In practice this is enforced by defining
-    \begin{equation}
-        f_{b}(\phi_1) = 1 - \sum_{\rm{q}\in \mbs{I_Q}\backslash b} \qth{f}(\phi_1)
-    \end{equation}
-    for some ``background" index $b \in \mbs{I_Q}$.
-
-    Assuming the measurement of each datum is independent, the likelihood is a sum over all data:
-    \begin{equation}
-        \mcal{L}\left(\mbf{x}_n | \mbs{\theta}(\phi_1)\right) = \sum_{q\in\mbs{I_Q}} \qth{P}\left(\nth{\mbs{x}} | \qth{\mbs{\theta}}(\phi_1)\right).
-    \end{equation}
-
-    The full posterior distribution includes the priors.
-
-    \begin{equation}
-        \ln\posterior\left(\mbf{X} | \mbs{\theta}(\mbs{x})\right) = \ln\mcal{L}\left(\mbf{X} | \mbs{\theta}(\mbs{x})\right) +  \sum_{n \in \mbs{I_N}} \ln \left[ \sum_{q\in\mbs{I_Q}} \qth{\prior}\left(\qth{\mbs{\theta}}(\mbf{x}_n)\right) \right].
-    \end{equation}
+%     The PDF of the MDN is
+
+%     \begin{equation} \label{eq:general_mixture_network}
+%         \pdf(\nth{\mbs{x}} | \mbs{\theta}(\phi_1))
+%         = \sum_{\mrm{q} \in \mbs{I_Q}} \ \qth{f}(\phi_1) \qth{P}(\nth{x}|\qth{\mbs{\theta}}(\phi_1),q\!=\!\mrm{q})
+%     \end{equation}
+%     The mixture coefficients $\qth{f}$ are normalized s.t.
+%     \begin{equation}
+%         \sum_{\mrm{q}} \qth{f}(\phi_1) = 1 \qquad \forall \phi_1
+%     \end{equation}
+%     In practice this is enforced by defining
+%     \begin{equation}
+%         f_{b}(\phi_1) = 1 - \sum_{\rm{q}\in \mbs{I_Q}\backslash b} \qth{f}(\phi_1)
+%     \end{equation}
+%     for some ``background" index $b \in \mbs{I_Q}$.
+
+%     Assuming the measurement of each datum is independent, the likelihood is a sum over all data:
+%     \begin{equation}
+%         \mcal{L}\left(\mbf{x}_n | \mbs{\theta}(\phi_1)\right) = \sum_{q\in\mbs{I_Q}} \qth{P}\left(\nth{\mbs{x}} | \qth{\mbs{\theta}}(\phi_1)\right).
+%     \end{equation}
+
+%     The full posterior distribution includes the priors.
+
+%     \begin{equation}
+%         \ln\posterior\left(\mbf{X} | \mbs{\theta}(\mbs{x})\right) = \ln\mcal{L}\left(\mbf{X} | \mbs{\theta}(\mbs{x})\right) +  \sum_{n \in \mbs{I_N}} \ln \left[ \sum_{q\in\mbs{I_Q}} \qth{\prior}\left(\qth{\mbs{\theta}}(\mbf{x}_n)\right) \right].
+%     \end{equation}
 

### 2023-08-14 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-        \subsubsection{Bounding Boxes}
+        \subsubsection{Parameter Bounds}
+
+            We implement a hard bound on the range of all parameters.
 
@@
 The background astrometric  points in are generated from exponential distributions at each $\phi_1$.
-The number of stream stars is \variable{mock/nstream_variable.txt}, while the number of background stars is \JN{Y}.
+The number of stream stars is $\variable{output/mock/nstream_variable.txt}$, while the number of background stars is $\variable{output/mock/nbackground_variable.txt}$.
 
@@
 
-            \variable{output/gd1_select_members.tex}
+            \variable{output/gd1/select_members.tex}
 

### 2023-08-14 src/tex/ms.tex
[showyourwork] overleaf sync

@@
             We implement a hard bound on the range of all parameters.
+            Hard cutoffs can be an unwise choice of prior, but we set the ranges to larger than the data prefers and check that the trained parameters are never ``up against" the bounds.
+            This makes the priors safe.
+            We require these priors for training the neural network. It helps to have a well-bounded problem. Simple hard priors have advantages and disadvantages in this regard.
+            An advantage is that in the allowed region the prior does not not contribute to the posterior at all.
+We don't want it to.
+We want to keep the posterior as simple as possible, driven as much as possible by the likelihood and not any priors.
 

### 2023-08-14 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 We want to keep the posterior as simple as possible, driven as much as possible by the likelihood and not any priors.
+            A marked disadvantage is that outside the bounded region the prior does not contribute a gradient to the loss function the optimizer can use in the fitting.
+            However, we sidestep this issue by encoding the prior bounds into the ``geometry" \TODO{(What is this called?)} of the neural network, so that the network can never
+            produce outputs outside the hard bounds. This is a standard technique in ML to ensure that the nerual network is efficient, only covering the required region of the output space
 

### 2023-08-14 src/tex/ms.tex
[showyourwork] overleaf sync

@@
             However, we sidestep this issue by encoding the prior bounds into the ``geometry" \TODO{(What is this called?)} of the neural network, so that the network can never
-            produce outputs outside the hard bounds. This is a standard technique in ML to ensure that the nerual network is efficient, only covering the required region of the output space
+            produce outputs outside the hard bounds.
+This is a standard technique in ML to ensure that the neural network is efficient, only covering the required region of the output space \TODO{[cite]}.
 
@@
     \todo[inline]{zenodo url}. The git repository associated
-    with this study is publicly available at \GitHubURL{}.
+    with this study is publicly available at $\GitHubURL{}$.
 

### 2023-08-15 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
+            % link to the code!
+            In the code we offer a few ansatz for the PDMF. The default assumption, which is known to be non-physical is a uniform distribution over $\gamma$. Any user-defined function may be used
+
             \todo[inline]{More on the PDMF}
@@
             \begin{enumerate}
-                \item Get rid of the dropout in the plot
                 \item the linear density in the stream-fraction plot
@@
         \subsubsection{Parameter Bounds}
+
+            \todo[inline]{}
 
@@
             where the additive normalization is 
-            $-\ln\left(\sqrt{\frac{\pi}{\tau}} \left(\frac{1}{2}\text{erf}\left(2 \sqrt{\tau } w\right)+1\right)\right)$
+            $-\ln\left(\sqrt{\frac{\pi}{\tau}} \left(\frac{1}{2}\text{erf}\left(2 \sqrt{\tau } w\right)+1\right)\right)$.
+In this form we see that $\tau$ may be increased to strengthen the prior and encourage $\mbs{\theta}$ to pass through
 
@@
 The dashed curve represents the output of our data-driven model, while the solid curve is the ground truth.
-\JN{todo: maybe the kde should be a histogram}, the second panel shows the stream and background in the $(\phi_1,\phi_2)$ plane, and the third panel shows the stream and background in the $(\phi_1,\varpi)$ plane.
+The second panel shows the stream and background in the $(\phi_1,\phi_2)$ plane, and the third panel shows the stream and background in the $(\phi_1,\varpi)$ plane.
 Points are color-coded according to their membership probability (Eq.~X) \JN{would be good to remove the $\sigma$ bands in this plot.} The weight parameter clearly shows that the model has captured the two prominent density variations along the stream.

### 2023-08-15 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 mass segregation in the progenitor \TODO{[cite]}.
-To date this effect has not been observed \TODO{[cite?]}, so in practice we drop the $\phi_1$ dependence -- $\prior_{\cal{I}}(\gamma, \phi_1) = \prior_{\cal{I}}(\gamma)$ -- assuming that the PDMF is constant along the stream.
+To date this effect has not been observed \TODO{[cite]}, so in practice we drop the $\phi_1$ dependence -- $\prior_{\cal{I}}(\gamma, \phi_1) = \prior_{\cal{I}}(\gamma)$ -- assuming that the PDMF is constant along the stream.
 
             % link to the code!
-            In the code we offer a few ansatz for the PDMF. The default assumption, which is known to be non-physical is a uniform distribution over $\gamma$. Any user-defined function may be used
+            In the code we offer a few ansatz for the PDMF. The default assumption, which is known to be non-physical is a uniform distribution over $\gamma$.
+            Any user-defined function may be used.
 
@@
             \begin{enumerate}
-                \item problems with just a Kroupa -- it's not present day
+                \item problems with just a Kroupa -- it's not present day.
                 \item could parameterize a more general distribution and fit for the PDMF
-                \item we are interested in the photometric model for a number of reasons, but an important one is that we can fit the distance modulus of the stream, for this only a subsection of the isochrone is needed.
+                \item Alternatively, we are interested in the photometric model for a number of reasons, but an important one is that we can fit the distance modulus of the stream, for this only a subsection of the isochrone is needed.
 The best section is the MS turnoff.
@@
             We use \package{dustmaps} Bayestar 19 for the dust modeling. We treat it as known. Include as a source of error in $\Sigma_n$
+            % TODO: actually implement that in the model
 
@@
             The widths are similarly constrained.
-
-            % TODO: include the specific functions?
-            % \begin{align}
-            %     \mu_I(\varpi) &= 10 - 5\log_{10}(\varpi) \\
-            %     \sigma_I(\sigma_\varpi) &= \TODO{\text{write down the equation}}
-            % \end{align}
-
-            \todo[inline]{expand on this}
+            \begin{align}
+                \mu_I(\varpi) &= 10 - 5\log_{10}(\varpi) \\
+                \sigma_I(\sigma_\varpi) &= \frac{5}{\ln{10}} \mu_I \sigma_\varpi
+            \end{align}
+
+            \todo[inline]{expand on this?}
 

### 2023-08-15 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
+\newcommand{\parallax}{\varpi}
 \newcommand{\sigobs}{{\sigma_*}}
@@
     % TODO: rephrase following sentence
-    We develop a flexible Bayesian model framework, using Mixture Density Networks, that allows arbitrary numbers of phase-space dimensions to be incorporated in the model and permits missing phase-space observations.
-
-    % \subsection*{}  Conceptual Description
-
+    We develop a flexible Bayesian model framework, that allows arbitrary numbers of phase-space dimensions to be incorporated in the model and permits missing phase-space observations. 
     Below, we offer a concise overview of our approach, followed by a more in-depth technical explanation in subsequent sections.
-
-        We take a Bayesian approach modeling the stream and background distribution.
-
-        Mixture model are a general formalism for modelling arbitrary conditional density functions.
-
-        In this case we want to model the density function, conditioned on the location along the track.
-
-        However, previously we discussed how stream will vary along the track, with changes in the width and possible gaps.
-        Also observational effects, e.g the distance gradient changes the on-sky width (should this be mentioned earlier?)
-
-        We can take the parameters of the mixture model -- the mixing coefficients and component distribution parameters -- to be general (continuous) functions of the conditioning variable.
-        We do this by modelling the parameters as This is achieved outputs of a feed-forward neural network that takes the conditioning variable as its input.
-This is called a Mixture Density Network (MDN)
+    We start, in \autoref{sub:framing_the_data}, by transforming the astrometric data into
+    a stream-oriented on-sky reference frame ($\phi_1, \phi_2, \parallax, \mu_{\phi_1}^*, \mu_{\phi_2}, v_r)$, for each stream. In this frame, 
+    the stream track lies along $\phi_1$, and the stream density may be described by distributions in the other parameters as injective functions of $\phi_1$.
+    % TODO: ⬆ I think a few more sentences explaining why this is important, feature variations, etc?
+    % However, previously we discussed how stream will vary along the track, with changes in the width and possible gaps.
+    % Also observational effects, e.g the distance gradient changes the on-sky width (should this be mentioned earlier?)
+    Likewise, the background of the Galactic field may be described with $\phi_1$-conditioned distributions.
+    % TODO: ⬆ I think this should be expanded.
+    Even non-astrometric coordinates, e.g. photometry and metallicity, are modelled along the stream and background as functions of $\phi_1$.
+
+    The distributions for the stream and background are collected in a single mixture model that describes the entire field.
+    We take the parameters of the mixture model -- the mixing coefficients and component distribution parameters -- to be general (continuous) functions of the conditioning variable, $\phi_1$.
+This is done using feed-forward neural network that takes the conditioning variable as its input and output the parameter value.
+Mixture models of conditional probability distributions using neural networks are called Mixture Density Networks (MDNs).
+Since the model coefficients may evolve with $\phi_1$, MNDs are well suited to characterize streams (and the background) with all their
+    variations in position, width, and linear density.
 
@@
     \subsection{Framing the Data} \label{sub:framing_the_data}
+
+        As a stream progenitor orbits the Galactic center of mass (GCOM), its orbital path
+        describes an ellipse in the orbital plane. The associated arms of the stream generally
+        align closely with its orbital plane.
+        From a Galactocentric reference frame, an orbital plane assumes the form of a great
+        circle in the observer's celestial "sky," thereby allowing the potential realignment of
+        longitudinal ($\ell$) and latitudinal ($b$) coordinates to a coordinate system aligned
+        with the stream ($\cmp{GCOM}{\phi_1}, \phi_2^{(GCOM)}$). Here, the progenitor is
+        established at the origin, with the stream progressing along
+        $\cmp{GCOM}{\phi_1} (\phi_2^{(GCOM)} \approx 0)$. $\cmp{GCOM}{\phi_1}$ is clearly a good
+        affine parameter along which to construct models and analyze the stream's characteristics.
+
+        However, data observations are not taken from the GCOM, but from  $\sim 8$ kpc distant
+        \citep{GRAVITY2018, Leung2022} in a local frame, typically from vantage points such as
+        Earth or its solar Lagrange points, and subsequently represented in the International
+        Celestial Reference System (ICRS) \citep{ICRS1997}.
+        Restricted as we are to a very local volume, there is no means to observe systems from
+        the more ``intrinsic" reference frames. In our observational frames there is no inherent
+        assurance of effecting a rotation that would similarly align the stream within observer
+        coordinates such that $\phi_2(\phi_1) \approx 0$.
+        Thankfully, most streams are adequately distant from both the Galactic center and the
+        observer, or exhibit orientations such that a rotation a) can be established or
+        b) holds valid.
+
+        Within a Galactocentric framework and expressed in spherical coordinates, streams
+        effectively approximate linear formations on a great circle, wherein a phase angle
+        traverses the entire stream length.
+
+        % Data observations are taken in an (approximately) heliocentric reference frame, e.g. from the Earth or a Lagrange point, and is reported in an ICRS
+        % \citep{ICRS1997} frame. Restricted as we are to a very local volume, there
+        % is no means to observe systems from more ``intrinsic" reference frames, namely from the Galactic center of mass about which orbit satellites such as stellar streams.
+
+        % As the progenitor orbits the Galactic COM (center of mass), its
+        % orbital path describes an elliptical path in an orbital plane. The
+        % progenitor's tidal tails (stream) will likewise lie near the progenitor's
+        % orbital plane. Observing from the Galactic center, an orbital plane lies on a
+        % great circle in the observer's `sky' and it is possible to re-orient the
+        % longitude ($\ell$) and latitude ($b$) to a stream-oriented coordinate system
+        % ($\phi_1, \phi_2$) with the progenitor at the origin and the stream along
+        % $\phi_1 (\phi_2 \approx 0)$. However, our observations are not from the
+        % Galactic center, but approximately 8 kpc distant \citep[for recent
+        % measurements, see][]{GRAVITY2018, Leung2022}. For an arbitrary stream lying
+        % (approximately) along a galactocentric ellipse there is no guaranteed rotation to similarly align the stream in the observer coordinates so that the stream
+        % lies along $\phi_2(\phi_1) \approx 0$. Thankfully, many streams are sufficiently
+        % distant from both the Galaxy and observer or oriented such that a rotation a)
+        % exists, or b) applies to significant lengths of the stream before deviations
+        % become problematic.
+
+        % In a Galactocentric frame and in spherical coordinates  streams are approximately lines on a great circle, with a phase-angle sweeping the length of the stream.
+This, clearly, is a good affine parameter along which to model and study the stream.
 
@@
 
-        \IfFileExists{static/DAG_StreamDensity.pdf}{
         \begin{figure}
             \centering
-                \includegraphics[scale=0.5]{static/DAG_StreamDensity.pdf}
-                \caption{Fill in.}
+            \includegraphics[scale=0.5]{static/model/DAG_StreamDensity.pdf}
+            \caption{Probabilistic Graphical Model of the Mixture Density Network (MDN)}
+            \todo[inline]{todo}
+            \begin{enumerate}
+                \item Do this with \url{https://github.com/daft-dev/daft}
+            \end{enumerate}
             \label{fig:DAG}
         \end{figure}
-        }{
-        }
 
@@
             \begin{align}
-                \prior(\{\mu_I, \mu_\varpi \} | \phi_1) &= \delta( \rm{dist}(\mu_I) - \rm{dist}(\varpi) )(\phi_1), \label{eq:distance_track_prior}
-                % \prior(\{\sigma_I, \sigma_\varpi \}(\phi_1)) &= \delta( \rm{dist}(\mu_I) - \rm{dist}(\varpi) )(\phi_1) \label{eq:distance_width_prior}
+                \prior(\{\mu_I, \mu_\parallax \} | \phi_1) &= \delta( \rm{dist}(\mu_I) - \rm{dist}(\parallax) )(\phi_1), \label{eq:distance_track_prior}
+                % \prior(\{\sigma_I, \sigma_\parallax \}(\phi_1)) &= \delta( \rm{dist}(\mu_I) - \rm{dist}(\parallax) )(\phi_1) \label{eq:distance_width_prior}
             \end{align}
@@
             \begin{align}
-                \mu_I(\varpi) &= 10 - 5\log_{10}(\varpi) \\
-                \sigma_I(\sigma_\varpi) &= \frac{5}{\ln{10}} \mu_I \sigma_\varpi
+                \mu_I(\parallax) &= 10 - 5\log_{10}(\parallax) \\
+                \sigma_I(\sigma_\parallax) &= \frac{5}{\ln{10}} \mu_I \sigma_\parallax
             \end{align}
@@
 
-            In practice, at the distance of many streams the parallaxes are informative and are excluded from most models.
+            In practice, at the distance of many streams the errors in the parallaxes are of order 1 and we excluded the feature from most models.
             % TODO!
@@
 
-            \todo[inline]{}
+            \todo[inline]{this section is very rough}
 
@@
 
-        \todo[inline]{TODO:}
+        \todo[inline]{TODO: how much should be included here?}
 
@@
             \item Normalizing flow - specific pieces
+            \item connective priors
+            \item 
             \item Architecture in the Appendix
@@
 The dashed curve represents the output of our data-driven model, while the solid curve is the ground truth.
-The second panel shows the stream and background in the $(\phi_1,\phi_2)$ plane, and the third panel shows the stream and background in the $(\phi_1,\varpi)$ plane.
+The second panel shows the stream and background in the $(\phi_1,\phi_2)$ plane, and the third panel shows the stream and background in the $(\phi_1,\parallax)$ plane.
 Points are color-coded according to their membership probability (Eq.~X) \JN{would be good to remove the $\sigma$ bands in this plot.} The weight parameter clearly shows that the model has captured the two prominent density variations along the stream.
@@
     $F$ & The number of measured features, e.g.
-$(\alpha, \delta, \varpi, \mu_{\alpha^*}, \mu_\delta, v_r, g, r)$,  not including the the `independent' feature over which the others are conditioned.
+$(\alpha, \delta, \parallax, \mu_{\alpha^*}, \mu_\delta, v_r, g, r)$,  not including the the `independent' feature over which the others are conditioned.
 \\

### 2023-08-20 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     Stellar streams are the disrupted remnants of globular clusters and satellite galaxies, and their census has grown extensively in the Milky Way thanks to all-sky astrometric missions like {\it Gaia} and low-surface brightness photometric surveys (\JN{cite}).
-The formation of streams can be traced back to a progenitor cluster (i.e., a satellite galaxy or globular cluster), whose stars are gradually lost to the tidal field of the host galaxy and extend along a series of similar orbits producing tidal tails which can sometimes span many tens of degrees across the sky.
-This orbital proximity of stars belonging to a stream makes them sensitive detectors of the mass distribution of galaxies, sourced by both the baryonic and dark matter components across a large range of mass-scales.
+The formation of streams can be traced back to a progenitor cluster (i.e., a satellite galaxy or globular cluster), whose stars are gradually lost to the tidal field of the host galaxy and extend along a series of similar orbits producing tidal tails, which can sometimes span many tens of degrees across the sky.
+This orbital proximity of stars belonging to a stream makes them sensitive tracers of the mass distribution of galaxies, sourced by both the baryonic and dark matter components.
 
     The average properties of a stream (e.g., the mean position and velocity track of the tidal tails) can be used to reconstruct the global dark matter distribution of the stellar halo (e.g., \JN{cite}), while local variations in the stream track and surface density encode information about the stream's encounters with baryonic structures such as (e.g.) the stellar bar (\JN{cite}), and non-luminous structures like dark matter subhalos (\JN{cite}).
+Importantly, these galactic components span orders of magnitude in mass, highlighting the importance of characterizing a population of stellar streams both in morphology and kinematics.
 
@@
 In order to generate more precise constraints on the structure of the galaxy, it is therefore imperative that a statistically sound and homogenized catalog of stellar streams is produced so that theoretical models for the gravitational potential of the galaxy across a large range of spatial scales can be constrained.
+
+    While streams are well described in (e.g.) action angle coordinates or $N-$body simulations, these methods relying on prior assumptions about the galaxy and its underlying potential.
+Therefore, it is important to devise data-driven methods to characterize stellar streams without appealing to strong prior assumptions about the galaxy's structure.
+
+    There are a few previous works which have modeled stellar streams in this context.
+\citet{2022MNRAS.514.1757P} developed a data-driven spline-based model for modeling the photometric qualities of previously identified streams.
+Their method works by fitting the stream's stellar surface density with a series of splines, capturing both surface brightness variations along the stream and changes in the position of the stream track and width.
+Their method also utilize a simultaneous ischorone fit to the stream, from which a distance modulus can be derived by assuming that the entire stream originates from the same stellar population.
+While this method is very successful at characterizing the photometric properties of a stream, it does not consider the kinematic dimensions which have become increasing well-measured with successive data releases from {\it Gaia}, as well as targeted observations.
+From a population of RR Lyrae stars, \citet{2019AJ....158..223P} utilized a mixture model to fit the globular cluster stream Pal-5 in the space of proper motions and heliocentric distances.
+The mixture modeling approach enables a simultaneous fit to both the stream and background density, enabling better separation of a coherent stream from an otherwise noisy background distribution.
+However, the track of the stream in on-sky coordinates is not fit.
+The method identified 27 RR Lyrae stars consistent with being members of the stream.
+While useful for determining the average properties of the stream (e.g., its mean distance track), a limited population of RR Lyrae stars are not sufficient to capture the fine-grained properties of streams expected to inform constraints on (e.g.) a population of perturbers in the galaxy.
+\JN{are there other methods?}
+
+    Other methods for extracting stellar streams from the data include matched-filter approaches, where over-densities in color-magnitude space are inspected as possible clusters undergoing tidal stripping \JN{cite the many key papers using this method}.
+While the matched-filter technique has been extremely successful at stream discovery, it is not equipped to characterize streams at the level of detailed necessary to inform precise constraints on the potential of the galaxy and its substructure.
+
+    In order to address the need for a flexible model of stellar streams both in photometric and kinematic spaces, in this work we develop a new method for characterizing streams and quantifying the membership probability of possible stream stars.
+Our approach provides several key advantage over previous stream modeling efforts, specifically in its ability to jointly model the kinematic and photometric properties of streams simultaneously.
+Furthermore, our method is well-suited to fitting streams with only partial or incomplete phase-space or photometric observations, enabling a full characterization of streams insofar as the available data allows.
 
@@
         first to simulated data (\autoref{sub:mock_data}) to demonstrate the model with a known ground truth dataset,
-        then to the stellar streams \stream{GD-1} (\autoref{sub:gd1}) and \stream{Pal\,5} (\autoref{sub:pal5}).
+        then to the stellar streams \stream{GD-1} (\autoref{sec:results_gd1}) and \stream{Pal\,5} (\autoref{sub:pal5}).
         We compare our approach to characterizing stellar streams to other methods in \autoref{sec:comparison}.
@@
     % TODO: ⬆ I think this should be expanded.
-    Even non-astrometric coordinates, e.g. photometry and metallicity, are modelled along the stream and background as functions of $\phi_1$.
+    Non-astrometric coordinates, e.g. photometry and metallicity, are also modelled along the stream and background as functions of $\phi_1$.
 
@@
         From a Galactocentric reference frame, an orbital plane assumes the form of a great
-        circle in the observer's celestial "sky," thereby allowing the potential realignment of
+        circle in the observer's celestial ``sky," thereby allowing the potential realignment of
         longitudinal ($\ell$) and latitudinal ($b$) coordinates to a coordinate system aligned
@@
         observer, or exhibit orientations such that a rotation a) can be established or
-        b) holds valid.
-
-        Within a Galactocentric framework and expressed in spherical coordinates, streams
-        effectively approximate linear formations on a great circle, wherein a phase angle
-        traverses the entire stream length.
-
-        % Data observations are taken in an (approximately) heliocentric reference frame, e.g. from the Earth or a Lagrange point, and is reported in an ICRS
-        % \citep{ICRS1997} frame. Restricted as we are to a very local volume, there
-        % is no means to observe systems from more ``intrinsic" reference frames, namely from the Galactic center of mass about which orbit satellites such as stellar streams.
-
-        % As the progenitor orbits the Galactic COM (center of mass), its
-        % orbital path describes an elliptical path in an orbital plane. The
-        % progenitor's tidal tails (stream) will likewise lie near the progenitor's
-        % orbital plane. Observing from the Galactic center, an orbital plane lies on a
-        % great circle in the observer's `sky' and it is possible to re-orient the
-        % longitude ($\ell$) and latitude ($b$) to a stream-oriented coordinate system
-        % ($\phi_1, \phi_2$) with the progenitor at the origin and the stream along
-        % $\phi_1 (\phi_2 \approx 0)$. However, our observations are not from the
-        % Galactic center, but approximately 8 kpc distant \citep[for recent
-        % measurements, see][]{GRAVITY2018, Leung2022}. For an arbitrary stream lying
-        % (approximately) along a galactocentric ellipse there is no guaranteed rotation to similarly align the stream in the observer coordinates so that the stream
-        % lies along $\phi_2(\phi_1) \approx 0$. Thankfully, many streams are sufficiently
-        % distant from both the Galaxy and observer or oriented such that a rotation a)
-        % exists, or b) applies to significant lengths of the stream before deviations
-        % become problematic.
-
-        % In a Galactocentric frame and in spherical coordinates  streams are approximately lines on a great circle, with a phase-angle sweeping the length of the stream.
-This, clearly, is a good affine parameter along which to model and study the stream.
-
-        {\color{red} Assume we know a stream track}
-
-        Instead we will approach this in the standard way: by parameterizing the stream along its the longitude -- $w_{\cdot, j\equiv0} \equiv \phi_1$ -- in a stream-oriented reference frame.
-        $\phi_1$ becomes our conditioning variable.
-
-        \begin{quotation}
-            The stream is projected from its initial reference frame, e.g. ICRS
-            \citep{ICRS1997}, into a rotated on-sky frame, with longitude $\phi_1$ and
-            latitude $\phi_2$, such that the stream extends along $\phi_1$. In this frame
-            the stream may be fit by a low-order polynomial as a function of $\phi_1$
-            \citep[e.g.][]{Bonaca2020}. Similar, if more sophisticated, methods swap tools
-            like univariate splines \citep[e.g.][]{Erkal2017, Bonaca2018} for the
-            low-order polynomials. Using a coordinate dimension, here $\phi_1$, as the
-            independent variable works for many streams, as $\phi_1$ sweeps monotonically
-            along the stream. For example \stream{GD-1} is straight for over 80 degrees
-            \citep{Webb2019, Price-Whelan2018}.
-        \end{quotation}
-
-        There are known to be issues with this...
-
-        \begin{quotation}
-            However, this is not true in general: a
-            stream's path can become kinked by subhalo interactions, or curved on the
-            celestial sphere in an observer's reference frame, or like the Magellanic
-            stream wrap multiple times around the Milky Way \citep{Wannier1972}. When a
-            stream track is not a function, methods fitting $\phi_2(\phi_1)$ fail.
-        \end{quotation}
-
-        We leave extending the model framework to phase-wrapped, doubled-backed paths, etc to a future work.
+        b) holds valid. For most of the best-studied globular cluster streams -- \stream{GD-1},
+        \stream{Palomar 5}, \stream{Jhelum}, etc. -- this holds true. However for some streams
+        of dwarf galaxies, like the Magellanic stream which wraps multiple times around the
+        Milky Way \citep{Wannier1972}, no such transformation is possible. More generally,
+        a stream's ``sky"-projected path may be kinked, e.g. by subhalo interactions, such
+        that it is a many-to-one function in $\phi_1$.
+
+        In this work we treat with the vast majority of streams, which have a ``sky" transformation such that the stream is an injective function in $\phi_2(\phi_1)$.
+        Since we are examining known streams this transformation is known \textit{a priori}, or
+        may be constructed during pre-processing \citep[see][\S2.1]{StarkmanEtAl2023}.
+        We note that, with sufficient prior knowledge, many-to-one functions may be broken into injective segments and their connection constrained by a prior. Thus the methods
+        developed subsequently may extented and applied even to wrapped and kinked streams. However, 
+        we leave extending the model framework to a future work.
 
@@
             \begin{enumerate}
-                \item Do this with \url{https://github.com/daft-dev/daft}
+                \item remake this example this with \url{https://github.com/daft-dev/daft}.
             \end{enumerate}
@@
 These distributions are characterized by their parameters and the mixture by a corresponding set of mixture coefficients.
-Scalar mixture models may be extended to model completely general conditional distributions by making the distribution parameters and mixture coefficients functions of a conditional input \citep{McLachlan1989MixtureM}.
+Scalar mixture models may be extended to model completely general conditional distributions by making the distribution parameters and mixture coefficients into functions of a conditional input \citep{McLachlan1989MixtureM}.
         Mixture Density Networks (MDNs) are a machine learning method to implement these general MM, taking the parameters and coefficients to be the outputs of feed-forward neural networks and as such, general continuous functions \citep{Bishop1994}.
-Functional parameters allows the model to capture variation over those parameters that is not possible with scalar-valued models.
+Functional parameters allow the model to capture variation over those parameters that is not possible with scalar-valued models.
 Moreover, by using neural networks the inferred functional forms are ``model-free" and driven entirely by the data.
@@
 The parameters of the stream, the background field, and the mixing coefficients of the two are now general data-driven continuous functions along $\phi_1$.
-        {\color{cyan} \\ connecting to intro...
-
-            The hypertube idea is connected to orbits.
-            One might think then that a variable like the phase-angle or the arc-length, or any variable that directly sweeps along the stream would be best to use as the conditioning variable.
-            This is not the case for a number of reasons (see \cite{StarkmanEtAl2023} for some discussion on this topic), not least of which is that we do not have any of these quantities.
-We do not know the stream track, it's what we want to know.
-        }
 
@@
             \!\!\! \pdf(\nth{\mbs{x}} | \mbs{\theta}(\phi_1))
-            \!=\! \sum_{\mrm{q} \in \mbs{I_Q}} \! \qth{f}(\phi_1) \cmp{q}{\pdf}(\nth{\mbs{x}}|\qth{\mbs{\theta}}(\phi_1))
+            \!=\! \sum_{\mrm{q} \in \mbs{I_Q}} \! \qth{f}(\phi_1) \cmp{q}{\pdf}(\nth{\mbs{x}}|\qth{\mbs{\theta}}(\phi_1)),
             % \prior(\nth{\mbs{x}}, \phi_1)
         \end{equation}
-        where $\pdf_q$ is the PDF of the $q$-th model and $f_q$ its mixing coefficient for all $q$ models in the set of models indexed by $\mbs{I_Q}$.
+        where $\cmp{q}{\pdf}$ is the PDF of the $q$-th model and $f_q$ its mixing coefficient for all $q$ models in the set of models indexed by $\mbs{I_Q}$.
 $\mbs{\theta}$ is the $\phi_1$-conditional output of the feed-forward neural network, and $\nth{\mbs{x}}$ the data on the $n$-th star in $\mbs{X}$, not including $\phi_1$.
-For convenience we drop the implied subscript $n$ in $\phi_1$.
+For convenience we drop the implied subscript $n$ in $\phi_1$, the explicit notation of $\mbs{\theta}$'s dependence on $\phi_1$, and the index set $\mbs{I}_X$ in summations over its elements $x$.
 A full detailing of notation and symbols is included in \autoref{app:notation}.
-For convenience we drop the explicit notation of $\mbs{\theta}$'s dependence on $\phi_1$ and the index set $\mbs{I}_X$ in summations over its elements $x$.
 
@@
 
+    \vspace{10pt}
     \subsection{Determination of the Mixture Weight} \label{sub:mixture_weight}
@@
         \begin{equation}
-            N_q\left(\phi_1\right) = f_q N_{\rm tot} \left(\phi_1\right)  = f_q \left[N_{\rm tot,0} P_{\phi_1}\left(\phi_1\right) \right] .
+            N_q\left(\phi_1\right) = f_q N_{\rm tot} \left(\phi_1\right)  = f_q N_{\rm tot,0} P_{\phi_1}\left(\phi_1\right) .
         \end{equation}
@@
             where $\astroM{\mbs{\theta}}$ is the set of neural network parameters that define $\astroM{\mbs{\mu}}$ and $\astroM{\mbs{\Sigma}}$; and $\cmp{w}{\nth{\mbs{\Sigma}}}$ the data uncertainties.
-            In the simplest case, we take $\astroM{\mbs{\Sigma}}$ to be diagonal, consisting of both intrinsic dispersion for each dimension of $\mbs{w}$ and the data uncertainties added in quadrature.
+            In the simplest case, we take $\cmp{w}{\nth{\mbs{\Sigma}}}, \astroM{\mbs{\Sigma}}$ to be diagonal, consisting of both intrinsic dispersion for each dimension of $\mbs{w}$ and the data uncertainties added in quadrature.
 The data uncertainties $\cmp{w}{\nth{\mbs{\Sigma}}}$ are drawn from $\mbs{\delta}\mbf{W}$, the dataset of astrometric uncertainties (see \autoref{app:notation}).
@@
             In the presence of missing phase-space coordinate $f_k$ we reduce the dimensionality of the Gaussian to that of the data-vector.
-Namely, for $\mbs{I}_{\tilde{F}} = \mbs{I}_{F} \backslash \{f_k\}$
+Namely, for $\mbs{I}_{\tilde{F}} \equiv \mbs{I}_{F} \backslash \{f_k\}$
             \begin{align}
@@
             \begin{multline} \label{eq:photometric_probability_point}
-                \cmp{S,m}{P}(\mbs{m_i}, \gamma | \mbs{\theta}(\phi_1)) 
+                \cmp{S,m}{\pdf}(\mbs{m_i}, \gamma | \mbs{\theta}(\phi_1)) 
                 \\ \sim \mcal{N}(\nth{\mbs{m}} | \{\mcal{I(\gamma)} + \mu(\phi_1), \mbs{\Sigma}_{\mcal{I}}^2(\gamma) + \mathds{1} \sigma_\mu^2(\phi_1) + {\cmp{m}{\nth{\mbs{\Sigma}}}}^2 \}) \\ \times \prior(\gamma, \nth{\mbs{m}}, \phi_1),
@@
             \begin{align} \label{eq:photometric_probability}
-                &\cmp{S,m}{P}(\nth{\mbs{m}} | \mbs{\theta}(\phi_1)) = \\
+                &\cmp{S,m}{\pdf}(\nth{\mbs{m}} | \mbs{\theta}(\phi_1)) = \\
                 &\ \int\limits_{\gamma=0}^{1} \mcal{N}(\nth{\mbs{m}} | \{\mcal{I(\gamma)} + \mu(\phi_1), \mbs{\Sigma}_{\mcal{I}}^2(\gamma) + \mathds{1}\sigma_\mu^2(\phi_1) + {\cmp{m}{\nth{\mbs{\Sigma}}}}^2 \}) \nonumber
@@
             % link to the code!
-            In the code we offer a few ansatz for the PDMF. The default assumption, which is known to be non-physical is a uniform distribution over $\gamma$.
-            Any user-defined function may be used.
+            In the code we offer a few ansatz for the PDMF, though any user-defined function may be used instead.
+The default assumption, which is known to be non-physical is a uniform distribution over $\gamma$.
+Similarly are truncated uniform distributions, considering only a segment of the isochrone, e.g.
+the main sequence turnoff (MSTO).
+We include also a Kroupa initial mass function (IMF) \citep{2001MNRAS.322..231K}.
+The Kroupa IMF, and all physically-motivated IMFs,
+            have an much larger fraction of low-mass stars then high-mass stars, the latter being less likely to form.
+This is observed in streams, particularly their progenitors.
+However the Kroupa IMF, and all IMF, are poor fits to the observed PDMF as stream progenitors like globular clusters are extremely old ($\sim10$ Gyr) while an IMF is the zero-age distribution.
+            How then should the PDMF $\prior_{\cal{I}}$ be treated?
+            % ⬆ rephrase previous sentence
+            One approach to the PDMF is to use a more informed distribution, for example time-evolving an IMF, either analytically or by simulation.
+            Using any fixed distribution is simple in implementation, however the choice of distribution is not \TODO{[cite]}.
+            There is large uncertainty in the PDMF of most globular clusters.
+            % ⬆ rephrase previous sentence
+
+            Similarly, the PDMF might be incorporated into the model,
+            parameterized by some distribution and fit simultaneously to the distance modulus and other $\cmp{m}{\mbs{\theta}}$.
+            Using a fixed distribution is a simple matter, however 
+            \TODO{[cite]}
+
+            characterizing the stream PDMF, and the
+
+            % Mention uniform modeling?
+            An alternative approach to the PDMF issue is to restrict the mass range of the isochrone such that the PDMF is unimportant.
+            This restriction means we are not modeling the full range of the 
+            photometric data and not
 
@@
             \begin{enumerate}
-                \item problems with just a Kroupa -- it's not present day.
                 \item could parameterize a more general distribution and fit for the PDMF
@@
             \end{align}
+            % TODO: should we show that these are different distance functions? or is it obvious
             where $\delta$ is the Dirac delta function, and simply expresses that the distance modulus track and parallax track must be equal (when converted to the actual distance) as a function of $\phi_1$.
@@
                 \mu_I(\parallax) &= 10 - 5\log_{10}(\parallax) \\
-                \sigma_I(\sigma_\parallax) &= \frac{5}{\ln{10}} \mu_I \sigma_\parallax
+                \sigma_I(\sigma_\parallax)  &= \frac{5}{\ln{10}} \mu_I \lvert\sigma_\parallax\rvert
             \end{align}
 
-            \todo[inline]{expand on this?}
-
-            In practice, at the distance of many streams the errors in the parallaxes are of order 1 and we excluded the feature from most models.
+            In practice, at the distance of many streams the errors in the parallaxes are of order 1 and we exclude the feature from the model.
             % TODO!
@@
             In this section we introduce our model for the distribution of backgrounds in photometric coordinates. 
-
             In general, the distribution of stars in color (i.e., $g-r$) and magnitude (i.e., $g$) is a complicated function of location in the galaxy \TODO{(e.g.
@@
 When one (or more) feature dimension is missing, however, evaluating the marginal log-likelihood involves integrals over the flow.
-While the procedure is straightforward procedure, it is computationally expensive.
+While the procedure is straightforward it is computationally expensive.
 As an alternative, we conservatively set the log-likelihood to $0$, the maximum value, overemphasizing the flow's contribution to the background model.
@@
 Another approach, which we leave to a future work, is to construct normalizing flows of each marginal distribution, e.g.
-$q_{\rm flow}\left(\{m_i\}_{i \in \mbs{I}_F, i \neq {j, k}} | m_j, m_k, \phi_1\right)$, and select for each $\nth{\mbs{m}}$ the correct flow given the missing features.
+$q_{\rm flow}\left(\{m_i\}_{i \in \mbs{I}_F, i \neq {j, k}} | m_j, m_k, \phi_1\right)$, and select for each $\nth{\mbs{m}}$ the correct flow given the features.
 
@@
 
-    % \vspace{10pt}
-
-    % \subsection[Astrometric Background]{Astrometric Background: pieces of $\Bcmp{P}(\mbs{w})$} \label{sub:background_astrometric}
-
-    %     When looking for a stellar stream, the highly complex Galaxy is the background.
-There are numerous approaches to modeling a complex structure, from a mix of very simple models to a single highly flexible model, like a basis function expansion or ML network.
-    %     We aim towards the mix of simple models, but use more flexible models as needed.
-In this section we describe the various models used when modeling the background, in different coordinates of the phase space.
-
-        % \subsubsection{Flat Background} \label{ssub:flat_background}
-
-        %     The simplest possible background is the flat background.
-        %     Perhaps surprisingly, the Galaxy around GD-1 is well modeled by a flat distribution in the $\phi_2(\phi_1)$ phase space.
-        %     For a domain $x \in [a, b]$ the normalized PDF is given by
-        %     \begin{align}
-        %         \pdf(x|a,b) &= \frac{1}{b-a} & \text{and} \\
-        %         \ln \pdf(x | a, b) &= -\ln\left({b-a}\right)
-        %     \end{align}
-        %     where $a,b$ are the $\phi_2$ bounds of the data selection box.
-
-        % % subsubsection flat_background (end)
-
-        % \subsubsection{Exponential-like Background} \label{ssub:exponential_background}
-
-        %     In many coordinate axes, the distribution of the background data is better described by an exponential distribution.
-        %     The unit-normalized exponential distribution in the domain $[a, b]$ ($a \neq b$) is given by:
-        %     \begin{equation}\label{eq:exp_distr}
-        %         f(x) = \frac{m \Exp{-m (x - a))}}{1 - \Exp{-m(b - a)}}.
-        %     \end{equation}
-        %     However for $m \rightarrow 0$, which describes the flat distribution (\autoref{ssub:flat_background}), this functional form can be numerically unstable, particularly with lower bit precision numerics like \texttt{float32} data-types.
-In the context of ML, the numerical instability is problematic when employing parameter drop-out for $m$.
-While for parameter dropout this might be avoided by re-parameterizing to $m+\epsilon$, the numerical instability remains and may be encountered later, creating a difficult-to-diagnose \texttt{NaN}.
-        %     For both compatibility with the flat distribution and for practical reasons we modify the above distribution and approximate the exponential distribution with a 3rd order expansion around $m=0$ when $|m| < \epsilon$, for some small $\epsilon$.
-
-        % % subsubsection exponential_background (end)
-
-        %% PLOT HERE OF ALL THE BACKGROUNDS?? **
-
-    % subsection astrometric background (end)
-
-        % Let $\Omega$ be the independent variable in $\mbf{w}$.
-
-        % $\pdf(m_i | ) \rm{KDE(\mbf{m}_i|\omega_{i} )}$
-
     % subsection photmetric background (end)
-
-        \begin{figure}
-            \script{mock/plot/photometric_background_selection.py}
-            \centering
-            \includegraphics[width=1\linewidth]{figures/mock/photometric_background_selection.pdf}
-            \caption{Caption: TO-DO need to show this with a ground truth (e.g. show true weight in top panel).}
-            \label{fig:mock_data_photometric_background_selection}
-        \end{figure}
 
@@
         \subsubsection{Region Prior} \label{sub:track_region_prior}
+
+            \todo[inline]{this section is very rough}
 
@@
         Dropout layers were used to prevent network co-adaptation and over-fitting.
-Droput works by randomly zeroing out nodes in the network, decreasing the importance of single nodes versus emergent patterns across the  network.
+Dropout works by randomly zeroing out nodes in the network, decreasing the importance of any single node, encouraging instead emergent patterns across the network.
 
@@
 %\newpage
-\section{Results} \label{sec:results}
+\section{Results: Mock} \label{sec:results_mock}
 
     In this section we present an application of our model to a synthetic stream with known ground truths, and demonstrate the model's ability to characterize stream density variations and membership probabilities in an unsupervised manner.
-We then apply the method to real stellar streams in \autoref{sub:gd1} and \autoref{sub:pal5}.
+We then apply the method to real stellar streams in \autoref{sec:results_gd1} and \autoref{sub:pal5}.
 
@@
 The number of stream stars is $\variable{output/mock/nstream_variable.txt}$, while the number of background stars is $\variable{output/mock/nbackground_variable.txt}$.
+
+        \begin{figure}
+            \script{mock/plot/photometric_background_selection.py}
+            \centering
+            \includegraphics[width=1\linewidth]{figures/mock/photometric_background_selection.pdf}
+            \caption{Caption: TODO need to show this with a ground truth (e.g. show true weight in top panel).}
+            \label{fig:mock_data_photometric_background_selection}
+        \end{figure}
 
@@
 
-    \subsection{Results on GD-1} \label{sub:gd1}
-
-        We now apply our density modeling approach to the stellar stream GD-1. We discuss the data selection in \autoref{ssub:gd1_data} and results in \autoref{ssub:trained_gd1}.
-
-        \subsubsection{Data Selection} \label{ssub:gd1_data}
+\section{Results: GD-1} \label{sec:results_gd1}
+
+        We now apply our density modeling approach to the stellar stream GD-1. We discuss the data selection in \autoref{ssec:results_gd1_data} and results in \autoref{ssub:trained_gd1}.
+
+        \subsubsection{Data Selection} \label{ssec:results_gd1_data}
 
@@
 In order to guide our model towards GD-1, we set down 4 ``control points" along GD-1's main track, and 3 control points along the spur (illustrated in \JN{x}).
-These control points act as gaussian priors on the model.
+These control points act as Gaussian priors on the model.
 We set the Gaussian error on these control points to large values, so that their influence on the model is not dominant.

### 2023-08-20 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 Another approach, which we leave to a future work, is to construct normalizing flows of each marginal distribution, e.g.
-$q_{\rm flow}\left(\{m_i\}_{i \in \mbs{I}_F, i \neq {j, k}} | m_j, m_k, \phi_1\right)$, and select for each $\nth{\mbs{m}}$ the correct flow given the features.
+$q_{\rm flow}\left(\{m_i\}_{i \in \mbs{I}_F, i \neq {j, k}} | m_j, m_k, \phi_1\right)$, and select for each $\nth{\mbs{m}}$ the correct flow given the present features.
 
@@
 
-        \begin{figure*}
-            \script{mock/plot/results.py}
-            \centering
-            \includegraphics[width=1\linewidth]{figures/mock/results.pdf}
-            \caption{Caption: .}
-            TODO:
-            \begin{enumerate}
-                \item the linear density in the stream-fraction plot
-            \end{enumerate}
-            \label{fig:mock_data_result}
-        \end{figure*}
-
     \subsection{Priors} \label{sub:priors}
@@
         \subsubsection{Parameter Bounds}
+
+            We implement hard bounds on the range of each parameter $\theta$.
 
@@
 Thus, the synthetic data scenario described here generates a mock stream in astrometric coordinates and photometric coordinates, with density variations, a distance gradient which is consistent in parallax and distance modulus (i.e., magnitudes), all superimposed over a noisy field of background points in each astrometric and photometric dimension.
+
+        \begin{figure*}
+            \script{mock/plot/results.py}
+            \centering
+            \includegraphics[width=1\linewidth]{figures/mock/results.pdf}
+            \caption{Caption: .}
+            TODO:
+            \begin{enumerate}
+                \item the linear density in the stream-fraction plot
+            \end{enumerate}
+            \label{fig:mock_data_result}
+        \end{figure*}
 

### 2023-08-20 src/tex/ms.tex
[showyourwork] overleaf sync

@@
             \includegraphics[width=1\linewidth]{figures/mock/photometric_background_selection.pdf}
-            \caption{Caption: TODO need to show this with a ground truth (e.g. show true weight in top panel).}
+            \caption{
+                % 
+                \textbf{Top panel:} Astrometric coordinates ($\phi_1$, $\phi_2$) for the mock data set.
+                Light blue points are the stream and background within an ``on"-stream region. Black points are in the ``off"-stream region used to train the background photometric model.
+                % 
+                \textbf{Bottom panel:} Astrometric coordinates ($\phi_1$, $\phi_2$) for the mock data set.
+                Black points are in the ``off"-stream region from the region defined in the astrometric coordinates.
+                Light blue points are the stream and background from the on-stream region. The stream's isochrone is apparent as an overdensity around (g-r, g)$\approx (0, 20)$.
+            }
             \label{fig:mock_data_photometric_background_selection}
@@
 The second panel shows the stream and background in the $(\phi_1,\phi_2)$ plane, and the third panel shows the stream and background in the $(\phi_1,\parallax)$ plane.
-Points are color-coded according to their membership probability (Eq.~X) \JN{would be good to remove the $\sigma$ bands in this plot.} The weight parameter clearly shows that the model has captured the two prominent density variations along the stream.
+Points are color-coded according to their membership probability \autoref{eq:membership_prob}.
+The weight parameter clearly shows that the model has captured the two prominent density variations along the stream.
 The are additional variations  mostly around the edges of the stream, though re-sampling the neural network weights with dropout reveals that these variations represent regions of higher model uncertainty.

### 2023-08-21 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \usepackage{showyourwork}
-\usepackage{amsmath}
+\usepackage{amsmath, amssymb}
 \usepackage{xcolor}
@@
 \usepackage{dsfont}
+\usepackage[inline]{enumitem}
 \usepackage{todonotes}
@@
             \includegraphics[width=1\linewidth]{figures/mock/results.pdf}
-            \caption{Caption: .}
+            \caption{
+                %
+                \textbf{Top panel:}%
+                The stream mixture coefficient $f(\phi_1)$ 
+                Stream fraction.
+                %
+                \textbf{Middle panel:}%
+                $\phi_2(\phi_1)$
+                %
+                \textbf{Lower panel 3:}%
+                %
+                \textbf{Upper Histograms:}%
+                %
+                \textbf{Upper Middle Histograms:}%
+                %
+                \textbf{Lower Middle Histograms:}%
+                %
+                \textbf{Lower Histograms:}%
+            }
             TODO:
@@
 
-            \variable{output/gd1/select_members.tex}
+            \variable{output/gd1/member_table_select.tex}
 
@@
 
-    The data availability statement is modified from
+    The data availability statement is modified from one provided to ShowYourWork by Mathieu Renzo.
 
@@
         \package{SciPy} \citep{Scipy2020},
+        \package{ShowYourWork} \citep{}
 
@@
     \todo[inline]{zenodo url}. The git repository associated
-    with this study is publicly available at $\GitHubURL{}$.
+    with this study is publicly available at \GitHubURL{}.
 

### 2023-08-21 src/tex/ms.tex
[showyourwork] overleaf sync

@@
         We discuss the data in \autoref{sub:framing_the_data} and build a probabilistic framework to model the stream and background in \autoref{sub:likelihood_setup}-\autoref{sub:priors}.
-        In \autoref{sec:results} we apply our method,
-        % TODO: rephrase the mock data
-        first to simulated data (\autoref{sub:mock_data}) to demonstrate the model with a known ground truth dataset,
-        then to the stellar streams \stream{GD-1} (\autoref{sec:results_gd1}) and \stream{Pal\,5} (\autoref{sub:pal5}).
+        In \autoref{sec:results_mock} we apply our method to simulated data (\autoref{sub:mock_data}) to demonstrate the model with a known ground truth dataset,
+        then to the stellar streams \stream{GD-1} (\autoref{sec:results_gd1}) and \stream{Pal\,5} (\autoref{sec:results_pal5}).
         We compare our approach to characterizing stellar streams to other methods in \autoref{sec:comparison}.
@@
             \caption{Probabilistic Graphical Model of the Mixture Density Network (MDN)}
-            \todo[inline]{todo}
+            \todo[inline]{TODO:}
             \begin{enumerate}
-                \item remake this example this with \url{https://github.com/daft-dev/daft}.
+                \item remake this example this with \url{https://github.com/daft-dev/daft}. See \url{https://en.wikipedia.org/wiki/Mixture_model} for examples.
             \end{enumerate}
@@
 
-            The photometric probability, \autoref{eq:photometric_probability} includes the term $\prior(\gamma, \nth{\mbs{m}}, \phi_1)$, which encodes all priors on both the isochrone as well as observational constraints.
-It is safe to assume that the properties of the isochrone are conditionally independent from observational constraints; namely
+            The photometric probability, \autoref{eq:photometric_probability}, includes the term $\prior(\gamma, \nth{\mbs{m}}, \phi_1)$, which encodes all priors on both the isochrone as well as observational constraints.
+We assume that the properties of the isochrone are conditionally independent from observational constraints; namely
             \begin{equation} \label{eq:isochrone_prior_components}
@@
 Physically, this amplitude is the the present-day mass function (PDMF).
-We include the PDMF as $\prior_{\cal{I}}(\gamma, \phi_1)$.
-$\prior_{\cal{I}}$ is a joint distribution, depending on $\gamma$ since it is the $\gamma$-dependent distribution amplitude, and also on $\phi_1$.
-This latter dependence is confusing termed the ``mass function of the stream", which is the expected variation in the average stellar mass along the stream, due to e.g.
+We The PDMF $\prior_{\cal{I}}(\gamma, \phi_1)$ is a joint distribution, depending on $\gamma$ since it is the $\gamma$-dependent distribution amplitude, and also on $\phi_1$.
+This latter dependence is confusingly termed the ``mass function of the stream", which is the expected variation in the stellar mass distrubion along the stream, arising due to e.g.
 mass segregation in the progenitor \TODO{[cite]}.
-To date this effect has not been observed \TODO{[cite]}, so in practice we drop the $\phi_1$ dependence -- $\prior_{\cal{I}}(\gamma, \phi_1) = \prior_{\cal{I}}(\gamma)$ -- assuming that the PDMF is constant along the stream.
+To date this variation along the stream has not been observed \TODO{[cite]}, so in practice we drop the $\phi_1$ dependence -- $\prior_{\cal{I}}(\gamma, \phi_1) = \prior_{\cal{I}}(\gamma)$ -- assuming that the PDMF is constant along the stream.
 
@@
             In the code we offer a few ansatz for the PDMF, though any user-defined function may be used instead.
-The default assumption, which is known to be non-physical is a uniform distribution over $\gamma$.
-Similarly are truncated uniform distributions, considering only a segment of the isochrone, e.g.
+The default assumption, known to be non-physical, is a uniform distribution over $\gamma$.
+Similarly non-physical are truncated uniform distributions, considering only a segment of the isochrone, e.g.
 the main sequence turnoff (MSTO).
@@
             % ⬆ rephrase previous sentence
-            One approach to the PDMF is to use a more informed distribution, for example time-evolving an IMF, either analytically or by simulation.
-            Using any fixed distribution is simple in implementation, however the choice of distribution is not \TODO{[cite]}.
-            There is large uncertainty in the PDMF of most globular clusters.
-            % ⬆ rephrase previous sentence
-
+            One approach to the PDMF is to use a more informed distribution, for example time-evolving an IMF, either analytically or by simulation, to the age of the stream's stellar population.
+            As discussed previously, globular clusters are known to be poorly fit by theoretic isochrones with realistic inputs (e.g.
+age, $Z$).
+Thus fitting an isochrone's track to the data means its age, metallicity and therefore PDMF
+            are not well fit \TODO{[cite]}. Moreover, for many streams, e.g. those lacking known progenitors, the PDMF is observationally poorly constrained.
+            In short, using any fixed distribution is simple in implementation, however the choice of distribution is not.
+
+            Rather than using a fixed \textit{a priori} 
             Similarly, the PDMF might be incorporated into the model,
@@
     In this section we present an application of our model to a synthetic stream with known ground truths, and demonstrate the model's ability to characterize stream density variations and membership probabilities in an unsupervised manner.
-We then apply the method to real stellar streams in \autoref{sec:results_gd1} and \autoref{sub:pal5}.
+We then apply the method to real stellar streams in \autoref{sec:results_gd1} and \autoref{sec:results_pal5}.
 
@@
 
-        We now apply our density modeling approach to the stellar stream GD-1. We discuss the data selection in \autoref{ssec:results_gd1_data} and results in \autoref{ssub:trained_gd1}.
-
-        \subsubsection{Data Selection} \label{ssec:results_gd1_data}
+    We now apply our density modeling approach to the stellar stream GD-1. We discuss the data selection in \autoref{sub:results_gd1_data} and results in \autoref{ssub:trained_gd1}.
+
+    \subsection{Data Selection} \label{sub:results_gd1_data}
 
@@
 
-        \subsubsection{Model Specification}\label{sec:GD_1_ModelSpecification}
+    \subsection{Model Specification}\label{sec:GD_1_ModelSpecification}
 
@@
 
-        \subsubsection{Trained Density Model}\label{ssub:trained_gd1}
+    \subsection{Trained Density Model}\label{ssub:trained_gd1}
 
@@
 
-    \subsection{Palomar 5} \label{sub:pal5}
+\section{Palomar 5} \label{sec:results_pal5}
 
@@
 
-    % subsection pal5 (end)
+% section pal5 (end)
 

### 2023-08-21 src/tex/ms.tex
[showyourwork] overleaf sync

@@
                 \\
-                &\qquad \times \prior(\gamma, \nth{\mbs{m}}, \phi_1) \rm{d}\gamma. \nonumber
+                &\qquad \times \prior(\gamma, \nth{\mbs{m}} | \phi_1) \rm{d}\gamma. \nonumber
             \end{align}
@@
             Let $\cmp{S,m}{\mbs{\theta}}(\phi_1)$ represent the feed-forward neural network which outputs a vector of parameters characterizing the stream's photometric distribution at a given $\phi_1$.
-The network has 2 outputs -- $\mu, \Sigma_\mu$ -- as we only consider the distance track of the isochrone, holding fixed stellar population parameters internal to modeling the isochrone, such as its age and metallicity.
+The network has 2 outputs -- $\mu, \sigma_\mu$ -- as we only consider the distance track of the isochrone, holding fixed stellar population parameters internal to modeling the isochrone, such as its age and metallicity.
             In principle we might include parameters of the isochrone in the model, now $\mcal{I}(\mbs{\theta}, \gamma)$, where $\theta = {a, Z, ...}$ and any other generating parameters of the isochrone.
@@
             does not meaningfully contribute to constraining results on the stream's stellar population.
-Moreover, age and metallicity are partially degenerate with the distance modulus.
+Moreover, age and metallicity are partially degenerate with the distance modulus, working counter to the goal of fitting a distance track to the stream.
 An alternate approach is to use data-driven isochrones instead of theoretic ones.
-In some forms of this approach the age and metallicity are not meaningful quantities.
+the age and metallicity are not meaningful quantities.
 In others, e.g.
@@
 
-            The photometric probability, \autoref{eq:photometric_probability}, includes the term $\prior(\gamma, \nth{\mbs{m}}, \phi_1)$, which encodes all priors on both the isochrone as well as observational constraints.
+            The photometric probability, \autoref{eq:photometric_probability} encodes the photometric distribution -- the ``track" -- of the isochrone model at each point along the track, as well as the amplitudes, the relative probability of points along the track.
+This is the term $\prior(\gamma, \nth{\mbs{m}}, \phi_1)$, which encodes all priors on both the isochrone as well as observational constraints.
 We assume that the properties of the isochrone are conditionally independent from observational constraints; namely
             \begin{equation} \label{eq:isochrone_prior_components}
-                \prior(\gamma, \nth{\mbs{m}}, \phi_1) = \prior_{\cal{I}}(\gamma, \phi_1) \prior_{obs}(\nth{\mbs{m}}, \phi_1)
+                \prior(\gamma, \nth{\mbs{m}} | \phi_1) = \prior_{\cal{I}}(\gamma | \phi_1) \prior_{obs}(\nth{\mbs{m}} | \phi_1)
             \end{equation}
             where $\prior_{\cal{I}}$ and $\prior_{obs}$ are the isochrone and observational priors, respectively.
-            \autoref{eq:photometric_probability} already encodes the photometric distribution -- the ``track" -- of the isochrone model at each point along the track, but not the amplitudes, the relative probability of points.
+
+            The second term in \autoref{eq:isochrone_prior_components} -- $\prior_{obs}(\nth{\mbs{m}} | \phi_1)$ -- encodes all observational effects in the photometric dataset.
+Some effects are easily modeled, e.g.
+datasets have magnitude limits, both faint and bright.
+Other effects are not, e.g, complex location-dependent completeness issues.
+            Accounting for the latter is very challenging.
+
+            \citep{GaiaCompleteness}
+
+            \begin{enumerate}
+                \item survey completeness is challenging.
+We pre-select the dataset so that we don't need to concern ourselves with this.
+For Gaia this means cutting $G_{ \Gaia} > 20$.
+Our discussion of the PDMF emphasizes why this isn't a problem for the isochrone.
+                \item we don't actually cut the data, but apply a mask.
+\autoref{sub:missing_data} explains how this is done.
+In this case ALL the photometric feature dimensions are masked.
+This means that the on-stream component is a track of 0-dimensional Gaussians, which means it doesn't enter into the probability.
+Any astrometric data enters the astrometric model, so the membership likelihood of these stars is driven entirely by the astrometric model.
+            \end{enumerate}
+
             Physically, this amplitude is the the present-day mass function (PDMF).
-We The PDMF $\prior_{\cal{I}}(\gamma, \phi_1)$ is a joint distribution, depending on $\gamma$ since it is the $\gamma$-dependent distribution amplitude, and also on $\phi_1$.
+The PDMF $\prior_{\cal{I}}(\gamma, \phi_1)$ is a joint distribution, depending on $\gamma$ since it is the $\gamma$-dependent distribution amplitude, and also on $\phi_1$.
 This latter dependence is confusingly termed the ``mass function of the stream", which is the expected variation in the stellar mass distrubion along the stream, arising due to e.g.
@@
 
-            Rather than using a fixed \textit{a priori} 
-            Similarly, the PDMF might be incorporated into the model,
+            Rather than using a fixed \textit{a priori} ansatz, another approach to the PDMF is to incorporate it into the model,
             parameterized by some distribution and fit simultaneously to the distance modulus and other $\cmp{m}{\mbs{\theta}}$.
-            Using a fixed distribution is a simple matter, however 
-            \TODO{[cite]}
-
-            characterizing the stream PDMF, and the
-
-            % Mention uniform modeling?
-            An alternative approach to the PDMF issue is to restrict the mass range of the isochrone such that the PDMF is unimportant.
-            This restriction means we are not modeling the full range of the 
-            photometric data and not
+            We find this, like incorporating $a, Z$ into the isochrone model, to be interesting avenues by which to develop the model.
+However the resulting significant increase in model flexibility necessitates careful regulation,
+            and we leave this to a future work.
+
+            \todo[inline]{I don't think this is necessary}
+            The last approach to the issue of the PDMF, and the one we take in this work, is to render it unimportant. The purpose of the 
+            We restrict the mass range of the isochrone such that we are modeling only a region of interest in the
+            isochrone. For streams with observable main sequence turn-offs we model
+            this region.
 
@@
                 Consequently, if we focus on the MS turnoff then the variation in the PDMF is much smaller and we can use a flat distribution. (Maybe need a plot demonstrating this?)
-            \end{enumerate}
-
-            The second term in \autoref{eq:isochrone_prior_components} -- $\prior_{obs}(\nth{\mbs{m}}, \phi_1)$ -- encodes all observational effects in the photometric dataset. In particular we are
-
-            \todo[inline]{discussion of the $\prior_{obs}(\nth{\mbs{m}}, \phi_1)$}
-
-            \begin{enumerate}
-                \item survey completeness is challenging.
-We pre-select the dataset so that we don't need to concern ourselves with this.
-For Gaia this means cutting $G_{ \Gaia} > 20$.
-Our discussion of the PDMF emphasizes why this isn't a problem for the isochrone.
-                \item we don't actually cut the data, but apply a mask.
-\autoref{sub:missing_data} explains how this is done.
-In this case ALL the photometric feature dimensions are masked.
-This means that the on-stream component is a track of 0-dimensional Gaussians, which means it doesn't enter into the probability.
-Any astrometric data enters the astrometric model, so the membership likelihood of these stars is driven entirely by the astrometric model.
             \end{enumerate}

### 2023-08-23 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \usepackage[inline]{enumitem}
+\usepackage{cleveref}
 \usepackage{todonotes}
@@
             The photometric probability, \autoref{eq:photometric_probability} encodes the photometric distribution -- the ``track" -- of the isochrone model at each point along the track, as well as the amplitudes, the relative probability of points along the track.
-This is the term $\prior(\gamma, \nth{\mbs{m}}, \phi_1)$, which encodes all priors on both the isochrone as well as observational constraints.
+This is the term $\prior(\gamma, \nth{\mbs{m}} | \phi_1)$, which describes all priors on both the isochrone as well as observational constraints.
 We assume that the properties of the isochrone are conditionally independent from observational constraints; namely
@@
             \end{equation}
-            where $\prior_{\cal{I}}$ and $\prior_{obs}$ are the isochrone and observational priors, respectively.
+            where $\prior_{\mcal{I}}$ and $\prior_{obs}$ are the isochrone and observational priors, respectively.
 
@@
 Some effects are easily modeled, e.g.
-datasets have magnitude limits, both faint and bright.
-Other effects are not, e.g, complex location-dependent completeness issues.
-            Accounting for the latter is very challenging.
-
-            \citep{GaiaCompleteness}
-
-            \begin{enumerate}
-                \item survey completeness is challenging.
-We pre-select the dataset so that we don't need to concern ourselves with this.
-For Gaia this means cutting $G_{ \Gaia} > 20$.
-Our discussion of the PDMF emphasizes why this isn't a problem for the isochrone.
-                \item we don't actually cut the data, but apply a mask.
-\autoref{sub:missing_data} explains how this is done.
-In this case ALL the photometric feature dimensions are masked.
-This means that the on-stream component is a track of 0-dimensional Gaussians, which means it doesn't enter into the probability.
-Any astrometric data enters the astrometric model, so the membership likelihood of these stars is driven entirely by the astrometric model.
-            \end{enumerate}
-
+instruments have well-characterized magnitude limits, both faint and bright.
+Other effects are not easily modeled, e.g, complex location-dependent completeness issues \citep{GaiaCompleteness}.
+            Accounting for the completeness is very challenging. In practice we avoid
+            the contribution of completeness to $\prior_{obs}$, masking data for which it is relevant.
+\Gaia, for instance, is complete from $12 < G < 17$ and has high completeness up to $G ~20$, thus we mask $G > 20$.
+            The masks are easily modeled as magnitude limits and replace the complex completeness model in $\prior_{obs}$.
+            \autoref{sub:missing_data} explains how masking is implemented in the models, though in this case every feature is masked, not only a few feature dimensions.
+With every featured masked, the photometric model in \autoref{eq:photometric_probability} reduces from an $F_m$-dimensional Gaussian to a 0-D Gaussian, which is a null distribution and does not enter into the likelihood.
+            In photometric coordinates completeness depends on a stars apparent magnitude; vied in in astrometric coordinates, the completeness cannot be described so simply.
+\Gaia, for instance has scanning law residuals in the density field.
+When photometric coordinates are masked due to completeness, we do not mask the corresponding  astrometric features, so that the stars  membership probability is determined solely by the astrometric model.
+This practice allows us to include stars with good astrometric measurements, not penalizing those stars for which the photometric model is insufficient.
+            We examine the results to confirm that the scan pattern does not impact the
+            membership distribution.
+
+            The first term in \autoref{eq:isochrone_prior_components} -- $\prior_{\mcal{I}}$ -- encodes the point-wise amplitude of the isochrone.
             Physically, this amplitude is the the present-day mass function (PDMF).
@@
 
-            \todo[inline]{Dust}
-            We use \package{dustmaps} Bayestar 19 for the dust modeling. We treat it as known. Include as a source of error in $\Sigma_n$
-            % TODO: actually implement that in the model
-
         % ssub: on_stream (end)
@@
             In particular, the distance modulus in the photometric model and the parallax in the astrometric model are both measures of the distance track of the stream.
-
             We introduce a prior to connect these components of the model:
@@
             % TODO: should we show that these are different distance functions? or is it obvious
-            where $\delta$ is the Dirac delta function, and simply expresses that the distance modulus track and parallax track must be equal (when converted to the actual distance) as a function of $\phi_1$.
+            where $\delta$ is the Dirac delta function \citep{1947pqm..book.....D}, and simply expresses that the distance modulus track and parallax track must be equal (when converted to the actual distance) as a function of $\phi_1$.
             The widths are similarly constrained.
@@
             In this section we introduce our model for the distribution of backgrounds in photometric coordinates. 
-            In general, the distribution of stars in color (i.e., $g-r$) and magnitude (i.e., $g$) is a complicated function of location in the galaxy \TODO{(e.g.
+            The distribution of stars in color (i.e., $g-r$) and magnitude (i.e., $g$) is a complicated function of location in the galaxy \TODO{(e.g.
 [cite])}.
@@
 
-        \todo[inline]{intro sentences}
-
-        \subsubsection{Parameter Bounds}
-
-            We implement hard bounds on the range of each parameter $\theta$.
-
-            \todo[inline]{this section is very rough}
-
-            We implement a hard bound on the range of all parameters.
-            Hard cutoffs can be an unwise choice of prior, but we set the ranges to larger than the data prefers and check that the trained parameters are never ``up against" the bounds.
-            This makes the priors safe.
-            We require these priors for training the neural network. It helps to have a well-bounded problem. Simple hard priors have advantages and disadvantages in this regard.
-            An advantage is that in the allowed region the prior does not not contribute to the posterior at all.
-We don't want it to.
-We want to keep the posterior as simple as possible, driven as much as possible by the likelihood and not any priors.
-            A marked disadvantage is that outside the bounded region the prior does not contribute a gradient to the loss function the optimizer can use in the fitting.
-            However, we sidestep this issue by encoding the prior bounds into the ``geometry" \TODO{(What is this called?)} of the neural network, so that the network can never
-            produce outputs outside the hard bounds.
-This is a standard technique in ML to ensure that the neural network is efficient, only covering the required region of the output space \TODO{[cite]}.
+        In \autoref{sub:likelihood_setup} we introduced the likelihood setup.
+In \autoref{sub:photometric_model_on_stream} we added priors in the form of the isochrone's PDMF and photometric observational constraints.
+In this section we
+        introduce and develop more priors that are important for training the BMDN's parameters' neural network(s).
+
+        \subsubsection{Parameter Bounds} \label{ssub:parameter_bounds}
+
+            For each parameter in $\mbs{\theta}$ of the model we implement priors on its range.
+            Uninformative, e.g.
+uniform $\mcal{U}(a, b)$, priors are often assumed where little is known about a parameter (except that $(a,b]$ contain the correct $\theta$ and its distribution).
+Where more is known about $\theta$, for instance that it is a categorical, more informative priors like the Dirichlet distribution \citep{Bishop_Christopher_M_2016-08-23} may be used.
+Our code permits any user-defined prior, and we include $\mcal{U}(a, b)$.
+            The default choice of bounds is the limits of the dataset in each feature dimension.
+            % ⬆ where should this sentence be?
+
+            The choice of prior is important, not only for the information it adds to the model, but also for how optimizers explore the parameter space.
+Simple optimizers, like MCMC \TODO{[cite]}, propose a parameter vector then compute its likelihood given the data.
+Priors with compact support  $\theta \sim \mcal{D}((a, b])$, e.g.
+$\mcal{U}(a, b)$, may be very dangerous as the optimizer can be initialized in a region with zero probability and has no means but blind luck to find the region of support, with non-zero likelihood.
+More sophisticated optimizers, like gradient-based descent \TODO{[cite]}, are susceptible to a similar initialization problem, requiring a non-zero gradient to make informed updates to the optimizers state.
+            With MDNs, model parameters are neural network outputs.
+Unlike for conventional models where an informed initial parameter state may be chosen by hand, it is impractical and undesirable to initialize by hand a neural network's output by setting all its internal weights.
+One might imagine accomplishing a desired initial output by pre-training the network with a toy model that forces convergence on a set output vector.
+However,
+            neural networks are highly non-linear in their response to internal state changes (a desirable property).
+It is quite possible that when switching form the toy to real model's loss function the pre-trained network is in
+            a local probability island from which the global optimum is unreachable.  
+            Therefore, with the MDN neural networks, initialization is mostly for checking the dependence of the results on the initial state -- though even this dependence may instead be done using parameter dropout.
+Rather than
+            focusing on initializing to a particular parameter vector, for neural networks it is instead important that the initial state, whatever it is, has non-zero probability (or non-zero gradient, depending on the optimizer).
+            Neural networks have some intrinsic phase-space range that depends on the architecture of the network.
+Therefore the network architecture must be chosen such that the outputs match well with priors.
+For example, with a
+            uniform prior $\theta \sim \mcal{U}(a,b)$, the network should be restricted such that $\theta \in (a, b]$, e.g. by a scaled logistic function.
+            \begin{equation}\label{eq:scaled_logistic}
+                  \sigma(x, \{a,b\}) = a + (b - a) * \sigma(x)
+            \end{equation}
+            Therefore, we pair every parameter bound with a bound in the network architecture.
+
+            % ⬇ where should this sentence be?
+            The parameter bounds may be independent of $\phi_1$, as is implicit to the above discussion, or conditionally dependent and vary as any user-defined function of $\phi_1$.
+            Alternatively, priors parameter may be separated into pieces, dealing with different modeling needs, e.g. defining broad parameter bounds as was done in this section.
+            We introduce a different piece subsequently.
+
+        % subsection subsubsection parameter_bounds (end)
 
@@
 
-            \todo[inline]{this section is very rough}
-
-            Region priors encourage the model to pass through a user-defined control region, while also remaining compatible with the data.
-
-            The overall track of the stream is known, so it makes sense to give this information to the system.
-However, we don't want the prior to dominate the results on small scales.
-A good balance between these two goals is to have a prior that only influences the track on large scales.
-            We introduce the ``split" Gaussian prior, which is a Gaussian split at the peak and pieced back together with a flat region connecting the halves. 
-            It is smooth up to the first derivative, so works well in an auto-grad setting.
-            The unnormalized PDF is described by:
+            In \autoref{ssub:astrometric_model_on_stream} the stream model's parameters were unconstrained.
+Bounds on the parameters and the neural network architecture were introduced in \autoref{ssub:parameter_bounds} to ensure the initial state of the model and network were compatible with the optimizer.
+Now we provide known information about physical systems, particular the track of the stream.
+            Our density modeling is aimed at characterization of \textit{known} streams, not stream discovery. From previous studies, the broad track of a
+            stream is known for significant portions of its length \citep[e.g.
+see the atlas in][]{Mateu2022}.
+It makes sense, then, to provide this information to the model.
+Care must be taken that this prior information does not dominate the model.
+            % A good balance between these two goals is to have a prior that only influences the track on large scales.
+            We introduce a region prior to encourage the stream model to pass through a user-defined control region, while also remaining compatible with the data.
+            We refer to the prior as a ``split" Gaussian prior: a Gaussian split and separated at the peak and pieced back together with a flat region connecting the halves.
+The un-normalized PDF is given by:
             \begin{small}
             \begin{equation}
-                \pdf(x,\mu,\sigma,w) \propto  \frac{1}{\sigma \sqrt{2 \pi}} \begin{cases} 
+                \pdf(\theta,\mu,\sigma,w) \propto \begin{cases} 
                    \Exp{-\frac{1}{2}\left(\frac{x-(\mu-w)}{\sigma}\right)^2} & \phantom{\mu - w <}\ x < \mu - w \\
@@
             \end{equation}\end{small}
+            The piecewise PDF is smooth up to the first derivative and can be used with gradient-based optimizers.
 
             Since this prior is equi-probable in the region $\mu - w < x < \mu + w$, the impact is to encourage the stream to fall anywhere within this region. 
-            It is convenient to reparametrize, with $\tau = \frac{1}{\sigma}$.
+            It is convenient to reparametrize, with $\tau = \frac{1}{\sigma}$. Namely,
             \begin{small}
             \begin{equation}
-                \ln \pdf(x,\mu,w) \propto \tau \begin{cases} 
+                \ln \pdf(\theta,\mu,w) \propto \tau \begin{cases} 
                     -\left(x-(\mu-w)\right)^2 & \phantom{\mu - w <}\ x < \mu - w \\
@@
             $-\ln\left(\sqrt{\frac{\pi}{\tau}} \left(\frac{1}{2}\text{erf}\left(2 \sqrt{\tau } w\right)+1\right)\right)$.
-In this form we see that $\tau$ may be increased to strengthen the prior and encourage $\mbs{\theta}$ to pass through
+In this form we see that $\tau$ may be increased to strengthen the prior and encourage $\theta$ to lie within
+            the desired region.
 
     \subsection{Model Implementation, aka the code} \label{sub:model_implementation}
+
+        Thus far we have described the mathematical model.
+        Now we describe
 
@@
     In this section we present an application of our model to a synthetic stream with known ground truths, and demonstrate the model's ability to characterize stream density variations and membership probabilities in an unsupervised manner.
-We then apply the method to real stellar streams in \autoref{sec:results_gd1} and \autoref{sec:results_pal5}.
-
-    \subsection{Test on a Synthetic Stream} \label{sub:mock_data}
+    % We then apply the method to real stellar streams in \autoref{sec:results_gd1} and \autoref{sec:results_pal5}.
+
+    % \subsection{Test on a Synthetic Stream} \label{sub:mock_data}
 
@@
         The result is a field populated by \JN{x} stars, from which we would like to identify stream members.
+
+        \todo[inline]{Dust}
+            We use \package{dustmaps} Bayestar 19 for the dust modeling. We treat it as known. Include as a source of error in $\Sigma_n$
+            % TODO: actually implement that in the model
 

### 2023-08-23 src/tex/ms.tex
[showyourwork] overleaf sync

@@
             neural networks are highly non-linear in their response to internal state changes (a desirable property).
-It is quite possible that when switching form the toy to real model's loss function the pre-trained network is in
+It is quite possible that when switching from the toy to real model's loss function the pre-trained network is in
             a local probability island from which the global optimum is unreachable.  

### 2023-08-23 src/tex/ms.tex
[showyourwork] overleaf sync

@@
             % TODO: should we show that these are different distance functions? or is it obvious
-            where $\delta$ is the Dirac delta function \citep{1947pqm..book.....D}, and simply expresses that the distance modulus track and parallax track must be equal (when converted to the actual distance) as a function of $\phi_1$.
-            The widths are similarly constrained.
+            where $\delta$ is the Dirac delta function \citep{1947pqm..book.....D}, and enforces that the distance modulus track and parallax track must be equal (when converted to the actual distance) as a function of $\phi_1$.
+            The widths are similarly constrained. The distance and first-order error conversion are given by
             \begin{align}
                 \mu_I(\parallax) &= 10 - 5\log_{10}(\parallax) \\
-                \sigma_I(\sigma_\parallax)  &= \frac{5}{\ln{10}} \mu_I \lvert\sigma_\parallax\rvert
+                \sigma_I(\sigma_\parallax)  &= \frac{5}{\ln{10}} \mu_I \lvert\sigma_\parallax\rvert + \mcal{O}.
             \end{align}

### 2023-08-23 src/tex/ms.tex
[showyourwork] overleaf sync

@@
         We discuss the data in \autoref{sub:framing_the_data} and build a probabilistic framework to model the stream and background in \autoref{sub:likelihood_setup}-\autoref{sub:priors}.
-        In \autoref{sec:results_mock} we apply our method to simulated data (\autoref{sub:mock_data}) to demonstrate the model with a known ground truth dataset,
+        In \autoref{sec:results_mock} we apply our method to simulated data to demonstrate the model with a known ground truth dataset,
         then to the stellar streams \stream{GD-1} (\autoref{sec:results_gd1}) and \stream{Pal\,5} (\autoref{sec:results_pal5}).
@@
                 \mu_I(\parallax) &= 10 - 5\log_{10}(\parallax) \\
-                \sigma_I(\sigma_\parallax)  &= \frac{5}{\ln{10}} \mu_I \lvert\sigma_\parallax\rvert + \mcal{O}.
+                \sigma_I(\sigma_\parallax)  &\approxeq \frac{5}{\ln{10}} \mu_I \lvert\sigma_\parallax\rvert.
             \end{align}
@@
 Our code permits any user-defined prior, and we include $\mcal{U}(a, b)$.
-            The default choice of bounds is the limits of the dataset in each feature dimension.
+            The default choice of prior and bounds $\mcal{U}$ set to the limits of the dataset in each feature dimension.
             % ⬆ where should this sentence be?
@@
 Priors with compact support  $\theta \sim \mcal{D}((a, b])$, e.g.
-$\mcal{U}(a, b)$, may be very dangerous as the optimizer can be initialized in a region with zero probability and has no means but blind luck to find the region of support, with non-zero likelihood.
-More sophisticated optimizers, like gradient-based descent \TODO{[cite]}, are susceptible to a similar initialization problem, requiring a non-zero gradient to make informed updates to the optimizers state.
+$\mcal{U}(a, b)$, may be very dangerous as the optimizer can be initialized in a region with zero probability and has no means but blind luck to find the region of support -- the region with non-zero likelihood.
+More sophisticated optimizers, like gradient-based descent \TODO{[cite]}, are susceptible to a similar initialization problem, allowing zero-probability regions, but requiring at least a non-zero gradient to make informed updates to the optimizers state.
+Outside the  support the gradient can be zero.
             With MDNs, model parameters are neural network outputs.
@@
             Neural networks have some intrinsic phase-space range that depends on the architecture of the network.
-Therefore the network architecture must be chosen such that the outputs match well with priors.
+Therefore the network architecture must be chosen such that the outputs match well with the priors.
 For example, with a
-            uniform prior $\theta \sim \mcal{U}(a,b)$, the network should be restricted such that $\theta \in (a, b]$, e.g. by a scaled logistic function.
+            uniform prior $\theta \sim \mcal{U}(a,b)$, the network should be restricted such that $\theta \in (a, b]$, e.g. by ending the network's $\theta$ channel with a scaled logistic function.
             \begin{equation}\label{eq:scaled_logistic}
@@
             \end{equation}
-            Therefore, we pair every parameter bound with a bound in the network architecture.
+            Therefore, we pair every parameter bound with a matching bound in the network architecture.
 
@@
             We introduce a region prior to encourage the stream model to pass through a user-defined control region, while also remaining compatible with the data.
-            We refer to the prior as a ``split" Gaussian prior: a Gaussian split and separated at the peak and pieced back together with a flat region connecting the halves.
+            We refer to the prior as a ``split"-Normal prior: a Gaussian split and separated at the peak and pieced back together with a flat region connecting the halves.
 The un-normalized PDF is given by:
@@
 
-            Since this prior is equi-probable in the region $\mu - w < x < \mu + w$, the impact is to encourage the stream to fall anywhere within this region. 
+            The Gaussian portions of the prior encourage the network towards the central region $\mu - w < x < \mu + w$.
+Since the prior is equi-probable in the region, the stream may lie anywhere as preferred by the data and the stream model.
             It is convenient to reparametrize, with $\tau = \frac{1}{\sigma}$. Namely,
@@
             the desired region.
+It is important that the region be set large enough that we may be confident the prior is not driving the final result on small scales.
+As an added measure, it is often useful to turn off this prior after the stream lies within the desired regions.
 
     \subsection{Model Implementation, aka the code} \label{sub:model_implementation}
+
+        In prior sections we
 

### 2023-08-23 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \renewcommand{\equationautorefname}{Eq.}
+\renewcommand{\tableautorefname}{Tab.}
 
@@
 
-    % subsection framing_the_data (end)
+    % sub: framing_the_data (end)
 
@@
 
-    % subsection likelihood_setup (end)
+    % sub: likelihood_setup (end)
 
@@
 
-        \subsubsection{Linking to Astrometrics: the Distance Modulus and the Parallax}
+        \subsubsection{Linking to Astrometrics: the Distance Modulus and the Parallax} \label{ssub:linking_to_astrometrics}
 
@@
 
+        % ssub: linking_to_astrometrics (end)
+
         \subsubsection{Off-stream} \label{sub:photometric_model_off_stream}
@@
     % sub: photometric_model (end)
-
-    % subsection photmetric background (end)
 
@@
 
-        % subsection subsubsection parameter_bounds (end)
+        % ssub: parameter_bounds (end)
 
@@
 
+        % ssub: region_prior (end)
+
+    % sub: priors (end)
+
+    \vspace{5pt}
     \subsection{Model Implementation, aka the code} \label{sub:model_implementation}
 
-        In prior sections we
-
-        Thus far we have described the mathematical model.
-        Now we describe
-
         \todo[inline]{TODO: how much should be included here?}
 
-        \begin{enumerate}
-            \item A network per model component, e.g. one for the weights, one for the stream track and width, one for the background distribution.
-            \item MLP for the components - lin / tanh + dropout
-            \item Normalizing flow - specific pieces
-            \item connective priors
-            \item 
-            \item Architecture in the Appendix
-        \end{enumerate}
+        In prior sections we discussed the mathematical implementation of each component of the Mixture Density Network.
+Here we make brief remarks on the code implementation and architecture of the neural networks.
+        % Rephrase: I don't like this topic sentence.
+
+        The neural networks are built with the \package{PyTorch} stack \TODO{[cite]}.
+We wrap the network \texttt{pytorch.Module} in a custom framework, allowing the Bayesian likelihood, prior, evidence, etc.
+to be bundled with the network's forward step.
+This framework allows for a high degree of modularity.
+Component models, e.g.
+the stream model, of the mixture are easily added to (and moved from) as items in the larger mixture model.
+Probability methods understand how to traverse the mixture model, calling and combining the appropriate methods of the constituent models, so it unnecessary to write custom loss functions.
+        Another benefit of the modular framework is the ease of building and experimenting with different mixture models.
+Furthermore, each model component may be saved and serialized separately from the other components, allowing for
+        portability of the components between models.
+For example, if a stream has a prominent extra-tidal feature, e.g.
+the spur of \stream{GD-1}, a fiducial model of just the thin stream may be trained, then the stream (and background) model components may be saved and used as the initialization to the stream (and background) of a more complete model that includes the spur.
+This modularity also has a cost: by allowing each model component (including the categorical mixture model itself) to contain its own network we decrease the cross-talk between nodes in separated networks.
+The networks communicate only through the backwards propagation of the loss function, increasing the required training time of the models.
+We note that the code framework, being built on \package{PyTorch}, easily permits a single model with single network.
+Having found a good model by experimenting with the modular layout, the model may be reproduced and re-trained as a single network.
+Alternatively, though we leave this to a future version of the code, it is possible to ``fuse" the mixture, providing one network whose outputs are apportioned appropriately to each constituent model.
+
+        The models permit user-defined priors to be passed at model instantiation.
+        Priors specific to a single model are contained on that model, while priors connecting two (or more) models are held on the mixture model object.
+As an example of the latter, see \autoref{ssub:linking_to_astrometrics}, which connects the distance component of the astrometric and photometric stream models.
+
+        The custom model framework combines for each model a neural network with Bayesian probability functions.
+The latter are set by the model type, e.g.
+the Gaussian model has a Gaussian likelihood function, but the former, the neural network, is set and determined by the user.
+So long as the network has the correct number of inputs (e.g.
+one for $\phi_1$) and outputs (one per parameter), any feed-forward network may be used.
+Our default choice, and for which we provide a helper function, is an MLP with a sequence of (\texttt{Linear} \textrightarrow \texttt{Tanh} \textrightarrow \texttt{Dropout}) blocks.
+This is illustrated in \autoref{table:mlp_structure}.
+        % FIXME! reference not being picked up correctly.
+        One model for which the lin-tanh network cannot be used is the normalizing flow
+        used in the photometric background model (\autoref{sub:photometric_model_off_stream}).
+Here we use the \package{nflows} package, with a conditional diagonal normal base distribution and composite transform network of a reverse permutation and masked affine auto-regressive transform layers.
+As noted in our data availability statement, all the codes used in this paper are bundled by \href{https://github.com/showyourwork/showyourwork}{\package{showyourwork}} in a public repository at $\GitHubURL{}$.
+We will describe for each stream model specifics relevant to that stream but refer readers to the publicly-available code itself for code implementation details.
+        % TODO: Maybe more details in the Appendix?
 
@@
             \centering
-            \caption{MLP structure}
+            \caption{\todo[inline]{MLP structure}}
+            \label{table:mlp_structure}
             \begin{tabular}{@{}rrcl@{}}
@@
             \midrule
-            & Linear & (None, 1, F) & 1  \\
-            & Tanh & (None, 1, F) & 1  \\
-            & Dropout & (None, 1, F) & 0  \\
-            & Linear & (None, 1, F) & 1  \\
+            & Linear & (None, 1, H) & 1  \\
+            & Tanh & (None, H, H) & 1  \\
+            & Dropout & (None, H, H) & 0  \\
+            & Linear & (None, H, H) & 1  \\
+            & Tanh & (None, H, H) & 1  \\
+            & Dropout & (None, H, H) & 0  \\
+            & Linear & (None, H, F) & 1  \\
+            & Tanh & (None, F, F) & 1  \\
+            & Dropout & (None, F, F) & 0  \\
             \bottomrule
@@
 
-    % subsection test_on_a_synthetic_stream (end)
+    % sub: test_on_a_synthetic_stream (end)
 
@@
 
-% subsection gd1 (end)
+% sub: gd1 (end)
 
@@
 
-        % subsection streamfinder (end)
+        % sub: streamfinder (end)
 
@@
 
-        % subsection via_machinae (end)
+        % sub: via_machinae (end)
 
@@
 
-        % subsection uniform_modeling_of_13_stellar_streams (end)
+        % sub: uniform_modeling_of_13_stellar_streams (end)
 

### 2023-08-23 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-            \todo[inline]{I don't think this is necessary}
-            The last approach to the issue of the PDMF, and the one we take in this work, is to render it unimportant. The purpose of the 
-            We restrict the mass range of the isochrone such that we are modeling only a region of interest in the
-            isochrone. For streams with observable main sequence turn-offs we model
-            this region.
-
-            \todo[inline]{More on the PDMF}
-            \begin{enumerate}
-                \item could parameterize a more general distribution and fit for the PDMF
-                \item Alternatively, we are interested in the photometric model for a number of reasons, but an important one is that we can fit the distance modulus of the stream, for this only a subsection of the isochrone is needed.
-The best section is the MS turnoff.
-                Consequently, if we focus on the MS turnoff then the variation in the PDMF is much smaller and we can use a flat distribution. (Maybe need a plot demonstrating this?)
-            \end{enumerate}
+            % TODO? expand this section.
+            The last approach to the issue of the PDMF, and the one we take in this work, is to render it unimportant. 
+            With fixed age, metallicity, and other isochrone model parameters, the primary purpose of the isochrone is to allow the model to determine the distance modulus of the stream.
+For this, only a portion of the stream need be modeled.
+            For streams with observable main sequence turn-offs, like \stream{GD-1} in \gaia, this portion of the isochrone has both many stars and a relatively small range in masses.
+Thus, we restrict the mass range of the isochrone such that we are modeling only a region of interest over which the PDMF does not contribute to the final result.
+            % TODO? work in something to the effect of:
+            % The PDMF doesn't have an enormous impact, regardless as the isochrone model is very thin and stars close to the isochrone photometrically are generally quite far astrometrically.
+This is an advantange of simultaneous modeling, where errors in one model are balanced by other parts of the model.
 
@@
 one for $\phi_1$) and outputs (one per parameter), any feed-forward network may be used.
-Our default choice, and for which we provide a helper function, is an MLP with a sequence of (\texttt{Linear} \textrightarrow \texttt{Tanh} \textrightarrow \texttt{Dropout}) blocks.
+Our default choice, and for which we provide a helper function, is an MLP with a sequence of \texttt{Linear} \!\!\textrightarrow \texttt{Tanh} \!\!\textrightarrow \texttt{Dropout} blocks.
 This is illustrated in \autoref{table:mlp_structure}.
         % FIXME! reference not being picked up correctly.
-        One model for which the lin-tanh network cannot be used is the normalizing flow
+        Dropout layers are used to prevent network co-adaptation and over-fitting.
+Dropout works by randomly zeroing out nodes in the network, decreasing the importance of any single node, encouraging instead emergent patterns across the network.
+        One model for which the lin-tanh-dropout network cannot be used is the normalizing flow
         used in the photometric background model (\autoref{sub:photometric_model_off_stream}).
@@
             \centering
-            \caption{\todo[inline]{MLP structure}}
+            \caption{
+            Example neural network structure consisting of 1 input block mapping a $\phi_1$ scalar to the $H$ nodes of the hidden blocks, the number of which determines the depth of the network.
+The hidden blocks map to the $F$ outputs in the output block.
+Each block consists of a \texttt{Linear} \!\!\textrightarrow \texttt{Tanh} \!\!\textrightarrow \texttt{Dropout} sequence.
+Vector $\phi_1$ inputs are supported as an element-wise application of the network.
+            }
             \label{table:mlp_structure}
@@
             \toprule
-            & Layer & Shape & Param \# \\
+            & Layer & Shape & Parameters \\
             \midrule
-            & Linear & (None, 1, H) & 1  \\
-            & Tanh & (None, H, H) & 1  \\
-            & Dropout & (None, H, H) & 0  \\
-            & Linear & (None, H, H) & 1  \\
-            & Tanh & (None, H, H) & 1  \\
-            & Dropout & (None, H, H) & 0  \\
-            & Linear & (None, H, F) & 1  \\
-            & Tanh & (None, F, F) & 1  \\
-            & Dropout & (None, F, F) & 0  \\
+            & Linear & (1, H) & 2H  \\
+            & Tanh & (H, H) & 0  \\
+            & Dropout & (H, H) & 0  \\
+            \hline
+            & Linear & (H, H) & $2H^2$  \\
+            $N_{\rm hidden} \times$ & Tanh & (H, H) & 0  \\
+            & Dropout & (H, H) & 0  \\
+            \hline
+            & Linear & (H, F) & $2HF$  \\
+            & Tanh & (F, F) & 0 \\
+            & Dropout & (F, F) & 0  \\
             \bottomrule
@@
         \end{table}
-
-        Dropout layers were used to prevent network co-adaptation and over-fitting.
-Dropout works by randomly zeroing out nodes in the network, decreasing the importance of any single node, encouraging instead emergent patterns across the network.
 

### 2023-08-26 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     \subsection{Model Implementation, aka the code} \label{sub:model_implementation}
-
-        \todo[inline]{TODO: how much should be included here?}
 
@@
     In this section we present an application of our model to a synthetic stream with known ground truths, and demonstrate the model's ability to characterize stream density variations and membership probabilities in an unsupervised manner.
-    % We then apply the method to real stellar streams in \autoref{sec:results_gd1} and \autoref{sec:results_pal5}.
 
@@
             \textbf{Top panel:}%
-                The stream mixture coefficient $f(\phi_1)$ 
-                Stream fraction.
+                The stream mixture coefficient $f(\phi_1)$ (black dotted line) predicted by the model, overplotted on the true stream fraction (black-outlined histogram),
+                calculated as the ratio of stream stars to total stars in 55 bins
+                over the $\phi_1$ range of the isochrone.
+            \textbf{Middle panel: }%
+                $\phi_2(\phi_1)$ over the full range of $\phi_1$.
+The data color and transparency is set by the model's MLE stream probability (with dropout turned off).
+Plotted behind the data are the true labels for the stream stars (large black circles).
+                The true labels exactly limn the model-identified stream stars.
+                The MLE stream track (black dashed line) is over-plotted on the probability-colored data.
             %
-                \textbf{Middle panel:}%
-                $\phi_2(\phi_1)$
+            \textbf{Lower panel 3: }%
+                $\varpi_2(\phi_1)$ over the full range of $\phi_1$.
+Like for $\phi_2$, the data color and transparency is set by the MLE probability, with the true labels (large black circles) under-plotted and MLE track (black dashed line) over-plotted.
             %
-                \textbf{Lower panel 3:}%
+            \textbf{Upper Histograms: }%
+                $\phi_2$ histograms for each model component (blue background, red stream), in 4 $\phi_1$ ranges across the data set.
+                The height of each bin is the probability-weighted density.
+                The background is a uniform distribution, while the stream is a Gaussian.
+In projection across the $\phi_1$ range it can appear multi-modal (panel 2) if there are large gaps or `smeared' out if the Gaussian's mean changes significantly over the range.
             %
-                \textbf{Upper Histograms:}%
+            \textbf{Upper Middle Histograms: }%
+                Parallax $\varpi$ histograms for each model component (blue background, red stream), in 4 $\phi_1$ ranges across the data set.
+                The height of each bin is the probability-weighted density.
             %
-                \textbf{Upper Middle Histograms:}%
-                %
-                \textbf{Lower Middle Histograms:}%
-                %
-                \textbf{Lower Histograms:}%
+            \textbf{Lower Middle and Lower Histograms:}%
+                Photometric coordinate $(g, r)$ plots for each model component in 4 $\phi_1$ ranges across the data set.
+The top row plots the stream stars (red) over the background.
+The lower row plots the background stars (blue) over the stream stars to show that the
+                how the two distributions mix.
         }
@@
 
-    % sub: test_on_a_synthetic_stream (end)
+% sec: test_on_a_synthetic_stream (end)
 

### 2023-08-26 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \section{Introduction} \label{sec:intro}
-    Stellar streams are the disrupted remnants of globular clusters and satellite galaxies, and their census has grown extensively in the Milky Way thanks to all-sky astrometric missions like {\it Gaia} and low-surface brightness photometric surveys (\JN{cite}).
-The formation of streams can be traced back to a progenitor cluster (i.e., a satellite galaxy or globular cluster), whose stars are gradually lost to the tidal field of the host galaxy and extend along a series of similar orbits producing tidal tails, which can sometimes span many tens of degrees across the sky.
-This orbital proximity of stars belonging to a stream makes them sensitive tracers of the mass distribution of galaxies, sourced by both the baryonic and dark matter components.
-
-    The average properties of a stream (e.g., the mean position and velocity track of the tidal tails) can be used to reconstruct the global dark matter distribution of the stellar halo (e.g., \JN{cite}), while local variations in the stream track and surface density encode information about the stream's encounters with baryonic structures such as (e.g.) the stellar bar (\JN{cite}), and non-luminous structures like dark matter subhalos (\JN{cite}).
-Importantly, these galactic components span orders of magnitude in mass, highlighting the importance of characterizing a population of stellar streams both in morphology and kinematics.
-
-    While several methods have been developed to model stream properties as a function of global halo properties (e.g., flattening and orientation;\JN{cite}) and local substructures (e.g., the bar's pattern speed and the mass of subhalo perturbers; \JN{cite}), these methods and insights often rely on the existence of a homogenized stream-tracer population that characterizes the stream across each of the observable phase-space dimensions.
-Additionally, because even the fine-grain properties of streams are influenced by the detailed mass distribution of galaxies, it is important to propagate errors both in measurement uncertainty and membership uncertainty (i.e., which stars belong to the stream versus the background) when attempting to model the galaxy.
-Otherwise, a stream that has been poorly characterized could bias constraints on (e.g.) the total mass of the galaxy, the dark matter halo shape, and the mass of subhalo perturbers.
-In order to generate more precise constraints on the structure of the galaxy, it is therefore imperative that a statistically sound and homogenized catalog of stellar streams is produced so that theoretical models for the gravitational potential of the galaxy across a large range of spatial scales can be constrained.
-
-    While streams are well described in (e.g.) action angle coordinates or $N-$body simulations, these methods relying on prior assumptions about the galaxy and its underlying potential.
-Therefore, it is important to devise data-driven methods to characterize stellar streams without appealing to strong prior assumptions about the galaxy's structure.
-
-    There are a few previous works which have modeled stellar streams in this context.
-\citet{2022MNRAS.514.1757P} developed a data-driven spline-based model for modeling the photometric qualities of previously identified streams.
-Their method works by fitting the stream's stellar surface density with a series of splines, capturing both surface brightness variations along the stream and changes in the position of the stream track and width.
-Their method also utilize a simultaneous ischorone fit to the stream, from which a distance modulus can be derived by assuming that the entire stream originates from the same stellar population.
-While this method is very successful at characterizing the photometric properties of a stream, it does not consider the kinematic dimensions which have become increasing well-measured with successive data releases from {\it Gaia}, as well as targeted observations.
-From a population of RR Lyrae stars, \citet{2019AJ....158..223P} utilized a mixture model to fit the globular cluster stream Pal-5 in the space of proper motions and heliocentric distances.
-The mixture modeling approach enables a simultaneous fit to both the stream and background density, enabling better separation of a coherent stream from an otherwise noisy background distribution.
-However, the track of the stream in on-sky coordinates is not fit.
-The method identified 27 RR Lyrae stars consistent with being members of the stream.
-While useful for determining the average properties of the stream (e.g., its mean distance track), a limited population of RR Lyrae stars are not sufficient to capture the fine-grained properties of streams expected to inform constraints on (e.g.) a population of perturbers in the galaxy.
-\JN{are there other methods?}
-
-    Other methods for extracting stellar streams from the data include matched-filter approaches, where over-densities in color-magnitude space are inspected as possible clusters undergoing tidal stripping \JN{cite the many key papers using this method}.
-While the matched-filter technique has been extremely successful at stream discovery, it is not equipped to characterize streams at the level of detailed necessary to inform precise constraints on the potential of the galaxy and its substructure.
-
-    In order to address the need for a flexible model of stellar streams both in photometric and kinematic spaces, in this work we develop a new method for characterizing streams and quantifying the membership probability of possible stream stars.
-Our approach provides several key advantage over previous stream modeling efforts, specifically in its ability to jointly model the kinematic and photometric properties of streams simultaneously.
-Furthermore, our method is well-suited to fitting streams with only partial or incomplete phase-space or photometric observations, enabling a full characterization of streams insofar as the available data allows.
+    %
+    Stellar streams are the disrupted
+    remnants of globular clusters and satellite galaxies, and their census has
+    grown extensively in the Milky Way thanks to all-sky astrometric missions
+    like {\it Gaia} and low-surface brightness photometric surveys (\JN{cite}).
+    The formation of streams can be traced back to a progenitor cluster (i.e., a
+    satellite galaxy or globular cluster), whose stars are gradually lost to the
+    tidal field of the host galaxy and extend along a series of similar orbits
+    producing tidal tails, which can sometimes span many tens of degrees across
+    the sky. This orbital proximity of stars belonging to a stream makes them
+    sensitive tracers of the mass distribution of galaxies, sourced by both the
+    baryonic and dark matter components.
+    % 
+    The average properties of a stream (e.g., the mean position and velocity
+    track of the tidal tails) can be used to reconstruct the global dark matter
+    distribution of the stellar halo (e.g., \JN{cite}), while local variations
+    in the stream track and surface density encode information about the
+    stream's encounters with baryonic structures such as (e.g.) the stellar bar
+    (\JN{cite}), and non-luminous structures like dark matter subhalos
+    (\JN{cite}). Importantly, these galactic components span orders of magnitude
+    in mass, highlighting the importance of characterizing a population of
+    stellar streams both in morphology and kinematics. 
+    % 
+    While several methods have been developed to model stream properties as a
+    function of global halo properties (e.g., flattening and
+    orientation;\JN{cite}) and local substructures (e.g., the bar's pattern
+    speed and the mass of subhalo perturbers; \JN{cite}), these methods and
+    insights often rely on the existence of a homogenized stream-tracer
+    population that characterizes the stream across each of the observable
+    phase-space dimensions. Additionally, because even the fine-grain properties
+    of streams are influenced by the detailed mass distribution of galaxies, it
+    is important to propagate errors both in measurement uncertainty and
+    membership uncertainty (i.e., which stars belong to the stream versus the
+    background) when attempting to model the galaxy. Otherwise, a stream that
+    has been poorly characterized could bias constraints on (e.g.) the total
+    mass of the galaxy, the dark matter halo shape, and the mass of subhalo
+    perturbers. In order to generate more precise constraints on the structure
+    of the galaxy, it is therefore imperative that a statistically sound and
+    homogenized catalog of stellar streams is produced so that theoretical
+    models for the gravitational potential of the galaxy across a large range of
+    spatial scales can be constrained. 
+    %
+    While streams are well described in (e.g.) action angle coordinates or
+    $N-$body simulations, these methods relying on prior assumptions about the
+    galaxy and its underlying potential. Therefore, it is important to devise
+    data-driven methods to characterize stellar streams without appealing to
+    strong prior assumptions about the galaxy's structure. 
+    % 
+    There are a few previous works which have modeled stellar streams in this
+    context. \citet{2022MNRAS.514.1757P} developed a data-driven spline-based
+    model for modeling the photometric qualities of previously identified
+    streams. Their method works by fitting the stream's stellar surface density
+    with a series of splines, capturing both surface brightness variations along
+    the stream and changes in the position of the stream track and width. Their
+    method also utilize a simultaneous ischorone fit to the stream, from which a
+    distance modulus can be derived by assuming that the entire stream
+    originates from the same stellar population. While this method is very
+    successful at characterizing the photometric properties of a stream, it does
+    not consider the kinematic dimensions which have become increasing
+    well-measured with successive data releases from {\it Gaia}, as well as
+    targeted observations. From a population of RR Lyrae stars,
+    \citet{2019AJ....158..223P} utilized a mixture model to fit the globular
+    cluster stream Pal-5 in the space of proper motions and heliocentric
+    distances. The mixture modeling approach enables a simultaneous fit to both
+    the stream and background density, enabling better separation of a coherent
+    stream from an otherwise noisy background distribution. However, the track
+    of the stream in on-sky coordinates is not fit. The method identified 27 RR
+    Lyrae stars consistent with being members of the stream. While useful for
+    determining the average properties of the stream (e.g., its mean distance
+    track), a limited population of RR Lyrae stars are not sufficient to capture
+    the fine-grained properties of streams expected to inform constraints on
+    (e.g.) a population of perturbers in the galaxy. \JN{are there other
+    methods?}
+    % 
+    Other methods for extracting stellar streams from the data include
+    matched-filter approaches, where over-densities in color-magnitude space are
+    inspected as possible clusters undergoing tidal stripping \JN{cite the many
+    key papers using this method}. While the matched-filter technique has been
+    extremely successful at stream discovery, it is not equipped to characterize
+    streams at the level of detailed necessary to inform precise constraints on
+    the potential of the galaxy and its substructure.
+    % 
+    In order to address the need for a flexible model of stellar streams both in
+    photometric and kinematic spaces, in this work we develop a new method for
+    characterizing streams and quantifying the membership probability of
+    possible stream stars. Our approach provides several key advantage over
+    previous stream modeling efforts, specifically in its ability to jointly
+    model the kinematic and photometric properties of streams simultaneously.
+    Furthermore, our method is well-suited to fitting streams with only partial
+    or incomplete phase-space or photometric observations, enabling a full
+    characterization of streams insofar as the available data allows.
 
@@
 
-        A stellar stream is the association of stars tidally stripped from a common
-        progenitor system that orbits in an underlying galactic gravitational field
-        \citep{Johnston1998, HelmiWhite1999}. Stream progenitors are gravitationally
-        bound systems, such as satellite dwarf galaxies or star clusters
-        \citep{Odenkirchen2001, Majewski2003}. In the absence of external interactions
-        these systems are stable, though still capable of mass loss driven by internal
-        processes \citep{Hills1975, HeggieHut2003}, e.g. relaxation and binary
-        interactions. Considering external interactions, these progenitor systems may
-        be disrupted: completely, as in the merger events that formed the Galactic
-        stellar halo \citep{Lynden-Bell1967, Searle1978}; or partially, such as tidal
+        A stellar stream is the association of stars tidally stripped from a
+        common progenitor system that orbits in an underlying galactic
+        gravitational field \citep{Johnston1998, HelmiWhite1999}. Stream
+        progenitors are gravitationally bound systems, such as satellite dwarf
+        galaxies or star clusters \citep{Odenkirchen2001, Majewski2003}. In the
+        absence of external interactions these systems are stable, though still
+        capable of mass loss driven by internal processes \citep{Hills1975,
+        HeggieHut2003}, e.g. relaxation and binary interactions. Considering
+        external interactions, these progenitor systems may be disrupted:
+        completely, as in the merger events that formed the Galactic stellar
+        halo \citep{Lynden-Bell1967, Searle1978}; or partially, such as tidal
         disruption forming a stellar stream.
@@
         In the approximation of a smooth galactic gravitational field, the
-        progenitor's extent is limited to the tidal radius. Through processes internal
-        and external, progenitor stars can achieve sufficient energy to bring them
-        beyond the tidal boundary, thus ``escaping'' into the galactic field. Escape
-        primarily occurs at both an inner and outer saddle point of the combined
-        potential -- e.g. the L2 and L3 Lagrange points for a spherical galactic field
-        \citep{Ross1997, Fukushige2000, BinneyTremaine2008}. Generally, the initial
-        phase space position of the escaped star is very similar to that of the
-        progenitor: the configuration position is the tidal boundary and the star has
-        a low peculiar velocity. Since both the escaped star and its progenitor orbit
+        progenitor's extent is limited to the tidal radius. Through processes
+        internal and external, progenitor stars can achieve sufficient energy to
+        bring them beyond the tidal boundary, thus ``escaping'' into the
+        galactic field. Escape primarily occurs at both an inner and outer
+        saddle point of the combined potential -- e.g. the L2 and L3 Lagrange
+        points for a spherical galactic field \citep{Ross1997, Fukushige2000,
+        BinneyTremaine2008}. Generally, the initial phase space position of the
+        escaped star is very similar to that of the progenitor: the
+        configuration position is the tidal boundary and the star has a low
+        peculiar velocity. Since both the escaped star and its progenitor orbit
         in the same underlying galactic potential and have similar phase space
         positions their orbits are similar \citep{BinneyTremaine2008}. Given
-        sufficient time the phase space separation will increase and an escaped star
-        will lead or trail the position of the progenitor, depending on the location
-        from which it escaped. Therefore, a collection of tidally stripped stars will
-        form extended structures, aka tails or streams, that are few to thousands of
-        parsecs in length \citep{Johnston1998, HelmiWhite1999, Bovy2014}.
-
-        To be a coherent, observable structure the peculiar velocity dispersion of
-        escaped stars relative to the progenitor must be relatively low, but does vary
-        from system to system. Stars in kinematically hot streams (e.g. from
-        progenitors with larger kinematic dispersions) have more dissimilar orbits
-        from each other and the progenitor than do stars in cold streams, with smaller
-        dispersions \citep{Johnston1998, Hendel2015}. The orbit of a star depends on
-        its phase space position and the gravitational potential; therefore measuring
-        a star's position and velocity and observing its orbit reveals the local
-        potential, which is normally dominated by the Galaxy (primarily the dark
-        matter halo at large distances) \citep{Gibbons2014}. However, an orbit is
-        impractical to observe on human timescales. Cold streams offer a workaround.
-        Like measuring one star at many points in one orbit over an extended period,
-        streams are many stars measured at different points along approximately one
-        orbit at the same time. Therefore stellar streams are one of the most
-        promising means to study the Galactic gravitational potential: the stellar
-        components as well as the dark matter \citep{Johnston2016}.
-
-        On the observational front there has been a large concerted effort in the
-        field to find new stellar streams \citep[for an extensive list of known
-        Galactic streams see][]{Mateu2022}, extend the detected extents of known
-        streams \citep[e.g. for \stream{Palomar 5} alone:][]{Rockosi2002, Ibata2017,
-        Grillmair2006, Carlberg2012, StarkmanEtAl2019}, and increase the general
-        purity of stream catalogs.
+        sufficient time the phase space separation will increase and an escaped
+        star will lead or trail the position of the progenitor, depending on the
+        location from which it escaped. Therefore, a collection of tidally
+        stripped stars will form extended structures, aka tails or streams, that
+        are few to thousands of parsecs in length \citep{Johnston1998,
+        HelmiWhite1999, Bovy2014}.
+
+        To be a coherent, observable structure the peculiar velocity dispersion
+        of escaped stars relative to the progenitor must be relatively low, but
+        does vary from system to system. Stars in kinematically hot streams
+        (e.g. from progenitors with larger kinematic dispersions) have more
+        dissimilar orbits from each other and the progenitor than do stars in
+        cold streams, with smaller dispersions \citep{Johnston1998, Hendel2015}.
+        The orbit of a star depends on its phase space position and the
+        gravitational potential; therefore measuring a star's position and
+        velocity and observing its orbit reveals the local potential, which is
+        normally dominated by the Galaxy (primarily the dark matter halo at
+        large distances) \citep{Gibbons2014}. However, an orbit is impractical
+        to observe on human timescales. Cold streams offer a workaround.  Like
+        measuring one star at many points in one orbit over an extended period,
+        streams are many stars measured at different points along approximately
+        one orbit at the same time. Therefore stellar streams are one of the
+        most promising means to study the Galactic gravitational potential: the
+        stellar components as well as the dark matter \citep{Johnston2016}.
+
+        On the observational front there has been a large concerted effort in
+        the field to find new stellar streams \citep[for an extensive list of
+        known Galactic streams see][]{Mateu2022}, extend the detected extents of
+        known streams \citep[e.g. for \stream{Palomar 5} alone:][]{Rockosi2002,
+        Ibata2017, Grillmair2006, Carlberg2012, StarkmanEtAl2019}, and increase
+        the general purity of stream catalogs.
 
@@
 
-        Stellar streams consist of stars that are tidally disrupted from a progenitor system.
-        To a first approximation, the stars occupy a single orbit, that of their progenitor.
-        Additionally, as stars formed in the progenitor they retain its photometric and chemical characteristics: which for globular clusters means following an isochrone.
-        In this simplistic picture, astrometrically characterizing a stream requires only finding it's orbit.
-Member stars fall directly on the orbit and the isochrone, making membership likelihood determination trivial.
-
-        % Observational errors complicate this picture.
-Instead of a certain membership calculation, we must build a probabilistic model, assigning a likelihood that an observed star falls along the stream's orbit.
+        Stellar streams consist of stars that are tidally disrupted from a
+        progenitor system.  To a first approximation, the stars occupy a single
+        orbit, that of their progenitor.  Additionally, as stars formed in the
+        progenitor they retain its photometric and chemical characteristics:
+        which for globular clusters means following an isochrone.  In this
+        simplistic picture, astrometrically characterizing a stream requires
+        only finding it's orbit. Member stars fall directly on the orbit and the
+        isochrone, making membership likelihood determination trivial.
+
+        % Observational errors complicate this picture. Instead of a certain
+        % membership calculation, we must build a probabilistic model, assigning
+        % a likelihood that an observed star falls along the stream's orbit.
 
@@
 
-        Occupying a single orbit implies that streams remain a point in action space, and having a common origin would thus not become extended structure. This is not true.
-        Differences in stream stars' orbits from the progenitor's arise from various factors including internal dynamics of the progenitor and the host Galactic potential.
+        Occupying a single orbit implies that streams remain a point in action
+        space, and having a common origin would thus not become extended
+        structure. This is not true.  Differences in stream stars' orbits from
+        the progenitor's arise from various factors including internal dynamics
+        of the progenitor and the host Galactic potential.
 
@@
 
-        This defines an astrometric phase-space hyper-tube \cite{2018MNRAS.477.4063M}, with a distribution radial to the track.
-
-        Instead of characterizing the stream by its orbit, we characterize it by it's track and the distribution around that track.
-        Computing membership likelihoods now requires fitting the track and distribution. This cannot be
-        done without then also fitting the field of stars in which the stream lives, since the stream 
-        and field cannot be clearly separated.
+        This defines an astrometric phase-space hyper-tube
+        \cite{2018MNRAS.477.4063M}, with a distribution radial to the track.
+
+        Instead of characterizing the stream by its orbit, we characterize it by
+        it's track and the distribution around that track.  Computing membership
+        likelihoods now requires fitting the track and distribution. This cannot
+        be done without then also fitting the field of stars in which the stream
+        lives, since the stream and field cannot be clearly separated.
 
@@
 
-        Perturbations to the Galactic potential, in the form of time evolution and non-axisymmetry, as well as substructure can disrupt the stellar stream. 
-        Even most perturbations don't ruin the idea of the phase-space hypertube. They either drop the mixture weight (rephrase, not yet introduced) to 0 or change the width of the hypertube.
+        Perturbations to the Galactic potential, in the form of time evolution
+        and non-axisymmetry, as well as substructure can disrupt the stellar
+        stream.  Even most perturbations don't ruin the idea of the phase-space
+        hypertube. They either drop the mixture weight (rephrase, not yet
+        introduced) to 0 or change the width of the hypertube.
 
@@
         Identifying streams of globular of clusters is a challenging task.
-Streams are very low signal-to-noise structures spread over comparatively large regions of the sky.
-They live in a vast background of field stars.
+        Streams are very low signal-to-noise structures spread over
+        comparatively large regions of the sky. They live in a vast background
+        of field stars.
 
@@
         % Add citations
-        You took an isochrone and shifted it by a distance modulus until a stream stood out in longitude and latitude as an extended overdensity structure.
-
-        With the advent of Gaia, we gained access to detailed astrometric data. For most streams this
-
-        poses a challenging task due to their intricate and diffuse nature
-        from large-scale surveys is challenging due to the complex and overlapping distributions of stars in different regions of the sky; disentangling members from the vast background of field stars
+        You took an isochrone and shifted it by a distance modulus until a
+        stream stood out in longitude and latitude as an extended overdensity
+        structure.
+
+        With the advent of Gaia, we gained access to detailed astrometric data.
+        For most streams this
+
+        poses a challenging task due to their intricate and diffuse nature from
+        large-scale surveys is challenging due to the complex and overlapping
+        distributions of stars in different regions of the sky; disentangling
+        members from the vast background of field stars
 
@@
 
-        The paper is organized as follows.
-        In \autoref{sec:method} we introduce our method for characterizing stream tracks and computing stellar membership.
-        We discuss the data in \autoref{sub:framing_the_data} and build a probabilistic framework to model the stream and background in \autoref{sub:likelihood_setup}-\autoref{sub:priors}.
-        In \autoref{sec:results_mock} we apply our method to simulated data to demonstrate the model with a known ground truth dataset,
-        then to the stellar streams \stream{GD-1} (\autoref{sec:results_gd1}) and \stream{Pal\,5} (\autoref{sec:results_pal5}).
-        We compare our approach to characterizing stellar streams to other methods in \autoref{sec:comparison}.
-        We conclude in \autoref{sec:conclusions}, discussing the results of this work and future directions.
+        The paper is organized as follows.  In \autoref{sec:method} we introduce
+        our method for characterizing stream tracks and computing stellar
+        membership.  We discuss the data in \autoref{sub:method:framing_the_data} and
+        build a probabilistic framework to model the stream and background in
+        \autoref{sub:method:likelihood_setup}-\autoref{sub:methods:priors}.  In
+        \autoref{sec:results_mock} we apply our method to simulated data to
+        demonstrate the model with a known ground truth dataset, then to the
+        stellar streams \stream{GD-1} (\autoref{sec:results_gd1}) and
+        \stream{Pal\,5} (\autoref{sec:results_pal5}).  We compare our approach
+        to characterizing stellar streams to other methods in
+        \autoref{sec:comparison}.  We conclude in \autoref{sec:conclusions},
+        discussing the results of this work and future directions.
 
@@
 
-    We now introduce our method for characterizing stellar stream tracks and computing stream membership likelihoods from N-D phase-space measurements.
+    We now introduce our method for characterizing stellar stream tracks and
+    computing stream membership likelihoods from N-D phase-space measurements.
     % TODO: rephrase following sentence
-    We develop a flexible Bayesian model framework, that allows arbitrary numbers of phase-space dimensions to be incorporated in the model and permits missing phase-space observations. 
-    Below, we offer a concise overview of our approach, followed by a more in-depth technical explanation in subsequent sections.
-    We start, in \autoref{sub:framing_the_data}, by transforming the astrometric data into
-    a stream-oriented on-sky reference frame ($\phi_1, \phi_2, \parallax, \mu_{\phi_1}^*, \mu_{\phi_2}, v_r)$, for each stream. In this frame, 
-    the stream track lies along $\phi_1$, and the stream density may be described by distributions in the other parameters as injective functions of $\phi_1$.
-    % TODO: ⬆ I think a few more sentences explaining why this is important, feature variations, etc?
-    % However, previously we discussed how stream will vary along the track, with changes in the width and possible gaps.
-    % Also observational effects, e.g the distance gradient changes the on-sky width (should this be mentioned earlier?)
-    Likewise, the background of the Galactic field may be described with $\phi_1$-conditioned distributions.
+    We develop a flexible Bayesian model framework, that allows arbitrary
+    numbers of phase-space dimensions to be incorporated in the model and
+    permits missing phase-space observations.  Below, we offer a concise
+    overview of our approach, followed by a more in-depth technical explanation
+    in subsequent sections.  We start, in \autoref{sub:method:framing_the_data}, by
+    transforming the astrometric data into a stream-oriented on-sky reference
+    frame ($\phi_1, \phi_2, \parallax, \mu_{\phi_1}^*, \mu_{\phi_2}, v_r)$, for
+    each stream. In this frame, the stream track lies along $\phi_1$, and the
+    stream density may be described by distributions in the other parameters as
+    injective functions of $\phi_1$.
+    % TODO: ⬆ I think a few more sentences explaining why this is important,
+    % feature variations, etc?  However, previously we discussed how stream will
+    % vary along the track, with changes in the width and possible gaps.  Also
+    % observational effects, e.g the distance gradient changes the on-sky width
+    % (should this be mentioned earlier?)
+    Likewise, the background of the Galactic field may be described with
+    $\phi_1$-conditioned distributions.
     % TODO: ⬆ I think this should be expanded.
-    Non-astrometric coordinates, e.g. photometry and metallicity, are also modelled along the stream and background as functions of $\phi_1$.
-
-    The distributions for the stream and background are collected in a single mixture model that describes the entire field.
-    We take the parameters of the mixture model -- the mixing coefficients and component distribution parameters -- to be general (continuous) functions of the conditioning variable, $\phi_1$.
-This is done using feed-forward neural network that takes the conditioning variable as its input and output the parameter value.
-Mixture models of conditional probability distributions using neural networks are called Mixture Density Networks (MDNs).
-Since the model coefficients may evolve with $\phi_1$, MNDs are well suited to characterize streams (and the background) with all their
-    variations in position, width, and linear density.
+    Non-astrometric coordinates, e.g. photometry and metallicity, are also
+    modelled along the stream and background as functions of $\phi_1$.
+
+    The distributions for the stream and background are collected in a single
+    mixture model that describes the entire field.  We take the parameters of
+    the mixture model -- the mixing coefficients and component distribution
+    parameters -- to be general (continuous) functions of the conditioning
+    variable, $\phi_1$. This is done using feed-forward neural network that
+    takes the conditioning variable as its input and output the parameter value.
+    Mixture models of conditional probability distributions using neural
+    networks are called Mixture Density Networks (MDNs). Since the model
+    coefficients may evolve with $\phi_1$, MNDs are well suited to characterize
+    streams (and the background) with all their variations in position, width,
+    and linear density.
 
@@
 
-    \subsection{Framing the Data} \label{sub:framing_the_data}
-
-        As a stream progenitor orbits the Galactic center of mass (GCOM), its orbital path
-        describes an ellipse in the orbital plane. The associated arms of the stream generally
-        align closely with its orbital plane.
-        From a Galactocentric reference frame, an orbital plane assumes the form of a great
-        circle in the observer's celestial ``sky," thereby allowing the potential realignment of
-        longitudinal ($\ell$) and latitudinal ($b$) coordinates to a coordinate system aligned
-        with the stream ($\cmp{GCOM}{\phi_1}, \phi_2^{(GCOM)}$). Here, the progenitor is
+    \subsection{Framing the Data} \label{sub:method:framing_the_data}
+
+        As a stream progenitor orbits the Galactic center of mass (GCOM), its
+        orbital path describes an ellipse in the orbital plane. The associated
+        arms of the stream generally align closely with its orbital plane.  From
+        a Galactocentric reference frame, an orbital plane assumes the form of a
+        great circle in the observer's celestial ``sky," thereby allowing the
+        potential realignment of longitudinal ($\ell$) and latitudinal ($b$)
+        coordinates to a coordinate system aligned with the stream
+        ($\cmp{GCOM}{\phi_1}, \phi_2^{(GCOM)}$). Here, the progenitor is
         established at the origin, with the stream progressing along
-        $\cmp{GCOM}{\phi_1} (\phi_2^{(GCOM)} \approx 0)$. $\cmp{GCOM}{\phi_1}$ is clearly a good
-        affine parameter along which to construct models and analyze the stream's characteristics.
-
-        However, data observations are not taken from the GCOM, but from  $\sim 8$ kpc distant
-        \citep{GRAVITY2018, Leung2022} in a local frame, typically from vantage points such as
-        Earth or its solar Lagrange points, and subsequently represented in the International
-        Celestial Reference System (ICRS) \citep{ICRS1997}.
-        Restricted as we are to a very local volume, there is no means to observe systems from
-        the more ``intrinsic" reference frames. In our observational frames there is no inherent
-        assurance of effecting a rotation that would similarly align the stream within observer
-        coordinates such that $\phi_2(\phi_1) \approx 0$.
-        Thankfully, most streams are adequately distant from both the Galactic center and the
-        observer, or exhibit orientations such that a rotation a) can be established or
-        b) holds valid. For most of the best-studied globular cluster streams -- \stream{GD-1},
-        \stream{Palomar 5}, \stream{Jhelum}, etc. -- this holds true. However for some streams
-        of dwarf galaxies, like the Magellanic stream which wraps multiple times around the
-        Milky Way \citep{Wannier1972}, no such transformation is possible. More generally,
-        a stream's ``sky"-projected path may be kinked, e.g. by subhalo interactions, such
-        that it is a many-to-one function in $\phi_1$.
-
-        In this work we treat with the vast majority of streams, which have a ``sky" transformation such that the stream is an injective function in $\phi_2(\phi_1)$.
-        Since we are examining known streams this transformation is known \textit{a priori}, or
-        may be constructed during pre-processing \citep[see][\S2.1]{StarkmanEtAl2023}.
-        We note that, with sufficient prior knowledge, many-to-one functions may be broken into injective segments and their connection constrained by a prior. Thus the methods
-        developed subsequently may extented and applied even to wrapped and kinked streams. However, 
-        we leave extending the model framework to a future work.
-
-    \subsection{Likelihood Setup}\label{sub:likelihood_setup}
+        $\cmp{GCOM}{\phi_1} (\phi_2^{(GCOM)} \approx 0)$. $\cmp{GCOM}{\phi_1}$
+        is clearly a good affine parameter along which to construct models and
+        analyze the stream's characteristics.
+
+        However, data observations are not taken from the GCOM, but from  $\sim
+        8$ kpc distant \citep{GRAVITY2018, Leung2022} in a local frame,
+        typically from vantage points such as Earth or its solar Lagrange
+        points, and subsequently represented in the International Celestial
+        Reference System (ICRS) \citep{ICRS1997}.  Restricted as we are to a
+        very local volume, there is no means to observe systems from the more
+        ``intrinsic" reference frames. In our observational frames there is no
+        inherent assurance of effecting a rotation that would similarly align
+        the stream within observer coordinates such that $\phi_2(\phi_1) \approx
+        0$.  Thankfully, most streams are adequately distant from both the
+        Galactic center and the observer, or exhibit orientations such that a
+        rotation a) can be established or b) holds valid. For most of the
+        best-studied globular cluster streams -- \stream{GD-1}, \stream{Palomar
+        5}, \stream{Jhelum}, etc. -- this holds true. However for some streams
+        of dwarf galaxies, like the Magellanic stream which wraps multiple times
+        around the Milky Way \citep{Wannier1972}, no such transformation is
+        possible. More generally, a stream's ``sky"-projected path may be
+        kinked, e.g. by subhalo interactions, such that it is a many-to-one
+        function in $\phi_1$.
+
+        In this work we treat with the vast majority of streams, which have a
+        ``sky" transformation such that the stream is an injective function in
+        $\phi_2(\phi_1)$.  Since we are examining known streams this
+        transformation is known \textit{a priori}, or may be constructed during
+        pre-processing \citep[see][\S2.1]{StarkmanEtAl2023}.  We note that, with
+        sufficient prior knowledge, many-to-one functions may be broken into
+        injective segments and their connection constrained by a prior. Thus the
+        methods developed subsequently may extented and applied even to wrapped
+        and kinked streams. However, we leave extending the model framework to a
+        future work.
+
+    \subsection{Likelihood Setup}\label{sub:method:likelihood_setup}
 
@@
 
-        Mixture models (MMs) are a statistical method to represent a population as a set of a sub-populations specified by probability distributions.
-These distributions are characterized by their parameters and the mixture by a corresponding set of mixture coefficients.
-Scalar mixture models may be extended to model completely general conditional distributions by making the distribution parameters and mixture coefficients into functions of a conditional input \citep{McLachlan1989MixtureM}.
-        Mixture Density Networks (MDNs) are a machine learning method to implement these general MM, taking the parameters and coefficients to be the outputs of feed-forward neural networks and as such, general continuous functions \citep{Bishop1994}.
-Functional parameters allow the model to capture variation over those parameters that is not possible with scalar-valued models.
-Moreover, by using neural networks the inferred functional forms are ``model-free" and driven entirely by the data.
-
-        For the MDN we take $x_{\cdot, 0}$, which is the first feature column of the data $\mbf{X}$, as the `independent' coordinate over which the MDN parameters are conditioned.
-In the context of streams $x_{\cdot, 0} \equiv \phi_1$ is the longitude coordinate in a reference frame rotated such that the stream is aligned along $\phi_1$.
-The parameters of the stream, the background field, and the mixing coefficients of the two are now general data-driven continuous functions along $\phi_1$.
+        Mixture models (MMs) are a statistical method to represent a population
+        as a set of a sub-populations specified by probability distributions.
+        These distributions are characterized by their parameters and the
+        mixture by a corresponding set of mixture coefficients. Scalar mixture
+        models may be extended to model completely general conditional
+        distributions by making the distribution parameters and mixture
+        coefficients into functions of a conditional input
+        \citep{McLachlan1989MixtureM}.  Mixture Density Networks (MDNs) are a
+        machine learning method to implement these general MM, taking the
+        parameters and coefficients to be the outputs of feed-forward neural
+        networks and as such, general continuous functions \citep{Bishop1994}.
+        Functional parameters allow the model to capture variation over those
+        parameters that is not possible with scalar-valued models. Moreover, by
+        using neural networks the inferred functional forms are ``model-free"
+        and driven entirely by the data.
+
+        For the MDN we take $x_{\cdot, 0}$, which is the first feature column of
+        the data $\mbf{X}$, as the `independent' coordinate over which the MDN
+        parameters are conditioned. In the context of streams $x_{\cdot, 0}
+        \equiv \phi_1$ is the longitude coordinate in a reference frame rotated
+        such that the stream is aligned along $\phi_1$. The parameters of the
+        stream, the background field, and the mixing coefficients of the two are
+        now general data-driven continuous functions along $\phi_1$.
 
@@
         \end{equation}
-        where $\cmp{q}{\pdf}$ is the PDF of the $q$-th model and $f_q$ its mixing coefficient for all $q$ models in the set of models indexed by $\mbs{I_Q}$.
-$\mbs{\theta}$ is the $\phi_1$-conditional output of the feed-forward neural network, and $\nth{\mbs{x}}$ the data on the $n$-th star in $\mbs{X}$, not including $\phi_1$.
-For convenience we drop the implied subscript $n$ in $\phi_1$, the explicit notation of $\mbs{\theta}$'s dependence on $\phi_1$, and the index set $\mbs{I}_X$ in summations over its elements $x$.
-A full detailing of notation and symbols is included in \autoref{app:notation}.
+        where $\cmp{q}{\pdf}$ is the PDF of the $q$-th model and $f_q$ its
+        mixing coefficient for all $q$ models in the set of models indexed by
+        $\mbs{I_Q}$. $\mbs{\theta}$ is the $\phi_1$-conditional output of the
+        feed-forward neural network, and $\nth{\mbs{x}}$ the data on the $n$-th
+        star in $\mbs{X}$, not including $\phi_1$. For convenience we drop the
+        implied subscript $n$ in $\phi_1$, the explicit notation of
+        $\mbs{\theta}$'s dependence on $\phi_1$, and the index set $\mbs{I}_X$
+        in summations over its elements $x$. A full detailing of notation and
+        symbols is included in \autoref{app:notation}.
 
@@
         \end{equation}
-        the summation over all models except for some ``background" index $b \in \mbs{I_Q}$.
-        We discuss the mixture weights further in \autoref{sub:mixture_weight}.
-
-        In this work we consider primarily astrometric and photometric data, (notated $\mbs{W}$ and $\mbs{M}$, respectively, as detailed in \autoref{app:notation}), but note that the MDN framework may be extended to arbitrary feature dimensions.
-        Assuming the conditional independence of the astrometry and photometry,
-        we split each model into linearly separable astrometric and photometric models $\cmp{q}{\pdf} = \cmp{q,w}{\pdf} \cmp{q,m}{\pdf}$ .
-
-        The likelihood for a single star then becomes, simplifying from \autoref{eq:general_mixture_network},
+        the summation over all models except for some ``background" index $b \in
+        \mbs{I_Q}$.  We discuss the mixture weights further in
+        \autoref{sub:method:mixture_weight}.
+
+        In this work we consider primarily astrometric and photometric data,
+        (notated $\mbs{W}$ and $\mbs{M}$, respectively, as detailed in
+        \autoref{app:notation}), but note that the MDN framework may be extended
+        to arbitrary feature dimensions.  Assuming the conditional independence
+        of the astrometry and photometry, we split each model into linearly
+        separable astrometric and photometric models $\cmp{q}{\pdf} =
+        \cmp{q,w}{\pdf} \cmp{q,m}{\pdf}$ .
+
+        The likelihood for a single star then becomes, simplifying from
+        \autoref{eq:general_mixture_network},
         \begin{equation} \label{eq:general_model}
@@
         \end{align}
-        where we have dropped the $(w), (m)$ superscript as the model types are evident from their inputs.
-We applied \autoref{eq:mixture_weight_normalization} to require only a single mixture coefficient.
-        Of course, if more components are included in the mixture then \autoref{eq:stream_and_bkg_prob} becomes the more general \autoref{eq:general_model}.
-However, this an implementation detail as any more complex model, e.g a model including a cold stream, extra-tidal features, the background stellar halo, and field globular clusters may be rearranged such that all stream-related components (cold or extra-tidal) and all other components (stellar halo and globular clusters) are grouped into multi-component \textit{stream} and \textit{background} models which themselves adhere to a \autoref{eq:general_model}-type relation.
+        where we have dropped the $(w), (m)$ superscript as the model types are
+        evident from their inputs. We applied
+        \autoref{eq:mixture_weight_normalization} to require only a single
+        mixture coefficient.  Of course, if more components are included in the
+        mixture then \autoref{eq:stream_and_bkg_prob} becomes the more general
+        \autoref{eq:general_model}. However, this an implementation detail as
+        any more complex model, e.g a model including a cold stream, extra-tidal
+        features, the background stellar halo, and field globular clusters may
+        be rearranged such that all stream-related components (cold or
+        extra-tidal) and all other components (stellar halo and globular
+        clusters) are grouped into multi-component \textit{stream} and
+        \textit{background} models which themselves adhere to a
+        \autoref{eq:general_model}-type relation.
 
@@
         Hereafter, when we refer to ``membership probability,"
-        \autoref{eq:membership_prob} provides the formal definition. We nuance this definition by considering missing feature dimensions in the following subsection.
-
-    \subsection{Missing Phase-Space Observations} \label{sub:missing_data}
-
-        Streams have a diversity of measurement coverage: several have full 6-D astrometrics as well as photometrics and chemical abundances available \citep[e.g.,][]{Koposov2019, 2020A&A...635L...3A, 2022ApJ...928...30L}, while most have partial coverage, lacking some feature dimensions.
+        \autoref{eq:membership_prob} provides the formal definition. We nuance
+        this definition by considering missing feature dimensions in the
+        following subsection.
+
+    \subsection{Missing Phase-Space Observations} \label{sub:method:missing_data}
+
+        Streams have a diversity of measurement coverage: several have full 6-D
+        astrometrics as well as photometrics and chemical abundances available
+        \citep[e.g.,][]{Koposov2019, 2020A&A...635L...3A, 2022ApJ...928...30L},
+        while most have partial coverage, lacking some feature dimensions.
         % TODO: terminology ND-phase-space vs feature columns
-        Most streams in \gaia {\color{red} [cite]}, for instance, have proper motions but not radial velocities nor reliable parallax measurements.
-Followup surveys, like \dataarchive{S5} {\color{red} [cite]}, add many feature dimensions, however only for a select set of streams.
-Given the diversity of coverage it is important that the likelihood model -- \autoref{eq:membership_prob} -- account for missing data.
-
-        The method of treatment of missing data depends on the cause for that data to be missing.
-        Broadly, there are two categories of causes: randomness and systematics.
-        Consider a dataset with all features measured but with a random subset of features masked.
-        One possible approach is to attempt to impute the missing features, then feed the full-featured data to the likelihood model.
-Alternatively, the likelihood model might use only the present features, ignoring those missing.
-If however, features are missing for systematic reasons, then this approach can introduce systematic bias.
-Consider a star too far away to measure it's parallax distance or radial velocity.
-This is a systematic reason and this information should be incorporated into any model as a prior.
-Not doing so, the data imputation approach might predict too-close distances.
-Likewise, using only present features in the likelihood model misses that the star is likely very distant.
-        The effects of mask systematics are mitigated by not including such data,
+        Most streams in \gaia {\color{red} [cite]}, for instance, have proper
+        motions but not radial velocities nor reliable parallax measurements.
+        Followup surveys, like \dataarchive{S5} {\color{red} [cite]}, add many
+        feature dimensions, however only for a select set of streams. Given the
+        diversity of coverage it is important that the likelihood model --
+        \autoref{eq:membership_prob} -- account for missing data.
+
+        The method of treatment of missing data depends on the cause for that
+        data to be missing.  Broadly, there are two categories of causes:
+        randomness and systematics.  Consider a dataset with all features
+        measured but with a random subset of features masked.  One possible
+        approach is to attempt to impute the missing features, then feed the
+        full-featured data to the likelihood model. Alternatively, the
+        likelihood model might use only the present features, ignoring those
+        missing. If however, features are missing for systematic reasons, then
+        this approach can introduce systematic bias. Consider a star too far
+        away to measure it's parallax distance or radial velocity. This is a
+        systematic reason and this information should be incorporated into any
+        model as a prior. Not doing so, the data imputation approach might
+        predict too-close distances. Likewise, using only present features in
+        the likelihood model misses that the star is likely very distant.  The
+        effects of mask systematics are mitigated by not including such data,
         moving the contribution of the systematics from a prior to the evidence.
-        Our models compute likelihoods under a specific dataset, and \autoref{eq:membership_prob} is a ratio of the probabilities, so the removed systematics are not expected to be impactful.
-
-        We adopt the approach of modeling the data masks as randomly-distributed and not systematic.
-We do not impute missing data, instead the per-star likelihood is modelled with a distribution with the same dimensionality as the data vector.
-        For example, a star with a 6D astrometric measurement will be modelled with a full 6D distribution, while a star missing its radial velocity measurement will be modelled with a dimensionally-reduced (5D) form of the 6D distribution.
-Using dimensionally reduced distributions ensure that missing phase-space dimensions do not amplify nor suppress the likelihood.
-        Notwithstanding, we include a quality flag on our calculations indicating the number of missing features.
-        We leave incorporating priors on the data mask distribution to future work.
+        Our models compute likelihoods under a specific dataset, and
+        \autoref{eq:membership_prob} is a ratio of the probabilities, so the
+        removed systematics are not expected to be impactful.
+
+        We adopt the approach of modeling the data masks as randomly-distributed
+        and not systematic. We do not impute missing data, instead the per-star
+        likelihood is modelled with a distribution with the same dimensionality
+        as the data vector.  For example, a star with a 6D astrometric
+        measurement will be modelled with a full 6D distribution, while a star
+        missing its radial velocity measurement will be modelled with a
+        dimensionally-reduced (5D) form of the 6D distribution. Using
+        dimensionally reduced distributions ensure that missing phase-space
+        dimensions do not amplify nor suppress the likelihood.  Notwithstanding,
+        we include a quality flag on our calculations indicating the number of
+        missing features.  We leave incorporating priors on the data mask
+        distribution to future work.
 
@@
     \vspace{10pt}
-    \subsection{Determination of the Mixture Weight} \label{sub:mixture_weight}
-        The mixture weight $f_q(\phi_1)$ as used in \autoref{eq:general_model} is characterized as the fraction of stars belonging to the mixture component $q$ over an increment $[\phi_1, \phi_1 + \dif{\phi_1}]$.
-Thus, the mixture weight encodes information about the linear density of the stream, which has been shown to depend on substructure in the galaxy (CITE-x).
-The dependence of the mixture weight on the linear density is captured by the expression
+    \subsection{Determination of the Mixture Weight} \label{sub:method:mixture_weight}
+
+        The mixture weight $f_q(\phi_1)$ as used in \autoref{eq:general_model}
+        is characterized as the fraction of stars belonging to the mixture
+        component $q$ over an increment $[\phi_1, \phi_1 + \dif{\phi_1}]$. Thus,
+        the mixture weight encodes information about the linear density of the
+        stream, which has been shown to depend on substructure in the galaxy
+        (CITE-x). The dependence of the mixture weight on the linear density is
+        captured by the expression
         \begin{equation}\label{eq:fraction_param}
@@
         \end{equation}
-        where $N_q\left(\phi_1\right)$ is the number of stars in component $q$ within an interval $[\phi_1, \phi_1 + \dif{\phi_1}]$, and 
-        $N_{\rm tot}$ is the total number of stars in the same band (including those in component $q$). The linear  density for component $q$ is then entirely specified by the function $N_q(\phi_1)$.
-
-        The mixture model specified in \S-X only models the weight parameter $f_q$, and not the components of the ratio in \autoref{eq:fraction_param}.
-However, the linear density $N_q(\phi_1)$ can be readily obtained from $f_q$, provided that $N_{\rm tot}\left(\phi_1\right)$ can be calculated.
-Importantly, this function does not depend on the parameters of the on-stream or off-stream model.
-Instead, $N_{\rm tot}(\phi_1)$ is simply the number of stars in a small $\phi_1$ increment.
-We therefore model $N_{\rm tot}\left(\phi_1\right)$ as a post-processing step using a single normalzing flow in $\phi_1$.
-
-        In particular, for a given field the distribution of $\phi_1$ coordinates is specified by the set $\{\phi_1\}_f$.
-A normalizng flow is trained to this dataset, and will satisfy $\int d\phi_1 P_{\phi_f}(\phi_1) = 1$ by construction.
-In order to re-weight the normalizing flow to obtain $N_{\rm tot}(\phi_1)$, we simply rescale $P_{\phi}(\phi_1)$ by $N_{\rm tot,0}$, which is the total number of stars in the field considered.
-We can then obtain the linear stream density with
+        where $N_q\left(\phi_1\right)$ is the number of stars in component $q$
+        within an interval $[\phi_1, \phi_1 + \dif{\phi_1}]$, and $N_{\rm tot}$
+        is the total number of stars in the same band (including those in
+        component $q$). The linear  density for component $q$ is then entirely
+        specified by the function $N_q(\phi_1)$.
+
+        The mixture model specified in \S-X only models the weight parameter
+        $f_q$, and not the components of the ratio in
+        \autoref{eq:fraction_param}. However, the linear density $N_q(\phi_1)$
+        can be readily obtained from $f_q$, provided that $N_{\rm
+        tot}\left(\phi_1\right)$ can be calculated. Importantly, this function
+        does not depend on the parameters of the on-stream or off-stream model.
+        Instead, $N_{\rm tot}(\phi_1)$ is simply the number of stars in a small
+        $\phi_1$ increment. We therefore model $N_{\rm tot}\left(\phi_1\right)$
+        as a post-processing step using a single normalzing flow in $\phi_1$.
+
+        In particular, for a given field the distribution of $\phi_1$
+        coordinates is specified by the set $\{\phi_1\}_f$. A normalizng flow is
+        trained to this dataset, and will satisfy $\int d\phi_1
+        P_{\phi_f}(\phi_1) = 1$ by construction. In order to re-weight the
+        normalizing flow to obtain $N_{\rm tot}(\phi_1)$, we simply rescale
+        $P_{\phi}(\phi_1)$ by $N_{\rm tot,0}$, which is the total number of
+        stars in the field considered. We can then obtain the linear stream
+        density with
         \begin{equation}
@@
 
-    \subsection{Astrometric Model} \label{sub:astrometric_model}
-
-        \subsubsection{On-Stream} \label{ssub:astrometric_model_on_stream}
-
-            The astrometric track is modeled with a neural network, encompassing each phase space dimension, parameterized as a function of $\phi_1$.
-The neural network output for a single stream component is the mean location of the stream track in each dimension, $\astroM{\mbs{\mu}}(\phi_1)$, and its associated covariance matrix $\astroM{\mbs{\Sigma}}(\phi_1)$.
-The probability for the data is then
+    \subsection{Astrometric Model} \label{sub:method:astrometric_model}
+
+        \subsubsection{On-Stream} \label{ssub:method:astrometric_model:on_stream}
+
+            The astrometric track is modeled with a neural network, encompassing
+            each phase space dimension, parameterized as a function of $\phi_1$.
+            The neural network output for a single stream component is the mean
+            location of the stream track in each dimension,
+            $\astroM{\mbs{\mu}}(\phi_1)$, and its associated covariance matrix
+            $\astroM{\mbs{\Sigma}}(\phi_1)$. The probability for the data is
+            then
             \begin{equation}
@@
             \end{equation}
-            where $\astroM{\mbs{\theta}}$ is the set of neural network parameters that define $\astroM{\mbs{\mu}}$ and $\astroM{\mbs{\Sigma}}$; and $\cmp{w}{\nth{\mbs{\Sigma}}}$ the data uncertainties.
-            In the simplest case, we take $\cmp{w}{\nth{\mbs{\Sigma}}}, \astroM{\mbs{\Sigma}}$ to be diagonal, consisting of both intrinsic dispersion for each dimension of $\mbs{w}$ and the data uncertainties added in quadrature.
-The data uncertainties $\cmp{w}{\nth{\mbs{\Sigma}}}$ are drawn from $\mbs{\delta}\mbf{W}$, the dataset of astrometric uncertainties (see \autoref{app:notation}).
-
-            In practice, we work with truncated Gaussians, where the truncation is set by the size of the field in each astrometric dimension.
-Details of the truncated Gaussian are included in \autoref{app:sub:normal_distribution}.
-Truncating to the field ensures that the probability density is zero wherever there is no data.
-This has an added benefit of correctly normalizing the Gaussian distribution, which is not compact (has non-zero probability over all space) and would otherwise not integrate to one within the field.
-
-            As a MDN, we implement the Gaussian distribution parameters with a multi-layered feed-forward neural network.
-The number of layers required depends on the maximum dimensionality of the Gaussian, and whether the neural network employs regularization techniques like dropout.
-We use alternating layers of linear and tanh units.
-Details of the network architecture are discussed in \autoref{sub:model_implementation}.
-
-            In the presence of missing phase-space coordinate $f_k$ we reduce the dimensionality of the Gaussian to that of the data-vector.
-Namely, for $\mbs{I}_{\tilde{F}} \equiv \mbs{I}_{F} \backslash \{f_k\}$
+            where $\astroM{\mbs{\theta}}$ is the set of neural network
+            parameters that define $\astroM{\mbs{\mu}}$ and
+            $\astroM{\mbs{\Sigma}}$; and $\cmp{w}{\nth{\mbs{\Sigma}}}$ the data
+            uncertainties.  In the simplest case, we take
+            $\cmp{w}{\nth{\mbs{\Sigma}}}, \astroM{\mbs{\Sigma}}$ to be diagonal,
+            consisting of both intrinsic dispersion for each dimension of
+            $\mbs{w}$ and the data uncertainties added in quadrature. The data
+            uncertainties $\cmp{w}{\nth{\mbs{\Sigma}}}$ are drawn from
+            $\mbs{\delta}\mbf{W}$, the dataset of astrometric uncertainties (see
+            \autoref{app:notation}).
+
+            In practice, we work with truncated Gaussians, where the truncation
+            is set by the size of the field in each astrometric dimension.
+            Details of the truncated Gaussian are included in
+            \autoref{app:sub:normal_distribution}. Truncating to the field
+            ensures that the probability density is zero wherever there is no
+            data. This has an added benefit of correctly normalizing the
+            Gaussian distribution, which is not compact (has non-zero
+            probability over all space) and would otherwise not integrate to one
+            within the field.
+
+            As a MDN, we implement the Gaussian distribution parameters with a
+            multi-layered feed-forward neural network. The number of layers
+            required depends on the maximum dimensionality of the Gaussian, and
+            whether the neural network employs regularization techniques like
+            dropout. We use alternating layers of linear and tanh units. Details
+            of the network architecture are discussed in
+            \autoref{sub:methods:model_implementation}.
+
+            In the presence of missing phase-space coordinate $f_k$ we reduce
+            the dimensionality of the Gaussian to that of the data-vector.
+            Namely, for $\mbs{I}_{\tilde{F}} \equiv \mbs{I}_{F} \backslash
+            \{f_k\}$
             \begin{align}
@@
 
-        \subsubsection{Off-stream} \label{ssub:astrometric_model_off_stream}
-
-            We now outline the off-stream astrometric model.
-We take a similar approach to the on-stream astrometric model discussed in \autoref{ssub:astrometric_model_on_stream}, though we typically do not characterize the backgrounds with a Gaussian distribution.
-Instead, we utilize a range of distributions (i.e., exponential, skew-normal) discussed in \autoref{app:distributions}.
-The parameters of the user-specified background distributions are themselves neural network outputs, such that any $\phi_1$ ``slice" of the background should be characterized by some analytic density, but the evolution of the backgrounds with $\phi_1$ can be complex.
-Details of the network architecture are discussed in \autoref{sub:model_implementation}.
-
-            Let $\Bcmp{\fth{\mbs{\theta}}}(\phi_1)$ represent the neural network which outputs a vector of parameters characterizing the background distribution at a given $\phi_1$ for astrometric dimension $f$.
-The number of outputs for the background model is equal to $\mathrm{dim}\left(\fth{\Bcmp{\mbs{\theta}}}\right)$ (where $f=0$ corresponds to $\phi_1$, which we do not model).
-At a given $\phi_1$, the probability density for the astrometric dimension $f>0$ is $\Bcmp{\fth{\pdf}}\left(\mbs{w}_{n,f} | \Bcmp{\fth{\mbs{\theta}}}(\phi_1) \right)$.
-We treat each background component as independent, allowing us to write the likelihood as a product over the astrometric dimensions:
+        \subsubsection{Off-stream} \label{ssub:method:astrometric_model:off_stream}
+
+            We now outline the off-stream astrometric model. We take a similar
+            approach to the on-stream astrometric model discussed in
+            \autoref{ssub:method:astrometric_model:on_stream}, though we
+            typically do not characterize the backgrounds with a Gaussian
+            distribution. Instead, we utilize a range of distributions (i.e.,
+            exponential, skew-normal) discussed in \autoref{app:distributions}.
+            The parameters of the user-specified background distributions are
+            themselves neural network outputs, such that any $\phi_1$ ``slice"
+            of the background should be characterized by some analytic density,
+            but the evolution of the backgrounds with $\phi_1$ can be complex.
+            Details of the network architecture are discussed in
+            \autoref{sub:methods:model_implementation}.
+
+            Let $\Bcmp{\fth{\mbs{\theta}}}(\phi_1)$ represent the neural network
+            which outputs a vector of parameters characterizing the background
+            distribution at a given $\phi_1$ for astrometric dimension $f$. The
+            number of outputs for the background model is equal to
+            $\mathrm{dim}\left(\fth{\Bcmp{\mbs{\theta}}}\right)$ (where $f=0$
+            corresponds to $\phi_1$, which we do not model). At a given
+            $\phi_1$, the probability density for the astrometric dimension
+            $f>0$ is $\Bcmp{\fth{\pdf}}\left(\mbs{w}_{n,f} |
+            \Bcmp{\fth{\mbs{\theta}}}(\phi_1) \right)$. We treat each background
+            component as independent, allowing us to write the likelihood as a
+            product over the astrometric dimensions:
             \begin{equation} \label{eq:astrometric_model_off_stream_probability}
@@
             \end{equation}
-            Where $\mbs{I}_{\tilde{F}}$ is the set of indices of the features, omitting missing phase space dimensions.
+            Where $\mbs{I}_{\tilde{F}}$ is the set of indices of the features,
+            omitting missing phase space dimensions.
 
@@
 
-    \subsection{Photometric Model} \label{sub:photometric_model}
-
-        \subsubsection{On-Stream} \label{sub:photometric_model_on_stream}
-            In photometric coordinates we model the stream as a single-population isochrone with the possibility of a non-zero distance gradient.
-We accomplish this by modeling the distance of the isochrone as a neural network output, parametrized as a function of $\phi_1$.
-The result is a distance track along the stream, estimated from the variation in its isochrone with $\phi_1$.
-
-            At any given $\phi_1$, the isochrone is modeled in absolute magnitudes
-            and parameterized by the normalized stellar mass, labeled $\gamma \in (0, 1]$, in the modeled mass range.
-For example, increasing $\gamma$ corresponds to movement up the main sequence towards the red giant branch.
-We denote the isochrone as $\mcal{I(\gamma)}$.
-The intrinsic dipsersion around the isochrone is $\Sigma_\mcal{I}(\gamma)$.
-Since the isochrone is in absolute magnitudes, but the data are in apparent magnitudes,
-            it is necessary to shift the isochrone by a distance modulus to the predicted distance of the stream, labeled  $\mu(\phi_1)$, with intrinsic stream distance variation $\sigma_\mu(\gamma)$.
+    \subsection{Photometric Model} \label{sub:method:photometric_model}
+
+        \subsubsection{On-Stream} \label{sub:method:photometric_model:on_stream}
+
+            In photometric coordinates we model the stream as a
+            single-population isochrone with the possibility of a non-zero
+            distance gradient. We accomplish this by modeling the distance of
+            the isochrone as a neural network output, parametrized as a function
+            of $\phi_1$. The result is a distance track along the stream,
+            estimated from the variation in its isochrone with $\phi_1$.
+
+            At any given $\phi_1$, the isochrone is modeled in absolute
+            magnitudes and parameterized by the normalized stellar mass, labeled
+            $\gamma \in (0, 1]$, in the modeled mass range. For example,
+            increasing $\gamma$ corresponds to movement up the main sequence
+            towards the red giant branch. We denote the isochrone as
+            $\mcal{I(\gamma)}$. The intrinsic dipsersion around the isochrone is
+            $\Sigma_\mcal{I}(\gamma)$. Since the isochrone is in absolute
+            magnitudes, but the data are in apparent magnitudes, it is necessary
+            to shift the isochrone by a distance modulus to the predicted
+            distance of the stream, labeled  $\mu(\phi_1)$, with intrinsic
+            stream distance variation $\sigma_\mu(\gamma)$.
 
@@
 
-            where $\cmp{m}{\nth{\mbs{\Sigma}}}$ is the data covariance and $\prior(\gamma, \nth{\mbs{m}}, \phi_1)$ encodes both the present-day mass function of the stream, as well as any observational constraints (e.g.
-$g < 20$ mag).
-
-            We are interested in the total probability (at some $\phi_1$) and so integrate over $\gamma$ to find:
+            where $\cmp{m}{\nth{\mbs{\Sigma}}}$ is the data covariance and
+            $\prior(\gamma, \nth{\mbs{m}}, \phi_1)$ encodes both the present-day
+            mass function of the stream, as well as any observational
+            constraints (e.g. $g < 20$ mag).
+
+            We are interested in the total probability (at some $\phi_1$) and so
+            integrate over $\gamma$ to find:
             \begin{small}
@@
             \end{small}
-            Then, for a given $\phi_1$ we can obtain a distribution over the distance modulus using 
+            Then, for a given $\phi_1$ we can obtain a distribution over the
+            distance modulus using 
             \begin{align}
@@
             \end{align}
-            For each sample, we can convert the distance-modulus distribution (and error) to the distance track using 
+            For each sample, we can convert the distance-modulus distribution
+            (and error) to the distance track using 
             \begin{align}
@@
 
-            Let $\cmp{S,m}{\mbs{\theta}}(\phi_1)$ represent the feed-forward neural network which outputs a vector of parameters characterizing the stream's photometric distribution at a given $\phi_1$.
-The network has 2 outputs -- $\mu, \sigma_\mu$ -- as we only consider the distance track of the isochrone, holding fixed stellar population parameters internal to modeling the isochrone, such as its age and metallicity.
-            In principle we might include parameters of the isochrone in the model, now $\mcal{I}(\mbs{\theta}, \gamma)$, where $\theta = {a, Z, ...}$ and any other generating parameters of the isochrone.
+            Let $\cmp{S,m}{\mbs{\theta}}(\phi_1)$ represent the feed-forward
+            neural network which outputs a vector of parameters characterizing
+            the stream's photometric distribution at a given $\phi_1$. The
+            network has 2 outputs -- $\mu, \sigma_\mu$ -- as we only consider
+            the distance track of the isochrone, holding fixed stellar
+            population parameters internal to modeling the isochrone, such as
+            its age and metallicity.  In principle we might include parameters
+            of the isochrone in the model, now $\mcal{I}(\mbs{\theta}, \gamma)$,
+            where $\theta = {a, Z, ...}$ and any other generating parameters of
+            the isochrone.
             % FIXME! DO this Likewise, the dust map may be treated as a prior and it's errors incorporated into the data errors.
-            However, stellar streams are generally poorly fit by theoretic isochrones, at least ones with realistic ages and metallicities.
+            However, stellar streams are generally poorly fit by theoretic
+            isochrones, at least ones with realistic ages and metallicities.
             Consequently including the age and metallicity as model parameters
-            does not meaningfully contribute to constraining results on the stream's stellar population.
-Moreover, age and metallicity are partially degenerate with the distance modulus, working counter to the goal of fitting a distance track to the stream.
-An alternate approach is to use data-driven isochrones instead of theoretic ones.
-the age and metallicity are not meaningful quantities.
-In others, e.g.
-with a suite of models or a trained emulator, the data-driven isochrones might have realistic ages and metallicities and thus meaningfully contribute to the model.
+            does not meaningfully contribute to constraining results on the
+            stream's stellar population. Moreover, age and metallicity are
+            partially degenerate with the distance modulus, working counter to
+            the goal of fitting a distance track to the stream. An alternate
+            approach is to use data-driven isochrones instead of theoretic ones.
+            the age and metallicity are not meaningful quantities. In others,
+            e.g. with a suite of models or a trained emulator, the data-driven
+            isochrones might have realistic ages and metallicities and thus
+            meaningfully contribute to the model.
             % Is this true? re-read Uniform Modeling of 13 streams
@@
 
-            The photometric probability, \autoref{eq:photometric_probability} encodes the photometric distribution -- the ``track" -- of the isochrone model at each point along the track, as well as the amplitudes, the relative probability of points along the track.
-This is the term $\prior(\gamma, \nth{\mbs{m}} | \phi_1)$, which describes all priors on both the isochrone as well as observational constraints.
-We assume that the properties of the isochrone are conditionally independent from observational constraints; namely
+            The photometric probability, \autoref{eq:photometric_probability}
+            encodes the photometric distribution -- the ``track" -- of the
+            isochrone model at each point along the track, as well as the
+            amplitudes, the relative probability of points along the track. This
+            is the term $\prior(\gamma, \nth{\mbs{m}} | \phi_1)$, which
+            describes all priors on both the isochrone as well as observational
+            constraints. We assume that the properties of the isochrone are
+            conditionally independent from observational constraints; namely
             \begin{equation} \label{eq:isochrone_prior_components}
@@
             \end{equation}
-            where $\prior_{\mcal{I}}$ and $\prior_{obs}$ are the isochrone and observational priors, respectively.
-
-            The second term in \autoref{eq:isochrone_prior_components} -- $\prior_{obs}(\nth{\mbs{m}} | \phi_1)$ -- encodes all observational effects in the photometric dataset.
-Some effects are easily modeled, e.g.
-instruments have well-characterized magnitude limits, both faint and bright.
-Other effects are not easily modeled, e.g, complex location-dependent completeness issues \citep{GaiaCompleteness}.
-            Accounting for the completeness is very challenging. In practice we avoid
-            the contribution of completeness to $\prior_{obs}$, masking data for which it is relevant.
-\Gaia, for instance, is complete from $12 < G < 17$ and has high completeness up to $G ~20$, thus we mask $G > 20$.
-            The masks are easily modeled as magnitude limits and replace the complex completeness model in $\prior_{obs}$.
-            \autoref{sub:missing_data} explains how masking is implemented in the models, though in this case every feature is masked, not only a few feature dimensions.
-With every featured masked, the photometric model in \autoref{eq:photometric_probability} reduces from an $F_m$-dimensional Gaussian to a 0-D Gaussian, which is a null distribution and does not enter into the likelihood.
-            In photometric coordinates completeness depends on a stars apparent magnitude; vied in in astrometric coordinates, the completeness cannot be described so simply.
-\Gaia, for instance has scanning law residuals in the density field.
-When photometric coordinates are masked due to completeness, we do not mask the corresponding  astrometric features, so that the stars  membership probability is determined solely by the astrometric model.
-This practice allows us to include stars with good astrometric measurements, not penalizing those stars for which the photometric model is insufficient.
-            We examine the results to confirm that the scan pattern does not impact the
+            where $\prior_{\mcal{I}}$ and $\prior_{obs}$ are the isochrone and
+            observational priors, respectively.
+
+            The second term in \autoref{eq:isochrone_prior_components} --
+            $\prior_{obs}(\nth{\mbs{m}} | \phi_1)$ -- encodes all observational
+            effects in the photometric dataset. Some effects are easily modeled,
+            e.g. instruments have well-characterized magnitude limits, both
+            faint and bright. Other effects are not easily modeled, e.g, complex
+            location-dependent completeness issues \citep{GaiaCompleteness}.
+            Accounting for the completeness is very challenging. In practice we
+            avoid the contribution of completeness to $\prior_{obs}$, masking
+            data for which it is relevant. \Gaia, for instance, is complete from
+            $12 < G < 17$ and has high completeness up to $G ~20$, thus we mask
+            $G > 20$.  The masks are easily modeled as magnitude limits and
+            replace the complex completeness model in $\prior_{obs}$.
+            \autoref{sub:method:missing_data} explains how masking is
+            implemented in the models, though in this case every feature is
+            masked, not only a few feature dimensions. With every featured
+            masked, the photometric model in
+            \autoref{eq:photometric_probability} reduces from an
+            $F_m$-dimensional Gaussian to a 0-D Gaussian, which is a null
+            distribution and does not enter into the likelihood.  In photometric
+            coordinates completeness depends on a stars apparent magnitude; vied
+            in in astrometric coordinates, the completeness cannot be described
+            so simply. \Gaia, for instance has scanning law residuals in the
+            density field. When photometric coordinates are masked due to
+            completeness, we do not mask the corresponding  astrometric
+            features, so that the stars  membership probability is determined
+            solely by the astrometric model. This practice allows us to include
+            stars with good astrometric measurements, not penalizing those stars
+            for which the photometric model is insufficient.  We examine the
+            results to confirm that the scan pattern does not impact the
             membership distribution.
 
-            The first term in \autoref{eq:isochrone_prior_components} -- $\prior_{\mcal{I}}$ -- encodes the point-wise amplitude of the isochrone.
-            Physically, this amplitude is the the present-day mass function (PDMF).
-The PDMF $\prior_{\cal{I}}(\gamma, \phi_1)$ is a joint distribution, depending on $\gamma$ since it is the $\gamma$-dependent distribution amplitude, and also on $\phi_1$.
-This latter dependence is confusingly termed the ``mass function of the stream", which is the expected variation in the stellar mass distrubion along the stream, arising due to e.g.
-mass segregation in the progenitor \TODO{[cite]}.
-To date this variation along the stream has not been observed \TODO{[cite]}, so in practice we drop the $\phi_1$ dependence -- $\prior_{\cal{I}}(\gamma, \phi_1) = \prior_{\cal{I}}(\gamma)$ -- assuming that the PDMF is constant along the stream.
+            The first term in \autoref{eq:isochrone_prior_components} --
+            $\prior_{\mcal{I}}$ -- encodes the point-wise amplitude of the
+            isochrone.  Physically, this amplitude is the the present-day mass
+            function (PDMF). The PDMF $\prior_{\cal{I}}(\gamma, \phi_1)$ is a
+            joint distribution, depending on $\gamma$ since it is the
+            $\gamma$-dependent distribution amplitude, and also on $\phi_1$.
+            This latter dependence is confusingly termed the ``mass function of
+            the stream", which is the expected variation in the stellar mass
+            distrubion along the stream, arising due to e.g. mass segregation in
+            the progenitor \TODO{[cite]}. To date this variation along the
+            stream has not been observed \TODO{[cite]}, so in practice we drop
+            the $\phi_1$ dependence -- $\prior_{\cal{I}}(\gamma, \phi_1) =
+            \prior_{\cal{I}}(\gamma)$ -- assuming that the PDMF is constant
+            along the stream.
 
             % link to the code!
-            In the code we offer a few ansatz for the PDMF, though any user-defined function may be used instead.
-The default assumption, known to be non-physical, is a uniform distribution over $\gamma$.
-Similarly non-physical are truncated uniform distributions, considering only a segment of the isochrone, e.g.
-the main sequence turnoff (MSTO).
-We include also a Kroupa initial mass function (IMF) \citep{2001MNRAS.322..231K}.
-The Kroupa IMF, and all physically-motivated IMFs,
-            have an much larger fraction of low-mass stars then high-mass stars, the latter being less likely to form.
-This is observed in streams, particularly their progenitors.
-However the Kroupa IMF, and all IMF, are poor fits to the observed PDMF as stream progenitors like globular clusters are extremely old ($\sim10$ Gyr) while an IMF is the zero-age distribution.
-            How then should the PDMF $\prior_{\cal{I}}$ be treated?
+            In the code we offer a few ansatz for the PDMF, though any
+            user-defined function may be used instead. The default assumption,
+            known to be non-physical, is a uniform distribution over $\gamma$.
+            Similarly non-physical are truncated uniform distributions,
+            considering only a segment of the isochrone, e.g. the main sequence
+            turnoff (MSTO). We include also a Kroupa initial mass function (IMF)
+            \citep{2001MNRAS.322..231K}. The Kroupa IMF, and all
+            physically-motivated IMFs, have an much larger fraction of low-mass
+            stars then high-mass stars, the latter being less likely to form.
+            This is observed in streams, particularly their progenitors. However
+            the Kroupa IMF, and all IMF, are poor fits to the observed PDMF as
+            stream progenitors like globular clusters are extremely old
+            ($\sim10$ Gyr) while an IMF is the zero-age distribution.  How then
+            should the PDMF $\prior_{\cal{I}}$ be treated?
             % ⬆ rephrase previous sentence
-            One approach to the PDMF is to use a more informed distribution, for example time-evolving an IMF, either analytically or by simulation, to the age of the stream's stellar population.
-            As discussed previously, globular clusters are known to be poorly fit by theoretic isochrones with realistic inputs (e.g.
-age, $Z$).
-Thus fitting an isochrone's track to the data means its age, metallicity and therefore PDMF
-            are not well fit \TODO{[cite]}. Moreover, for many streams, e.g. those lacking known progenitors, the PDMF is observationally poorly constrained.
-            In short, using any fixed distribution is simple in implementation, however the choice of distribution is not.
-
-            Rather than using a fixed \textit{a priori} ansatz, another approach to the PDMF is to incorporate it into the model,
-            parameterized by some distribution and fit simultaneously to the distance modulus and other $\cmp{m}{\mbs{\theta}}$.
-            We find this, like incorporating $a, Z$ into the isochrone model, to be interesting avenues by which to develop the model.
-However the resulting significant increase in model flexibility necessitates careful regulation,
-            and we leave this to a future work.
+            One approach to the PDMF is to use a more informed distribution, for
+            example time-evolving an IMF, either analytically or by simulation,
+            to the age of the stream's stellar population.  As discussed
+            previously, globular clusters are known to be poorly fit by
+            theoretic isochrones with realistic inputs (e.g. age, $Z$). Thus
+            fitting an isochrone's track to the data means its age, metallicity
+            and therefore PDMF are not well fit \TODO{[cite]}. Moreover, for
+            many streams, e.g. those lacking known progenitors, the PDMF is
+            observationally poorly constrained.  In short, using any fixed
+            distribution is simple in implementation, however the choice of
+            distribution is not.
+
+            Rather than using a fixed \textit{a priori} ansatz, another approach
+            to the PDMF is to incorporate it into the model, parameterized by
+            some distribution and fit simultaneously to the distance modulus and
+            other $\cmp{m}{\mbs{\theta}}$.  We find this, like incorporating $a,
+            Z$ into the isochrone model, to be interesting avenues by which to
+            develop the model. However the resulting significant increase in
+            model flexibility necessitates careful regulation, and we leave this
+            to a future work.
 
             % TODO? expand this section.
-            The last approach to the issue of the PDMF, and the one we take in this work, is to render it unimportant. 
-            With fixed age, metallicity, and other isochrone model parameters, the primary purpose of the isochrone is to allow the model to determine the distance modulus of the stream.
-For this, only a portion of the stream need be modeled.
-            For streams with observable main sequence turn-offs, like \stream{GD-1} in \gaia, this portion of the isochrone has both many stars and a relatively small range in masses.
-Thus, we restrict the mass range of the isochrone such that we are modeling only a region of interest over which the PDMF does not contribute to the final result.
-            % TODO? work in something to the effect of:
-            % The PDMF doesn't have an enormous impact, regardless as the isochrone model is very thin and stars close to the isochrone photometrically are generally quite far astrometrically.
-This is an advantange of simultaneous modeling, where errors in one model are balanced by other parts of the model.
+            The last approach to the issue of the PDMF, and the one we take in
+            this work, is to render it unimportant.  With fixed age,
+            metallicity, and other isochrone model parameters, the primary
+            purpose of the isochrone is to allow the model to determine the
+            distance modulus of the stream. For this, only a portion of the
+            stream need be modeled.  For streams with observable main sequence
+            turn-offs, like \stream{GD-1} in \gaia, this portion of the
+            isochrone has both many stars and a relatively small range in
+            masses. Thus, we restrict the mass range of the isochrone such that
+            we are modeling only a region of interest over which the PDMF does
+            not contribute to the final result.
+            % TODO? work in something to the effect of: The PDMF doesn't have an
+            % enormous impact, regardless as the isochrone model is very thin
+            % and stars close to the isochrone photometrically are generally
+            % quite far astrometrically. This is an advantange of simultaneous
+            % modeling, where errors in one model are balanced by other parts of
+            % the model.
 
@@
 
-        \subsubsection{Linking to Astrometrics: the Distance Modulus and the Parallax} \label{ssub:linking_to_astrometrics}
+        \subsubsection{Linking to Astrometrics: the Distance Modulus and the Parallax} \label{ssub:method:linking_to_astrometrics}
 
             % TODO: rephrase
-            By modeling jointly the astrometrics and photometrics we may tie together components of the models.
-            In particular, the distance modulus in the photometric model and the parallax in the astrometric model are both measures of the distance track of the stream.
-            We introduce a prior to connect these components of the model:
+            By modeling jointly the astrometrics and photometrics we may tie
+            together components of the models.  In particular, the distance
+            modulus in the photometric model and the parallax in the astrometric
+            model are both measures of the distance track of the stream.  We
+            introduce a prior to connect these components of the model:
             \begin{align}
@@
             % TODO: should we show that these are different distance functions? or is it obvious
-            where $\delta$ is the Dirac delta function \citep{1947pqm..book.....D}, and enforces that the distance modulus track and parallax track must be equal (when converted to the actual distance) as a function of $\phi_1$.
-            The widths are similarly constrained. The distance and first-order error conversion are given by
+            where $\delta$ is the Dirac delta function
+            \citep{1947pqm..book.....D}, and enforces that the distance modulus
+            track and parallax track must be equal (when converted to the actual
+            distance) as a function of $\phi_1$.  The widths are similarly
+            constrained. The distance and first-order error conversion are given
+            by
             \begin{align}
@@
 
-            In practice, at the distance of many streams the errors in the parallaxes are of order 1 and we exclude the feature from the model.
+            In practice, at the distance of many streams the errors in the
+            parallaxes are of order 1 and we exclude the feature from the model.
             % TODO!
@@
 
-        \subsubsection{Off-stream} \label{sub:photometric_model_off_stream}
-            In this section we introduce our model for the distribution of backgrounds in photometric coordinates. 
-            The distribution of stars in color (i.e., $g-r$) and magnitude (i.e., $g$) is a complicated function of location in the galaxy \TODO{(e.g.
-[cite])}.
-Even within a field centered on the stream of interest, the color-magnitude diagram (CMD) is a combination of stellar populations distributed over a range in distances.
-Because of this, we do not expect an analytic density to provide a realistic description of the data.
-In this work we take a data-driven approach, and represent the CMD using a normalizing flow model.
-
-            Normalizing flows provide a flexible description of a probability density, by transforming samples generated from a simple base distribution (i.e., a Gaussian) to the more complicated target distribution.
-The transformations are typically non-linear outputs of a neural neural network, whose parameters are optimized until the target density accurately characterizes the data.
-The neural network transformation is differentiable, so that jacobian factors can be combined to ensure that the the target distribution remains a valid probability density (i.e., integrates to one) \TODO{[cite]}.
-
-            Our implementation is as follows.
-For a given stream, we restrict the data to some field characterized by a polygon drawn around the stream.
-Because our density modeling is aimed at stream characterization rather than discovery, we assume that the stream is sufficiently well known so that it can be masked out as a simple cut in (e.g.) $\phi1-\phi_2$ coordinates.
-With the stream masked out, we then fit a normalizing flow to the photometric data.
-Because the background CMD can evolve with $\phi_1$, we fit a \emph{conditional} normalizing flow, $q_{\rm flow}(\mathbf{m}|\phi_1)$, so that the color-magnitude diagram is conditionally dependent on position along the stream.
-In practice, we model magntiudes and not colors (i.e., $\mathbf{m} = (g,r)$ rather than $g \ \mathrm{and} \ g-r$.
-Otherwise, the two arguments will always be covariate).
-Our central assumption with this model is that the distribution of colors and magnitudes for background stars in the masked region are quantitatively similar to those in the unmasked region.
-For a sufficiently narrow mask we expect this to be the case, and find that this assumption does not introduce bias for the streams considered in this work.
-
-            Once the normalizing flow, $q_{\rm flow}\left(\mathbf{m} | \phi_1\right)$, is fit to the data, its parameters are fixed while the other components of the model begin training.
-Therefore, the normalizing flow can be rapidly trained and computed as a pre-processing step.
-
-            % The specific architecture of the photometric normalizing flow are discussed in \autoref{sub:model_implementation}. But
-            It is easy to evaluate the log-likelihood a normalizing flow at a point $\mbs{m}$ when all feature dimensions are present.
-When one (or more) feature dimension is missing, however, evaluating the marginal log-likelihood involves integrals over the flow.
-While the procedure is straightforward it is computationally expensive.
-As an alternative, we conservatively set the log-likelihood to $0$, the maximum value, overemphasizing the flow's contribution to the background model.
-Conceptually, up-weighting the background model decreases the false-positive rate in stream membership identification, at the
-            cost of increasing the false-negative rate.
-However, the intrinsic width of stellar streams tends to be quite small, with correspondingly small $\sigma_\mu$ (see \autoref{eq:photometric_probability}); thus the effective region of the isochrone model is well determined and we do not find the marginal log-likelihood approach to be impactful.
-Another approach, which we leave to a future work, is to construct normalizing flows of each marginal distribution, e.g.
-$q_{\rm flow}\left(\{m_i\}_{i \in \mbs{I}_F, i \neq {j, k}} | m_j, m_k, \phi_1\right)$, and select for each $\nth{\mbs{m}}$ the correct flow given the present features.
+        \subsubsection{Off-stream}
+        \label{sub:method:photometric_model:off_stream}
+
+            In this section we introduce our model for the distribution of
+            backgrounds in photometric coordinates.  The distribution of stars
+            in color (i.e., $g-r$) and magnitude (i.e., $g$) is a complicated
+            function of location in the galaxy \TODO{(e.g. [cite])}. Even within
+            a field centered on the stream of interest, the color-magnitude
+            diagram (CMD) is a combination of stellar populations distributed
+            over a range in distances. Because of this, we do not expect an
+            analytic density to provide a realistic description of the data. In
+            this work we take a data-driven approach, and represent the CMD
+            using a normalizing flow model.
+
+            Normalizing flows provide a flexible description of a probability
+            density, by transforming samples generated from a simple base
+            distribution (i.e., a Gaussian) to the more complicated target
+            distribution. The transformations are typically non-linear outputs
+            of a neural neural network, whose parameters are optimized until the
+            target density accurately characterizes the data. The neural network
+            transformation is differentiable, so that jacobian factors can be
+            combined to ensure that the the target distribution remains a valid
+            probability density (i.e., integrates to one) \TODO{[cite]}.
+
+            Our implementation is as follows. For a given stream, we restrict
+            the data to some field characterized by a polygon drawn around the
+            stream. Because our density modeling is aimed at stream
+            characterization rather than discovery, we assume that the stream is
+            sufficiently well known so that it can be masked out as a simple cut
+            in (e.g.) $\phi1-\phi_2$ coordinates. With the stream masked out, we
+            then fit a normalizing flow to the photometric data. Because the
+            background CMD can evolve with $\phi_1$, we fit a \emph{conditional}
+            normalizing flow, $q_{\rm flow}(\mathbf{m}|\phi_1)$, so that the
+            color-magnitude diagram is conditionally dependent on position along
+            the stream. In practice, we model magntiudes and not colors (i.e.,
+            $\mathbf{m} = (g,r)$ rather than $g \ \mathrm{and} \ g-r$.
+            Otherwise, the two arguments will always be covariate). Our central
+            assumption with this model is that the distribution of colors and
+            magnitudes for background stars in the masked region are
+            quantitatively similar to those in the unmasked region. For a
+            sufficiently narrow mask we expect this to be the case, and find
+            that this assumption does not introduce bias for the streams
+            considered in this work.
+
+            Once the normalizing flow, $q_{\rm flow}\left(\mathbf{m} |
+            \phi_1\right)$, is fit to the data, its parameters are fixed while
+            the other components of the model begin training. Therefore, the
+            normalizing flow can be rapidly trained and computed as a
+            pre-processing step.
+
+            % The specific architecture of the photometric normalizing flow are
+            % discussed in \autoref{sub:methods:model_implementation}. But
+            It is easy to evaluate the log-likelihood a normalizing flow at a
+            point $\mbs{m}$ when all feature dimensions are present. When one
+            (or more) feature dimension is missing, however, evaluating the
+            marginal log-likelihood involves integrals over the flow. While the
+            procedure is straightforward it is computationally expensive. As an
+            alternative, we conservatively set the log-likelihood to $0$, the
+            maximum value, overemphasizing the flow's contribution to the
+            background model. Conceptually, up-weighting the background model
+            decreases the false-positive rate in stream membership
+            identification, at the cost of increasing the false-negative rate.
+            However, the intrinsic width of stellar streams tends to be quite
+            small, with correspondingly small $\sigma_\mu$ (see
+            \autoref{eq:photometric_probability}); thus the effective region of
+            the isochrone model is well determined and we do not find the
+            marginal log-likelihood approach to be impactful. Another approach,
+            which we leave to a future work, is to construct normalizing flows
+            of each marginal distribution, e.g. $q_{\rm flow}\left(\{m_i\}_{i
+            \in \mbs{I}_F, i \neq {j, k}} | m_j, m_k, \phi_1\right)$, and select
+            for each $\nth{\mbs{m}}$ the correct flow given the present
+            features.
 
@@
 
-    \subsection{Priors} \label{sub:priors}
-
-        In \autoref{sub:likelihood_setup} we introduced the likelihood setup.
-In \autoref{sub:photometric_model_on_stream} we added priors in the form of the isochrone's PDMF and photometric observational constraints.
-In this section we
-        introduce and develop more priors that are important for training the BMDN's parameters' neural network(s).
-
-        \subsubsection{Parameter Bounds} \label{ssub:parameter_bounds}
-
-            For each parameter in $\mbs{\theta}$ of the model we implement priors on its range.
-            Uninformative, e.g.
-uniform $\mcal{U}(a, b)$, priors are often assumed where little is known about a parameter (except that $(a,b]$ contain the correct $\theta$ and its distribution).
-Where more is known about $\theta$, for instance that it is a categorical, more informative priors like the Dirichlet distribution \citep{Bishop_Christopher_M_2016-08-23} may be used.
-Our code permits any user-defined prior, and we include $\mcal{U}(a, b)$.
-            The default choice of prior and bounds $\mcal{U}$ set to the limits of the dataset in each feature dimension.
+    \subsection{Priors} \label{sub:methods:priors}
+
+        In \autoref{sub:method:likelihood_setup} we introduced the likelihood
+        setup. In \autoref{sub:method:photometric_model:on_stream} we added
+        priors in the form of the isochrone's PDMF and photometric observational
+        constraints. In this section we introduce and develop more priors that
+        are important for training the BMDN's parameters' neural network(s).
+
+        \subsubsection{Parameter Bounds} \label{ssub:methods:priors:parameter_bounds}
+
+            For each parameter in $\mbs{\theta}$ of the model we implement
+            priors on its range.  Uninformative, e.g. uniform $\mcal{U}(a, b)$,
+            priors are often assumed where little is known about a parameter
+            (except that $(a,b]$ contain the correct $\theta$ and its
+            distribution). Where more is known about $\theta$, for instance that
+            it is a categorical, more informative priors like the Dirichlet
+            distribution \citep{Bishop_Christopher_M_2016-08-23} may be used.
+            Our code permits any user-defined prior, and we include $\mcal{U}(a,
+            b)$.  The default choice of prior and bounds $\mcal{U}$ set to the
+            limits of the dataset in each feature dimension.
             % ⬆ where should this sentence be?
 
-            The choice of prior is important, not only for the information it adds to the model, but also for how optimizers explore the parameter space.
-Simple optimizers, like MCMC \TODO{[cite]}, propose a parameter vector then compute its likelihood given the data.
-Priors with compact support  $\theta \sim \mcal{D}((a, b])$, e.g.
-$\mcal{U}(a, b)$, may be very dangerous as the optimizer can be initialized in a region with zero probability and has no means but blind luck to find the region of support -- the region with non-zero likelihood.
-More sophisticated optimizers, like gradient-based descent \TODO{[cite]}, are susceptible to a similar initialization problem, allowing zero-probability regions, but requiring at least a non-zero gradient to make informed updates to the optimizers state.
-Outside the  support the gradient can be zero.
-            With MDNs, model parameters are neural network outputs.
-Unlike for conventional models where an informed initial parameter state may be chosen by hand, it is impractical and undesirable to initialize by hand a neural network's output by setting all its internal weights.
-One might imagine accomplishing a desired initial output by pre-training the network with a toy model that forces convergence on a set output vector.
-However,
-            neural networks are highly non-linear in their response to internal state changes (a desirable property).
-It is quite possible that when switching from the toy to real model's loss function the pre-trained network is in
-            a local probability island from which the global optimum is unreachable.  
-            Therefore, with the MDN neural networks, initialization is mostly for checking the dependence of the results on the initial state -- though even this dependence may instead be done using parameter dropout.
-Rather than
-            focusing on initializing to a particular parameter vector, for neural networks it is instead important that the initial state, whatever it is, has non-zero probability (or non-zero gradient, depending on the optimizer).
-            Neural networks have some intrinsic phase-space range that depends on the architecture of the network.
-Therefore the network architecture must be chosen such that the outputs match well with the priors.
-For example, with a
-            uniform prior $\theta \sim \mcal{U}(a,b)$, the network should be restricted such that $\theta \in (a, b]$, e.g. by ending the network's $\theta$ channel with a scaled logistic function.
+            The choice of prior is important, not only for the information it
+            adds to the model, but also for how optimizers explore the parameter
+            space. Simple optimizers, like MCMC \TODO{[cite]}, propose a
+            parameter vector then compute its likelihood given the data. Priors
+            with compact support  $\theta \sim \mcal{D}((a, b])$, e.g.
+            $\mcal{U}(a, b)$, may be very dangerous as the optimizer can be
+            initialized in a region with zero probability and has no means but
+            blind luck to find the region of support -- the region with non-zero
+            likelihood. More sophisticated optimizers, like gradient-based
+            descent \TODO{[cite]}, are susceptible to a similar initialization
+            problem, allowing zero-probability regions, but requiring at least a
+            non-zero gradient to make informed updates to the optimizers state.
+            Outside the  support the gradient can be zero.  With MDNs, model
+            parameters are neural network outputs. Unlike for conventional
+            models where an informed initial parameter state may be chosen by
+            hand, it is impractical and undesirable to initialize by hand a
+            neural network's output by setting all its internal weights. One
+            might imagine accomplishing a desired initial output by pre-training
+            the network with a toy model that forces convergence on a set output
+            vector. However, neural networks are highly non-linear in their
+            response to internal state changes (a desirable property). It is
+            quite possible that when switching from the toy to real model's loss
+            function the pre-trained network is in a local probability island
+            from which the global optimum is unreachable.  
+            Therefore, with the MDN neural networks, initialization is mostly
+            for checking the dependence of the results on the initial state --
+            though even this dependence may instead be done using parameter
+            dropout. Rather than focusing on initializing to a particular
+            parameter vector, for neural networks it is instead important that
+            the initial state, whatever it is, has non-zero probability (or
+            non-zero gradient, depending on the optimizer).  Neural networks
+            have some intrinsic phase-space range that depends on the
+            architecture of the network. Therefore the network architecture must
+            be chosen such that the outputs match well with the priors. For
+            example, with a uniform prior $\theta \sim \mcal{U}(a,b)$, the
+            network should be restricted such that $\theta \in (a, b]$, e.g. by
+            ending the network's $\theta$ channel with a scaled logistic
+            function.
             \begin{equation}\label{eq:scaled_logistic}
@@
             \end{equation}
-            Therefore, we pair every parameter bound with a matching bound in the network architecture.
+            Therefore, we pair every parameter bound with a matching bound in
+            the network architecture.
 
             % ⬇ where should this sentence be?
-            The parameter bounds may be independent of $\phi_1$, as is implicit to the above discussion, or conditionally dependent and vary as any user-defined function of $\phi_1$.
-            Alternatively, priors parameter may be separated into pieces, dealing with different modeling needs, e.g. defining broad parameter bounds as was done in this section.
+            The parameter bounds may be independent of $\phi_1$, as is implicit
+            to the above discussion, or conditionally dependent and vary as any
+            user-defined function of $\phi_1$.  Alternatively, priors parameter
+            may be separated into pieces, dealing with different modeling needs,
+            e.g. defining broad parameter bounds as was done in this section.
             We introduce a different piece subsequently.
@@
 
-        \subsubsection{Region Prior} \label{sub:track_region_prior}
-
-            In \autoref{ssub:astrometric_model_on_stream} the stream model's parameters were unconstrained.
-Bounds on the parameters and the neural network architecture were introduced in \autoref{ssub:parameter_bounds} to ensure the initial state of the model and network were compatible with the optimizer.
-Now we provide known information about physical systems, particular the track of the stream.
-            Our density modeling is aimed at characterization of \textit{known} streams, not stream discovery. From previous studies, the broad track of a
-            stream is known for significant portions of its length \citep[e.g.
-see the atlas in][]{Mateu2022}.
-It makes sense, then, to provide this information to the model.
-Care must be taken that this prior information does not dominate the model.
-            % A good balance between these two goals is to have a prior that only influences the track on large scales.
-            We introduce a region prior to encourage the stream model to pass through a user-defined control region, while also remaining compatible with the data.
-            We refer to the prior as a ``split"-Normal prior: a Gaussian split and separated at the peak and pieced back together with a flat region connecting the halves.
+        \subsubsection{Region Prior} \label{sub:methods:priors:track_region_prior}
+
+            In \autoref{ssub:method:astrometric_model:on_stream} the stream
+            model's parameters were unconstrained. Bounds on the parameters and
+            the neural network architecture were introduced in
+            \autoref{ssub:methods:priors:parameter_bounds} to ensure the initial
+            state of the model and network were compatible with the optimizer.
+            Now we provide known information about physical systems, particular
+            the track of the stream.  Our density modeling is aimed at
+            characterization of \textit{known} streams, not stream discovery.
+            From previous studies, the broad track of a stream is known for
+            significant portions of its length \citep[e.g. see the atlas
+            in][]{Mateu2022}. It makes sense, then, to provide this information
+            to the model. Care must be taken that this prior information does
+            not dominate the model.
+            % A good balance between these two goals is to have a prior that
+            % only influences the track on large scales.
+            We introduce a region prior to encourage the stream model to pass
+            through a user-defined control region, while also remaining
+            compatible with the data.  We refer to the prior as a
+            ``split"-Normal prior: a Gaussian split and separated at the peak
+            and pieced back together with a flat region connecting the halves.
             The un-normalized PDF is given by:
@@
             \end{equation}\end{small}
-            The piecewise PDF is smooth up to the first derivative and can be used with gradient-based optimizers.
-
-            The Gaussian portions of the prior encourage the network towards the central region $\mu - w < x < \mu + w$.
-Since the prior is equi-probable in the region, the stream may lie anywhere as preferred by the data and the stream model.
-            It is convenient to reparametrize, with $\tau = \frac{1}{\sigma}$. Namely,
+            The piecewise PDF is smooth up to the first derivative and can be
+            used with gradient-based optimizers.
+
+            The Gaussian portions of the prior encourage the network towards the
+            central region $\mu - w < x < \mu + w$. Since the prior is
+            equi-probable in the region, the stream may lie anywhere as
+            preferred by the data and the stream model.  It is convenient to
+            reparametrize, with $\tau = \frac{1}{\sigma}$. Namely,
             \begin{small}
@@
             where the additive normalization is
-            $-\ln\left(\sqrt{\frac{\pi}{\tau}} \left(\frac{1}{2}\text{erf}\left(2 \sqrt{\tau } w\right)+1\right)\right)$.
-In this form we see that $\tau$ may be increased to strengthen the prior and encourage $\theta$ to lie within
-            the desired region.
-It is important that the region be set large enough that we may be confident the prior is not driving the final result on small scales.
-As an added measure, it is often useful to turn off this prior after the stream lies within the desired regions.
+            $-\ln\left(\sqrt{\frac{\pi}{\tau}}
+            \left(\frac{1}{2}\text{erf}\left(2 \sqrt{\tau }
+            w\right)+1\right)\right)$. In this form we see that $\tau$ may be
+            increased to strengthen the prior and encourage $\theta$ to lie
+            within the desired region. It is important that the region be set
+            large enough that we may be confident the prior is not driving the
+            final result on small scales. As an added measure, it is often
+            useful to turn off this prior after the stream lies within the
+            desired regions.
 
@@
     \vspace{5pt}
-    \subsection{Model Implementation, aka the code} \label{sub:model_implementation}
-
-        In prior sections we discussed the mathematical implementation of each component of the Mixture Density Network.
-Here we make brief remarks on the code implementation and architecture of the neural networks.
+    \subsection{Model Implementation, aka the code} \label{sub:methods:model_implementation}
+
+        In prior sections we discussed the mathematical implementation of each
+        component of the Mixture Density Network. Here we make brief remarks on
+        the code implementation and architecture of the neural networks.
         % Rephrase: I don't like this topic sentence.
 
-        The neural networks are built with the \package{PyTorch} stack \TODO{[cite]}.
-We wrap the network \texttt{pytorch.Module} in a custom framework, allowing the Bayesian likelihood, prior, evidence, etc.
-to be bundled with the network's forward step.
-This framework allows for a high degree of modularity.
-Component models, e.g.
-the stream model, of the mixture are easily added to (and moved from) as items in the larger mixture model.
-Probability methods understand how to traverse the mixture model, calling and combining the appropriate methods of the constituent models, so it unnecessary to write custom loss functions.
-        Another benefit of the modular framework is the ease of building and experimenting with different mixture models.
-Furthermore, each model component may be saved and serialized separately from the other components, allowing for
-        portability of the components between models.
-For example, if a stream has a prominent extra-tidal feature, e.g.
-the spur of \stream{GD-1}, a fiducial model of just the thin stream may be trained, then the stream (and background) model components may be saved and used as the initialization to the stream (and background) of a more complete model that includes the spur.
-This modularity also has a cost: by allowing each model component (including the categorical mixture model itself) to contain its own network we decrease the cross-talk between nodes in separated networks.
-The networks communicate only through the backwards propagation of the loss function, increasing the required training time of the models.
-We note that the code framework, being built on \package{PyTorch}, easily permits a single model with single network.
-Having found a good model by experimenting with the modular layout, the model may be reproduced and re-trained as a single network.
-Alternatively, though we leave this to a future version of the code, it is possible to ``fuse" the mixture, providing one network whose outputs are apportioned appropriately to each constituent model.
-
-        The models permit user-defined priors to be passed at model instantiation.
-        Priors specific to a single model are contained on that model, while priors connecting two (or more) models are held on the mixture model object.
-As an example of the latter, see \autoref{ssub:linking_to_astrometrics}, which connects the distance component of the astrometric and photometric stream models.
-
-        The custom model framework combines for each model a neural network with Bayesian probability functions.
-The latter are set by the model type, e.g.
-the Gaussian model has a Gaussian likelihood function, but the former, the neural network, is set and determined by the user.
-So long as the network has the correct number of inputs (e.g.
-one for $\phi_1$) and outputs (one per parameter), any feed-forward network may be used.
-Our default choice, and for which we provide a helper function, is an MLP with a sequence of \texttt{Linear} \!\!\textrightarrow \texttt{Tanh} \!\!\textrightarrow \texttt{Dropout} blocks.
-This is illustrated in \autoref{table:mlp_structure}.
+        The neural networks are built with the \package{PyTorch} stack
+        \TODO{[cite]}. We wrap the network \texttt{pytorch.Module} in a custom
+        framework, allowing the Bayesian likelihood, prior, evidence, etc. to be
+        bundled with the network's forward step. This framework allows for a
+        high degree of modularity. Component models, e.g. the stream model, of
+        the mixture are easily added to (and moved from) as items in the larger
+        mixture model. Probability methods understand how to traverse the
+        mixture model, calling and combining the appropriate methods of the
+        constituent models, so it unnecessary to write custom loss functions.
+        Another benefit of the modular framework is the ease of building and
+        experimenting with different mixture models. Furthermore, each model
+        component may be saved and serialized separately from the other
+        components, allowing for portability of the components between models.
+        For example, if a stream has a prominent extra-tidal feature, e.g. the
+        spur of \stream{GD-1}, a fiducial model of just the thin stream may be
+        trained, then the stream (and background) model components may be saved
+        and used as the initialization to the stream (and background) of a more
+        complete model that includes the spur. This modularity also has a cost:
+        by allowing each model component (including the categorical mixture
+        model itself) to contain its own network we decrease the cross-talk
+        between nodes in separated networks. The networks communicate only
+        through the backwards propagation of the loss function, increasing the
+        required training time of the models. We note that the code framework,
+        being built on \package{PyTorch}, easily permits a single model with
+        single network. Having found a good model by experimenting with the
+        modular layout, the model may be reproduced and re-trained as a single
+        network. Alternatively, though we leave this to a future version of the
+        code, it is possible to ``fuse" the mixture, providing one network whose
+        outputs are apportioned appropriately to each constituent model.
+
+        The models permit user-defined priors to be passed at model
+        instantiation.  Priors specific to a single model are contained on that
+        model, while priors connecting two (or more) models are held on the
+        mixture model object. As an example of the latter, see
+        \autoref{ssub:method:linking_to_astrometrics}, which connects the
+        distance component of the astrometric and photometric stream models.
+
+        The custom model framework combines for each model a neural network with
+        Bayesian probability functions. The latter are set by the model type,
+        e.g. the Gaussian model has a Gaussian likelihood function, but the
+        former, the neural network, is set and determined by the user. So long
+        as the network has the correct number of inputs (e.g. one for $\phi_1$)
+        and outputs (one per parameter), any feed-forward network may be used.
+        Our default choice, and for which we provide a helper function, is an
+        MLP with a sequence of \texttt{Linear} \!\!\textrightarrow \texttt{Tanh}
+        \!\!\textrightarrow \texttt{Dropout} blocks. This is illustrated in
+        \autoref{table:mlp_structure}.
         % FIXME! reference not being picked up correctly.
-        Dropout layers are used to prevent network co-adaptation and over-fitting.
-Dropout works by randomly zeroing out nodes in the network, decreasing the importance of any single node, encouraging instead emergent patterns across the network.
-        One model for which the lin-tanh-dropout network cannot be used is the normalizing flow
-        used in the photometric background model (\autoref{sub:photometric_model_off_stream}).
-Here we use the \package{nflows} package, with a conditional diagonal normal base distribution and composite transform network of a reverse permutation and masked affine auto-regressive transform layers.
-As noted in our data availability statement, all the codes used in this paper are bundled by \href{https://github.com/showyourwork/showyourwork}{\package{showyourwork}} in a public repository at $\GitHubURL{}$.
-We will describe for each stream model specifics relevant to that stream but refer readers to the publicly-available code itself for code implementation details.
+        Dropout layers are used to prevent network co-adaptation and
+        over-fitting. Dropout works by randomly zeroing out nodes in the
+        network, decreasing the importance of any single node, encouraging
+        instead emergent patterns across the network.  One model for which the
+        lin-tanh-dropout network cannot be used is the normalizing flow used in
+        the photometric background model
+        (\autoref{sub:method:photometric_model:off_stream}). Here we use the
+        \package{nflows} package, with a conditional diagonal normal base
+        distribution and composite transform network of a reverse permutation
+        and masked affine auto-regressive transform layers. As noted in our data
+        availability statement, all the codes used in this paper are bundled by
+        \href{https://github.com/showyourwork/showyourwork}{\package{showyourwork}}
+        in a public repository at $\GitHubURL{}$. We will describe for each
+        stream model specifics relevant to that stream but refer readers to the
+        publicly-available code itself for code implementation details.
         % TODO: Maybe more details in the Appendix?
@@
             \centering
-            \caption{
-            Example neural network structure consisting of 1 input block mapping a $\phi_1$ scalar to the $H$ nodes of the hidden blocks, the number of which determines the depth of the network.
-The hidden blocks map to the $F$ outputs in the output block.
-Each block consists of a \texttt{Linear} \!\!\textrightarrow \texttt{Tanh} \!\!\textrightarrow \texttt{Dropout} sequence.
-Vector $\phi_1$ inputs are supported as an element-wise application of the network.
+            \caption{% 
+            Example neural network structure consisting of 1 input block mapping
+            a $\phi_1$ scalar to the $H$ nodes of the hidden blocks, the number
+            of which determines the depth of the network. The hidden blocks map
+            to the $F$ outputs in the output block. Each block consists of a
+            \texttt{Linear} \!\!\textrightarrow \texttt{Tanh}
+            \!\!\textrightarrow \texttt{Dropout} sequence. Vector $\phi_1$
+            inputs are supported as an element-wise application of the network.
             }
@@
 
-    In this section we present an application of our model to a synthetic stream with known ground truths, and demonstrate the model's ability to characterize stream density variations and membership probabilities in an unsupervised manner.
-
-    % \subsection{Test on a Synthetic Stream} \label{sub:mock_data}
-
-    In this section we apply our model to a synethic stream in order to demonstrate an accurate recovery of stream members and density variations.
-
-    We generate synthetic observations by sampling points from a third degree polynomial \JN{check this} with a constant scatter.
-Density variations are then simulated by evaluating the stream density with two Gaussian distributions centered at different values of $\phi_1$ with random amplitudes (which sum to $1$) and widths.
-Stream stars are then removed using random sampling, weighted by their likelihood of belonging to the density.
-The background astrometric  points in are generated from exponential distributions at each $\phi_1$.
-The number of stream stars is $\variable{output/mock/nstream_variable.txt}$, while the number of background stars is $\variable{output/mock/nbackground_variable.txt}$.
+    In this section we present an application of our model to a synthetic stream
+    with known ground truths, and demonstrate the model's ability to
+    characterize stream density variations and membership probabilities in an
+    unsupervised manner.
+
+    In this section we apply our model to a synethic stream in order to
+    demonstrate an accurate recovery of stream members and density variations.
+
+    We generate synthetic observations by sampling points from a third degree
+    polynomial \JN{check this} with a constant scatter. Density variations are
+    then simulated by evaluating the stream density with two Gaussian
+    distributions centered at different values of $\phi_1$ with random
+    amplitudes (which sum to $1$) and widths. Stream stars are then removed
+    using random sampling, weighted by their likelihood of belonging to the
+    density. The background astrometric  points in are generated from
+    exponential distributions at each $\phi_1$. The number of stream stars is
+    $\variable{output/mock/nstream_variable.txt}$, while the number of
+    background stars is $\variable{output/mock/nbackground_variable.txt}$.
 
@@
             % 
-            \textbf{Top panel:} Astrometric coordinates ($\phi_1$, $\phi_2$) for the mock data set.
-            Light blue points are the stream and background within an ``on"-stream region. Black points are in the ``off"-stream region used to train the background photometric model.
+            \textbf{Top panel:} Astrometric coordinates ($\phi_1$, $\phi_2$) for
+            the mock data set.  Light blue points are the stream and background
+            within an ``on"-stream region. Black points are in the ``off"-stream
+            region used to train the background photometric model.
             % 
-            \textbf{Bottom panel:} Astrometric coordinates ($\phi_1$, $\phi_2$) for the mock data set.
-            Black points are in the ``off"-stream region from the region defined in the astrometric coordinates.
-            Light blue points are the stream and background from the on-stream region. The stream's isochrone is apparent as an overdensity around (g-r, g)$\approx (0, 20)$.
-        }
+            \textbf{Bottom panel:} Astrometric coordinates ($\phi_1$, $\phi_2$)
+            for the mock data set.  Black points are in the ``off"-stream region
+            from the region defined in the astrometric coordinates.  Light blue
+            points are the stream and background from the on-stream region. The
+            stream's isochrone is apparent as an overdensity around (g-r,
+            g)$\approx (0, 20)$.  }
         \label{fig:mock_data_photometric_background_selection}
@@
 
-    The synthetic stream is also simulated in magnitudes using a 12~Gyr isochrone with [Fe/H] = -1.35~dex.
-The isochrone truncates just short of the giant branch, and sampled from uniformly (i.e., the initial mass function, $P(\gamma)$, is uniform).
-The background photometric coordinates are generated as a 2-dimensional Gaussian with non-zero covariance.
-The distance modulus is derived from a polynomial parallax track with uniform thickness.
-Thus, the synthetic data scenario described here generates a mock stream in astrometric coordinates and photometric coordinates, with density variations, a distance gradient which is consistent in parallax and distance modulus (i.e., magnitudes), all superimposed over a noisy field of background points in each astrometric and photometric dimension.
+    The synthetic stream is also simulated in magnitudes using a 12~Gyr
+    isochrone with [Fe/H] = -1.35~dex. The isochrone truncates just short of the
+    giant branch, and sampled from uniformly (i.e., the initial mass function,
+    $P(\gamma)$, is uniform). The background photometric coordinates are
+    generated as a 2-dimensional Gaussian with non-zero covariance. The distance
+    modulus is derived from a polynomial parallax track with uniform thickness.
+    Thus, the synthetic data scenario described here generates a mock stream in
+    astrometric coordinates and photometric coordinates, with density
+    variations, a distance gradient which is consistent in parallax and distance
+    modulus (i.e., magnitudes), all superimposed over a noisy field of
+    background points in each astrometric and photometric dimension.
 
@@
             \textbf{Top panel:}%
-                The stream mixture coefficient $f(\phi_1)$ (black dotted line) predicted by the model, overplotted on the true stream fraction (black-outlined histogram),
-                calculated as the ratio of stream stars to total stars in 55 bins
-                over the $\phi_1$ range of the isochrone.
-            \textbf{Middle panel: }%
-                $\phi_2(\phi_1)$ over the full range of $\phi_1$.
-The data color and transparency is set by the model's MLE stream probability (with dropout turned off).
-Plotted behind the data are the true labels for the stream stars (large black circles).
-                The true labels exactly limn the model-identified stream stars.
-                The MLE stream track (black dashed line) is over-plotted on the probability-colored data.
+                The stream mixture coefficient $f(\phi_1)$ (black dotted line)
+                predicted by the model, overplotted on the true stream fraction
+                (black-outlined histogram), calculated as the ratio of stream
+                stars to total stars in 55 bins over the $\phi_1$ range of the
+                isochrone.  \textbf{Middle panel: }%
+                $\phi_2(\phi_1)$ over the full range of $\phi_1$. The data color
+                and transparency is set by the model's MLE stream probability
+                (with dropout turned off). Plotted behind the data are the true
+                labels for the stream stars (large black circles).  The true
+                labels exactly limn the model-identified stream stars.  The MLE
+                stream track (black dashed line) is over-plotted on the
+                probability-colored data.
             %
             \textbf{Lower panel 3: }%
-                $\varpi_2(\phi_1)$ over the full range of $\phi_1$.
-Like for $\phi_2$, the data color and transparency is set by the MLE probability, with the true labels (large black circles) under-plotted and MLE track (black dashed line) over-plotted.
+                $\varpi_2(\phi_1)$ over the full range of $\phi_1$. Like for
+                $\phi_2$, the data color and transparency is set by the MLE
+                probability, with the true labels (large black circles)
+                under-plotted and MLE track (black dashed line) over-plotted.
             %
             \textbf{Upper Histograms: }%
-                $\phi_2$ histograms for each model component (blue background, red stream), in 4 $\phi_1$ ranges across the data set.
-                The height of each bin is the probability-weighted density.
-                The background is a uniform distribution, while the stream is a Gaussian.
-In projection across the $\phi_1$ range it can appear multi-modal (panel 2) if there are large gaps or `smeared' out if the Gaussian's mean changes significantly over the range.
+                $\phi_2$ histograms for each model component (blue background,
+                red stream), in 4 $\phi_1$ ranges across the data set.  The
+                height of each bin is the probability-weighted density.  The
+                background is a uniform distribution, while the stream is a
+                Gaussian. In projection across the $\phi_1$ range it can appear
+                multi-modal (panel 2) if there are large gaps or `smeared' out
+                if the Gaussian's mean changes significantly over the range.
             %
             \textbf{Upper Middle Histograms: }%
-                Parallax $\varpi$ histograms for each model component (blue background, red stream), in 4 $\phi_1$ ranges across the data set.
-                The height of each bin is the probability-weighted density.
+                Parallax $\varpi$ histograms for each model component (blue
+                background, red stream), in 4 $\phi_1$ ranges across the data
+                set.  The height of each bin is the probability-weighted
+                density.
             %
             \textbf{Lower Middle and Lower Histograms:}%
-                Photometric coordinate $(g, r)$ plots for each model component in 4 $\phi_1$ ranges across the data set.
-The top row plots the stream stars (red) over the background.
-The lower row plots the background stars (blue) over the stream stars to show that the
-                how the two distributions mix.
-        }
-        TODO:
+                Photometric coordinate $(g, r)$ plots for each model component
+                in 4 $\phi_1$ ranges across the data set. The top row plots the
+                stream stars (red) over the background. The lower row plots the
+                background stars (blue) over the stream stars to show that the
+                how the two distributions mix.  } TODO:
         \begin{enumerate}
@@
 
-    The result of applying our density model to the synthetic data is illustrated in \autoref{fig:mock_data_result}.
-The top panel shows the weight parameter that controls membership probability as a function of $\phi_1$.
-The dashed curve represents the output of our data-driven model, while the solid curve is the ground truth.
-The second panel shows the stream and background in the $(\phi_1,\phi_2)$ plane, and the third panel shows the stream and background in the $(\phi_1,\parallax)$ plane.
-Points are color-coded according to their membership probability \autoref{eq:membership_prob}.
-The weight parameter clearly shows that the model has captured the two prominent density variations along the stream.
-The are additional variations  mostly around the edges of the stream, though re-sampling the neural network weights with dropout reveals that these variations represent regions of higher model uncertainty.
-
-    We find that the stream is successfully recovered in both astrometric and photometric coordinates, with $x\%$ stream stars being recovered with membership probability greater than $y$.
-The false positive rate (i.e., stars misidentified as stream members) for this test is found to be $z\%$ when cutting on this threshold.
-
-    In the bottom two rows of \autoref{fig:mock_data_result} we illustrate the synthetic data color-coded by stream membership probability (top) and background membership probability (background) for different $\phi_1$ slices.
-Importantly, the photometric portion of the mixture model successfully identifies the stream in magnitude space, showing a high stream membership probability where the stream is present, and a low probability ($\sim 0$) where the stream is absent.
+    The result of applying our density model to the synthetic data is
+    illustrated in \autoref{fig:mock_data_result}. The top panel shows the
+    weight parameter that controls membership probability as a function of
+    $\phi_1$. The dashed curve represents the output of our data-driven model,
+    while the solid curve is the ground truth. The second panel shows the stream
+    and background in the $(\phi_1,\phi_2)$ plane, and the third panel shows the
+    stream and background in the $(\phi_1,\parallax)$ plane. Points are
+    color-coded according to their membership probability
+    \autoref{eq:membership_prob}. The weight parameter clearly shows that the
+    model has captured the two prominent density variations along the stream.
+    The are additional variations  mostly around the edges of the stream, though
+    re-sampling the neural network weights with dropout reveals that these
+    variations represent regions of higher model uncertainty.
+
+    We find that the stream is successfully recovered in both astrometric and
+    photometric coordinates, with $x\%$ stream stars being recovered with
+    membership probability greater than $y$. The false positive rate (i.e.,
+    stars misidentified as stream members) for this test is found to be $z\%$
+    when cutting on this threshold.
+
+    In the bottom two rows of \autoref{fig:mock_data_result} we illustrate the
+    synthetic data color-coded by stream membership probability (top) and
+    background membership probability (background) for different $\phi_1$
+    slices. Importantly, the photometric portion of the mixture model
+    successfully identifies the stream in magnitude space, showing a high stream
+    membership probability where the stream is present, and a low probability
+    ($\sim 0$) where the stream is absent.
 
@@
 
-    We now apply our density modeling approach to the stellar stream GD-1. We discuss the data selection in \autoref{sub:results_gd1_data} and results in \autoref{ssub:trained_gd1}.
+    We now apply our density modeling approach to the stellar stream GD-1. We
+    discuss the data selection in \autoref{sub:results_gd1_data} and results in
+    \autoref{ssub:trained_gd1}.
 
@@
 
-        We utilize data from {\it Gaia} DR3 for the astrometric coordinates of each star, and Pan-STARRS1 to obtain more accurate color information.
-We adopt broad cuts on the cross-matched data to limit the field to a region known to contain GD-1.
-We perform these rough cuts by requiring \JN{fill in what the cuts are and reference proper motion figure and CMD figure.}
-
-        The result is a field populated by \JN{x} stars, from which we would like to identify stream members.
+        We utilize data from {\it Gaia} DR3 for the astrometric coordinates of
+        each star, and Pan-STARRS1 to obtain more accurate color information. We
+        adopt broad cuts on the cross-matched data to limit the field to a
+        region known to contain GD-1. We perform these rough cuts by requiring
+        \JN{fill in what the cuts are and reference proper motion figure and CMD
+        figure.}
+
+        The result is a field populated by \JN{x} stars, from which we would
+        like to identify stream members.
 
@@
 
-        We model GD-1 as a three-component mixture consisting of a main stream component, a spur, and background.
-In order to guide our model towards GD-1, we set down 4 ``control points" along GD-1's main track, and 3 control points along the spur (illustrated in \JN{x}).
-These control points act as Gaussian priors on the model.
-We set the Gaussian error on these control points to large values, so that their influence on the model is not dominant.
-Indeed, we find that the value of the control points is to help reduce training time, since otherwise it will take the flexible density model longer time to converge to the actual stream.
+        We model GD-1 as a three-component mixture consisting of a main stream
+        component, a spur, and background. In order to guide our model towards
+        GD-1, we set down 4 ``control points" along GD-1's main track, and 3
+        control points along the spur (illustrated in \JN{x}). These control
+        points act as Gaussian priors on the model. We set the Gaussian error on
+        these control points to large values, so that their influence on the
+        model is not dominant. Indeed, we find that the value of the control
+        points is to help reduce training time, since otherwise it will take the
+        flexible density model longer time to converge to the actual stream.
 
@@
 
-        In this section we present results from our model applied to real {\it Gaia} and Pan-STARRS data of GD-1.
-
-        We visualize the performance of our model in identifying stream stars and characterizing the astrometric background with \autoref{fig:gd1-results-full} and \autoref{fig:gd1-results-panels}.
-In \autoref{fig:gd1-results-full} The top panel shows the stream in $\phi_1$, $\phi_2$ coordinates, color-coded by membership probability (derived from \autoref{eq:membership_prob}).
-The following three rows represent background distributions in $\phi_2, \mu_{\phi_1}, \rm{\ and} \ \mu_{\rm phi_2}$, respectively taken at different $\phi_1$ increments centered on the red lines.
-The $\phi_1$ increments are roughly $\sim X$ in size.
-
-        The blue lines over-plotted represent the best fit model at the given $\phi_1$ slice.
-We find that the backgrounds are typically well characterized by the distributions adopted (described in \S-x).
-We can also see from \autoref{fig:gd1-results-panels}
-        that the stream and spur components appear to be well characterized.
-
-        Our ability to recover the stream is demonstrated further in \autoref{fig:gd1-results-full}.
-In this figure, we only plot stars if their membership probability is greater than \JN{X}.
-The result is a ``gold" catalog of probable stream and spur members, extending over $X$-degrees in $\phi_1$.
-We find the expected gap around $\phi_1 \sim -20~\rm{deg}$, which has been proposed to be the location of the dissolved progenitor (CITE).
-
-        Our model also fits the distribution of stream stars in the CMD.
-These fits are illustrated in \autoref{fig:gd1-results-panels}, where the CMD for the population in a given $\phi_1$ band is plotted, color-coded by stream membership probability.
-For the on-stream regions, the isochrone appears to provide a decent description of the stream, though there is room for further improvements (discussed in \S-x).
-However, we note that the stream's presence and absence in the isochrone is well captured by the mixture weight, which is a neural network output.
-
-        Additionally, the distance modulus is also a neural network output, conditioned on $\phi_1$.
-This allows us to obtain a distance modulus at each $\phi_1$ along the stream.
-The distance modulus track and (converted) distance track are illustrated in \autoref{fig:gd1-results-full}.
-The left panel shows the distance modulus (in magnitudes), while the right shows the corresponding distance track.
-Importantly, the prior on the distance track is that the stream must fall between $[4,40]~\rm{kpc}$.
-Thus, our ability to recover the distance to GD-1 without substantial bias provides a useful indicator that our color-magnitude model combined with the astrometric model provide an adequate description of the data.
-\JN{more on this...}
+        In this section we present results from our model applied to real {\it
+        Gaia} and Pan-STARRS data of GD-1.
+
+        We visualize the performance of our model in identifying stream stars
+        and characterizing the astrometric background with
+        \autoref{fig:gd1-results-full} and \autoref{fig:gd1-results-panels}. In
+        \autoref{fig:gd1-results-full} The top panel shows the stream in
+        $\phi_1$, $\phi_2$ coordinates, color-coded by membership probability
+        (derived from \autoref{eq:membership_prob}). The following three rows
+        represent background distributions in $\phi_2, \mu_{\phi_1}, \rm{\ and}
+        \ \mu_{\rm phi_2}$, respectively taken at different $\phi_1$ increments
+        centered on the red lines. The $\phi_1$ increments are roughly $\sim X$
+        in size.
+
+        The blue lines over-plotted represent the best fit model at the given
+        $\phi_1$ slice. We find that the backgrounds are typically well
+        characterized by the distributions adopted (described in \S-x). We can
+        also see from \autoref{fig:gd1-results-panels} that the stream and spur
+        components appear to be well characterized.
+
+        Our ability to recover the stream is demonstrated further in
+        \autoref{fig:gd1-results-full}. In this figure, we only plot stars if
+        their membership probability is greater than \JN{X}. The result is a
+        ``gold" catalog of probable stream and spur members, extending over
+        $X$-degrees in $\phi_1$. We find the expected gap around $\phi_1 \sim
+        -20~\rm{deg}$, which has been proposed to be the location of the
+        dissolved progenitor (CITE).
+
+        Our model also fits the distribution of stream stars in the CMD. These
+        fits are illustrated in \autoref{fig:gd1-results-panels}, where the CMD
+        for the population in a given $\phi_1$ band is plotted, color-coded by
+        stream membership probability. For the on-stream regions, the isochrone
+        appears to provide a decent description of the stream, though there is
+        room for further improvements (discussed in \S-x). However, we note that
+        the stream's presence and absence in the isochrone is well captured by
+        the mixture weight, which is a neural network output.
+
+        Additionally, the distance modulus is also a neural network output,
+        conditioned on $\phi_1$. This allows us to obtain a distance modulus at
+        each $\phi_1$ along the stream. The distance modulus track and
+        (converted) distance track are illustrated in
+        \autoref{fig:gd1-results-full}. The left panel shows the distance
+        modulus (in magnitudes), while the right shows the corresponding
+        distance track. Importantly, the prior on the distance track is that the
+        stream must fall between $[4,40]~\rm{kpc}$. Thus, our ability to recover
+        the distance to GD-1 without substantial bias provides a useful
+        indicator that our color-magnitude model combined with the astrometric
+        model provide an adequate description of the data. \JN{more on this...}
 
@@
 
-    In this work we use multiple data sets and a variety of mathematical tools to analyze the data, including machine learning algorithms and statistical models.
-    For clarity and to connect related components of the models used in this work, a consistent mathematical notation is crucial. Here we establish the notation and symbols used throughout this work.
-    \autoref{table:symbol_table} enumerates the symbols used for the statistical models and the different datasets, e.g. distinguishing astrometric from photometric data.
+    In this work we use multiple data sets and a variety of mathematical tools
+    to analyze the data, including machine learning algorithms and statistical
+    models.  For clarity and to connect related components of the models used in
+    this work, a consistent mathematical notation is crucial. Here we establish
+    the notation and symbols used throughout this work.
+    \autoref{table:symbol_table} enumerates the symbols used for the statistical
+    models and the different datasets, e.g. distinguishing astrometric from
+    photometric data.
 
@@
 
-        In practice, the bounds $a,b$ are the bounds of the observation window, creating a subset of a larger field.
-        Suppose the larger field is uniformly distributed in a region larger than the bounds $a, b$, ie. $P_{\mcal{U}}(x|\alpha,\beta)$.
-        Let each observed datum $x_n$ in the field have Gaussian error $\sigobs_n$,
-        then the PDF of the uniform-Gaussian-convolved distribution is given by:
+        In practice, the bounds $a,b$ are the bounds of the observation window,
+        creating a subset of a larger field.  Suppose the larger field is
+        uniformly distributed in a region larger than the bounds $a, b$, ie.
+        $P_{\mcal{U}}(x|\alpha,\beta)$.  Let each observed datum $x_n$ in the
+        field have Gaussian error $\sigobs_n$, then the PDF of the
+        uniform-Gaussian-convolved distribution is given by:
 
@@
 
-        The properties of the Normal distribution are well known. For completeness we state
+        The properties of the Normal distribution are well known. For
+        completeness we state
 
@@
 
-        The Normal distribution is not compact, with non-zero value over all $x$. In an observational window $(a,b]$ the PDF is truncated, giving
+        The Normal distribution is not compact, with non-zero value over all
+        $x$. In an observational window $(a,b]$ the PDF is truncated, giving
 
@@
 
-        Despite the popularity of this distribution we are not aware of any work showing the convolution of the skew-normal distribution with a centered Gaussian.
-Moreover, our Mathematica (v13.2) does not successfully perform this convolution.
-Consequently we present a step-by-step derivation of $P_{X\cdot\mcal{N}}$.
-
-        \autoref{eq:general_convolution} establishes that convolutions of PDFs are an integral operation.
-Integrals are often intractable, but the problem is solvable if recast in different terms.
-Rather that working with PDFs of distributions we can instead consider the moment-generating function (MGF) corresponding to the PDF's distribution.
-Like the PDF, the MGF uniquely determines a distribution, so a MFG uniquely maps to a PDF.
-For the MGF of two distributions the convolutions is a multiplication, not an integral.
-        Therefore, for the convolution of two PDFs their MGFs are multiplied and if the product is the MGF of a known distribution, the corresponding PDF is the convolution of the two original PDFs.
+        Despite the popularity of this distribution we are not aware of any work
+        showing the convolution of the skew-normal distribution with a centered
+        Gaussian. Moreover, our Mathematica (v13.2) does not successfully
+        perform this convolution. Consequently we present a step-by-step
+        derivation of $P_{X\cdot\mcal{N}}$.
+
+        \autoref{eq:general_convolution} establishes that convolutions of PDFs
+        are an integral operation. Integrals are often intractable, but the
+        problem is solvable if recast in different terms. Rather that working
+        with PDFs of distributions we can instead consider the moment-generating
+        function (MGF) corresponding to the PDF's distribution. Like the PDF,
+        the MGF uniquely determines a distribution, so a MFG uniquely maps to a
+        PDF. For the MGF of two distributions the convolutions is a
+        multiplication, not an integral.  Therefore, for the convolution of two
+        PDFs their MGFs are multiplied and if the product is the MGF of a known
+        distribution, the corresponding PDF is the convolution of the two
+        original PDFs.
 
@@
         \end{equation}
-        This has the same form as the skew-normal, only with $\sigma \rightarrow \tilde\sigma$ and $\delta \rightarrow \tilde\delta$.
+        This has the same form as the skew-normal, only with $\sigma \rightarrow
+        \tilde\sigma$ and $\delta \rightarrow \tilde\delta$.
 

### 2023-08-28 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-    In this section we apply our model to a synethic stream in order to
-    demonstrate an accurate recovery of stream members and density variations.
-
-    We generate synthetic observations by sampling points from a third degree
-    polynomial \JN{check this} with a constant scatter. Density variations are
-    then simulated by evaluating the stream density with two Gaussian
+    We generate synthetic stream observations by sampling uniformly in $\phi_1$
+    In $\phi_2$ we sample from a quadratic in $\phi_1$ with normally-distributed
+    $0.15\degree$ scatter.  The distances are sampled from a linear funciton in
+    $\phi_1$ with normally-distributed $0.25 \unit{kpc}$ scatter, then
+    transformed to the parallax $\parallax$.  Non-poissonian density variations
+    are then simulated by evaluating the stream density with two Gaussian
     distributions centered at different values of $\phi_1$ with random
@@
     using random sampling, weighted by their likelihood of belonging to the
-    density. The background astrometric  points in are generated from
-    exponential distributions at each $\phi_1$. The number of stream stars is
+    density. The background astrometric points in are generated from exponential
+    distributions at each $\phi_1$.  The number of stream stars is
     $\variable{output/mock/nstream_variable.txt}$, while the number of
     background stars is $\variable{output/mock/nbackground_variable.txt}$.
+
+    The synthetic stream's photometry is also simulated using a 12~Gyr, [Fe/H] =
+    -1.35~dex NMIST isochrone \TODO{[cite brutus]}. The isochrone truncates just
+    short of the giant branch, and is sampled from uniformly along the isochrone
+    (i.e., the initial mass function, $P(\gamma)$, is uniform) as well as with
+    an intrinsic uniform 0.2~dex scatter orthogonal to the isochrone track. The
+    isochrone is shifted by the stream's parallax modulus, which is derived from
+    the astrometric distance track.  The background photometric coordinates are
+    generated as a 2-dimensional Gaussian with non-zero covariance.  Thus, the
+    synthetic data scenario described here generates a mock stream in
+    astrometric coordinates and photometric coordinates, with density
+    variations, a distance gradient which is consistent in parallax and distance
+    modulus (i.e., magnitudes), all superimposed over a noisy field of
+    background points in each astrometric and photometric dimension.
 
@@
 
-    The synthetic stream is also simulated in magnitudes using a 12~Gyr
-    isochrone with [Fe/H] = -1.35~dex. The isochrone truncates just short of the
-    giant branch, and sampled from uniformly (i.e., the initial mass function,
-    $P(\gamma)$, is uniform). The background photometric coordinates are
-    generated as a 2-dimensional Gaussian with non-zero covariance. The distance
-    modulus is derived from a polynomial parallax track with uniform thickness.
-    Thus, the synthetic data scenario described here generates a mock stream in
-    astrometric coordinates and photometric coordinates, with density
-    variations, a distance gradient which is consistent in parallax and distance
-    modulus (i.e., magnitudes), all superimposed over a noisy field of
-    background points in each astrometric and photometric dimension.
+    We pre-train a normalizing flow (see
+    \autoref{sub:method:photometric_model:off_stream}) on an off-stream
+    selection.  We train on the photometry.  You can see the selection in
+    \auroref{fig:mock_data_photometric_background_selection}.  You can see both
+    the on-stream and off-stream labels, blue and black respectively.  We select
+    using an astrometric selection. In the photometry you can see that the
+    on-stream selection has two populations, drawn from the isochrone and drawn
+    from the background The off-stream selection, meanwhile, has only the
+    background population. Next we train the full model.
 
@@
 
-    A variety of probability distributions are used when modeling the stream and Galactic background. This appendix presents relevant mathematical details of these distributions.
-    In particular, observational errors are modeled as Gaussian distributions, which requires modifying each distribution to account for the Gaussian noise.
+    A variety of probability distributions are used when modeling the stream and
+    Galactic background. This appendix presents relevant mathematical details of
+    these distributions.  In particular, observational errors are modeled as
+    Gaussian distributions, which requires modifying each distribution to
+    account for the Gaussian noise.
 
@@
 
-        The simplest distribution is that of the univariate uniform distribution.
-        For a domain $x \in [a, b]$ the PDF is given by
+        The simplest distribution is that of the univariate uniform
+        distribution.  For a domain $x \in [a, b]$ the PDF is given by
         \begin{equation}\label{eq:pdf_flat_univariate}

### 2023-08-28 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     In $\phi_2$ we sample from a quadratic in $\phi_1$ with normally-distributed
-    $0.15\degree$ scatter.  The distances are sampled from a linear funciton in
+    $0.15^{\circ}$ scatter.  The distances are sampled from a linear funciton in
     $\phi_1$ with normally-distributed $0.25 \unit{kpc}$ scatter, then
@@
     selection.  We train on the photometry.  You can see the selection in
-    \auroref{fig:mock_data_photometric_background_selection}.  You can see both
+    \autoref{fig:mock_data_photometric_background_selection}.  You can see both
     the on-stream and off-stream labels, blue and black respectively.  We select

### 2023-08-29 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     $0.15^{\circ}$ scatter.  The distances are sampled from a linear funciton in
-    $\phi_1$ with normally-distributed $0.25 \unit{kpc}$ scatter, then
+    $\phi_1$ with normally-distributed $0.25 \ \unit{kpc}$ scatter, then
     transformed to the parallax $\parallax$.  Non-poissonian density variations
@@
     using random sampling, weighted by their likelihood of belonging to the
-    density. The background astrometric points in are generated from exponential
-    distributions at each $\phi_1$.  The number of stream stars is
-    $\variable{output/mock/nstream_variable.txt}$, while the number of
-    background stars is $\variable{output/mock/nbackground_variable.txt}$.
+    density. Post removal, the number of stream stars is
+    $\variable{output/mock/nstream_variable.txt}$.
+    $\variable{output/mock/nbackground_variable.txt}$ background astrometric points
+    are generated from exponential distributions at each $\phi_1$.
 
     The synthetic stream's photometry is also simulated using a 12~Gyr, [Fe/H] =
-    -1.35~dex NMIST isochrone \TODO{[cite brutus]}. The isochrone truncates just
+    -1.35~dex NMIST isochrone \TODO{[cite brutus]}. The isochrone is truncated just
     short of the giant branch, and is sampled from uniformly along the isochrone
@@
 
-    We pre-train a normalizing flow (see
-    \autoref{sub:method:photometric_model:off_stream}) on an off-stream
-    selection.  We train on the photometry.  You can see the selection in
-    \autoref{fig:mock_data_photometric_background_selection}.  You can see both
-    the on-stream and off-stream labels, blue and black respectively.  We select
-    using an astrometric selection. In the photometry you can see that the
-    on-stream selection has two populations, drawn from the isochrone and drawn
-    from the background The off-stream selection, meanwhile, has only the
-    background population. Next we train the full model.
+    We select on-stream and off-stream regions using the known $\phi_1, \phi_2$
+    range of the mock stream. The upper panel of
+    \autoref{fig:mock_data_photometric_background_selection} shows these
+    selections blue and black, respectively. The lower panel shows the on and
+    off-stream selections in photometric coordinates. In this space it is
+    apparent that the on-stream region has two populations, drawn from the
+    isochrone and from background points included in the simple $\phi_1, \phi_2$
+    box. In contrast the off-stream region, has only the the background population.
+    We use the off-stream population to train a conditional normalizing flow
+    (see \autoref{sub:method:photometric_model:off_stream}) on the magnitudes
+    $g$ and $r$ and conditioned on $\phi_1$. The normalizing flow is now a
+    non-parametric distribution characterizing the photometric background,
+    including its variation over $\phi_1$. For this mock stream the flexibility
+    of the normalizing flow greatly exceeds necessity: the background is
+    drawn from a $\phi_1$-invariant multivariate normal, essentially the base
+    distribution of the normalizing flow. It is therefore no surprise that
+    the trained normalizing flow provides an excellent characterization of
+    the background. We will later see that the flow performs similarly well
+    on complex distributions. Having trained the background photometric model
+    we proceed to train the full model.
 

### 2023-08-29 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-    The synthetic stream's photometry is also simulated using a 12~Gyr, [Fe/H] =
-    -1.35~dex NMIST isochrone \TODO{[cite brutus]}. The isochrone is truncated just
+    The synthetic stream's photometry is also simulated using a \variable{output/mock/isochrone_age_variable.txt},
+    [Fe/H] = \variable{output/mock/isochrone_feh_variable.txt} MIST isochrone \TODO{[cite brutus]}. The isochrone is truncated just
     short of the giant branch, and is sampled from uniformly along the isochrone

### 2023-08-29 src/tex/ms.tex
[showyourwork] overleaf sync

--- 2023-08-29 src/tex/ms.tex
@@
 
-        \subsubsection{On-Stream} \label{sub:method:photometric_model:on_stream}
+        \subsubsection{On-Stream} \label{ssub:method:photometric_model:on_stream}
 
@@
         In \autoref{sub:method:likelihood_setup} we introduced the likelihood
-        setup. In \autoref{sub:method:photometric_model:on_stream} we added
+        setup. In \autoref{ssub:method:photometric_model:on_stream} we added
         priors in the form of the isochrone's PDMF and photometric observational
@@
         MLP with a sequence of \texttt{Linear} \!\!\textrightarrow \texttt{Tanh}
-        \!\!\textrightarrow \texttt{Dropout} blocks. This is illustrated in
+        \!\!\textrightarrow \texttt{Dropout} (hereafter \texttt{LinTanh}) blocks. This is illustrated in
         \autoref{table:mlp_structure}.
@@
 
-    The synthetic stream's photometry is also simulated using a 12~Gyr, [Fe/H] =
-    -1.35~dex NMIST isochrone \TODO{[cite brutus]}. The isochrone is truncated just
+    The synthetic stream's photometry is also simulated using a
+    \variable{output/mock/isochrone_age_variable.txt},
+    [Fe/H] = \variable{output/mock/isochrone_feh_variable.txt} MIST isochrone
+    \TODO{[cite brutus]}. The isochrone is truncated just
     short of the giant branch, and is sampled from uniformly along the isochrone
@@
     on complex distributions.  Having trained the background photometric model
-    we proceed to train the full model.
+    we proceed to build and train the full model.
+
+    Per \autoref{eq:stream_and_bkg_prob} the stream is a conditionally independent
+    addition of both astrometric and photometric models.
+    In astrometrics the stream is a Gaussian track in $\phi_2$ and
+    parallax $\varpi$, using the model defined in
+    \autoref{ssub:method:astrometric_model:on_stream}. We use a 4-layer 
+    (\texttt{LinTanh} with shape (1 input, 64 hidden, 4 output), where the 4 outputs
+    are $[\mu_{\phi_2}, \sigma_{\phi_2}, \mu_{\varpi}, \sigma_{\varpi}](\phi_1)$.
+    The network is small, but sufficiently large to permit 15\% dropout and retain
+    robust predictions.
+    The photometric model is a distance modulus-shifted isochrone, using the model
+    outlined in  \autoref{ssub:method:photometric_model:on_stream}. We use the
+    same isochrone parameters as were used to simulate the stream. For this mock
+    stream we demonstrate simultaneous astrometric and photometric modeling, linking
+    the distance modulus and parallax track, as explained in
+    \autoref{ssub:method:linking_to_astrometrics}. Thus the photometric model
+    does not have its own network, using instead the outputs
+    $[\mu_{\varpi}, \sigma_{\varpi}](\phi_1)$.
+    The background model is split in two components, the first is a uniform distribution
+    in $\phi_2$, the second an exponential.
 

### 2023-08-29 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     The background model is split in two components, the first is a uniform distribution
-    in $\phi_2$, the second an exponential.
+    in $\phi_2$, the second is an exponential distribution for $\varpi$.
+    The uniform distribution does not have any parameters, and thus no neural network.
+    The exponential distribution has only the slope parameter and we use a 3-layer 
+    (\texttt{LinTanh} with shape (1, 32, 1) and 15\% dropout.
 

### 2023-08-29 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     \autoref{ssub:method:astrometric_model:on_stream}. We use a 4-layer 
-    (\texttt{LinTanh} with shape (1 input, 64 hidden, 4 output), where the 4 outputs
+    \texttt{LinTanh} with shape (1 input, 64 hidden, 4 output), where the 4 outputs
     are $[\mu_{\phi_2}, \sigma_{\phi_2}, \mu_{\varpi}, \sigma_{\varpi}](\phi_1)$.
@@
     The exponential distribution has only the slope parameter and we use a 3-layer 
-    (\texttt{LinTanh} with shape (1, 32, 1) and 15\% dropout.
+    \texttt{LinTanh} with shape (1, 32, 1) and 15\% dropout. Background and
+    stream are combined in a mixture model whose mixture parameters are a 4-layer 
+    (1, 64, 1) \texttt{LinTanh} network. We train the mixture model with an
+    \texttt{AdamW} optimizer with learning rate of $5\times10^{-3}$ and a scheduler
+    to periodically and temporarily increase the learning rate, encouraging the optimizer
+    towards better minima.
 

### 2023-08-29 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     model has captured the two prominent density variations along the stream.
-    The are additional variations  mostly around the edges of the stream, though
+    There are additional variations, mostly around the edges of the stream, though
     re-sampling the neural network weights with dropout reveals that these

### 2023-08-29 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     We find that the stream is successfully recovered in both astrometric and
-    photometric coordinates, with $x\%$ stream stars being recovered with
-    membership probability greater than $y$. The false positive rate (i.e.,
-    stars misidentified as stream members) for this test is found to be $z\%$
-    when cutting on this threshold.
+    photometric coordinates, with $\variable{output/mock/ncorrect_variable}\%$ stream
+    stars being recovered with membership probability greater than $80\%$. The false
+    positive rate (i.e., stars misidentified as stream members) for this test is
+    found to be $\variable{output/mock/falseident_variable.txt}\%$ when cutting on
+    this threshold.
 

### 2023-08-29 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     We find that the stream is successfully recovered in both astrometric and
-    photometric coordinates, with $\variable{output/mock/ncorrect_variable}\%$ stream
+    photometric coordinates, with $\variable{output/mock/ncorrect_variable.txt}\%$ stream
     stars being recovered with membership probability greater than $80\%$. The false

### 2023-08-29 src/tex/ms.tex
[showyourwork] overleaf sync

@@
                 multi-modal (panel 2) if there are large gaps or `smeared' out
-                if the Gaussian's mean changes significantly over the range.
+                (panel 3) if the Gaussian's mean changes significantly over the range.
             %
@@
                 background stars (blue) over the stream stars to show that the
-                how the two distributions mix.  } TODO:
+                how the two distributions mix.
+            % 
+        }
+        \label{fig:mock_data_result}
+        TODO:
         \begin{enumerate}
@@
         \end{enumerate}
-        \label{fig:mock_data_result}
     \end{figure*}
@@
     photometric coordinates, with $\variable{output/mock/ncorrect_variable.txt}\%$ stream
-    stars being recovered with membership probability greater than $80\%$. The false
-    positive rate (i.e., stars misidentified as stream members) for this test is
-    found to be $\variable{output/mock/falseident_variable.txt}\%$ when cutting on
-    this threshold.
-
+    stars being recovered with membership probability greater than $80\%$.
     In the bottom two rows of \autoref{fig:mock_data_result} we illustrate the
@@
     ($\sim 0$) where the stream is absent.
+    The false positive rate (i.e., stars misidentified as stream members) for this test
+    is found to be $\variable{output/mock/falseident_variable.txt}\%$ when cutting on
+    the 80\% membership probability threshold.
+    % The perfect recovery rate and low false identification rate demonstrate the efficacy
+    % of this method.
+
+    % Discussion why not finding the small-scale fluctuations?
 
@@
 
-    We now apply our density modeling approach to the stellar stream GD-1. We
-    discuss the data selection in \autoref{sub:results_gd1_data} and results in
-    \autoref{ssub:trained_gd1}.
-
-    \subsection{Data Selection} \label{sub:results_gd1_data}
+    Having successful applied the modeling framework to a mock stream,
+    we now apply our density modeling approach to the stellar stream GD-1.
+    We
+    discuss the data selection in \autoref{sub:results_gd1:data},
+    model specifics in \autoref{sub:results_gd1:model},
+    and the results in \autoref{sub:results_gd1:results}.
+
+    \subsection{Data Selection} \label{sub:results_gd1:data}
 
@@
 
-    \subsection{Model Specification}\label{sec:GD_1_ModelSpecification}
+    \subsection{Model Specification}\label{sub:results_gd1:model}
 
@@
 
-    \subsection{Trained Density Model}\label{ssub:trained_gd1}
+    \subsection{Trained Density Model}\label{sub:results_gd1:results}
 

### 2023-08-29 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
+    \subsection{Data Simulation} \label{sub:results_mock:data}
+
         We generate synthetic stream observations by sampling uniformly in $\phi_1$
@@
         background points in each astrometric and photometric dimension.
+
+    \subsection{Model Specification} \label{sub:resultes_mock:model}
 
@@
         towards better minima.
+
+    \subsection{Trained Density Model} \label{sub:results_mock:results}
 
@@
 
-% sec: test_on_a_synthetic_stream (end)
+% sec: results  (end)
 
@@
 
-    Having successful applied the modeling framework to a mock stream,
-    we now apply our density modeling approach to the stellar stream GD-1.
+    Having successful applied the density modeling framework to a
+    mock stream, we now apply the method to the stellar stream GD-1.
+    % TODO: some reiteration on the importance of GD-1
     We

### 2023-08-29 src/tex/ms.tex
[showyourwork] overleaf sync

@@
         We find that the stream is successfully recovered in both astrometric and
-        photometric coordinates, with $\variable{output/mock/ncorrect_variable.txt}\%$ stream
+        photometric coordinates, with $\variable{output/mock/ncorrect_variable.txt}\%$ of stream
         stars being recovered with membership probability greater than $80\%$.
@@
 
-        \begin{enumerate}
-            \item Gaia data.
-                \begin{enumerate}
-                    \item box size
-                    \item selection criteria
-                \end{enumerate}
-            \item crossmatched with panstarrs1
-            \item extinction corrected with bayestar2019
-        \end{enumerate}
+        % \begin{enumerate}
+        %     \item Gaia data.
+        %         \begin{enumerate}
+        %             \item box size
+        %             \item selection criteria
+        %         \end{enumerate}
+        %     \item crossmatched with panstarrs1
+        %     \item extinction corrected with bayestar2019
+        % \end{enumerate}
 

### 2023-08-29 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \newcommand{\Gaia}{\dataarchive{Gaia}}
-\newcommand{\gaia}{\dataarchive{gaia}}
+\newcommand{\PanStarrs}{\dataarchive{Pan-STARRS1}}
 
@@
         % TODO: terminology ND-phase-space vs feature columns
-        Most streams in \gaia {\color{red} [cite]}, for instance, have proper
+        Most streams in \Gaia {\color{red} [cite]}, for instance, have proper
         motions but not radial velocities nor reliable parallax measurements.
@@
             stream need be modeled.  For streams with observable main sequence
-            turn-offs, like \stream{GD-1} in \gaia, this portion of the
+            turn-offs, like \stream{GD-1} in \Gaia, this portion of the
             isochrone has both many stars and a relatively small range in
@@
 
-        We utilize data from {\it Gaia} DR3 for the astrometric coordinates of
-        each star, and Pan-STARRS1 to obtain more accurate color information. We
+        We utilize data from \Gaia{} DR3 for the astrometric coordinates of
+        each star, and \PanStarrs{} to obtain more accurate color information.
+
+        We cross-match the \Gaia{} field on \PanStarrs{} using the provided
+        \texttt{Best-neighbors} catalog.
+
         adopt broad cuts on the cross-matched data to limit the field to a
-        region known to contain GD-1. We perform these rough cuts by requiring
+        region known to contain GD-1. We perform these rough cuts by requiring...
+
+        We use the \texttt{GD1Koposov10} frame defined in Gala \TODO{[cite gala and Koposov10]}
+
         \JN{fill in what the cuts are and reference proper motion figure and CMD

### 2023-08-29 src/tex/ms.tex
[showyourwork] overleaf sync

@@
         This defines an astrometric phase-space hyper-tube
-        \cite{2018MNRAS.477.4063M}, with a distribution radial to the track.
+        \cite{STREAMFINDER}, with a distribution radial to the track.
 
@@
         \begin{enumerate}
-            \item Streamfinder \citep{2018MNRAS.477.4063M}. This method requires the potential
+            \item Streamfinder \citep{STREAMFINDER}. This method requires the potential
             \item VIA MACHINAE \citep{2022MNRAS.509.5992S}
@@
         astrometrics as well as photometrics and chemical abundances available
-        \citep[e.g.,][]{Koposov2019, 2020A&A...635L...3A, 2022ApJ...928...30L},
+        \citep[e.g.,][]{Koposov2019, Antoja2020, 2022ApJ...928...30L},
         while most have partial coverage, lacking some feature dimensions.
@@
             where $\delta$ is the Dirac delta function
-            \citep{1947pqm..book.....D}, and enforces that the distance modulus
+            \citep{Dirac1947}, and enforces that the distance modulus
             track and parallax track must be equal (when converted to the actual
@@
             it is a categorical, more informative priors like the Dirichlet
-            distribution \citep{Bishop_Christopher_M_2016-08-23} may be used.
+            distribution \citep{Christopher2016} may be used.
             Our code permits any user-defined prior, and we include $\mcal{U}(a,
@@
 
-        \subsubsection[STREAMFINDER]{\cite{2018MNRAS.477.4063M}}
+        \subsubsection[STREAMFINDER]{\cite{STREAMFINDER}}
 

### 2023-08-30 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \usepackage{amsmath, amssymb}
+\usepackage{gensymb}
 \usepackage{xcolor}
@@
     There are a few previous works which have modeled stellar streams in this
-    context. \citet{2022MNRAS.514.1757P} developed a data-driven spline-based
+    context. \citet{Patrick+2022} developed a data-driven spline-based
     model for modeling the photometric qualities of previously identified
@@
     targeted observations. From a population of RR Lyrae stars,
-    \citet{2019AJ....158..223P} utilized a mixture model to fit the globular
+    \citet{Price-Whelan+2019} utilized a mixture model to fit the globular
     cluster stream Pal-5 in the space of proper motions and heliocentric
@@
         progenitors are gravitationally bound systems, such as satellite dwarf
-        galaxies or star clusters \citep{Odenkirchen2001, Majewski2003}. In the
+        galaxies or star clusters \citep{Odenkirchen+2001, Majewski+2003}. In the
         absence of external interactions these systems are stable, though still
@@
         completely, as in the merger events that formed the Galactic stellar
-        halo \citep{Lynden-Bell1967, Searle1978}; or partially, such as tidal
+        halo \citep{Lynden-Bell1967, SearleZinn1978}; or partially, such as tidal
         disruption forming a stellar stream.
@@
         saddle point of the combined potential -- e.g. the L2 and L3 Lagrange
-        points for a spherical galactic field \citep{Ross1997, Fukushige2000,
+        points for a spherical galactic field \citep{Ross+1997, FukushigeHeggie2000,
         BinneyTremaine2008}. Generally, the initial phase space position of the
@@
         dissimilar orbits from each other and the progenitor than do stars in
-        cold streams, with smaller dispersions \citep{Johnston1998, Hendel2015}.
+        cold streams, with smaller dispersions \citep{Johnston1998, HendelJohnston2015}.
         The orbit of a star depends on its phase space position and the
@@
         normally dominated by the Galaxy (primarily the dark matter halo at
-        large distances) \citep{Gibbons2014}. However, an orbit is impractical
+        large distances) \citep{Gibbons+2014}. However, an orbit is impractical
         to observe on human timescales. Cold streams offer a workaround.  Like
@@
         known Galactic streams see][]{Mateu2022}, extend the detected extents of
-        known streams \citep[e.g. for \stream{Palomar 5} alone:][]{Rockosi2002,
-        Ibata2017, Grillmair2006, Carlberg2012, StarkmanEtAl2019}, and increase
+        known streams \citep[e.g. for \stream{Palomar 5} alone:][]{Rockosi+2002,
+        Ibata+2017, Grillmair+2006, Carlberg+2012, Starkman+2019}, and increase
         the general purity of stream catalogs.
@@
             \item Streamfinder \citep{STREAMFINDER}. This method requires the potential
-            \item VIA MACHINAE \citep{2022MNRAS.509.5992S}
+            \item VIA MACHINAE \citep{Shih+2022}
             \item Kiyan and Adrian
@@
             \item Gaia stuff: Adrian and Ana and Sara et al
-            \item Uniform Modeling of 12 Stellar stream \citep{PatrickEtAl2022}. Only on phi1, phi2, and CMD. Their CMD method is more sophisticated. Worth discussing.
+            \item Uniform Modeling of 12 Stellar stream \citep{Patrick+2022}. Only on phi1, phi2, and CMD. Their CMD method is more sophisticated. Worth discussing.
         \end{enumerate}
@@
         However, data observations are not taken from the GCOM, but from  $\sim
-        8$ kpc distant \citep{GRAVITY2018, Leung2022} in a local frame,
+        8$ kpc distant \citep{GRAVITY2018, Leung+2022} in a local frame,
         typically from vantage points such as Earth or its solar Lagrange
@@
         of dwarf galaxies, like the Magellanic stream which wraps multiple times
-        around the Milky Way \citep{Wannier1972}, no such transformation is
+        around the Milky Way \citep{WannierWrixon1972}, no such transformation is
         possible. More generally, a stream's ``sky"-projected path may be
@@
         transformation is known \textit{a priori}, or may be constructed during
-        pre-processing \citep[see][\S2.1]{StarkmanEtAl2023}.  We note that, with
+        pre-processing \citep[see][\S2.1]{Starkman+2023}.  We note that, with
         sufficient prior knowledge, many-to-one functions may be broken into
@@
         coefficients into functions of a conditional input
-        \citep{McLachlan1989MixtureM}.  Mixture Density Networks (MDNs) are a
+        \citep{McLachlanBasford1989}.  Mixture Density Networks (MDNs) are a
         machine learning method to implement these general MM, taking the
@@
         astrometrics as well as photometrics and chemical abundances available
-        \citep[e.g.,][]{Koposov2019, Antoja2020, 2022ApJ...928...30L},
+        \citep[e.g.,][]{Koposov+2019, Antoja+2020, Li+2022},
         while most have partial coverage, lacking some feature dimensions.
@@
             turnoff (MSTO). We include also a Kroupa initial mass function (IMF)
-            \citep{2001MNRAS.322..231K}. The Kroupa IMF, and all
+            \citep{Kroupa2001}. The Kroupa IMF, and all
             physically-motivated IMFs, have an much larger fraction of low-mass
@@
         In $\phi_2$ we sample from a quadratic in $\phi_1$ with normally-distributed
-        $0.15^{\circ}$ scatter.  The distances are sampled from a linear funciton in
+        $0.15^{\degree}$ scatter.  The distances are sampled from a linear funciton in
         $\phi_1$ with normally-distributed $0.25 \ \unit{kpc}$ scatter, then
@@
         [Fe/H] = \variable{output/mock/isochrone_feh_variable.txt} MIST isochrone
-        \TODO{[cite brutus]}. The isochrone is truncated just
+        \citep{brutus, Dotter2016, Choi+2016}. The isochrone is truncated just
         short of the giant branch, and is sampled from uniformly along the isochrone
@@
         \autoref{fig:mock_data_photometric_background_selection} shows these
-        selections blue and black, respectively.  The lower panel shows the on and
+        selections in blue and black, respectively.  The lower panel shows the on and
         off-stream selections in photometric coordinates.  In this space it is
@@
 
-        Per \autoref{eq:stream_and_bkg_prob} the stream is a conditionally independent
+        Per \autoref{eq:stream_and_bkg_prob} the stream is an independent
         addition of both astrometric and photometric models.
@@
         $[\mu_{\varpi}, \sigma_{\varpi}](\phi_1)$.
-        The background model is split in two components, the first is a uniform distribution
-        in $\phi_2$, the second is an exponential distribution for $\varpi$.
+
+        The total background model has two pieces, an astrometric and a photometric model.
+        As a pre-training phase the photometric normalizing flow model was fitted to
+        an off-stream selection and is now held fixed. The astrometric model
+        is split in two components, the first is a uniform distribution
+        in $\phi_2$, and the second is an exponential distribution for $\varpi$.
         The uniform distribution does not have any parameters, and thus no neural network.
@@
     % TODO: some reiteration on the importance of GD-1
-    We
-    discuss the data selection in \autoref{sub:results_gd1:data},
+    We discuss the data selection in \autoref{sub:results_gd1:data},
     model specifics in \autoref{sub:results_gd1:model},
@@
 
-        % \begin{enumerate}
-        %     \item Gaia data.
-        %         \begin{enumerate}
-        %             \item box size
-        %             \item selection criteria
-        %         \end{enumerate}
-        %     \item crossmatched with panstarrs1
-        %     \item extinction corrected with bayestar2019
-        % \end{enumerate}
-
         We utilize data from \Gaia{} DR3 for the astrometric coordinates of
-        each star, and \PanStarrs{} to obtain more accurate color information.
-
-        We cross-match the \Gaia{} field on \PanStarrs{} using the provided
-        \texttt{Best-neighbors} catalog.
-
-        adopt broad cuts on the cross-matched data to limit the field to a
-        region known to contain GD-1. We perform these rough cuts by requiring...
-
-        We use the \texttt{GD1Koposov10} frame defined in Gala \TODO{[cite gala and Koposov10]}
-
-        \JN{fill in what the cuts are and reference proper motion figure and CMD
-        figure.}
-
-        The result is a field populated by \JN{x} stars, from which we would
+        each star. 
+        To obtain more accurate color information, we cross-match the \Gaia{}
+        field on \PanStarrs{} \citep{PanSTARRS1} using 
+        \Gaia's provided \texttt{Best-neighbors} catalog.
+        To limit the field to a region known to contain GD-1 we adopt broad cuts
+        on the cross-matched data. We perform these rough cuts by requiring
+        the data lie within the phase-space cube:
+        \begin{itemize}
+            \item $\phi_1 \in [-100, 40] \ \rm{\degree}$,
+            \item $\phi_2 \in [-9, 5] \rm{\degree}$,
+            \item $\varpi \in [-10, 1] \ \rm{mas}$,
+            \item $\rm{bp-rp} \in [-1, 3] \ \rm{mag}$
+            \item $g, r \in [0, 50] \ \rm{mag}$, and not \texttt{null}.
+        \end{itemize}
+        where, we use Gala's \citep{gala, galav1.3} \texttt{GD1Koposov10} frame
+        \citep{Koposov+2010} to define $\phi_1$, $\phi_2$, and associated proper motions.
+        For downloading purposes, we split the query into 10 sub-regions,
+        in even $\phi_1$ increments. A plot of the $\phi_1, \phi_2$ regions is included
+        in the \href{\GitHubURL{}}{\package{ShowYourWork}} repository.
+        Stream-specific coordinates ($\phi_1, \phi_2$) are not included in \Gaia.
+        One could embed the coordinate transform in the ADQL \citep{ADQL2.0},
+        or define great-circle arcs in ICRS \citep{ICRS1997}. Since only rough
+        cuts are required and since the boxes are sufficiently small for a reasonable flat-sky
+        approximation  we simply translate the ($\phi_1, \phi_2$) sub-region boxes to ICRS.
+        We correct the \PanStarrs{} photometry for dust extinction
+        using the \textit{Bayestar19} \citep{Green+2019} models in the \package{dustmaps} package \citep{Green2018}.
+        \textit{Bayestar19 is a three-dimensional dust map of the Milky Way
+        for which we use \Gaia's parallax distance information.
+        We include the $1-\sigma$ errors as a source of uncertainty
+        in $\Sigma_n$, the per-star photometric uncertainty.
+        % TODO: actually implement that in the model
+        The result is a field populated by \variable{output/gd1/ndata_variable.txt} stars, from which we would
         like to identify stream members.
 
-        \todo[inline]{Dust}
-            We use \package{dustmaps} Bayestar 19 for the dust modeling. We treat it as known. Include as a source of error in $\Sigma_n$
-            % TODO: actually implement that in the model
+        In \autoref{fig:gd1-data_selection} we create data masks for a more refined
+        selection around the stream.
+
+        We make proper motion selection boxes at box corners $(\mu_{\phi_1}, \mu_{\phi_2}) = [(-15,-10) (-4.5, -2)] \ \unit{mas/yr}$, and $(\mu_{\phi_1}, \mu_{\phi_2}) = [(-15,-5) (-5, -1)] \ \unit{mas/yr}$,
+
+        \begin{figure*}[h]
+            \script{gd1/plot/data_selection.py}
+            \centering
+            \includegraphics[width=1\linewidth]{figures/gd1/data_selection.pdf}
+            \caption{%
+                Data selections for \stream{GD-1}, within the data cube described
+                in \autoref{sub:results_gd1:data}.
+                %
+                \textbf{Row 1 Panels:}
+                Proper motion selection boxes in red and yellow.
+                The right plot
+                %
+                \textbf{Row 2 Panels:}
+                Photometric selection (blue curve). The selection is based on
+                a 12 Gyr, [Fe/H] = -1.3 MIST isochrone, buffered by 0.2 dex.
+                % 
+                \textbf{Row 3 Panels:}
+                Applying the red astrometric and blue photometric selections, plotted
+                for astrometric coordinates $\phi_2, \varpi, \mu_{\phi_1}, \mu_{\phi_2}$.
+                % 
+                \textbf{Row 4 Panels:}
+                Applying the yellow astrometric and blue photometric selections, plotted
+                for the same astrometric coordinates as the above row.
+            }
+            \label{fig:gd1-data_selection}
+        \end{figure*}
 
@@
 
+        \todo[inline]{rephrase, this is quoting from the mock stream}
+        We select on-stream and off-stream regions using the known $\phi_1,\phi_2$ range
+        of the stream. The upper panel of \autoref{fig:gd1-photometric_background_selection}
+        shows these selections in blue and black, respectively.
+        The lower panel shows the on and off-stream selections in photometric
+        coordinates. An isochrone is apparent in the distribution.
+        We use the off-stream population to train a
+        conditional normalizing flow (see \autoref{sub:method:photometric_model:off_stream})
+        on the magnitudes $g$ and $r$ and conditioned on $\phi_1$.
+        The normalizing flow is now a non-parametric distribution characterizing
+        the photometric background, including its variation over $\phi_1$.
+
+        \begin{figure}
+            \script{gd1/plot/photometric_background_selection.py}
+            \centering
+            \includegraphics[width=1\linewidth]{figures/gd1/photometric_background_selection.pdf}
+            \caption{Caption}
+            \label{fig:gd1-photometric_background_selection}
+        \end{figure}
+
         We model GD-1 as a three-component mixture consisting of a main stream
-        component, a spur, and background. In order to guide our model towards
+        component, a spur, and background.
+
+        \todo[inline]{rephrase }
+        Per \autoref{eq:stream_and_bkg_prob} the stream is an independent addition
+        of both astrometric and photometric models.
+        In astrometrics the stream is a Gaussian track in $\phi_2, \mu_{\phi_1}, \mu_{\phi_2}$
+        using the model defined in \autoref{ssub:method:astrometric_model:on_stream}.
+        We use a 4-layer \texttt{LinTanh} with shape (1, 128, 6), where the 6 outputs
+        are $[\mu_{\phi_2}, \sigma_{\phi_2}, \mu_{\mu_{\phi_1}^*}, \sigma_{\mu_{\phi_1}^*}, \mu_{\mu_{\phi_2}}, \sigma_{\mu_{\phi_2}}](\phi_1)$. The network
+        is small, but sufficiently large to permit 15\% dropout and retain robust
+        predictions. The photometric model is a distance modulus-shifted isochrone,
+        using the model outlined in \autoref{ssub:method:photometric_model:on_stream}.
+        We use the same isochrone parameters used in the photometric selection.
+        The photometric model has its own network.
+
+        In order to guide our model towards
         GD-1, we set down 4 ``control points" along GD-1's main track, and 3
-        control points along the spur (illustrated in \JN{x}). These control
+        control points along the spur (illustrated in \TODO{x}). These control
         points act as Gaussian priors on the model. We set the Gaussian error on
@@
 
-        The weight parameter is also set to truncate to $0$ at $\phi_1 < X$ and $\phi_1 > Y$. This ensures that we do not model stream stars that fall
+        We also add 3 control points in the distance modulus.
+        We draw the points from \TODO{[cite]} and add significant width.
+
+        The background model is an exponential distribution.
+
+        The weight parameter is also set to truncate to $0$ at $\phi_1 < X$
+        and $\phi_1 > Y$. This ensures that we do not model stream stars that fall.
 
@@
         model provide an adequate description of the data. \JN{more on this...}
-
-        \begin{figure*}[h]
-            \script{gd1/plot/data_selection.py}
-            \centering
-            \includegraphics[width=1\linewidth]{figures/gd1/data_selection.pdf}
-            \caption{Caption}
-            \label{fig:gd1-data_selection}
-        \end{figure*}
-
-        \begin{figure}
-            \script{gd1/plot/photometric_background_selection.py}
-            \centering
-            \includegraphics[width=1\linewidth]{figures/gd1/photometric_background_selection.pdf}
-            \caption{Caption}
-            \label{fig:gd1-photometric_background_selection}
-        \end{figure}
 
@@
 
-        \subsubsection{VIA MACHINAE}{\cite{2022MNRAS.509.5992S}}
+        \subsubsection{VIA MACHINAE}{\cite{Shih+2022}}
 
@@
 
-        \subsubsection[Uniform Modeling of 13 Stellar Streams]{\cite{PatrickEtAl2022}}
+        \subsubsection[Uniform Modeling of 13 Stellar Streams]{\cite{Patrick+2022}}
 
@@
 
-        \package{asdf} \citep{Greenfield2015},
+        \package{asdf} \citep{Greenfield+2015},
         \package{astropy} \citep{Astropy2013, Astropy2018, Astropy2022},
@@
         \package{Matplotlib} \citep{Hunter2007},
-        \package{NumPy} \citep{Harris2020},
+        \package{NumPy} \citep{Harris+2020},
         \package{Pytorch} \citep{Pytorch2019},
@@
     \href{https://github.com/showyourwork/showyourwork}{\showyourwork}
-    \citep{Luger2021}, which uses continuous integration to
+    \citep{Luger+2021}, which uses continuous integration to
     programmatically download the data, perform the analyses, create the
@@
         \end{equation}
-        where $T$ is Owen's T distribution \citep{Owen_1956}.
+        where $T$ is Owen's T distribution \citep{Owen1956}.
 

### 2023-08-30 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-\newcommand{\package}[1]{\textsc{#1}}
+\newcommand{\code}[1]{\textsc{#1}}
+\newcommand{\package}[1]{\code{#1}}
 \newcommand{\stream}[1]{#1}
@@
     like {\it Gaia} and low-surface brightness photometric surveys (\JN{cite}).
-    The formation of streams can be traced back to a progenitor cluster (i.e., a
-    satellite galaxy or globular cluster), whose stars are gradually lost to the
+    The formation of streams can be traced back to a progenitor cluster, whose stars are gradually lost to the
     tidal field of the host galaxy and extend along a series of similar orbits
-    producing tidal tails, which can sometimes span many tens of degrees across
-    the sky. This orbital proximity of stars belonging to a stream makes them
+    producing tidal tails, which can sometimes span several tens of degrees across
+    the sky. The orbital proximity of stars belonging to a stream makes them
     sensitive tracers of the mass distribution of galaxies, sourced by both the
     baryonic and dark matter components.
-    % 
+
     The average properties of a stream (e.g., the mean position and velocity
@@
     (\JN{cite}). Importantly, these galactic components span orders of magnitude
-    in mass, highlighting the importance of characterizing a population of
-    stellar streams both in morphology and kinematics. 
-    % 
+    in mass and spatial extent, highlighting the sensitivity of streams in constraining the structure of the galaxy.
+
     While several methods have been developed to model stream properties as a
-    function of global halo properties (e.g., flattening and
+    function of global halo characteristics (e.g., flattening and
     orientation;\JN{cite}) and local substructures (e.g., the bar's pattern
-    speed and the mass of subhalo perturbers; \JN{cite}), these methods and
-    insights often rely on the existence of a homogenized stream-tracer
-    population that characterizes the stream across each of the observable
+    speed and the mass of subhalo perturbers; \JN{cite}), these methods often rely on the existence of a homogenized stream-tracer
+    population that characterizes a given stream across each of the observable
     phase-space dimensions. Additionally, because even the fine-grain properties
-    of streams are influenced by the detailed mass distribution of galaxies, it
+    of streams are influenced by the detailed mass distribution of its host galaxy, it
     is important to propagate errors both in measurement uncertainty and
     membership uncertainty (i.e., which stars belong to the stream versus the
-    background) when attempting to model the galaxy. Otherwise, a stream that
-    has been poorly characterized could bias constraints on (e.g.) the total
+    background) when attempting to model a stream. Otherwise, a poorly characterized stream could bias constraints on (e.g.) the total
     mass of the galaxy, the dark matter halo shape, and the mass of subhalo
@@
     of the galaxy, it is therefore imperative that a statistically sound and
-    homogenized catalog of stellar streams is produced so that theoretical
-    models for the gravitational potential of the galaxy across a large range of
-    spatial scales can be constrained. 
-    %
+    homogenized catalog of stellar streams is produced.
+
     While streams are well described in (e.g.) action angle coordinates or
-    $N-$body simulations, these methods relying on prior assumptions about the
-    galaxy and its underlying potential. Therefore, it is important to devise
+    $N-$body simulations, these methods rely on prior assumptions about the
+    galaxy and its underlying gravitational potential. Therefore, it is necessary to devise
     data-driven methods to characterize stellar streams without appealing to
     strong prior assumptions about the galaxy's structure.
-    % 
+
     There are a few previous works which have modeled stellar streams in this
     context. \citet{Patrick+2022} developed a data-driven spline-based
-    model for modeling the photometric qualities of previously identified
+    method for modeling the photometric properties and on-sky positions of previously identified
     streams. Their method works by fitting the stream's stellar surface density
@@
     the stream and changes in the position of the stream track and width. Their
-    method also utilize a simultaneous ischorone fit to the stream, from which a
-    distance modulus can be derived by assuming that the entire stream
-    originates from the same stellar population. While this method is very
+    method also utilize a simultaneous isochrone fit to a given stream, from which a
+    distance modulus can be derived. While this method is very
     successful at characterizing the photometric properties of a stream, it does
-    not consider the kinematic dimensions which have become increasing
+    not consider the kinematic dimensions which have become increasingly
     well-measured with successive data releases from {\it Gaia}, as well as
@@
     distances. The mixture modeling approach enables a simultaneous fit to both
-    the stream and background density, enabling better separation of a coherent
-    stream from an otherwise noisy background distribution. However, the track
+    the stream and background density, allowing for better separation of the stream from the background distribution. However, the track
     of the stream in on-sky coordinates is not fit. The method identified 27 RR
     Lyrae stars consistent with being members of the stream. While useful for
-    determining the average properties of the stream (e.g., its mean distance
+    determining the average properties of a stream (e.g., its mean distance
     track), a limited population of RR Lyrae stars are not sufficient to capture
-    the fine-grained properties of streams expected to inform constraints on
+    the small-scale properties of streams expected to inform constraints on
     (e.g.) a population of perturbers in the galaxy. \JN{are there other
     methods?}
-    % 
+
     Other methods for extracting stellar streams from the data include
@@
     key papers using this method}. While the matched-filter technique has been
-    extremely successful at stream discovery, it is not equipped to characterize
+    extremely successful in stream discovery, it is not equipped to characterize
     streams at the level of detailed necessary to inform precise constraints on
     the potential of the galaxy and its substructure.
-    % 
+
     In order to address the need for a flexible model of stellar streams both in
@@
     characterization of streams insofar as the available data allows.
+We do not rely on assumptions about the potential of the galaxy, and utilize mixture density nextworks to flexibly capture the qualities of a stream.
 
@@
                 %
-                \textbf{Top panel:}%
+                \textbf{Top panel: }%
                     The stream mixture coefficient $f(\phi_1)$ (black dotted line)
@@
         The false positive rate (i.e., stars misidentified as stream members) for this test
-        is found to be $\variable{output/mock/falseident_variable.txt}\%$ when cutting on
+        is found to be $\variable{output/mock/falseident_variable.txt}\%$ (3 stars) when cutting on
         the 80\% membership probability threshold.
@@
         \Gaia's provided \texttt{Best-neighbors} catalog.
-        To limit the field to a region known to contain GD-1 we adopt broad cuts
+        To limit the field to a region known to contain \stream{GD-1} we adopt broad cuts
         on the cross-matched data. We perform these rough cuts by requiring
@@
         \end{itemize}
-        where, we use Gala's \citep{gala, galav1.3} \texttt{GD1Koposov10} frame
+        where, we use \package{gala}'s \citep{gala, galav1.3} \code{GD1Koposov10} frame
         \citep{Koposov+2010} to define $\phi_1$, $\phi_2$, and associated proper motions.
@@
         or define great-circle arcs in ICRS \citep{ICRS1997}. Since only rough
-        cuts are required and since the boxes are sufficiently small for a reasonable flat-sky
-        approximation  we simply translate the ($\phi_1, \phi_2$) sub-region boxes to ICRS.
+        cuts are required and since the sub-region boxes are sufficiently small for a reasonable flat-sky
+        approximation  we simply translate the ($\phi_1, \phi_2$) boxes to ICRS.
         We correct the \PanStarrs{} photometry for dust extinction
         using the \textit{Bayestar19} \citep{Green+2019} models in the \package{dustmaps} package \citep{Green2018}.
-        \textit{Bayestar19 is a three-dimensional dust map of the Milky Way
+        \textit{Bayestar19} is a three-dimensional dust map of the Milky Way
         for which we use \Gaia's parallax distance information.
         We include the $1-\sigma$ errors as a source of uncertainty
-        in $\Sigma_n$, the per-star photometric uncertainty.
+        in $\mbs{\Sigma}_n$, the per-star photometric uncertainty.
         % TODO: actually implement that in the model
-        The result is a field populated by \variable{output/gd1/ndata_variable.txt} stars, from which we would
-        like to identify stream members.
-
-        In \autoref{fig:gd1-data_selection} we create data masks for a more refined
-        selection around the stream.
-
-        We make proper motion selection boxes at box corners $(\mu_{\phi_1}, \mu_{\phi_2}) = [(-15,-10) (-4.5, -2)] \ \unit{mas/yr}$, and $(\mu_{\phi_1}, \mu_{\phi_2}) = [(-15,-5) (-5, -1)] \ \unit{mas/yr}$,
+        The result is a field populated by \variable{output/gd1/ndata_variable.txt} stars,
+        from which we would like to identify stream members.
+
+        We create data masks for a more refined selection around \stream{GD-1}.
+        The two mask types, proper motion and photometric,
+        are show in \autoref{fig:gd1-data_selection}.
+        The proper motion masks select rectangular regions, containing the primary overdensity
+        of \stream{GD-1} and a surrounding area following the tail of the distribution.
+        The tighter mask (red) has corners $(\mu_{\phi_1}, \mu_{\phi_2}) = [(-15,-10) (-4.5, -2)] \ \unit{mas/yr}$, while the larger mask (yellow) has $(\mu_{\phi_1}, \mu_{\phi_2}) = [(-15,-5) (-5, -1)] \ \unit{mas/yr}$.
+        In photometric coordinates we define a mask around
+        % TODO: make these variables, like in mock
+        a 12 Gyr, [Fe/H] = -1.3 isochrone at a distance of 7.8 kpc. The selection region is a 0.2 dex orthogonal buffer around the MIST isochrone \citep[using]{brutus}, which
+        is illustrated in the 2nd-from-the-top-left plot in \autoref{fig:gd1-data_selection}.
+        In addition, to avoid detailed modeling of the completeness as a term in $\prior_{obs}$ (from \autoref{isochrone_prior_components}) we mask out photometry with $G_{\Gaia{}} > 20$.
+        With combinations of these masks the stream has much larger signal-to-noise, though
+        is still only a small percent of the total data.
 
@@
                 Proper motion selection boxes in red and yellow.
-                The right plot
+                The right plot shows the application of these selections.
+                \stream{GD-1} is apparent from around $-60$ to $-10$ deg in the red
+                selection and present, if less clearly, in the yellow selection.
                 %
@@
                 a 12 Gyr, [Fe/H] = -1.3 MIST isochrone, buffered by 0.2 dex.
+                The right plot shows the application of this selection. By eye, the stream
+                is a small overdensity extending from $-50$ to $0$ deg.
                 % 
                 \textbf{Row 3 Panels:}
-                Applying the red astrometric and blue photometric selections, plotted
-                for astrometric coordinates $\phi_2, \varpi, \mu_{\phi_1}, \mu_{\phi_2}$.
+                Applying the combination of red astrometric and blue photometric selections,
+                plotted for astrometric coordinates $\phi_2, \varpi, \mu_{\phi_1}, \mu_{\phi_2}$.
+                The stream is an identifiable overdensity in all phase-space coordinates
+                except $\varpi$ where the errors are significant.
                 % 
@@
                 for the same astrometric coordinates as the above row.
+                In these coordinates the stream is clearly observable in $\phi_2$ and very
+                faintly in $\mu_{\phi_1}^*$.
             }
@@
             \caption{CAPTION}
+            \label{fig:gd1-results-full}
             TODO:
@@
             \end{itemize}
-            \label{fig:gd1-results-full}
         \end{figure*}

### 2023-08-30 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     grown extensively in the Milky Way thanks to all-sky astrometric missions
-    like {\it Gaia} and low-surface brightness photometric surveys (\JN{cite}).
+    like {\it Gaia} and low-surface brightness photometric surveys (e.g., \citealt{2018ApJ...862..114S, 2021ApJ...914..123I}).
     The formation of streams can be traced back to a progenitor cluster, whose stars are gradually lost to the
@@
     characterization of streams insofar as the available data allows.
-We do not rely on assumptions about the potential of the galaxy, and utilize mixture density nextworks to flexibly capture the qualities of a stream.
 

### 2023-08-31 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \section{Introduction} \label{sec:intro}
-    %
-    Stellar streams are the disrupted
-    remnants of globular clusters and satellite galaxies, and their census has
-    grown extensively in the Milky Way thanks to all-sky astrometric missions
-    like {\it Gaia} and low-surface brightness photometric surveys (e.g., \citealt{2018ApJ...862..114S, 2021ApJ...914..123I}).
-    The formation of streams can be traced back to a progenitor cluster, whose stars are gradually lost to the
-    tidal field of the host galaxy and extend along a series of similar orbits
-    producing tidal tails, which can sometimes span several tens of degrees across
-    the sky. The orbital proximity of stars belonging to a stream makes them
-    sensitive tracers of the mass distribution of galaxies, sourced by both the
-    baryonic and dark matter components.
+
+    Stellar streams are the disrupted remnants of globular clusters and
+    satellite galaxies, and their census has grown extensively in the Milky Way
+    thanks to all-sky astrometric missions like {\it Gaia} and low-surface
+    brightness photometric surveys (e.g., \citealt{2018ApJ...862..114S,
+    2021ApJ...914..123I}).  The formation of streams can be traced back to a
+    progenitor cluster, whose stars are gradually lost to the tidal field of the
+    host galaxy and extend along a series of similar orbits producing tidal
+    tails, which can sometimes span several tens of degrees across the sky. The
+    orbital proximity of stars belonging to a stream makes them sensitive
+    tracers of the mass distribution of galaxies, sourced by both the baryonic
+    and dark matter components.
 
@@
     (\JN{cite}). Importantly, these galactic components span orders of magnitude
-    in mass and spatial extent, highlighting the sensitivity of streams in constraining the structure of the galaxy.
+    in mass and spatial extent, highlighting the sensitivity of streams in
+    constraining the structure of the galaxy.
 
@@
     orientation;\JN{cite}) and local substructures (e.g., the bar's pattern
-    speed and the mass of subhalo perturbers; \JN{cite}), these methods often rely on the existence of a homogenized stream-tracer
-    population that characterizes a given stream across each of the observable
-    phase-space dimensions. Additionally, because even the fine-grain properties
-    of streams are influenced by the detailed mass distribution of its host galaxy, it
-    is important to propagate errors both in measurement uncertainty and
-    membership uncertainty (i.e., which stars belong to the stream versus the
-    background) when attempting to model a stream. Otherwise, a poorly characterized stream could bias constraints on (e.g.) the total
-    mass of the galaxy, the dark matter halo shape, and the mass of subhalo
-    perturbers. In order to generate more precise constraints on the structure
-    of the galaxy, it is therefore imperative that a statistically sound and
-    homogenized catalog of stellar streams is produced.
+    speed and the mass of subhalo perturbers; \JN{cite}), these methods often
+    rely on the existence of a homogenized stream-tracer population that
+    characterizes a given stream across each of the observable phase-space
+    dimensions. Additionally, because even the fine-grain properties of streams
+    are influenced by the detailed mass distribution of its host galaxy, it is
+    important to propagate errors both in measurement uncertainty and membership
+    uncertainty (i.e., which stars belong to the stream versus the background)
+    when attempting to model a stream. Otherwise, a poorly characterized stream
+    could bias constraints on (e.g.) the total mass of the galaxy, the dark
+    matter halo shape, and the mass of subhalo perturbers. In order to generate
+    more precise constraints on the structure of the galaxy, it is therefore
+    imperative that a statistically sound and homogenized catalog of stellar
+    streams is produced.
 
@@
     $N-$body simulations, these methods rely on prior assumptions about the
-    galaxy and its underlying gravitational potential. Therefore, it is necessary to devise
-    data-driven methods to characterize stellar streams without appealing to
-    strong prior assumptions about the galaxy's structure.
+    galaxy and its underlying gravitational potential. Therefore, it is
+    necessary to devise data-driven methods to characterize stellar streams
+    without appealing to strong prior assumptions about the galaxy's structure.
 
     There are a few previous works which have modeled stellar streams in this
-    context. \citet{Patrick+2022} developed a data-driven spline-based
-    method for modeling the photometric properties and on-sky positions of previously identified
-    streams. Their method works by fitting the stream's stellar surface density
-    with a series of splines, capturing both surface brightness variations along
-    the stream and changes in the position of the stream track and width. Their
-    method also utilize a simultaneous isochrone fit to a given stream, from which a
-    distance modulus can be derived. While this method is very
-    successful at characterizing the photometric properties of a stream, it does
-    not consider the kinematic dimensions which have become increasingly
+    context. \citet{Patrick+2022} developed a data-driven spline-based method
+    for modeling the photometric properties and on-sky positions of previously
+    identified streams. Their method works by fitting the stream's stellar
+    surface density with a series of splines, capturing both surface brightness
+    variations along the stream and changes in the position of the stream track
+    and width. Their method also utilize a simultaneous isochrone fit to a given
+    stream, from which a distance modulus can be derived. While this method is
+    very successful at characterizing the photometric properties of a stream, it
+    does not consider the kinematic dimensions which have become increasingly
     well-measured with successive data releases from {\it Gaia}, as well as
@@
     distances. The mixture modeling approach enables a simultaneous fit to both
-    the stream and background density, allowing for better separation of the stream from the background distribution. However, the track
-    of the stream in on-sky coordinates is not fit. The method identified 27 RR
-    Lyrae stars consistent with being members of the stream. While useful for
-    determining the average properties of a stream (e.g., its mean distance
-    track), a limited population of RR Lyrae stars are not sufficient to capture
-    the small-scale properties of streams expected to inform constraints on
-    (e.g.) a population of perturbers in the galaxy. \JN{are there other
-    methods?}
+    the stream and background density, allowing for better separation of the
+    stream from the background distribution. However, the track of the stream in
+    on-sky coordinates is not fit. The method identified 27 RR Lyrae stars
+    consistent with being members of the stream. While useful for determining
+    the average properties of a stream (e.g., its mean distance track), a
+    limited population of RR Lyrae stars are not sufficient to capture the
+    small-scale properties of streams expected to inform constraints on (e.g.) a
+    population of perturbers in the galaxy. \JN{are there other methods?}
 
@@
         progenitors are gravitationally bound systems, such as satellite dwarf
-        galaxies or star clusters \citep{Odenkirchen+2001, Majewski+2003}. In the
-        absence of external interactions these systems are stable, though still
-        capable of mass loss driven by internal processes \citep{Hills1975,
-        HeggieHut2003}, e.g. relaxation and binary interactions. Considering
-        external interactions, these progenitor systems may be disrupted:
-        completely, as in the merger events that formed the Galactic stellar
-        halo \citep{Lynden-Bell1967, SearleZinn1978}; or partially, such as tidal
-        disruption forming a stellar stream.
+        galaxies or star clusters \citep{Odenkirchen+2001, Majewski+2003}. In
+        the absence of external interactions these systems are stable, though
+        still capable of mass loss driven by internal processes
+        \citep{Hills1975, HeggieHut2003}, e.g. relaxation and binary
+        interactions. Considering external interactions, these progenitor
+        systems may be disrupted: completely, as in the merger events that
+        formed the Galactic stellar halo \citep{Lynden-Bell1967,
+        SearleZinn1978}; or partially, such as tidal disruption forming a
+        stellar stream.
 
@@
         saddle point of the combined potential -- e.g. the L2 and L3 Lagrange
-        points for a spherical galactic field \citep{Ross+1997, FukushigeHeggie2000,
-        BinneyTremaine2008}. Generally, the initial phase space position of the
-        escaped star is very similar to that of the progenitor: the
-        configuration position is the tidal boundary and the star has a low
-        peculiar velocity. Since both the escaped star and its progenitor orbit
-        in the same underlying galactic potential and have similar phase space
-        positions their orbits are similar \citep{BinneyTremaine2008}. Given
-        sufficient time the phase space separation will increase and an escaped
-        star will lead or trail the position of the progenitor, depending on the
-        location from which it escaped. Therefore, a collection of tidally
-        stripped stars will form extended structures, aka tails or streams, that
-        are few to thousands of parsecs in length \citep{Johnston1998,
-        HelmiWhite1999, Bovy2014}.
+        points for a spherical galactic field \citep{Ross+1997,
+        FukushigeHeggie2000, BinneyTremaine2008}. Generally, the initial phase
+        space position of the escaped star is very similar to that of the
+        progenitor: the configuration position is the tidal boundary and the
+        star has a low peculiar velocity. Since both the escaped star and its
+        progenitor orbit in the same underlying galactic potential and have
+        similar phase space positions their orbits are similar
+        \citep{BinneyTremaine2008}. Given sufficient time the phase space
+        separation will increase and an escaped star will lead or trail the
+        position of the progenitor, depending on the location from which it
+        escaped. Therefore, a collection of tidally stripped stars will form
+        extended structures, aka tails or streams, that are few to thousands of
+        parsecs in length \citep{Johnston1998, HelmiWhite1999, Bovy2014}.
 
@@
         dissimilar orbits from each other and the progenitor than do stars in
-        cold streams, with smaller dispersions \citep{Johnston1998, HendelJohnston2015}.
-        The orbit of a star depends on its phase space position and the
-        gravitational potential; therefore measuring a star's position and
-        velocity and observing its orbit reveals the local potential, which is
-        normally dominated by the Galaxy (primarily the dark matter halo at
-        large distances) \citep{Gibbons+2014}. However, an orbit is impractical
-        to observe on human timescales. Cold streams offer a workaround.  Like
-        measuring one star at many points in one orbit over an extended period,
-        streams are many stars measured at different points along approximately
-        one orbit at the same time. Therefore stellar streams are one of the
-        most promising means to study the Galactic gravitational potential: the
-        stellar components as well as the dark matter \citep{Johnston2016}.
+        cold streams, with smaller dispersions \citep{Johnston1998,
+        HendelJohnston2015}.  The orbit of a star depends on its phase space
+        position and the gravitational potential; therefore measuring a star's
+        position and velocity and observing its orbit reveals the local
+        potential, which is normally dominated by the Galaxy (primarily the dark
+        matter halo at large distances) \citep{Gibbons+2014}. However, an orbit
+        is impractical to observe on human timescales. Cold streams offer a
+        workaround.  Like measuring one star at many points in one orbit over an
+        extended period, streams are many stars measured at different points
+        along approximately one orbit at the same time. Therefore stellar
+        streams are one of the most promising means to study the Galactic
+        gravitational potential: the stellar components as well as the dark
+        matter \citep{Johnston2016}.
 
@@
 
-        This defines an astrometric phase-space hyper-tube
-        \cite{STREAMFINDER}, with a distribution radial to the track.
+        This defines an astrometric phase-space hyper-tube \cite{STREAMFINDER},
+        with a distribution radial to the track.
 
@@
         \begin{enumerate}
-            \item Streamfinder \citep{STREAMFINDER}. This method requires the potential
+            \item Streamfinder \citep{STREAMFINDER}. This method requires the
+            potential
             \item VIA MACHINAE \citep{Shih+2022}
@@
             \item Gaia stuff: Adrian and Ana and Sara et al
-            \item Uniform Modeling of 12 Stellar stream \citep{Patrick+2022}. Only on phi1, phi2, and CMD. Their CMD method is more sophisticated. Worth discussing.
+            \item Uniform Modeling of 12 Stellar stream \citep{Patrick+2022}.
+            Only on phi1, phi2, and CMD. Their CMD method is more sophisticated.
+            Worth discussing.
         \end{enumerate}
@@
     \begin{enumerate}
-        \item Gaia.
-Streams in Gaia have on-sky positions and proper motions, and parallaxes, though for most streams the parallax errors are prohibitively large.
-Likewise, most streams in Gaia do not have good radial velocity measurements.
-The photometry is generally poor, generally necessitating cross-matching with other datasets.
-        \item S5. This is a much smaller dataset. It has deeper photometry and radial velocity measurements.
+        \item Gaia. Streams in Gaia have on-sky positions and proper motions,
+        and parallaxes, though for most streams the parallax errors are
+        prohibitively large. Likewise, most streams in Gaia do not have good
+        radial velocity measurements. The photometry is generally poor,
+        generally necessitating cross-matching with other datasets.
+        \item S5. This is a much smaller dataset. It has deeper photometry and
+        radial velocity measurements.
     \end{enumerate}
@@
         our method for characterizing stream tracks and computing stellar
-        membership.  We discuss the data in \autoref{sub:method:framing_the_data} and
-        build a probabilistic framework to model the stream and background in
+        membership.  We discuss the data in
+        \autoref{sub:method:framing_the_data} and build a probabilistic
+        framework to model the stream and background in
         \autoref{sub:method:likelihood_setup}-\autoref{sub:methods:priors}.  In
@@
     overview of our approach, followed by a more in-depth technical explanation
-    in subsequent sections.  We start, in \autoref{sub:method:framing_the_data}, by
-    transforming the astrometric data into a stream-oriented on-sky reference
+    in subsequent sections.  We start, in \autoref{sub:method:framing_the_data},
+    by transforming the astrometric data into a stream-oriented on-sky reference
     frame ($\phi_1, \phi_2, \parallax, \mu_{\phi_1}^*, \mu_{\phi_2}, v_r)$, for
@@
         of dwarf galaxies, like the Magellanic stream which wraps multiple times
-        around the Milky Way \citep{WannierWrixon1972}, no such transformation is
-        possible. More generally, a stream's ``sky"-projected path may be
+        around the Milky Way \citep{WannierWrixon1972}, no such transformation
+        is possible. More generally, a stream's ``sky"-projected path may be
         kinked, e.g. by subhalo interactions, such that it is a many-to-one
@@
             \begin{enumerate}
-                \item remake this example this with \url{https://github.com/daft-dev/daft}. See \url{https://en.wikipedia.org/wiki/Mixture_model} for examples.
+                \item remake this example this with
+                \url{https://github.com/daft-dev/daft}. See
+                \url{https://en.wikipedia.org/wiki/Mixture_model} for examples.
             \end{enumerate}
@@
         \begin{equation}\label{eq:membership_prob}
-            \pdf\left(S | \nth{\mbs{w}}, \nth{\mbs{m}}, \mbs{\theta} \right) = \frac{f \Spdf(\nth{\mbs{w}}|\mbs{\theta}) \Spdf(\nth{\mbs{m}}|\mbs{\theta}) }{ \pdf(\nth{\mbs{w}}, \nth{\mbs{m}} | \mbs{\theta})}.
+            \pdf\left(S | \nth{\mbs{w}}, \nth{\mbs{m}}, \mbs{\theta} \right)
+            = \frac{f \Spdf(\nth{\mbs{w}}|\mbs{\theta}) \Spdf(\nth{\mbs{m}}|\mbs{\theta}) }{ \pdf(\nth{\mbs{w}}, \nth{\mbs{m}} | \mbs{\theta})}.
         \end{equation}
@@
 
-    \subsection{Missing Phase-Space Observations} \label{sub:method:missing_data}
+    \subsection{Missing Phase-Space Observations}
+    \label{sub:method:missing_data}
 
@@
         astrometrics as well as photometrics and chemical abundances available
-        \citep[e.g.,][]{Koposov+2019, Antoja+2020, Li+2022},
-        while most have partial coverage, lacking some feature dimensions.
+        \citep[e.g.,][]{Koposov+2019, Antoja+2020, Li+2022}, while most have
+        partial coverage, lacking some feature dimensions.
         % TODO: terminology ND-phase-space vs feature columns
@@
             the isochrone.
-            % FIXME! DO this Likewise, the dust map may be treated as a prior and it's errors incorporated into the data errors.
+            % FIXME! DO this Likewise, the dust map may be treated as a prior
+            % and it's errors incorporated into the data errors.
             However, stellar streams are generally poorly fit by theoretic
@@
             turnoff (MSTO). We include also a Kroupa initial mass function (IMF)
-            \citep{Kroupa2001}. The Kroupa IMF, and all
-            physically-motivated IMFs, have an much larger fraction of low-mass
-            stars then high-mass stars, the latter being less likely to form.
-            This is observed in streams, particularly their progenitors. However
-            the Kroupa IMF, and all IMF, are poor fits to the observed PDMF as
-            stream progenitors like globular clusters are extremely old
-            ($\sim10$ Gyr) while an IMF is the zero-age distribution.  How then
-            should the PDMF $\prior_{\cal{I}}$ be treated?
+            \citep{Kroupa2001}. The Kroupa IMF, and all physically-motivated
+            IMFs, have an much larger fraction of low-mass stars then high-mass
+            stars, the latter being less likely to form.  This is observed in
+            streams, particularly their progenitors. However the Kroupa IMF, and
+            all IMF, are poor fits to the observed PDMF as stream progenitors
+            like globular clusters are extremely old ($\sim10$ Gyr) while an IMF
+            is the zero-age distribution.  How then should the PDMF
+            $\prior_{\cal{I}}$ be treated?
             % ⬆ rephrase previous sentence
@@
             \end{align}
-            % TODO: should we show that these are different distance functions? or is it obvious
-            where $\delta$ is the Dirac delta function
-            \citep{Dirac1947}, and enforces that the distance modulus
-            track and parallax track must be equal (when converted to the actual
-            distance) as a function of $\phi_1$.  The widths are similarly
-            constrained. The distance and first-order error conversion are given
-            by
+            % TODO: should we show that these are different distance functions?
+            % or is it obvious
+            where $\delta$ is the Dirac delta function \citep{Dirac1947}, and
+            enforces that the distance modulus track and parallax track must be
+            equal (when converted to the actual distance) as a function of
+            $\phi_1$.  The widths are similarly constrained. The distance and
+            first-order error conversion are given by
             \begin{align}
@@
             it is a categorical, more informative priors like the Dirichlet
-            distribution \citep{Christopher2016} may be used.
-            Our code permits any user-defined prior, and we include $\mcal{U}(a,
-            b)$.  The default choice of prior and bounds $\mcal{U}$ set to the
-            limits of the dataset in each feature dimension.
+            distribution \citep{Christopher2016} may be used.  Our code permits
+            any user-defined prior, and we include $\mcal{U}(a, b)$.  The
+            default choice of prior and bounds $\mcal{U}$ set to the limits of
+            the dataset in each feature dimension.
             % ⬆ where should this sentence be?
@@
         MLP with a sequence of \texttt{Linear} \!\!\textrightarrow \texttt{Tanh}
-        \!\!\textrightarrow \texttt{Dropout} (hereafter \texttt{LinTanh}) blocks. This is illustrated in
-        \autoref{table:mlp_structure}.
+        \!\!\textrightarrow \texttt{Dropout} (hereafter \texttt{LinTanh})
+        blocks. This is illustrated in \autoref{table:mlp_structure}.
         % FIXME! reference not being picked up correctly.
@@
 
-        We generate synthetic stream observations by sampling uniformly in $\phi_1$
-        In $\phi_2$ we sample from a quadratic in $\phi_1$ with normally-distributed
-        $0.15^{\degree}$ scatter.  The distances are sampled from a linear funciton in
-        $\phi_1$ with normally-distributed $0.25 \ \unit{kpc}$ scatter, then
-        transformed to the parallax $\parallax$.  Non-poissonian density variations
-        are then simulated by evaluating the stream density with two Gaussian
-        distributions centered at different values of $\phi_1$ with random
-        amplitudes (which sum to $1$) and widths.  Stream stars are then removed
-        using random sampling, weighted by their likelihood of belonging to the
-        density. Post removal, the number of stream stars is
+        We generate synthetic stream observations by sampling uniformly in
+        $\phi_1$ In $\phi_2$ we sample from a quadratic in $\phi_1$ with
+        normally-distributed $0.15^{\degree}$ scatter.  The distances are
+        sampled from a linear funciton in $\phi_1$ with normally-distributed
+        $0.25 \ \unit{kpc}$ scatter, then transformed to the parallax
+        $\parallax$.  Non-poissonian density variations are then simulated by
+        evaluating the stream density with two Gaussian distributions centered
+        at different values of $\phi_1$ with random amplitudes (which sum to
+        $1$) and widths.  Stream stars are then removed using random sampling,
+        weighted by their likelihood of belonging to the density. Post removal,
+        the number of stream stars is
         $\variable{output/mock/nstream_variable.txt}$.
-        $\variable{output/mock/nbackground_variable.txt}$ background astrometric points
-        are generated from exponential distributions at each $\phi_1$.
+        $\variable{output/mock/nbackground_variable.txt}$ background astrometric
+        points are generated from exponential distributions at each $\phi_1$.
 
         The synthetic stream's photometry is also simulated using a
-        \variable{output/mock/isochrone_age_variable.txt},
-        [Fe/H] = \variable{output/mock/isochrone_feh_variable.txt} MIST isochrone
+        \variable{output/mock/isochrone_age_variable.txt}, [Fe/H] =
+        \variable{output/mock/isochrone_feh_variable.txt} MIST isochrone
         \citep{brutus, Dotter2016, Choi+2016}. The isochrone is truncated just
-        short of the giant branch, and is sampled from uniformly along the isochrone
-        (i.e., the initial mass function, $P(\gamma)$, is uniform) as well as with
-        an intrinsic uniform 0.2~dex scatter orthogonal to the isochrone track. The
-        isochrone is shifted by the stream's parallax modulus, which is derived from
-        the astrometric distance track.  The background photometric coordinates are
-        generated as a 2-dimensional Gaussian with non-zero covariance.  Thus, the
-        synthetic data scenario described here generates a mock stream in
-        astrometric coordinates and photometric coordinates, with density
-        variations, a distance gradient which is consistent in parallax and distance
-        modulus (i.e., magnitudes), all superimposed over a noisy field of
-        background points in each astrometric and photometric dimension.
+        short of the giant branch, and is sampled from uniformly along the
+        isochrone (i.e., the initial mass function, $P(\gamma)$, is uniform) as
+        well as with an intrinsic uniform 0.2~dex scatter orthogonal to the
+        isochrone track. The isochrone is shifted by the stream's parallax
+        modulus, which is derived from the astrometric distance track.  The
+        background photometric coordinates are generated as a 2-dimensional
+        Gaussian with non-zero covariance.  Thus, the synthetic data scenario
+        described here generates a mock stream in astrometric coordinates and
+        photometric coordinates, with density variations, a distance gradient
+        which is consistent in parallax and distance modulus (i.e., magnitudes),
+        all superimposed over a noisy field of background points in each
+        astrometric and photometric dimension.
 
@@
                 %
-                \textbf{Top panel:} Astrometric coordinates ($\phi_1$, $\phi_2$) for
-                the mock data set.  Light blue points are the stream and background
-                within an ``on"-stream region. Black points are in the ``off"-stream
-                region used to train the background photometric model.
+                \textbf{Top panel:} Astrometric coordinates ($\phi_1$, $\phi_2$)
+                for the mock data set.  Light blue points are the stream and
+                background within an ``on"-stream region. Black points are in
+                the ``off"-stream region used to train the background
+                photometric model.
                 %
-                \textbf{Bottom panel:} Astrometric coordinates ($\phi_1$, $\phi_2$)
-                for the mock data set.  Black points are in the ``off"-stream region
-                from the region defined in the astrometric coordinates.  Light blue
-                points are the stream and background from the on-stream region. The
-                stream's isochrone is apparent as an overdensity around (g-r,
-                g)$\approx (0, 20)$.  }
+                \textbf{Bottom panel:} Astrometric coordinates ($\phi_1$,
+                $\phi_2$) for the mock data set.  Black points are in the
+                ``off"-stream region from the region defined in the astrometric
+                coordinates.  Light blue points are the stream and background
+                from the on-stream region. The stream's isochrone is apparent as
+                an overdensity around (g-r, g)$\approx (0, 20)$.
+                %
+            }
             \label{fig:mock_data_photometric_background_selection}
@@
 
-        We select on-stream and off-stream regions using the known $\phi_1, \phi_2$
-        range of the mock stream.  The upper panel of
+        We select on-stream and off-stream regions using the known $\phi_1,
+        \phi_2$ range of the mock stream.  The upper panel of
         \autoref{fig:mock_data_photometric_background_selection} shows these
-        selections in blue and black, respectively.  The lower panel shows the on and
-        off-stream selections in photometric coordinates.  In this space it is
-        apparent that the on-stream region has two populations, drawn from the
-        isochrone and from background points included in the simple $\phi_1, \phi_2$
-        box.  In contrast the off-stream region, has only the the background population.
-        We use the off-stream population to train a conditional normalizing flow
-        (see \autoref{sub:method:photometric_model:off_stream}) on the magnitudes
-        $g$ and $r$ and conditioned on $\phi_1$.  The normalizing flow is now a
+        selections in blue and black, respectively.  The lower panel shows the
+        on and off-stream selections in photometric coordinates.  In this space
+        it is apparent that the on-stream region has two populations, drawn from
+        the isochrone and from background points included in the simple $\phi_1,
+        \phi_2$ box.  In contrast the off-stream region, has only the the
+        background population.  We use the off-stream population to train a
+        conditional normalizing flow (see
+        \autoref{sub:method:photometric_model:off_stream}) on the magnitudes $g$
+        and $r$ and conditioned on $\phi_1$.  The normalizing flow is now a
         non-parametric distribution characterizing the photometric background,
-        including its variation over $\phi_1$.  For this mock stream the flexibility
-        of the normalizing flow greatly exceeds necessity: the background is
-        drawn from a $\phi_1$-invariant multivariate normal, essentially the base
-        distribution of the normalizing flow.  It is therefore no surprise that
-        the trained normalizing flow provides an excellent characterization of
-        the background.  We will later see that the flow performs similarly well
-        on complex distributions.  Having trained the background photometric model
-        we proceed to build and train the full model.
+        including its variation over $\phi_1$.  For this mock stream the
+        flexibility of the normalizing flow greatly exceeds necessity: the
+        background is drawn from a $\phi_1$-invariant multivariate normal,
+        essentially the base distribution of the normalizing flow.  It is
+        therefore no surprise that the trained normalizing flow provides an
+        excellent characterization of the background.  We will later see that
+        the flow performs similarly well on complex distributions.  Having
+        trained the background photometric model we proceed to build and train
+        the full model.
 
         Per \autoref{eq:stream_and_bkg_prob} the stream is an independent
-        addition of both astrometric and photometric models.
-        In astrometrics the stream is a Gaussian track in $\phi_2$ and
-        parallax $\varpi$, using the model defined in
-        \autoref{ssub:method:astrometric_model:on_stream}. We use a 4-layer 
-        \texttt{LinTanh} with shape (1 input, 64 hidden, 4 output), where the 4 outputs
-        are $[\mu_{\phi_2}, \sigma_{\phi_2}, \mu_{\varpi}, \sigma_{\varpi}](\phi_1)$.
-        The network is small, but sufficiently large to permit 15\% dropout and retain
-        robust predictions.
-        The photometric model is a distance modulus-shifted isochrone, using the model
-        outlined in  \autoref{ssub:method:photometric_model:on_stream}. We use the
-        same isochrone parameters as were used to simulate the stream. For this mock
-        stream we demonstrate simultaneous astrometric and photometric modeling, linking
-        the distance modulus and parallax track, as explained in
-        \autoref{ssub:method:linking_to_astrometrics}. Thus the photometric model
-        does not have its own network, using instead the outputs
-        $[\mu_{\varpi}, \sigma_{\varpi}](\phi_1)$.
-
-        The total background model has two pieces, an astrometric and a photometric model.
-        As a pre-training phase the photometric normalizing flow model was fitted to
-        an off-stream selection and is now held fixed. The astrometric model
-        is split in two components, the first is a uniform distribution
-        in $\phi_2$, and the second is an exponential distribution for $\varpi$.
-        The uniform distribution does not have any parameters, and thus no neural network.
-        The exponential distribution has only the slope parameter and we use a 3-layer 
-        \texttt{LinTanh} with shape (1, 32, 1) and 15\% dropout. Background and
-        stream are combined in a mixture model whose mixture parameters are a 4-layer 
-        (1, 64, 1) \texttt{LinTanh} network. We train the mixture model with an
-        \texttt{AdamW} optimizer with learning rate of $5\times10^{-3}$ and a scheduler
-        to periodically and temporarily increase the learning rate, encouraging the optimizer
+        addition of both astrometric and photometric models.  In astrometrics
+        the stream is a Gaussian track in $\phi_2$ and parallax $\varpi$, using
+        the model defined in \autoref{ssub:method:astrometric_model:on_stream}.
+        We use a 4-layer \texttt{LinTanh} with shape (1 input, 64 hidden, 4
+        output), where the 4 outputs are $[\mu_{\phi_2}, \sigma_{\phi_2},
+        \mu_{\varpi}, \sigma_{\varpi}](\phi_1)$.  The network is small, but
+        sufficiently large to permit 15\% dropout and retain robust predictions.
+        The photometric model is a distance modulus-shifted isochrone, using the
+        model outlined in  \autoref{ssub:method:photometric_model:on_stream}. We
+        use the same isochrone parameters as were used to simulate the stream.
+        For this mock stream we demonstrate simultaneous astrometric and
+        photometric modeling, linking the distance modulus and parallax track,
+        as explained in \autoref{ssub:method:linking_to_astrometrics}. Thus the
+        photometric model does not have its own network, using instead the
+        outputs $[\mu_{\varpi}, \sigma_{\varpi}](\phi_1)$.
+
+        The total background model has two pieces, an astrometric and a
+        photometric model.  As a pre-training phase the photometric normalizing
+        flow model was fitted to an off-stream selection and is now held fixed.
+        The astrometric model is split in two components, the first is a uniform
+        distribution in $\phi_2$, and the second is an exponential distribution
+        for $\varpi$.  The uniform distribution does not have any parameters,
+        and thus no neural network.  The exponential distribution has only the
+        slope parameter and we use a 3-layer \texttt{LinTanh} with shape (1, 32,
+        1) and 15\% dropout. Background and stream are combined in a mixture
+        model whose mixture parameters are a 4-layer (1, 64, 1) \texttt{LinTanh}
+        network. We train the mixture model with an \texttt{AdamW} optimizer
+        with learning rate of $5\times10^{-3}$ and a scheduler to periodically
+        and temporarily increase the learning rate, encouraging the optimizer
         towards better minima.
@@
                 \textbf{Top panel: }%
-                    The stream mixture coefficient $f(\phi_1)$ (black dotted line)
-                    predicted by the model, overplotted on the true stream fraction
-                    (black-outlined histogram), calculated as the ratio of stream
-                    stars to total stars in 55 bins over the $\phi_1$ range of the
-                    isochrone.  \textbf{Middle panel: }%
-                    $\phi_2(\phi_1)$ over the full range of $\phi_1$. The data color
-                    and transparency is set by the model's MLE stream probability
-                    (with dropout turned off). Plotted behind the data are the true
-                    labels for the stream stars (large black circles).  The true
-                    labels exactly limn the model-identified stream stars.  The MLE
-                    stream track (black dashed line) is over-plotted on the
-                    probability-colored data.
+                    The stream mixture coefficient $f(\phi_1)$ (black dotted
+                    line) predicted by the model, overplotted on the true stream
+                    fraction (black-outlined histogram), calculated as the ratio
+                    of stream stars to total stars in 55 bins over the $\phi_1$
+                    range of the isochrone.  \textbf{Middle panel: }%
+                    $\phi_2(\phi_1)$ over the full range of $\phi_1$. The data
+                    color and transparency is set by the model's MLE stream
+                    probability (with dropout turned off). Plotted behind the
+                    data are the true labels for the stream stars (large black
+                    circles).  The true labels exactly limn the model-identified
+                    stream stars.  The MLE stream track (black dashed line) is
+                    over-plotted on the probability-colored data.
                 %
@@
                     probability, with the true labels (large black circles)
-                    under-plotted and MLE track (black dashed line) over-plotted.
+                    under-plotted and MLE track (black dashed line)
+                    over-plotted.
                 %
                 \textbf{Upper Histograms: }%
-                    $\phi_2$ histograms for each model component (blue background,
-                    red stream), in 4 $\phi_1$ ranges across the data set.  The
-                    height of each bin is the probability-weighted density.  The
-                    background is a uniform distribution, while the stream is a
-                    Gaussian. In projection across the $\phi_1$ range it can appear
-                    multi-modal (panel 2) if there are large gaps or `smeared' out
-                    (panel 3) if the Gaussian's mean changes significantly over the range.
+                    $\phi_2$ histograms for each model component (blue
+                    background, red stream), in 4 $\phi_1$ ranges across the
+                    data set.  The height of each bin is the
+                    probability-weighted density.  The background is a uniform
+                    distribution, while the stream is a Gaussian. In projection
+                    across the $\phi_1$ range it can appear multi-modal (panel
+                    2) if there are large gaps or `smeared' out (panel 3) if the
+                    Gaussian's mean changes significantly over the range.
                 %
@@
                     Parallax $\varpi$ histograms for each model component (blue
-                    background, red stream), in 4 $\phi_1$ ranges across the data
-                    set.  The height of each bin is the probability-weighted
-                    density.
+                    background, red stream), in 4 $\phi_1$ ranges across the
+                    data set.  The height of each bin is the
+                    probability-weighted density.
                 %
                 \textbf{Lower Middle and Lower Histograms:}%
-                    Photometric coordinate $(g, r)$ plots for each model component
-                    in 4 $\phi_1$ ranges across the data set. The top row plots the
-                    stream stars (red) over the background. The lower row plots the
-                    background stars (blue) over the stream stars to show that the
-                    how the two distributions mix.
+                    Photometric coordinate $(g, r)$ plots for each model
+                    component in 4 $\phi_1$ ranges across the data set. The top
+                    row plots the stream stars (red) over the background. The
+                    lower row plots the background stars (blue) over the stream
+                    stars to show that the how the two distributions mix.
                 %
@@
         weight parameter that controls membership probability as a function of
-        $\phi_1$. The dashed curve represents the output of our data-driven model,
-        while the solid curve is the ground truth. The second panel shows the stream
-        and background in the $(\phi_1,\phi_2)$ plane, and the third panel shows the
-        stream and background in the $(\phi_1,\parallax)$ plane. Points are
-        color-coded according to their membership probability
-        \autoref{eq:membership_prob}. The weight parameter clearly shows that the
-        model has captured the two prominent density variations along the stream.
-        There are additional variations, mostly around the edges of the stream, though
-        re-sampling the neural network weights with dropout reveals that these
-        variations represent regions of higher model uncertainty.
-
-        We find that the stream is successfully recovered in both astrometric and
-        photometric coordinates, with $\variable{output/mock/ncorrect_variable.txt}\%$ of stream
-        stars being recovered with membership probability greater than $80\%$.
-        In the bottom two rows of \autoref{fig:mock_data_result} we illustrate the
+        $\phi_1$. The dashed curve represents the output of our data-driven
+        model, while the solid curve is the ground truth. The second panel shows
+        the stream and background in the $(\phi_1,\phi_2)$ plane, and the third
+        panel shows the stream and background in the $(\phi_1,\parallax)$ plane.
+        Points are color-coded according to their membership probability
+        \autoref{eq:membership_prob}. The weight parameter clearly shows that
+        the model has captured the two prominent density variations along the
+        stream.  There are additional variations, mostly around the edges of the
+        stream, though re-sampling the neural network weights with dropout
+        reveals that these variations represent regions of higher model
+        uncertainty.
+
+        We find that the stream is successfully recovered in both astrometric
+        and photometric coordinates, with
+        $\variable{output/mock/ncorrect_variable.txt}\%$ of stream stars being
+        recovered with membership probability greater than $80\%$.  In the
+        bottom two rows of \autoref{fig:mock_data_result} we illustrate the
         synthetic data color-coded by stream membership probability (top) and
@@
         slices. Importantly, the photometric portion of the mixture model
-        successfully identifies the stream in magnitude space, showing a high stream
-        membership probability where the stream is present, and a low probability
-        ($\sim 0$) where the stream is absent.
-        The false positive rate (i.e., stars misidentified as stream members) for this test
-        is found to be $\variable{output/mock/falseident_variable.txt}\%$ (3 stars) when cutting on
-        the 80\% membership probability threshold.
-        % The perfect recovery rate and low false identification rate demonstrate the efficacy
-        % of this method.
+        successfully identifies the stream in magnitude space, showing a high
+        stream membership probability where the stream is present, and a low
+        probability ($\sim 0$) where the stream is absent.  The false positive
+        rate (i.e., stars misidentified as stream members) for this test is
+        found to be $\variable{output/mock/falseident_variable.txt}\%$ (3 stars)
+        when cutting on the 80\% membership probability threshold.
+        % The perfect recovery rate and low false identification rate
+        % demonstrate the efficacy of this method.
 
@@
 
-    Having successful applied the density modeling framework to a
-    mock stream, we now apply the method to the stellar stream GD-1.
+    Having successful applied the density modeling framework to a mock stream,
+    we now apply the method to the stellar stream GD-1.
     % TODO: some reiteration on the importance of GD-1
-    We discuss the data selection in \autoref{sub:results_gd1:data},
-    model specifics in \autoref{sub:results_gd1:model},
-    and the results in \autoref{sub:results_gd1:results}.
+    We discuss the data selection in \autoref{sub:results_gd1:data}, model
+    specifics in \autoref{sub:results_gd1:model}, and the results in
+    \autoref{sub:results_gd1:results}.
 
@@
 
-        We utilize data from \Gaia{} DR3 for the astrometric coordinates of
-        each star. 
-        To obtain more accurate color information, we cross-match the \Gaia{}
-        field on \PanStarrs{} \citep{PanSTARRS1} using 
-        \Gaia's provided \texttt{Best-neighbors} catalog.
-        To limit the field to a region known to contain \stream{GD-1} we adopt broad cuts
-        on the cross-matched data. We perform these rough cuts by requiring
-        the data lie within the phase-space cube:
+        We utilize data from \Gaia{} DR3 for the astrometric coordinates of each
+        star.  To obtain more accurate color information, we cross-match the
+        \Gaia{} field on \PanStarrs{} \citep{PanSTARRS1} using \Gaia's provided
+        \texttt{Best-neighbors} catalog.  To limit the field to a region known
+        to contain \stream{GD-1} we adopt broad cuts on the cross-matched data.
+        We perform these rough cuts by requiring the data lie within the
+        phase-space cube:
         \begin{itemize}
@@
         \end{itemize}
-        where, we use \package{gala}'s \citep{gala, galav1.3} \code{GD1Koposov10} frame
-        \citep{Koposov+2010} to define $\phi_1$, $\phi_2$, and associated proper motions.
-        For downloading purposes, we split the query into 10 sub-regions,
-        in even $\phi_1$ increments. A plot of the $\phi_1, \phi_2$ regions is included
-        in the \href{\GitHubURL{}}{\package{ShowYourWork}} repository.
-        Stream-specific coordinates ($\phi_1, \phi_2$) are not included in \Gaia.
-        One could embed the coordinate transform in the ADQL \citep{ADQL2.0},
-        or define great-circle arcs in ICRS \citep{ICRS1997}. Since only rough
-        cuts are required and since the sub-region boxes are sufficiently small for a reasonable flat-sky
-        approximation  we simply translate the ($\phi_1, \phi_2$) boxes to ICRS.
-        We correct the \PanStarrs{} photometry for dust extinction
-        using the \textit{Bayestar19} \citep{Green+2019} models in the \package{dustmaps} package \citep{Green2018}.
-        \textit{Bayestar19} is a three-dimensional dust map of the Milky Way
-        for which we use \Gaia's parallax distance information.
-        We include the $1-\sigma$ errors as a source of uncertainty
-        in $\mbs{\Sigma}_n$, the per-star photometric uncertainty.
+        where, we use \package{gala}'s \citep{gala, galav1.3}
+        \code{GD1Koposov10} frame \citep{Koposov+2010} to define $\phi_1$,
+        $\phi_2$, and associated proper motions.  For downloading purposes, we
+        split the query into 10 sub-regions, in even $\phi_1$ increments. A plot
+        of the $\phi_1, \phi_2$ regions is included in the
+        \href{\GitHubURL{}}{\package{ShowYourWork}} repository.  Stream-specific
+        coordinates ($\phi_1, \phi_2$) are not included in \Gaia.  One could
+        embed the coordinate transform in the ADQL \citep{ADQL2.0}, or define
+        great-circle arcs in ICRS \citep{ICRS1997}. Since only rough cuts are
+        required and since the sub-region boxes are sufficiently small for a
+        reasonable flat-sky approximation  we simply translate the ($\phi_1,
+        \phi_2$) boxes to ICRS.  We correct the \PanStarrs{} photometry for dust
+        extinction using the \textit{Bayestar19} \citep{Green+2019} models in
+        the \package{dustmaps} package \citep{Green2018}.  \textit{Bayestar19}
+        is a three-dimensional dust map of the Milky Way for which we use
+        \Gaia's parallax distance information.  We include the $1-\sigma$ errors
+        as a source of uncertainty in $\mbs{\Sigma}_n$, the per-star photometric
+        uncertainty.
         % TODO: actually implement that in the model
-        The result is a field populated by \variable{output/gd1/ndata_variable.txt} stars,
-        from which we would like to identify stream members.
+        The result is a field populated by
+        \variable{output/gd1/ndata_variable.txt} stars, from which we would like
+        to identify stream members.
 
         We create data masks for a more refined selection around \stream{GD-1}.
-        The two mask types, proper motion and photometric,
-        are show in \autoref{fig:gd1-data_selection}.
-        The proper motion masks select rectangular regions, containing the primary overdensity
-        of \stream{GD-1} and a surrounding area following the tail of the distribution.
-        The tighter mask (red) has corners $(\mu_{\phi_1}, \mu_{\phi_2}) = [(-15,-10) (-4.5, -2)] \ \unit{mas/yr}$, while the larger mask (yellow) has $(\mu_{\phi_1}, \mu_{\phi_2}) = [(-15,-5) (-5, -1)] \ \unit{mas/yr}$.
-        In photometric coordinates we define a mask around
+        The two mask types, proper motion and photometric, are show in
+        \autoref{fig:gd1-data_selection}.  The proper motion masks select
+        rectangular regions, containing the primary overdensity of \stream{GD-1}
+        and a surrounding area following the tail of the distribution.  The
+        tighter mask (red) has corners $(\mu_{\phi_1}, \mu_{\phi_2}) =
+        [(-15,-10) (-4.5, -2)] \ \unit{mas/yr}$, while the larger mask (yellow)
+        has $(\mu_{\phi_1}, \mu_{\phi_2}) = [(-15,-5) (-5, -1)] \
+        \unit{mas/yr}$.  In photometric coordinates we define a mask around
         % TODO: make these variables, like in mock
-        a 12 Gyr, [Fe/H] = -1.3 isochrone at a distance of 7.8 kpc. The selection region is a 0.2 dex orthogonal buffer around the MIST isochrone \citep[using]{brutus}, which
-        is illustrated in the 2nd-from-the-top-left plot in \autoref{fig:gd1-data_selection}.
-        In addition, to avoid detailed modeling of the completeness as a term in $\prior_{obs}$ (from \autoref{isochrone_prior_components}) we mask out photometry with $G_{\Gaia{}} > 20$.
-        With combinations of these masks the stream has much larger signal-to-noise, though
-        is still only a small percent of the total data.
+        a 12 Gyr, [Fe/H] = -1.3 isochrone at a distance of 7.8 kpc. The
+        selection region is a 0.2 dex orthogonal buffer around the MIST
+        isochrone \citep[using]{brutus}, which is illustrated in the
+        2nd-from-the-top-left plot in \autoref{fig:gd1-data_selection}.  In
+        addition, to avoid detailed modeling of the completeness as a term in
+        $\prior_{obs}$ (from \autoref{isochrone_prior_components}) we mask out
+        photometry with $G_{\Gaia{}} > 20$.  With combinations of these masks
+        the stream has much larger signal-to-noise, though is still only a small
+        percent of the total data.
 
@@
             \caption{%
-                Data selections for \stream{GD-1}, within the data cube described
-                in \autoref{sub:results_gd1:data}.
+                Data selections for \stream{GD-1}, within the data cube
+                described in \autoref{sub:results_gd1:data}.
                 %
                 \textbf{Row 1 Panels:}
-                Proper motion selection boxes in red and yellow.
-                The right plot shows the application of these selections.
-                \stream{GD-1} is apparent from around $-60$ to $-10$ deg in the red
-                selection and present, if less clearly, in the yellow selection.
+                Proper motion selection boxes in red and yellow.  The right plot
+                shows the application of these selections.  \stream{GD-1} is
+                apparent from around $-60$ to $-10$ deg in the red selection and
+                present, if less clearly, in the yellow selection.
                 %
                 \textbf{Row 2 Panels:}
-                Photometric selection (blue curve). The selection is based on
-                a 12 Gyr, [Fe/H] = -1.3 MIST isochrone, buffered by 0.2 dex.
-                The right plot shows the application of this selection. By eye, the stream
-                is a small overdensity extending from $-50$ to $0$ deg.
+                Photometric selection (blue curve). The selection is based on a
+                12 Gyr, [Fe/H] = -1.3 MIST isochrone, buffered by 0.2 dex.  The
+                right plot shows the application of this selection. By eye, the
+                stream is a small overdensity extending from $-50$ to $0$ deg.
                 %
                 \textbf{Row 3 Panels:}
-                Applying the combination of red astrometric and blue photometric selections,
-                plotted for astrometric coordinates $\phi_2, \varpi, \mu_{\phi_1}, \mu_{\phi_2}$.
-                The stream is an identifiable overdensity in all phase-space coordinates
-                except $\varpi$ where the errors are significant.
+                Applying the combination of red astrometric and blue photometric
+                selections, plotted for astrometric coordinates $\phi_2, \varpi,
+                \mu_{\phi_1}, \mu_{\phi_2}$.  The stream is an identifiable
+                overdensity in all phase-space coordinates except $\varpi$ where
+                the errors are significant.
                 %
                 \textbf{Row 4 Panels:}
-                Applying the yellow astrometric and blue photometric selections, plotted
-                for the same astrometric coordinates as the above row.
-                In these coordinates the stream is clearly observable in $\phi_2$ and very
-                faintly in $\mu_{\phi_1}^*$.
-            }
+                Applying the yellow astrometric and blue photometric selections,
+                plotted for the same astrometric coordinates as the above row.
+                In these coordinates the stream is clearly observable in
+                $\phi_2$ and very faintly in $\mu_{\phi_1}^*$.  }
             \label{fig:gd1-data_selection}
@@
         \todo[inline]{rephrase, this is quoting from the mock stream}
-        We select on-stream and off-stream regions using the known $\phi_1,\phi_2$ range
-        of the stream. The upper panel of \autoref{fig:gd1-photometric_background_selection}
-        shows these selections in blue and black, respectively.
-        The lower panel shows the on and off-stream selections in photometric
-        coordinates. An isochrone is apparent in the distribution.
-        We use the off-stream population to train a
-        conditional normalizing flow (see \autoref{sub:method:photometric_model:off_stream})
-        on the magnitudes $g$ and $r$ and conditioned on $\phi_1$.
-        The normalizing flow is now a non-parametric distribution characterizing
-        the photometric background, including its variation over $\phi_1$.
+        We select on-stream and off-stream regions using the known
+        $\phi_1,\phi_2$ range of the stream. The upper panel of
+        \autoref{fig:gd1-photometric_background_selection} shows these
+        selections in blue and black, respectively.  The lower panel shows the
+        on and off-stream selections in photometric coordinates. An isochrone is
+        apparent in the distribution.  We use the off-stream population to train
+        a conditional normalizing flow (see
+        \autoref{sub:method:photometric_model:off_stream}) on the magnitudes $g$
+        and $r$ and conditioned on $\phi_1$.  The normalizing flow is now a
+        non-parametric distribution characterizing the photometric background,
+        including its variation over $\phi_1$.
 
@@
         \todo[inline]{rephrase }
-        Per \autoref{eq:stream_and_bkg_prob} the stream is an independent addition
-        of both astrometric and photometric models.
-        In astrometrics the stream is a Gaussian track in $\phi_2, \mu_{\phi_1}, \mu_{\phi_2}$
-        using the model defined in \autoref{ssub:method:astrometric_model:on_stream}.
-        We use a 4-layer \texttt{LinTanh} with shape (1, 128, 6), where the 6 outputs
-        are $[\mu_{\phi_2}, \sigma_{\phi_2}, \mu_{\mu_{\phi_1}^*}, \sigma_{\mu_{\phi_1}^*}, \mu_{\mu_{\phi_2}}, \sigma_{\mu_{\phi_2}}](\phi_1)$. The network
-        is small, but sufficiently large to permit 15\% dropout and retain robust
-        predictions. The photometric model is a distance modulus-shifted isochrone,
-        using the model outlined in \autoref{ssub:method:photometric_model:on_stream}.
-        We use the same isochrone parameters used in the photometric selection.
+        Per \autoref{eq:stream_and_bkg_prob} the stream is an independent
+        addition of both astrometric and photometric models.  In astrometrics
+        the stream is a Gaussian track in $\phi_2, \mu_{\phi_1}, \mu_{\phi_2}$
+        using the model defined in
+        \autoref{ssub:method:astrometric_model:on_stream}.  We use a 4-layer
+        \texttt{LinTanh} with shape (1, 128, 6), where the 6 outputs are
+        $[\mu_{\phi_2}, \sigma_{\phi_2}, \mu_{\mu_{\phi_1}^*},
+        \sigma_{\mu_{\phi_1}^*}, \mu_{\mu_{\phi_2}},
+        \sigma_{\mu_{\phi_2}}](\phi_1)$. The network is small, but sufficiently
+        large to permit 15\% dropout and retain robust predictions. The
+        photometric model is a distance modulus-shifted isochrone, using the
+        model outlined in \autoref{ssub:method:photometric_model:on_stream}.  We
+        use the same isochrone parameters used in the photometric selection.
         The photometric model has its own network.
 
-        In order to guide our model towards
-        GD-1, we set down 4 ``control points" along GD-1's main track, and 3
-        control points along the spur (illustrated in \TODO{x}). These control
-        points act as Gaussian priors on the model. We set the Gaussian error on
-        these control points to large values, so that their influence on the
-        model is not dominant. Indeed, we find that the value of the control
-        points is to help reduce training time, since otherwise it will take the
-        flexible density model longer time to converge to the actual stream.
-
-        We also add 3 control points in the distance modulus.
-        We draw the points from \TODO{[cite]} and add significant width.
+        In order to guide our model towards GD-1, we set down 4 ``control
+        points" along GD-1's main track, and 3 control points along the spur
+        (illustrated in \TODO{x}). These control points act as Gaussian priors
+        on the model. We set the Gaussian error on these control points to large
+        values, so that their influence on the model is not dominant. Indeed, we
+        find that the value of the control points is to help reduce training
+        time, since otherwise it will take the flexible density model longer
+        time to converge to the actual stream.
+
+        We also add 3 control points in the distance modulus.  We draw the
+        points from \TODO{[cite]} and add significant width.
 
@@
 
-        The weight parameter is also set to truncate to $0$ at $\phi_1 < X$
-        and $\phi_1 > Y$. This ensures that we do not model stream stars that fall.
+        The weight parameter is also set to truncate to $0$ at $\phi_1 < X$ and
+        $\phi_1 > Y$. This ensures that we do not model stream stars that fall.
 
@@
 
-        \subsubsection[Uniform Modeling of 13 Stellar Streams]{\cite{Patrick+2022}}
+        \subsubsection[Uniform Modeling of 13 Stellar
+        Streams]{\cite{Patrick+2022}}
 
@@
 
-    The data availability statement is modified from one provided to ShowYourWork by Mathieu Renzo.
+    The data availability statement is modified from one provided to
+    ShowYourWork by Mathieu Renzo.
 
@@
 
-        \package{asdf} \citep{Greenfield+2015},
-        \package{astropy} \citep{Astropy2013, Astropy2018, Astropy2022},
-        \package{astroquery} \citep{Astroquery2019},
-        \package{Matplotlib} \citep{Hunter2007},
-        \package{NumPy} \citep{Harris+2020},
-        \package{Pytorch} \citep{Pytorch2019},
-        \package{SciPy} \citep{Scipy2020},
+        \package{asdf} \citep{Greenfield+2015}, \package{astropy}
+        \citep{Astropy2013, Astropy2018, Astropy2022}, \package{astroquery}
+        \citep{Astroquery2019}, \package{Matplotlib} \citep{Hunter2007},
+        \package{NumPy} \citep{Harris+2020}, \package{Pytorch}
+        \citep{Pytorch2019}, \package{SciPy} \citep{Scipy2020},
         \package{ShowYourWork} \citep{}
@@
     \href{https://github.com/showyourwork/showyourwork}{\showyourwork}
-    \citep{Luger+2021}, which uses continuous integration to
-    programmatically download the data, perform the analyses, create the
-    figures, and compile the manuscript. Each figure caption contains two links:
-    one to the dataset used in the corresponding figure, and the other to the
-    script used to make the figure. The datasets are stored at
-    \todo[inline]{zenodo url}. The git repository associated
-    with this study is publicly available at $\GitHubURL{}$.
+    \citep{Luger+2021}, which uses continuous integration to programmatically
+    download the data, perform the analyses, create the figures, and compile the
+    manuscript. Each figure caption contains two links: one to the dataset used
+    in the corresponding figure, and the other to the script used to make the
+    figure. The datasets are stored at \todo[inline]{zenodo url}. The git
+    repository associated with this study is publicly available at
+    $\GitHubURL{}$.
 
@@
 
-    We use $\tilde{F}$ to indicate that there a missing features, e.g. radial velocities.
-    The index set $\mbs{I}_F \mapsto \mbs{I}_{\tilde{F}} = \{1, ..., k-1, k+1, ... \}$ where $k$ is the index of the missing feature.
+    We use $\tilde{F}$ to indicate that there a missing features, e.g. radial
+    velocities.  The index set $\mbs{I}_F \mapsto \mbs{I}_{\tilde{F}} = \{1,
+    ..., k-1, k+1, ... \}$ where $k$ is the index of the missing feature.
 
@@
 
-% \section{Theory of Mixture Density Networks (MDNs)} \label{app:theory_of_mixture_density_networks}
-
-%     Mixture models (MMs) are a statistical method to represent a population as a set of a sub-populations specified by probability distributions.
-These distributions are characterized by their parameters and mixture by a corresponding set of mixture weights.
-Mixture Density Networks (MDNs)
-%     are a machine learning method to combine a MM with neural networks, increasing the flexibility of the model.
-An MDN replaces the scalar distribution parameters of the MM with neural networks, allowing the distribution parameters and mixture weights to vary as smooth functions \citep{Bishop1994}.
-Functional parameters allows the model to capture variation over those parameters that is not possible with scalar-valued models.
-Moreover, by using neural networks the inferred functional forms are ``model-free" and driven entirely by the data.
-
-%     % Quote from https://mikedusenberry.com/mixture-density-networks
-%     % A mixture density network (MDN) is an interesting model formalism built within the general framework of neural networks and probability theory for working on supervised learning problems in which the target variable cannot be easily approximated by a single standard probability distribution.
-Essentially an MDN allows one to model a conditional probability distribution as a mixture of distributions, in which the individual distributions and the corresponding mixture coefficients are parameterized by functions of the inputs
-
-%     For the MDN we take $x_{\cdot, 0} \equiv x_{\cdot}$ (indexed from 0), which is the first feature column of $\mbf{X}$, as the `independent' coordinate over which the MDN parameters are conditioned.
-In the context of streams $x_{\cdot, 0} \equiv \phi_1$ is the longitude coordinate in a reference frame rotated such that the stream is aligned along $\phi_1$.
+% \section{Theory of Mixture Density Networks (MDNs)}
+% \label{app:theory_of_mixture_density_networks}
+
+%     Mixture models (MMs) are a statistical method to represent a population as
+%     a set of a sub-populations specified by probability distributions. These
+%     distributions are characterized by their parameters and mixture by a
+%     corresponding set of mixture weights. Mixture Density Networks (MDNs) are
+%     a machine learning method to combine a MM with neural networks, increasing
+%     the flexibility of the model. An MDN replaces the scalar distribution
+%     parameters of the MM with neural networks, allowing the distribution
+%     parameters and mixture weights to vary as smooth functions
+%     \citep{Bishop1994}. Functional parameters allows the model to capture
+%     variation over those parameters that is not possible with scalar-valued
+%     models. Moreover, by using neural networks the inferred functional forms
+%     are ``model-free" and driven entirely by the data.
+
+%     % Quote from https://mikedusenberry.com/mixture-density-networks % A
+%     mixture density network (MDN) is an interesting model formalism built
+%     within the general framework of neural networks and probability theory for
+%     working on supervised learning problems in which the target variable
+%     cannot be easily approximated by a single standard probability
+%     distribution. Essentially an MDN allows one to model a conditional
+%     probability distribution as a mixture of distributions, in which the
+%     individual distributions and the corresponding mixture coefficients are
+%     parameterized by functions of the inputs
+
+%     For the MDN we take $x_{\cdot, 0} \equiv x_{\cdot}$ (indexed from 0),
+%     which is the first feature column of $\mbf{X}$, as the `independent'
+%     coordinate over which the MDN parameters are conditioned. In the context
+%     of streams $x_{\cdot, 0} \equiv \phi_1$ is the longitude coordinate in a
+%     reference frame rotated such that the stream is aligned along $\phi_1$.
 
@@
 
-%     \begin{equation} \label{eq:general_mixture_network}
-%         \pdf(\nth{\mbs{x}} | \mbs{\theta}(\phi_1))
-%         = \sum_{\mrm{q} \in \mbs{I_Q}} \ \qth{f}(\phi_1) \qth{P}(\nth{x}|\qth{\mbs{\theta}}(\phi_1),q\!=\!\mrm{q})
+%     \begin{equation} \label{eq:general_mixture_network} \pdf(\nth{\mbs{x}} |
+%         \mbs{\theta}(\phi_1)) = \sum_{\mrm{q} \in \mbs{I_Q}} \ \qth{f}(\phi_1)
+%         \qth{P}(\nth{x}|\qth{\mbs{\theta}}(\phi_1),q\!=\!\mrm{q})
+%         \end{equation} The mixture coefficients $\qth{f}$ are normalized s.t.
+%         \begin{equation} \sum_{\mrm{q}} \qth{f}(\phi_1) = 1 \qquad \forall
+%         \phi_1 \end{equation} In practice this is enforced by defining
+%         \begin{equation} f_{b}(\phi_1) = 1 - \sum_{\rm{q}\in
+%         \mbs{I_Q}\backslash b} \qth{f}(\phi_1) \end{equation} for some
+%         ``background" index $b \in \mbs{I_Q}$.
+
+%     Assuming the measurement of each datum is independent, the likelihood is a
+%     sum over all data: \begin{equation} \mcal{L}\left(\mbf{x}_n |
+%     \mbs{\theta}(\phi_1)\right) = \sum_{q\in\mbs{I_Q}}
+%     \qth{P}\left(\nth{\mbs{x}} | \qth{\mbs{\theta}}(\phi_1)\right).
 %     \end{equation}
-%     The mixture coefficients $\qth{f}$ are normalized s.t.
-%     \begin{equation}
-%         \sum_{\mrm{q}} \qth{f}(\phi_1) = 1 \qquad \forall \phi_1
-%     \end{equation}
-%     In practice this is enforced by defining
-%     \begin{equation}
-%         f_{b}(\phi_1) = 1 - \sum_{\rm{q}\in \mbs{I_Q}\backslash b} \qth{f}(\phi_1)
-%     \end{equation}
-%     for some ``background" index $b \in \mbs{I_Q}$.
-
-%     Assuming the measurement of each datum is independent, the likelihood is a sum over all data:
-%     \begin{equation}
-%         \mcal{L}\left(\mbf{x}_n | \mbs{\theta}(\phi_1)\right) = \sum_{q\in\mbs{I_Q}} \qth{P}\left(\nth{\mbs{x}} | \qth{\mbs{\theta}}(\phi_1)\right).
-%     \end{equation}
 
@@
 
-%     \begin{equation}
-%         \ln\posterior\left(\mbf{X} | \mbs{\theta}(\mbs{x})\right) = \ln\mcal{L}\left(\mbf{X} | \mbs{\theta}(\mbs{x})\right) +  \sum_{n \in \mbs{I_N}} \ln \left[ \sum_{q\in\mbs{I_Q}} \qth{\prior}\left(\qth{\mbs{\theta}}(\mbf{x}_n)\right) \right].
+%     \begin{equation} \ln\posterior\left(\mbf{X} | \mbs{\theta}(\mbs{x})\right)
+%         = \ln\mcal{L}\left(\mbf{X} | \mbs{\theta}(\mbs{x})\right) +  \sum_{n
+%         \in \mbs{I_N}} \ln \left[ \sum_{q\in\mbs{I_Q}}
+%         \qth{\prior}\left(\qth{\mbs{\theta}}(\mbf{x}_n)\right) \right].
 %         \end{equation}
@@
         \end{equation}
-        We rewrite $\tilde\sigma^2 = \sigma^2 + \sigma_*^2$, and $\tilde{\sigma} \tilde{\delta} = \sigma \delta$.
+        We rewrite $\tilde\sigma^2 = \sigma^2 + \sigma_*^2$, and $\tilde{\sigma}
+        \tilde{\delta} = \sigma \delta$.
 
@@
         \end{equation}
-        where $\tilde\sigma^2 = \sigma^2 + \sigma_*^2$ and $\tilde{\alpha} = \frac{\tilde{\delta}}{\sqrt{1-\tilde{\delta}^2}}$, $\tilde{\delta} = \frac{\sigma}{\tilde{\sigma}}\delta$.
+        where $\tilde\sigma^2 = \sigma^2 + \sigma_*^2$ and $\tilde{\alpha} =
+        \frac{\tilde{\delta}}{\sqrt{1-\tilde{\delta}^2}}$, $\tilde{\delta} =
+        \frac{\sigma}{\tilde{\sigma}}\delta$.
 
@@
 
-% \section{Plots} \label{app:developing_plots}
-
-%     \begin{figure*}
-%         \centering
-%         \includegraphics[scale=0.7]{figures-not-syw/gd1/tot_stream_and_spur_prob.png}
-%         \caption{Caption}
-%         \label{fig:gd1-astrometrics}
-%     \end{figure*}
-
-%     \begin{figure*}
-%         \centering
-%         \includegraphics[scale=0.8]{figures-not-syw/gd1/Unknown.png}
-%         \caption{Caption}
-%         \label{fig:gd1-distance_modulus}
-%     \end{figure*}
-
-%     \begin{figure}
-%         \centering
-%         \includegraphics[scale=0.6]{figures-not-syw/gd1/Unknown-2.png}
-%         \caption{Caption}
-%         \label{fig:gd1-cmd}
-%     \end{figure}
-
-%     \begin{figure*}
-%         \centering
-%         \includegraphics[scale=0.6]{figures-not-syw/gd1/Unknown-4.png}
-%         \caption{Caption}
-%         \label{fig:gd1-cmds}
-%     \end{figure*}
-
 \end{document}

### 2023-08-31 src/tex/ms.tex
[showyourwork] overleaf sync

@@
         \href{https://github.com/showyourwork/showyourwork}{\package{showyourwork}}
-        in a public repository at $\GitHubURL{}$. We will describe for each
+        in a public repository at \GitHubURL{}. We will describe for each
         stream model specifics relevant to that stream but refer readers to the
@@
         \end{itemize}
-        where, we use \package{gala}'s \citep{gala, galav1.3}
+        where we use \package{gala}'s \citep{gala, galav1.3}
         \code{GD1Koposov10} frame \citep{Koposov+2010} to define $\phi_1$,
-        $\phi_2$, and associated proper motions.  For downloading purposes, we
-        split the query into 10 sub-regions, in even $\phi_1$ increments. A plot
+        $\phi_2$, and associated proper motions.  For downloading purposes we
+        split the query into 10 sub-regions in even $\phi_1$ increments. A plot
         of the $\phi_1, \phi_2$ regions is included in the

### 2023-08-31 src/tex/ms.tex
[showyourwork] overleaf sync

@@
         \href{https://github.com/showyourwork/showyourwork}{\package{showyourwork}}
-        in a public repository at \GitHubURL{}. We will describe for each
+        in a public repository at \url{\GitHubURL{}}. We will describe for each
         stream model specifics relevant to that stream but refer readers to the
@@
 
-    \subsection{Model Specification} \label{sub:resultes_mock:model}
+    \subsection{Model Specification} \label{sub:results_mock:model}
 
@@
 
+        \autoref{sec:results_mock:model}
+
         \todo[inline]{rephrase, this is quoting from the mock stream}

### 2023-08-31 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-        \autoref{sec:results_mock:model}
-
-        \todo[inline]{rephrase, this is quoting from the mock stream}
-        We select on-stream and off-stream regions using the known
-        $\phi_1,\phi_2$ range of the stream. The upper panel of
-        \autoref{fig:gd1-photometric_background_selection} shows these
-        selections in blue and black, respectively.  The lower panel shows the
-        on and off-stream selections in photometric coordinates. An isochrone is
-        apparent in the distribution.  We use the off-stream population to train
-        a conditional normalizing flow (see
-        \autoref{sub:method:photometric_model:off_stream}) on the magnitudes $g$
-        and $r$ and conditioned on $\phi_1$.  The normalizing flow is now a
-        non-parametric distribution characterizing the photometric background,
-        including its variation over $\phi_1$.
+        The modeling framework, detailed in the \autoref{sec:method} sections, is
+        modular, allowing many model components to be combined, nested, added
+        to the mixture, and linked via priors.
+        The model we require for \stream{GD-1} is similar to 
+        the model built for the mock stream in \autoref{sec:results_mock:model},
+        but has additional components for \stream{GD-1}'s spur.
+        In this section we will discuss how the total model is built, noting 
+        similarities to the example mocks-stream model.
+
+        All full Bayesian stream models necessarily include a background model,
+        which we model in both astrometric and photometric spaces.
+        The photometric background is too complex to capture with simple analytic
+        distributions. Instead, we train a normalizing flow on the magnitudes $g, r$,
+        conditioned on $\phi_1$. We refer readers to
+        \autoref{sub:method:photometric_model:off_stream} for discussion of the photometric distribution and how a normalizing flow
+        can characterize this complex distribution, including its variation over $\phi_1$.
+        The flow's flexibility, while necessary in this context, also poses
+        a problem: the flow captures the stream as easily as the background.
+        Consequently we select on-stream and off-stream regions using the known
+        $\phi_1,\phi_2$ range of the stream, as shown in the
+        upper panel of \autoref{fig:gd1-photometric_background_selection}.
+        In the lower panel are plotted these selections in photometric coordinates,
+        where an isochrone is apparent in the on-stream selection.
+        The normalizing flow is trained on the off-stream selection, and will be
+        fixed when incorporated into the larger model.
+
+        One part of the larger model is the astrometric component of the background.
+        Unlike for the photometry, the background may be fit with simple analytic
+        distributions. We use an exponential distribution (see \autoref{sub:exponential_distribution})
 

### 2023-08-31 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-    We would like to thank the Academy.
+    NS acknowledges support from the Natural Sciences and Engineering Research
+    Council of Canada (NSERC) - Canadian Graduate Scholarships Doctorate Program
+    [funding reference number 547219 - 2020].  NS received partial support from
+    NSERC (funding reference number RGPIN-2020-04712) and from an Ontario Early
+    Researcher Award (ER16-12-061; PI Bovy). NS would also like thank Prof. Webb
+    for providing computational resources and travel funding.
+
+    \JN{TODO}
 
@@
 
-        \package{asdf} \citep{Greenfield+2015}, \package{astropy}
-        \citep{Astropy2013, Astropy2018, Astropy2022}, \package{astroquery}
-        \citep{Astroquery2019}, \package{Matplotlib} \citep{Hunter2007},
-        \package{NumPy} \citep{Harris+2020}, \package{Pytorch}
-        \citep{Pytorch2019}, \package{SciPy} \citep{Scipy2020},
-        \package{ShowYourWork} \citep{}
+        \package{asdf} \citep{Greenfield+2015},%
+        \package{astropy} \citep{Astropy2013, Astropy2018, Astropy2022},%
+        \package{astroquery} \citep{Astroquery2019},%
+        \package{Matplotlib} \citep{Hunter2007},%
+        \package{NumPy} \citep{Harris+2020},%
+        \package{Pytorch} \citep{Pytorch2019},%
+        \package{SciPy} \citep{Scipy2020},%
+        \package{ShowYourWork} \citep{Luger2021}%
 

### 2023-09-06 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \renewcommand{\equationautorefname}{Eq.}
-\renewcommand{\tableautorefname}{Tab.}
+\renewcommand{\tableautorefname}{Table}
 
@@
 
-    \begin{quotation}
-
-        A stellar stream is the association of stars tidally stripped from a
-        common progenitor system that orbits in an underlying galactic
-        gravitational field \citep{Johnston1998, HelmiWhite1999}. Stream
-        progenitors are gravitationally bound systems, such as satellite dwarf
-        galaxies or star clusters \citep{Odenkirchen+2001, Majewski+2003}. In
-        the absence of external interactions these systems are stable, though
-        still capable of mass loss driven by internal processes
-        \citep{Hills1975, HeggieHut2003}, e.g. relaxation and binary
-        interactions. Considering external interactions, these progenitor
-        systems may be disrupted: completely, as in the merger events that
-        formed the Galactic stellar halo \citep{Lynden-Bell1967,
-        SearleZinn1978}; or partially, such as tidal disruption forming a
-        stellar stream.
-
-        In the approximation of a smooth galactic gravitational field, the
-        progenitor's extent is limited to the tidal radius. Through processes
-        internal and external, progenitor stars can achieve sufficient energy to
-        bring them beyond the tidal boundary, thus ``escaping'' into the
-        galactic field. Escape primarily occurs at both an inner and outer
-        saddle point of the combined potential -- e.g. the L2 and L3 Lagrange
-        points for a spherical galactic field \citep{Ross+1997,
-        FukushigeHeggie2000, BinneyTremaine2008}. Generally, the initial phase
-        space position of the escaped star is very similar to that of the
-        progenitor: the configuration position is the tidal boundary and the
-        star has a low peculiar velocity. Since both the escaped star and its
-        progenitor orbit in the same underlying galactic potential and have
-        similar phase space positions their orbits are similar
-        \citep{BinneyTremaine2008}. Given sufficient time the phase space
-        separation will increase and an escaped star will lead or trail the
-        position of the progenitor, depending on the location from which it
-        escaped. Therefore, a collection of tidally stripped stars will form
-        extended structures, aka tails or streams, that are few to thousands of
-        parsecs in length \citep{Johnston1998, HelmiWhite1999, Bovy2014}.
-
-        To be a coherent, observable structure the peculiar velocity dispersion
-        of escaped stars relative to the progenitor must be relatively low, but
-        does vary from system to system. Stars in kinematically hot streams
-        (e.g. from progenitors with larger kinematic dispersions) have more
-        dissimilar orbits from each other and the progenitor than do stars in
-        cold streams, with smaller dispersions \citep{Johnston1998,
-        HendelJohnston2015}.  The orbit of a star depends on its phase space
-        position and the gravitational potential; therefore measuring a star's
-        position and velocity and observing its orbit reveals the local
-        potential, which is normally dominated by the Galaxy (primarily the dark
-        matter halo at large distances) \citep{Gibbons+2014}. However, an orbit
-        is impractical to observe on human timescales. Cold streams offer a
-        workaround.  Like measuring one star at many points in one orbit over an
-        extended period, streams are many stars measured at different points
-        along approximately one orbit at the same time. Therefore stellar
-        streams are one of the most promising means to study the Galactic
-        gravitational potential: the stellar components as well as the dark
-        matter \citep{Johnston2016}.
-
-        On the observational front there has been a large concerted effort in
-        the field to find new stellar streams \citep[for an extensive list of
-        known Galactic streams see][]{Mateu2022}, extend the detected extents of
-        known streams \citep[e.g. for \stream{Palomar 5} alone:][]{Rockosi+2002,
-        Ibata+2017, Grillmair+2006, Carlberg+2012, Starkman+2019}, and increase
-        the general purity of stream catalogs.
-
-    \end{quotation}
-
-    \todo[inline]{--- Rephrase}
-
-    \paragraph{one orbit and a single population}
-
-        Stellar streams consist of stars that are tidally disrupted from a
-        progenitor system.  To a first approximation, the stars occupy a single
-        orbit, that of their progenitor.  Additionally, as stars formed in the
-        progenitor they retain its photometric and chemical characteristics:
-        which for globular clusters means following an isochrone.  In this
-        simplistic picture, astrometrically characterizing a stream requires
-        only finding it's orbit. Member stars fall directly on the orbit and the
-        isochrone, making membership likelihood determination trivial.
-
-        % Observational errors complicate this picture. Instead of a certain
-        % membership calculation, we must build a probabilistic model, assigning
-        % a likelihood that an observed star falls along the stream's orbit.
-
-    \paragraph{similar orbits and a somewhat noisy population}
-
-        Occupying a single orbit implies that streams remain a point in action
-        space, and having a common origin would thus not become extended
-        structure. This is not true.  Differences in stream stars' orbits from
-        the progenitor's arise from various factors including internal dynamics
-        of the progenitor and the host Galactic potential.
-
-        An intrinsic width, in configuration and kinematic space.
-
-        Centered on a track, not an orbit.
-
-        This defines an astrometric phase-space hyper-tube \cite{STREAMFINDER},
-        with a distribution radial to the track.
-
-        Instead of characterizing the stream by its orbit, we characterize it by
-        it's track and the distribution around that track.  Computing membership
-        likelihoods now requires fitting the track and distribution. This cannot
-        be done without then also fitting the field of stars in which the stream
-        lives, since the stream and field cannot be clearly separated.
-
-    \paragraph{gaps orbits and a somewhat noisy population}
-
-        This is still a simplistic picture of streams.
-
-        Perturbations to the Galactic potential, in the form of time evolution
-        and non-axisymmetry, as well as substructure can disrupt the stellar
-        stream.  Even most perturbations don't ruin the idea of the phase-space
-        hypertube. They either drop the mixture weight (rephrase, not yet
-        introduced) to 0 or change the width of the hypertube.
-
-    \paragraph{Review of detection methods}
-
-        Identifying streams of globular of clusters is a challenging task.
-        Streams are very low signal-to-noise structures spread over
-        comparatively large regions of the sky. They live in a vast background
-        of field stars.
-
-        Historically streams were detected by matched-filter techniques
-        % Add citations
-        You took an isochrone and shifted it by a distance modulus until a
-        stream stood out in longitude and latitude as an extended overdensity
-        structure.
-
-        With the advent of Gaia, we gained access to detailed astrometric data.
-        For most streams this
-
-        poses a challenging task due to their intricate and diffuse nature from
-        large-scale surveys is challenging due to the complex and overlapping
-        distributions of stars in different regions of the sky; disentangling
-        members from the vast background of field stars
-
-        \begin{enumerate}
-            \item Streamfinder \citep{STREAMFINDER}. This method requires the
-            potential
-            \item VIA MACHINAE \citep{Shih+2022}
-            \item Kiyan and Adrian
-            \item Matched Filter
-            \item Gaia stuff: Adrian and Ana and Sara et al
-            \item Uniform Modeling of 12 Stellar stream \citep{Patrick+2022}.
-            Only on phi1, phi2, and CMD. Their CMD method is more sophisticated.
-            Worth discussing.
-        \end{enumerate}
-
-    Review of available data:
-    \begin{enumerate}
-        \item Gaia. Streams in Gaia have on-sky positions and proper motions,
-        and parallaxes, though for most streams the parallax errors are
-        prohibitively large. Likewise, most streams in Gaia do not have good
-        radial velocity measurements. The photometry is generally poor,
-        generally necessitating cross-matching with other datasets.
-        \item S5. This is a much smaller dataset. It has deeper photometry and
-        radial velocity measurements.
-    \end{enumerate}
+    % \begin{quotation}
+
+    %     A stellar stream is the association of stars tidally stripped from a
+    %     common progenitor system that orbits in an underlying galactic
+    %     gravitational field \citep{Johnston1998, HelmiWhite1999}. Stream
+    %     progenitors are gravitationally bound systems, such as satellite dwarf
+    %     galaxies or star clusters \citep{Odenkirchen+2001, Majewski+2003}. In
+    %     the absence of external interactions these systems are stable, though
+    %     still capable of mass loss driven by internal processes
+    %     \citep{Hills1975, HeggieHut2003}, e.g. relaxation and binary
+    %     interactions. Considering external interactions, these progenitor
+    %     systems may be disrupted: completely, as in the merger events that
+    %     formed the Galactic stellar halo \citep{Lynden-Bell1967,
+    %     SearleZinn1978}; or partially, such as tidal disruption forming a
+    %     stellar stream.
+
+    %     In the approximation of a smooth galactic gravitational field, the
+    %     progenitor's extent is limited to the tidal radius. Through processes
+    %     internal and external, progenitor stars can achieve sufficient energy to
+    %     bring them beyond the tidal boundary, thus ``escaping'' into the
+    %     galactic field. Escape primarily occurs at both an inner and outer
+    %     saddle point of the combined potential -- e.g. the L2 and L3 Lagrange
+    %     points for a spherical galactic field \citep{Ross+1997,
+    %     FukushigeHeggie2000, BinneyTremaine2008}. Generally, the initial phase
+    %     space position of the escaped star is very similar to that of the
+    %     progenitor: the configuration position is the tidal boundary and the
+    %     star has a low peculiar velocity. Since both the escaped star and its
+    %     progenitor orbit in the same underlying galactic potential and have
+    %     similar phase space positions their orbits are similar
+    %     \citep{BinneyTremaine2008}. Given sufficient time the phase space
+    %     separation will increase and an escaped star will lead or trail the
+    %     position of the progenitor, depending on the location from which it
+    %     escaped. Therefore, a collection of tidally stripped stars will form
+    %     extended structures, aka tails or streams, that are few to thousands of
+    %     parsecs in length \citep{Johnston1998, HelmiWhite1999, Bovy2014}.
+
+    %     To be a coherent, observable structure the peculiar velocity dispersion
+    %     of escaped stars relative to the progenitor must be relatively low, but
+    %     does vary from system to system. Stars in kinematically hot streams
+    %     (e.g. from progenitors with larger kinematic dispersions) have more
+    %     dissimilar orbits from each other and the progenitor than do stars in
+    %     cold streams, with smaller dispersions \citep{Johnston1998,
+    %     HendelJohnston2015}.  The orbit of a star depends on its phase space
+    %     position and the gravitational potential; therefore measuring a star's
+    %     position and velocity and observing its orbit reveals the local
+    %     potential, which is normally dominated by the Galaxy (primarily the dark
+    %     matter halo at large distances) \citep{Gibbons+2014}. However, an orbit
+    %     is impractical to observe on human timescales. Cold streams offer a
+    %     workaround.  Like measuring one star at many points in one orbit over an
+    %     extended period, streams are many stars measured at different points
+    %     along approximately one orbit at the same time. Therefore stellar
+    %     streams are one of the most promising means to study the Galactic
+    %     gravitational potential: the stellar components as well as the dark
+    %     matter \citep{Johnston2016}.
+
+    %     On the observational front there has been a large concerted effort in
+    %     the field to find new stellar streams \citep[for an extensive list of
+    %     known Galactic streams see][]{Mateu2022}, extend the detected extents of
+    %     known streams \citep[e.g. for \stream{Palomar 5} alone:][]{Rockosi+2002,
+    %     Ibata+2017, Grillmair+2006, Carlberg+2012, Starkman+2019}, and increase
+    %     the general purity of stream catalogs.
+
+    % \end{quotation}
+
+    % \todo[inline]{--- Rephrase}
+
+    % \paragraph{one orbit and a single population}
+
+    %     Stellar streams consist of stars that are tidally disrupted from a
+    %     progenitor system.  To a first approximation, the stars occupy a single
+    %     orbit, that of their progenitor.  Additionally, as stars formed in the
+    %     progenitor they retain its photometric and chemical characteristics:
+    %     which for globular clusters means following an isochrone.  In this
+    %     simplistic picture, astrometrically characterizing a stream requires
+    %     only finding it's orbit. Member stars fall directly on the orbit and the
+    %     isochrone, making membership likelihood determination trivial.
+
+    %     % Observational errors complicate this picture. Instead of a certain
+    %     % membership calculation, we must build a probabilistic model, assigning
+    %     % a likelihood that an observed star falls along the stream's orbit.
+
+    % \paragraph{similar orbits and a somewhat noisy population}
+
+    %     Occupying a single orbit implies that streams remain a point in action
+    %     space, and having a common origin would thus not become extended
+    %     structure. This is not true.  Differences in stream stars' orbits from
+    %     the progenitor's arise from various factors including internal dynamics
+    %     of the progenitor and the host Galactic potential.
+
+    %     An intrinsic width, in configuration and kinematic space.
+
+    %     Centered on a track, not an orbit.
+
+    %     This defines an astrometric phase-space hyper-tube \cite{STREAMFINDER},
+    %     with a distribution radial to the track.
+
+    %     Instead of characterizing the stream by its orbit, we characterize it by
+    %     it's track and the distribution around that track.  Computing membership
+    %     likelihoods now requires fitting the track and distribution. This cannot
+    %     be done without then also fitting the field of stars in which the stream
+    %     lives, since the stream and field cannot be clearly separated.
+
+    % \paragraph{gaps orbits and a somewhat noisy population}
+
+    %     This is still a simplistic picture of streams.
+
+    %     Perturbations to the Galactic potential, in the form of time evolution
+    %     and non-axisymmetry, as well as substructure can disrupt the stellar
+    %     stream.  Even most perturbations don't ruin the idea of the phase-space
+    %     hypertube. They either drop the mixture weight (rephrase, not yet
+    %     introduced) to 0 or change the width of the hypertube.
+
+    % \paragraph{Review of detection methods}
+
+    %     Identifying streams of globular of clusters is a challenging task.
+    %     Streams are very low signal-to-noise structures spread over
+    %     comparatively large regions of the sky. They live in a vast background
+    %     of field stars.
+
+    %     Historically streams were detected by matched-filter techniques
+    %     % Add citations
+    %     You took an isochrone and shifted it by a distance modulus until a
+    %     stream stood out in longitude and latitude as an extended overdensity
+    %     structure.
+
+    %     With the advent of Gaia, we gained access to detailed astrometric data.
+    %     For most streams this
+
+    %     poses a challenging task due to their intricate and diffuse nature from
+    %     large-scale surveys is challenging due to the complex and overlapping
+    %     distributions of stars in different regions of the sky; disentangling
+    %     members from the vast background of field stars
+
+    %     \begin{enumerate}
+    %         \item Streamfinder \citep{STREAMFINDER}. This method requires the
+    %         potential
+    %         \item VIA MACHINAE \citep{Shih+2022}
+    %         \item Kiyan and Adrian
+    %         \item Matched Filter
+    %         \item Gaia stuff: Adrian and Ana and Sara et al
+    %         \item Uniform Modeling of 12 Stellar stream \citep{Patrick+2022}.
+    %         Only on phi1, phi2, and CMD. Their CMD method is more sophisticated.
+    %         Worth discussing.
+    %     \end{enumerate}
+
+    % Review of available data:
+    % \begin{enumerate}
+    %     \item Gaia. Streams in Gaia have on-sky positions and proper motions,
+    %     and parallaxes, though for most streams the parallax errors are
+    %     prohibitively large. Likewise, most streams in Gaia do not have good
+    %     radial velocity measurements. The photometry is generally poor,
+    %     generally necessitating cross-matching with other datasets.
+    %     \item S5. This is a much smaller dataset. It has deeper photometry and
+    %     radial velocity measurements.
+    % \end{enumerate}
 
@@
         addition of both astrometric and photometric models.  In astrometrics
-        the stream is a Gaussian track in $\phi_2$ and parallax $\varpi$, using
+        the stream is a Gaussian track in $\phi_2$ and parallax $\parallax$, using
         the model defined in \autoref{ssub:method:astrometric_model:on_stream}.
@@
         output), where the 4 outputs are $[\mu_{\phi_2}, \sigma_{\phi_2},
-        \mu_{\varpi}, \sigma_{\varpi}](\phi_1)$.  The network is small, but
+        \mu_{\parallax}, \sigma_{\parallax}](\phi_1)$.  The network is small, but
         sufficiently large to permit 15\% dropout and retain robust predictions.
@@
         photometric model does not have its own network, using instead the
-        outputs $[\mu_{\varpi}, \sigma_{\varpi}](\phi_1)$.
+        outputs $[\mu_{\parallax}, \sigma_{\parallax}](\phi_1)$.
 
@@
         distribution in $\phi_2$, and the second is an exponential distribution
-        for $\varpi$.  The uniform distribution does not have any parameters,
+        for $\parallax$.  The uniform distribution does not have any parameters,
         and thus no neural network.  The exponential distribution has only the
@@
                 \textbf{Lower panel 3: }%
-                    $\varpi_2(\phi_1)$ over the full range of $\phi_1$. Like for
+                    $\parallax_2(\phi_1)$ over the full range of $\phi_1$. Like for
                     $\phi_2$, the data color and transparency is set by the MLE
@@
                 \textbf{Upper Middle Histograms: }%
-                    Parallax $\varpi$ histograms for each model component (blue
+                    Parallax $\parallax$ histograms for each model component (blue
                     background, red stream), in 4 $\phi_1$ ranges across the
@@
     Having successful applied the density modeling framework to a mock stream,
-    we now apply the method to the stellar stream GD-1.
+    we now apply the method to the stellar stream \stream{GD-1}.
     % TODO: some reiteration on the importance of GD-1
@@
             \item $\phi_2 \in [-9, 5] \rm{\degree}$,
-            \item $\varpi \in [-10, 1] \ \rm{mas}$,
+            \item $\parallax \in [-10, 1] \ \rm{mas}$,
             \item $\rm{bp-rp} \in [-1, 3] \ \rm{mag}$
@@
         is a three-dimensional dust map of the Milky Way for which we use
-        \Gaia's parallax distance information.  We include the $1-\sigma$ errors
+        \Gaia's parallax distance information. For stars with missing parallax measurements we assume a distance of $8.5 \ \unit[kpc]$.  We include the $1-\sigma$ errors
         as a source of uncertainty in $\mbs{\Sigma}_n$, the per-star photometric
         uncertainty.
-        % TODO: actually implement that in the model
+        We also correct the parallax for the zero-point using the \code{gaiadr3-zeropoint} package, which implements the findings from \cite{Lindegren+2021}.
         The result is a field populated by
@@
         % TODO: make these variables, like in mock
-        a 12 Gyr, [Fe/H] = -1.3 isochrone at a distance of 7.8 kpc. The
-        selection region is a 0.2 dex orthogonal buffer around the MIST
-        isochrone \citep[using]{brutus}, which is illustrated in the
+        % TODO: change the actual isochrone used in the code to -1.2, not -1.3
+        a 12 Gyr, [Fe/H] = -1.2 isochrone at a distance of 7.8 kpc.
+        The selection region is a 0.2 dex orthogonal buffer around the MIST
+        isochrone \citep[using][]{brutus}, which is illustrated in the
         2nd-from-the-top-left plot in \autoref{fig:gd1-data_selection}.  In
         addition, to avoid detailed modeling of the completeness as a term in
-        $\prior_{obs}$ (from \autoref{isochrone_prior_components}) we mask out
+        $\prior_{obs}$ (from \autoref{eq:isochrone_prior_components}) we mask out
         photometry with $G_{\Gaia{}} > 20$.  With combinations of these masks
@@
                 Photometric selection (blue curve). The selection is based on a
-                12 Gyr, [Fe/H] = -1.3 MIST isochrone, buffered by 0.2 dex.  The
+                12 Gyr, [Fe/H] = -1.2 MIST isochrone, buffered by 0.2 dex.  The
                 right plot shows the application of this selection. By eye, the
@@
                 Applying the combination of red astrometric and blue photometric
-                selections, plotted for astrometric coordinates $\phi_2, \varpi,
+                selections, plotted for astrometric coordinates $\phi_2, \parallax,
                 \mu_{\phi_1}, \mu_{\phi_2}$.  The stream is an identifiable
-                overdensity in all phase-space coordinates except $\varpi$ where
+                overdensity in all phase-space coordinates except $\parallax$ where
                 the errors are significant.
@@
         The model we require for \stream{GD-1} is similar to 
-        the model built for the mock stream in \autoref{sec:results_mock:model},
+        the model built for the mock stream in \autoref{sub:results_mock:model},
         but has additional components for \stream{GD-1}'s spur.
@@
         The normalizing flow is trained on the off-stream selection, and will be
-        fixed when incorporated into the larger model.
-
-        One part of the larger model is the astrometric component of the background.
-        Unlike for the photometry, the background may be fit with simple analytic
-        distributions. We use an exponential distribution (see \autoref{sub:exponential_distribution})
+        fixed (not trainable, nor contribute to the gradient) when incorporated into the larger model.
 
@@
 
-        We model GD-1 as a three-component mixture consisting of a main stream
-        component, a spur, and background.
-
-        \todo[inline]{rephrase }
-        Per \autoref{eq:stream_and_bkg_prob} the stream is an independent
-        addition of both astrometric and photometric models.  In astrometrics
-        the stream is a Gaussian track in $\phi_2, \mu_{\phi_1}, \mu_{\phi_2}$
-        using the model defined in
-        \autoref{ssub:method:astrometric_model:on_stream}.  We use a 4-layer
-        \texttt{LinTanh} with shape (1, 128, 6), where the 6 outputs are
-        $[\mu_{\phi_2}, \sigma_{\phi_2}, \mu_{\mu_{\phi_1}^*},
+        Unlike for the photometry, the astrometric background may be (mostly) fit with simple analytic distributions.
+        \begin{itemize}
+            \item $\phi_2, \mu_{\phi_1} \sim \rm{TruncExp}(\lambda; a, b)$:
+                a truncated exponential distribution (see \autoref{app:sub:exponential_distribution}). 
+                The distribution has 2 slope parameters (one per coordinate) and we use a 4-layer 
+                \texttt{LinTanh} neural network with shape (1, 64, 2) and 15\% dropout.
+            \item $\mu_{\phi_2} \sim \rm{Trunc}\mcal{N}(\mu, \Sigma; a, b)$:
+                a truncated normal distribution (see \autoref{app:sub:normal_distribution}).
+                The distribution has 4 parameters (2 per coordinate) and we use a 4-layer 
+                \texttt{LinTanh} neural network with shape (1, 32, 4) and 15\% dropout.
+        \end{itemize}
+        We also model the parallax $\parallax$ distribution. For much of the extent of
+        \stream{GD1's} field the parallax is well modeled by a truncated skew-normal
+        distribution, $\parallax \sim \rm{TruncSkew}\mcal{N}(\mu, \Sigma; a, b)$, however for
+        $\phi_1 \in [-100, -60]$ this does not hold. Rather then splitting the model at a
+        somewhat arbitrary $\phi_1$ or interpolating between two distributions \TODO{[CITE]}
+        we instead fit the parallax with a $\phi_1$-conditioned normalizing flow.
+        \todo[inline]{flow details}
+
+        We model the main stream of \stream{GD-1} similarly to the mock stream --
+        as an independent addition of both astrometric and photometric models.
+        The astrometric model is a 5-dimensional Gaussian in
+        a Gaussian track in $\phi_2, \parallax, \mu_{\phi_1}, \mu_{\phi_2}, \parallax$,
+        using the model defined in \autoref{ssub:method:astrometric_model:on_stream}.
+        The parameter network is a 5-layer \texttt{LinTanh} with shape (1, 128, 10),
+        where the 10 outputs are
+        $\mbs{\theta} = [\mu_{\phi_2}, \sigma_{\phi_2}, \mu_\parallax, \sigma_\parallax, \mu_{\mu_{\phi_1}^*},
         \sigma_{\mu_{\phi_1}^*}, \mu_{\mu_{\phi_2}},
-        \sigma_{\mu_{\phi_2}}](\phi_1)$. The network is small, but sufficiently
-        large to permit 15\% dropout and retain robust predictions. The
-        photometric model is a distance modulus-shifted isochrone, using the
-        model outlined in \autoref{ssub:method:photometric_model:on_stream}.  We
-        use the same isochrone parameters used in the photometric selection.
-        The photometric model has its own network.
-
-        In order to guide our model towards GD-1, we set down 4 ``control
-        points" along GD-1's main track, and 3 control points along the spur
-        (illustrated in \TODO{x}). These control points act as Gaussian priors
+        \sigma_{\mu_{\phi_2}}, \mu_\parallax, \sigma_\parallax](\phi_1)$.
+        In testing the network is sufficiently
+        large to permit 15\% dropout and retain robust predictions.
+
+        The photometric model is a distance modulus-shifted isochrone, using the
+        model from \autoref{ssub:method:photometric_model:on_stream}.
+        % We use the same isochrone parameters used in the photometric selection.
+        We use a 12 Gyr, [Fe/H] = -1.2 MIST isochrone with no assumed intrinsic dispersion.
+        Using the method described in \autoref{ssub:method:linking_to_astrometrics}
+        the distance modulus track is set by the parallax track in the astrometric model. Thus the photometric model has no independent parameters and consequently no neural network.
+        % TODO: talk about priors on the ishochrone, e.g PDM
+
+        We model the spur of \stream{GD-1} as a separate component to the main
+        stream. We use an identical model as the stream: a 5-D astrometric Gaussian and isochrone in the photometry. We impose the prior that the spur and stream
+        share the same parallax and distance modulus.
+
+        The parameter phase-space is large and a random initialization will take significant
+        time to converge towards the stream track. This initial training is
+        unnecessary as the rough stream track is known \textit{a priori}.
+        To guide the astrometric model towards the known \stream{GD-1},
+        we set down ``control regions" (see \autoref{sub:methods:priors:track_region_prior})
+        along \stream{GD-1}'s main track and on the spur.
+        These control points act as Gaussian priors
         on the model. We set the Gaussian error on these control points to large
@@
         time to converge to the actual stream.
-
-        We also add 3 control points in the distance modulus.  We draw the
-        points from \TODO{[cite]} and add significant width.
-
-        The background model is an exponential distribution.
-
-        The weight parameter is also set to truncate to $0$ at $\phi_1 < X$ and
-        $\phi_1 > Y$. This ensures that we do not model stream stars that fall.
+        We include all the track regions in \autoref{tab:gd1_track_prior}.
+        The main stream has six points: 3 of which apply to the distance modulus
+        and 4 which apply to $\phi_2$ and $\mu_{\phi_1}$.
+        The spur has 3 control points, but since the distance moduli between the stream and spur are linked, the stream control regions also apply.
+
+        \begin{table}
+            \centering
+            \setlength{\tabcolsep}{0pt}
+            \newcommand\capitem{\\$\phantom{+}\ast$\ }
+            \caption{%
+                Stream Track Regions Prior%
+                This table includes all the region priors used to guide the model towards the known stream track. The model will converge to the
+                region $_{\rm minimum}^{\rm maximum}$.
+                See \autoref{sub:methods:priors:track_region_prior} for details.
+            }
+            \label{tab:gd1_track_prior}
+            {\rowcolors{2}{gray!10}{white!10}
+            \begin{tabular}{@{}r<{\hspace{7pt}}*{4}{r<{\hspace{7pt}}}l<{\hspace{7pt}}@{}}
+                \toprule
+                component & $\phi_1 \,\unit{\degree}$ & $\phi_2 \,\unit{\degree}$ & $\mu_{\phi_1} \,[\frac{\rm{mas}}{\rm{yr}}]$ & $\mu \,\unit{mag}$ & $(\simeq \parallax \,\unit{mas})$ \\
+                \midrule
+                stream & -70 & & & $_{14.2}^{14.8}$ & $_{0.11}^{0.14}$ \\ 
+                stream & -60 & $_{-2.55}^{\phantom{+}0.95}$ & $_{-13.25}^{-11.75}$ & & \\ 
+                stream & -50 & $_{-1.75}^{\phantom{+}1.75}$ & $_{-14.05}^{-12.55}$ & & \\ 
+                stream & -40 & $_{-1.75}^{\phantom{+}1.75}$ & $_{-14.05}^{-12.55}$ & $_{14.1}^{ 14.7}$ & $_{0.11}^{0.15}$ \\
+                spur & -35 & $_{0.45}^{2.15}$ & $_{-15.95}^{\phantom{0}-9.95}$ & & \\
+                stream & -30 & $_{-1.75}^{\phantom{+}1.75}$ & $_{-13.35}^{-11.85}$ & $_{14.1}^{ 14.7}$ & $_{0.11}^{0.15}$ \\
+                spur & -30 & $_{0.45}^{2.15}$ & $_{-15.60}^{\phantom{0}-9.60}$ & & \\
+                spur & -20 & $_{0.65}^{2.35}$ & $_{-16.50}^{\phantom{0}-6.50}$ & & \\
+                stream & 0 &  & & $_{14.7}^{15.3}$ & $_{0.09}^{0.15}$ \\
+                \bottomrule\bottomrule
+            \end{tabular}
+            }
+        \end{table}
+
+        All the component models are tied together into a mixture model.
+        Instead of grouping together the stream components in a hierarchical
+        mixture model (background + (stream + spur)) we keep the structure flat,
+        using a single mixture (background + stream + spur) and reducing the number
+        of neural networks. The singular weight parameter network is a 4-layer (1, 32, 2) \texttt{LinTanh} network with 15\% dropout.
+        The stream weights are in the range $f \in [10^{-3}, 0.3]$, while 
+        the spur weights are $f \in [10^{-3}, 0.1]$ and set to 0 $\phi_1 < -45, -15 < \phi_1$.
+By \autoref{eq:mixture_weight_normalization} the background  brings the cumulative weight to one, normalizing the mixture.
 
@@
 
+        \JN{TODO}
+
         In this section we present results from our model applied to real {\it
-        Gaia} and Pan-STARRS data of GD-1.
+        Gaia} and Pan-STARRS data of \stream{GD-1}.
 
@@
         stream must fall between $[4,40]~\rm{kpc}$. Thus, our ability to recover
-        the distance to GD-1 without substantial bias provides a useful
+        the distance to \stream{GD-1} without substantial bias provides a useful
         indicator that our color-magnitude model combined with the astrometric
@@
 
-    Content
+    We now apply the method to the stellar stream \stream{Palomar 5}.
+    % TODO: some reiteration on the importance of Pal5
+    We discuss the data selection in \autoref{sub:results_pal5:data}, model
+    specifics in \autoref{sub:results_pal5:model}, and the results in
+    \autoref{sub:results_pal5:results}.
+
+    \subsection{Data Selection} \label{sub:results_pal5:data}
+
+        \todo[inline]{rephrase (numbers are correct, phrasing is from GD-1}
+
+        We utilize data from \Gaia{} DR3 for the astrometric coordinates of each
+        star.  To obtain more accurate color information, we cross-match the
+        \Gaia{} field on \PanStarrs{} \citep{PanSTARRS1} using \Gaia's provided
+        \texttt{Best-neighbors} catalog.  To limit the field to a region known
+        to contain \stream{Pal\;5} we adopt broad cuts on the cross-matched data.
+        We perform these rough cuts by requiring the data lie within the
+        phase-space cube:
+        \begin{itemize}
+            \item $\phi_1 \in [-30, 30] \ \rm{\degree}$,
+            \item $\phi_2 \in [-5, 10] \rm{\degree}$,
+            \item $\parallax \in [-10, 1] \ \rm{mas}$,
+            \item $\rm{G-R} \in [-1, 3] \ \rm{mag}$
+            \item $g, r \in [0, 50] \ \rm{mag}$,
+        \end{itemize}
+        where we use \package{gala}'s
+        \code{Pal5PriceWhelan18} frame \citep{Price-Whelan+2019} to define $\phi_1$,
+        $\phi_2$, and associated proper motions.  For downloading purposes we
+        split the query into 10 sub-regions in even $\phi_1$ increments. A plot
+        of the $\phi_1, \phi_2$ regions is included in the
+        \href{\GitHubURL{}}{\package{ShowYourWork}} repository.
+        % ...
+        We correct the \PanStarrs{} photometry for dust
+        extinction using the \textit{Bayestar19} \citep{Green+2019} models in
+        the \package{dustmaps} package \citep{Green2018}.
+        For stars with missing parallax measurements we assume a distance of $8.5 \ \unit{kpc}$.  We include the $1-\sigma$ errors
+        as a source of uncertainty in $\mbs{\Sigma}_n$, the per-star photometric
+        uncertainty.
+        We also correct the parallax for the zero-point using the \code{gaiadr3-zeropoint} package, which implements the findings from \cite{Lindegren+2021}.
+        The result is a field populated by
+        \variable{output/pal5/ndata_variable.txt} stars, from which we would like
+        to identify stream members.
+
+        We create data masks for a more refined selection around \stream{Pal\;5}.
+        The two mask types, proper motion and photometric, are show in
+        \autoref{fig:gd1-data_selection}.  The proper motion masks select
+        rectangular regions, containing the primary overdensity of \stream{Pal\;5}
+        % and a surrounding area following the tail of the distribution.  The
+        % tighter mask (red) has corners $(\mu_{\phi_1}, \mu_{\phi_2}) =
+        % [(-15,-10) (-4.5, -2)] \ \unit{mas/yr}$, while the larger mask (yellow)
+        % has $(\mu_{\phi_1}, \mu_{\phi_2}) = [(-15,-5) (-5, -1)] \
+        % \unit{mas/yr}$.  In photometric coordinates we define a mask around
+        % % TODO: make these variables, like in mock
+        % % TODO: change the actual isochrone used in the code to -1.2, not -1.3
+        % a 12 Gyr, [Fe/H] = -1.2 isochrone at a distance of 7.8 kpc.
+        % The selection region is a 0.2 dex orthogonal buffer around the MIST
+        % isochrone \citep[using][]{brutus}, which is illustrated in the
+        % 2nd-from-the-top-left plot in \autoref{fig:gd1-data_selection}.
+        In
+        addition, to avoid detailed modeling of the completeness as a term in
+        $\prior_{obs}$ (from \autoref{eq:isochrone_prior_components}) we mask out
+        photometry with $G_{\Gaia{}} > 20$.  With combinations of these masks
+        the stream has much larger signal-to-noise, though is still only a small
+        percent of the total data.
+
+    % sub data_selection (end)
+
+    \subsection{Model Specification} \label{sub:results_pal5:model}
+
+        \todo[inline]{rephrase (numbers are correct, phrasing is from GD-1}
+
+    % sub model_specification (end)
+
+    \subsection{Trained Density Model} \label{sub:results_pal5:results}
+
+    % sub trained_density_model
 
@@
 \section{Discussion}
+
+    \subsection{Review of detection methods}
+        \todo[inline]{is this section necessary?}
+
+        Identifying streams of globular of clusters is a challenging task.
+        Streams are very low signal-to-noise structures spread over
+        comparatively large regions of the sky. They live in a vast background
+        of field stars.
+
+        Historically streams were detected by matched-filter techniques
+        % Add citations
+        You took an isochrone and shifted it by a distance modulus until a
+        stream stood out in longitude and latitude as an extended overdensity
+        structure.
+
+        With the advent of Gaia, we gained access to detailed astrometric data.
+        For most streams this
+
+        poses a challenging task due to their intricate and diffuse nature from
+        large-scale surveys is challenging due to the complex and overlapping
+        distributions of stars in different regions of the sky; disentangling
+        members from the vast background of field stars
+
+        \begin{enumerate}
+            \item Streamfinder \citep{STREAMFINDER}. This method requires the
+            potential
+            \item VIA MACHINAE \citep{Shih+2022}
+            \item Kiyan and Adrian
+            \item Matched Filter
+            \item Gaia stuff: Adrian and Ana and Sara et al
+            \item Uniform Modeling of 12 Stellar stream \citep{Patrick+2022}.
+            Only on phi1, phi2, and CMD. Their CMD method is more sophisticated.
+            Worth discussing.
+        \end{enumerate}
 
@@
 
-        \package{asdf} \citep{Greenfield+2015},%
-        \package{astropy} \citep{Astropy2013, Astropy2018, Astropy2022},%
-        \package{astroquery} \citep{Astroquery2019},%
-        \package{Matplotlib} \citep{Hunter2007},%
-        \package{NumPy} \citep{Harris+2020},%
-        \package{Pytorch} \citep{Pytorch2019},%
-        \package{SciPy} \citep{Scipy2020},%
-        \package{ShowYourWork} \citep{Luger2021}%
+        \package{asdf} \citep{Greenfield+2015}, %
+        \package{astropy} \citep{Astropy2013, Astropy2018, Astropy2022}, %
+        \package{astroquery} \citep{Astroquery2019}, %
+        \package{brutus} \citep{brutus}, %
+        \package{Matplotlib} \citep{Hunter2007}, %
+        \package{NumPy} \citep{Harris+2020}, %
+        \package{Pytorch} \citep{Pytorch2019}, %
+        \package{SciPy} \citep{Scipy2020}, %
+        \package{ShowYourWork} \citep{Luger+2021} %
+        \package{zuko} \citep{zuko}, %
 
@@
     \vspace{10pt}
-    \subsection{Skew-Normal Distribution}
+    \subsection{Skew-Normal Distribution} \label{sub:skewnormal_distribution}
 

### 2023-09-15 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \usepackage{cleveref}
+\usepackage{transparent}
 \usepackage{todonotes}
@@
     brightness photometric surveys (e.g., \citealt{2018ApJ...862..114S,
-    2021ApJ...914..123I}).  The formation of streams can be traced back to a
+    2021ApJ...914..123I} \JN{add more}).  The formation of streams can be traced back to a
     progenitor cluster, whose stars are gradually lost to the tidal field of the
@@
     track of the tidal tails) can be used to reconstruct the global dark matter
-    distribution of the stellar halo (e.g., \JN{cite}), while local variations
+    distribution of the stellar halo (e.g., \citealt{1999ApJ...512L.109J, 2014ApJ...795...94B, 2014ApJ...795...95B,2022ApJ...940...22N,2023MNRAS.521.4936K}), while local variations
     in the stream track and surface density encode information about the
-    stream's encounters with baryonic structures such as (e.g.) the stellar bar
-    (\JN{cite}), and non-luminous structures like dark matter subhalos
-    (\JN{cite}). Importantly, these galactic components span orders of magnitude
+    stream's encounters with baryonic structures such as the stellar bar
+   (e.g., \citealt{2017MNRAS.470...60E, 2017NatAs...1..633P}) , and non-luminous structures like dark matter subhalos (e.g., \citealt{2017MNRAS.466..628B,2019ApJ...880...38B}).
+Importantly, these galactic components span orders of magnitude
     in mass and spatial extent, highlighting the sensitivity of streams in
@@
     We now introduce our method for characterizing stellar stream tracks and
-    computing stream membership likelihoods from N-D phase-space measurements.
-    % TODO: rephrase following sentence
-    We develop a flexible Bayesian model framework, that allows arbitrary
-    numbers of phase-space dimensions to be incorporated in the model and
-    permits missing phase-space observations.  Below, we offer a concise
+    computing membership probabilities from kinematic and photometric measurements of stars. 
+    We develop a flexible Bayesian modeling framework that incorporates all of the available kinematic information for a field of stars, including those with only partial phase-space measurements.
+Below, we offer a concise
     overview of our approach, followed by a more in-depth technical explanation
@@
     % TODO: ⬆ I think this should be expanded.
-    Non-astrometric coordinates, e.g. photometry and metallicity, are also
+    Non-astrometric coordinates, e.g. photometry and metallicity \JN{do we ever actually do [Fe/H]$(\phi_1)$? If not, can remove metallicity}, are also
     modelled along the stream and background as functions of $\phi_1$.
@@
     mixture model that describes the entire field.  We take the parameters of
-    the mixture model -- the mixing coefficients and component distribution
+    the mixture model -- the mixture weights and component distribution
     parameters -- to be general (continuous) functions of the conditioning
-    variable, $\phi_1$. This is done using feed-forward neural network that
-    takes the conditioning variable as its input and output the parameter value.
+    variable, $\phi_1$. This is done using a feed-forward neural network that
+    takes the conditioning variable as its input and outputs the parameter value(s) that characterize the distribution of stars at a $\phi_1$ ``slice".
     Mixture models of conditional probability distributions using neural
-    networks are called Mixture Density Networks (MDNs). Since the model
+    networks are called Mixture Density Networks (MDNs) \JN{cite CM Bishop}. Since the model
     coefficients may evolve with $\phi_1$, MNDs are well suited to characterize
@@
     \subsection{Framing the Data} \label{sub:method:framing_the_data}
+        \JN{I like this section since we're really thinking deeply about ``what does it mean to construct a stream frame", which is important for this paper!
+Though I think the point can be made with less words and notation.
+I.e., I think we just want to establish that (a) streams can be parameterized as a function of some affine parameter, and (b) in a heliocentric frame even a stream on a circular orbit will not appear flat in on-sky angular coordinates.
+}
+
+        \JN{My modification of the paragraph below:  As a stream progenitor orbits the Galactic center of mass, its path can be approximated locally as an elliptical segment. The associated
+        arms of the stream generally align closely with its orbital plane.
+As viewed from a Galactocentirc reference frame, the stream assumes the form of a great circle enabling a 1:1 mapping from some phase parameter to a unique position along the stream.
+}
+
+        \JN{
+        While it would be ideal to characterize streams in a Galactocentirc frame, transformation to this frame requires knowledge of the solar motion around the galactic center, and accurate distances to a field stars (among other uncertain quantities).
+In a heliocentric frame, projection effects can obscure the shape of a stream leading to a non-trivial stream track.}
+
+        \JN{
+        In a heliocentric frame, projection effects can obscure this simple description. Thankfully... (as before)}
 
@@
 
+        % \begin{figure}
+        %     \centering
+        %     \includegraphics[scale=0.5]{static/model/DAG_StreamDensity.pdf}
+        %     \caption{Probabilistic Graphical Model of the Mixture Density Network (MDN)}
+        %     \todo[inline]{TODO:}
+        %     \begin{enumerate}
+        %         \item remake this example this with
+        %         \url{https://github.com/daft-dev/daft}. See
+        %         \url{https://en.wikipedia.org/wiki/Mixture_model} for examples.
+        %     \end{enumerate}
+        %     \label{fig:DAG}
+        % \end{figure}
         \begin{figure}
+            \script{gd1/plot/pgm_stream.py}
             \centering
-            \includegraphics[scale=0.5]{static/model/DAG_StreamDensity.pdf}
+            \includegraphics[scale=0.5]{figures/gd1/pgm_stream.pdf}
             \caption{Probabilistic Graphical Model of the Mixture Density Network (MDN)}
-            \todo[inline]{TODO:}
-            \begin{enumerate}
-                \item remake this example this with
-                \url{https://github.com/daft-dev/daft}. See
-                \url{https://en.wikipedia.org/wiki/Mixture_model} for examples.
-            \end{enumerate}
-            \label{fig:DAG}
+            \label{fig:PGM_stream}
+        \end{figure}
+
+        \begin{figure}
+            \script{gd1/plot/pgm_background.py}
+            \centering
+            \includegraphics[scale=0.5]{figures/gd1/pgm_background.pdf}
+            \caption{Probabilistic Graphical Model of the Mixture Density Network (MDN) \JN{I think these could go side by side and take up the top of this page nicely (two column figure)}}
+            \label{fig:PGM_background}
         \end{figure}
@@
 
-        The mixture coefficients $\qth{f}$ are normalized s.t.
+        The mixture coefficients $\qth{f}$ are normalized such that
         \begin{equation}
+        \label{eq:mixture_weight_sum}
             \sum_{\mrm{q}} \qth{f}(\phi_1) = 1 \qquad \forall \phi_1
         \end{equation}
-        In practice this is enforced by defining
+        In practice this is enforced by defining a background
         \begin{equation} \label{eq:mixture_weight_normalization}
@@
         \mbs{I_Q}$.  We discuss the mixture weights further in
-        \autoref{sub:method:mixture_weight}.
+        \autoref{sub:method:mixture_weight}. \JN{I think it's enough just to have Eq.~\ref{eq:mixture_weight_sum}.}
 
@@
         \autoref{eq:mixture_weight_normalization} to require only a single
-        mixture coefficient.  Of course, if more components are included in the
+        mixture coefficient.
+\JN{I think we should simplify the sentences below, it interrupts the flow.
+For this work, can we just say: ``Note that the stream and background PDFs can consist of further components.
+This will become important for our characterization of the stream \stream{GD-1}, which appears spatially bifurcated.}Of course, if more components are included in the
         mixture then \autoref{eq:stream_and_bkg_prob} becomes the more general
@@
         % TODO: terminology ND-phase-space vs feature columns
-        Most streams in \Gaia {\color{red} [cite]}, for instance, have proper
+        Most streams in \Gaia {\color{red} [cite]}\JN{Should be italics right?}, for instance, have proper
         motions but not radial velocities nor reliable parallax measurements.
@@
         \begin{equation}\label{eq:fraction_param}
-            f_q\left(w_{i,0}\right) = \frac{N_q\left(\phi_1\right)}{N_{\rm tot}\left(\phi_1\right)},
+            f_q\left(\phi_1\right) = \frac{N_q\left(\phi_1\right)}{N_{\rm tot}\left(\phi_1\right)},
         \end{equation}
@@
         $\phi_1$ increment. We therefore model $N_{\rm tot}\left(\phi_1\right)$
-        as a post-processing step using a single normalzing flow in $\phi_1$.
+        as a post-processing step using a single normalizing flow in $\phi_1$.
 
         In particular, for a given field the distribution of $\phi_1$
-        coordinates is specified by the set $\{\phi_1\}_f$. A normalizng flow is
+        coordinates is specified by the set $\{\phi_1\}_f$. A normalizing flow is
         trained to this dataset, and will satisfy $\int d\phi_1
@@
                 \cmp{S,w}{\pdf}(\nth{\mbs{w}} | \mbs{\theta}) \!
-= \mcal{N}_F \big(\nth{\mbs{w}} | \astroM{\mbs{\mu}}\!(\phi_1), {\cmp{w}{\nth{\mbs{\Sigma}}}}^2 \!
+= \mcal{N}_F {\transparent{0.5}\big(}\nth{\mbs{w}} | \astroM{\mbs{\mu}}\!(\phi_1), {\cmp{w}{\nth{\mbs{\Sigma}}}}^2 \!
 + \!
@@
             probability density (i.e., integrates to one) \TODO{[cite]}.
+            For the neural networks we regularize the data (minus the mean, dividied by the standard deviation per feature column); thus we correct the overall normalization of the flow by the product of the jacobian of the regularization operation.
 
@@
         (\autoref{sub:method:photometric_model:off_stream}). Here we use the
-        \package{nflows} package, with a conditional diagonal normal base
+        \package{zuko} package, with a conditional diagonal normal base
         distribution and composite transform network of a reverse permutation
@@
 \section{Results: GD-1} \label{sec:results_gd1}
-
-    Having successful applied the density modeling framework to a mock stream,
-    we now apply the method to the stellar stream \stream{GD-1}.
+    We now apply our method for stream characterization to the stellar stream \stream{GD-1} , initially discovered by \citet{2006ApJ...643L..17G}.
+Previous work has identified several density variations along \stream{GD-1}, including a bifurcation that is well-modeled by an encounter with a dark matter subhalo.
+Characterizing the detailed density fluctuations of this stream is therefore important for constraining a population of perturbers.
     % TODO: some reiteration on the importance of GD-1
@@
         $\phi_2$, and associated proper motions.  For downloading purposes we
-        split the query into 10 sub-regions in even $\phi_1$ increments. A plot
-        of the $\phi_1, \phi_2$ regions is included in the
+        split the query into 32 sub-regions in even $\phi_1$ increments.
+        % TODO: make this a \variable
+        A plot of the $\phi_1, \phi_2$ regions is included in the
         \href{\GitHubURL{}}{\package{ShowYourWork}} repository.  Stream-specific
@@
 
+        % TODO: make this dynamically generated from the actual data.
         \begin{table}
@@
             \caption{%
-                Stream Track Regions Prior%
+                Stream Track Regions Prior: %
                 This table includes all the region priors used to guide the model towards the known stream track. The model will converge to the
@@
                 \midrule
-                stream & -70 & & & $_{14.2}^{14.8}$ & $_{0.11}^{0.14}$ \\ 
-                stream & -60 & $_{-2.55}^{\phantom{+}0.95}$ & $_{-13.25}^{-11.75}$ & & \\ 
-                stream & -50 & $_{-1.75}^{\phantom{+}1.75}$ & $_{-14.05}^{-12.55}$ & & \\ 
-                stream & -40 & $_{-1.75}^{\phantom{+}1.75}$ & $_{-14.05}^{-12.55}$ & $_{14.1}^{ 14.7}$ & $_{0.11}^{0.15}$ \\
-                spur & -35 & $_{0.45}^{2.15}$ & $_{-15.95}^{\phantom{0}-9.95}$ & & \\
-                stream & -30 & $_{-1.75}^{\phantom{+}1.75}$ & $_{-13.35}^{-11.85}$ & $_{14.1}^{ 14.7}$ & $_{0.11}^{0.15}$ \\
-                spur & -30 & $_{0.45}^{2.15}$ & $_{-15.60}^{\phantom{0}-9.60}$ & & \\
-                spur & -20 & $_{0.65}^{2.35}$ & $_{-16.50}^{\phantom{0}-6.50}$ & & \\
-                stream & 0 &  & & $_{14.7}^{15.3}$ & $_{0.09}^{0.15}$ \\
+                stream & -70 & & & ${\transparent{0.5}\big(}_{14.2}^{14.8}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{0.11}^{0.14}{\transparent{0.5}\big)}$ \\ 
+                stream & -60 & ${\transparent{0.5}\big(}_{-2.55}^{\phantom{+}0.95}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{-13.25}^{-11.75}{\transparent{0.5}\big)}$ & & \\ 
+                stream & -50 & ${\transparent{0.5}\big(}_{-1.75}^{\phantom{+}1.75}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{-14.05}^{-12.55}{\transparent{0.5}\big)}$ & & \\ 
+                stream & -40 & ${\transparent{0.5}\big(}_{-1.75}^{\phantom{+}1.75}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{-14.05}^{-12.55}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{14.1}^{ 14.7}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{0.11}^{0.15}{\transparent{0.5}\big)}$ \\
+                spur & -35 & ${\transparent{0.5}\big(}_{\phantom{+}0.45}^{\phantom{+}2.15}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{-15.95}^{\phantom{0}-9.95}{\transparent{0.5}\big)}$ & & \\
+                stream & -30 & ${\transparent{0.5}\big(}_{-1.75}^{\phantom{+}1.75}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{-13.35}^{-11.85}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{14.1}^{ 14.7}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{0.11}^{0.15}{\transparent{0.5}\big)}$ \\
+                spur & -30 & ${\transparent{0.5}\big(}_{\phantom{+}0.45}^{\phantom{+}2.15}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{-15.60}^{\phantom{0}-9.60}{\transparent{0.5}\big)}$ & & \\
+                spur & -20 & ${\transparent{0.5}\big(}_{\phantom{+}0.65}^{\phantom{+}2.35}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{-16.50}^{\phantom{0}-6.50}{\transparent{0.5}\big)}$ & & \\
+                stream & 0 &  & & ${\transparent{0.5}\big(}_{14.7}^{15.3}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{0.09}^{0.15}{\transparent{0.5}\big)}$ \\
                 \bottomrule\bottomrule
@@
 
+\clearpage
 \section{Palomar 5} \label{sec:results_pal5}
@@
         the \package{dustmaps} package \citep{Green2018}.
-        For stars with missing parallax measurements we assume a distance of $8.5 \ \unit{kpc}$.  We include the $1-\sigma$ errors
+        For stars with missing parallax measurements we assume a distance of $20 \ \rm{kpc}$.  We include the $1-\sigma$ errors
         as a source of uncertainty in $\mbs{\Sigma}_n$, the per-star photometric
@@
         We create data masks for a more refined selection around \stream{Pal\;5}.
+
+        \begin{itemize}
+            \item M5 mask
+            \item that other thing
+        \end{itemize}
+
         The two mask types, proper motion and photometric, are show in
-        \autoref{fig:gd1-data_selection}.  The proper motion masks select
+        \autoref{fig:pal5-data_selection}.  The proper motion masks select
         rectangular regions, containing the primary overdensity of \stream{Pal\;5}
@@
 
+        \begin{figure*}[h]
+            \script{pal5/plot/data_selection.py}
+            \centering
+            \includegraphics[width=1\linewidth]{figures/pal5/data_selection.pdf}
+            \caption{%
+                Data selections for \stream{Pal\;5}, within the data cube
+                described in \autoref{sub:results_pal5:data}.
+            }
+            \label{fig:pal5-data_selection}
+        \end{figure*}
+
     % sub data_selection (end)
@@
 
+        The modeling framework, detailed in the \autoref{sec:method} sections, is
+        modular, allowing many model components to be combined, nested, added
+        to the mixture, and linked via priors.
+        The model we require for \stream{GD-1} is similar to 
+        the model built for the mock stream in \autoref{sub:results_mock:model},
+        but has additional components for \stream{GD-1}'s spur.
+        In this section we will discuss how the total model is built, noting 
+        similarities to the example mocks-stream model.
+
+        All full Bayesian stream models necessarily include a background model,
+        which we model in both astrometric and photometric spaces.
+        The photometric background is too complex to capture with simple analytic
+        distributions. Instead, we train a normalizing flow on the magnitudes $g, r$,
+        conditioned on $\phi_1$. We refer readers to
+        \autoref{sub:method:photometric_model:off_stream} for discussion of the photometric distribution and how a normalizing flow
+        can characterize this complex distribution, including its variation over $\phi_1$.
+        The flow's flexibility, while necessary in this context, also poses
+        a problem: the flow captures the stream as easily as the background.
+        Consequently we select on-stream and off-stream regions using the known
+        $\phi_1,\phi_2$ range of the stream, as shown in the
+        upper panel of \autoref{fig:gd1-photometric_background_selection}.
+        In the lower panel are plotted these selections in photometric coordinates,
+        where an isochrone is apparent in the on-stream selection.
+        The normalizing flow is trained on the off-stream selection, and will be
+        fixed (not trainable, nor contribute to the gradient) when incorporated into the larger model.
+
+        \begin{figure}
+            \script{pal5/plot/photometric_background_selection.py}
+            \centering
+            \includegraphics[width=1\linewidth]{figures/pal5/photometric_background_selection.pdf}
+            \caption{Caption}
+            \label{fig:pal5-photometric_background_selection}
+        \end{figure}
+
+        Unlike for the photometry, the astrometric background may be (mostly) fit with simple analytic distributions.
+        \begin{itemize}
+            \item $\phi_2, \mu_{\phi_1} \sim \rm{TruncExp}(\lambda; a, b)$:
+                a truncated exponential distribution (see \autoref{app:sub:exponential_distribution}). 
+                The distribution has 2 slope parameters (one per coordinate) and we use a 4-layer 
+                \texttt{LinTanh} neural network with shape (1, 64, 2) and 15\% dropout.
+            \item $\mu_{\phi_2} \sim \rm{Trunc}\mcal{N}(\mu, \Sigma; a, b)$:
+                a truncated normal distribution (see \autoref{app:sub:normal_distribution}).
+                The distribution has 4 parameters (2 per coordinate) and we use a 4-layer 
+                \texttt{LinTanh} neural network with shape (1, 32, 4) and 15\% dropout.
+        \end{itemize}
+        We also model the parallax $\parallax$ distribution. For much of the extent of
+        \stream{GD1's} field the parallax is well modeled by a truncated skew-normal
+        distribution, $\parallax \sim \rm{TruncSkew}\mcal{N}(\mu, \Sigma; a, b)$, however for
+        $\phi_1 \in [-100, -60]$ this does not hold. Rather then splitting the model at a
+        somewhat arbitrary $\phi_1$ or interpolating between two distributions \TODO{[CITE]}
+        we instead fit the parallax with a $\phi_1$-conditioned normalizing flow.
+        \todo[inline]{flow details}
+
+        We model the main stream of \stream{GD-1} similarly to the mock stream --
+        as an independent addition of both astrometric and photometric models.
+        The astrometric model is a 5-dimensional Gaussian in
+        a Gaussian track in $\phi_2, \parallax, \mu_{\phi_1}, \mu_{\phi_2}, \parallax$,
+        using the model defined in \autoref{ssub:method:astrometric_model:on_stream}.
+        The parameter network is a 5-layer \texttt{LinTanh} with shape (1, 128, 10),
+        where the 10 outputs are
+        $\mbs{\theta} = [\mu_{\phi_2}, \sigma_{\phi_2}, \mu_\parallax, \sigma_\parallax, \mu_{\mu_{\phi_1}^*},
+        \sigma_{\mu_{\phi_1}^*}, \mu_{\mu_{\phi_2}},
+        \sigma_{\mu_{\phi_2}}, \mu_\parallax, \sigma_\parallax](\phi_1)$.
+        In testing the network is sufficiently
+        large to permit 15\% dropout and retain robust predictions.
+
+        The photometric model is a distance modulus-shifted isochrone, using the
+        model from \autoref{ssub:method:photometric_model:on_stream}.
+        % We use the same isochrone parameters used in the photometric selection.
+        We use a 12 Gyr, [Fe/H] = -1.2 MIST isochrone with no assumed intrinsic dispersion.
+        Using the method described in \autoref{ssub:method:linking_to_astrometrics}
+        the distance modulus track is set by the parallax track in the astrometric model. Thus the photometric model has no independent parameters and consequently no neural network.
+        % TODO: talk about priors on the ishochrone, e.g PDM
+
+        We model the spur of \stream{GD-1} as a separate component to the main
+        stream. We use an identical model as the stream: a 5-D astrometric Gaussian and isochrone in the photometry. We impose the prior that the spur and stream
+        share the same parallax and distance modulus.
+
+        The parameter phase-space is large and a random initialization will take significant
+        time to converge towards the stream track. This initial training is
+        unnecessary as the rough stream track is known \textit{a priori}.
+        To guide the astrometric model towards the known \stream{GD-1},
+        we set down ``control regions" (see \autoref{sub:methods:priors:track_region_prior})
+        along \stream{GD-1}'s main track and on the spur.
+        These control points act as Gaussian priors
+        on the model. We set the Gaussian error on these control points to large
+        values, so that their influence on the model is not dominant. Indeed, we
+        find that the value of the control points is to help reduce training
+        time, since otherwise it will take the flexible density model longer
+        time to converge to the actual stream.
+        We include all the track regions in \autoref{tab:gd1_track_prior}.
+        The main stream has six points: 3 of which apply to the distance modulus
+        and 4 which apply to $\phi_2$ and $\mu_{\phi_1}$.
+        The spur has 3 control points, but since the distance moduli between the stream and spur are linked, the stream control regions also apply.
+
+        % TODO: make this dynamically generated from the actual data.
+        \begin{table}
+            \centering
+            \setlength{\tabcolsep}{0pt}
+            \newcommand\capitem{\\$\phantom{+}\ast$\ }
+            \caption{%
+                Stream Track Regions Prior: %
+                This table includes all the region priors used to guide the model towards the known stream track. The model will converge to the
+                region $_{\rm minimum}^{\rm maximum}$.
+                See \autoref{sub:methods:priors:track_region_prior} for details.
+            }
+            \label{tab:pal5_track_prior}
+            {\rowcolors{2}{gray!10}{white!10}
+            \begin{tabular}{@{}*{4}{r<{\hspace{7pt}}}l<{\hspace{7pt}}@{}}
+                \toprule
+                $\phi_1 \,\unit{\degree}$ & $\phi_2 \,\unit{\degree}$ & $\mu_{\phi_1} \,[\frac{\rm{mas}}{\rm{yr}}]$ & $\mu \,\unit{mag}$ & $(\simeq \parallax \,\unit{mas})$ \\
+                \midrule
+                0 & & & & \\ 
+                \bottomrule\bottomrule
+            \end{tabular}
+            }
+        \end{table}
+
+        All the component models are tied together into a mixture model.
+        Instead of grouping together the stream components in a hierarchical
+        mixture model (background + (stream + spur)) we keep the structure flat,
+        using a single mixture (background + stream + spur) and reducing the number
+        of neural networks. The singular weight parameter network is a 4-layer (1, 32, 2) \texttt{LinTanh} network with 15\% dropout.
+        The stream weights are in the range $f \in [10^{-3}, 0.3]$, while 
+        the spur weights are $f \in [10^{-3}, 0.1]$ and set to 0 $\phi_1 < -45, -15 < \phi_1$.
+By \autoref{eq:mixture_weight_normalization} the background  brings the cumulative weight to one, normalizing the mixture.
+
     % sub model_specification (end)
@@
     \subsection{Trained Density Model} \label{sub:results_pal5:results}
+
+        \begin{figure*}[h]
+            \script{pal5/plot/results_full.py}
+            \centering
+            \includegraphics[width=1\linewidth]{figures/pal5/results_full.pdf}
+            \caption{CAPTION}
+            \label{fig:pal5-results-full}
+            TODO:
+            \begin{itemize}
+                \item Add plot of the stream linear density
+                \item Color palette for the spur
+                \item more subtle stream MLE path
+                \item rerun model with larger pmphi2 sigma
+                \item add the isochrones to the cmd plots
+            \end{itemize}
+        \end{figure*}
+
+        \begin{figure*}[h]
+            \script{pal5/plot/results_panels.py}
+            \centering
+            \includegraphics[width=1\linewidth]{figures/pal5/results_panels.pdf}
+            \caption{CAPTION}
+            TODO:
+            \begin{itemize}
+                \item Add plot of the stream linear density
+                \item Color palette for the spur
+                \item add the isochrones to the cmd plots
+            \end{itemize}
+            \label{fig:pal5-results-panels}
+        \end{figure*}
+
+        \begin{figure*}
+            \script{pal5/plot/smooth_likelihood.py}
+            \centering
+            \includegraphics[scale=0.8]{figures/pal5/smooth_likelihood.pdf}
+            \caption{Caption}
+            \label{fig:pal5-heatmap}
+        \end{figure*}
+
+        \variable{output/pal5/member_table_select.tex}
 

### 2023-09-15 src/tex/ms.tex
[showyourwork] overleaf sync

@@
             \begin{equation}
-                \cmp{S,w}{\pdf}(\nth{\mbs{w}} | \mbs{\theta}) \!
-= \mcal{N}_F {\transparent{0.5}\big(}\nth{\mbs{w}} | \astroM{\mbs{\mu}}\!(\phi_1), {\cmp{w}{\nth{\mbs{\Sigma}}}}^2 \!
-+ \!
-\astroM{\mbs{\Sigma}}^2\!\left(\phi_1\right) \!\big),
+                \cmp{S,w}{\pdf}(\nth{\mbs{w}} | \mbs{\theta})
+                \!= \mcal{N}_F \big(\nth{\mbs{w}} | \astroM{\mbs{\mu}}\!(\phi_1), {\cmp{w}{\nth{\mbs{\Sigma}}}}^2 \! + \!  \astroM{\mbs{\Sigma}}^2\!\left(\phi_1\right) \!\big),
             \end{equation}
@@
                 \midrule
-                stream & -70 & & & ${\transparent{0.5}\big(}_{14.2}^{14.8}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{0.11}^{0.14}{\transparent{0.5}\big)}$ \\ 
-                stream & -60 & ${\transparent{0.5}\big(}_{-2.55}^{\phantom{+}0.95}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{-13.25}^{-11.75}{\transparent{0.5}\big)}$ & & \\ 
-                stream & -50 & ${\transparent{0.5}\big(}_{-1.75}^{\phantom{+}1.75}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{-14.05}^{-12.55}{\transparent{0.5}\big)}$ & & \\ 
-                stream & -40 & ${\transparent{0.5}\big(}_{-1.75}^{\phantom{+}1.75}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{-14.05}^{-12.55}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{14.1}^{ 14.7}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{0.11}^{0.15}{\transparent{0.5}\big)}$ \\
-                spur & -35 & ${\transparent{0.5}\big(}_{\phantom{+}0.45}^{\phantom{+}2.15}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{-15.95}^{\phantom{0}-9.95}{\transparent{0.5}\big)}$ & & \\
-                stream & -30 & ${\transparent{0.5}\big(}_{-1.75}^{\phantom{+}1.75}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{-13.35}^{-11.85}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{14.1}^{ 14.7}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{0.11}^{0.15}{\transparent{0.5}\big)}$ \\
-                spur & -30 & ${\transparent{0.5}\big(}_{\phantom{+}0.45}^{\phantom{+}2.15}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{-15.60}^{\phantom{0}-9.60}{\transparent{0.5}\big)}$ & & \\
-                spur & -20 & ${\transparent{0.5}\big(}_{\phantom{+}0.65}^{\phantom{+}2.35}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{-16.50}^{\phantom{0}-6.50}{\transparent{0.5}\big)}$ & & \\
-                stream & 0 &  & & ${\transparent{0.5}\big(}_{14.7}^{15.3}{\transparent{0.5}\big)}$ & ${\transparent{0.5}\big(}_{0.09}^{0.15}{\transparent{0.5}\big)}$ \\
+                stream & -70 & & & ${\color{gray}\big(}_{14.2}^{14.8}{\color{gray}\big)}$ & ${\color{gray}\big(}_{0.11}^{0.14}{\color{gray}\big)}$ \\ 
+                stream & -60 & ${\color{gray}\big(}_{-2.55}^{\phantom{+}0.95}{\color{gray}\big)}$ & ${\color{gray}\big(}_{-13.25}^{-11.75}{\color{gray}\big)}$ & & \\ 
+                stream & -50 & ${\color{gray}\big(}_{-1.75}^{\phantom{+}1.75}{\color{gray}\big)}$ & ${\color{gray}\big(}_{-14.05}^{-12.55}{\color{gray}\big)}$ & & \\ 
+                stream & -40 & ${\color{gray}\big(}_{-1.75}^{\phantom{+}1.75}{\color{gray}\big)}$ & ${\color{gray}\big(}_{-14.05}^{-12.55}{\color{gray}\big)}$ & ${\color{gray}\big(}_{14.1}^{ 14.7}{\color{gray}\big)}$ & ${\color{gray}\big(}_{0.11}^{0.15}{\color{gray}\big)}$ \\
+                spur & -35 & ${\color{gray}\big(}_{\phantom{+}0.45}^{\phantom{+}2.15}{\color{gray}\big)}$ & ${\color{gray}\big(}_{-15.95}^{\phantom{0}-9.95}{\color{gray}\big)}$ & & \\
+                stream & -30 & ${\color{gray}\big(}_{-1.75}^{\phantom{+}1.75}{\color{gray}\big)}$ & ${\color{gray}\big(}_{-13.35}^{-11.85}{\color{gray}\big)}$ & ${\color{gray}\big(}_{14.1}^{ 14.7}{\color{gray}\big)}$ & ${\color{gray}\big(}_{0.11}^{0.15}{\color{gray}\big)}$ \\
+                spur & -30 & ${\color{gray}\big(}_{\phantom{+}0.45}^{\phantom{+}2.15}{\color{gray}\big)}$ & ${\color{gray}\big(}_{-15.60}^{\phantom{0}-9.60}{\color{gray}\big)}$ & & \\
+                spur & -20 & ${\color{gray}\big(}_{\phantom{+}0.65}^{\phantom{+}2.35}{\color{gray}\big)}$ & ${\color{gray}\big(}_{-16.50}^{\phantom{0}-6.50}{\color{gray}\big)}$ & & \\
+                stream & 0 &  & & ${\color{gray}\big(}_{14.7}^{15.3}{\color{gray}\big)}$ & ${\color{gray}\big(}_{0.09}^{0.15}{\color{gray}\big)}$ \\
                 \bottomrule\bottomrule

### 2023-09-15 src/scripts/gd1/table/member_table_select.py
fix calcs
Signed-off-by: nstarman <nstarman@users.noreply.github.com>

@@ -8,6 +8,8 @@ from astropy.table import QTable
 from numpy.lib.recfunctions import structured_to_unstructured
 from showyourwork.paths import user as user_paths
 
+from stream_ml.core.typing import Array
+
 paths = user_paths()
 
 # Add the parent directory to the path
@@ -52,6 +54,15 @@ rows.extend(prob_idx[subselect])
 # subselect = rng.choice(np.arange(len(prob_idx)), size=3, replace=False, shuffle=False)
 # rows.extend(prob_idx[subselect])
 
+
+def process_lines(vs: Array, es: Array) -> list[str]:
+    """Process to value +/- error string."""
+    return [
+        (rf"${v:0.2f} \pm {e:0.2f}$" if not np.isnan(v) else "---")
+        for v, e in zip(vs, es, strict=True)
+    ]
+
+
 table = QTable()
 # yada yada the source_id column
 # table[r"\texttt{source\_id}"] = [f"...{str(sid)[-4:]}" for sid in table[r"\texttt{source\_id}"]]  # noqa: E501
@@ -62,48 +73,30 @@ table[r"$\alpha$ [$\mathrm{{}^{\circ}}$]"] = data_table["ra"][sel][rows].to_valu
 table[r"$\delta$ [$\mathrm{{}^{\circ}}$]"] = data_table["dec"][sel][rows].to_value(
     "deg"
 )
-table[r"$\mu_{\alpha}^{*}$ [$\frac{\rm{mas}}{\rm{yr}}$]"] = [
-    f"${v:0.2f} \\pm {e:0.2f}$"
-    for v, e in zip(
-        data_table["pmra"][sel][rows].to_value("mas/yr"),
-        data_table["pmra_error"][sel][rows].to_value("mas/yr"),
-        strict=True,
-    )
-]
-table[r"$\mu_{\delta}$ [$\frac{\rm{mas}}{\rm{yr}}$]"] = [
-    rf"${v:0.2f} \pm {e:0.2f}$"
-    for v, e in zip(
-        data_table["pmdec"][sel][rows].to_value("mas/yr"),
-        data_table["pmdec_error"][sel][rows].to_value("mas/yr"),
-        strict=True,
-    )
-]
-table[r"$\varpi$ [\rm{mas}]"] = [
-    rf"${v:0.2f} \pm {e:0.2f}$"
-    for v, e in zip(
[…]

### 2023-09-15 src/scripts/pal5/model/4-likelihoods.py

@@ -38,12 +38,13 @@ with xp.no_grad():
 
     for i in tqdm(range(N), total=N):
         mpars = model.unpack_params(model(data))
-        stream_lik = model.component_posterior("stream", mpars, data, where=where)
-        bkg_lik = model.component_posterior("background", mpars, data, where=where)
-        tot_lik = model.posterior(mpars, data, where=where)
+        stream_lnlik = model.component_ln_posterior("stream", mpars, data, where=where)
+        bkg_lnlik = model.component_ln_posterior("background", mpars, data, where=where)
+        # tot_lnlik = model.ln_posterior(mpars, data, where=where)  # FIXME!
+        tot_lnlik = xp.logaddexp(stream_lnlik, bkg_lnlik)
 
-        stream_probs[:, i] = stream_lik / tot_lik
-        bkg_probs[:, i] = bkg_lik / tot_lik
+        stream_probs[:, i] = xp.exp(stream_lnlik - tot_lnlik)
+        bkg_probs[:, i] = xp.exp(bkg_lnlik - tot_lnlik)
 
 stream_prob_percentiles = np.c_[
     np.percentile(stream_probs, 5, axis=1),
@@ -64,12 +65,13 @@ manually_set_dropout(model, 0.0)
 with xp.no_grad():
     mpars = model.unpack_params(model(data))
 
-    stream_lik = model.component_ln_posterior("stream", mpars, data, where=where)
-    bkg_lik = model.component_ln_posterior("background", mpars, data, where=where)
-    tot_lik = model.ln_posterior(mpars, data, where=where)
+    stream_lnlik = model.component_ln_posterior("stream", mpars, data, where=where)
+    bkg_lnlik = model.component_ln_posterior("background", mpars, data, where=where)
+    # tot_lnlik = model.ln_posterior(mpars, data, where=where)  # FIXME!
+    tot_lnlik = xp.logaddexp(stream_lnlik, bkg_lnlik)
 
-stream_prob = xp.exp(stream_lik - tot_lik)
-bkg_prob = xp.exp(bkg_lik - tot_lik)
+bkg_prob = xp.exp(bkg_lnlik - tot_lnlik)
+stream_prob = xp.exp(stream_lnlik - tot_lnlik)
 
 # =============================================================================
 

### 2023-09-15 src/scripts/pal5/model/helper.py

@@ -31,17 +31,17 @@ def diagnostic_plot(model: ModelAPI, data: Data, where: Data) -> plt.Figure:
         model.eval()
         mpars = model.unpack_params(model(data))
 
-        stream_lik = model.component_ln_posterior("stream", mpars, data, where=where)
-        bkg_lik = model.component_ln_posterior("background", mpars, data, where=where)
-        # tot_lik = model.ln_posterior(mpars, data, where=where)  # FIXME!
-        tot_lik = xp.logaddexp(stream_lik, bkg_lik)
+        stream_lnlik = model.component_ln_posterior("stream", mpars, data, where=where)
+        bkg_lnlik = model.component_ln_posterior("background", mpars, data, where=where)
+        # tot_lnlik = model.ln_posterior(mpars, data, where=where)  # FIXME!
+        tot_lnlik = xp.logaddexp(stream_lnlik, bkg_lnlik)
 
     stream_weight = mpars[("stream.weight",)]
     stream_cutoff = stream_weight > 2e-2
 
-    bkg_prob = xp.exp(bkg_lik - tot_lik)
-    stream_prob = xp.exp(stream_lik - tot_lik)
-    allstream_prob = xp.exp(stream_lik - tot_lik)
+    bkg_prob = xp.exp(bkg_lnlik - tot_lnlik)
+    stream_prob = xp.exp(stream_lnlik - tot_lnlik)
+    allstream_prob = xp.exp(stream_lnlik - tot_lnlik)
 
     psort = np.argsort(stream_prob)
     pmax = xp.max(stream_prob.max(), xp.tensor(0.95))

### 2023-09-15 src/scripts/pal5/plot/results_full.py

@@ -46,7 +46,7 @@ with xp.no_grad():
     stream_lnlik = model.component_ln_posterior("stream", mpars, data, where=where)
     bkg_lnlik = model.component_ln_posterior("background", mpars, data, where=where)
     # tot_lnlik = model.ln_posterior(mpars, data, where=where)  # FIXME
-    tot_lnlik = xp.logsumexp(xp.stack((stream_lnlik, bkg_lnlik), 1), 1)
+    tot_lnlik = xp.logaddexp(stream_lnlik, bkg_lnlik)
 
 
 def _iter_mpars(key: str, subkey: str | None) -> np.ndarray:

### 2023-09-15 src/scripts/pal5/plot/results_panels.py

@@ -47,7 +47,7 @@ with xp.no_grad():
     stream_lnlik = model.component_ln_posterior("stream", mpars, data, where=where)
     bkg_lnlik = model.component_ln_posterior("background", mpars, data, where=where)
     # tot_lnlik = model.ln_posterior(mpars, data, where=where)  # FIXME
-    tot_lnlik = xp.logsumexp(xp.stack((stream_lnlik, bkg_lnlik), 1), 1)
+    tot_lnlik = xp.logaddexp(stream_lnlik, bkg_lnlik)
 
 
 stream_weight = mpars[("stream.weight",)]

### 2023-09-15 src/scripts/pal5/table/member_table_select.py

@@ -8,6 +8,8 @@ from astropy.table import QTable
 from numpy.lib.recfunctions import structured_to_unstructured
 from showyourwork.paths import user as user_paths
 
+from stream_ml.core.typing import Array
+
 paths = user_paths()
 
 # Add the parent directory to the path
@@ -40,6 +42,15 @@ rows.extend(prob_idx[subselect])
 # subselect = rng.choice(np.arange(len(prob_idx)), size=4, replace=False, shuffle=False)
 # rows.extend(prob_idx[subselect])
 
+
+def process_lines(vs: Array, es: Array) -> list[str]:
+    """Process to value +/- error string."""
+    return [
+        (rf"${v:0.2f} \pm {e:0.2f}$" if not np.isnan(v) else "---")
+        for v, e in zip(vs, es, strict=True)
+    ]
+
+
 table = QTable()
 # yada yada the source_id column
 table[r"\texttt{source\_id}"] = ["---"] * len(rows)
@@ -49,40 +60,24 @@ table[r"$\alpha$ [$\mathrm{{}^{\circ}}$]"] = data_table["ra"][sel][rows].to_valu
 table[r"$\delta$ [$\mathrm{{}^{\circ}}$]"] = data_table["dec"][sel][rows].to_value(
     "deg"
 )
-table[r"$\mu_{\alpha}^{*}$ [$\frac{\rm{mas}}{\rm{yr}}$]"] = [
-    f"${v:0.2f} \\pm {e:0.2f}$"
-    for v, e in zip(
-        data_table["pmra"][sel][rows].to_value("mas/yr"),
-        data_table["pmra_error"][sel][rows].to_value("mas/yr"),
-        strict=True,
-    )
-]
-table[r"$\mu_{\delta}$ [$\frac{\rm{mas}}{\rm{yr}}$]"] = [
-    rf"${v:0.2f} \pm {e:0.2f}$"
-    for v, e in zip(
-        data_table["pmdec"][sel][rows].to_value("mas/yr"),
-        data_table["pmdec_error"][sel][rows].to_value("mas/yr"),
-        strict=True,
-    )
-]
+table[r"$\mu_{\alpha}^{*}$ [$\frac{\rm{mas}}{\rm{yr}}$]"] = process_lines(
+    data_table["pmra"][sel][rows].to_value("mas/yr"),
+    data_table["pmra_error"][sel][rows].to_value("mas/yr"),
+)
[…]

### 2023-11-22 src/tex/ms.tex
fix calcs
Signed-off-by: nstarman <nstarman@users.noreply.github.com>
[showyourwork] overleaf sync
Signed-off-by: nstarman <nstarman@users.noreply.github.com>

--- 2023-09-06 src/tex/ms.tex
@@
 \usepackage{cleveref}
+\usepackage{transparent}
 \usepackage{todonotes}
+\usepackage{array}
+\usepackage{float}
 
@@
 \renewcommand{\tableautorefname}{Table}
+\renewcommand{\figureautorefname}{Fig.}
 
@@
 \newcommand{\stream}[1]{#1}
-\newcommand{\dataarchive}[1]{\texttt{#1}}
+\newcommand{\dataarchive}[1]{\textit{#1}}
 \newcommand{\Gaia}{\dataarchive{Gaia}}
@@
 % Statistics
-\newcommand{\pdf}{\mcal{P}}
-\newcommand{\cdf}{\mfk{P}}
+\newcommand{\pdf}{p}
+\newcommand{\cdf}{P}
 \newcommand{\likelihood}{\mcal{L}}
@@
 
+\newcommand{\galaxy}[1]{
+    \ifthenelse{\equal{#1}{}}{
+        \includegraphics[width=9pt]{static/galaxy.png}
+    }{
+        \includegraphics[width={#1}pt]{static/galaxy.png}
+    }%
+}
+
+\defcitealias{Ibata+2021}{I21}
+
 \newcommand{\TODO}[1]{{\textcolor{red}{#1}}}
@@
 % Title
-\title{Characterizing Stellar Streams by ML}
+\title{Does this Star Belong? Data-Driven Characterization of Stellar Streams \\ with Mixture Density Networks}
 
 % Author list
-\author{Nathaniel Starkman \& Jacob Nibauer}
-\author{Jo Bovy}
-\author{Jeremy Webb}
-\author{Ana Bonaca}
+\author[0000-0003-3954-3291]{Nathaniel Starkman}
+\affiliation{David A Dunlap Department of Astronomy and Astrophysics, University of Toronto}
+
+\author[0000-0001-8042-5794]{Jacob Nibauer}
+\altaffiliation{Co-first author.}
+\affiliation{Department of Astrophysical Sciences, Princeton University}
+
+\author[0000-0001-6855-442X]{Jo Bovy}
+\affiliation{David A Dunlap Department of Astronomy and Astrophysics, University of Toronto}
+
+\author[0000-0003-3613-0854]{Jeremy J. Webb}
+\affiliation{Division of Natural Science, Department of Science, Technology and Society, York University}
+
+% \author[0000-0002-7846-9787]{Ana Bonaca}
+% \affiliation{Carnegie Observatories: Pasadena, California, US}
+
+\correspondingauthor{Nathaniel Starkman}
+\email{n.starkman@mail.utoronto.ca}
+
+\shortauthors{Starkman and Nibauer et al.}
 
@@
 \begin{abstract}
-    Stellar stream membership likelihoods with ML. It works!
+    Stellar streams are sensitive probes of the Milky Way's gravitational
+    potential. The mean track of a stream constrains global properties of the
+    potential, while its fine-grained surface density contains information about
+    galactic substructure.
+A precise characterization of streams from potentially noisy data marks a crucial step in constraining galactic structure across orders of magnitude in mass scales.
+Here we present a new method for constructing a smooth probability
+    density model of stellar streams using all of the available astrometric and
+    photometric data. To characterize the stream's morphology and kinematics, we
+    utilize mixture density networks to construct a flexible representation of
+    the stream and its on-sky track, width, stellar number density, and
+    kinematic distribution. In photometric coordinates we model each stream as a
+    single-stellar population, with a distance track that is simultaneously
+    estimated from the stream's inferred distance modulus (using photometry) and
+    parallax distribution (using astrometry). Normalizing flows are used to characterize the distribution of background stars. We apply the method to the stream
+    \stream{GD-1}, and the tidal tails of \stream{Palomar 5}. For both streams we obtain a catalog
+    of stellar membership probabilities that are made publicly available.
+    Importantly, our model is capable of handling data with incomplete
+    phase-space observations, making our method applicable to the growing census
+    of Milky Way stellar streams. When applied to a population of streams, the
+    resulting membership probabilities from our model form the required input to
+    infer the Milky Way's dark matter distribution from the scale of the stellar
+    halo down to subhalos. 
 \end{abstract}
@@
     satellite galaxies, and their census has grown extensively in the Milky Way
-    thanks to all-sky astrometric missions like {\it Gaia} and low-surface
-    brightness photometric surveys (e.g., \citealt{2018ApJ...862..114S,
-    2021ApJ...914..123I}).  The formation of streams can be traced back to a
-    progenitor cluster, whose stars are gradually lost to the tidal field of the
-    host galaxy and extend along a series of similar orbits producing tidal
-    tails, which can sometimes span several tens of degrees across the sky. The
-    orbital proximity of stars belonging to a stream makes them sensitive
-    tracers of the mass distribution of galaxies, sourced by both the baryonic
-    and dark matter components.
+    thanks to all-sky astrometric missions like \Gaia{}
+    \citep{GaiaCollaboration+2016, GaiaCollaboration+2023} and low-surface
+    brightness photometric surveys (e.g., \citealt{Ibata+1998,
+    GrillmairDionatos2006, Shipp+2018, Ibata+2021}).  The formation of streams
+    can be traced back to a progenitor (a globular cluster or satellite galaxy)
+    whose stars are gradually lost to the tidal field of the host galaxy. The
+    stars extend along a series of similar orbits, called tidal tails, which can
+    sometimes span several tens of degrees across the sky. The orbital proximity
+    of stars belonging to a stream makes them sensitive tracers of the mass
+    distribution of galaxies, sourced by both the baryonic and dark matter
+    components.
 
@@
     track of the tidal tails) can be used to reconstruct the global dark matter
-    distribution of the stellar halo (e.g., \JN{cite}), while local variations
-    in the stream track and surface density encode information about the
-    stream's encounters with baryonic structures such as (e.g.) the stellar bar
-    (\JN{cite}), and non-luminous structures like dark matter subhalos
-    (\JN{cite}). Importantly, these galactic components span orders of magnitude
-    in mass and spatial extent, highlighting the sensitivity of streams in
-    constraining the structure of the galaxy.
+    distribution of the stellar halo (e.g., \citealt{Johnston+1999, Bonaca+2014,
+    Bovy2014, Bovy+2016, Nibauer+2022, Koposov+2023}), while local variations in
+    the stream track and surface density encode information about the stream's
+    encounters with baryonic structures such as the stellar bar (e.g.,
+    \citealt{Erkal+2017, Pearson+2017}), and non-luminous structures like dark
+    matter subhalos (e.g., \citealt{Ibata+2002, Johnston+2002,
+    Carlberg+2012-74820C, Bovy+2017, Bonaca+2019, Hermans+2021}).
 
     While several methods have been developed to model stream properties as a
-    function of global halo characteristics (e.g., flattening and
-    orientation;\JN{cite}) and local substructures (e.g., the bar's pattern
-    speed and the mass of subhalo perturbers; \JN{cite}), these methods often
+    function of global halo characteristics (e.g., the mass distribution,
+    flattening; \citealt{Johnston+1999,2008MNRAS.386L..47B,Koposov+2010,2013MNRAS.433.1826S,Bovy2014,Nibauer+2022}) and local substructures (e.g., the bar's pattern
+    speed and the mass of subhalo perturbers; \citealt{2014A&A...563A..60A,Pearson+2017,2016MNRAS.460..497H,Bovy+2017,Bonaca+2019}), these methods often
     rely on the existence of a homogenized stream-tracer population that
     characterizes a given stream across each of the observable phase-space
-    dimensions. Additionally, because even the fine-grain properties of streams
-    are influenced by the detailed mass distribution of its host galaxy, it is
-    important to propagate errors both in measurement uncertainty and membership
-    uncertainty (i.e., which stars belong to the stream versus the background)
-    when attempting to model a stream. Otherwise, a poorly characterized stream
-    could bias constraints on (e.g.) the total mass of the galaxy, the dark
-    matter halo shape, and the mass of subhalo perturbers. In order to generate
-    more precise constraints on the structure of the galaxy, it is therefore
-    imperative that a statistically sound and homogenized catalog of stellar
-    streams is produced.
-
-    While streams are well described in (e.g.) action angle coordinates or
-    $N-$body simulations, these methods rely on prior assumptions about the
-    galaxy and its underlying gravitational potential. Therefore, it is
+    dimensions. Additionally, because even the fine-grained properties of
+    streams are influenced by the detailed mass distribution of its host galaxy,
+    it is important to propagate errors both in measurement uncertainty and
+    membership uncertainty (i.e., which stars belong to the stream versus the
+    background) when attempting to model a stream. Otherwise, a poorly
+    characterized stream could bias constraints on, e.g., the total mass of the
+    galaxy, the dark matter halo shape, and the mass of subhalo perturbers. In
+    order to generate more precise constraints on the structure of the galaxy,
+    it is therefore imperative that a statistically sound and homogenized
+    catalog of stellar streams is produced.
+
+    While streams are well described in action-angle coordinates
+    \citep[e.g.][]{Bovy2014} or (restricted) $N$-body simulations
+    \citep[e.g.][]{Dehnen+2004}, these methods rely on prior assumptions about
+    the galaxy and its underlying gravitational potential. Therefore, it is
     necessary to devise data-driven methods to characterize stellar streams
@@
     There are a few previous works which have modeled stellar streams in this
-    context. \citet{Patrick+2022} developed a data-driven spline-based method
-    for modeling the photometric properties and on-sky positions of previously
-    identified streams. Their method works by fitting the stream's stellar
-    surface density with a series of splines, capturing both surface brightness
-    variations along the stream and changes in the position of the stream track
-    and width. Their method also utilize a simultaneous isochrone fit to a given
-    stream, from which a distance modulus can be derived. While this method is
-    very successful at characterizing the photometric properties of a stream, it
-    does not consider the kinematic dimensions which have become increasingly
-    well-measured with successive data releases from {\it Gaia}, as well as
-    targeted observations. From a population of RR Lyrae stars,
-    \citet{Price-Whelan+2019} utilized a mixture model to fit the globular
-    cluster stream Pal-5 in the space of proper motions and heliocentric
-    distances. The mixture modeling approach enables a simultaneous fit to both
-    the stream and background density, allowing for better separation of the
-    stream from the background distribution. However, the track of the stream in
-    on-sky coordinates is not fit. The method identified 27 RR Lyrae stars
-    consistent with being members of the stream. While useful for determining
-    the average properties of a stream (e.g., its mean distance track), a
-    limited population of RR Lyrae stars are not sufficient to capture the
-    small-scale properties of streams expected to inform constraints on (e.g.) a
-    population of perturbers in the galaxy. \JN{are there other methods?}
+    context. \citet{Patrick+2022} developed the method introduced by
+    \citet{Erkal+2017}, which is a data-driven, spline-based method for modeling
+    the photometric properties and on-sky positions of previously identified
+    streams. Their method works by fitting the stream's stellar surface density
+    with a series of splines, capturing both surface brightness variations along
+    the stream and changes in the position of the stream track and width. Their
+    method also utilizes an isochrone fit to a given stream, from which a
+    distance modulus can be derived. While this method is very successful at
+    characterizing the photometric properties of a stream, it does not consider
+    the kinematic dimensions which have become increasingly well-measured with
+    successive data releases from \Gaia{}, as well as targeted observations.
+    From a population of RR Lyrae stars, \citet{Price-Whelan+2019} utilized a
+    mixture model to fit the globular cluster stream Pal-5 in the space of
+    proper motions and heliocentric distances. The mixture modeling approach
+    enables a simultaneous fit to both the stream and background density,
+    allowing for better separation of the stream from the background
+    distribution. However, the track of the stream in on-sky coordinates is not
+    fit. The method identified 27 RR Lyrae stars consistent with being members
+    of the stream. While useful for determining the average properties of a
+    stream (e.g., its mean distance track), a limited population of RR Lyrae
+    stars are not sufficient to capture the small-scale properties of streams
+    expected to inform constraints on, e.g., a population of perturbers in the
+    galaxy.
 
     Other methods for extracting stellar streams from the data include
-    matched-filter approaches, where over-densities in color-magnitude space are
-    inspected as possible clusters undergoing tidal stripping \JN{cite the many
-    key papers using this method}. While the matched-filter technique has been
-    extremely successful in stream discovery, it is not equipped to characterize
-    streams at the level of detailed necessary to inform precise constraints on
-    the potential of the galaxy and its substructure.
+    matched-filter algorithms, where over-densities in color-magnitude space are
+    inspected as possible clusters undergoing tidal stripping
+    \citep{Grillmair+1995, GrillmairJohnson2006, Shipp+2018}. While the
+    matched-filter technique has been extremely successful in stream discovery,
+    it is not equipped to characterize streams at the level of detail necessary
+    to inform precise constraints on the potential of the galaxy and its
+    substructure.
 
@@
     previous stream modeling efforts, specifically in its ability to jointly
-    model the kinematic and photometric properties of streams simultaneously.
-    Furthermore, our method is well-suited to fitting streams with only partial
-    or incomplete phase-space or photometric observations, enabling a full
-    characterization of streams insofar as the available data allows.
-
-    % \begin{quotation}
-
-    %     A stellar stream is the association of stars tidally stripped from a
-    %     common progenitor system that orbits in an underlying galactic
-    %     gravitational field \citep{Johnston1998, HelmiWhite1999}. Stream
-    %     progenitors are gravitationally bound systems, such as satellite dwarf
-    %     galaxies or star clusters \citep{Odenkirchen+2001, Majewski+2003}. In
-    %     the absence of external interactions these systems are stable, though
-    %     still capable of mass loss driven by internal processes
-    %     \citep{Hills1975, HeggieHut2003}, e.g. relaxation and binary
-    %     interactions. Considering external interactions, these progenitor
-    %     systems may be disrupted: completely, as in the merger events that
-    %     formed the Galactic stellar halo \citep{Lynden-Bell1967,
-    %     SearleZinn1978}; or partially, such as tidal disruption forming a
-    %     stellar stream.
-
-    %     In the approximation of a smooth galactic gravitational field, the
-    %     progenitor's extent is limited to the tidal radius. Through processes
-    %     internal and external, progenitor stars can achieve sufficient energy to
-    %     bring them beyond the tidal boundary, thus ``escaping'' into the
-    %     galactic field. Escape primarily occurs at both an inner and outer
-    %     saddle point of the combined potential -- e.g. the L2 and L3 Lagrange
-    %     points for a spherical galactic field \citep{Ross+1997,
-    %     FukushigeHeggie2000, BinneyTremaine2008}. Generally, the initial phase
-    %     space position of the escaped star is very similar to that of the
-    %     progenitor: the configuration position is the tidal boundary and the
-    %     star has a low peculiar velocity. Since both the escaped star and its
-    %     progenitor orbit in the same underlying galactic potential and have
-    %     similar phase space positions their orbits are similar
-    %     \citep{BinneyTremaine2008}. Given sufficient time the phase space
-    %     separation will increase and an escaped star will lead or trail the
-    %     position of the progenitor, depending on the location from which it
-    %     escaped. Therefore, a collection of tidally stripped stars will form
-    %     extended structures, aka tails or streams, that are few to thousands of
-    %     parsecs in length \citep{Johnston1998, HelmiWhite1999, Bovy2014}.
-
-    %     To be a coherent, observable structure the peculiar velocity dispersion
-    %     of escaped stars relative to the progenitor must be relatively low, but
-    %     does vary from system to system. Stars in kinematically hot streams
-    %     (e.g. from progenitors with larger kinematic dispersions) have more
-    %     dissimilar orbits from each other and the progenitor than do stars in
-    %     cold streams, with smaller dispersions \citep{Johnston1998,
-    %     HendelJohnston2015}.  The orbit of a star depends on its phase space
-    %     position and the gravitational potential; therefore measuring a star's
-    %     position and velocity and observing its orbit reveals the local
-    %     potential, which is normally dominated by the Galaxy (primarily the dark
-    %     matter halo at large distances) \citep{Gibbons+2014}. However, an orbit
-    %     is impractical to observe on human timescales. Cold streams offer a
-    %     workaround.  Like measuring one star at many points in one orbit over an
-    %     extended period, streams are many stars measured at different points
-    %     along approximately one orbit at the same time. Therefore stellar
-    %     streams are one of the most promising means to study the Galactic
-    %     gravitational potential: the stellar components as well as the dark
-    %     matter \citep{Johnston2016}.
-
-    %     On the observational front there has been a large concerted effort in
-    %     the field to find new stellar streams \citep[for an extensive list of
-    %     known Galactic streams see][]{Mateu2022}, extend the detected extents of
-    %     known streams \citep[e.g. for \stream{Palomar 5} alone:][]{Rockosi+2002,
-    %     Ibata+2017, Grillmair+2006, Carlberg+2012, Starkman+2019}, and increase
-    %     the general purity of stream catalogs.
-
-    % \end{quotation}
-
-    % \todo[inline]{--- Rephrase}
-
-    % \paragraph{one orbit and a single population}
-
-    %     Stellar streams consist of stars that are tidally disrupted from a
-    %     progenitor system.  To a first approximation, the stars occupy a single
-    %     orbit, that of their progenitor.  Additionally, as stars formed in the
-    %     progenitor they retain its photometric and chemical characteristics:
-    %     which for globular clusters means following an isochrone.  In this
-    %     simplistic picture, astrometrically characterizing a stream requires
-    %     only finding it's orbit. Member stars fall directly on the orbit and the
-    %     isochrone, making membership likelihood determination trivial.
-
-    %     % Observational errors complicate this picture. Instead of a certain
-    %     % membership calculation, we must build a probabilistic model, assigning
-    %     % a likelihood that an observed star falls along the stream's orbit.
-
-    % \paragraph{similar orbits and a somewhat noisy population}
-
-    %     Occupying a single orbit implies that streams remain a point in action
-    %     space, and having a common origin would thus not become extended
-    %     structure. This is not true.  Differences in stream stars' orbits from
-    %     the progenitor's arise from various factors including internal dynamics
-    %     of the progenitor and the host Galactic potential.
-
-    %     An intrinsic width, in configuration and kinematic space.
-
-    %     Centered on a track, not an orbit.
-
-    %     This defines an astrometric phase-space hyper-tube \cite{STREAMFINDER},
-    %     with a distribution radial to the track.
-
-    %     Instead of characterizing the stream by its orbit, we characterize it by
-    %     it's track and the distribution around that track.  Computing membership
-    %     likelihoods now requires fitting the track and distribution. This cannot
-    %     be done without then also fitting the field of stars in which the stream
-    %     lives, since the stream and field cannot be clearly separated.
-
-    % \paragraph{gaps orbits and a somewhat noisy population}
-
-    %     This is still a simplistic picture of streams.
-
-    %     Perturbations to the Galactic potential, in the form of time evolution
-    %     and non-axisymmetry, as well as substructure can disrupt the stellar
-    %     stream.  Even most perturbations don't ruin the idea of the phase-space
-    %     hypertube. They either drop the mixture weight (rephrase, not yet
-    %     introduced) to 0 or change the width of the hypertube.
-
-    % \paragraph{Review of detection methods}
-
-    %     Identifying streams of globular of clusters is a challenging task.
-    %     Streams are very low signal-to-noise structures spread over
-    %     comparatively large regions of the sky. They live in a vast background
-    %     of field stars.
-
-    %     Historically streams were detected by matched-filter techniques
-    %     % Add citations
-    %     You took an isochrone and shifted it by a distance modulus until a
-    %     stream stood out in longitude and latitude as an extended overdensity
-    %     structure.
-
-    %     With the advent of Gaia, we gained access to detailed astrometric data.
-    %     For most streams this
-
-    %     poses a challenging task due to their intricate and diffuse nature from
-    %     large-scale surveys is challenging due to the complex and overlapping
-    %     distributions of stars in different regions of the sky; disentangling
-    %     members from the vast background of field stars
-
-    %     \begin{enumerate}
-    %         \item Streamfinder \citep{STREAMFINDER}. This method requires the
-    %         potential
-    %         \item VIA MACHINAE \citep{Shih+2022}
-    %         \item Kiyan and Adrian
-    %         \item Matched Filter
-    %         \item Gaia stuff: Adrian and Ana and Sara et al
-    %         \item Uniform Modeling of 12 Stellar stream \citep{Patrick+2022}.
-    %         Only on phi1, phi2, and CMD. Their CMD method is more sophisticated.
-    %         Worth discussing.
-    %     \end{enumerate}
-
-    % Review of available data:
-    % \begin{enumerate}
-    %     \item Gaia. Streams in Gaia have on-sky positions and proper motions,
-    %     and parallaxes, though for most streams the parallax errors are
-    %     prohibitively large. Likewise, most streams in Gaia do not have good
-    %     radial velocity measurements. The photometry is generally poor,
-    %     generally necessitating cross-matching with other datasets.
-    %     \item S5. This is a much smaller dataset. It has deeper photometry and
-    %     radial velocity measurements.
-    % \end{enumerate}
+    model the kinematic and photometric properties of streams simultaneously
+    using a flexible model.  Furthermore, our method is well-suited to fitting
+    streams with only partial or incomplete phase-space or photometric
+    observations, enabling a full characterization of streams insofar as the
+    available data allows.
 
@@
         our method for characterizing stream tracks and computing stellar
-        membership.  We discuss the data in
+        membership.  We discuss initial data processing in
         \autoref{sub:method:framing_the_data} and build a probabilistic
@@
         to characterizing stellar streams to other methods in
-        \autoref{sec:comparison}.  We conclude in \autoref{sec:conclusions},
+        \autoref{sec:discussion}.  We conclude in \autoref{sec:conclusions},
         discussing the results of this work and future directions.
@@
 
-    We now introduce our method for characterizing stellar stream tracks and
-    computing stream membership likelihoods from N-D phase-space measurements.
-    % TODO: rephrase following sentence
-    We develop a flexible Bayesian model framework, that allows arbitrary
-    numbers of phase-space dimensions to be incorporated in the model and
-    permits missing phase-space observations.  Below, we offer a concise
-    overview of our approach, followed by a more in-depth technical explanation
-    in subsequent sections.  We start, in \autoref{sub:method:framing_the_data},
-    by transforming the astrometric data into a stream-oriented on-sky reference
+    To characterize stellar stream tracks and for computing membership
+    probabilities from kinematic and photometric measurements of stars, we
+    develop a flexible Bayesian modeling framework that incorporates all of the
+    available kinematic information for a field of stars, including those with
+    only partial phase-space measurements. Below, we offer a concise overview of
+    our approach, followed by a more in-depth technical explanation in
+    subsequent sections.  We start, in \autoref{sub:method:framing_the_data}, by
+    transforming the astrometric data into a stream-oriented on-sky reference
     frame ($\phi_1, \phi_2, \parallax, \mu_{\phi_1}^*, \mu_{\phi_2}, v_r)$, for
@@
     stream density may be described by distributions in the other parameters as
-    injective functions of $\phi_1$.
-    % TODO: ⬆ I think a few more sentences explaining why this is important,
-    % feature variations, etc?  However, previously we discussed how stream will
-    % vary along the track, with changes in the width and possible gaps.  Also
-    % observational effects, e.g the distance gradient changes the on-sky width
-    % (should this be mentioned earlier?)
-    Likewise, the background of the Galactic field may be described with
-    $\phi_1$-conditioned distributions.
-    % TODO: ⬆ I think this should be expanded.
-    Non-astrometric coordinates, e.g. photometry and metallicity, are also
-    modelled along the stream and background as functions of $\phi_1$.
+    injective functions of $\phi_1$.  Likewise, the background of the Galactic
+    field may be described with $\phi_1$-conditioned distributions.  We will
+    also model the stream in photometric coordinates. Additional features, e.g.
+    metallicity, can also be modeled along the stream and background as
+    functions of $\phi_1$, though we leave this to a future work.
 
@@
     mixture model that describes the entire field.  We take the parameters of
-    the mixture model -- the mixing coefficients and component distribution
+    the mixture model -- the mixture weights and component distribution
     parameters -- to be general (continuous) functions of the conditioning
-    variable, $\phi_1$. This is done using feed-forward neural network that
-    takes the conditioning variable as its input and output the parameter value.
+    variable, $\phi_1$. This is done using a feed-forward neural network that
+    takes the conditioning variable as its input and outputs the parameter
+    value(s) that characterize the distribution of stars at a $\phi_1$ ``slice".
     Mixture models of conditional probability distributions using neural
-    networks are called Mixture Density Networks (MDNs). Since the model
-    coefficients may evolve with $\phi_1$, MNDs are well suited to characterize
-    streams (and the background) with all their variations in position, width,
-    and linear density.
+    networks are called Mixture Density Networks (MDNs) \citep{Bishop+1994}.
+    Since the model coefficients may evolve with $\phi_1$, MNDs are well suited
+    to characterize streams (and the background) with all their variations in
+    position, width, and linear density.
 
@@
 
-        As a stream progenitor orbits the Galactic center of mass (GCOM), its
-        orbital path describes an ellipse in the orbital plane. The associated
-        arms of the stream generally align closely with its orbital plane.  From
-        a Galactocentric reference frame, an orbital plane assumes the form of a
-        great circle in the observer's celestial ``sky," thereby allowing the
-        potential realignment of longitudinal ($\ell$) and latitudinal ($b$)
-        coordinates to a coordinate system aligned with the stream
-        ($\cmp{GCOM}{\phi_1}, \phi_2^{(GCOM)}$). Here, the progenitor is
-        established at the origin, with the stream progressing along
-        $\cmp{GCOM}{\phi_1} (\phi_2^{(GCOM)} \approx 0)$. $\cmp{GCOM}{\phi_1}$
-        is clearly a good affine parameter along which to construct models and
-        analyze the stream's characteristics.
-
-        However, data observations are not taken from the GCOM, but from  $\sim
-        8$ kpc distant \citep{GRAVITY2018, Leung+2022} in a local frame,
-        typically from vantage points such as Earth or its solar Lagrange
-        points, and subsequently represented in the International Celestial
-        Reference System (ICRS) \citep{ICRS1997}.  Restricted as we are to a
-        very local volume, there is no means to observe systems from the more
-        ``intrinsic" reference frames. In our observational frames there is no
-        inherent assurance of effecting a rotation that would similarly align
-        the stream within observer coordinates such that $\phi_2(\phi_1) \approx
-        0$.  Thankfully, most streams are adequately distant from both the
-        Galactic center and the observer, or exhibit orientations such that a
-        rotation a) can be established or b) holds valid. For most of the
-        best-studied globular cluster streams -- \stream{GD-1}, \stream{Palomar
-        5}, \stream{Jhelum}, etc. -- this holds true. However for some streams
-        of dwarf galaxies, like the Magellanic stream which wraps multiple times
+        As a stream progenitor orbits the Galactic center of mass, its path can
+        be approximated locally as an elliptical segment. The associated arms of
+        the stream generally align closely with its orbital plane.  As viewed
+        from a Galactocentric reference frame, the stream approximately assumes
+        the form of a great circle enabling a 1:1 mapping from some phase
+        parameter to a unique position along the stream. Thus in a `stream'
+        oriented frame the rotated longitudinal and latitudinal coordinates
+        ($\phi_1, \phi_2$) align with the stream such that the stream's phase is
+        $\phi_1$ and $\phi_2 \simeq 0$.
+
+        While it would be ideal to characterize streams in this Galactocentirc
+        frame, transformation to the frame requires knowledge of the distance to
+        the Galactic center  \citep{GRAVITY2018, BennettBovy2019, Leung+2022},
+        the solar motion around the Galactic center, and accurate distances to
+        field stars (among other uncertain quantities). In a heliocentric frame,
+        e.g. the standard ICRS\footnote{International Celestial Reference
+        System} \citep{ICRS1997}, projection effects can obscure the shape of a
+        stream leading to a non-trivial stream track. Therefore in a
+        heliocentric frame, there is no assurance of effecting a rotation like
+        in the Galactocentric frame that would similarly align the stream in an
+        observer's coordinates such that $\phi_2(\phi_1) \approx 0$.
+        Thankfully, most streams are adequately distant from both the Galactic
+        center and the observer, or exhibit orientations such that a rotation a)
+        can be established or b) holds valid. For most of the best-studied
+        globular cluster streams -- \stream{GD-1}, \stream{Palomar 5},
+        \stream{Jhelum}, etc. -- this holds true. However for some streams of
+        dwarf galaxies, like the Magellanic stream which wraps multiple times
         around the Milky Way \citep{WannierWrixon1972}, no such transformation
@@
         injective segments and their connection constrained by a prior. Thus the
-        methods developed subsequently may extented and applied even to wrapped
-        and kinked streams. However, we leave extending the model framework to a
-        future work.
+        methods developed subsequently may be extended and applied even to
+        wrapped and kinked streams. However, we leave extending the model
+        framework to a future work.
 
@@
 
-        \begin{figure}
+        \begin{figure*}
+            \script{pgm.py}
             \centering
-            \includegraphics[scale=0.5]{static/model/DAG_StreamDensity.pdf}
-            \caption{Probabilistic Graphical Model of the Mixture Density Network (MDN)}
-            \todo[inline]{TODO:}
-            \begin{enumerate}
-                \item remake this example this with
-                \url{https://github.com/daft-dev/daft}. See
-                \url{https://en.wikipedia.org/wiki/Mixture_model} for examples.
-            \end{enumerate}
-            \label{fig:DAG}
-        \end{figure}
+            \includegraphics[scale=0.6]{figures/pgm.pdf}
+            \caption{%
+                Probabilistic Graphical Models (PGMs) of the Mixture Density
+                Networks used in this work.
+                %
+                \textbf{Left}: A PGM of the stream model. The full dataset
+                $x_n^{obs}$ is made of the observed astrometry $w_n^{obs}$ and
+                photometry $m_n^{obs}$, along with the corresponding
+                observational errors. We model the data as a mixture of
+                Gaussians (in astrometry + distance modulus), with the Gaussians
+                indexed by $q$. The weight $\alpha$ determines the weighted
+                contribution of each Gaussian to each datum. All models are
+                conditioned on $\phi_1$.
+                %
+                \textbf{Right}: a PGM of the background model. The data is
+                identical to that of the stream, however the model is not a
+                mixture of Gaussians, but of a variety of distributions. We
+                further distinguish between trainable distribution parameters
+                (circles) and fixed distributions (points), like a pre-trained
+                normalizing flow background model, explained in further detail
+                in \autoref{sub:method:pre-training_distributions}. Alike to the
+                stream model, all background models are conditioned on $\phi_1$.
+                % 
+            }
+            \label{fig:PGM}
+        \end{figure*}
 
@@
         $\mbs{\theta}$'s dependence on $\phi_1$, and the index set $\mbs{I}_X$
-        in summations over its elements $x$. A full detailing of notation and
-        symbols is included in \autoref{app:notation}.
-
-        The mixture coefficients $\qth{f}$ are normalized s.t.
-        \begin{equation}
-            \sum_{\mrm{q}} \qth{f}(\phi_1) = 1 \qquad \forall \phi_1
+        in summations over its elements $x$.
+
+        The mixture coefficients $\qth{f}$ are normalized such that
+        \begin{equation} \label{eq:mixture_weight_sum}
+            \sum_{\mrm{q}} \qth{f}(\phi_1) = 1, \qquad \forall \phi_1
         \end{equation}
-        In practice this is enforced by defining
+        In practice this is enforced by defining a background
         \begin{equation} \label{eq:mixture_weight_normalization}
@@
         the summation over all models except for some ``background" index $b \in
-        \mbs{I_Q}$.  We discuss the mixture weights further in
-        \autoref{sub:method:mixture_weight}.
+        \mbs{I_Q}$.  In the context of Galactic streams the ``foreground" is the
+        stream itself, while the background is the Galaxy - bulge, bar, disc,
+        halo - and additional structures, like globular clusters and dwarf
+        galaxies, that are not associated with the stream itself.  We discuss
+        the mixture weights further in \autoref{sub:method:mixture_weight}.
 
         In this work we consider primarily astrometric and photometric data,
-        (notated $\mbs{W}$ and $\mbs{M}$, respectively, as detailed in
-        \autoref{app:notation}), but note that the MDN framework may be extended
-        to arbitrary feature dimensions.  Assuming the conditional independence
-        of the astrometry and photometry, we split each model into linearly
-        separable astrometric and photometric models $\cmp{q}{\pdf} =
-        \cmp{q,w}{\pdf} \cmp{q,m}{\pdf}$ .
+        (notated $\mbs{W}$ and $\mbs{M}$, respectively), but note that the MDN
+        framework may be extended to arbitrary feature dimensions. Assuming the
+        conditional independence of the astrometry and photometry\footnote{ For
+        \Gaia{} data this is true in practice but not in detail: there exist
+        small correlations between the astrometric and photometric data.}, we
+        split each model into linearly separable astrometric and photometric
+        models $\cmp{q}{\pdf} = \cmp{q,w}{\pdf} \cmp{q,m}{\pdf}$.
 
@@
             \pdf(\nth{\mbs{w}}, \nth{\mbs{m}} | \mbs{\theta})
-            =& \phantom{+} \qquad f \phantom{+} \Scmp{P}(\nth{\mbs{w}}|\mbs{\theta}) \Spdf(\nth{\mbs{m}}|\mbs{\theta}) \\
+            =& \phantom{+} \qquad f \phantom{+} \Spdf(\nth{\mbs{w}}|\mbs{\theta}) \Spdf(\nth{\mbs{m}}|\mbs{\theta}) \\
             & + (1-f) \Bpdf(\nth{\mbs{w}}|\mbs{\theta}) \Bpdf(\nth{\mbs{m}}|\mbs{\theta}), \nonumber
@@
         \autoref{eq:mixture_weight_normalization} to require only a single
-        mixture coefficient.  Of course, if more components are included in the
-        mixture then \autoref{eq:stream_and_bkg_prob} becomes the more general
-        \autoref{eq:general_model}. However, this an implementation detail as
-        any more complex model, e.g a model including a cold stream, extra-tidal
-        features, the background stellar halo, and field globular clusters may
-        be rearranged such that all stream-related components (cold or
-        extra-tidal) and all other components (stellar halo and globular
-        clusters) are grouped into multi-component \textit{stream} and
-        \textit{background} models which themselves adhere to a
-        \autoref{eq:general_model}-type relation.
+        mixture coefficient.  Note that the stream and background PDFs can
+        consist of further components. This will become important for our
+        characterization of the stream \stream{GD-1}, which appears spatially
+        bifurcated. We note this as an implementation detail since all
+        stream-related components (cold, extra-tidal, perturbed) and all other
+        components (stellar halo, globular clusters, etc) may be grouped into
+        multi-component \autoref{eq:stream_and_bkg_prob} \textit{stream} and
+        \textit{background} models.  The stream and background models are
+        included graphically in \autoref{fig:PGM}, where the left plot shows the
+        stream model, and the right the background.
 
@@
         \begin{equation}\label{eq:membership_prob}
-            \pdf\left(S | \nth{\mbs{w}}, \nth{\mbs{m}}, \mbs{\theta} \right)
+            \pdf\!\left(S | \nth{\mbs{w}}, \nth{\mbs{m}}, \mbs{\theta} \right)
             = \frac{f \Spdf(\nth{\mbs{w}}|\mbs{\theta}) \Spdf(\nth{\mbs{m}}|\mbs{\theta}) }{ \pdf(\nth{\mbs{w}}, \nth{\mbs{m}} | \mbs{\theta})}.
@@
 
+    %\newpage
     \subsection{Missing Phase-Space Observations}
@@
         Streams have a diversity of measurement coverage: several have full 6-D
-        astrometrics as well as photometrics and chemical abundances available
+        astrometrics as well as photometry and chemical abundances available
         \citep[e.g.,][]{Koposov+2019, Antoja+2020, Li+2022}, while most have
-        partial coverage, lacking some feature dimensions.
-        % TODO: terminology ND-phase-space vs feature columns
-        Most streams in \Gaia {\color{red} [cite]}, for instance, have proper
-        motions but not radial velocities nor reliable parallax measurements.
-        Followup surveys, like \dataarchive{S5} {\color{red} [cite]}, add many
+        partial coverage, lacking some feature dimensions.  Most streams in
+        \Gaia \citep{Gaia2016, Gaia2023}, for instance, have proper motions but
+        not radial velocities nor high signal-to-noise parallax measurements.
+        Follow-up surveys, like \dataarchive{S5} \citep{Li+2019}, add many
         feature dimensions, however only for a select set of streams. Given the
@@
         this approach can introduce systematic bias. Consider a star too far
-        away to measure it's parallax distance or radial velocity. This is a
+        away to measure its parallax distance or radial velocity. This is a
         systematic reason and this information should be incorporated into any
@@
 
-    % sub: likelihood_setup (end)
+    % sub: missing_phase_space_observations (end)
+
+    \subsection{Pre-training distributions} 
+    \label{sub:method:pre-training_distributions}
+
+        In \autoref{sub:method:likelihood_setup} we set up the general
+        mathematical framework of MDNs then specified the models on two axes:
+        the component and the data type. Broadly, the components are stream
+        versus background and the data types are astrometric and photometric.
+        For some components, e.g. the stream, the data density will be well fit
+        by an analytic function.  For others, no analytic density provides a
+        realistic description of the data. In this work we take a data-driven
+        approach, and represent non-analytic distributions using a normalizing
+        flow model.
+
+        Normalizing flows provide a flexible description of a probability
+        density, by transforming samples generated from a simple base
+        distribution (i.e., a Gaussian) to the more complicated target
+        distribution \citep{EstebanVanden2010, Rippel2013, RezendeMohamed2015}.
+        The transformations are typically non-linear outputs of a neural neural
+        network, whose parameters are optimized until the target density
+        accurately characterizes the data. The neural network transformation is
+        differentiable, so that jacobian factors can be combined to ensure that
+        the target distribution remains a valid probability density (i.e.,
+        integrates to one) \citep{Kobyzev+2019}.  For the neural networks we
+        regularize the data (minus the mean, divided by the standard deviation
+        per feature column); thus we correct the overall normalization of the
+        flow by the product of the jacobian of the regularization operation.
+
+        Our implementation is as follows. For a given stream, we restrict the
+        data to some field characterized by a polygon drawn around the stream.
+        Because our density modeling is aimed at stream characterization rather
+        than discovery, we assume that the stream is sufficiently well known so
+        that it can be masked out as a simple cut in (e.g.) $\phi_1-\phi_2$
+        coordinates. With the stream masked out, we then fit a normalizing flow
+        to the data. Because the distribution can evolve with $\phi_1$, we fit a
+        \emph{conditional} normalizing flow, $q_{\rm flow}(\mathbf{x}|\phi_1)$.
+        Our central assumption with this model is that the distribution for
+        background stars in the masked region are quantitatively similar to
+        those in the unmasked region. For a sufficiently narrow mask we expect
+        this to be the case, and find that this assumption does not introduce
+        bias for the streams considered in this work.
+
+        Once the normalizing flow, $q_{\rm flow}\left(\mathbf{x} |
+        \phi_1\right)$, is fit to the data, its parameters are fixed while the
+        other components of the model begin training. Therefore, the normalizing
+        flow can be rapidly trained and computed as a pre-processing step.
+
+        It is easy to evaluate the log-likelihood of a normalizing flow at a
+        point $\mbs{x}$ when all feature dimensions are present. When one (or
+        more) feature dimension is missing, however, evaluating the marginal
+        log-likelihood involves integrals over the flow. While the procedure is
+        straightforward it is computationally expensive. As an alternative, we
+        conservatively set the log-likelihood to $0$, the maximum value,
+        overemphasizing the flow's contribution to the background model.
+        Conceptually, up-weighting the background model decreases the
+        false-positive rate in stream membership identification, at the cost of
+        increasing the false-negative rate.  Another approach, which we leave to
+        a future work, is to construct normalizing flows of each marginal
+        distribution, e.g. $q_{\rm flow}\left(\{x_i\}_{i \in \mbs{I}_F, i \neq
+        {j, k}} | x_j, x_k, \phi_1\right)$, and select for each $\nth{\mbs{x}}$
+        the correct flow given the present features.
+
+    % sub: pre-training_distributions (end)
 
@@
         stream, which has been shown to depend on substructure in the galaxy
-        (CITE-x). The dependence of the mixture weight on the linear density is
-        captured by the expression
+        \citep{Siegal-GaskinsValluri2009, Yoon+2011}. The dependence of the
+        mixture weight on the linear density is captured by the expression
         \begin{equation}\label{eq:fraction_param}
-            f_q\left(w_{i,0}\right) = \frac{N_q\left(\phi_1\right)}{N_{\rm tot}\left(\phi_1\right)},
+            f_q\left(\phi_1\right) = \frac{N_q\left(\phi_1\right)}{N_{\rm tot}\left(\phi_1\right)},
         \end{equation}
@@
 
-        The mixture model specified in \S-X only models the weight parameter
-        $f_q$, and not the components of the ratio in
+        The mixture model specified in \autoref{eq:general_model} only models
+        the weight parameter $f_q$, and not the components of the ratio in
         \autoref{eq:fraction_param}. However, the linear density $N_q(\phi_1)$
@@
         $\phi_1$ increment. We therefore model $N_{\rm tot}\left(\phi_1\right)$
-        as a post-processing step using a single normalzing flow in $\phi_1$.
+        as a post-processing step using a single normalizing flow in $\phi_1$.
 
         In particular, for a given field the distribution of $\phi_1$
-        coordinates is specified by the set $\{\phi_1\}_f$. A normalizng flow is
-        trained to this dataset, and will satisfy $\int d\phi_1
+        coordinates is specified by the set $\{\phi_1\}_f$. A normalizing flow
+        is trained to this dataset, and will satisfy $\int d\phi_1
         P_{\phi_f}(\phi_1) = 1$ by construction. In order to re-weight the
@@
         \begin{equation}
-            N_q\left(\phi_1\right) = f_q N_{\rm tot} \left(\phi_1\right)  = f_q N_{\rm tot,0} P_{\phi_1}\left(\phi_1\right) .
+            N_q\left(\phi_1\right) = [f_q N_{\rm tot}] \left(\phi_1\right)  = N_{\rm tot,0}[f_q P_{\phi_1}]\left(\phi_1\right) .
         \end{equation}
 
+    % subsection: determination_of_the_mixture_weight (end)
+
     \subsection{Astrometric Model} \label{sub:method:astrometric_model}
@@
 
-            The astrometric track is modeled with a neural network, encompassing
-            each phase space dimension, parameterized as a function of $\phi_1$.
-            The neural network output for a single stream component is the mean
-            location of the stream track in each dimension,
-            $\astroM{\mbs{\mu}}(\phi_1)$, and its associated covariance matrix
+            The N-dimensional astrometric track is modeled with a single neural
+            network, parameterized as a function of $\phi_1$.  The neural
+            network output for a single stream component is the mean location of
+            the stream track in each dimension, $\astroM{\mbs{\mu}}(\phi_1)$,
+            and its associated covariance matrix
             $\astroM{\mbs{\Sigma}}(\phi_1)$. The probability for the data is
@@
             \begin{equation}
-                \cmp{S,w}{\pdf}(\nth{\mbs{w}} | \mbs{\theta}) \!
-= \mcal{N}_F \big(\nth{\mbs{w}} | \astroM{\mbs{\mu}}\!(\phi_1), {\cmp{w}{\nth{\mbs{\Sigma}}}}^2 \!
-+ \!
-\astroM{\mbs{\Sigma}}^2\!\left(\phi_1\right) \!\big),
+                \cmp{S,w}{\pdf}(\nth{\mbs{w}} | \mbs{\theta})
+                \!= \mcal{N}_F \big(\nth{\mbs{w}} | \astroM{\mbs{\mu}}\!(\phi_1), {\cmp{w}{\nth{\mbs{\Sigma}}}}^2 \! + \!  \astroM{\mbs{\Sigma}}^2\!\left(\phi_1\right) \!\big),
             \end{equation}
@@
             $\mbs{w}$ and the data uncertainties added in quadrature. The data
-            uncertainties $\cmp{w}{\nth{\mbs{\Sigma}}}$ are drawn from
-            $\mbs{\delta}\mbf{W}$, the dataset of astrometric uncertainties (see
-            \autoref{app:notation}).
+            uncertainties $\cmp{w}{\nth{\mbs{\Sigma}}}$ are elements of
+            $\mbs{\delta}\mbf{W}$, the dataset of astrometric uncertainties.
+            % (see \autoref{app:notation}).
 
@@
                 \Spdf(\nth{\mbs{w}} & | \astroM{\mbs{\theta}}(\phi_1))
-                    \mapsto \Spdf(\nth{\tilde{\mbs{w}}} | \astroM{\tilde{\mbs{\theta}}} (\phi_1)) = \mcal{N}_{\tilde{F}}.
+                    \mapsto \Spdf(\nth{\tilde{\mbs{w}}} | \astroM{\tilde{\mbs{\theta}}} (\phi_1))\,. % = \mcal{N}_{\tilde{F}}.
             \end{align}
@@
             \Bcmp{\fth{\mbs{\theta}}}(\phi_1) \right)$. We treat each background
-            component as independent, allowing us to write the likelihood as a
-            product over the astrometric dimensions:
+            component dimension as independent, allowing us to write the
+            likelihood as a product over the astrometric dimensions:
             \begin{equation} \label{eq:astrometric_model_off_stream_probability}
-                \pdf^{(B)}\left(\nth{\mbs{w}} | \mbs{\theta}(\phi_1) \right) = \prod_{f\in \mbs{I}_{\tilde{F}}} \pdf_f^{(B)}\left(\mbs{w}_{n,f} | \Bcmp{\fth{\mbs{\theta}}}(\phi_1) \right).
+                \pdf^{(B)}\left(\nth{\mbs{w}} | \mbs{\theta}(\phi_1) \right) = \prod_{f\in \mbs{I}_{\tilde{F}}} \pdf_f^{(B)}\left(\mbs{w}_{n,f} | \Bcmp{\fth{\mbs{\theta}}}(\phi_1) \right)\,,
             \end{equation}
-            Where $\mbs{I}_{\tilde{F}}$ is the set of indices of the features,
+            where $\mbs{I}_{\tilde{F}}$ is the set of indices of the features,
             omitting missing phase space dimensions.
 
-        % ssub: off_stream (end)
+        % ssub:method:astrometric_model:off_stream (end)
 
@@
             mass function of the stream, as well as any observational
-            constraints (e.g. $g < 20$ mag).
-
-            We are interested in the total probability (at some $\phi_1$) and so
-            integrate over $\gamma$ to find:
+            constraints (e.g., $g < 20$ mag).
+
+            For a given star, we are interested in its probability of belonging
+            to the stream's isochrone. Therefore, we marginalize over $\gamma$
+            to find:
             \begin{small}
@@
             \begin{align}
-                \mu_{\rm sample}\left(\phi_1\right) \sim \mathcal{N}\left(\mu(\phi_1), \sigma^2_\mu(\phi_1) \right) & \quad\unit{mag}.
+                \mu_{\rm sample}\left(\phi_1\right) \sim \mathcal{N}\left(\mu(\phi_1), \sigma^2_\mu(\phi_1) \right). %& \quad\unit{mag$^{-1}$}.
             \end{align}
@@
             where $\theta = {a, Z, ...}$ and any other generating parameters of
-            the isochrone.
-            % FIXME! DO this Likewise, the dust map may be treated as a prior
-            % and it's errors incorporated into the data errors.
-            However, stellar streams are generally poorly fit by theoretic
-            isochrones, at least ones with realistic ages and metallicities.
-            Consequently including the age and metallicity as model parameters
-            does not meaningfully contribute to constraining results on the
-            stream's stellar population. Moreover, age and metallicity are
-            partially degenerate with the distance modulus, working counter to
-            the goal of fitting a distance track to the stream. An alternate
-            approach is to use data-driven isochrones instead of theoretic ones.
-            the age and metallicity are not meaningful quantities. In others,
-            e.g. with a suite of models or a trained emulator, the data-driven
-            isochrones might have realistic ages and metallicities and thus
-            meaningfully contribute to the model.
-            % Is this true? re-read Uniform Modeling of 13 streams
-            We defer this to a future work.
-
-            The photometric probability, \autoref{eq:photometric_probability}
+            the isochrone.  However, at a detailed level stellar streams are
+            generally poorly fit by theoretical isochrones, at least ones with
+            realistic ages and metallicities.  Consequently including the age
+            and metallicity as model parameters does not meaningfully contribute
+            to constraining results on the stream's stellar population.
+            Moreover, age and metallicity are partially degenerate with the
+            distance modulus, working counter to the goal of fitting a distance
+            track to the stream. An alternate approach is to use data-driven
+            isochrones instead of theoretic ones.  We defer this to a future
+            work.
+
+            The photometric probability, \autoref{eq:photometric_probability},
             encodes the photometric distribution -- the ``track" -- of the
             isochrone model at each point along the track, as well as the
-            amplitudes, the relative probability of points along the track. This
-            is the term $\prior(\gamma, \nth{\mbs{m}} | \phi_1)$, which
-            describes all priors on both the isochrone as well as observational
-            constraints. We assume that the properties of the isochrone are
+            relative probability of points along the track. This is the term
+            $\prior(\gamma, \nth{\mbs{m}} | \phi_1)$, which describes all priors
+            on both the isochrone as well as survey constraints and selection
+            effects. We assume that the properties of the isochrone are
             conditionally independent from observational constraints; namely
@@
             data for which it is relevant. \Gaia, for instance, is complete from
-            $12 < G < 17$ and has high completeness up to $G ~20$, thus we mask
-            $G > 20$.  The masks are easily modeled as magnitude limits and
-            replace the complex completeness model in $\prior_{obs}$.
+            $12 < G < 17$ and has high completeness up to $G \approx 20$, thus
+            we mask $G > 20$.  The masks are easily modeled as magnitude limits
+            and replace the complex completeness model in $\prior_{obs}$.
             \autoref{sub:method:missing_data} explains how masking is
@@
             distribution and does not enter into the likelihood.  In photometric
-            coordinates completeness depends on a stars apparent magnitude; vied
-            in in astrometric coordinates, the completeness cannot be described
-            so simply. \Gaia, for instance has scanning law residuals in the
-            density field. When photometric coordinates are masked due to
+            coordinates completeness depends on a stars apparent magnitude;
+            viewed in astrometric coordinates, the completeness cannot be
+            described so simply. \Gaia, for instance has scanning law residuals
+            in the density field. When photometric coordinates are masked due to
             completeness, we do not mask the corresponding  astrometric
@@
             distrubion along the stream, arising due to e.g. mass segregation in
-            the progenitor \TODO{[cite]}. To date this variation along the
-            stream has not been observed \TODO{[cite]}, so in practice we drop
-            the $\phi_1$ dependence -- $\prior_{\cal{I}}(\gamma, \phi_1) =
+            the progenitor \citep{WebbBovy2022}. To date this variation along
+            the stream has not been observed, so in practice we drop the
+            $\phi_1$ dependence -- $\prior_{\cal{I}}(\gamma, \phi_1) =
             \prior_{\cal{I}}(\gamma)$ -- assuming that the PDMF is constant
@@
 
-            % link to the code!
-            In the code we offer a few ansatz for the PDMF, though any
-            user-defined function may be used instead. The default assumption,
-            known to be non-physical, is a uniform distribution over $\gamma$.
-            Similarly non-physical are truncated uniform distributions,
-            considering only a segment of the isochrone, e.g. the main sequence
-            turnoff (MSTO). We include also a Kroupa initial mass function (IMF)
+            In the \href{https://github.com/GalOrrery/stream_ml-pytorch}{code}
+            we offer a few ansatz for the PDMF, though any user-defined function
+            may be used instead. The default assumption, known to be
+            non-physical, is a uniform distribution over $\gamma$.  Similarly
+            non-physical are truncated uniform distributions, considering only a
+            segment of the isochrone, e.g. the main sequence turnoff (MSTO). We
+            include also a Kroupa initial mass function (IMF)
             \citep{Kroupa2001}. The Kroupa IMF, and all physically-motivated
-            IMFs, have an much larger fraction of low-mass stars then high-mass
+            IMFs, have a much larger fraction of low-mass stars than high-mass
             stars, the latter being less likely to form.  This is observed in
             streams, particularly their progenitors. However the Kroupa IMF, and
-            all IMF, are poor fits to the observed PDMF as stream progenitors
-            like globular clusters are extremely old ($\sim10$ Gyr) while an IMF
-            is the zero-age distribution.  How then should the PDMF
-            $\prior_{\cal{I}}$ be treated?
-            % ⬆ rephrase previous sentence
-            One approach to the PDMF is to use a more informed distribution, for
-            example time-evolving an IMF, either analytically or by simulation,
-            to the age of the stream's stellar population.  As discussed
-            previously, globular clusters are known to be poorly fit by
-            theoretic isochrones with realistic inputs (e.g. age, $Z$). Thus
-            fitting an isochrone's track to the data means its age, metallicity
-            and therefore PDMF are not well fit \TODO{[cite]}. Moreover, for
-            many streams, e.g. those lacking known progenitors, the PDMF is
-            observationally poorly constrained.  In short, using any fixed
-            distribution is simple in implementation, however the choice of
-            distribution is not.
+            most out-of-the-box IMFs, are poor fits to the observed PDMF as
+            stream progenitors like globular clusters are extremely old
+            ($\sim10$ Gyr) and may be dynamically evolved
+            \citep{GrillmairSmith2001} while an IMF is the zero-age
+            distribution.  How then should the PDMF $\prior_{\cal{I}}$ be
+            treated?  One approach to the PDMF is to use a more informed
+            distribution, for example time-evolving an IMF, either analytically
+            or by simulation, to the age of the stream's stellar population. %As
+            %discussed previously, globular clusters are known to be poorly fit
+            %by theoretical isochrones with realistic inputs (e.g. age, $Z$).
+            %Thus fitting an isochrone's track to the data means its age,
+            %metallicity and therefore PDMF are %not well fit \TODO{[cite]}.
+            However, for many streams, e.g. those lacking known progenitors,
+            the PDMF is observationally poorly constrained.  In short, using any
+            fixed distribution is simple in implementation, however the choice
+            of distribution is not.
 
@@
 
-            % TODO? expand this section.
             The last approach to the issue of the PDMF, and the one we take in
@@
             we are modeling only a region of interest over which the PDMF does
-            not contribute to the final result.
-            % TODO? work in something to the effect of: The PDMF doesn't have an
-            % enormous impact, regardless as the isochrone model is very thin
-            % and stars close to the isochrone photometrically are generally
-            % quite far astrometrically. This is an advantange of simultaneous
-            % modeling, where errors in one model are balanced by other parts of
-            % the model.
+            not meaningfully contribute to the final result.
 
@@
                 \prior(\{\mu_I, \mu_\parallax \} | \phi_1) &= \delta( \rm{dist}(\mu_I) - \rm{dist}(\parallax) )(\phi_1), \label{eq:distance_track_prior}
-                % \prior(\{\sigma_I, \sigma_\parallax \}(\phi_1)) &= \delta( \rm{dist}(\mu_I) - \rm{dist}(\parallax) )(\phi_1) \label{eq:distance_width_prior}
             \end{align}
-            % TODO: should we show that these are different distance functions?
-            % or is it obvious
             where $\delta$ is the Dirac delta function \citep{Dirac1947}, and
@@
             parallaxes are of order 1 and we exclude the feature from the model.
-            % TODO!
 
@@
 
-            In this section we introduce our model for the distribution of
-            backgrounds in photometric coordinates.  The distribution of stars
-            in color (i.e., $g-r$) and magnitude (i.e., $g$) is a complicated
-            function of location in the galaxy \TODO{(e.g. [cite])}. Even within
-            a field centered on the stream of interest, the color-magnitude
-            diagram (CMD) is a combination of stellar populations distributed
-            over a range in distances. Because of this, we do not expect an
-            analytic density to provide a realistic description of the data. In
-            this work we take a data-driven approach, and represent the CMD
-            using a normalizing flow model.
-
-            Normalizing flows provide a flexible description of a probability
-            density, by transforming samples generated from a simple base
-            distribution (i.e., a Gaussian) to the more complicated target
-            distribution. The transformations are typically non-linear outputs
-            of a neural neural network, whose parameters are optimized until the
-            target density accurately characterizes the data. The neural network
-            transformation is differentiable, so that jacobian factors can be
-            combined to ensure that the the target distribution remains a valid
-            probability density (i.e., integrates to one) \TODO{[cite]}.
-
-            Our implementation is as follows. For a given stream, we restrict
-            the data to some field characterized by a polygon drawn around the
-            stream. Because our density modeling is aimed at stream
-            characterization rather than discovery, we assume that the stream is
-            sufficiently well known so that it can be masked out as a simple cut
-            in (e.g.) $\phi1-\phi_2$ coordinates. With the stream masked out, we
-            then fit a normalizing flow to the photometric data. Because the
+            The distribution of background stars in color (i.e., $g-r$) and
+            magnitude (i.e., $g$) is a complicated function of location in the
+            galaxy. Even within a field centered on the
+            stream of interest, the color-magnitude diagram (CMD) is a
+            combination of stellar populations distributed over a range in
+            distances. Because of this, we do not find an analytic density that
+            describes the data and use instead a normalizing flow, discussed in
+            \autoref{sub:method:pre-training_distributions}.  Because the
             background CMD can evolve with $\phi_1$, we fit a \emph{conditional}
@@
             color-magnitude diagram is conditionally dependent on position along
-            the stream. In practice, we model magntiudes and not colors (i.e.,
+            the stream. In practice, we model magnitudes and not colors (i.e.,
             $\mathbf{m} = (g,r)$ rather than $g \ \mathrm{and} \ g-r$.
-            Otherwise, the two arguments will always be covariate). Our central
-            assumption with this model is that the distribution of colors and
-            magnitudes for background stars in the masked region are
-            quantitatively similar to those in the unmasked region. For a
-            sufficiently narrow mask we expect this to be the case, and find
-            that this assumption does not introduce bias for the streams
-            considered in this work.
-
-            Once the normalizing flow, $q_{\rm flow}\left(\mathbf{m} |
-            \phi_1\right)$, is fit to the data, its parameters are fixed while
-            the other components of the model begin training. Therefore, the
-            normalizing flow can be rapidly trained and computed as a
-            pre-processing step.
-
-            % The specific architecture of the photometric normalizing flow are
-            % discussed in \autoref{sub:methods:model_implementation}. But
-            It is easy to evaluate the log-likelihood a normalizing flow at a
-            point $\mbs{m}$ when all feature dimensions are present. When one
-            (or more) feature dimension is missing, however, evaluating the
-            marginal log-likelihood involves integrals over the flow. While the
-            procedure is straightforward it is computationally expensive. As an
-            alternative, we conservatively set the log-likelihood to $0$, the
-            maximum value, overemphasizing the flow's contribution to the
-            background model. Conceptually, up-weighting the background model
-            decreases the false-positive rate in stream membership
-            identification, at the cost of increasing the false-negative rate.
-            However, the intrinsic width of stellar streams tends to be quite
-            small, with correspondingly small $\sigma_\mu$ (see
-            \autoref{eq:photometric_probability}); thus the effective region of
-            the isochrone model is well determined and we do not find the
-            marginal log-likelihood approach to be impactful. Another approach,
-            which we leave to a future work, is to construct normalizing flows
-            of each marginal distribution, e.g. $q_{\rm flow}\left(\{m_i\}_{i
-            \in \mbs{I}_F, i \neq {j, k}} | m_j, m_k, \phi_1\right)$, and select
-            for each $\nth{\mbs{m}}$ the correct flow given the present
-            features.
+            Otherwise, the two arguments will always be covariate). The
+            normalizing flow approach makes modeling the photometry relatively
+            straightforward.
+
+            In photometry the intrinsic width of stellar streams tends to be
+            quite small, with correspondingly small $\sigma_\mu$ (see
+            \autoref{eq:photometric_probability}). Therefore the effective
+            region of the isochrone model is well determined and we do not find
+            the marginal log-likelihood approach discussed in
+            \autoref{sub:method:pre-training_distributions} to be impactful.
 
@@
 
+    %\newpage
     \subsection{Priors} \label{sub:methods:priors}
@@
         constraints. In this section we introduce and develop more priors that
-        are important for training the BMDN's parameters' neural network(s).
+        are important for training our Bayesian Mixture Density Network's
+        parameters' neural network(s).
 
@@
             the dataset in each feature dimension.
-            % ⬆ where should this sentence be?
 
@@
             adds to the model, but also for how optimizers explore the parameter
-            space. Simple optimizers, like MCMC \TODO{[cite]}, propose a
-            parameter vector then compute its likelihood given the data. Priors
-            with compact support  $\theta \sim \mcal{D}((a, b])$, e.g.
-            $\mcal{U}(a, b)$, may be very dangerous as the optimizer can be
-            initialized in a region with zero probability and has no means but
-            blind luck to find the region of support -- the region with non-zero
-            likelihood. More sophisticated optimizers, like gradient-based
-            descent \TODO{[cite]}, are susceptible to a similar initialization
-            problem, allowing zero-probability regions, but requiring at least a
-            non-zero gradient to make informed updates to the optimizers state.
-            Outside the  support the gradient can be zero.  With MDNs, model
-            parameters are neural network outputs. Unlike for conventional
-            models where an informed initial parameter state may be chosen by
-            hand, it is impractical and undesirable to initialize by hand a
-            neural network's output by setting all its internal weights. One
-            might imagine accomplishing a desired initial output by pre-training
-            the network with a toy model that forces convergence on a set output
-            vector. However, neural networks are highly non-linear in their
-            response to internal state changes (a desirable property). It is
-            quite possible that when switching from the toy to real model's loss
-            function the pre-trained network is in a local probability island
-            from which the global optimum is unreachable.  
+            space. Simple optimizers, like MCMC, propose a parameter vector then
+            compute its likelihood given the data
+            \citep{HoggForeman-Mackey2018}. Priors with compact support  $\theta
+            \sim \mcal{D}((a, b])$, e.g.  $\mcal{U}(a, b)$, may be very
+            dangerous as the optimizer can be initialized in a region with zero
+            probability and has no means but blind luck to find the region of
+            support -- the region with non-zero likelihood. More sophisticated
+            optimizers, like gradient-based descent \citep{cauchy_2009}, are
+            susceptible to a similar initialization problem, allowing
+            zero-probability regions, but requiring at least a non-zero gradient
+            to make informed updates to the optimizers state.  Outside the
+            support the gradient can be zero.  With MDNs, model parameters are
+            neural network outputs. Unlike for conventional models where an
+            informed initial parameter state may be chosen by hand, it is
+            impractical and undesirable to initialize by hand a neural network's
+            output by setting all its internal weights. One might imagine
+            accomplishing a desired initial output by pre-training the network
+            with a toy model that forces convergence on a set output vector.
+            However, neural networks are highly non-linear in their response to
+            internal state changes (a desirable property). It is quite possible
+            that when switching from the toy to real model's loss function the
+            pre-trained network is in a local probability island from which the
+            global optimum is unreachable.  
             Therefore, with the MDN neural networks, initialization is mostly
@@
 
-            % ⬇ where should this sentence be?
             The parameter bounds may be independent of $\phi_1$, as is implicit
             to the above discussion, or conditionally dependent and vary as any
-            user-defined function of $\phi_1$.  Alternatively, priors parameter
+            user-defined function of $\phi_1$.  Alternatively, prior parameters
             may be separated into pieces, dealing with different modeling needs,
@@
 
-        % ssub: parameter_bounds (end)
-
-        \subsubsection{Region Prior} \label{sub:methods:priors:track_region_prior}
+        % ssub:methods:priors:parameter_bounds (end)
+
+        \subsubsection{Guides Prior} \label{sub:methods:priors:track_region_prior}
 
@@
             state of the model and network were compatible with the optimizer.
-            Now we provide known information about physical systems, particular
-            the track of the stream.  Our density modeling is aimed at
-            characterization of \textit{known} streams, not stream discovery.
+            Now we provide known information about physical systems,
+            particularly the track of the stream.  Our density modeling is aimed
+            at characterization of \textit{known} streams, not stream discovery.
             From previous studies, the broad track of a stream is known for
@@
             to the model. Care must be taken that this prior information does
-            not dominate the model.
-            % A good balance between these two goals is to have a prior that
-            % only influences the track on large scales.
-            We introduce a region prior to encourage the stream model to pass
-            through a user-defined control region, while also remaining
-            compatible with the data.  We refer to the prior as a
+            not dominate the model.  We introduce a region prior to encourage
+            the stream model to pass through a user-defined guide region, while
+            also remaining compatible with the data.  We refer to the prior as a
             ``split"-Normal prior: a Gaussian split and separated at the peak
@@
             The un-normalized PDF is given by:
-            \begin{small}
             \begin{equation}
@@
                 \end{cases}.
-            \end{equation}\end{small}
+            \end{equation}
             The piecewise PDF is smooth up to the first derivative and can be
@@
             central region $\mu - w < x < \mu + w$. Since the prior is
-            equi-probable in the region, the stream may lie anywhere as
-            preferred by the data and the stream model.  It is convenient to
+            equi-probable in the guide, the stream may lie anywhere as preferred
+            by the data and the stream model.  It is convenient to
             reparametrize, with $\tau = \frac{1}{\sigma}$. Namely,
-            \begin{small}
+            % \begin{small}
             \begin{equation}
-                \ln \pdf(\theta,\mu,w) \propto \tau \begin{cases} 
+                \ln \pdf(\theta,\mu,w) \propto \tau
+                \begin{cases} 
                     -\left(x-(\mu-w)\right)^2 & \phantom{\mu - w <}\ x < \mu - w \\
@@
                 \end{cases},
-            \end{equation}\end{small}
+            \end{equation}
+            % \end{small}
             where the additive normalization is
+            \\
             $-\ln\left(\sqrt{\frac{\pi}{\tau}}
@@
             useful to turn off this prior after the stream lies within the
-            desired regions.
-
-        % ssub: region_prior (end)
-
-    % sub: priors (end)
+            desired guides and the learning rate of the optimizer is low enough
+            that the model does not wander out.
+
+        % sub:methods:priors:track_region_prior (end)
+
+    % sub:methods:priors (end)
 
@@
         the code implementation and architecture of the neural networks.
-        % Rephrase: I don't like this topic sentence.
 
         The neural networks are built with the \package{PyTorch} stack
-        \TODO{[cite]}. We wrap the network \texttt{pytorch.Module} in a custom
-        framework, allowing the Bayesian likelihood, prior, evidence, etc. to be
-        bundled with the network's forward step. This framework allows for a
-        high degree of modularity. Component models, e.g. the stream model, of
-        the mixture are easily added to (and moved from) as items in the larger
-        mixture model. Probability methods understand how to traverse the
-        mixture model, calling and combining the appropriate methods of the
-        constituent models, so it unnecessary to write custom loss functions.
-        Another benefit of the modular framework is the ease of building and
-        experimenting with different mixture models. Furthermore, each model
-        component may be saved and serialized separately from the other
-        components, allowing for portability of the components between models.
-        For example, if a stream has a prominent extra-tidal feature, e.g. the
-        spur of \stream{GD-1}, a fiducial model of just the thin stream may be
-        trained, then the stream (and background) model components may be saved
-        and used as the initialization to the stream (and background) of a more
-        complete model that includes the spur. This modularity also has a cost:
-        by allowing each model component (including the categorical mixture
-        model itself) to contain its own network we decrease the cross-talk
-        between nodes in separated networks. The networks communicate only
-        through the backwards propagation of the loss function, increasing the
-        required training time of the models. We note that the code framework,
-        being built on \package{PyTorch}, easily permits a single model with
-        single network. Having found a good model by experimenting with the
-        modular layout, the model may be reproduced and re-trained as a single
-        network. Alternatively, though we leave this to a future version of the
-        code, it is possible to ``fuse" the mixture, providing one network whose
-        outputs are apportioned appropriately to each constituent model.
+        \citep{Pytorch2019}. We wrap the network \texttt{pytorch.Module} in a
+        custom framework, allowing the Bayesian likelihood, prior, evidence,
+        etc. to be bundled with the network's forward step. This framework
+        allows for a high degree of modularity. Component models, e.g. the
+        stream model, of the mixture are easily added to (and moved from) as
+        items in the larger mixture model. Probability methods understand how to
+        traverse the mixture model, calling and combining the appropriate
+        methods of the constituent models, so it unnecessary to write custom
+        loss functions.  Another benefit of the modular framework is the ease of
+        building and experimenting with different mixture models. Furthermore,
+        each model component may be saved and serialized separately from the
+        other components, allowing for portability of the components between
+        models.  For example, if a stream has a prominent extra-tidal feature,
+        e.g. the spur of \stream{GD-1}, a fiducial model of just the thin stream
+        may be trained, then the stream (and background) model components may be
+        saved and used as the initialization to the stream (and background) of a
+        more complete model that includes the spur. This modularity also has a
+        cost: by allowing each model component (including the categorical
+        mixture model itself) to contain its own network we decrease the
+        cross-talk between nodes in separated networks. The networks communicate
+        only through the backwards propagation of the loss function, increasing
+        the required training time of the models. We note that the code
+        framework, being built on \package{PyTorch}, easily permits a single
+        model with single network. Having found a good model by experimenting
+        with the modular layout, the model may be reproduced and re-trained as a
+        single network. Alternatively, though we leave this to a future version
+        of the code, it is possible to ``fuse" the mixture, providing one
+        network whose outputs are apportioned appropriately to each constituent
+        model.
 
@@
         MLP with a sequence of \texttt{Linear} \!\!\textrightarrow \texttt{Tanh}
-        \!\!\textrightarrow \texttt{Dropout} (hereafter \texttt{LinTanh})
-        blocks. This is illustrated in \autoref{table:mlp_structure}.
-        % FIXME! reference not being picked up correctly.
+        \!\!\textrightarrow \texttt{Dropout} (hereafter \texttt{LTD}) blocks.
         Dropout layers are used to prevent network co-adaptation and
@@
         network, decreasing the importance of any single node, encouraging
-        instead emergent patterns across the network.  One model for which the
-        lin-tanh-dropout network cannot be used is the normalizing flow used in
-        the photometric background model
+        instead emergent patterns across the network \citep{GalGhahramani2015}.
+        One model for which the \texttt{LTD} network cannot be used is the
+        normalizing flow used in the photometric background model
         (\autoref{sub:method:photometric_model:off_stream}). Here we use the
-        \package{nflows} package, with a conditional diagonal normal base
+        \package{zuko} package, with a conditional diagonal normal base
         distribution and composite transform network of a reverse permutation
@@
         \href{https://github.com/showyourwork/showyourwork}{\package{showyourwork}}
-        in a public repository at \url{\GitHubURL{}}. We will describe for each
-        stream model specifics relevant to that stream but refer readers to the
-        publicly-available code itself for code implementation details.
-        % TODO: Maybe more details in the Appendix?
-
-        \begin{table}
-            \centering
-            \caption{% 
-            Example neural network structure consisting of 1 input block mapping
-            a $\phi_1$ scalar to the $H$ nodes of the hidden blocks, the number
-            of which determines the depth of the network. The hidden blocks map
-            to the $F$ outputs in the output block. Each block consists of a
-            \texttt{Linear} \!\!\textrightarrow \texttt{Tanh}
-            \!\!\textrightarrow \texttt{Dropout} sequence. Vector $\phi_1$
-            inputs are supported as an element-wise application of the network.
-            }
-            \label{table:mlp_structure}
-            \begin{tabular}{@{}rrcl@{}}
-            \toprule
-            & Layer & Shape & Parameters \\
-            \midrule
-            & Linear & (1, H) & 2H  \\
-            & Tanh & (H, H) & 0  \\
-            & Dropout & (H, H) & 0  \\
-            \hline
-            & Linear & (H, H) & $2H^2$  \\
-            $N_{\rm hidden} \times$ & Tanh & (H, H) & 0  \\
-            & Dropout & (H, H) & 0  \\
-            \hline
-            & Linear & (H, F) & $2HF$  \\
-            & Tanh & (F, F) & 0 \\
-            & Dropout & (F, F) & 0  \\
-            \bottomrule
-            \end{tabular}
-        \end{table}
-
-% section method (end)
-
-%\newpage
+        in a public repository. We will describe for each stream model specifics
+        relevant to that stream but refer readers to the publicly-available code
+        itself for code implementation details.
+
+% sec:method (end)
+
 \section{Results: Mock} \label{sec:results_mock}
@@
 
-        We generate synthetic stream observations by sampling uniformly in
-        $\phi_1$ In $\phi_2$ we sample from a quadratic in $\phi_1$ with
-        normally-distributed $0.15^{\degree}$ scatter.  The distances are
-        sampled from a linear funciton in $\phi_1$ with normally-distributed
-        $0.25 \ \unit{kpc}$ scatter, then transformed to the parallax
-        $\parallax$.  Non-poissonian density variations are then simulated by
-        evaluating the stream density with two Gaussian distributions centered
-        at different values of $\phi_1$ with random amplitudes (which sum to
-        $1$) and widths.  Stream stars are then removed using random sampling,
-        weighted by their likelihood of belonging to the density. Post removal,
-        the number of stream stars is
+        We generate a simple and illustrative synthetic stream observations by
+        sampling from simple algebraic forms.  In $\phi_1$ we sample from a
+        uniform distribution. Non-Poissonian density variations, like gaps, are
+        introduced by adding to the uniform distribution two Gaussian
+        distributions centered at different values of $\phi_1$ with negative
+        amplitudes and random widths. Stream stars are then sampled from this
+        uniform-plus-gaps mixture distribution.  In $\phi_2$ we sample from a
+        quadratic in $\phi_1$ with normally-distributed $0.15^{\degree}$
+        scatter.  The distances are uniformly sampled from $7$ to $15$ kpc in a
+        linear function in $\phi_1$ with normally-distributed $0.25 \ \rm{kpc}$
+        scatter, then transformed to the parallax $\parallax$. Even though the
+        stream width is constant in the distance the width in parallax is not,
+        which will be used to demonstrate that we can recover $\phi_1$ dependent
+        distributions.  The number of stream stars is
         $\variable{output/mock/nstream_variable.txt}$.
         $\variable{output/mock/nbackground_variable.txt}$ background astrometric
-        points are generated from exponential distributions at each $\phi_1$.
+        points are generated by sampling from uniform distributions in each
+        coordinate.
 
         The synthetic stream's photometry is also simulated using a
-        \variable{output/mock/isochrone_age_variable.txt}, [Fe/H] =
+        \variable{output/mock/isochrone_age_variable.txt}\unskip, [Fe/H] =
         \variable{output/mock/isochrone_feh_variable.txt} MIST isochrone
-        \citep{brutus, Dotter2016, Choi+2016}. The isochrone is truncated just
-        short of the giant branch, and is sampled from uniformly along the
-        isochrone (i.e., the initial mass function, $P(\gamma)$, is uniform) as
-        well as with an intrinsic uniform 0.2~dex scatter orthogonal to the
-        isochrone track. The isochrone is shifted by the stream's parallax
-        modulus, which is derived from the astrometric distance track.  The
-        background photometric coordinates are generated as a 2-dimensional
-        Gaussian with non-zero covariance.  Thus, the synthetic data scenario
-        described here generates a mock stream in astrometric coordinates and
-        photometric coordinates, with density variations, a distance gradient
-        which is consistent in parallax and distance modulus (i.e., magnitudes),
-        all superimposed over a noisy field of background points in each
-        astrometric and photometric dimension.
+        \citep{Dotter2016, Choi+2016,brutus}. The isochrone is truncated just
+        short of the giant branch, and is sampled from assuming a stream mass
+        function similar to \stream{Pal\,5} \citep{GrillmairSmith2001} as well
+        as with an intrinsic uniform 0.2~dex scatter orthogonal to the isochrone
+        track.
+
+        The isochrone is shifted by the stream's distance modulus, which is
+        derived from the astrometric distance track.  The background photometric
+        coordinates are generated as a 2-dimensional Gaussian with non-zero
+        covariance.  Thus, the synthetic data scenario described here, and
+        presented in \autoref{fig:mock_data_photometric_background_selection},
+        generates a mock stream in astrometric coordinates and photometric
+        coordinates, with density variations, a distance gradient which is
+        consistent in parallax and distance modulus (i.e., magnitudes), all
+        superimposed over a noisy field of background points in each astrometric
+        and photometric dimension.
 
@@
                 %
-                \textbf{Bottom panel:} Astrometric coordinates ($\phi_1$,
-                $\phi_2$) for the mock data set.  Black points are in the
-                ``off"-stream region from the region defined in the astrometric
-                coordinates.  Light blue points are the stream and background
-                from the on-stream region. The stream's isochrone is apparent as
-                an overdensity around (g-r, g)$\approx (0, 20)$.
+                \textbf{Bottom panel:} Photometric coordinates ($g-r$, $g$) for
+                the mock data set.  Black points are in the ``off"-stream region
+                from the region defined in the astrometric coordinates.  Light
+                blue points are the stream and background from the on-stream
+                region. The stream's isochrone is apparent as an overdensity
+                around (g-r, g)$\ \approx (0, 20)$.
                 %
@@
         \end{figure}
+
+        \begin{figure*}[!h]
+            \script{mock/plot/results.py}
+            \centering
+            \includegraphics[width=0.9\linewidth]{figures/mock/results.pdf}
+            \caption{
+                %
+                \textbf{Top panel: }%
+                    The stream mixture coefficient $f(\phi_1)$ (black dotted
+                    line) predicted by the model, overplotted on the true stream
+                    fraction (black-outlined histogram), calculated as the ratio
+                    of stream stars to total stars in 55 bins over the $\phi_1$
+                    range of the isochrone.
+                %
+                \textbf{Middle panel: }
+                    $\phi_2(\phi_1)$ over the full range of $\phi_1$. The data
+                    color and transparency is set by the model's MLE stream
+                    probability (with dropout turned off). Plotted behind the
+                    data are the true labels for the stream stars (large black
+                    circles).  The true labels exactly match the
+                    model-identified stream stars.  The MLE stream track (black
+                    dashed line) is over-plotted on the probability-colored
+                    data.
+                %
+                \textbf{Lower panel 3: }%
+                    $\parallax(\phi_1)$ over the full range of $\phi_1$. Like for
+                    $\phi_2$, the data color and transparency is set by the MLE
+                    probability, with the true labels (large black circles)
+                    under-plotted and MLE track (black dashed line)
+                    over-plotted.
+                %
+                \textbf{Upper Histograms: }%
+                    $\phi_2$ histograms for each model component (blue
+                    background, red stream), in 4 $\phi_1$ ranges across the
+                    data set.  The height of each bin is the
+                    probability-weighted density.  The background is a uniform
+                    distribution, while the stream is a Gaussian. In projection
+                    across the $\phi_1$ range it can appear multi-modal (panel
+                    2) if there are large gaps or `smeared' out (panel 3) if the
+                    Gaussian's mean changes significantly over the range.
+                %
+                \textbf{Upper Middle Histograms: }%
+                    Parallax $\parallax$ histograms for each model component (blue
+                    background, red stream), in 4 $\phi_1$ ranges across the
+                    data set.  The height of each bin is the
+                    probability-weighted density.
+                %
+                \textbf{Lower Middle and Lower Histograms:}%
+                    Photometric coordinate $(g, r)$ plots for each model
+                    component in 4 $\phi_1$ ranges across the data set. The top
+                    row plots the stream stars (red) over the background. The
+                    lower row plots the background stars (blue) over the stream
+                    stars to show  how the two distributions mix.
+                %
+            }
+            \label{fig:mock_data_result}
+        \end{figure*}
 
@@
         the isochrone and from background points included in the simple $\phi_1,
-        \phi_2$ box.  In contrast the off-stream region, has only the the
+        \phi_2$ box.  In contrast, the off-stream region has only the the
         background population.  We use the off-stream population to train a
         conditional normalizing flow (see
-        \autoref{sub:method:photometric_model:off_stream}) on the magnitudes $g$
+        \autoref{sub:method:pre-training_distributions}) on the magnitudes $g$
         and $r$ and conditioned on $\phi_1$.  The normalizing flow is now a
@@
         addition of both astrometric and photometric models.  In astrometrics
-        the stream is a Gaussian track in $\phi_2$ and parallax $\parallax$, using
-        the model defined in \autoref{ssub:method:astrometric_model:on_stream}.
-        We use a 4-layer \texttt{LinTanh} with shape (1 input, 64 hidden, 4
-        output), where the 4 outputs are $[\mu_{\phi_2}, \sigma_{\phi_2},
-        \mu_{\parallax}, \sigma_{\parallax}](\phi_1)$.  The network is small, but
-        sufficiently large to permit 15\% dropout and retain robust predictions.
-        The photometric model is a distance modulus-shifted isochrone, using the
+        the stream is a Gaussian track in $\phi_2$ and parallax $\parallax$,
+        using the model defined in
+        \autoref{ssub:method:astrometric_model:on_stream}.  We use a 4-layer
+        \texttt{LTD} with overall shape ($\phi_1$ input, 4 outputs), where the 4
+        outputs are $[\mu_{\phi_2}, \sigma_{\phi_2}, \mu_{\parallax},
+        \sigma_{\parallax}](\phi_1)$.  The network is small, but sufficiently
+        large to permit 15\% dropout and retain robust predictions.  The
+        photometric model is a distance modulus-shifted isochrone, using the
         model outlined in  \autoref{ssub:method:photometric_model:on_stream}. We
-        use the same isochrone parameters as were used to simulate the stream.
-        For this mock stream we demonstrate simultaneous astrometric and
-        photometric modeling, linking the distance modulus and parallax track,
-        as explained in \autoref{ssub:method:linking_to_astrometrics}. Thus the
-        photometric model does not have its own network, using instead the
-        outputs $[\mu_{\parallax}, \sigma_{\parallax}](\phi_1)$.
+        use the same isochrone parameters as were used to simulate the stream,
+        including the \citep{GrillmairSmith2001} mass function.  For this mock
+        stream, we demonstrate simultaneous astrometric and photometric
+        modeling, linking the distance modulus and parallax track, as explained
+        in \autoref{ssub:method:linking_to_astrometrics}. Thus the photometric
+        model does not have its own network, using instead the outputs
+        $[\mu_{\parallax}, \sigma_{\parallax}](\phi_1)$.
 
@@
         and thus no neural network.  The exponential distribution has only the
-        slope parameter and we use a 3-layer \texttt{LinTanh} with shape (1, 32,
-        1) and 15\% dropout. Background and stream are combined in a mixture
-        model whose mixture parameters are a 4-layer (1, 64, 1) \texttt{LinTanh}
-        network. We train the mixture model with an \texttt{AdamW} optimizer
-        with learning rate of $5\times10^{-3}$ and a scheduler to periodically
-        and temporarily increase the learning rate, encouraging the optimizer
+        slope parameter and we use a 3-layer \texttt{LTD} with shape (1, 32, 1)
+        and 15\% dropout. Background and stream are combined in a mixture model
+        whose mixture parameters are a 4-layer (1, 64, 1) \texttt{LTD} network.
+        We train the mixture model with an \texttt{AdamW} optimizer with
+        learning rate of $5\times10^{-3}$ and a scheduler to periodically and
+        temporarily increase the learning rate, encouraging the optimizer
         towards better minima.
@@
 
-        \begin{figure*}
-            \script{mock/plot/results.py}
+% sec: results_gd1 ---
+    \begin{figure*}[ht]
+        \script{gd1/plot/data_selection.py}
         \centering
-            \includegraphics[width=1\linewidth]{figures/mock/results.pdf}
-            \caption{
-                %
-                \textbf{Top panel: }%
-                    The stream mixture coefficient $f(\phi_1)$ (black dotted
-                    line) predicted by the model, overplotted on the true stream
-                    fraction (black-outlined histogram), calculated as the ratio
-                    of stream stars to total stars in 55 bins over the $\phi_1$
-                    range of the isochrone.  \textbf{Middle panel: }%
-                    $\phi_2(\phi_1)$ over the full range of $\phi_1$. The data
-                    color and transparency is set by the model's MLE stream
-                    probability (with dropout turned off). Plotted behind the
-                    data are the true labels for the stream stars (large black
-                    circles).  The true labels exactly limn the model-identified
-                    stream stars.  The MLE stream track (black dashed line) is
-                    over-plotted on the probability-colored data.
-                %
-                \textbf{Lower panel 3: }%
-                    $\parallax_2(\phi_1)$ over the full range of $\phi_1$. Like for
-                    $\phi_2$, the data color and transparency is set by the MLE
-                    probability, with the true labels (large black circles)
-                    under-plotted and MLE track (black dashed line)
-                    over-plotted.
-                %
-                \textbf{Upper Histograms: }%
-                    $\phi_2$ histograms for each model component (blue
-                    background, red stream), in 4 $\phi_1$ ranges across the
-                    data set.  The height of each bin is the
-                    probability-weighted density.  The background is a uniform
-                    distribution, while the stream is a Gaussian. In projection
-                    across the $\phi_1$ range it can appear multi-modal (panel
-                    2) if there are large gaps or `smeared' out (panel 3) if the
-                    Gaussian's mean changes significantly over the range.
-                %
-                \textbf{Upper Middle Histograms: }%
-                    Parallax $\parallax$ histograms for each model component (blue
-                    background, red stream), in 4 $\phi_1$ ranges across the
-                    data set.  The height of each bin is the
-                    probability-weighted density.
-                %
-                \textbf{Lower Middle and Lower Histograms:}%
-                    Photometric coordinate $(g, r)$ plots for each model
-                    component in 4 $\phi_1$ ranges across the data set. The top
-                    row plots the stream stars (red) over the background. The
-                    lower row plots the background stars (blue) over the stream
-                    stars to show that the how the two distributions mix.
-                %
-            }
-            \label{fig:mock_data_result}
-            TODO:
-            \begin{enumerate}
-                \item the linear density in the stream-fraction plot
-            \end{enumerate}
+        \includegraphics[width=1\linewidth]{figures/gd1/data_selection.pdf}
+        \caption{%
+            Data selections for \stream{GD-1}, within the data cube described in
+            \autoref{sub:results_gd1:data}.
+            %
+            \textbf{Row 1 Panels:}
+            Proper motion and photometric selections.  \stream{GD-1} is apparent
+            in the proper motions as a small overdensity. The photometric
+            selection is based on a 12 Gyr, [Fe/H] = -1.2 MIST isochrone,
+            buffered by 0.3 mag to select .
+            %
+            \textbf{Rows 2 \& 3 Panels:}
+            Applying the combination of astrometric and photometric selections,
+            plotted for astrometric coordinates $\phi_2, \parallax,
+            \mu_{\phi_1}, \mu_{\phi_2}$.  The proper motions are plotted
+            relative to \citetalias{Ibata+2021}. Using a log-density coloring,
+            the stream is identifiable in all phase-space coordinates except
+            $\parallax$ where the errors are significant.  }
+        \label{fig:gd1-data_selection}
     \end{figure*}
+% --- sec: results_gd1 (end)
 
@@
         when cutting on the 80\% membership probability threshold.
-        % The perfect recovery rate and low false identification rate
-        % demonstrate the efficacy of this method.
-
-        % Discussion why not finding the small-scale fluctuations?
 
@@
 
-    Having successful applied the density modeling framework to a mock stream,
-    we now apply the method to the stellar stream \stream{GD-1}.
-    % TODO: some reiteration on the importance of GD-1
-    We discuss the data selection in \autoref{sub:results_gd1:data}, model
-    specifics in \autoref{sub:results_gd1:model}, and the results in
+    We now apply our method for stream characterization to the stellar stream
+    \stream{GD-1}, initially discovered by \citet{GrillmairDionatos2006}.
+    Previous work has identified several density variations along \stream{GD-1}
+    \citep{deBoer+2018}, including a bifurcation that can be modeled by an
+    encounter with a dense dark matter subhalo \citep{Bonaca+2019, Webb+2019}.
+    Characterizing the detailed density fluctuations of this stream is therefore
+    important for constraining a population of perturbers.  We discuss the data
+    selection in \autoref{sub:results_gd1:data}, model specifics in
+    \autoref{sub:results_gd1:model}, and the results in
     \autoref{sub:results_gd1:results}.
@@
         \begin{itemize}
-            \item $\phi_1 \in [-100, 40] \ \rm{\degree}$,
-            \item $\phi_2 \in [-9, 5] \rm{\degree}$,
+            \setlength\itemsep{0em}
+            \item $\phi_1 \in [-100, 40] \ \rm{deg}$,
+            \item $\phi_2 \in [-9, 5] \ \rm{deg}$,
             \item $\parallax \in [-10, 1] \ \rm{mas}$,
-            \item $\rm{bp-rp} \in [-1, 3] \ \rm{mag}$
-            \item $g, r \in [0, 50] \ \rm{mag}$, and not \texttt{null}.
+            \item $G_{\rm BP} \in [-1, 3] \ \rm{mag}$
+            \item $g, r \in [0, 50] \ \rm{mag}$, %, and not \texttt{null},
         \end{itemize}
-        where we use \package{gala}'s \citep{gala, galav1.3}
-        \code{GD1Koposov10} frame \citep{Koposov+2010} to define $\phi_1$,
-        $\phi_2$, and associated proper motions.  For downloading purposes we
-        split the query into 10 sub-regions in even $\phi_1$ increments. A plot
-        of the $\phi_1, \phi_2$ regions is included in the
+        where we use \package{gala}'s \citep{gala, galav1.3} \code{GD1Koposov10}
+        frame \citep{Koposov+2010} to define $\phi_1$, $\phi_2$, and associated
+        proper motions.  For downloading purposes we split the query into 32
+        sub-regions in even $\phi_1$ increments.
+        A plot of the $\phi_1, \phi_2$ regions is included in the
         \href{\GitHubURL{}}{\package{ShowYourWork}} repository.  Stream-specific
@@
         is a three-dimensional dust map of the Milky Way for which we use
-        \Gaia's parallax distance information. For stars with missing parallax measurements we assume a distance of $8.5 \ \unit[kpc]$.  We include the $1-\sigma$ errors
-        as a source of uncertainty in $\mbs{\Sigma}_n$, the per-star photometric
-        uncertainty.
-        We also correct the parallax for the zero-point using the \code{gaiadr3-zeropoint} package, which implements the findings from \cite{Lindegren+2021}.
-        The result is a field populated by
-        \variable{output/gd1/ndata_variable.txt} stars, from which we would like
-        to identify stream members.
-
-        We create data masks for a more refined selection around \stream{GD-1}.
-        The two mask types, proper motion and photometric, are show in
-        \autoref{fig:gd1-data_selection}.  The proper motion masks select
-        rectangular regions, containing the primary overdensity of \stream{GD-1}
-        and a surrounding area following the tail of the distribution.  The
-        tighter mask (red) has corners $(\mu_{\phi_1}, \mu_{\phi_2}) =
-        [(-15,-10) (-4.5, -2)] \ \unit{mas/yr}$, while the larger mask (yellow)
-        has $(\mu_{\phi_1}, \mu_{\phi_2}) = [(-15,-5) (-5, -1)] \
-        \unit{mas/yr}$.  In photometric coordinates we define a mask around
-        % TODO: make these variables, like in mock
-        % TODO: change the actual isochrone used in the code to -1.2, not -1.3
-        a 12 Gyr, [Fe/H] = -1.2 isochrone at a distance of 7.8 kpc.
-        The selection region is a 0.2 dex orthogonal buffer around the MIST
-        isochrone \citep[using][]{brutus}, which is illustrated in the
-        2nd-from-the-top-left plot in \autoref{fig:gd1-data_selection}.  In
-        addition, to avoid detailed modeling of the completeness as a term in
-        $\prior_{obs}$ (from \autoref{eq:isochrone_prior_components}) we mask out
-        photometry with $G_{\Gaia{}} > 20$.  With combinations of these masks
-        the stream has much larger signal-to-noise, though is still only a small
-        percent of the total data.
-
-        \begin{figure*}[h]
-            \script{gd1/plot/data_selection.py}
-            \centering
-            \includegraphics[width=1\linewidth]{figures/gd1/data_selection.pdf}
-            \caption{%
-                Data selections for \stream{GD-1}, within the data cube
-                described in \autoref{sub:results_gd1:data}.
-                %
-                \textbf{Row 1 Panels:}
-                Proper motion selection boxes in red and yellow.  The right plot
-                shows the application of these selections.  \stream{GD-1} is
-                apparent from around $-60$ to $-10$ deg in the red selection and
-                present, if less clearly, in the yellow selection.
-                %
-                \textbf{Row 2 Panels:}
-                Photometric selection (blue curve). The selection is based on a
-                12 Gyr, [Fe/H] = -1.2 MIST isochrone, buffered by 0.2 dex.  The
-                right plot shows the application of this selection. By eye, the
-                stream is a small overdensity extending from $-50$ to $0$ deg.
-                %
-                \textbf{Row 3 Panels:}
-                Applying the combination of red astrometric and blue photometric
-                selections, plotted for astrometric coordinates $\phi_2, \parallax,
-                \mu_{\phi_1}, \mu_{\phi_2}$.  The stream is an identifiable
-                overdensity in all phase-space coordinates except $\parallax$ where
-                the errors are significant.
-                %
-                \textbf{Row 4 Panels:}
-                Applying the yellow astrometric and blue photometric selections,
-                plotted for the same astrometric coordinates as the above row.
-                In these coordinates the stream is clearly observable in
-                $\phi_2$ and very faintly in $\mu_{\phi_1}^*$.  }
-            \label{fig:gd1-data_selection}
-        \end{figure*}
+        \Gaia's position and parallax distance information. We note that the
+        extinction has very little dependence on the distance past $\approx 8 \
+        \rm{kpc}$. For stars with missing parallax measurements we assume a
+        distance of $8.5 \ \rm{kpc}$, a typical distance to the stream, thus
+        increasing potential membership probability. Adopting a slightly lower
+        or higher fiducial distance does not significantly change the results of
+        our analysis. We include the 1$\sigma$ errors as a source of uncertainty
+        in $\mbs{\Sigma}_n$, the per-star photometric uncertainty.  We also
+        correct the parallax for the zero-point using the
+        \href{https://pypi.org/project/gaiadr3-zeropoint/}{\code{gaiadr3-zeropoint}}
+        package, which implements the findings from \cite{Lindegren+2021}.  The
+        result is a field populated by \variable{output/gd1/ndata_variable.txt}
+        stars, from which we would like to identify stream members.
+
+        We create data masks for a higher signal-to-noise selection around
+        \stream{GD-1}.  The two mask types, proper motion and photometric, are
+        shown in \autoref{fig:gd1-data_selection}. For the proper motions we use
+        \citet{Ibata+2021} (hereafter \citetalias{Ibata+2021}) as the reference
+        for the known track of the stream. We select all all stars with
+        $\mu_{\phi_1}^*, \mu_{\phi_2}$ within 6 mas/yr of the track, as a
+        function of $\phi_1$. In \autoref{fig:gd1-data_selection} the proper
+        motion data are shown as the difference from the \citetalias{Ibata+2021}
+        track.  In photometric coordinates we define a mask around a $12 \
+        \rm{Gyr}$, [Fe/H] = $-1.2$ isochrone at a distance of $7.8 \ \rm{kpc}$.
+        The selection region is a $0.3 \ \rm{mag}$ orthogonal buffer around the
+        MIST isochrone \citep[using][]{brutus}, which is illustrated in the
+        2nd-from-the-top-left plot in \autoref{fig:gd1-data_selection}. The
+        buffered isochrone selection is wide enough to contain \stream{GD-1}
+        over its full distance gradient.  In addition, to avoid detailed
+        modeling of the completeness as a term in $\prior_{obs}$ (from
+        \autoref{eq:isochrone_prior_components}) we mask out photometry with $G
+        > 20$.  With combinations of these masks the stream has much larger
+        signal-to-noise, though is still only a small percent of the total data.
 
     \subsection{Model Specification}\label{sub:results_gd1:model}
-
-        The modeling framework, detailed in the \autoref{sec:method} sections, is
-        modular, allowing many model components to be combined, nested, added
-        to the mixture, and linked via priors.
-        The model we require for \stream{GD-1} is similar to 
-        the model built for the mock stream in \autoref{sub:results_mock:model},
-        but has additional components for \stream{GD-1}'s spur.
-        In this section we will discuss how the total model is built, noting 
-        similarities to the example mocks-stream model.
-
-        All full Bayesian stream models necessarily include a background model,
-        which we model in both astrometric and photometric spaces.
-        The photometric background is too complex to capture with simple analytic
-        distributions. Instead, we train a normalizing flow on the magnitudes $g, r$,
-        conditioned on $\phi_1$. We refer readers to
-        \autoref{sub:method:photometric_model:off_stream} for discussion of the photometric distribution and how a normalizing flow
-        can characterize this complex distribution, including its variation over $\phi_1$.
-        The flow's flexibility, while necessary in this context, also poses
-        a problem: the flow captures the stream as easily as the background.
-        Consequently we select on-stream and off-stream regions using the known
-        $\phi_1,\phi_2$ range of the stream, as shown in the
-        upper panel of \autoref{fig:gd1-photometric_background_selection}.
-        In the lower panel are plotted these selections in photometric coordinates,
-        where an isochrone is apparent in the on-stream selection.
-        The normalizing flow is trained on the off-stream selection, and will be
-        fixed (not trainable, nor contribute to the gradient) when incorporated into the larger model.
 
@@
             \includegraphics[width=1\linewidth]{figures/gd1/photometric_background_selection.pdf}
-            \caption{Caption}
+            \caption{%
+                The on and off-stream selection.
+                % 
+                \textbf{Top panel:} Astrometric coordinates ($\phi_1$,
+                $\phi_2$).  Light blue points are the stream and background
+                within an on-stream region. Black points are in the off-stream
+                region used to train the background photometric model. Note this
+                is on a reduced field with a tighter proper motion cut (the
+                stream visibly truncates at $-10 \ \rm{deg}$ to increase the
+                visibility of the stream's CMD).  The proper motion cut is $-15
+                < \mu_{\phi_1}^* < -10$, $-4.5 < \mu_{\phi_2} < -2$ [mas/yr].
+                %
+                \textbf{Bottom panel:} CMD pl got of the astrometric selection
+                above. The stream's isochrone is apparent as an overdensity.
+                %
+            }
             \label{fig:gd1-photometric_background_selection}
@@
 
-        Unlike for the photometry, the astrometric background may be (mostly) fit with simple analytic distributions.
+        The modeling framework, detailed in section \autoref{sec:method}, is
+        modular, allowing many model components to be combined, nested, added to
+        the mixture, and linked via priors.  The model we require for
+        \stream{GD-1} is similar to the model built for the mock stream in
+        \autoref{sub:results_mock:model}, but has additional components for
+        \stream{GD-1}'s spur.  In this section we will discuss how the total
+        model is built, noting similarities to the example mocks-stream model.
+
+        All full Bayesian stream models necessarily include a background model,
+        which we model in both astrometric and photometric spaces.  The
+        photometric background is too complex to capture with simple analytic
+        distributions.  Instead, we train a normalizing flow on the magnitudes
+        $g, r$, conditioned on $\phi_1$. We refer readers to
+        \autoref{sub:method:pre-training_distributions} for discussion of the
+        photometric distribution and how a normalizing flow can characterize
+        this complex distribution, including its variation over $\phi_1$.  The
+        flow's flexibility, while necessary in this context, also poses a
+        problem: the flow captures the stream as easily as the background.
+        Consequently we select on-stream and off-stream regions using the known
+        $\phi_1,\phi_2$ range of the stream, as shown in the upper panel of
+        \autoref{fig:gd1-photometric_background_selection}.  In the lower panel
+        are plotted these selections in photometric coordinates, where an
+        isochrone is apparent in the on-stream selection.  The normalizing flow
+        is trained on the off-stream selection, and will be fixed (not
+        trainable, nor contribute to the gradient) when incorporated into the
+        larger model.
+
+        Unlike for the photometry, the astrometric background could be (mostly)
+        fit with simple analytic distributions.  This is true if the selected
+        field is large enough -- the distribution in each coordinate is
+        approximately a skew-normal or a similarly tailed exponential-type
+        function. However by defining a higher signal-to-noise field around the
+        \citet{Ibata+2021} stream track in $\mu_{\phi_1}^*, \mu_{\phi_2}$, the
+        background in these coordinates is no longer well described by an
+        exponential distribution. Similarly, for much of the extent of
+        \stream{GD1's} field the parallax is well modeled by a truncated
+        skew-normal distribution, $\parallax \sim \rm{TruncSkew}\mcal{N}(\mu,
+        \Sigma; a, b)$, however for $\phi_1 \in [-100, -60]$ this does not hold.
+        Rather than splitting the model at a somewhat arbitrary $\phi_1$ or
+        interpolating between two distributions we instead fit the astrometry
+        with a $\phi_1$-conditioned normalizing flow.
+
         \begin{itemize}
-            \item $\phi_2, \mu_{\phi_1} \sim \rm{TruncExp}(\lambda; a, b)$:
-                a truncated exponential distribution (see \autoref{app:sub:exponential_distribution}). 
-                The distribution has 2 slope parameters (one per coordinate) and we use a 4-layer 
-                \texttt{LinTanh} neural network with shape (1, 64, 2) and 15\% dropout.
-            \item $\mu_{\phi_2} \sim \rm{Trunc}\mcal{N}(\mu, \Sigma; a, b)$:
-                a truncated normal distribution (see \autoref{app:sub:normal_distribution}).
-                The distribution has 4 parameters (2 per coordinate) and we use a 4-layer 
-                \texttt{LinTanh} neural network with shape (1, 32, 4) and 15\% dropout.
+            \item $\phi_2, \sim \rm{TruncExp}(\lambda; a, b)$: a truncated
+                exponential distribution (see
+                \autoref{app:sub:exponential_distribution}).  The distribution
+                has 1 slope parameters.
+            \item $\mu_{\phi_1}^*, \mu_{\phi_2}, \varpi \sim q_{\rm flow}$: a 3
+                feature, one context feature normalizing flow trained on an
+                off-stream selection (see
+                \autoref{fig:gd1-photometric_background_selection} for that
+                selection). Though discussed in the context of a photometric
+                background, \autoref{sub:method:pre-training_distributions}
+                details how these flows are constructed and trained.
         \end{itemize}
-        We also model the parallax $\parallax$ distribution. For much of the extent of
-        \stream{GD1's} field the parallax is well modeled by a truncated skew-normal
-        distribution, $\parallax \sim \rm{TruncSkew}\mcal{N}(\mu, \Sigma; a, b)$, however for
-        $\phi_1 \in [-100, -60]$ this does not hold. Rather then splitting the model at a
-        somewhat arbitrary $\phi_1$ or interpolating between two distributions \TODO{[CITE]}
-        we instead fit the parallax with a $\phi_1$-conditioned normalizing flow.
-        \todo[inline]{flow details}
-
-        We model the main stream of \stream{GD-1} similarly to the mock stream --
-        as an independent addition of both astrometric and photometric models.
-        The astrometric model is a 5-dimensional Gaussian in
-        a Gaussian track in $\phi_2, \parallax, \mu_{\phi_1}, \mu_{\phi_2}, \parallax$,
-        using the model defined in \autoref{ssub:method:astrometric_model:on_stream}.
-        The parameter network is a 5-layer \texttt{LinTanh} with shape (1, 128, 10),
-        where the 10 outputs are
-        $\mbs{\theta} = [\mu_{\phi_2}, \sigma_{\phi_2}, \mu_\parallax, \sigma_\parallax, \mu_{\mu_{\phi_1}^*},
-        \sigma_{\mu_{\phi_1}^*}, \mu_{\mu_{\phi_2}},
-        \sigma_{\mu_{\phi_2}}, \mu_\parallax, \sigma_\parallax](\phi_1)$.
-        In testing the network is sufficiently
-        large to permit 15\% dropout and retain robust predictions.
-
-        The photometric model is a distance modulus-shifted isochrone, using the
-        model from \autoref{ssub:method:photometric_model:on_stream}.
-        % We use the same isochrone parameters used in the photometric selection.
-        We use a 12 Gyr, [Fe/H] = -1.2 MIST isochrone with no assumed intrinsic dispersion.
-        Using the method described in \autoref{ssub:method:linking_to_astrometrics}
-        the distance modulus track is set by the parallax track in the astrometric model. Thus the photometric model has no independent parameters and consequently no neural network.
-        % TODO: talk about priors on the ishochrone, e.g PDM
+
+        We model the main stream of \stream{GD-1} similarly to the mock stream
+        -- as an independent addition of both astrometric and photometric
+        models.  The astrometric model is a 5-dimensional Gaussian in a Gaussian
+        track in $\phi_2, \parallax, \mu_{\phi_1}, \mu_{\phi_2}, \parallax$,
+        using the model defined in
+        \autoref{ssub:method:astrometric_model:on_stream}.  The parameter
+        network's
+        % is a 5-layer \texttt{LTD} with shape (1, 128, 10), where the
+        10 outputs are $\mbs{\theta} = [\mu_{\phi_2}, \sigma_{\phi_2},
+        \mu_\parallax, \sigma_\parallax, \mu_{\mu_{\phi_1}^*},
+        \sigma_{\mu_{\phi_1}^*}, \mu_{\mu_{\phi_2}}, \sigma_{\mu_{\phi_2}},
+        \mu_\parallax, \sigma_\parallax](\phi_1)$.  In testing the network is
+        sufficiently large to permit 15\% dropout and retain robust predictions.
+
+        The stream's photometric model is a distance modulus-shifted isochrone,
+        using the model from \autoref{ssub:method:photometric_model:on_stream}.
+        We use a $12 \ \rm{Gyr}$, [Fe/H]$ = -1.2$ MIST isochrone with no assumed
+        intrinsic dispersion.  Using the method described in
+        \autoref{ssub:method:linking_to_astrometrics} the distance modulus track
+        is set by the parallax track in the astrometric model. Thus the
+        photometric model has no independent parameters and consequently no
+        neural network.
+
+        \variable{output/gd1/control_points.tex}
 
         We model the spur of \stream{GD-1} as a separate component to the main
-        stream. We use an identical model as the stream: a 5-D astrometric Gaussian and isochrone in the photometry. We impose the prior that the spur and stream
-        share the same parallax and distance modulus.
-
-        The parameter phase-space is large and a random initialization will take significant
-        time to converge towards the stream track. This initial training is
-        unnecessary as the rough stream track is known \textit{a priori}.
-        To guide the astrometric model towards the known \stream{GD-1},
-        we set down ``control regions" (see \autoref{sub:methods:priors:track_region_prior})
-        along \stream{GD-1}'s main track and on the spur.
-        These control points act as Gaussian priors
-        on the model. We set the Gaussian error on these control points to large
+        stream. The spur has an identical model as the stream: a 5-D astrometric
+        Gaussian and isochrone in the photometry. Owing to their common origin,
+        we impose the prior that the spur and stream share the same isochrone.
+        The parallax is also shared, motivated by initial findings, and that
+        there were too few stars to robustly detect any deviations.
+
+        \variable{output/gd1/member_table_select.tex}
+
+        The parameter phase-space is large and a random initialization will take
+        significant time to converge towards the stream track. This initial
+        training is unnecessary as the rough stream track is known \textit{a
+        priori}.  To guide the astrometric model towards the known
+        \stream{GD-1}, we set down guides (see
+        \autoref{sub:methods:priors:track_region_prior}) along \stream{GD-1}'s
+        main track and on the spur.  We set the width of these guides to large
         values, so that their influence on the model is not dominant. Indeed, we
-        find that the value of the control points is to help reduce training
-        time, since otherwise it will take the flexible density model longer
-        time to converge to the actual stream.
-        We include all the track regions in \autoref{tab:gd1_track_prior}.
-        The main stream has six points: 3 of which apply to the distance modulus
-        and 4 which apply to $\phi_2$ and $\mu_{\phi_1}$.
-        The spur has 3 control points, but since the distance moduli between the stream and spur are linked, the stream control regions also apply.
-
-        \begin{table}
-            \centering
-            \setlength{\tabcolsep}{0pt}
-            \newcommand\capitem{\\$\phantom{+}\ast$\ }
-            \caption{%
-                Stream Track Regions Prior%
-                This table includes all the region priors used to guide the model towards the known stream track. The model will converge to the
-                region $_{\rm minimum}^{\rm maximum}$.
-                See \autoref{sub:methods:priors:track_region_prior} for details.
-            }
-            \label{tab:gd1_track_prior}
-            {\rowcolors{2}{gray!10}{white!10}
-            \begin{tabular}{@{}r<{\hspace{7pt}}*{4}{r<{\hspace{7pt}}}l<{\hspace{7pt}}@{}}
-                \toprule
-                component & $\phi_1 \,\unit{\degree}$ & $\phi_2 \,\unit{\degree}$ & $\mu_{\phi_1} \,[\frac{\rm{mas}}{\rm{yr}}]$ & $\mu \,\unit{mag}$ & $(\simeq \parallax \,\unit{mas})$ \\
-                \midrule
-                stream & -70 & & & $_{14.2}^{14.8}$ & $_{0.11}^{0.14}$ \\ 
-                stream & -60 & $_{-2.55}^{\phantom{+}0.95}$ & $_{-13.25}^{-11.75}$ & & \\ 
-                stream & -50 & $_{-1.75}^{\phantom{+}1.75}$ & $_{-14.05}^{-12.55}$ & & \\ 
-                stream & -40 & $_{-1.75}^{\phantom{+}1.75}$ & $_{-14.05}^{-12.55}$ & $_{14.1}^{ 14.7}$ & $_{0.11}^{0.15}$ \\
-                spur & -35 & $_{0.45}^{2.15}$ & $_{-15.95}^{\phantom{0}-9.95}$ & & \\
-                stream & -30 & $_{-1.75}^{\phantom{+}1.75}$ & $_{-13.35}^{-11.85}$ & $_{14.1}^{ 14.7}$ & $_{0.11}^{0.15}$ \\
-                spur & -30 & $_{0.45}^{2.15}$ & $_{-15.60}^{\phantom{0}-9.60}$ & & \\
-                spur & -20 & $_{0.65}^{2.35}$ & $_{-16.50}^{\phantom{0}-6.50}$ & & \\
-                stream & 0 &  & & $_{14.7}^{15.3}$ & $_{0.09}^{0.15}$ \\
-                \bottomrule\bottomrule
-            \end{tabular}
-            }
-        \end{table}
-
-        All the component models are tied together into a mixture model.
-        Instead of grouping together the stream components in a hierarchical
-        mixture model (background + (stream + spur)) we keep the structure flat,
-        using a single mixture (background + stream + spur) and reducing the number
-        of neural networks. The singular weight parameter network is a 4-layer (1, 32, 2) \texttt{LinTanh} network with 15\% dropout.
-        The stream weights are in the range $f \in [10^{-3}, 0.3]$, while 
-        the spur weights are $f \in [10^{-3}, 0.1]$ and set to 0 $\phi_1 < -45, -15 < \phi_1$.
-By \autoref{eq:mixture_weight_normalization} the background  brings the cumulative weight to one, normalizing the mixture.
+        find that the value of the guides is to help reduce training time, since
+        otherwise it will take the flexible density model much longer to
+        converge to the actual stream.  We include all the track regions in
+        \autoref{tab:gd1_track_prior}.  We note that since the distance moduli
+        between the stream and spur are linked, those stream track guides also
+        apply.
+
+        All the component models are tied together into a mixture model.  As an
+        implementation detail, instead of grouping together the stream
+        components in a hierarchical mixture model (background + (stream +
+        spur)) we keep the structure flat, using a single mixture (background +
+        stream + spur) and reducing the number of neural networks. The singular
+        weight parameter network is a \texttt{LTD} network with 15\% dropout.
+        The stream weights are in the range $\ln f \in [-10, 0]$, while the spur
+        weights are $\ln f \in [-10, 0]$ and set to 0 $\phi_1 < -45, -15 <
+        \phi_1$. By \autoref{eq:mixture_weight_normalization} the background
+        brings the cumulative weight to one, normalizing the mixture.
 
@@
 
-        \JN{TODO}
-
-        In this section we present results from our model applied to real {\it
-        Gaia} and Pan-STARRS data of \stream{GD-1}.
-
-        We visualize the performance of our model in identifying stream stars
-        and characterizing the astrometric background with
-        \autoref{fig:gd1-results-full} and \autoref{fig:gd1-results-panels}. In
-        \autoref{fig:gd1-results-full} The top panel shows the stream in
-        $\phi_1$, $\phi_2$ coordinates, color-coded by membership probability
-        (derived from \autoref{eq:membership_prob}). The following three rows
-        represent background distributions in $\phi_2, \mu_{\phi_1}, \rm{\ and}
-        \ \mu_{\rm phi_2}$, respectively taken at different $\phi_1$ increments
-        centered on the red lines. The $\phi_1$ increments are roughly $\sim X$
-        in size.
-
-        The blue lines over-plotted represent the best fit model at the given
-        $\phi_1$ slice. We find that the backgrounds are typically well
-        characterized by the distributions adopted (described in \S-x). We can
-        also see from \autoref{fig:gd1-results-panels} that the stream and spur
-        components appear to be well characterized.
-
-        Our ability to recover the stream is demonstrated further in
-        \autoref{fig:gd1-results-full}. In this figure, we only plot stars if
-        their membership probability is greater than \JN{X}. The result is a
-        ``gold" catalog of probable stream and spur members, extending over
-        $X$-degrees in $\phi_1$. We find the expected gap around $\phi_1 \sim
-        -20~\rm{deg}$, which has been proposed to be the location of the
-        dissolved progenitor (CITE).
-
-        Our model also fits the distribution of stream stars in the CMD. These
-        fits are illustrated in \autoref{fig:gd1-results-panels}, where the CMD
-        for the population in a given $\phi_1$ band is plotted, color-coded by
-        stream membership probability. For the on-stream regions, the isochrone
-        appears to provide a decent description of the stream, though there is
-        room for further improvements (discussed in \S-x). However, we note that
-        the stream's presence and absence in the isochrone is well captured by
-        the mixture weight, which is a neural network output.
-
-        Additionally, the distance modulus is also a neural network output,
-        conditioned on $\phi_1$. This allows us to obtain a distance modulus at
-        each $\phi_1$ along the stream. The distance modulus track and
-        (converted) distance track are illustrated in
-        \autoref{fig:gd1-results-full}. The left panel shows the distance
-        modulus (in magnitudes), while the right shows the corresponding
-        distance track. Importantly, the prior on the distance track is that the
-        stream must fall between $[4,40]~\rm{kpc}$. Thus, our ability to recover
-        the distance to \stream{GD-1} without substantial bias provides a useful
-        indicator that our color-magnitude model combined with the astrometric
-        model provide an adequate description of the data. \JN{more on this...}
-
-        \begin{figure*}[h]
+        \begin{figure*}[ht]
             \script{gd1/plot/results_full.py}
             \centering
-            \includegraphics[width=1\linewidth]{figures/gd1/results_full.pdf}
-            \caption{CAPTION}
+            \includegraphics[width=0.83\linewidth]{figures/gd1/results_full.pdf}
+            \caption{%
+                The model for \stream{GD-1}, including both a thin-stream and
+                spur component.  For comparison we include the tracks from
+                \citet{Price-WhelanBonaca2018} and \citet{Ibata+2021}. Note how
+                the model largely agrees with the latter track in all
+                astrometric dimensions.
+                %
+                \textbf{Panel 1: }%
+                    The stream mixture coefficients $f(\phi_1)$ predicted by the
+                    model, colored by the stream and spur membership likelihood.
+                %
+                \textbf{Panel 2: }
+                    $\phi_2(\phi_1)$ over the full range of $\phi_1$. The data
+                    color and transparency is set by the model's 50th-percentile
+                    stream and spur probability. We include the error bars for
+                    stars with $>75\%$ membership probability. The predicted
+                    50th-percentile track $\pm$ width is over-plotted (red
+                    band), along with the 90\% confidence region (broader red
+                    band).  In the adjoining top plot is shown the 5th to 95th
+                    percentile variation in the width.
+                %
+                \textbf{Panel 3 \& 4: }%
+                    $\parallax(\phi_1)$ and $d(\phi_1)$ over the full range of
+                    $\phi_1$. The $\parallax$ is tied to the photometry -- see
+                    \autoref{fig:gd1-results-panels}.
+                %
+                \textbf{Panel 5 \& 6: }%
+                    The proper motions $\mu_{\phi_1^*}, \mu_{\phi_2}$. The model
+                    convolves observational errors with the stream width, but
+                    the large fractional errors make the determination
+                    difficult. The track is consistent with 0 at $\mu_{\phi_2} <
+                    -40 \ \rm{deg}$, but has noticeable variations in
+                    $\mu_{\phi_1}$.  }
             \label{fig:gd1-results-full}
-            TODO:
-            \begin{itemize}
-                \item Add plot of the stream linear density
-                \item Color palette for the spur
-                \item more subtle stream MLE path
-                \item rerun model with larger pmphi2 sigma
-                \item add the isochrones to the cmd plots
-            \end{itemize}
         \end{figure*}
 
-        \begin{figure*}[h]
+        In this section we present results from our model applied to real {\it
+        Gaia} and Pan-STARRS data of \stream{GD-1}.  We visualize the
+        performance of our model in identifying stream stars in
+        \autoref{fig:gd1-results-full}, and illustrate our photometric fit in
+        \autoref{fig:gd1-results-panels}. In \autoref{tab:gd1_member_table} we
+        provide a selection of \stream{GD-1} member stars. The full catalog is
+        available online \TODO{add zenodo link when upload}. Lastly,
+        \autoref{fig:gd1-heatmap} is a probability-weighted density heatmap of
+        the \stream{GD-1} stream derived from our fit.
+
+        In \autoref{fig:gd1-results-full}, the top panels shows the fraction of
+        stars belonging to the stream (red) and spur (yellow) as a function of
+        $\phi_1$. The second panel illustrates the stream in $\phi_1$, $\phi_2$
+        coordinates, color-coded by the membership probability for the stream
+        and spur components (derived from \autoref{eq:membership_prob}). The
+        following rows represent the other astrometric dimensions for the stream
+        and spur components, with the distance track obtained through our
+        photometric model (visualized in \autoref{fig:gd1-results-panels} and
+        discussed below). The red and yellow bands represent model predictions
+        for in each panel for the main stream and spur, respectively. The points
+        with thick error bars represent control points (discussed in
+        \autoref{sub:results_gd1:model}) for the stream and spur components,
+        which are priors on the location of the stream and spur components
+        across the astrometric dimensions. The control points in the parallax
+        panel represent the reliable parallax and distance modulus estimates
+        from \citet{deBoer+2020}. The actual data points are color-coded by the
+        maximum membership probability of belonging to any of the three model
+        components (i.e., maximum of the main stream, spur, or background
+        components). For stars with membership probability greater than $75\%$,
+        we also plot their astrometric errorbars from \package{Gaia} as the thin
+        red lines.
+
+        \begin{figure*}[t]
             \script{gd1/plot/results_panels.py}
@@
             \includegraphics[width=1\linewidth]{figures/gd1/results_panels.pdf}
-            \caption{CAPTION}
-            TODO:
-            \begin{itemize}
-                \item Add plot of the stream linear density
-                \item Color palette for the spur
-                \item add the isochrones to the cmd plots
-            \end{itemize}
+            \caption{%
+                Photometric coordinate $(g, r)$ plots for each model component
+                in 4 $\phi_1$ ranges across the data set. Over-plotted is the
+                model isochrone, shifted to the mean distance of the track
+                within the bin of $\phi_1$. Importantly this means we don't
+                expect the mean isochrone to exactly match the distribution of
+                points. See \autoref{fig:gd1-results-full} for the match of the
+                distance gradient to the data and prior literature results.
+                %
+            }
             \label{fig:gd1-results-panels}
@@
 
-        \begin{figure*}
+        Because the neural networks are trained with dropout, we can estimate
+        the modeling uncertainty in our fits to each stream with a Monte Carlo
+        procedure \citep{GalGhahramani2015}. Namely, by incorporating dropout
+        during both neural network training and inference, the distribution of
+        model outputs represents the posterior predictive distribution,
+        marginalized over the neural network parameters. An estimate of this
+        distribution is shown in the weight parameter of
+        \autoref{fig:gd1-results-full}, represented as the red (main stream) and
+        yellow (spur) bands. For the astrometric dimensions, our model predicts
+        a mean track, and a standard deviation. Error bands are estimated by
+        incorporating dropout with a rate of 15\%. Each of the panels in
+        \autoref{fig:gd1-results-full} shows the track mean and width,
+        calculated from the 50th percentile of the posterior predictive
+        distribution for both quantities. Plotted behind that is the 90\%
+        credible region of the track mean. We note that the credible region of
+        the mean alone is generally larger than that of the $\mu \pm \sigma$
+        50th-percentile ridge. This highlights the importance of exploring the
+        full posterior of parameters, not only a Maximum Likelihood Estimation
+        (MLE) or posterior ridge-line.
+
+        Our model finds \variable{output/gd1/nstream/nstream_variable.txt}stars
+        that belong to the main stream component with membership probability
+        greater than
+        \variable{output/gd1/nstream/minimum_membership_probability.txt} at the
+        \variable{output/gd1/nstream/posterior_percentile.txt} percentile in the
+        membership posterior distribution. For the spur component, there are
+        \variable{output/gd1/nspur/nspur_variable.txt} stars with the same
+        membership probability threshold at the same percentile of the posterior
+        distribution.  A tabulation of the astrometry, photometry, and
+        membership posterior distribution for each star is included in
+        \autoref{tab:gd1_member_table}. The full table may be found on the
+        paper's
+        \href{https://github.com/nstarman/stellar_stream_density_ml_paper}{GitHub
+        repository}. \autoref{tab:gd1_member_table} gives the MLE prediction,
+        but also samples the 5th-95th percentile of the posterior distribution
+        of the likelihood using the dropout method. The variation in the 90\%
+        credible region in the track means there can be significant variation in
+        a star's estimated membership probability.
+
+        The extent of the main stream in $\phi_1$ is roughly $70~\rm{deg}$, and
+        the angular extent of the spur is roughly $25~\rm{deg}$. The distance
+        track (bottom panel) places the stream in the range of $6-10~\rm{kpc}$,
+        with an upwards concavity as a function of $\phi_1$. This result is
+        consistent with other works, which find a similar distance to
+        \stream{GD-1} using other techniques \citep{deBoer+2020, Ibata+2021}.
+        Importantly, our distance estimate is not hard-coded to fall in this
+        range: we allow for the stream track to fall anywhere within
+        $[4,40]~\rm{kpc}$, with a broad prior around previous literature
+        estimates. Therefore, the similarity of our inferred distance track
+        compared to other works indicates that our photometric model is
+        performing satisfactorily.
+
+        We also recover the well-known underdensity gaps along the stream around
+        $\phi_1 \approx -40, -20 \ \rm{and } -5~\rm{deg}$ (seen best in
+        \autoref{fig:gd1-heatmap}). The $-20\degree$ feature was first reported
+        by \citet{CarlbergGrillmair2013}, and is one location hypothesized for
+        the dissolved stream progenitor. \citep{WebbBovy2019} suggests the
+        $-40\degree$ gap might be  the progenitor location.  The recovery of
+        this density fluctuation from a joint model in astrometric and
+        photometric coordinates developed here argues that the feature is indeed
+        intrinsic to the stream and not an artifact of the data.
+
+        The spur is a distinct component of our model, independent in its weight
+        and all astrometric dimensions except $\parallax$ which is shared with
+        the \stream{GD-1} main stream through the photometric model. The model
+        finds a non-negligible spur feature, with fractional weight approaching
+        the thin stream at its peak. Corroborating this finding, the proper
+        motion of the spur almost exactly agrees with the thin stream. The
+        alignment of these dimensions is not hard-coded in our model. The width
+        of the spur in proper motion is very thin, thinner even than the stream.
+        However with the large observational errors and low number density of
+        the spur it is difficult to attribute this to a physical difference
+        between the two systems. In contrast, the small errors in $\phi_2$
+        indicate the spur's width diverges from the thin stream at $\phi_1 > -35
+        \ \rm{deg}$, whereas the width is similar at lower $\phi_1$. There are
+        numerous mechanisms by which a stream's width may vary \citep[e.g.
+        epicyclic effects as in][]{Ibata+2020}, so differences between the spur
+        and stream are both notable and expected.
+
+        We note that the model-predicted track does not always closely align
+        with the predicted member stars or our notion of a slowly-evolving
+        stream. This misalignment is most evident in $\mu_{\phi_1^*}$, where the
+        track has a sharp turn up at $\phi_1 \sim -65 \ \rm{deg}$ and then
+        flattens out. There are a number of contributing factors. First, the
+        observational uncertainties are large enough that this flattening is
+        consistent with the data. Second, we do not enforce the stream track to
+        be smooth with $\phi_1$ -- our fits are dictated by the data.  Last,
+        examining 2D slices when fitting in high dimensional spaces can be
+        misleading \citep{Aggarwal+2002}. Unsurprisingly, the raw membership
+        probabilities for each model component provide a more accurate
+        representation of the stream's 6d phase-space distribution than any
+        phase-space slice could, as may be seen in \autoref{fig:gd1-heatmap}. We
+        discuss the smoothed stream model determined solely by membership
+        probabilities at the end of this section.
+
+        We highlight the performance of our photometric model in
+        \autoref{fig:gd1-results-panels}. In this figure, we color-code each
+        star by its membership probability (top row; same as
+        \autoref{fig:gd1-results-full}), and in the bottom row we visualize the
+        performance of our photometric model in bands of $\phi_1$. Our model
+        isochrone, which shifts vertically due to our estimate of a distance
+        modulus, is shown in green (we plot the mean-distance isochrone in each
+        $\phi_1$ band). Because our model preforms a joint fit in photometry and
+        astrometry, the most probable stream members do not need to fall exactly
+        along the isochrone.  Still, the likely stream members are
+        overwhelmingly distributed as might be expected from a single-stellar
+        population.  Even the more diffuse tails of the stream can be seen in
+        the CMD distribution, where they still roughly follow a single-stellar
+        population.
+
+        With membership probabilities for each component of the stream estimated
+        from both astrometry and photometry, it is possible to quickly construct
+        a custom representation of the stream's phase-space density. We
+        illustrate this in  \autoref{fig:gd1-heatmap}, which shows a Gaussian
+        kernel density estimate (KDE) of bandwidth $0.1 \ \rm{deg}$ fit to the
+        model. The primary overdensities at $\phi_1 = (-50, -30, -10) \
+        \rm{deg}$ are all visible in $\phi_2$. The gap at $20 \ \rm{deg}$ is
+        prominent in all features, but the gap at $-40$ is less visible in
+        proper motions, since the spur shares the stream's proper motions and
+        thus contributes to the density in those coordinates. This highlights
+        the importance of constructing a multidimensional smooth density model
+        of streams.
+
+        \begin{figure}[h]
             \script{gd1/plot/smooth_likelihood.py}
             \centering
-            \includegraphics[scale=0.8]{figures/gd1/smooth_likelihood.pdf}
-            \caption{Caption}
+            \hspace{-25  pt}\includegraphics[width=1.1\linewidth]{figures/gd1/smooth_likelihood.pdf}
+            \caption{%
+                Smoothed KDE model of \stream{GD-1}'s member stars, weighted by
+                their membership probability. The KDE has a bandwidth of $0.1 \
+                \rm{deg}$.  In $\phi_2$ the spur is clearly visible in the KDE.
+                The gaps at $-20\degree$ is prominent in both $\phi_2$ and
+                $\mu_{\phi_1}$.  The gap at $-40\degree$ is most prominent in
+                $\phi_2$.
+                %
+            }
             \label{fig:gd1-heatmap}
-        \end{figure*}
-
-        \variable{output/gd1/member_table_select.tex}
+        \end{figure}
 
@@
 
-\section{Palomar 5} \label{sec:results_pal5}
+% \newpage
+\section{Results: Palomar 5} \label{sec:results_pal5}
 
     We now apply the method to the stellar stream \stream{Palomar 5}.
-    % TODO: some reiteration on the importance of Pal5
+    Historically lengths of the stream have been found with matched filter
+    photometric techniques, like with the discovery in \citet{Odenkirchen+2001}.
+    Post-\package{Gaia} the stream was also observed by filtering kinematically
+    \cite[e.g.,][]{Starkman+2019, Ibata+2021}.  However at $\sim 20 \ \rm{kpc}$,
+    the \stream{Pal\,5} main sequence is not observed by \package{Gaia}, making
+    a high signal-to-noise astrometric detection challenging.
+    %In this work we detect over $10 \ \rm{deg}$ of stream.
     We discuss the data selection in \autoref{sub:results_pal5:data}, model
@@
 
-        \todo[inline]{rephrase (numbers are correct, phrasing is from GD-1}
-
-        We utilize data from \Gaia{} DR3 for the astrometric coordinates of each
-        star.  To obtain more accurate color information, we cross-match the
-        \Gaia{} field on \PanStarrs{} \citep{PanSTARRS1} using \Gaia's provided
-        \texttt{Best-neighbors} catalog.  To limit the field to a region known
-        to contain \stream{Pal\;5} we adopt broad cuts on the cross-matched data.
-        We perform these rough cuts by requiring the data lie within the
-        phase-space cube:
+        We construct a \Gaia{} DR3 - \PanStarrs{} crossmatched field very
+        similarly to the procedure outlined in \autoref{sub:results_gd1:data}
+        for \stream{GD-1}.  To limit the field to a region containing
+        \stream{Pal\;5} we adopt broad cuts on the data by requiring the data
+        lie within the phase-space cube:
         \begin{itemize}
-            \item $\phi_1 \in [-30, 30] \ \rm{\degree}$,
-            \item $\phi_2 \in [-5, 10] \rm{\degree}$,
+            \setlength\itemsep{0em}
+            \item $\phi_1 \in [-20, 20] \ \rm{deg}$,
+            \item $\phi_2 \in [-5, 10] \ \rm{deg}$,
             \item $\parallax \in [-10, 1] \ \rm{mas}$,
-            \item $\rm{G-R} \in [-1, 3] \ \rm{mag}$
-            \item $g, r \in [0, 50] \ \rm{mag}$,
+            \item $\rm{G-R} \in [-0.5, 1.2] \ \rm{mag}$
+            \item $g, r \in [0, 30] \ \rm{mag}$,
         \end{itemize}
-        where we use \package{gala}'s
-        \code{Pal5PriceWhelan18} frame \citep{Price-Whelan+2019} to define $\phi_1$,
-        $\phi_2$, and associated proper motions.  For downloading purposes we
-        split the query into 10 sub-regions in even $\phi_1$ increments. A plot
-        of the $\phi_1, \phi_2$ regions is included in the
-        \href{\GitHubURL{}}{\package{ShowYourWork}} repository.
-        % ...
-        We correct the \PanStarrs{} photometry for dust
-        extinction using the \textit{Bayestar19} \citep{Green+2019} models in
-        the \package{dustmaps} package \citep{Green2018}.
-        For stars with missing parallax measurements we assume a distance of $8.5 \ \unit{kpc}$.  We include the $1-\sigma$ errors
-        as a source of uncertainty in $\mbs{\Sigma}_n$, the per-star photometric
-        uncertainty.
-        We also correct the parallax for the zero-point using the \code{gaiadr3-zeropoint} package, which implements the findings from \cite{Lindegren+2021}.
-        The result is a field populated by
-        \variable{output/pal5/ndata_variable.txt} stars, from which we would like
-        to identify stream members.
-
-        We create data masks for a more refined selection around \stream{Pal\;5}.
-        The two mask types, proper motion and photometric, are show in
-        \autoref{fig:gd1-data_selection}.  The proper motion masks select
-        rectangular regions, containing the primary overdensity of \stream{Pal\;5}
-        % and a surrounding area following the tail of the distribution.  The
-        % tighter mask (red) has corners $(\mu_{\phi_1}, \mu_{\phi_2}) =
-        % [(-15,-10) (-4.5, -2)] \ \unit{mas/yr}$, while the larger mask (yellow)
-        % has $(\mu_{\phi_1}, \mu_{\phi_2}) = [(-15,-5) (-5, -1)] \
-        % \unit{mas/yr}$.  In photometric coordinates we define a mask around
-        % % TODO: make these variables, like in mock
-        % % TODO: change the actual isochrone used in the code to -1.2, not -1.3
-        % a 12 Gyr, [Fe/H] = -1.2 isochrone at a distance of 7.8 kpc.
-        % The selection region is a 0.2 dex orthogonal buffer around the MIST
-        % isochrone \citep[using][]{brutus}, which is illustrated in the
-        % 2nd-from-the-top-left plot in \autoref{fig:gd1-data_selection}.
-        In
-        addition, to avoid detailed modeling of the completeness as a term in
-        $\prior_{obs}$ (from \autoref{eq:isochrone_prior_components}) we mask out
-        photometry with $G_{\Gaia{}} > 20$.  With combinations of these masks
-        the stream has much larger signal-to-noise, though is still only a small
-        percent of the total data.
+        where we use \package{gala}'s \code{Pal5PriceWhelan18} frame
+        \citep{Price-Whelan+2019} to define $\phi_1$, $\phi_2$, and associated
+        proper motions.  Using the \textit{Bayestar19} maps we correct the
+        \PanStarrs{} photometry for dust extinction.  For stars without distance
+        information we assume a distance of $20 \ \rm{kpc}$, a typical distance
+        to the stream \citep{Harris1996, Odenkirchen2003, Grillmair2006,
+        Ibata+2016, Price-Whelan+2019} and thus increasing the probability of
+        the star being considered a member.  The 1$\sigma$ dust correction
+        errors are included by quadrature in $\mbs{\Sigma}_n$, the per-star
+        photometric uncertainty. We also correct the parallax for the \Gaia\
+        zero-point as in \autoref{sub:results_gd1:data}.  The result is a field
+        populated by \variable{output/pal5/ndata_variable.txt} stars, from which
+        we would like to identify stream members.
+
+        Within the broad selection cuts, we create more specific data masks.  In
+        particular we mask concentrated over-densities, like the globular
+        cluster \stream{M5}, that are not associated with \stream{Pal\;5}.  In
+        \autoref{fig:pal5-data_selection} we show the proper motion and
+        photometric masks, with \stream{M5} already filtered out.  The proper
+        motion mask extends from $\mu_{\phi_1}$ and $\mu_{\phi_2} \in (-4, -1)$
+        [mas/yr].  The photometric mask is defined by a $0.15 \ \rm{mag}$ buffer
+        around a $[\rm{Fe}/{H}] = -1.3$, $11.5 \ \rm{Gyr}$ isochrone. It is the
+        shape of the isochrone which is important, not the physical reality of
+        the metallicity nor age, discussed in further detail in
+        \autoref{ssub:method:photometric_model:on_stream}.  In addition, to
+        avoid detailed modeling of the completeness as a term in $\prior_{obs}$
+        (from \autoref{eq:isochrone_prior_components}) we mask out photometry
+        with $G > 20$.  With combinations of these masks the stream has much
+        larger signal-to-noise, though is still only a small fraction of the
+        total data.
+
+        \begin{figure*}[ht]
+            \script{pal5/plot/data_selection.py}
+            \centering
+            \includegraphics[width=1\linewidth]{figures/pal5/data_selection.pdf}
+            \caption{%
+                Data selections for \stream{Pal\,5}, within the data cube
+                described in \autoref{sub:results_pal5:data}.
+                %
+                \textbf{Row 1 Panels:}
+                Proper motion and photometric selections.  \stream{Pal\,5} is
+                apparent in the proper motions as a small overdensity. The
+                photometric selection is based on a 12 Gyr, [Fe/H] = -1.2 MIST
+                isochrone, buffered by 0.3 dex.
+                %
+                \textbf{Rows 2 \& 3 Panels:}
+                Applying the combination of astrometric and photometric
+                selections, plotted for astrometric coordinates $\phi_2,
+                \parallax, \mu_{\phi_1}, \mu_{\phi_2}$.  The stream is an
+                identifiable overdensity in only $\phi_2$ and errors dominate
+                all other coordinates.  }
+            \label{fig:pal5-data_selection}
+        \end{figure*}
+
+        The reduced dataset, with all specific masks applied, is included below
+        the data mask plots in \autoref{fig:pal5-data_selection}. In $\phi_2$,
+        $\mu_{\phi_1}^*$, and $\mu_{\phi_2}$ the \stream{Pal\,5} progenitor is
+        clearly visible. Only in $\phi_2$ is the stream visible, and then only
+        for a few degrees around the progenitor. The distance of \stream{Pal\,5}
+        means most $\parallax$ measurements have $\sim 100\%$ errors, so neither
+        the stream nor even the progenitor are evident.
 
@@
 
-        \todo[inline]{rephrase (numbers are correct, phrasing is from GD-1}
+        In this section we discuss how the total \stream{Pal\,5} model is built,
+        using the modular modeling framework from \autoref{sec:method}.  We
+        model the stream of \stream{Pal\;5} as a single Gaussian component
+        conditioned on $\phi_1$. As a function of $\phi_1$, the astrometric
+        stream density is a 3-dimensional Gaussian in $\phi_2, \mu_{\phi_1},
+        \mu_{\phi_2}$, using the model defined in
+        \autoref{ssub:method:astrometric_model:on_stream}.  The parameter
+        network is a 5-layer \texttt{LTD} where the 6 outputs are $\mbs{\theta}
+        = [\mu_{\phi_2}, \sigma_{\phi_2}, \mu_{\mu_{\phi_1}^*},
+        \sigma_{\mu_{\phi_1}^*}, \mu_{\mu_{\phi_2}},
+        \sigma_{\mu_{\phi_2}}](\phi_1)$.  In testing, the network is
+        sufficiently large to permit 15\% dropout and retain robust predictions.
+        At $\sim 20 \ \rm{kpc}$ any \package{Gaia}-crossmatched data is not
+        photometrically deep enough to contain the main sequence nor its turn
+        off. Thus we do not model the stream photometrically. We only use
+        photometric cuts to remove some background. Similarly, we do not include
+        the parallax as the errors are too large for the parallax to contribute
+        to the model.
+
+        \begin{figure}[ht]
+            \script{pal5/plot/photometric_background_selection.py}
+            \centering
+            \includegraphics[width=1\linewidth]{figures/pal5/photometric_background_selection.pdf}
+            \caption{%
+                \textbf{Top panel:} Astrometric coordinates ($\phi_1$,
+                $\phi_2$).  Light blue points are the stream and background
+                within an ``on"-stream region. Black points are in the
+                ``off"-stream region used to train the background photometric
+                model. The \stream{M5} cluster is masked as a black circle
+                cutting into the on-stream selection at $\phi_1\sim-1\degree$.
+                %
+                \textbf{Bottom panel:} CMD plot of the astrometric selection
+                above. The stream's isochrone is somewhat apparent, but the
+                background contamination is large.
+                %
+            }
+            \label{fig:pal5-photometric_background_selection}
+        \end{figure}
+
+        To avoid a large convergence time, we use as a prior the known stream
+        track, in this case \package{galstream}'s \citep{Mateu2022}
+        implementation of \stream{Pal\,5} from \citet{Ibata+2021}. From the
+        track, we set down guides (see
+        \autoref{sub:methods:priors:track_region_prior}) regularly spaced in
+        $\phi_1$. We include all the guides in \autoref{tab:pal5_track_prior}.
+        We don't place guides in the other coordinates, except at the location
+        of the progenitor, because the stream is not visible and the models
+        disagree on the proper motions (see \autoref{fig:pal5-data_selection},
+        top left plot).  The progenitor is an exception, both visible
+        kinematically and also extremely well measured
+        \citep{VasilievBaumgardt2021}, and we place a tight kinematic prior on
+        the stream track at the location of the progenitor.  The guide priors
+        are visible in \autoref{fig:pal5-results-full}.
+        \variable{output/pal5/control_points.tex}
+
+        The background is fit with an analytic distribution and a normalizing
+        flow:
+        \begin{itemize}
+            \setlength\itemsep{0em}
+            \item $\phi_2 \sim \rm{TruncExp}(\lambda; a, b)$: a truncated
+                exponential distribution (see
+                \autoref{app:sub:exponential_distribution}).  The distribution
+                has 1 parameter and we use a \texttt{LTD} neural network with
+                15\% dropout.
+            \item $\mu_{\phi_1}, \mu_{\phi_2} \sim q_{\rm flow}$: a two feature,
+                one context feature normalizing flow trained on an off-stream
+                selection (see
+                \autoref{fig:pal5-photometric_background_selection} for that
+                selection). \autoref{sub:method:pre-training_distributions}
+                details how these flows are constructed and trained.
+        \end{itemize}
+
+        All the component models are tied together into a mixture model.  The
+        weight parameter network is the usual \texttt{LTD} with 15\% dropout.
+        The stream weights are in the range $\ln{f_{\rm stream}} \in [-10, 0]$
+        and set to $-\infty$ for $\phi_1 \notin [-10^\circ, 10^\circ]$. By
+        \autoref{eq:mixture_weight_normalization} the background  brings the
+        cumulative weight to one, normalizing the mixture.
 
@@
 
+        \begin{figure*}[ht]
+            \script{pal5/plot/results_full.py}
+            \centering
+            \includegraphics[width=0.85\linewidth]{figures/pal5/results_full.pdf}
+            \caption{%
+                The model for \stream{Pal\,5}.  For comparison we include the
+                tracks from \citet{Price-Whelan+2019} and \citet{Ibata+2021}.
+                Note how the model largely agrees with both tracks in all
+                astrometric dimensions from $-5 < \phi_1 < 5 \ \rm{deg}$. The
+                stream fraction and number density drop to near $0$ for $5 \
+                \rm{deg} < \phi_1$, making the track dominated by low-number
+                statistics. The progenitor is not separated from the stream as a
+                distinct component, demonstrating how the neural networks can
+                capture a large range of linear densities.
+                %
+                \textbf{Panel 1: }%
+                The stream mixture coefficients $f(\phi_1)$ predicted by the
+                model, colored by the stream membership likelihood.
+                %
+                \textbf{Panel 2: }
+                $\phi_2(\phi_1)$ over the full range of $\phi_1$. The two stream
+                arms visibly emerge from the Lagrange points of the stream.  The
+                data color and transparency is set by the model's
+                50th-percentile stream and spur probability. We include the
+                error bars for stars with $>75\%$ membership probability. The
+                predicted 50th-percentile track $\pm$ width is over-plotted (red
+                band), along with the 90\% confidence region (broader red bend).
+                In the adjoining top plot is shown the 5th to 95th percentile
+                variation in the width.
+                %
+                \textbf{Panel 3: }%
+                $\parallax(\phi_1)$ and $d(\phi_1)$ over the full range of
+                $\phi_1$.
+                %
+                \textbf{Panel 4 \& 5: }%
+                The proper motions $\mu_{\phi_1^*}, \mu_{\phi_2}$. The model
+                convolves observational errors with the stream width, but the
+                large fractional errors make the determination difficult. The
+                track is largely consistent with 0 width driven by small number
+                statistics.  }
+            \label{fig:pal5-results-full}
+        \end{figure*}
+
+        \begin{figure*}[htp]
+            \script{pal5/plot/results_panels.py}
+            \centering
+            \includegraphics[width=1\linewidth]{figures/pal5/results_panels.pdf}
+            \caption{%
+                Photometric coordinate $(g, r)$ plots for each model component
+                in 5 $\phi_1$ ranges across the data set, centered on the
+                \stream{Pal\,5} progenitor.
+                %
+                On either side of the progenitor we strongly detect the stream
+                for $\approx 5\degree$  and tentatively for an additional
+                $\approx 5\degree$. The leading arm (positive $\phi_1$) track
+                for $\phi_1 > 5\degree$ is consistent with
+                \citet{Starkman+2019}. We do detect any fanning of the stream,
+                but given the shallow photometry, this is expected.
+                %
+            }
+            \label{fig:pal5-results-panels}
+        \end{figure*}
+
+        \variable{output/pal5/member_table_select.tex}
+
+        Our fit to \stream{Pal\,5} and its tidal tails is illustrated in
+        \autoref{fig:pal5-results-full}. In the top panel we plot the stream
+        fraction and its uncertainty, estimated by applying dropout during
+        inference and evaluation of our model. The model clearly identifies the
+        progenitor cluster $(\phi_1 = 0)$.
+
+        The membership probability of stream stars is illustrated in subsequent
+        panels of \autoref{fig:pal5-results-full}, with guide points and their
+        widths shown in red. The leading and trailing arms of the stream are
+        clearly identified in our fits, with high membership probability on
+        either side of the cluster. Our model prefers a thin on-sky morphology
+        for \stream{Pal\,5}'s tidal tails, with an angular width of the stream
+        (parameterized by $\ln{\sigma_{\phi_2}}$) around $\sim 0.1~\rm{deg}$.
+        This is contrary to our fit of \stream{GD-1} in
+        \autoref{fig:gd1-results-full}, where we find a more appreciable width
+        of $\sim 0.2~\rm{deg}$ and above.  This inferred width is consistent
+        with \stream{Pal\,5} being more distant than \stream{GD-1}, though we
+        expect a thin inferred width for \stream{Pal\,5} since we do not model
+        the stream in photometric coordinates. When photometry is available, we
+        expect that our photometric model provides substantial constraining
+        power in characterizing the stream, since diffuse parts of the tidal
+        tails in on-sky angular coordinates remain tightly clustered in the CMD.
+        This clustering is seen in our \stream{GD-1} fits
+        (\autoref{fig:gd1-results-panels}), where even the more extended parts
+        of the stream remain clustered in the CMD.
+
+        The parallax, proper motion tracks, and their widths are also shown in
+        \autoref{fig:pal5-results-full}. The red vertical lines represent the
+        astrometric errors in each dimension, shown only for stars with
+        membership probability greater than $75\%$. The errors are large
+        compared to the width of the best fit stream track (shown as the red
+        band). The track is a valid minimum to our loss function: because our
+        model incorporates the large astrometric uncertainties, small variations
+        to the estimated width of the stream in each dimension do not produce
+        substantial changes to the loss function. Thus, a narrow stream in the
+        kinematic dimensions provides a valid fit to the stream given the data
+        at hand.
+
+        We also note that the track of the stream shown as the red band in each
+        dimension appears to have an abrupt change in direction around $\phi_1
+        \approx 7^\circ$. This also represents the region with the lowest stream
+        fraction, as seen in the top panel of \autoref{fig:pal5-results-full}.
+        In low stream fraction regions, the model is uncertain about the track
+        of the stream since only a few stars contribute to the on-stream fit.
+        The track changes highlight the importance of utilizing the membership
+        probabilities of individual stars when analyzing any given stream, since
+        membership probabilities incorporate information on the stream fraction
+        while the mean stream-track alone does not provide this information.
+
+        In \autoref{fig:pal5-results-panels} we again show the data in
+        $\phi_1-\phi_2$ coordinates, color-coded by membership probabilities in
+        the top panel (same colorbar as in \autoref{fig:pal5-results-full}). In
+        the bottom panels we plot the CMD of the data in bands of $\phi_1$. As
+        discussed, our fit to \stream{Pal\,5} does not incorporate information
+        from the CMD.  Thus, the bottom row represents a data-driven isochrone
+        for \stream{Pal\,5} and its tidal tails, obtained by fitting the
+        stream's astrometric overdensity. Indeed, the highest probability
+        regions of the CMD appear qualitatively similar to a standard isochrone,
+        with an extended and clustered sequence. The main sequence appears to be
+        missing, which is expected given our cut at $G = 20~\rm{mag}$, below
+        which the main sequence of \stream{Pal\,5} resides \citep{Bonaca+2020}.
+        The similarity of the color-magnitude distribution of \stream{Pal\,5}'s
+        tidal tails to the red end of a standard isochrone highlights the
+        validity of our astrometric membership model, since a photometric fit
+        was never performed.
+
+        The stream solution, ie the per-star membership likelihood, is a
+        posterior distribution. \autoref{fig:pal5-results-full} and
+        \autoref{fig:pal5-results-panels} show the membership likelihood
+        evaluated at the $50$th percentile of this distribution, per star. In
+        \autoref{fig:pal5-heatmap} we sample over the full distribution and
+        smooth by a 0.1 $deg$ kernel to produce a smooth representation of the
+        stream. As a consequence of the sampling we see the model's stream
+        solution extends beyond the $\approx \pm5\degree$ shown previously.
+        Though the model certainty and individual membership likelihoods are
+        low, the stream path matches closely with findings in deeper photometric
+        catalogues, like \citet{Ibata+2017}.
+
+        \begin{figure}[h]
+            \script{pal5/plot/smooth_likelihood.py}
+            \centering
+            \includegraphics[width=1\linewidth]{figures/pal5/smooth_likelihood.pdf}
+            \caption{%
+                Smoothed KDE model of the stream's member stars, weighted by
+                their membership probability. The KDE has a bandwidth of $0.1 \
+                \rm{deg}$. We exclude the progenitor to limit the density range
+                and better display the diffuse tidal tails. The stream extends
+                from $-12$ to $10$ degrees in this plot, which appears longer
+                than in \autoref{fig:pal5-results-full} and
+                \autoref{fig:pal5-results-panels}. Those show the membership
+                likelihood at the $50$th-percentile of its distribution. This
+                figure samples over the full posterior, showing the contribution
+                of less-likely members.
+                %
+            }
+            \label{fig:pal5-heatmap}
+        \end{figure}
+
+        While \package{Gaia} alone is not photometrically capable of observing
+        the main sequence of \stream{Pal\,5}'s tidal tails, the modeling
+        framework we present here is capable of operating on outer-joined
+        datasets. This allows us to easily combine deep photometric data with
+        kinematics from, e.g., \package{Gaia}.  We leave that to a future work,
+        though expect that a simultaneous model in photometry and astrometry
+        would help identify the more diffuse parts of the stream, which become
+        washed out in our astrometric fit due to the substantial number of
+        background stars. Still, this section highlights the capability of our
+        model when applied to a noisy field with a diffuse stream.
+
     % sub trained_density_model
@@
 
-% section results (end)
-
-\section{Discussion}
-
-    \subsection{Review of detection methods}
-        \todo[inline]{is this section necessary?}
-
-        Identifying streams of globular of clusters is a challenging task.
-        Streams are very low signal-to-noise structures spread over
-        comparatively large regions of the sky. They live in a vast background
-        of field stars.
-
-        Historically streams were detected by matched-filter techniques
-        % Add citations
-        You took an isochrone and shifted it by a distance modulus until a
-        stream stood out in longitude and latitude as an extended overdensity
-        structure.
-
-        With the advent of Gaia, we gained access to detailed astrometric data.
-        For most streams this
-
-        poses a challenging task due to their intricate and diffuse nature from
-        large-scale surveys is challenging due to the complex and overlapping
-        distributions of stars in different regions of the sky; disentangling
-        members from the vast background of field stars
-
-        \begin{enumerate}
-            \item Streamfinder \citep{STREAMFINDER}. This method requires the
-            potential
-            \item VIA MACHINAE \citep{Shih+2022}
-            \item Kiyan and Adrian
-            \item Matched Filter
-            \item Gaia stuff: Adrian and Ana and Sara et al
-            \item Uniform Modeling of 12 Stellar stream \citep{Patrick+2022}.
-            Only on phi1, phi2, and CMD. Their CMD method is more sophisticated.
-            Worth discussing.
-        \end{enumerate}
-
-    \subsection{Comparison to Other Methods} \label{sec:comparison}
-
-        \subsubsection[STREAMFINDER]{\cite{STREAMFINDER}}
-
-            Assumes a potential
-
-        % sub: streamfinder (end)
-
-        \subsubsection{VIA MACHINAE}{\cite{Shih+2022}}
-
-            Only astrometric.
-
-        % sub: via_machinae (end)
-
-        \subsubsection[Uniform Modeling of 13 Stellar
-        Streams]{\cite{Patrick+2022}}
-
-            Doesn't do simultaneous modeling.
-
-        % sub: uniform_modeling_of_13_stellar_streams (end)
-
-\section{Conclusions} \label{sec:conclusions}
+\section{Discussion} \label{sec:discussion}
+
+    We now provide a discussion of the methods presented in the paper, focusing
+    on future directions in \autoref{sec:conclusions} and comparison to other
+    works in \autoref{sec:comparison}.
+
+    \subsection{Limitations}\label{sec:limitations}
+
+        We first highlight the limitations of our method, and areas for
+        potential improvement.
+
+        First, our usage of neural networks ensures that our method is
+        expressive, and capable of describing a diverse range of stream
+        morphologies all under one unified framework. At the same time, neural
+        network training is computationally expensive, and takes a long time on
+        a local device. Our fits to \stream{GD-1} and \stream{Pal\,5} presented
+        in this work were performed on a local computer without GPU support,
+        though training time takes on the order of a few hours per stream. This
+        can be improved substantially with the use of GPUs.
+
+        Second, our fits to \stream{GD-1} in \S\ref{sec:results_gd1} rely on a
+        theoretical isochrone. While the stream does appear to be decently
+        characterized by a theoretical isochrone, there is room for improvement.
+        Especially considering that globular clusters do not always follow
+        simple single-stellar population (see, e.g.,
+        \citealt{2022Univ....8..359M} for a review of this subject), it is worth
+        considering whether more data-driven approaches can be used to model the
+        photometry of a stream without imposing tight priors on the stellar
+        population.
+
+        Third, we have used a combination of analytic distributions and more
+        flexible machine learning methods like normalizing flows to describe the
+        distribution of background stars. However, the field of the Galaxy is
+        complicated, in all coordinates. The analytic distributions in our
+        modeling are clearly approximate. While the analytic distributions might
+        be made more complex, the alternative is to substitute for
+        non-parameteric flexible models. We have postponed this to future work,
+        since the analytic backgrounds provide a decent description in the
+        fields of \stream{GD-1} and \stream{Pal\,5}. However, this might not be
+        the case for other streams. Constructing flexible background models will
+        therefore provide further improvement over our method.
+
+        Finally, our method is suited for characterizing streams rather than
+        detecting them. Thus, some amount of supervised work is required to
+        reduce the data down to a clean enough selection of stars so that our
+        model can converge to a high likelihood solution. If the field is too
+        noisy and control points cannot be reliably placed, our method might not
+        be able to characterize the stream of interest. An end-to-end stream
+        discovery and detailed characterization algorithm could therefore
+        provide a substantial improvement over our method and existing work.
+
+    \subsection{Comparison to Existing Methods} \label{sec:comparison}
+
+        There are several existing methods for the detection of stellar streams,
+        and some existing work on detailed stream characterization. Here we
+        briefly overview the existing methods, and highlight commonalities and
+        differences between the results of our work and previous studies.
+
+        Currently, the matched filter is the most common method for detecting
+        and characterizing streams. The method works by selecting a stellar
+        population in the CMD (i.e., from a metal-poor isochrone) and searching
+        for a stellar overdensity in the astrometric data. The approach has
+        proved successful for stream detection, but to a lesser extent for
+        characterization. From the matched filter approach alone, stream
+        membership probabilities are not obtained and there is substantial
+        contamination from background stars. While the approach can provide an
+        excellent coarse-grained description of a given stream, it does not
+        provide a density model in astrometry and photometry.
+
+        To a good approximation streams are expected to roughly trace a stellar
+        orbit. The Streamfinder algorithm exploits this physical expectation
+        \citep{STREAMFINDER}, by integrating orbits in a trial Galactic
+        potential and identifying stellar overdensities that appear to coincide
+        with the trial orbits. While the method has identified many stream
+        candidates, using these streams for potential reconstruction is circular
+        in reasoning. That is, the detection and characterization of these
+        streams is conditioned on a choice of the potential. The method we
+        present here does not make assumptions about the gravitational
+        potential, nor do we enforce physical assumptions about the dynamics of
+        each stream.
+
+        This work represents one machine learning-based approach for stream
+        characterization. Another method is presented in \citet{Shih+2022}, VIA
+        MACHINAE, which uses conditional density estimation and a linear feature
+        detector to discover streams and identify probable members. While the
+        method is promising for stream discovery, its intended use is not for
+        detailed characterization (as stated in \citealt{Shih+2022}). Our work
+        has the opposite approach: the method presented is not designed to
+        detect streams, rather, it is well-suited for characterizing streams
+        that fall within some predefined field. Thus, our method can be used for
+        characterizing the VIA MACHINAE candidates, and obtaining more robust
+        membership probabilities.
+
+        In \citet{Patrick+2022} the stellar density of 13 tidal streams is
+        modeled in on-sky positions and color-magnitude coordinates. The
+        morphology of each stream is characterized by a series of splines, which
+        are themselves a function of $\phi_1$. This method was originally
+        developed in \citet{Erkal+2017}.  Importantly, \citet{Patrick+2022}
+        performs a fit in $\phi_1-\phi_2$ and photometry, similar to our work.
+        The photometric approach in \citet{Patrick+2022} relies on generating
+        mock stellar populations in the CMD, selecting probable stream stars,
+        modeling the $\phi_1-\phi_2$ distribution for those stars, and then
+        refining the CMD fit based on the $\phi_1-\phi_2$ fit. This approach
+        therefore represents a more principled way of carrying out a matched
+        filter analysis. The model does not currently incorporate kinematic
+        information, though the work could be extended. The improvement of our
+        work is that we do not require an iterative fit to the CMD and
+        astrometry: we handle both spaces through a joint likelihood without
+        simulating mock-observations. Additionally, we can easily incorporate
+        kinematic information and data with missing phase-space dimensions.
+
+        Finally, our method relies on neural networks to describe the stream
+        track rather than splines, and a combination of normalizing flows and
+        analytic densities to characterize the distribution of background stars
+        in photometry and astrometry. While splines are attractive in their
+        simplicity and flexibility, the expressiveness of a spline is largely
+        determined by (a) the number of spline ``knots", and (b) the location of
+        each knot. This is not entirely dissimilar from a neural network, which
+        is subject to some choice of hyper-parameters. However, neural networks
+        are universal function approximators and are therefore readily equipped
+        to describe non-trivial density distributions without imposing priors on
+        the ``reach" of a model. However, when priors are needed, we have shown
+        that they can be added as control points in the loss function, guiding
+        our fits to prefer extended filamentary structures on the sky.
+        Therefore, our neural network based approach enjoys many of the same
+        benfits as splines, with the benefit of being more agnostic to choices
+        like the number and location of knots, and the order of the spline
+        (i.e., cubic, quartic, etc.).
+
+        We also highlight upcoming work from Tavangar et al. 2023 (in prep.),
+        which provides a spline-based characterization of streams implemented in
+        the \package{Jax} library \citep{jax2018github}. The \package{Jax}
+        backend ensures that fitting the model to a stream is very fast (on the
+        order of minutes rather than hours), and also has the capability of
+        incorporating kinematic data with missing phase-space dimensions. The
+        method does not currently model the color-magnitude distribution of a
+        stream, but relies on a loose photometric selection. The photometric
+        model in this work could be extended to the method in Tavangar et al.
+        2023 (In prep.) in a straightforward matter.
+
+        In total, having multiple methods to characterize streams and their
+        membership probabilities is advantageous. As the volume of tidal
+        features continues to grow, it will become important to fit different
+        models to the same stream, in order to evaluate whether certain features
+        or density variations are real versus spurious artifacts from the
+        adopted method. Considering the information encoded about perturbations
+        in the small-scale density fluctuations along a given stream, a
+        posterior distribution over models will help capture systematic errors
+        in our description of streams and the field of perturbations that give
+        rise to their density.
+
+\section{Summary and Conclusion} \label{sec:conclusions}
+
+    We have constructed and demonstrated a new method for characterizing stellar
+    streams, given all of the astrometric and photometric data available. We
+    model a stream in astrometric coordinates using mixture density networks,
+    allowing for a flexible representation of diverse stream morphologies under
+    a single modeling framework. Additionally, our astrometric fit does not rely
+    on assumptions about the gravitational potential. Our simultaneous
+    photometric model treats each stream as a single-stellar population,
+    generated from a theoretical isochrone. The distance modulus along the
+    stream is itself a function of $\phi_1$, allowing us to tie photometric
+    information to parallax measurements along the stream. This tie enables a
+    reconstruction of stellar stream distance tracks that are compatible with
+    photometry and astrometry by construction. A joint model in astrometric and
+    photometric coordinates also naturally allows for more spatially diffuse
+    regions of a stream to be detected. Additionally, our background model
+    relies on a combination of analytic densities and normalizing flows, each of
+    which are modular in our code-base and readily adaptable to a given field.
+
+    The combination of a flexible stream and background model allows us to
+    obtain robust stream-membership probabilities for each star in a given
+    field. This enables the generation of statistical samples for stream stars,
+    informed by astrometry and photometry. We apply the method to the stream
+    \stream{GD-1} and the tidal tails of \stream{Palomar 5}, generating
+    membership catalogs for both streams that are publicly available
+    \JN{reference link or footnote}. Our characterization of \stream{GD-1}
+    reveals a significant detection of the stream's main component as well as
+    the ``spur" component, which represents a bifurcation from the main stream.
+    We also recover density variations and gaps along the stream that have been
+    previously observed. Our fit to \stream{Pal\,5} demonstrates the performance
+    of our model on a more diffuse stream with low signal-to-noise measurements.
+    The inclusion of deeper photometric data for \stream{Pal\,5} will enable a
+    more extended view of the stream.
+
+    Our method represents a new avenue to characterize the growing census of
+    stellar streams discovered in the Milky Way. While most streams have been
+    roughly characterized with matched filter algorithms, a statistical and
+    homogeneous determination of stream-membership probabilities for each star
+    has not been performed or made publicly available. A homogeneous catalog of
+    stellar streams and stellar membership probabilities will therefore
+    represent a substantial step forward for galactic dynamics, since both the
+    global track of a stream and its small-scale density distribution are
+    sensitive to the Milky Way's gravitational potential.
+
+    Especially when considering the small-scale perturbation history of a stream
+    predicted by $\Lambda\rm{CDM}$, the inclusion or exclusion of stream stars
+    can make a substantial difference in our inference of the perturbers.
+    Constructing catalogs with membership probabilities as we do in this work
+    provides a crucial step forward to making our inference of, e.g., dark
+    matter subhalos in the Galaxy more robust. Equipped with membership
+    probabilities, one is finally able to propagate the uncertainty in our
+    determination of the ``on-stream data" through to the posterior distribution
+    of model parameters (e.g., those characterizing the subhalo mass function).
+    Thus, our works provides a new technique to generate samples of stream stars
+    using all of the existing kinematic and photometric data, from which models
+    for the Milky Way and its potential can be constrained in a statistically
+    sound manner.
 
@@
     NSERC (funding reference number RGPIN-2020-04712) and from an Ontario Early
-    Researcher Award (ER16-12-061; PI Bovy). NS would also like thank Prof. Webb
-    for providing computational resources and travel funding.
-
-    \JN{TODO}
+    Researcher Award (ER16-12-061; PI Bovy).
+
+    JN is supported by a National Science Foundation Graduate Research
+    Fellowship, Grant No. \JN{fill in}.
+
+    Both NS and JN would like to thank the
+    \href{https://stellarstreams.org/streams22/}{Community Atlas of Tidal
+    Streams 2022} conference for starting the discussions that led to this work.
+
+    This work has made use of data from the European Space Agency (ESA) mission
+    \Gaia{} (\url{https://www.cosmos.esa.int/gaia}), processed by the \Gaia{}
+    Data Processing and Analysis Consortium (DPAC,
+    \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the
+    DPAC has been provided by national institutions, in particular the
+    institutions participating in the \Gaia{} Multilateral Agreement.
 
@@
     repository associated with this study is publicly available at
-    $\GitHubURL{}$.
+    \package{\url{https://github.com/nstarman/stellar_stream_density_ml_paper}}.
 
@@
 \appendix
-
-\section{Notation} \label{app:notation}
-
-    In this work we use multiple data sets and a variety of mathematical tools
-    to analyze the data, including machine learning algorithms and statistical
-    models.  For clarity and to connect related components of the models used in
-    this work, a consistent mathematical notation is crucial. Here we establish
-    the notation and symbols used throughout this work.
-    \autoref{table:symbol_table} enumerates the symbols used for the statistical
-    models and the different datasets, e.g. distinguishing astrometric from
-    photometric data.
-
-    \TODO{position the table here}
-
-    \begin{table}
-    \centering
-    \caption{Symbol Table}
-    \label{table:symbol_table}
-    \begin{tabular}{p{0.35\linewidth} p{0.6\linewidth}}
-    Symbol                         & Explanation \\
-    \toprule
-    % -----------------------------------------------------------------------------
-    \\
-    \multicolumn{2}{l}{\textbf{Datasets}:} \\
-    \midrule
-    % -------------------------------------------------
-    \multicolumn{2}{l}{\textbf{Full Data}:}  \vspace{5pt} \\
-    $\mbf{X} \in \mbb{R}^{(N, F+1)}$ & The full dataset, including all measurements (rows) and features (columns).  \\
-    $\mbs{\delta}\mbf{X} \in \mbb{R}^{(N, F+1)}$ & The full set of uncertainties in $\mbf{X}$, e.g. Gaussian $\sigma_{n,f}$ and correlation terms $\sigma_{n,(f_i, f_j)}$.\\
-    $N$ & The number of independent measurements (aka stars) in the dataset.  \\
-    $F$ & The number of measured features, e.g.
-$(\alpha, \delta, \parallax, \mu_{\alpha^*}, \mu_\delta, v_r, g, r)$,  not including the the `independent' feature over which the others are conditioned.
-\\
-    $\mrm{n} \in \mbs{I_N} \equiv \{1, ..., N\} \in \mbb{Z^+}$ & Index into the set of measurements $\mbf{X}$ (and $\mbs{\delta}\mbf{X}$), i.e. the $n$-th star. \\
-    $\mrm{f} \in \mbs{I_F}  \equiv \{1, ..., F\} \in \mbb{Z^+}$ & Index into the set of features of $\mbf{X}$  (and $\mbs{\delta}\mbf{X}$). $ f=0$ is the `independent' feature.\\
-    $(\delta)x_{\mrm{n,f}}$ & $n$-th star with $f$-th feature in $(\mbs{\delta})\mbf{X}$. \\
-    $(\mbs{\delta})\nth{\mbs{x}}$ & $n$-th star as a row vector of all features of $(\mbs{\delta})\mbf{X}$. \\
-
-    % -------------------------------------------------
-    \\
-    \multicolumn{2}{l}{\textbf{Astrometric Data}:}  \vspace{5pt} \\
-    $\mbf{W} \in \mathbb{R}^{(N, F_w + 1)}$ & Full astrometric dataset. \\
-    $\mrm{f_w} \in \mbs{I_{F_w}} \equiv \{1, ..., F_w\} \in \mathbb{Z^+}$ & Index into the set of astrometric features. $f_w = f = 0$ is the `independent' feature.\\
-    $w_{\mrm{n,f_w}}$ & $f_w$-th astrometric feature of the $n$-th star in $\mbf{W}.$\\
-    $\nth{\mbs{w}}$ & $n$-th star as a row-vector of all astrometric features. \\
-    $\phi_1 \equiv w_{\cdot,0}$ & The `independent' (index 0) feature column on which the models are conditioned.
-For convenience $\phi_1$ is used instead of $\nth{\phi_1}$ (or $w_{n,0}$) except where the $n$ subscript cannot be inferred from context.\\
-    % -------------------------------------------------
-    \\
-    \multicolumn{2}{l}{\textbf{Photometric Data}:}  \vspace{5pt} \\
-    $\mbf{M} \in \mathbb{R}^{(N, F_m)}$ & Full photometric dataset. \\
-    $\mrm{f_m} \in \mbs{I_{F_m}} \equiv \{1, ..., F_m\} \in \mathbb{Z^+}$ & Index into the set of photometric features. \\
-    $m_{\mrm{n,f_m}}$ & $n$-th measurement of the $f_m$-th feature of $\mbf{M}$. \\
-    $\nth{\mbs{m}}$ & $n$-th row-vector of all features. \\
-    % -----------------------------------------------------------------------------
-    \\
-    \multicolumn{2}{l}{\textbf{Statistics}:} \\
-    \midrule
-    $\pdf(...)$ & The PDF of the distribution. \\
-    $\cdf(...)$ & The CDF corresponding to $\pdf(...)$. \\
-    $\mbs{\theta} = \{\theta_f\}_f$ & The vector of a distribution's parameters. \\
-    $\mcal{L}(\nth{\mbf{x}}, \mbs{\theta}(\phi_1))$ & The likelihood of the data given the parameters. \\
-    $Q$ & The number of models in a mixture model. \\
-    $\mrm{q} \in \mbs{I_Q} \equiv \{1, ..., Q \} \in \mbb{Z^+}$ & Index into the set of $Q$ models. \\
-    $\mrm{b} \in \mbs{I_Q}$ & The index of the background model in the set of $Q$ models.
-    % -------------------------------------------------
-    \\
-    \end{tabular}
-    \end{table}
-
-    We use $\tilde{F}$ to indicate that there a missing features, e.g. radial
-    velocities.  The index set $\mbs{I}_F \mapsto \mbs{I}_{\tilde{F}} = \{1,
-    ..., k-1, k+1, ... \}$ where $k$ is the index of the missing feature.
-
-% section notation (end)
-
-% \section{Theory of Mixture Density Networks (MDNs)}
-% \label{app:theory_of_mixture_density_networks}
-
-%     Mixture models (MMs) are a statistical method to represent a population as
-%     a set of a sub-populations specified by probability distributions. These
-%     distributions are characterized by their parameters and mixture by a
-%     corresponding set of mixture weights. Mixture Density Networks (MDNs) are
-%     a machine learning method to combine a MM with neural networks, increasing
-%     the flexibility of the model. An MDN replaces the scalar distribution
-%     parameters of the MM with neural networks, allowing the distribution
-%     parameters and mixture weights to vary as smooth functions
-%     \citep{Bishop1994}. Functional parameters allows the model to capture
-%     variation over those parameters that is not possible with scalar-valued
-%     models. Moreover, by using neural networks the inferred functional forms
-%     are ``model-free" and driven entirely by the data.
-
-%     % Quote from https://mikedusenberry.com/mixture-density-networks % A
-%     mixture density network (MDN) is an interesting model formalism built
-%     within the general framework of neural networks and probability theory for
-%     working on supervised learning problems in which the target variable
-%     cannot be easily approximated by a single standard probability
-%     distribution. Essentially an MDN allows one to model a conditional
-%     probability distribution as a mixture of distributions, in which the
-%     individual distributions and the corresponding mixture coefficients are
-%     parameterized by functions of the inputs
-
-%     For the MDN we take $x_{\cdot, 0} \equiv x_{\cdot}$ (indexed from 0),
-%     which is the first feature column of $\mbf{X}$, as the `independent'
-%     coordinate over which the MDN parameters are conditioned. In the context
-%     of streams $x_{\cdot, 0} \equiv \phi_1$ is the longitude coordinate in a
-%     reference frame rotated such that the stream is aligned along $\phi_1$.
-
-%     The PDF of the MDN is
-
-%     \begin{equation} \label{eq:general_mixture_network} \pdf(\nth{\mbs{x}} |
-%         \mbs{\theta}(\phi_1)) = \sum_{\mrm{q} \in \mbs{I_Q}} \ \qth{f}(\phi_1)
-%         \qth{P}(\nth{x}|\qth{\mbs{\theta}}(\phi_1),q\!=\!\mrm{q})
-%         \end{equation} The mixture coefficients $\qth{f}$ are normalized s.t.
-%         \begin{equation} \sum_{\mrm{q}} \qth{f}(\phi_1) = 1 \qquad \forall
-%         \phi_1 \end{equation} In practice this is enforced by defining
-%         \begin{equation} f_{b}(\phi_1) = 1 - \sum_{\rm{q}\in
-%         \mbs{I_Q}\backslash b} \qth{f}(\phi_1) \end{equation} for some
-%         ``background" index $b \in \mbs{I_Q}$.
-
-%     Assuming the measurement of each datum is independent, the likelihood is a
-%     sum over all data: \begin{equation} \mcal{L}\left(\mbf{x}_n |
-%     \mbs{\theta}(\phi_1)\right) = \sum_{q\in\mbs{I_Q}}
-%     \qth{P}\left(\nth{\mbs{x}} | \qth{\mbs{\theta}}(\phi_1)\right).
-%     \end{equation}
-
-%     The full posterior distribution includes the priors.
-
-%     \begin{equation} \ln\posterior\left(\mbf{X} | \mbs{\theta}(\mbs{x})\right)
-%         = \ln\mcal{L}\left(\mbf{X} | \mbs{\theta}(\mbs{x})\right) +  \sum_{n
-%         \in \mbs{I_N}} \ln \left[ \sum_{q\in\mbs{I_Q}}
-%         \qth{\prior}\left(\qth{\mbs{\theta}}(\mbf{x}_n)\right) \right].
-%         \end{equation}
 
@@
         distribution.  For a domain $x \in [a, b]$ the PDF is given by
-        \begin{equation}\label{eq:pdf_flat_univariate}
+        \begin{equation} \label{eq:pdf_flat_univariate}
             P_{\mcal{U}}(x|a,b) = \begin{cases}
@@
 
-        \begin{equation}
+        \begin{equation} \label{eq:flat_distribution}
             \pdf_{(\mcal{U}*\mcal{N})}(x; \alpha, \beta, \sigobs) = \begin{cases}
@@
 
-    \vspace{10pt}
-    \subsection{Skew-Normal Distribution} \label{sub:skewnormal_distribution}
-
-        The PDF of the skew-normal distribution is given by
-
-        \begin{equation}
-            \pdf_{SN}(x;\mu,\sigma,\alpha) = 2\pdf_{\mcal{N}}(x;\mu,\sigma)\cdf_{\mcal{N}}(\alpha x;\mu,\sigma).
-        \end{equation}
-
-        Despite the popularity of this distribution we are not aware of any work
-        showing the convolution of the skew-normal distribution with a centered
-        Gaussian. Moreover, our Mathematica (v13.2) does not successfully
-        perform this convolution. Consequently we present a step-by-step
-        derivation of $P_{X\cdot\mcal{N}}$.
-
-        \autoref{eq:general_convolution} establishes that convolutions of PDFs
-        are an integral operation. Integrals are often intractable, but the
-        problem is solvable if recast in different terms. Rather that working
-        with PDFs of distributions we can instead consider the moment-generating
-        function (MGF) corresponding to the PDF's distribution. Like the PDF,
-        the MGF uniquely determines a distribution, so a MFG uniquely maps to a
-        PDF. For the MGF of two distributions the convolutions is a
-        multiplication, not an integral.  Therefore, for the convolution of two
-        PDFs their MGFs are multiplied and if the product is the MGF of a known
-        distribution, the corresponding PDF is the convolution of the two
-        original PDFs.
-
-        The MGF of the Normal distribution is
-
-        \begin{equation} \label{eq:mgf_normal}
-            M_{\mcal{N}}(t) = \Exp{\frac{\sigma_*^2 t^2}{2}}
-        \end{equation}
-
-        And the MGF of the skew-normal is
-
-        \begin{equation} \label{eq:mgf_skewnormal}
-            M_{S\mcal{N}}(t) = 2 * \Exp{\mu t + \frac{\sigma^2 t^2}{2}} \cdf(\sigma \delta t), \quad \delta = \frac{\alpha}{\sqrt{1 + \alpha^2}}.
-        \end{equation}
-
-        The product of the two MGF is
-
-        \begin{equation}
-            M_{S\mcal{N}*\mcal{N}}(t) = M_{S\mcal{N}}(t) * M_{\mcal{N}}(t) = 2 * \Exp{\mu t + \frac{(\sigma^2 + \sigma_*^2) t^2}{2}} \cdf(\sigma \delta t).
-        \end{equation}
-        We rewrite $\tilde\sigma^2 = \sigma^2 + \sigma_*^2$, and $\tilde{\sigma}
-        \tilde{\delta} = \sigma \delta$.
-
-        \begin{equation}
-            M_{S\mcal{N}*\mcal{N}}(t) = 2 * \Exp{\mu t + \frac{\tilde{\sigma}^2 t^2}{2}} \cdf_{\mcal{N}}(\tilde{\sigma} \tilde{\delta} t)
-        \end{equation}
-        This has the same form as the skew-normal, only with $\sigma \rightarrow
-        \tilde\sigma$ and $\delta \rightarrow \tilde\delta$.
-
-        Therefore the PDF of the convolved distribution is
-
-        \begin{equation}
-            \pdf_{S\mcal{N}\cdot\mcal{N}}(x;\mu,\sigma,\alpha) = 2\pdf_{\mcal{N}}(x;\mu,\tilde{\sigma})\cdf_{\mcal{N}}(\tilde{\alpha} x;\mu,\tilde{\sigma})
-        \end{equation}
-        where $\tilde\sigma^2 = \sigma^2 + \sigma_*^2$ and $\tilde{\alpha} =
-        \frac{\tilde{\delta}}{\sqrt{1-\tilde{\delta}^2}}$, $\tilde{\delta} =
-        \frac{\sigma}{\tilde{\sigma}}\delta$.
-
-        The truncation of this distribution to the range $(a, b]$ is
-
-       \begin{equation}
-            \pdf_{S\mcal{N}_T}(x; \mu, \sigma, \alpha, a, b)
-                = \begin{cases}
-                    \frac{\pdf_{S\mcal{N}}(x; \mu, \tilde\sigma, \tilde\alpha)}{\cdf_{S\mcal{N}}(b; \mu, \tilde\sigma, \tilde\alpha) - \cdf_{S\mcal{N}}(a; \mu, \tilde\sigma, \tilde\alpha)} & a < x \leq b \\
-                    0 & \text{else}
-                \end{cases}
-        \end{equation}
-        where
-        \begin{equation}
-            \cdf_{S\mcal{N}}(x; \mu, \sigma) = \frac{1}{2} \text{erfc}\left(\frac{\mu -x}{\sqrt{2} \sigma }\right)-2 T\left(\frac{x-\mu }{\sigma },\alpha \right)
-        \end{equation}
-        where $T$ is Owen's T distribution \citep{Owen1956}.
-
 \end{document}

### 2024-04-21 src/tex/ms.tex
v2 - cleanup
Signed-off-by: nstarman <nstarman@users.noreply.github.com>

@@
 
-\documentclass[twocolumn]{aastex631}
+\documentclass[twocolumn, linenumbers]{aastex631}
 \usepackage{showyourwork}
@@
 \usepackage{transparent}
-\usepackage{todonotes}
 \usepackage{array}
@@
 
-\newcommand{\galaxy}[1]{
-    \ifthenelse{\equal{#1}{}}{
-        \includegraphics[width=9pt]{static/galaxy.png}
-    }{
-        \includegraphics[width={#1}pt]{static/galaxy.png}
-    }%
-}
-
 \defcitealias{Ibata+2021}{I21}
-
-\newcommand{\TODO}[1]{{\textcolor{red}{#1}}}
-\newcommand{\JN}[1]{\TODO{#1}}
 
@@
 % Title
-\title{Does this Star Belong? Data-Driven Characterization of Stellar Streams \\ with Mixture Density Networks}
+\title{Stream Members Only:\\ Data-Driven Characterization of Stellar Streams with Mixture Density Networks}
 
@@
 \author[0000-0003-3954-3291]{Nathaniel Starkman}
-\affiliation{David A Dunlap Department of Astronomy and Astrophysics, University of Toronto}
+\altaffiliation{Co-first author.}
+\affiliation{David A Dunlap Department of Astronomy and Astrophysics, University of Toronto, 50 St. George St, Toronto ON M5S 3H4, Canada}
 
@@
 \altaffiliation{Co-first author.}
-\affiliation{Department of Astrophysical Sciences, Princeton University}
+\affiliation{Department of Astrophysical Sciences, Princeton University, 4 Ivy Ln, Princeton, NJ 08544, USA}
 
 \author[0000-0001-6855-442X]{Jo Bovy}
-\affiliation{David A Dunlap Department of Astronomy and Astrophysics, University of Toronto}
+\affiliation{David A Dunlap Department of Astronomy and Astrophysics, University of Toronto, 50 St. George St, Toronto ON M5S 3H4, Canada}
 
 \author[0000-0003-3613-0854]{Jeremy J. Webb}
-\affiliation{Division of Natural Science, Department of Science, Technology and Society, York University}
-
-% \author[0000-0002-7846-9787]{Ana Bonaca}
-% \affiliation{Carnegie Observatories: Pasadena, California, US}
+\affiliation{Department of Science, Technology and Society, York University, 4700 Keele St, Toronto ON M3J 1P3, Canada}
+
+\author[0000-0001-6584-6144]{Kiyan Tavangar}
+\affiliation{Department of Astronomy, Columbia University, 538 West 120th Street, New York, NY 10027, USA}
+
+\author[0000-0003-0872-7098]{Adrian Price-Whelan}
+\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA}
+
+\author[0000-0002-7846-9787]{Ana Bonaca}
+\affiliation{The Observatories of the Carnegie Institution for Science, 813 Santa Barbara Street, Pasadena, CA 91101, USA}
 
@@
 
-% Abstract with filler text
 \begin{abstract}
+
     Stellar streams are sensitive probes of the Milky Way's gravitational
     potential. The mean track of a stream constrains global properties of the
-    potential, while its fine-grained surface density contains information about
-    galactic substructure.
-A precise characterization of streams from potentially noisy data marks a crucial step in constraining galactic structure across orders of magnitude in mass scales.
-Here we present a new method for constructing a smooth probability
-    density model of stellar streams using all of the available astrometric and
-    photometric data. To characterize the stream's morphology and kinematics, we
-    utilize mixture density networks to construct a flexible representation of
-    the stream and its on-sky track, width, stellar number density, and
-    kinematic distribution. In photometric coordinates we model each stream as a
-    single-stellar population, with a distance track that is simultaneously
+    potential, while its fine-grained surface density constrains galactic
+    substructure. A precise characterization of streams from potentially noisy
+    data marks a crucial step in inferring galactic structure, including the
+    dark matter, across orders of magnitude in mass scales. Here we present a
+    new method for constructing a smooth probability density model of stellar
+    streams using all of the available astrometric and photometric data. To
+    characterize a stream's morphology and kinematics, we utilize mixture
+    density networks to represent its on-sky track, width, stellar number
+    density, and kinematic distribution. We model the photometry for each stream
+    as a single-stellar population, with a distance track that is simultaneously
     estimated from the stream's inferred distance modulus (using photometry) and
-    parallax distribution (using astrometry). Normalizing flows are used to characterize the distribution of background stars. We apply the method to the stream
-    \stream{GD-1}, and the tidal tails of \stream{Palomar 5}. For both streams we obtain a catalog
-    of stellar membership probabilities that are made publicly available.
-    Importantly, our model is capable of handling data with incomplete
-    phase-space observations, making our method applicable to the growing census
-    of Milky Way stellar streams. When applied to a population of streams, the
-    resulting membership probabilities from our model form the required input to
-    infer the Milky Way's dark matter distribution from the scale of the stellar
-    halo down to subhalos. 
+    parallax distribution (using astrometry). We use normalizing flows to
+    characterize the distribution of background stars. We apply the method to
+    the stream \stream{GD-1}, and the tidal tails of \stream{Palomar 5}. For
+    both streams we obtain a catalog of stellar membership probabilities that
+    are made publicly available.  Importantly, our model is capable of handling
+    data with incomplete phase-space observations, making our method applicable
+    to the growing census of Milky Way stellar streams.
+
 \end{abstract}
@@
     brightness photometric surveys (e.g., \citealt{Ibata+1998,
-    GrillmairDionatos2006, Shipp+2018, Ibata+2021}).  The formation of streams
+    GrillmairDionatos2006, GrillmairCarlin2016, Shipp+2018, Ibata+2021}).  The formation of streams
     can be traced back to a progenitor (a globular cluster or satellite galaxy)
@@
 
-    The average properties of a stream (e.g., the mean position and velocity
+    The average properties of a stream along its track (e.g., the mean position and velocity
     track of the tidal tails) can be used to reconstruct the global dark matter
@@
     the stream track and surface density encode information about the stream's
-    encounters with baryonic structures such as the stellar bar (e.g.,
-    \citealt{Erkal+2017, Pearson+2017}), and non-luminous structures like dark
-    matter subhalos (e.g., \citealt{Ibata+2002, Johnston+2002,
-    Carlberg+2012-74820C, Bovy+2017, Bonaca+2019, Hermans+2021}).
+    progenitor \citep{Kupper+2012, Sanders+2013, Price-Whelan+2014}, encounters
+    with baryonic structures such as the stellar bar (e.g., \citealt{Erkal+2017,
+    Pearson+2017}), and non-luminous structures like dark matter subhalos (e.g.,
+    \citealt{Ibata+2002, Johnston+2002, Carlberg+2012-74820C, Bovy+2017,
+    Bonaca+2019, Hermans+2021}).
 
@@
     function of global halo characteristics (e.g., the mass distribution,
-    flattening; \citealt{Johnston+1999,2008MNRAS.386L..47B,Koposov+2010,2013MNRAS.433.1826S,Bovy2014,Nibauer+2022}) and local substructures (e.g., the bar's pattern
-    speed and the mass of subhalo perturbers; \citealt{2014A&A...563A..60A,Pearson+2017,2016MNRAS.460..497H,Bovy+2017,Bonaca+2019}), these methods often
-    rely on the existence of a homogenized stream-tracer population that
-    characterizes a given stream across each of the observable phase-space
-    dimensions. Additionally, because even the fine-grained properties of
-    streams are influenced by the detailed mass distribution of its host galaxy,
-    it is important to propagate errors both in measurement uncertainty and
-    membership uncertainty (i.e., which stars belong to the stream versus the
-    background) when attempting to model a stream. Otherwise, a poorly
-    characterized stream could bias constraints on, e.g., the total mass of the
-    galaxy, the dark matter halo shape, and the mass of subhalo perturbers. In
-    order to generate more precise constraints on the structure of the galaxy,
-    it is therefore imperative that a statistically sound and homogenized
-    catalog of stellar streams is produced.
+    flattening; \citealt{Johnston+1999, Binney2008, Koposov+2010,
+    SandersBinney2013, Bovy2014, Nibauer+2022}) and local substructures (e.g.,
+    the bar's pattern speed and the mass of subhalo perturbers;
+    \citealt{Antoja+2014, Hattori+2016, Price-Whelan+2016, Bovy+2017,
+    Pearson+2017, Bonaca+2019, Malhan+2021}), these methods often rely on the existence of a
+    homogenized stream-tracer population that characterizes a given stream
+    across each of the observable phase-space dimensions.  Additionally, because
+    even the fine-grained properties of streams are influenced by the detailed
+    mass distribution of its host galaxy, it is important to propagate errors
+    both in measurement uncertainty and membership uncertainty (i.e., which
+    stars belong to the stream versus the background) when attempting to model a
+    stream. Otherwise, a poorly characterized stream could bias constraints on,
+    e.g., the total mass of the galaxy, the dark matter halo shape, and the mass
+    of subhalo perturbers.  In order to generate more precise constraints on the
+    structure of the galaxy, it is therefore imperative that a statistically
+    sound and homogenized catalog of stellar streams is produced.
 
@@
     enables a simultaneous fit to both the stream and background density,
-    allowing for better separation of the stream from the background
-    distribution. However, the track of the stream in on-sky coordinates is not
-    fit. The method identified 27 RR Lyrae stars consistent with being members
-    of the stream. While useful for determining the average properties of a
-    stream (e.g., its mean distance track), a limited population of RR Lyrae
-    stars are not sufficient to capture the small-scale properties of streams
-    expected to inform constraints on, e.g., a population of perturbers in the
-    galaxy.
+    allowing for a cleaner selection of stream stars. However, the track of the
+    stream in on-sky coordinates is not fit. The method identified 27 RR Lyrae
+    stars consistent with being members of the stream. While useful for
+    determining the average properties of a stream (e.g., its mean distance
+    track), a limited population of RR Lyrae stars are not sufficient to capture
+    the small-scale properties of streams expected to inform constraints on,
+    e.g., a population of perturbers in the galaxy.
 
@@
         our method for characterizing stream tracks and computing stellar
-        membership.  We discuss initial data processing in
+        membership probabilities.  We discuss initial data processing in
         \autoref{sub:method:framing_the_data} and build a probabilistic
@@
         stellar streams \stream{GD-1} (\autoref{sec:results_gd1}) and
-        \stream{Pal\,5} (\autoref{sec:results_pal5}).  We compare our approach
-        to characterizing stellar streams to other methods in
-        \autoref{sec:discussion}.  We conclude in \autoref{sec:conclusions},
-        discussing the results of this work and future directions.
+        \stream{Pal\,5} (\autoref{sec:results_pal5}).  We compare our model to
+        other methods in \autoref{sec:discussion}.  We conclude in
+        \autoref{sec:conclusions}, discussing the results of this work and
+        future directions.
 
@@
 
+\newpage
 \section{Method} \label{sec:method}
 
-    To characterize stellar stream tracks and for computing membership
-    probabilities from kinematic and photometric measurements of stars, we
-    develop a flexible Bayesian modeling framework that incorporates all of the
-    available kinematic information for a field of stars, including those with
-    only partial phase-space measurements. Below, we offer a concise overview of
-    our approach, followed by a more in-depth technical explanation in
-    subsequent sections.  We start, in \autoref{sub:method:framing_the_data}, by
-    transforming the astrometric data into a stream-oriented on-sky reference
-    frame ($\phi_1, \phi_2, \parallax, \mu_{\phi_1}^*, \mu_{\phi_2}, v_r)$, for
-    each stream. In this frame, the stream track lies along $\phi_1$, and the
-    stream density may be described by distributions in the other parameters as
-    injective functions of $\phi_1$.  Likewise, the background of the Galactic
-    field may be described with $\phi_1$-conditioned distributions.  We will
-    also model the stream in photometric coordinates. Additional features, e.g.
-    metallicity, can also be modeled along the stream and background as
+    Below, we offer a concise overview of our approach, followed by a more
+    in-depth technical explanation in subsequent sections.  We start, in
+    \autoref{sub:method:framing_the_data}, by transforming the astrometric data
+    into a stream-oriented on-sky reference frame ($\phi_1, \phi_2, \parallax,
+    \mu_{\phi_1}^*, \mu_{\phi_2}, v_r)$, for each stream.  In this frame, the
+    stream track lies along $\phi_1$, and the stream density may be described by
+    distributions in the other parameters as injective functions of $\phi_1$
+    (called conditional distributions).  Likewise, the background of the
+    Galactic field may be described with $\phi_1$-conditioned distributions.  We
+    will also model the stream in photometric coordinates.  Additional features,
+    e.g.  metallicity, can also be modeled along the stream and background as
     functions of $\phi_1$, though we leave this to a future work.
@@
     mixture model that describes the entire field.  We take the parameters of
-    the mixture model -- the mixture weights and component distribution
-    parameters -- to be general (continuous) functions of the conditioning
-    variable, $\phi_1$. This is done using a feed-forward neural network that
-    takes the conditioning variable as its input and outputs the parameter
-    value(s) that characterize the distribution of stars at a $\phi_1$ ``slice".
-    Mixture models of conditional probability distributions using neural
-    networks are called Mixture Density Networks (MDNs) \citep{Bishop+1994}.
-    Since the model coefficients may evolve with $\phi_1$, MNDs are well suited
-    to characterize streams (and the background) with all their variations in
-    position, width, and linear density.
-
-    % sub: framing_the_data (end)
+    the mixture model --- the mixture weights and component distribution
+    parameters --- to be general (continuous) functions of $\phi_1$, the
+    conditioning variable. This is done using a feed-forward neural network that
+    takes $\phi_1$, the conditioning variable, as its input and outputs the
+    parameter value(s) that characterize the distribution of stars at a $\phi_1$
+    ``slice".  Mixture models of conditional probability distributions using
+    neural networks are called Mixture Density Networks (MDNs)
+    \citep{Bishop+1994}.  Since the model coefficients may evolve with $\phi_1$,
+    MNDs are well suited to characterize streams (and the background) with all
+    their variations in position, width, and linear density.
 
@@
 
-        While it would be ideal to characterize streams in this Galactocentirc
+        While it would be ideal to characterize streams in this Galactocentric
         frame, transformation to the frame requires knowledge of the distance to
@@
         \stream{Jhelum}, etc. -- this holds true. However for some streams of
-        dwarf galaxies, like the Magellanic stream which wraps multiple times
-        around the Milky Way \citep{WannierWrixon1972}, no such transformation
-        is possible. More generally, a stream's ``sky"-projected path may be
-        kinked, e.g. by subhalo interactions, such that it is a many-to-one
-        function in $\phi_1$.
-
-        In this work we treat with the vast majority of streams, which have a
-        ``sky" transformation such that the stream is an injective function in
-        $\phi_2(\phi_1)$.  Since we are examining known streams this
-        transformation is known \textit{a priori}, or may be constructed during
-        pre-processing \citep[see][\S2.1]{Starkman+2023}.  We note that, with
-        sufficient prior knowledge, many-to-one functions may be broken into
-        injective segments and their connection constrained by a prior. Thus the
-        methods developed subsequently may be extended and applied even to
-        wrapped and kinked streams. However, we leave extending the model
-        framework to a future work.
+        dwarf galaxies, like the Magellanic and Sagittarius streams which each
+        wrap around the Milky Way \citep{Newberg+2002, Majewski+2003,
+        WannierWrixon1972}, no such transformation is possible. More generally,
+        a stream's ``sky"-projected path may be kinked, e.g. by subhalo
+        interactions, such that it is a many-to-one function in $\phi_1$.
+
+        In this work we consider the vast majority of streams that can be
+        described as an injective function, $\phi_2(\phi_1)$.  Since we are
+        examining known streams this transformation is known \textit{a priori},
+        or may be constructed during pre-processing
+        \citep[see][\S2.1]{Starkman+2023}.  We note that, with sufficient prior
+        knowledge, many-to-one functions may be broken into injective segments
+        and their connection constrained by a prior. Thus the methods developed
+        here may be extended and applied even to wrapped and kinked streams.
+        However, we leave extending the model framework to a future work.
+
+    % sub: framing_the_data (end)
 
@@
                 \textbf{Left}: A PGM of the stream model. The full dataset
-                $x_n^{obs}$ is made of the observed astrometry $w_n^{obs}$ and
-                photometry $m_n^{obs}$, along with the corresponding
-                observational errors. We model the data as a mixture of
-                Gaussians (in astrometry + distance modulus), with the Gaussians
-                indexed by $q$. The weight $\alpha$ determines the weighted
-                contribution of each Gaussian to each datum. All models are
-                conditioned on $\phi_1$.
-                %
-                \textbf{Right}: a PGM of the background model. The data is
+                $x_n^{obs}$ is the aggregation of the observed astrometry
+                $w_n^{obs}$ and photometry $m_n^{obs}$, along with the
+                corresponding observational errors. We model the data as a
+                mixture of Gaussians (in astrometry + distance modulus), with
+                the Gaussians indexed by $q$. The weight $\alpha$ determines the
+                weighted contribution of each Gaussian to each datum. All models
+                are conditioned on $\phi_1$.
+                %
+                \textbf{Right}: a PGM of the background model. The data are
                 identical to that of the stream, however the model is not a
@@
 
-        Mixture models (MMs) are a statistical method to represent a population
-        as a set of a sub-populations specified by probability distributions.
-        These distributions are characterized by their parameters and the
-        mixture by a corresponding set of mixture coefficients. Scalar mixture
-        models may be extended to model completely general conditional
-        distributions by making the distribution parameters and mixture
-        coefficients into functions of a conditional input
-        \citep{McLachlanBasford1989}.  Mixture Density Networks (MDNs) are a
-        machine learning method to implement these general MM, taking the
-        parameters and coefficients to be the outputs of feed-forward neural
-        networks and as such, general continuous functions \citep{Bishop1994}.
-        Functional parameters allow the model to capture variation over those
-        parameters that is not possible with scalar-valued models. Moreover, by
-        using neural networks the inferred functional forms are ``model-free"
-        and driven entirely by the data.
-
-        For the MDN we take $x_{\cdot, 0}$, which is the first feature column of
-        the data $\mbf{X}$, as the `independent' coordinate over which the MDN
+        Mixture models are a statistical method to represent a population as a
+        set of a sub-populations specified by probability distributions.  These
+        distributions are characterized by their parameters and the mixture by a
+        corresponding set of mixture coefficients. Scalar mixture models may be
+        extended to model completely general conditional distributions by making
+        the distribution parameters and mixture coefficients into functions of a
+        conditional input \citep{McLachlanBasford1989}.  Mixture Density
+        Networks (MDNs) are a machine learning method to implement these general
+        mixture models, taking the parameters and coefficients to be the outputs
+        of feed-forward neural networks and as such, general continuous
+        functions \citep{Bishop1994}.  Functional parameters allow the model to
+        capture variation over those parameters that is not possible with
+        scalar-valued models. Moreover, by using neural networks the inferred
+        functional forms are ``model-free" and driven entirely by the data.
+
+        For the MDN we take $x_{\cdot, 0}$, the first feature column of the data
+        $\{\mbf{x}\}$, as the `independent' coordinate over which the MDN
         parameters are conditioned. In the context of streams $x_{\cdot, 0}
@@
             \!\!\! \pdf(\nth{\mbs{x}} | \mbs{\theta}(\phi_1))
-            \!=\! \sum_{\mrm{q} \in \mbs{I_Q}} \! \qth{f}(\phi_1) \cmp{q}{\pdf}(\nth{\mbs{x}}|\qth{\mbs{\theta}}(\phi_1)),
-            % \prior(\nth{\mbs{x}}, \phi_1)
+            \!=\! \sum_{\mrm{q} \in \mbs{I_Q}} \! \qth{f}(\phi_1) \cmp{q}{\pdf}\left(\nth{\mbs{x}}|\qth{\mbs{\theta}}(\phi_1)\right),
         \end{equation}
@@
         feed-forward neural network, and $\nth{\mbs{x}}$ the data on the $n$-th
-        star in $\mbs{X}$, not including $\phi_1$. For convenience we drop the
-        implied subscript $n$ in $\phi_1$, the explicit notation of
+        star in $\{\mbs{x}\}$, not including $\phi_1$. For convenience we drop
+        the implied subscript $n$ in $\phi_1$, the explicit notation of
         $\mbs{\theta}$'s dependence on $\phi_1$, and the index set $\mbs{I}_X$
@@
         \mbs{I_Q}$.  In the context of Galactic streams the ``foreground" is the
-        stream itself, while the background is the Galaxy - bulge, bar, disc,
-        halo - and additional structures, like globular clusters and dwarf
+        stream itself, while the background is the Galaxy --- bulge, bar, disc,
+        halo --- and additional structures, like globular clusters and dwarf
         galaxies, that are not associated with the stream itself.  We discuss
@@
         In this work we consider primarily astrometric and photometric data,
-        (notated $\mbs{W}$ and $\mbs{M}$, respectively), but note that the MDN
-        framework may be extended to arbitrary feature dimensions. Assuming the
-        conditional independence of the astrometry and photometry\footnote{ For
-        \Gaia{} data this is true in practice but not in detail: there exist
-        small correlations between the astrometric and photometric data.}, we
-        split each model into linearly separable astrometric and photometric
-        models $\cmp{q}{\pdf} = \cmp{q,w}{\pdf} \cmp{q,m}{\pdf}$.
+        (notated $\{\mbs{w}\}$ and $\{\mbs{m}\}$, respectively), but note that
+        the MDN framework may be extended to arbitrary feature dimensions.
+        Assuming the conditional independence of the astrometry and
+        photometry\footnote{ For \Gaia{} data this is true in practice but not
+        in detail: there exist small correlations between the astrometric and
+        photometric data \citep[see e.g.
+the \href{https://www.cosmos.esa.int/web/gaia/science-performance\#astrometric\%20performance}{\Gaia{} website} or][]{GaiaDR2Astrometry2018}.}, we split each model into linearly separable
+        astrometric and photometric models $\cmp{q}{\pdf} = \cmp{q,w}{\pdf}
+        \cmp{q,m}{\pdf}$.
 
@@
 
-    %\newpage
     \subsection{Missing Phase-Space Observations}
@@
         \citep[e.g.,][]{Koposov+2019, Antoja+2020, Li+2022}, while most have
-        partial coverage, lacking some feature dimensions.  Most streams in
-        \Gaia \citep{Gaia2016, Gaia2023}, for instance, have proper motions but
-        not radial velocities nor high signal-to-noise parallax measurements.
-        Follow-up surveys, like \dataarchive{S5} \citep{Li+2019}, add many
-        feature dimensions, however only for a select set of streams. Given the
-        diversity of coverage it is important that the likelihood model --
-        \autoref{eq:membership_prob} -- account for missing data.
+        partial coverage, lacking some feature dimensions.  Most streams
+        detected by \Gaia{} \citep{Gaia2016, Gaia2023}, for instance, have proper
+        motions but not radial velocities nor high signal-to-noise parallax
+        measurements.  Follow-up surveys, like \dataarchive{S5} \citep{Li+2019},
+        add many feature dimensions, however only for a select set of streams.
+        Given the diversity of coverage it is important that the likelihood
+        model -- \autoref{eq:membership_prob} -- account for missing data.
 
@@
         likelihood model might use only the present features, ignoring those
-        missing. If however, features are missing for systematic reasons, then
-        this approach can introduce systematic bias. Consider a star too far
-        away to measure its parallax distance or radial velocity. This is a
-        systematic reason and this information should be incorporated into any
-        model as a prior. Not doing so, the data imputation approach might
-        predict too-close distances. Likewise, using only present features in
-        the likelihood model misses that the star is likely very distant.  The
-        effects of mask systematics are mitigated by not including such data,
-        moving the contribution of the systematics from a prior to the evidence.
-        Our models compute likelihoods under a specific dataset, and
-        \autoref{eq:membership_prob} is a ratio of the probabilities, so the
-        removed systematics are not expected to be impactful.
+        missing. If however, features are missing for systematic reasons, due to
+        a selection function, then this approach will introduce systematic bias.
+        The way to avoid bias where the data is incomplete due to the selection
+        function is to know that selection function. Otherwise the probabilities
+        will not be properly normalized.  Selection functions are often very
+        challenging to characterize, so it is routine and convenient to simply
+        cut the data where the effects of the selection function become
+        significant.  Not including such affected data moves the contribution of
+        the selection function from a prior to the evidence.  Our models compute
+        likelihoods under a specific dataset, and \autoref{eq:membership_prob}
+        is a ratio of the probabilities, so the removed selection functions are
+        not expected to be impactful.
 
@@
         and not systematic. We do not impute missing data, instead the per-star
-        likelihood is modelled with a distribution with the same dimensionality
+        likelihood is modeled with a distribution with the same dimensionality
         as the data vector.  For example, a star with a 6D astrometric
-        measurement will be modelled with a full 6D distribution, while a star
-        missing its radial velocity measurement will be modelled with a
+        measurement will be modeled with a full 6D distribution, while a star
+        missing its radial velocity measurement will be modeled with a
         dimensionally-reduced (5D) form of the 6D distribution. Using
@@
         In \autoref{sub:method:likelihood_setup} we set up the general
-        mathematical framework of MDNs then specified the models on two axes:
+        mathematical framework of MDNs, then specified the models on two axes:
         the component and the data type. Broadly, the components are stream
@@
         distribution \citep{EstebanVanden2010, Rippel2013, RezendeMohamed2015}.
-        The transformations are typically non-linear outputs of a neural neural
+        The transformations are typically non-linear outputs of a neural
         network, whose parameters are optimized until the target density
@@
         \begin{equation}\label{eq:fraction_param}
-            f_q\left(\phi_1\right) = \frac{N_q\left(\phi_1\right)}{N_{\rm tot}\left(\phi_1\right)},
+            f_q\left(\phi_1\right) = \frac{n_q\left(\phi_1\right)}{n_{\rm tot}\left(\phi_1\right)},
         \end{equation}
-        where $N_q\left(\phi_1\right)$ is the number of stars in component $q$
-        within an interval $[\phi_1, \phi_1 + \dif{\phi_1}]$, and $N_{\rm tot}$
-        is the total number of stars in the same band (including those in
-        component $q$). The linear  density for component $q$ is then entirely
-        specified by the function $N_q(\phi_1)$.
+        where $n_q\left(\phi_1\right)$ is the number density of stars in
+        component $q$ (i.e., the number of stars belonging to component $q$ per
+        $\phi_1$ interval), and $n_{\rm tot}$ is the total number density of
+        stars in the same interval (including those in component $q$). The
+        linear  density for component $q$ is then entirely specified by the
+        function $n_q(\phi_1)$.
 
@@
         the weight parameter $f_q$, and not the components of the ratio in
-        \autoref{eq:fraction_param}. However, the linear density $N_q(\phi_1)$
-        can be readily obtained from $f_q$, provided that $N_{\rm
+        \autoref{eq:fraction_param}. However, the linear density $n_q(\phi_1)$
+        can be readily obtained from $f_q$, provided that $n_{\rm
         tot}\left(\phi_1\right)$ can be calculated. Importantly, this function
         does not depend on the parameters of the on-stream or off-stream model.
-        Instead, $N_{\rm tot}(\phi_1)$ is simply the number of stars in a small
-        $\phi_1$ increment. We therefore model $N_{\rm tot}\left(\phi_1\right)$
-        as a post-processing step using a single normalizing flow in $\phi_1$.
+        Instead, $n_{\rm tot}(\phi_1)$ is simply proportional to the number of
+        stars in a small $\phi_1$ increment. We therefore model $n_{\rm
+        tot}\left(\phi_1\right)$ as a post-processing step using a single
+        normalizing flow in $\phi_1$.
 
@@
         is trained to this dataset, and will satisfy $\int d\phi_1
-        P_{\phi_f}(\phi_1) = 1$ by construction. In order to re-weight the
-        normalizing flow to obtain $N_{\rm tot}(\phi_1)$, we simply rescale
-        $P_{\phi}(\phi_1)$ by $N_{\rm tot,0}$, which is the total number of
-        stars in the field considered. We can then obtain the linear stream
-        density with
+        P_{\phi_f}(\phi_1) = 1$ by construction.  We can then obtain the linear
+        stream density with
         \begin{equation}
-            N_q\left(\phi_1\right) = [f_q N_{\rm tot}] \left(\phi_1\right)  = N_{\rm tot,0}[f_q P_{\phi_1}]\left(\phi_1\right) .
+            n_q\left(\phi_1\right) = f_q\!\left(\phi_1\right) \, n_{\rm tot}\!\left(\phi_1\right)  \equiv f_q\!\left(\phi_1\right) P_{\phi_1}\!\!\left(\phi_1\right) .
         \end{equation}
@@
             $\mbs{\delta}\mbf{W}$, the dataset of astrometric uncertainties.
-            % (see \autoref{app:notation}).
 
@@
 
-            In the presence of missing phase-space coordinate $f_k$ we reduce
+            If a particular observation has missing phase-space coordinate(s) $f_k$, we reduce
             the dimensionality of the Gaussian to that of the data-vector.
@@
                 \Spdf(\nth{\mbs{w}} & | \astroM{\mbs{\theta}}(\phi_1))
-                    \mapsto \Spdf(\nth{\tilde{\mbs{w}}} | \astroM{\tilde{\mbs{\theta}}} (\phi_1))\,. % = \mcal{N}_{\tilde{F}}.
+                    \mapsto \Spdf(\nth{\tilde{\mbs{w}}} | \astroM{\tilde{\mbs{\theta}}} (\phi_1))\,.
             \end{align}
@@
 
-        \subsubsection{Off-stream} \label{ssub:method:astrometric_model:off_stream}
-
-            We now outline the off-stream astrometric model. We take a similar
-            approach to the on-stream astrometric model discussed in
+        \subsubsection{Off-stream}
+
+            \label{ssub:method:astrometric_model:off_stream} We now outline the
+            off-stream astrometric model. We take a similar approach to the
+            on-stream astrometric model discussed in
             \autoref{ssub:method:astrometric_model:on_stream}, though we
@@
             distance gradient. We accomplish this by modeling the distance of
-            the isochrone as a neural network output, parametrized as a function
-            of $\phi_1$. The result is a distance track along the stream,
-            estimated from the variation in its isochrone with $\phi_1$.
+            the isochrone as a neural network output, parameterized as a
+            function of $\phi_1$. The result is a distance track along the
+            stream, estimated from the variation in its isochrone with $\phi_1$.
 
@@
             towards the red giant branch. We denote the isochrone as
-            $\mcal{I(\gamma)}$. The intrinsic dipsersion around the isochrone is
+            $\mcal{I(\gamma)}$, and \package{StreamMapper} permits any such
+            distribution. The intrinsic dispersion around the isochrone is
             $\Sigma_\mcal{I}(\gamma)$. Since the isochrone is in absolute
@@
                 \cmp{S,m}{\pdf}(\mbs{m_i}, \gamma | \mbs{\theta}(\phi_1)) 
-                \\ \sim \mcal{N}(\nth{\mbs{m}} | \{\mcal{I(\gamma)} + \mu(\phi_1), \mbs{\Sigma}_{\mcal{I}}^2(\gamma) + \mathds{1} \sigma_\mu^2(\phi_1) + {\cmp{m}{\nth{\mbs{\Sigma}}}}^2 \}) \\ \times \prior(\gamma, \nth{\mbs{m}}, \phi_1),
+                \\ = \mcal{N}(\nth{\mbs{m}} | \{\mcal{I(\gamma)} + \mu(\phi_1), \mbs{\Sigma}_{\mcal{I}}^2(\gamma) + \mathds{1} \sigma_\mu^2(\phi_1) + {\cmp{m}{\nth{\mbs{\Sigma}}}}^2 \}) \\ \times \prior(\gamma, \nth{\mbs{m}}, \phi_1),
             \end{multline}
@@
             track to the stream. An alternate approach is to use data-driven
-            isochrones instead of theoretic ones.  We defer this to a future
-            work.
+            isochrones instead of theoretic ones.   \package{StreamMapper}
+            allows any isochrone from any theoretic or data-driven library to be
+            used, so long as the isochrone may be described as a curve
+            $\mcal{I}(\gamma, \phi_1)$ with dispersion
+            $\Sigma_{\mcal{I}}(\gamma, \phi_1)$. In this work we use MIST
+            \citep{Dotter2016, Choi+2016} isochrones for their convenience, but
+            recognize their limitations as compared to data-driven isochrones.
+            We defer using data-driven isochrones and constraining ages and
+            metallicities to a future work.
 
@@
             encodes the photometric distribution -- the ``track" -- of the
-            isochrone model at each point along the track, as well as the
-            relative probability of points along the track. This is the term
-            $\prior(\gamma, \nth{\mbs{m}} | \phi_1)$, which describes all priors
-            on both the isochrone as well as survey constraints and selection
-            effects. We assume that the properties of the isochrone are
-            conditionally independent from observational constraints; namely
+            isochrone model, as well as the relative probability of points along
+            the track. The latter is the term $\prior(\gamma, \nth{\mbs{m}} |
+            \phi_1)$, which describes all priors on both the isochrone as well
+            as survey constraints and selection effects. We assume that the
+            properties of the isochrone are conditionally independent from
+            observational constraints; namely
             \begin{equation} \label{eq:isochrone_prior_components}
@@
 
-            In the \href{https://github.com/GalOrrery/stream_ml-pytorch}{code}
+            In the
+            \href{https://github.com/GalOrrery/stream_mapper-pytorch}{\package{StreamMapper}}
             we offer a few ansatz for the PDMF, though any user-defined function
@@
             distribution, for example time-evolving an IMF, either analytically
-            or by simulation, to the age of the stream's stellar population. %As
-            %discussed previously, globular clusters are known to be poorly fit
-            %by theoretical isochrones with realistic inputs (e.g. age, $Z$).
-            %Thus fitting an isochrone's track to the data means its age,
-            %metallicity and therefore PDMF are %not well fit \TODO{[cite]}.
-            However, for many streams, e.g. those lacking known progenitors,
-            the PDMF is observationally poorly constrained.  In short, using any
+            or by simulation, to the age of the stream's stellar population.
+            However, for many streams, e.g. those lacking known progenitors, the
+            PDMF is observationally poorly constrained.  In short, using any
             fixed distribution is simple in implementation, however the choice
@@
 
-            % TODO: rephrase
             By modeling jointly the astrometrics and photometrics we may tie
@@
             model are both measures of the distance track of the stream. We
-            introduce a prior to connect these components of the model:
+            model in the same coordinates as the data, and thus prefer parallax
+            and distance modulus over the distance for each model type.  We
+            introduce a prior to connect these components of the models:
             \begin{align}
@@
             magnitude (i.e., $g$) is a complicated function of location in the
-            galaxy. Even within a field centered on the
-            stream of interest, the color-magnitude diagram (CMD) is a
-            combination of stellar populations distributed over a range in
-            distances. Because of this, we do not find an analytic density that
-            describes the data and use instead a normalizing flow, discussed in
+            galaxy. Even within a field centered on the stream of interest, the
+            color-magnitude diagram (CMD) is a combination of stellar
+            populations distributed over a range in distances. Because of this,
+            we do not find an analytic density that describes the data and use
+            instead a normalizing flow, discussed in
             \autoref{sub:method:pre-training_distributions}.  Because the
@@
 
-    %\newpage
     \subsection{Priors} \label{sub:methods:priors}
@@
         constraints. In this section we introduce and develop more priors that
-        are important for training our Bayesian Mixture Density Network's
-        parameters' neural network(s).
+        are important for training our Bayesian Mixture Density Network.
 
@@
             it is a categorical, more informative priors like the Dirichlet
-            distribution \citep{Christopher2016} may be used.  Our code permits
-            any user-defined prior, and we include $\mcal{U}(a, b)$.  The
-            default choice of prior and bounds $\mcal{U}$ set to the limits of
-            the dataset in each feature dimension.
-
-            The choice of prior is important, not only for the information it
-            adds to the model, but also for how optimizers explore the parameter
-            space. Simple optimizers, like MCMC, propose a parameter vector then
-            compute its likelihood given the data
-            \citep{HoggForeman-Mackey2018}. Priors with compact support  $\theta
-            \sim \mcal{D}((a, b])$, e.g.  $\mcal{U}(a, b)$, may be very
-            dangerous as the optimizer can be initialized in a region with zero
-            probability and has no means but blind luck to find the region of
-            support -- the region with non-zero likelihood. More sophisticated
-            optimizers, like gradient-based descent \citep{cauchy_2009}, are
-            susceptible to a similar initialization problem, allowing
-            zero-probability regions, but requiring at least a non-zero gradient
-            to make informed updates to the optimizers state.  Outside the
-            support the gradient can be zero.  With MDNs, model parameters are
-            neural network outputs. Unlike for conventional models where an
-            informed initial parameter state may be chosen by hand, it is
-            impractical and undesirable to initialize by hand a neural network's
-            output by setting all its internal weights. One might imagine
-            accomplishing a desired initial output by pre-training the network
-            with a toy model that forces convergence on a set output vector.
-            However, neural networks are highly non-linear in their response to
-            internal state changes (a desirable property). It is quite possible
-            that when switching from the toy to real model's loss function the
-            pre-trained network is in a local probability island from which the
-            global optimum is unreachable.  
-            Therefore, with the MDN neural networks, initialization is mostly
-            for checking the dependence of the results on the initial state --
-            though even this dependence may instead be done using parameter
-            dropout. Rather than focusing on initializing to a particular
-            parameter vector, for neural networks it is instead important that
-            the initial state, whatever it is, has non-zero probability (or
-            non-zero gradient, depending on the optimizer).  Neural networks
-            have some intrinsic phase-space range that depends on the
-            architecture of the network. Therefore the network architecture must
-            be chosen such that the outputs match well with the priors. For
-            example, with a uniform prior $\theta \sim \mcal{U}(a,b)$, the
-            network should be restricted such that $\theta \in (a, b]$, e.g. by
-            ending the network's $\theta$ channel with a scaled logistic
-            function.
+            distribution \citep{Christopher2016} may be used. Our code,
+            \package{StreamMapper}, permits any user-defined prior, and we
+            include $\mcal{U}(a, b)$.  The default choice of prior and bounds
+            $\mcal{U}$ set to the limits of the dataset in each feature
+            dimension.
+
+            We implement a hard-coded uniform prior on a neural network output
+            by applying a scaled logistic function of the form
             \begin{equation}\label{eq:scaled_logistic}
@@
             Therefore, we pair every parameter bound with a matching bound in
-            the network architecture.
+            the network architecture. Further details of this practice are
+            explained \autoref{app:nns_and_priors}.
 
@@
 
-        \subsubsection{Guides Prior} \label{sub:methods:priors:track_region_prior}
-
-            In \autoref{ssub:method:astrometric_model:on_stream} the stream
-            model's parameters were unconstrained. Bounds on the parameters and
-            the neural network architecture were introduced in
-            \autoref{ssub:methods:priors:parameter_bounds} to ensure the initial
-            state of the model and network were compatible with the optimizer.
-            Now we provide known information about physical systems,
-            particularly the track of the stream.  Our density modeling is aimed
-            at characterization of \textit{known} streams, not stream discovery.
+        \subsubsection{Priors on the Stream Track} \label{sub:methods:priors:track_region_prior}
+
+            We now discuss how our model incorporates known information about
+            the track of the stream.  Our density modeling is aimed at
+            characterization of \textit{known} streams, not stream discovery.
             From previous studies, the broad track of a stream is known for
@@
             to the model. Care must be taken that this prior information does
-            not dominate the model.  We introduce a region prior to encourage
+            not dominate the model.  We introduce a ``guide'' prior to encourage
             the stream model to pass through a user-defined guide region, while
-            also remaining compatible with the data.  We refer to the prior as a
-            ``split"-Normal prior: a Gaussian split and separated at the peak
-            and pieced back together with a flat region connecting the halves.
-            The un-normalized PDF is given by:
+            also remaining compatible with the data.  We use a ``split''-Normal
+            prior: a Gaussian split and separated at the peak and pieced back
+            together with a flat region connecting the halves.  The
+            un-normalized PDF is given by:
             \begin{equation}
-                \pdf(\theta,\mu,\sigma,w) \propto \begin{cases} 
+                \pdf(x,\mu,\sigma,w) \propto \begin{cases} 
                    \Exp{-\frac{1}{2}\left(\frac{x-(\mu-w)}{\sigma}\right)^2} & \phantom{\mu - w <}\ x < \mu - w \\
@@
             \end{equation}
-            The piecewise PDF is smooth up to the first derivative and can be
-            used with gradient-based optimizers.
+            Since the derivative at the peak of a Gaussian is $0$, the piecewise
+            PDF is smooth up to the first derivative and can be used with
+            gradient-based optimizers.
 
             The Gaussian portions of the prior encourage the network towards the
-            central region $\mu - w < x < \mu + w$. Since the prior is
-            equi-probable in the guide, the stream may lie anywhere as preferred
-            by the data and the stream model.  It is convenient to
-            reparametrize, with $\tau = \frac{1}{\sigma}$. Namely,
-            % \begin{small}
+            central region $\mu - w < x < \mu + w$. Because the prior is
+            equi-probable in the guided region, the stream may lie anywhere as
+            preferred by the data and the stream model.  It is convenient to
+            parameterize, with $\tau = \frac{1}{\sigma}$. Namely,
+            \begin{small}
             \begin{equation}
-                \ln \pdf(\theta,\mu,w) \propto \tau
+                \ln \pdf(x,\mu, \tau, w) \propto \tau
                 \begin{cases} 
@@
             \end{equation}
-            % \end{small}
+            \end{small}
             where the additive normalization is
@@
             large enough that we may be confident the prior is not driving the
-            final result on small scales. As an added measure, it is often
-            useful to turn off this prior after the stream lies within the
-            desired guides and the learning rate of the optimizer is low enough
-            that the model does not wander out.
+            final result on small scales. As an added measure, it may useful to
+            turn off this prior after the stream lies within the desired guides
+            and the learning rate of the optimizer is low enough that the model
+            does not escape the solution minima.
 
@@
 
-    \vspace{5pt}
-    \subsection{Model Implementation, aka the code} \label{sub:methods:model_implementation}
-
-        In prior sections we discussed the mathematical implementation of each
-        component of the Mixture Density Network. Here we make brief remarks on
-        the code implementation and architecture of the neural networks.
-
-        The neural networks are built with the \package{PyTorch} stack
-        \citep{Pytorch2019}. We wrap the network \texttt{pytorch.Module} in a
-        custom framework, allowing the Bayesian likelihood, prior, evidence,
-        etc. to be bundled with the network's forward step. This framework
-        allows for a high degree of modularity. Component models, e.g. the
-        stream model, of the mixture are easily added to (and moved from) as
-        items in the larger mixture model. Probability methods understand how to
-        traverse the mixture model, calling and combining the appropriate
-        methods of the constituent models, so it unnecessary to write custom
-        loss functions.  Another benefit of the modular framework is the ease of
-        building and experimenting with different mixture models. Furthermore,
-        each model component may be saved and serialized separately from the
-        other components, allowing for portability of the components between
-        models.  For example, if a stream has a prominent extra-tidal feature,
-        e.g. the spur of \stream{GD-1}, a fiducial model of just the thin stream
-        may be trained, then the stream (and background) model components may be
-        saved and used as the initialization to the stream (and background) of a
-        more complete model that includes the spur. This modularity also has a
-        cost: by allowing each model component (including the categorical
-        mixture model itself) to contain its own network we decrease the
-        cross-talk between nodes in separated networks. The networks communicate
-        only through the backwards propagation of the loss function, increasing
-        the required training time of the models. We note that the code
-        framework, being built on \package{PyTorch}, easily permits a single
-        model with single network. Having found a good model by experimenting
-        with the modular layout, the model may be reproduced and re-trained as a
-        single network. Alternatively, though we leave this to a future version
-        of the code, it is possible to ``fuse" the mixture, providing one
-        network whose outputs are apportioned appropriately to each constituent
-        model.
+    \subsection{Model Implementation} \label{sub:methods:model_implementation}
+
+        In previous sections we discussed the mathematical implementation of
+        each component of the Mixture Density Network. Here we make brief
+        remarks on the code implementation in \package{StreamMapper} and the
+        architecture of the neural networks.
+
+        The neural networks are all multi-layer perceptrons (MLP; built with the
+        \package{PyTorch} stack \citep{Pytorch2019}. We wrap the network
+        \texttt{pytorch.Module} in a custom framework, allowing the Bayesian
+        likelihood, prior, evidence, etc. to be bundled with the network's
+        forward step. This framework allows for a high degree of modularity.
+        Component models, e.g. the stream model, of the mixture are easily added
+        to (and moved from) as items in the larger mixture model. Probability
+        methods understand how to traverse the mixture model, calling and
+        combining the appropriate methods of the constituent models, so it
+        unnecessary to write custom loss functions.  Another benefit of the
+        modular framework is the ease of building and experimenting with
+        different mixture models. Furthermore, each model component may be saved
+        and serialized separately from the other components, allowing for
+        portability of the components between models.  For example, if a stream
+        has a prominent extra-tidal feature, e.g. the spur of \stream{GD-1}
+        \citep{Bonaca+2019}, a fiducial model of just the main stream may be
+        trained, then the stream (and background) model components may be saved
+        and used as the initialization to the stream (and background) of a more
+        complete model that includes the spur.  By using a modular framework,
+        the architecture of each neural network may be chosen to best-suit its
+        modeling needs: e.g. thin networks for simply varying components.  On
+        the other hand, large networks can have useful emergent phenomenon, e.g.
+        understanding covariate structures, that cannot be (or are unknown how
+        to be) replicated with multiple smaller networks. We choose to use the
+        smaller and more tailored models, finding their balance of performance
+        and reduced training time well-suited for this work.
 
@@
 
-        The custom model framework combines for each model a neural network with
-        Bayesian probability functions. The latter are set by the model type,
-        e.g. the Gaussian model has a Gaussian likelihood function, but the
-        former, the neural network, is set and determined by the user. So long
-        as the network has the correct number of inputs (e.g. one for $\phi_1$)
-        and outputs (one per parameter), any feed-forward network may be used.
-        Our default choice, and for which we provide a helper function, is an
-        MLP with a sequence of \texttt{Linear} \!\!\textrightarrow \texttt{Tanh}
-        \!\!\textrightarrow \texttt{Dropout} (hereafter \texttt{LTD}) blocks.
-        Dropout layers are used to prevent network co-adaptation and
-        over-fitting. Dropout works by randomly zeroing out nodes in the
-        network, decreasing the importance of any single node, encouraging
-        instead emergent patterns across the network \citep{GalGhahramani2015}.
-        One model for which the \texttt{LTD} network cannot be used is the
-        normalizing flow used in the photometric background model
-        (\autoref{sub:method:photometric_model:off_stream}). Here we use the
-        \package{zuko} package, with a conditional diagonal normal base
-        distribution and composite transform network of a reverse permutation
-        and masked affine auto-regressive transform layers. As noted in our data
-        availability statement, all the codes used in this paper are bundled by
+        The specific architecture of the neural network(s) is set and determined
+        by the user. So long as the network has the correct number of inputs
+        (e.g. one for $\phi_1$) and outputs (one per parameter), any
+        feed-forward network may be used.  Our default choice, and for which we
+        provide a helper function, is an MLP with a sequence of \texttt{Linear}
+        \!\!\textrightarrow \texttt{Tanh} \!\!\textrightarrow \texttt{Dropout}
+        (hereafter \texttt{LTD}) blocks.  Dropout layers are used to prevent
+        network co-adaptation and over-fitting. Dropout works by randomly
+        zeroing out nodes in the network, decreasing the importance of any
+        single node, encouraging instead emergent patterns across the network
+        \citep{GalGhahramani2015}.  One model for which the \texttt{LTD} network
+        cannot be used is the normalizing flow used in the photometric
+        background model (\autoref{sub:method:photometric_model:off_stream}).
+        Here we use the \package{zuko} package for normalizing flows, with a
+        conditional diagonal normal base distribution and composite transform
+        network of a reverse permutation and masked affine auto-regressive
+        transform layers. As noted in our data availability statement, all the
+        codes used in this paper are bundled by
         \href{https://github.com/showyourwork/showyourwork}{\package{showyourwork}}
-        in a public repository. We will describe for each stream model specifics
-        relevant to that stream but refer readers to the publicly-available code
-        itself for code implementation details.
+        \citep{Luger+2021} in a public repository. We will describe for each
+        stream model specifics relevant to that stream but refer readers to the
+        publicly-available code itself for more implementation details.
 
@@
 
-    In this section we present an application of our model to a synthetic stream
+    In this section we present an application of our model to a synthetic stream and background
     with known ground truths, and demonstrate the model's ability to
@@
     unsupervised manner.
+    In \autoref{app:tailored_mock} we apply the method to a more tailored data set, demonstrating that we can obtain near-perfect reconstruction of the stream -- the stream width in each components, and the presence of gaps -- and separation between stream and background stars.
+    Here, the mock synthetic data emulates real observations, with complex background distributions and observational uncertainties.
+As will be shown, even in these more adverse conditions our model maps the stream in great detail.
 
@@
 
-        We generate a simple and illustrative synthetic stream observations by
-        sampling from simple algebraic forms.  In $\phi_1$ we sample from a
-        uniform distribution. Non-Poissonian density variations, like gaps, are
-        introduced by adding to the uniform distribution two Gaussian
-        distributions centered at different values of $\phi_1$ with negative
-        amplitudes and random widths. Stream stars are then sampled from this
-        uniform-plus-gaps mixture distribution.  In $\phi_2$ we sample from a
-        quadratic in $\phi_1$ with normally-distributed $0.15^{\degree}$
-        scatter.  The distances are uniformly sampled from $7$ to $15$ kpc in a
-        linear function in $\phi_1$ with normally-distributed $0.25 \ \rm{kpc}$
-        scatter, then transformed to the parallax $\parallax$. Even though the
-        stream width is constant in the distance the width in parallax is not,
-        which will be used to demonstrate that we can recover $\phi_1$ dependent
-        distributions.  The number of stream stars is
-        $\variable{output/mock/nstream_variable.txt}$.
-        $\variable{output/mock/nbackground_variable.txt}$ background astrometric
-        points are generated by sampling from uniform distributions in each
-        coordinate.
-
-        The synthetic stream's photometry is also simulated using a
+        We generate realistic mock stream observations by sampling from a synthetic \Gaia{} catalog with an injected particle-spray mock stream.
+Realistic observational errors are applied to both the background and stream.
+
+        The background is based on the \Gaia{} mission's \href{https://gea.esac.esa.int/archive/documentation/GEDR3/Gaia_archive/chap_datamodel/sec_dm_simulation_tables/ssec_dm_gaia_source_simulation.html}{Main database Combined Data \texttt{gaia\_source\_simulation}}, which is a realization of the Gaia Object Generator (GOG; \citealt{2014EAS....67..355A}) simulation.
+The GOG is based on the Gaia Universe Model \citep{2012A&A...543A.100R}, which is in turn based on an updated Besan{\c c}on Galactic model \citep{2003A&A...409..523R}.
+The GOG Galactic catalogue simulates, among other observables, astrometric and photometric measurements for stars in a full 3D distribution about the Milky Way.
+While the model does well for large structure, e.g.
+the Disk and Halo, it does not contain substructure like stellar streams.
+One will be injected later.
+        We query the GOG catalogue around the region $(\alpha, 
+        \delta) = (148, 37)$ in a $40\times 10$ degree box, 
+        with the distance restricted to 5-15 kpc.
+        This is a data cube centered on the location of \stream{GD-1}. Given that the model will be applied to the \stream{GD-1} stream in \autoref{sec:results_gd1}, this is a good test case.
+        Rather than using the data cube directly, it is convenient to emulate the data and draw a new synthetic catalogue.
+We do this for two reasons.
+First, we want to control the stream-to-background count, which is $\variable{output/mock2/nstream_variable.txt} / \variable{output/mock2/nbackground_variable.txt} \, \sim 1\%$.
+        Second, the GOG has known issues with outliers (see \href{https://gea.esac.esa.int/archive/documentation/GEDR3/Data_processing/chap_simulated/ssec_cu2knowniss/}{GEDR3 known issues}) that can be avoided through emulation.
+We train two normalizing flows, one on the astrometry and the other on the photometry in the data cube.
+Two additional normalizing flows are trained on the error distributions of the real \Gaia{} data in the specified region.
+Using the real \Gaia{} data has the dual advantage of realism and mitigating issues in the GOG, including that the errors are too covariate.
+From the emulator we draw $\variable{output/mock2/nbackground_variable.txt}$ background stars.
+Their distribution may be seen in \autoref{fig:mock_data_photometric_background_selection} and \autoref{fig:mock_data_result}, particularly the histogram plots of the latter, discussed later.
+
+        Into the observed background distribution we inject a mock stellar stream.
+The stream is a particle-spray model, following \cite{2015MNRAS.452..301F}, integrated in a Milky Way-like potential.
+We give the stream $10^4 \ \rm{M}_\odot$ progenitor a phase-space position similar to \stream{GD-1}, but with modified proper motions so as to nicely spread along the observational field.
+We refer the reader to the code, bundled with this paper for details.
+In the field the stream comprises $\variable{output/mock2/nstream_variable.txt}$ stars.
+Astrometric uncertainties are drawn from the astrometric error emulator, convolved with the stream, and used in the later model.
+
+        The synthetic stream's photometry is simulated using a
         \variable{output/mock/isochrone_age_variable.txt}\unskip, [Fe/H] =
         \variable{output/mock/isochrone_feh_variable.txt} MIST isochrone
-        \citep{Dotter2016, Choi+2016,brutus}. The isochrone is truncated just
-        short of the giant branch, and is sampled from assuming a stream mass
-        function similar to \stream{Pal\,5} \citep{GrillmairSmith2001} as well
-        as with an intrinsic uniform 0.2~dex scatter orthogonal to the isochrone
-        track.
-
+        \citep[using][]{brutus}.
+This isochrone is empirically similar to \stream{GD-1} -- all that is required for this model which does not constrain the metallicity.
+To test the stream mass function priors -- \autoref{eq:isochrone_prior_components} -- and make the stream recovery more challenging by removing the main sequence turn-off, the isochrone is truncated just short of the
+        giant branch. The truncated isochrone is sampled from assuming a stream mass function
+        similar to \stream{Pal\,5} \citep{GrillmairSmith2001}, which is reasonable for many streams. Observational errors
+        are added according to the photometry error emulator.
         The isochrone is shifted by the stream's distance modulus, which is
-        derived from the astrometric distance track.  The background photometric
-        coordinates are generated as a 2-dimensional Gaussian with non-zero
-        covariance.  Thus, the synthetic data scenario described here, and
+        derived from the astrometric distance track.
+        Thus, the synthetic data scenario described here, and
         presented in \autoref{fig:mock_data_photometric_background_selection},
-        generates a mock stream in astrometric coordinates and photometric
-        coordinates, with density variations, a distance gradient which is
-        consistent in parallax and distance modulus (i.e., magnitudes), all
-        superimposed over a noisy field of background points in each astrometric
-        and photometric dimension.
+        generates a realistic mock stream in astrometric coordinates and photometric
+        coordinates, all superimposed over a $\sim 100$ times larger noisy field of background points in each astrometric and photometric dimension.
+
+    % sub: data_simulation (end)
 
@@
         \begin{figure}
-            \script{mock/plot/photometric_background_selection.py}
+            \script{mock2/plot/photometric_background_selection.py}
             \centering
-            \includegraphics[width=1\linewidth]{figures/mock/photometric_background_selection.pdf}
+            \includegraphics[width=1\linewidth]{figures/mock2/photometric_background_selection.pdf}
             \caption{
@@
                 %
-                \textbf{Bottom panel:} Photometric coordinates ($g-r$, $g$) for
-                the mock data set.  Black points are in the ``off"-stream region
-                from the region defined in the astrometric coordinates.  Light
-                blue points are the stream and background from the on-stream
-                region. The stream's isochrone is apparent as an overdensity
-                around (g-r, g)$\ \approx (0, 20)$.
+                \textbf{Bottom panel:} Photometric coordinates for the mock data
+                set.  Black points are in the ``off"-stream region from the
+                region defined in the astrometric coordinates.  Light blue
+                points are the stream and background from the on-stream region.
+                The stream's isochrone is apparent as an overdensity around
+                (g-r, g)$\ \approx (0, 20)$.  The background is an arbitrary
+                Gaussian distribution from which the stream must be separated.
                 %
@@
 
-        \begin{figure*}[!h]
-            \script{mock/plot/results.py}
+        \begin{figure*}[!ht]
+            \script{mock2/plot/results.py}
             \centering
-            \includegraphics[width=0.9\linewidth]{figures/mock/results.pdf}
-            \caption{
-                %
-                \textbf{Top panel: }%
-                    The stream mixture coefficient $f(\phi_1)$ (black dotted
-                    line) predicted by the model, overplotted on the true stream
-                    fraction (black-outlined histogram), calculated as the ratio
-                    of stream stars to total stars in 55 bins over the $\phi_1$
-                    range of the isochrone.
-                %
-                \textbf{Middle panel: }
-                    $\phi_2(\phi_1)$ over the full range of $\phi_1$. The data
-                    color and transparency is set by the model's MLE stream
-                    probability (with dropout turned off). Plotted behind the
-                    data are the true labels for the stream stars (large black
-                    circles).  The true labels exactly match the
-                    model-identified stream stars.  The MLE stream track (black
-                    dashed line) is over-plotted on the probability-colored
-                    data.
-                %
-                \textbf{Lower panel 3: }%
-                    $\parallax(\phi_1)$ over the full range of $\phi_1$. Like for
-                    $\phi_2$, the data color and transparency is set by the MLE
-                    probability, with the true labels (large black circles)
-                    under-plotted and MLE track (black dashed line)
-                    over-plotted.
-                %
-                \textbf{Upper Histograms: }%
-                    $\phi_2$ histograms for each model component (blue
-                    background, red stream), in 4 $\phi_1$ ranges across the
-                    data set.  The height of each bin is the
-                    probability-weighted density.  The background is a uniform
-                    distribution, while the stream is a Gaussian. In projection
-                    across the $\phi_1$ range it can appear multi-modal (panel
-                    2) if there are large gaps or `smeared' out (panel 3) if the
-                    Gaussian's mean changes significantly over the range.
-                %
-                \textbf{Upper Middle Histograms: }%
-                    Parallax $\parallax$ histograms for each model component (blue
-                    background, red stream), in 4 $\phi_1$ ranges across the
-                    data set.  The height of each bin is the
-                    probability-weighted density.
-                %
-                \textbf{Lower Middle and Lower Histograms:}%
-                    Photometric coordinate $(g, r)$ plots for each model
-                    component in 4 $\phi_1$ ranges across the data set. The top
-                    row plots the stream stars (red) over the background. The
-                    lower row plots the background stars (blue) over the stream
-                    stars to show  how the two distributions mix.
+            \includegraphics[width=0.89\linewidth]{figures/mock2/results.pdf}
+            \caption{%
+                Illustration of the model's performance in recovering a stream
+                from synthetic observations. The \textbf{top panel} shows the
+                stream mixture coefficient $f(\phi_1)$ (dashed red line)
+                predicted by the model, overplotted on the true stream fraction
+                (black-outlined histogram).
+                %
+                In the \textbf{middle three rows} we also show the $\phi_2$, $\parallax$, and $\mu_{\phi_1}^*$, tracks as a function of $\phi_1$ and
+                their associated widths (labeled as $\sigma_{\phi_2}$,
+                $\sigma_{\parallax}$, $\sigma_{\mu_{\phi_1}^*}$, respectively). The true values for these
+                quantities are shown in black, while our model prediction and
+                uncertainty is show by the red curve and band, and by
+                the color of the data points. The model does an excellent job at identifying the
+                ground truth stream stars.
+                %
+                In the \textbf{bottom four rows} we demonstrate our ability to
+                separate the stream from the background both astrometrically and
+                photometrically. Histograms are shown for each model component
+                (black for the ground truth, blue for the background, red for
+                the stream), in 4 $\phi_1$ ranges across the data set.  The
+                height of the histogram is the probability-weighted density for
+                the collection of stars in each bin. There is nearly perfect
+                agreement for the number of stars belonging to each model
+                component as a function of $\phi_1$. In the bottom row we show
+                photometric plots for each model component in the same 4
+                $\phi_1$ ranges across the data set. Points are color-coded by
+                stream membership probability. 
                 %
@@
 
-        We select on-stream and off-stream regions using the known $\phi_1,
+        We now specify the details of the background and on-stream model utilized for recovering the injected stream.
+
+        We first discuss our density model for the background distribution in photometry. We select on-stream and off-stream regions using the known $\phi_1,
         \phi_2$ range of the mock stream.  The upper panel of
@@
         selections in blue and black, respectively.  The lower panel shows the
-        on and off-stream selections in photometric coordinates.  In this space
-        it is apparent that the on-stream region has two populations, drawn from
+        on and off-stream selections in photometric coordinates. Given the low density of the stream, it is not apparent that the on-stream region has two populations, drawn from
         the isochrone and from background points included in the simple $\phi_1,
-        \phi_2$ box.  In contrast, the off-stream region has only the the
-        background population.  We use the off-stream population to train a
+        \phi_2$ box. We use the off-stream population to train a
         conditional normalizing flow (see
@@
         non-parametric distribution characterizing the photometric background,
-        including its variation over $\phi_1$.  For this mock stream the
-        flexibility of the normalizing flow greatly exceeds necessity: the
-        background is drawn from a $\phi_1$-invariant multivariate normal,
-        essentially the base distribution of the normalizing flow.  It is
-        therefore no surprise that the trained normalizing flow provides an
-        excellent characterization of the background.  We will later see that
-        the flow performs similarly well on complex distributions.  Having
-        trained the background photometric model we proceed to build and train
-        the full model.
-
-        Per \autoref{eq:stream_and_bkg_prob} the stream is an independent
+        including any variation over $\phi_1$. Importantly, we pre-train the photometric model described above and keep its parameters fixed in our mixture model.
+
+        Next, we discuss our astrometric model for the distribution of background stars.
+Unlike the photometric background model, we allow for the astrometric background model to adapt as we fit the stream.
+The astrometric background model is split into three components: the first is a uniform
+        distribution in $\phi_2$, the second is an exponential distribution
+        for $\parallax$, and the third is a Gaussian distribution for $\mu_{\phi_1}^*$.  The uniform distribution does not have any parameters,
+        and thus no associated neural network.  The exponential distribution has only the
+        slope parameter and we use a 3-layer \texttt{LTD} with shape (1, 32, 1)
+        and 15\% dropout. The Gaussian distribution has two parameters and is a 4-layer \texttt{LTD} with shape (1, 64, 1)
+        and 15\% dropout. The input for each of these neural networks is the stream's length coordinate, $\phi_1$. We therefore allow for the background density to change with angle along the stream.
+
+        Finally, we specify our model for the on-stream density. Per \autoref{eq:stream_and_bkg_prob} the stream is an independent
         addition of both astrometric and photometric models.  In astrometrics
-        the stream is a Gaussian track in $\phi_2$ and parallax $\parallax$,
+        the stream is a Gaussian track in $\phi_2$, parallax $\parallax$, and $\phi_1$ proper motion $\mu_{\phi_1}^*$
         using the model defined in
-        \autoref{ssub:method:astrometric_model:on_stream}.  We use a 4-layer
-        \texttt{LTD} with overall shape ($\phi_1$ input, 4 outputs), where the 4
+        \autoref{ssub:method:astrometric_model:on_stream}.  We use a 5-layer
+        \texttt{LTD} with overall shape ($\phi_1$ input, 6 outputs), where the 4
         outputs are $[\mu_{\phi_2}, \sigma_{\phi_2}, \mu_{\parallax},
-        \sigma_{\parallax}](\phi_1)$.  The network is small, but sufficiently
+        \sigma_{\parallax}, \mu_{\mu_{\phi_1}^*},
+        \sigma_{\mu_{\phi_1}^*}](\phi_1)$.  The network is small, but sufficiently
         large to permit 15\% dropout and retain robust predictions.  The
@@
         use the same isochrone parameters as were used to simulate the stream,
-        including the \citep{GrillmairSmith2001} mass function.  For this mock
+        including the \citet{GrillmairSmith2001} mass function.  For this mock
         stream, we demonstrate simultaneous astrometric and photometric
         modeling, linking the distance modulus and parallax track, as explained
-        in \autoref{ssub:method:linking_to_astrometrics}. Thus the photometric
-        model does not have its own network, using instead the outputs
-        $[\mu_{\parallax}, \sigma_{\parallax}](\phi_1)$.
-
-        The total background model has two pieces, an astrometric and a
-        photometric model.  As a pre-training phase the photometric normalizing
-        flow model was fitted to an off-stream selection and is now held fixed.
-        The astrometric model is split in two components, the first is a uniform
-        distribution in $\phi_2$, and the second is an exponential distribution
-        for $\parallax$.  The uniform distribution does not have any parameters,
-        and thus no neural network.  The exponential distribution has only the
-        slope parameter and we use a 3-layer \texttt{LTD} with shape (1, 32, 1)
-        and 15\% dropout. Background and stream are combined in a mixture model
-        whose mixture parameters are a 4-layer (1, 64, 1) \texttt{LTD} network.
+        in \autoref{ssub:method:linking_to_astrometrics}.
+
+        With the various pieces of the model identified, the background and stream densities are combined through a two-component mixture model
+        whose mixture parameters are a 4-layer (1, 64, 1) \texttt{LTD} network (input is $\phi_1$ and output is the mixture weight).
         We train the mixture model with an \texttt{AdamW} optimizer with
-        learning rate of $5\times10^{-3}$ and a scheduler to periodically and
-        temporarily increase the learning rate, encouraging the optimizer
-        towards better minima.
+        learning rate of $3\times10^{-3}$ and a scheduler to periodically decrease the learning rate, allowing for characterization of smaller-scale features.
 
     \subsection{Trained Density Model} \label{sub:results_mock:results}
+
+        The result of applying our density model to the synthetic data is
+        illustrated in \autoref{fig:mock_data_result}. The top panel shows the
+        weight parameter that controls membership probability as a function of
+        $\phi_1$. The dashed curve represents the output of our data-driven
+        model, while the histogram is the ground truth. The second panel shows
+        the stream and background in the $(\phi_1,\phi_2)$ plane, and the third
+        panel shows the stream and background in the $(\phi_1,\parallax)$ plane.
+        Points are color-coded according to their membership probability
+        \autoref{eq:membership_prob}. The weight parameter clearly shows that
+        the model has captured the overall density variations along the
+        stream.
+
+        We find that the stream is successfully recovered in both astrometric
+        and photometric coordinates, with
+        $\variable{output/mock2/ncorrect_variable.txt}\%$ 
+        of stream stars being recovered with membership probability greater than
+        $75\%$.
+Impressively, the model does a good job of recovering from the error convolved distribution (gray) the true distribution (black) of the stream, as can be seen in the $\sigma$ plots.
+In the lower rows of \autoref{fig:mock_data_result} we
+        illustrate the synthetic data color-coded by stream membership
+        probability (top) and background membership probability (background) for
+        different $\phi_1$ slices. Importantly, the photometric portion of the
+        mixture model successfully identifies the stream in magnitude space,
+        showing a high stream membership probability where the stream is
+        present, and a low probability ($\sim 0$) where the stream is absent.
+        The false positive rate (i.e., stars misidentified as stream members)
+        for this test is found to be $\variable{output/mock2/falseident_variable.txt}\%$ (6 stars) when cutting on the 75\%
+        membership probability threshold.
+
+% sec: results  (end)
+
+\section{Results: GD-1} \label{sec:results_gd1}
 
@@
             %
-            \textbf{Row 1 Panels:}
-            Proper motion and photometric selections.  \stream{GD-1} is apparent
-            in the proper motions as a small overdensity. The photometric
+            \textbf{Row 1:}
+            Proper motion and photometric selections.  
+            The proper motion selection is the $[\mu_{\phi_1},
+            \mu_{\phi_2}](\phi_1)$ curve from \citetalias{Ibata+2021} (dashed
+            black line) buffered by $6$ and $3$ mas/yr, respectively (blue
+            curves defining the bottom left and top-right of the shaded
+            rectangular region). Viewed without $\phi_1$ we see the
+            $\mu_{\phi_1}, \mu_{\phi_2}$ ``phase''-like diagram. The photometric
             selection is based on a 12 Gyr, [Fe/H] = -1.2 MIST isochrone,
-            buffered by 0.3 mag to select .
-            %
-            \textbf{Rows 2 \& 3 Panels:}
-            Applying the combination of astrometric and photometric selections,
+            buffered by 0.3 mag to select the stream. The data is cut at
+            $G\leq20$, before applying the isochrone selection.
+            Light green points are the stream and background from an ``on''-stream region defined in row 2, column 1. The stream's isochrone is apparent as an overdensity.
+            %
+            \textbf{Rows 2 \& 3:}
+            Applying the combination of astrometric and photometric selections (blue 2d bins),
             plotted for astrometric coordinates $\phi_2, \parallax,
@@
             the stream is identifiable in all phase-space coordinates except
-            $\parallax$ where the errors are significant.  }
+            $\parallax$ where the errors are significant.
+            % 
+            \textbf{Row 2, column 1:}
+            Light green points are the stream and background defining an ``on''-stream region. Blue points are in the off-stream
+            region used to train the background photometric model. Note the green points are generated from a reduced field with a tighter proper
+            motion cut to aid in visually identifying the stream.  The
+            proper motion cut is $-15 < \mu_{\phi_1}^* < -10$, $-4.5 <
+            \mu_{\phi_2} < -2$ [mas/yr].
+            %
+            }
         \label{fig:gd1-data_selection}
@@
 % --- sec: results_gd1 (end)
-
-        The result of applying our density model to the synthetic data is
-        illustrated in \autoref{fig:mock_data_result}. The top panel shows the
-        weight parameter that controls membership probability as a function of
-        $\phi_1$. The dashed curve represents the output of our data-driven
-        model, while the solid curve is the ground truth. The second panel shows
-        the stream and background in the $(\phi_1,\phi_2)$ plane, and the third
-        panel shows the stream and background in the $(\phi_1,\parallax)$ plane.
-        Points are color-coded according to their membership probability
-        \autoref{eq:membership_prob}. The weight parameter clearly shows that
-        the model has captured the two prominent density variations along the
-        stream.  There are additional variations, mostly around the edges of the
-        stream, though re-sampling the neural network weights with dropout
-        reveals that these variations represent regions of higher model
-        uncertainty.
-
-        We find that the stream is successfully recovered in both astrometric
-        and photometric coordinates, with
-        $\variable{output/mock/ncorrect_variable.txt}\%$ of stream stars being
-        recovered with membership probability greater than $80\%$.  In the
-        bottom two rows of \autoref{fig:mock_data_result} we illustrate the
-        synthetic data color-coded by stream membership probability (top) and
-        background membership probability (background) for different $\phi_1$
-        slices. Importantly, the photometric portion of the mixture model
-        successfully identifies the stream in magnitude space, showing a high
-        stream membership probability where the stream is present, and a low
-        probability ($\sim 0$) where the stream is absent.  The false positive
-        rate (i.e., stars misidentified as stream members) for this test is
-        found to be $\variable{output/mock/falseident_variable.txt}\%$ (3 stars)
-        when cutting on the 80\% membership probability threshold.
-
-% sec: results  (end)
-
-\section{Results: GD-1} \label{sec:results_gd1}
 
@@
     \citep{deBoer+2018}, including a bifurcation that can be modeled by an
-    encounter with a dense dark matter subhalo \citep{Bonaca+2019, Webb+2019}.
+    encounter with a dense perturber \citep{Bonaca+2019, Webb+2019}.
     Characterizing the detailed density fluctuations of this stream is therefore
@@
         proper motions.  For downloading purposes we split the query into 32
-        sub-regions in even $\phi_1$ increments.
-        A plot of the $\phi_1, \phi_2$ regions is included in the
-        \href{\GitHubURL{}}{\package{ShowYourWork}} repository.  Stream-specific
-        coordinates ($\phi_1, \phi_2$) are not included in \Gaia.  One could
-        embed the coordinate transform in the ADQL \citep{ADQL2.0}, or define
-        great-circle arcs in ICRS \citep{ICRS1997}. Since only rough cuts are
-        required and since the sub-region boxes are sufficiently small for a
-        reasonable flat-sky approximation  we simply translate the ($\phi_1,
-        \phi_2$) boxes to ICRS.  We correct the \PanStarrs{} photometry for dust
-        extinction using the \textit{Bayestar19} \citep{Green+2019} models in
-        the \package{dustmaps} package \citep{Green2018}.  \textit{Bayestar19}
-        is a three-dimensional dust map of the Milky Way for which we use
-        \Gaia's position and parallax distance information. We note that the
-        extinction has very little dependence on the distance past $\approx 8 \
-        \rm{kpc}$. For stars with missing parallax measurements we assume a
-        distance of $8.5 \ \rm{kpc}$, a typical distance to the stream, thus
-        increasing potential membership probability. Adopting a slightly lower
-        or higher fiducial distance does not significantly change the results of
-        our analysis. We include the 1$\sigma$ errors as a source of uncertainty
-        in $\mbs{\Sigma}_n$, the per-star photometric uncertainty.  We also
-        correct the parallax for the zero-point using the
+        sub-regions in even $\phi_1$ increments.  Stream-specific coordinates
+        ($\phi_1, \phi_2$) are not included in \Gaia.  One could embed the
+        coordinate transform in the ADQL \citep{ADQL2.0}, or define great-circle
+        arcs in ICRS \citep{ICRS1997}. Since only rough cuts are required and
+        since the sub-region boxes are sufficiently small for a reasonable
+        flat-sky approximation  we simply translate the ($\phi_1, \phi_2$) boxes
+        to ICRS.  We correct the \PanStarrs{} photometry for dust extinction
+        using the \textit{Bayestar19} \citep{Green+2019} models in the
+        \package{dustmaps} package \citep{Green2018}.  \textit{Bayestar19} is a
+        three-dimensional dust map of the Milky Way for which we use \Gaia's
+        position and parallax distance information. We note that the extinction
+        has very little dependence on the distance past $\approx 8 \ \rm{kpc}$.
+        For stars with missing parallax measurements we assume a distance of
+        $8.5 \ \rm{kpc}$, a typical distance to the stream, thus increasing
+        potential membership probability. Adopting a slightly lower or higher
+        fiducial distance does not significantly change the results of our
+        analysis. We include the 1$\sigma$ errors as a source of uncertainty in
+        $\mbs{\Sigma}_n$, the per-star photometric uncertainty.  We also correct
+        the parallax for the zero-point using the
         \href{https://pypi.org/project/gaiadr3-zeropoint/}{\code{gaiadr3-zeropoint}}
@@
         buffered isochrone selection is wide enough to contain \stream{GD-1}
-        over its full distance gradient.  In addition, to avoid detailed
-        modeling of the completeness as a term in $\prior_{obs}$ (from
+        over its full distance gradient, including the ``typical" distance of
+        8.5 kpc used in the photometric correction.  In addition, to avoid
+        detailed modeling of the completeness as a term in $\prior_{obs}$ (from
         \autoref{eq:isochrone_prior_components}) we mask out photometry with $G
@@
     \subsection{Model Specification}\label{sub:results_gd1:model}
-
-        \begin{figure}
-            \script{gd1/plot/photometric_background_selection.py}
-            \centering
-            \includegraphics[width=1\linewidth]{figures/gd1/photometric_background_selection.pdf}
-            \caption{%
-                The on and off-stream selection.
-                % 
-                \textbf{Top panel:} Astrometric coordinates ($\phi_1$,
-                $\phi_2$).  Light blue points are the stream and background
-                within an on-stream region. Black points are in the off-stream
-                region used to train the background photometric model. Note this
-                is on a reduced field with a tighter proper motion cut (the
-                stream visibly truncates at $-10 \ \rm{deg}$ to increase the
-                visibility of the stream's CMD).  The proper motion cut is $-15
-                < \mu_{\phi_1}^* < -10$, $-4.5 < \mu_{\phi_2} < -2$ [mas/yr].
-                %
-                \textbf{Bottom panel:} CMD pl got of the astrometric selection
-                above. The stream's isochrone is apparent as an overdensity.
-                %
-            }
-            \label{fig:gd1-photometric_background_selection}
-        \end{figure}
 
@@
 
-        All full Bayesian stream models necessarily include a background model,
-        which we model in both astrometric and photometric spaces.  The
-        photometric background is too complex to capture with simple analytic
-        distributions.  Instead, we train a normalizing flow on the magnitudes
-        $g, r$, conditioned on $\phi_1$. We refer readers to
+        All full stream models necessarily include a background model, which we
+        model in both astrometric and photometric spaces.  The photometric
+        background is too complex to capture with simple analytic distributions.
+        Instead, we train a normalizing flow on the magnitudes $g, r$,
+        conditioned on $\phi_1$. We refer readers to
         \autoref{sub:method:pre-training_distributions} for discussion of the
@@
         Consequently we select on-stream and off-stream regions using the known
-        $\phi_1,\phi_2$ range of the stream, as shown in the upper panel of
-        \autoref{fig:gd1-photometric_background_selection}.  In the lower panel
-        are plotted these selections in photometric coordinates, where an
-        isochrone is apparent in the on-stream selection.  The normalizing flow
-        is trained on the off-stream selection, and will be fixed (not
-        trainable, nor contribute to the gradient) when incorporated into the
-        larger model.
+        $\phi_1,\phi_2$ range of the stream, as shown in green points in 
+        \autoref{fig:gd1-data_selection}.  In the first row
+        we plotted this selection in photometric coordinates, where an isochrone
+        is apparent in the on-stream selection.  The normalizing flow is trained
+        on the off-stream selection, and will be fixed (not trainable, nor
+        contribute to the gradient) when incorporated into the larger model.
 
@@
         interpolating between two distributions we instead fit the astrometry
-        with a $\phi_1$-conditioned normalizing flow.
+        with a $\phi_1$-conditioned normalizing flow. The background model is
+        characterized by:
 
         \begin{itemize}
+            \setlength\itemsep{0em}
             \item $\phi_2, \sim \rm{TruncExp}(\lambda; a, b)$: a truncated
@@
                 \autoref{app:sub:exponential_distribution}).  The distribution
-                has 1 slope parameters.
+                has 1 slope parameter.
             \item $\mu_{\phi_1}^*, \mu_{\phi_2}, \varpi \sim q_{\rm flow}$: a 3
-                feature, one context feature normalizing flow trained on an
-                off-stream selection (see
-                \autoref{fig:gd1-photometric_background_selection} for that
+                argument , one context feature ($\phi_1$) normalizing flow
+                trained on an off-stream selection (see
+                \autoref{fig:gd1-data_selection} for that
                 selection). Though discussed in the context of a photometric
@@
         -- as an independent addition of both astrometric and photometric
-        models.  The astrometric model is a 5-dimensional Gaussian in a Gaussian
-        track in $\phi_2, \parallax, \mu_{\phi_1}, \mu_{\phi_2}, \parallax$,
-        using the model defined in
+        models.  The astrometric model for the stream is a 5-dimensional
+        Gaussian in a Gaussian track in $\phi_2, \parallax, \mu_{\phi_1},
+        \mu_{\phi_2}, \parallax$, using the model defined in
         \autoref{ssub:method:astrometric_model:on_stream}.  The parameter
-        network's
-        % is a 5-layer \texttt{LTD} with shape (1, 128, 10), where the
-        10 outputs are $\mbs{\theta} = [\mu_{\phi_2}, \sigma_{\phi_2},
+        network's 10 outputs are $\mbs{\theta} = [\mu_{\phi_2}, \sigma_{\phi_2},
         \mu_\parallax, \sigma_\parallax, \mu_{\mu_{\phi_1}^*},
@@
         We use a $12 \ \rm{Gyr}$, [Fe/H]$ = -1.2$ MIST isochrone with no assumed
-        intrinsic dispersion.  Using the method described in
+        intrinsic dispersion.  \stream{GD-1}'s true spectroscopic metallicity is
+        [Fe/H]$\lesssim-2$, but there is enough degeneracy in age and
+        metallicity that the chosen isochrone empirically matches the CMD locus
+        and is useful in this modeling context.  Using the method described in
         \autoref{ssub:method:linking_to_astrometrics} the distance modulus track
         is set by the parallax track in the astrometric model. Thus the
-        photometric model has no independent parameters and consequently no
-        neural network.
+        on-stream photometric model has no independent parameters and
+        consequently no neural network.
 
@@
         converge to the actual stream.  We include all the track regions in
-        \autoref{tab:gd1_track_prior}.  We note that since the distance moduli
-        between the stream and spur are linked, those stream track guides also
-        apply.
-
-        All the component models are tied together into a mixture model.  As an
-        implementation detail, instead of grouping together the stream
-        components in a hierarchical mixture model (background + (stream +
-        spur)) we keep the structure flat, using a single mixture (background +
-        stream + spur) and reducing the number of neural networks. The singular
-        weight parameter network is a \texttt{LTD} network with 15\% dropout.
-        The stream weights are in the range $\ln f \in [-10, 0]$, while the spur
-        weights are $\ln f \in [-10, 0]$ and set to 0 $\phi_1 < -45, -15 <
-        \phi_1$. By \autoref{eq:mixture_weight_normalization} the background
-        brings the cumulative weight to one, normalizing the mixture.
+        \autoref{tab:gd1_track_prior}.
+
+        All the component models are tied together into a mixture model.  The
+        singular weight parameter network is a \texttt{LTD} network with 15\%
+        dropout.  The stream weights are in the range $\ln f \in [-10, 0]$,
+        while the spur weights are $\ln f \in [-10, 0]$ and set to 0 for $\phi_1
+        < -45, -15 < \phi_1$.  By \autoref{eq:mixture_weight_normalization} the
+        background brings the cumulative weight to one, normalizing the mixture.
 
@@
                     $\phi_2(\phi_1)$ over the full range of $\phi_1$. The data
-                    color and transparency is set by the model's 50th-percentile
-                    stream and spur probability. We include the error bars for
-                    stars with $>75\%$ membership probability. The predicted
-                    50th-percentile track $\pm$ width is over-plotted (red
-                    band), along with the 90\% confidence region (broader red
-                    band).  In the adjoining top plot is shown the 5th to 95th
-                    percentile variation in the width.
+                    color and transparency are set by the model's
+                    50th-percentile stream and spur probability. We include the
+                    error bars for stars with $>75\%$ membership probability.
+                    The predicted 50th-percentile track $\pm$ width is
+                    over-plotted (red band), along with the 90\% confidence
+                    region (broader red band).  The 5th to 95th percentile
+                    variation in the width is shown  in the adjoining top plot.
                 %
@@
                 \textbf{Panel 5 \& 6: }%
-                    The proper motions $\mu_{\phi_1^*}, \mu_{\phi_2}$. The model
-                    convolves observational errors with the stream width, but
-                    the large fractional errors make the determination
-                    difficult. The track is consistent with 0 at $\mu_{\phi_2} <
-                    -40 \ \rm{deg}$, but has noticeable variations in
-                    $\mu_{\phi_1}$.  }
+                    The proper motions $\Delta \mu_{\phi_1^*}, \Delta
+                    \mu_{\phi_2}$ shown relative to the galstreams track (black
+                    dashed line). The model convolves observational errors with
+                    the stream width, but the large fractional errors make the
+                    determination difficult.   }
             \label{fig:gd1-results-full}
@@
 
-        In this section we present results from our model applied to real {\it
-        Gaia} and Pan-STARRS data of \stream{GD-1}.  We visualize the
+        \begin{figure}[t]
+            \script{gd1/plot/member_probabilities.py}
+            \centering
+            \includegraphics[width=1.05\linewidth]{figures/gd1/member_probabilities.pdf}
+            \caption{%
+                Distribution of membership probabilities (primary axis).
+                Number of stars exceeding the membership probability (secondary axis; green).
+                \stream{GD-1} stars have high membership probability, compared to low-membership probability background stars.
+As can be seen, the majority of stars are confidently separated, with a minima between the background and stream at $\sim 50\%$ membership probability.
+                %
+            }
+            \label{fig:gd1-member_probs}
+        \end{figure}
+
+        In this section we present results from our model applied to real \Gaia{} and Pan-STARRS data of \stream{GD-1}.  We visualize the
         performance of our model in identifying stream stars in
@@
         provide a selection of \stream{GD-1} member stars. The full catalog is
-        available online \TODO{add zenodo link when upload}. Lastly,
-        \autoref{fig:gd1-heatmap} is a probability-weighted density heatmap of
-        the \stream{GD-1} stream derived from our fit.
+        available online at
+        \href{https://zenodo.org/doi/10.5281/zenodo.10903751}{DOI 10.5281/zenodo.10211409}.
+In Fig.~\ref{fig:gd1-member_probs} a summary of stream membership probabilities for the GD-1 field considered is provided.
+Lastly,
+        \autoref{fig:gd1-heatmap} is a membership probability-weighted density
+        heatmap of the \stream{GD-1} stream derived from our fit.
 
@@
         discussed below). The red and yellow bands represent model predictions
-        for in each panel for the main stream and spur, respectively. The points
-        with thick error bars represent control points (discussed in
+        for the main stream and spur, respectively. The points with thick error
+        bars represent control points (discussed in
         \autoref{sub:results_gd1:model}) for the stream and spur components,
@@
         components). For stars with membership probability greater than $75\%$,
-        we also plot their astrometric errorbars from \package{Gaia} as the thin
-        red lines.
-
-        \begin{figure*}[t]
-            \script{gd1/plot/results_panels.py}
-            \centering
-            \includegraphics[width=1\linewidth]{figures/gd1/results_panels.pdf}
-            \caption{%
-                Photometric coordinate $(g, r)$ plots for each model component
-                in 4 $\phi_1$ ranges across the data set. Over-plotted is the
-                model isochrone, shifted to the mean distance of the track
-                within the bin of $\phi_1$. Importantly this means we don't
-                expect the mean isochrone to exactly match the distribution of
-                points. See \autoref{fig:gd1-results-full} for the match of the
-                distance gradient to the data and prior literature results.
-                %
-            }
-            \label{fig:gd1-results-panels}
-        \end{figure*}
+        we also plot their astrometric errorbars from \Gaia{} as the thin red
+        lines.
 
@@
 
-        The extent of the main stream in $\phi_1$ is roughly $70~\rm{deg}$, and
-        the angular extent of the spur is roughly $25~\rm{deg}$. The distance
+        We illustrate our determination of membership probabilities in Fig.~\ref{fig:gd1-member_probs}.
+The x-axis is the stream-membership probability, computed from Eq.~\ref{eq:membership_prob}.
+The histogram illustrates the number of stars (i.e., membership frequency) in bins of membership probability.
+The green curve (secondary y-axis) is the survival function of the histogram, or one minus the cumulative density function.
+This curve provides the number of stars with membership probability greater than the x-axis value.
+For instance, all stars in the field have membership probabilities greater than 0, while around 800 stars have membership probabilities greater than 0.8.
+
+        The extent of the main stream in $\phi_1$ is roughly $80~\rm{deg}$, and
+        the angular extent of the spur is roughly $15~\rm{deg}$. The distance
         track (bottom panel) places the stream in the range of $6-10~\rm{kpc}$,
@@
         $[4,40]~\rm{kpc}$, with a broad prior around previous literature
-        estimates. Therefore, the similarity of our inferred distance track
-        compared to other works indicates that our photometric model is
-        performing satisfactorily.
+        estimates. The similarity of our inferred distance track compared to
+        other works indicates that our photometric model is performing
+        satisfactorily.
+
+        \begin{figure*}[t]
+            \script{gd1/plot/results_panels.py}
+            \centering
+            \includegraphics[width=1\linewidth]{figures/gd1/results_panels.pdf}
+            \caption{%
+                Photometric coordinate $(g, r)$ plots for each model component
+                in 4 $\phi_1$ ranges across the data set. Over-plotted is the
+                model isochrone, shifted to the mean distance of the track
+                within the selected $\phi_1$ range. Importantly this means we do
+                not expect the mean isochrone to exactly match the distribution
+                of points. See \autoref{fig:gd1-results-full} for the match of
+                the distance gradient to the data and prior literature results.
+                %
+            }
+            \label{fig:gd1-results-panels}
+        \end{figure*}
 
@@
         by \citet{CarlbergGrillmair2013}, and is one location hypothesized for
-        the dissolved stream progenitor. \citep{WebbBovy2019} suggests the
+        the dissolved stream progenitor. \citet{WebbBovy2019} suggests the
         $-40\degree$ gap might be  the progenitor location.  The recovery of
@@
         the \stream{GD-1} main stream through the photometric model. The model
-        finds a non-negligible spur feature, with fractional weight approaching
-        the thin stream at its peak. Corroborating this finding, the proper
-        motion of the spur almost exactly agrees with the thin stream. The
-        alignment of these dimensions is not hard-coded in our model. The width
-        of the spur in proper motion is very thin, thinner even than the stream.
-        However with the large observational errors and low number density of
-        the spur it is difficult to attribute this to a physical difference
-        between the two systems. In contrast, the small errors in $\phi_2$
-        indicate the spur's width diverges from the thin stream at $\phi_1 > -35
-        \ \rm{deg}$, whereas the width is similar at lower $\phi_1$. There are
-        numerous mechanisms by which a stream's width may vary \citep[e.g.
-        epicyclic effects as in][]{Ibata+2020}, so differences between the spur
-        and stream are both notable and expected.
+        finds a non-negligible spur feature, with a peak fractional weight
+        approaching the thin stream. As corroboration, the proper motion of the
+        spur closely agrees with the thin stream. The alignment of these
+        dimensions is not hard-coded in our model. The width of the spur in
+        proper motion is very thin, thinner even than the stream.  However with
+        the large observational errors and low number density of the spur it is
+        difficult to attribute this to a physical difference between the two
+        systems. In contrast, the small errors in $\phi_2$ indicate the spur's
+        width diverges from the thin stream at $\phi_1 > -35 \ \rm{deg}$,
+        whereas the width is similar at lower $\phi_1$. There are numerous
+        mechanisms by which a stream's width may vary \citep[e.g.  epicyclic
+        effects as in][]{Ibata+2020}, so differences between the spur and stream
+        are both notable and expected.
+
+        \stream{GD-1} has other observed tidal features, namely the ``blob''
+        \citep{Price-WhelanBonaca2018}, which is a very diffuse component
+        enclosing the thin stream. When fitting our model to \stream{GD-1} with
+        a more stringent proper motion cut, we are able to recover the blob. In
+        a more crowded field, the stream makes up only a few percent of the
+        total number of stream stars, so diffuse features like the blob are not
+        separated from the background. We could, perhaps, guide the model
+        towards the blob by adding an additional mixture distribution that is
+        specialized to diffuse components around the thin stream. Because the
+        aim of the current paper is to introduce and demonstrate our method, we
+        defer a more detailed fit of the diffuse extra-tidal structure of Milky
+        Way streams to future work.
+
+        \begin{figure}[ht]
+            \script{gd1/plot/smooth_likelihood.py}
+            \centering
+            \hspace{-25 pt}\includegraphics[width=1.05\linewidth]{figures/gd1/smooth_likelihood.pdf}
+            \caption{%
+                Smoothed KDE model of \stream{GD-1}'s member stars, weighted by
+                their membership probability. The KDE has a bandwidth of $0.1 \
+                \rm{deg}$ (or mas/yr).  In $\phi_2$ the spur is clearly visible
+                in the KDE.  The gaps at $-20\degree$ are prominent in both
+                $\phi_2$ and $\mu_{\phi_1}$.  The gap at $-40\degree$ is most
+                prominent in $\phi_2$.
+                %
+            }
+            \label{fig:gd1-heatmap}
+        \end{figure}
 
@@
         performance of our photometric model in bands of $\phi_1$. Our model
-        isochrone, which shifts vertically due to our estimate of a distance
-        modulus, is shown in green (we plot the mean-distance isochrone in each
-        $\phi_1$ band). Because our model preforms a joint fit in photometry and
+        isochrone, which shifts vertically due to our distance modulus estimate,
+        is shown in green (we plot the mean-distance isochrone in each $\phi_1$
+        band). Because our model preforms a joint fit in photometry and
         astrometry, the most probable stream members do not need to fall exactly
@@
         illustrate this in  \autoref{fig:gd1-heatmap}, which shows a Gaussian
-        kernel density estimate (KDE) of bandwidth $0.1 \ \rm{deg}$ fit to the
-        model. The primary overdensities at $\phi_1 = (-50, -30, -10) \
-        \rm{deg}$ are all visible in $\phi_2$. The gap at $20 \ \rm{deg}$ is
+        kernel density estimate (KDE) of bandwidth $0.1 \ \rm{deg}$ (or mas/yr)
+        fit to the model. The primary overdensities at $\phi_1 = (-50, -30, -10)
+        \ \rm{deg}$ are all visible in $\phi_2$. The gap at $20 \ \rm{deg}$ is
         prominent in all features, but the gap at $-40$ is less visible in
@@
 
-        \begin{figure}[h]
-            \script{gd1/plot/smooth_likelihood.py}
+% sub: gd1 (end)
+
+% -----------------------------------
+
+    \begin{figure*}[ht]
+        \script{pal5/plot/data_selection.py}
         \centering
-            \hspace{-25  pt}\includegraphics[width=1.1\linewidth]{figures/gd1/smooth_likelihood.pdf}
+        \includegraphics[width=1\linewidth]{figures/pal5/data_selection.pdf}
         \caption{%
-                Smoothed KDE model of \stream{GD-1}'s member stars, weighted by
-                their membership probability. The KDE has a bandwidth of $0.1 \
-                \rm{deg}$.  In $\phi_2$ the spur is clearly visible in the KDE.
-                The gaps at $-20\degree$ is prominent in both $\phi_2$ and
-                $\mu_{\phi_1}$.  The gap at $-40\degree$ is most prominent in
-                $\phi_2$.
+            Data selections for \stream{Pal\,5}, within the data cube described
+            in \autoref{sub:results_pal5:data}.
+            %
+            \textbf{Row 1:}
+            Proper motion and photometric selections.  \stream{Pal\,5} is
+            apparent in the proper motions as a small overdensity. The
+            photometric selection is based on a 12 Gyr, [Fe/H] = $-1.2$ MIST
+            isochrone, buffered by 0.3 dex. The photometry is also cut to
+            \Gaia{}'s $G\leq20$ mag, before applying the isochrone selection.
+            In green is plotted an ``on''-stream selection (see $\phi_1, \phi_2$ plot). The stream's isochrone is somewhat apparent, but the
+            background contamination is large.
+            %
+            \textbf{Rows 2 \& 3:}
+            Applying the combination of astrometric and photometric selections (Row 1, blue regions),
+            plotted for astrometric coordinates $\phi_2, \parallax,
+            \mu_{\phi_1}, \mu_{\phi_2}$.  The stream is an identifiable
+            overdensity in only $\phi_2$ and errors dominate all other
+            coordinates.
+            \textbf{Row 2, left:}
+            Green points define an``on"-stream region. Light blue points are the background and are used to train the background photometric
+            model (\autoref{sub:results_pal5:model}). The \stream{M5} cluster is masked from the stream, cutting into the on-stream selection.
             %
         }
-            \label{fig:gd1-heatmap}
-        \end{figure}
-
-% sub: gd1 (end)
-
-% \newpage
+        \label{fig:pal5-data_selection}
+    \end{figure*}
+
+% -----------------------------------
+
 \section{Results: Palomar 5} \label{sec:results_pal5}
@@
     photometric techniques, like with the discovery in \citet{Odenkirchen+2001}.
-    Post-\package{Gaia} the stream was also observed by filtering kinematically
+    Post-\Gaia{} the stream was also observed by filtering kinematically
     \cite[e.g.,][]{Starkman+2019, Ibata+2021}.  However at $\sim 20 \ \rm{kpc}$,
-    the \stream{Pal\,5} main sequence is not observed by \package{Gaia}, making
-    a high signal-to-noise astrometric detection challenging.
-    %In this work we detect over $10 \ \rm{deg}$ of stream.
-    We discuss the data selection in \autoref{sub:results_pal5:data}, model
-    specifics in \autoref{sub:results_pal5:model}, and the results in
+    the \stream{Pal\,5} main sequence is not observed by \Gaia{}, making a high
+    signal-to-noise astrometric detection challenging.  We discuss the data
+    selection in \autoref{sub:results_pal5:data}, model specifics in
+    \autoref{sub:results_pal5:model}, and the results in
     \autoref{sub:results_pal5:results}.
@@
         errors are included by quadrature in $\mbs{\Sigma}_n$, the per-star
-        photometric uncertainty. We also correct the parallax for the \Gaia\
+        photometric uncertainty. We also correct the parallax for the \Gaia{}
         zero-point as in \autoref{sub:results_gd1:data}.  The result is a field
@@
 
-        \begin{figure*}[ht]
-            \script{pal5/plot/data_selection.py}
-            \centering
-            \includegraphics[width=1\linewidth]{figures/pal5/data_selection.pdf}
-            \caption{%
-                Data selections for \stream{Pal\,5}, within the data cube
-                described in \autoref{sub:results_pal5:data}.
-                %
-                \textbf{Row 1 Panels:}
-                Proper motion and photometric selections.  \stream{Pal\,5} is
-                apparent in the proper motions as a small overdensity. The
-                photometric selection is based on a 12 Gyr, [Fe/H] = -1.2 MIST
-                isochrone, buffered by 0.3 dex.
-                %
-                \textbf{Rows 2 \& 3 Panels:}
-                Applying the combination of astrometric and photometric
-                selections, plotted for astrometric coordinates $\phi_2,
-                \parallax, \mu_{\phi_1}, \mu_{\phi_2}$.  The stream is an
-                identifiable overdensity in only $\phi_2$ and errors dominate
-                all other coordinates.  }
-            \label{fig:pal5-data_selection}
-        \end{figure*}
-
         The reduced dataset, with all specific masks applied, is included below
@@
         sufficiently large to permit 15\% dropout and retain robust predictions.
-        At $\sim 20 \ \rm{kpc}$ any \package{Gaia}-crossmatched data is not
+        At $\sim 20 \ \rm{kpc}$ any \Gaia{}-crossmatched data is not
         photometrically deep enough to contain the main sequence nor its turn
@@
 
-        \begin{figure}[ht]
-            \script{pal5/plot/photometric_background_selection.py}
+% -----------------------------------
+
+        \begin{figure*}[ht]
+            \script{pal5/plot/results_full.py}
             \centering
-            \includegraphics[width=1\linewidth]{figures/pal5/photometric_background_selection.pdf}
+            \includegraphics[width=0.85\linewidth]{figures/pal5/results_full.pdf}
             \caption{%
-                \textbf{Top panel:} Astrometric coordinates ($\phi_1$,
-                $\phi_2$).  Light blue points are the stream and background
-                within an ``on"-stream region. Black points are in the
-                ``off"-stream region used to train the background photometric
-                model. The \stream{M5} cluster is masked as a black circle
-                cutting into the on-stream selection at $\phi_1\sim-1\degree$.
-                %
-                \textbf{Bottom panel:} CMD plot of the astrometric selection
-                above. The stream's isochrone is somewhat apparent, but the
-                background contamination is large.
-                %
-            }
-            \label{fig:pal5-photometric_background_selection}
-        \end{figure}
+                The model for \stream{Pal\,5}.  For comparison we include the
+                tracks from \citet{Price-Whelan+2019} and \citet{Ibata+2021}.
+                %
+                \textbf{Panel 1: }%
+                The stream mixture coefficients $f(\phi_1)$ predicted by the
+                model, colored by the stream membership likelihood. The
+                stream fraction and number density drop to nearly $0$ for $\phi_1 > 5 \
+                \rm{deg}$, making the track dominated by low-number
+                statistics.
+                %
+                \textbf{Panel 2: }
+                $\phi_2(\phi_1)$ over the full range of $\phi_1$. The data color
+                and transparency are set by the model's 50th-percentile stream
+                probability. We include the error bars for stars with $>75\%$
+                membership probability. The predicted 50th-percentile track
+                $\pm$ width is over-plotted (red band), along with the 90\%
+                confidence region (broader red bend). The 5th to 95th percentile
+                variation in the width is shown in the adjoining top plot.
+                %
+                \textbf{Panel 3: }%
+                $\parallax(\phi_1)$ and $d(\phi_1)$ over the full range of
+                $\phi_1$.
+                %
+                \textbf{Panel 4 \& 5: }%
+                The proper motions $\mu_{\phi_1^*}, \mu_{\phi_2}$. The model
+                convolves observational errors with the stream width, but the
+                large fractional errors make the determination difficult. The
+                track is largely consistent with 0 width driven by small number
+                statistics.  }
+            \label{fig:pal5-results-full}
+        \end{figure*}
+
+% -----------------------------------
 
@@
                 selection (see
-                \autoref{fig:pal5-photometric_background_selection} for that
+                \autoref{fig:pal5-data_selection} for that
                 selection). \autoref{sub:method:pre-training_distributions}
@@
 
-        All the component models are tied together into a mixture model.  The
-        weight parameter network is the usual \texttt{LTD} with 15\% dropout.
-        The stream weights are in the range $\ln{f_{\rm stream}} \in [-10, 0]$
-        and set to $-\infty$ for $\phi_1 \notin [-10^\circ, 10^\circ]$. By
-        \autoref{eq:mixture_weight_normalization} the background  brings the
-        cumulative weight to one, normalizing the mixture.
-
-    % sub model_specification (end)
-
-    \subsection{Trained Density Model} \label{sub:results_pal5:results}
-
-        \begin{figure*}[ht]
-            \script{pal5/plot/results_full.py}
-            \centering
-            \includegraphics[width=0.85\linewidth]{figures/pal5/results_full.pdf}
-            \caption{%
-                The model for \stream{Pal\,5}.  For comparison we include the
-                tracks from \citet{Price-Whelan+2019} and \citet{Ibata+2021}.
-                Note how the model largely agrees with both tracks in all
-                astrometric dimensions from $-5 < \phi_1 < 5 \ \rm{deg}$. The
-                stream fraction and number density drop to near $0$ for $5 \
-                \rm{deg} < \phi_1$, making the track dominated by low-number
-                statistics. The progenitor is not separated from the stream as a
-                distinct component, demonstrating how the neural networks can
-                capture a large range of linear densities.
-                %
-                \textbf{Panel 1: }%
-                The stream mixture coefficients $f(\phi_1)$ predicted by the
-                model, colored by the stream membership likelihood.
-                %
-                \textbf{Panel 2: }
-                $\phi_2(\phi_1)$ over the full range of $\phi_1$. The two stream
-                arms visibly emerge from the Lagrange points of the stream.  The
-                data color and transparency is set by the model's
-                50th-percentile stream and spur probability. We include the
-                error bars for stars with $>75\%$ membership probability. The
-                predicted 50th-percentile track $\pm$ width is over-plotted (red
-                band), along with the 90\% confidence region (broader red bend).
-                In the adjoining top plot is shown the 5th to 95th percentile
-                variation in the width.
-                %
-                \textbf{Panel 3: }%
-                $\parallax(\phi_1)$ and $d(\phi_1)$ over the full range of
-                $\phi_1$.
-                %
-                \textbf{Panel 4 \& 5: }%
-                The proper motions $\mu_{\phi_1^*}, \mu_{\phi_2}$. The model
-                convolves observational errors with the stream width, but the
-                large fractional errors make the determination difficult. The
-                track is largely consistent with 0 width driven by small number
-                statistics.  }
-            \label{fig:pal5-results-full}
-        \end{figure*}
-
-        \begin{figure*}[htp]
+% ------------------------
+        \begin{figure*}[tp]
             \script{pal5/plot/results_panels.py}
@@
                 for $\phi_1 > 5\degree$ is consistent with
-                \citet{Starkman+2019}. We do detect any fanning of the stream,
-                but given the shallow photometry, this is expected.
+                \citet{Starkman+2019}. We do not detect any fanning of the
+                stream, but given the shallow photometry, this is expected.
                 %
@@
         \end{figure*}
-
+% ------------------------
+
+        All the component models are tied together into a mixture model.  The
+        weight parameter network is the usual \texttt{LTD} with 15\% dropout.
+        The stream weights are in the range $\ln{f_{\rm stream}} \in [-10, 0]$
+        and set to $-\infty$ for $\phi_1 \notin [-10^\circ, 10^\circ]$. By
+        \autoref{eq:mixture_weight_normalization} the background  brings the
+        cumulative weight to one, normalizing the mixture.
+
+    % sub model_specification (end)
+
+    \subsection{Trained Density Model} \label{sub:results_pal5:results}
         \variable{output/pal5/member_table_select.tex}
 
-        Our fit to \stream{Pal\,5} and its tidal tails is illustrated in
-        \autoref{fig:pal5-results-full}. In the top panel we plot the stream
+        In this section we illustrate our fit to \stream{Pal\,5} and its tidal tails. The trained density model is shown in
+        \autoref{fig:pal5-results-full} in astrometric coordinates, 
+        \autoref{fig:pal5-results-panels} in photometric coordinates, and membership probabilities for all stars in the Pal-5 field considered are summarized in \autoref{fig:pal5-member_probs}.
+A heatmap of the stream, weighted by membership probabilities, is shown in \autoref{fig:pal5-heatmap}.
+
+        In the top panel of \autoref{fig:pal5-results-full} we plot the stream
         fraction and its uncertainty, estimated by applying dropout during
         inference and evaluation of our model. The model clearly identifies the
-        progenitor cluster $(\phi_1 = 0)$.
-
-        The membership probability of stream stars is illustrated in subsequent
+        progenitor cluster $(\phi_1 = 0)$. The membership probability of stream stars is illustrated in subsequent
         panels of \autoref{fig:pal5-results-full}, with guide points and their
@@
 
-        The stream solution, ie the per-star membership likelihood, is a
+        \begin{figure}[htp]
+            \script{pal5/plot/member_probabilities.py}
+            \centering
+            \includegraphics[width=1.05\linewidth]{figures/pal5/member_probabilities.pdf}
+            \caption{%
+                Distribution of membership probabilities (primary axis).
+                Number of stars with membership probability exceeding the threshold (secondary axis).
+                \stream{Pal\,5} stars have high membership probability, compared to low-membership probability background stars.
+As can be seen, there are two minima in the probability distribution, at $\sim 50\%$ and $\sim 85\%$ membership probability.
+                %
+            }
+            \label{fig:pal5-member_probs}
+        \end{figure}
+
+        Our determination of stream membership probabilities is summarized in Fig.~\ref{fig:pal5-member_probs}.
+The x-axis is the stream-membership probability, computed from Eq.~\ref{eq:membership_prob}.
+The histogram illustrates the number of stars (i.e., membership frequency) in bins of membership probability.
+The green curve is the survival function of the histogram, or one minus the cumulative distribution function.
+For example, this curve indicates that there are roughly 400 stars with membership probability greater than $0.8$.
+
+        \begin{figure}[htp]
+            \script{pal5/plot/smooth_likelihood.py}
+            \centering
+            \hspace{-25pt}\includegraphics[width=1.05\linewidth]{figures/pal5/smooth_likelihood.pdf}
+            \caption{%
+                Smoothed KDE model of the stream's member stars, weighted by
+                their membership probability. The KDE has a bandwidth of $0.1 \
+                \rm{deg}$ (or mas/yr). We exclude the progenitor to limit the
+                density range and better display the diffuse tidal tails. The
+                stream extends from $-12$ to $10$ degrees in this plot, which
+                appears longer than in \autoref{fig:pal5-results-full} and
+                \autoref{fig:pal5-results-panels}. Those show the membership
+                likelihood at the $50$th-percentile of its distribution. This
+                figure samples over the full posterior, showing the contribution
+                of less-likely members.
+                %
+            }
+            \label{fig:pal5-heatmap}
+        \end{figure}
+
+        The stream solution, i.e. the per-star membership likelihood, is a
         posterior distribution. \autoref{fig:pal5-results-full} and
@@
         \autoref{fig:pal5-heatmap} we sample over the full distribution and
-        smooth by a 0.1 $deg$ kernel to produce a smooth representation of the
-        stream. As a consequence of the sampling we see the model's stream
-        solution extends beyond the $\approx \pm5\degree$ shown previously.
-        Though the model certainty and individual membership likelihoods are
-        low, the stream path matches closely with findings in deeper photometric
-        catalogues, like \citet{Ibata+2017}.
-
-        \begin{figure}[h]
-            \script{pal5/plot/smooth_likelihood.py}
-            \centering
-            \includegraphics[width=1\linewidth]{figures/pal5/smooth_likelihood.pdf}
-            \caption{%
-                Smoothed KDE model of the stream's member stars, weighted by
-                their membership probability. The KDE has a bandwidth of $0.1 \
-                \rm{deg}$. We exclude the progenitor to limit the density range
-                and better display the diffuse tidal tails. The stream extends
-                from $-12$ to $10$ degrees in this plot, which appears longer
-                than in \autoref{fig:pal5-results-full} and
-                \autoref{fig:pal5-results-panels}. Those show the membership
-                likelihood at the $50$th-percentile of its distribution. This
-                figure samples over the full posterior, showing the contribution
-                of less-likely members.
-                %
-            }
-            \label{fig:pal5-heatmap}
-        \end{figure}
-
-        While \package{Gaia} alone is not photometrically capable of observing
-        the main sequence of \stream{Pal\,5}'s tidal tails, the modeling
-        framework we present here is capable of operating on outer-joined
-        datasets. This allows us to easily combine deep photometric data with
-        kinematics from, e.g., \package{Gaia}.  We leave that to a future work,
-        though expect that a simultaneous model in photometry and astrometry
-        would help identify the more diffuse parts of the stream, which become
-        washed out in our astrometric fit due to the substantial number of
-        background stars. Still, this section highlights the capability of our
-        model when applied to a noisy field with a diffuse stream.
-
-    % sub trained_density_model
+        smooth by a 0.1~deg (or mas/yr) kernel to produce a smooth
+        representation of the stream. As a consequence of the sampling we see
+        the model's stream solution extends beyond the $\approx \pm5\degree$
+        shown previously.  Though the model certainty and individual membership
+        likelihoods are low, the stream path matches closely with findings in
+        deeper photometric catalogues, like \citet{Ibata+2017}.
+
+        While \Gaia{} alone is not photometrically capable of observing the main
+        sequence of \stream{Pal\,5}'s tidal tails, the modeling framework we
+        present here is capable of operating on outer-joined datasets. This
+        allows us to easily combine deep photometric data with kinematics from,
+        e.g., \Gaia{}.  We leave that to a future work, though expect that a
+        simultaneous model in photometry and astrometry would help identify the
+        more diffuse parts of the stream, which become washed out in our
+        astrometric fit due to the substantial number of background stars.
+        Still, this section highlights the capability of our model when applied
+        to a noisy field with a diffuse stream.
+
+    % sub trained_density_model (end)
 
@@
     We now provide a discussion of the methods presented in the paper, focusing
-    on future directions in \autoref{sec:conclusions} and comparison to other
-    works in \autoref{sec:comparison}.
-
-    \subsection{Limitations}\label{sec:limitations}
-
-        We first highlight the limitations of our method, and areas for
-        potential improvement.
+    on limitations of our approach in \autoref{sec:limitations} and comparison
+    to existing methods in \autoref{sub:comparison}. In
+    \autoref{sub:future_surveys} we discuss prospects for applying our method to
+    existing and future datasets.
+
+    \subsection{Caveats and Limitations}\label{sec:limitations}
+
+        We now highlight the limitations of our method, and areas for potential
+        improvement.
 
@@
         expressive, and capable of describing a diverse range of stream
-        morphologies all under one unified framework. At the same time, neural
-        network training is computationally expensive, and takes a long time on
-        a local device. Our fits to \stream{GD-1} and \stream{Pal\,5} presented
-        in this work were performed on a local computer without GPU support,
-        though training time takes on the order of a few hours per stream. This
-        can be improved substantially with the use of GPUs.
+        morphologies all under one framework. At the same time, neural network
+        training is computationally expensive, and takes a long time on a local
+        device. Our fits to \stream{GD-1} and \stream{Pal\,5} presented in this
+        work were performed on a local computer without GPU support, though
+        training time takes on the order of a few hours per stream. This can be
+        improved substantially with the use of GPUs.
 
@@
         Especially considering that globular clusters do not always follow
-        simple single-stellar population (see, e.g.,
-        \citealt{2022Univ....8..359M} for a review of this subject), it is worth
-        considering whether more data-driven approaches can be used to model the
-        photometry of a stream without imposing tight priors on the stellar
-        population.
+        simple single-stellar population (see, e.g., \citealt{MiloneMarino2022}
+        for a review of this subject), it is worth considering whether more
+        data-driven approaches can be used to model the photometry of a stream
+        without imposing tight priors on the stellar population.
 
@@
         complicated, in all coordinates. The analytic distributions in our
-        modeling are clearly approximate. While the analytic distributions might
-        be made more complex, the alternative is to substitute for
-        non-parameteric flexible models. We have postponed this to future work,
-        since the analytic backgrounds provide a decent description in the
-        fields of \stream{GD-1} and \stream{Pal\,5}. However, this might not be
-        the case for other streams. Constructing flexible background models will
-        therefore provide further improvement over our method.
+        modeling (specifically the $\phi_2$ background distributions) are
+        clearly approximate. While the analytic distributions might be made more
+        complex, the alternative is to substitute for non-parameteric flexible
+        models. We have postponed this to future work, since the analytic
+        backgrounds provide a decent description in the fields of \stream{GD-1}
+        and \stream{Pal\,5}. However, this might not be the case for other
+        streams. Constructing flexible background models will therefore provide
+        further improvement over our method.
+
+        Fourth, the number density of stars belonging to a stream is determined
+        by several interesting physical processes. These include (e.g.)
+        epicyclic overdensities, the orbital phase of the stream, and
+        interactions with galactic substructure. Our model constrains the
+        stellar number density along any given stream, and can therefore be used
+        to infer the underlying mechanism(s) responsible for the stream’s
+        density. However, all observational surveys are subject to selection
+        effects. In order to determine the nature and reality of a stream’s
+        density fluctuations, selection effects must be accounted for. For the
+        case of \Gaia{}, there is ongoing work to model the survey’s selection
+        function \citep{Cantat-Gaudin+2023}. Our model provides the first step,
+        which is to characterize the observations.  With additional work, the
+        selection function may be incorporated into our model and fits as a
+        prior on the data.  Doing so will enable a more robust analysis of each
+        stream's linear density, allowing us to make more definitive conclusions
+        about its intrinsic structure. We defer this to future work
 
@@
         reduce the data down to a clean enough selection of stars so that our
-        model can converge to a high likelihood solution. If the field is too
-        noisy and control points cannot be reliably placed, our method might not
-        be able to characterize the stream of interest. An end-to-end stream
-        discovery and detailed characterization algorithm could therefore
-        provide a substantial improvement over our method and existing work.
-
-    \subsection{Comparison to Existing Methods} \label{sec:comparison}
+        model can converge to a high likelihood solution. Crucially, the field
+        must contain not only stream stars but also enough background stars to
+        model that component well and distinguish stream from background. As a
+        rule of thumb, it is best if the stream is at least a few percent of the
+        total data, preferably even 10\%. Better background models permit this
+        fraction to be pushed down further.  If the field is too noisy and
+        control points cannot be reliably placed, our method might not be able
+        to characterize the stream of interest.  This also applies to streams
+        with bifurcated features like GD-1's spur component. To model these
+        additional features we must add a separate mixture component. A more
+        data-driven approach to characterize previously unknown or diffuse
+        extensions to a stream would mark a substantial improvement over our
+        current implementation. We leave this to future work.
+
+    \subsection{Comparison to Existing Methods} \label{sub:comparison}
 
@@
         Currently, the matched filter is the most common method for detecting
-        and characterizing streams. The method works by selecting a stellar
-        population in the CMD (i.e., from a metal-poor isochrone) and searching
-        for a stellar overdensity in the astrometric data. The approach has
-        proved successful for stream detection, but to a lesser extent for
-        characterization. From the matched filter approach alone, stream
-        membership probabilities are not obtained and there is substantial
-        contamination from background stars. While the approach can provide an
-        excellent coarse-grained description of a given stream, it does not
-        provide a density model in astrometry and photometry.
+        and characterizing streams (e.g., \citealt{Rockosi+2002, Grillmair2014,
+        Bonaca+2012, Jethwa+2018, Shipp+2018}).  The method works by selecting a
+        stellar population in the CMD (i.e., from a metal-poor isochrone) and
+        searching for a stellar overdensity in the astrometric data. The
+        approach has proved successful for stream detection, but to a lesser
+        extent for characterization. From the matched filter approach alone,
+        stream membership probabilities are not obtained and there is
+        substantial contamination from background stars. While the approach can
+        provide an excellent coarse-grained description of a given stream, it
+        does not provide a density model in astrometry and photometry.
 
         To a good approximation streams are expected to roughly trace a stellar
-        orbit. The Streamfinder algorithm exploits this physical expectation
+        orbit. The STREAMFINDER algorithm exploits this physical expectation
         \citep{STREAMFINDER}, by integrating orbits in a trial Galactic
         potential and identifying stellar overdensities that appear to coincide
-        with the trial orbits. While the method has identified many stream
-        candidates, using these streams for potential reconstruction is circular
-        in reasoning. That is, the detection and characterization of these
-        streams is conditioned on a choice of the potential. The method we
+        with segments of the trial orbits. While the method has identified many
+        stream candidates, using these streams for potential reconstruction is
+        circular in reasoning. That is, the detection and characterization of
+        these streams is conditioned on a choice of the potential. The method we
         present here does not make assumptions about the gravitational
@@
         detailed characterization (as stated in \citealt{Shih+2022}). Our work
-        has the opposite approach: the method presented is not designed to
-        detect streams, rather, it is well-suited for characterizing streams
-        that fall within some predefined field. Thus, our method can be used for
+        has the opposite intent: the method presented is not designed to detect
+        streams, rather, it is well-suited for characterizing streams that fall
+        within some predefined field. Thus, our method can be used for
         characterizing the VIA MACHINAE candidates, and obtaining more robust
@@
         modeling the $\phi_1-\phi_2$ distribution for those stars, and then
-        refining the CMD fit based on the $\phi_1-\phi_2$ fit. This approach
-        therefore represents a more principled way of carrying out a matched
-        filter analysis. The model does not currently incorporate kinematic
-        information, though the work could be extended. The improvement of our
-        work is that we do not require an iterative fit to the CMD and
-        astrometry: we handle both spaces through a joint likelihood without
-        simulating mock-observations. Additionally, we can easily incorporate
-        kinematic information and data with missing phase-space dimensions.
-
-        Finally, our method relies on neural networks to describe the stream
-        track rather than splines, and a combination of normalizing flows and
-        analytic densities to characterize the distribution of background stars
-        in photometry and astrometry. While splines are attractive in their
-        simplicity and flexibility, the expressiveness of a spline is largely
-        determined by (a) the number of spline ``knots", and (b) the location of
-        each knot. This is not entirely dissimilar from a neural network, which
-        is subject to some choice of hyper-parameters. However, neural networks
-        are universal function approximators and are therefore readily equipped
-        to describe non-trivial density distributions without imposing priors on
-        the ``reach" of a model. However, when priors are needed, we have shown
-        that they can be added as control points in the loss function, guiding
-        our fits to prefer extended filamentary structures on the sky.
-        Therefore, our neural network based approach enjoys many of the same
-        benfits as splines, with the benefit of being more agnostic to choices
-        like the number and location of knots, and the order of the spline
-        (i.e., cubic, quartic, etc.).
-
-        We also highlight upcoming work from Tavangar et al. 2023 (in prep.),
-        which provides a spline-based characterization of streams implemented in
-        the \package{Jax} library \citep{jax2018github}. The \package{Jax}
-        backend ensures that fitting the model to a stream is very fast (on the
-        order of minutes rather than hours), and also has the capability of
+        refining the CMD fit based on the $\phi_1-\phi_2$ fit. This approach is
+        therefore similar to a matched filter analysis. The model does not
+        currently incorporate kinematic information, though the work could be
+        extended. The improvement of our work is that we do not require an
+        iterative fit to the CMD and astrometry: we handle both spaces through a
+        joint likelihood without simulating mock-observations. Additionally, we
+        can easily incorporate kinematic information and data with missing
+        phase-space dimensions.
+
+        We also highlight upcoming work from the CATS Collaboration 2023 (in
+        prep.), which provides a spline-based characterization of streams
+        implemented in the \package{Jax} library \citep{jax2018github}. The
+        \package{Jax} backend ensures that fitting the model to a stream is very
+        fast (on the order of minutes), and also has the capability of
         incorporating kinematic data with missing phase-space dimensions. The
@@
         stream, but relies on a loose photometric selection. The photometric
-        model in this work could be extended to the method in Tavangar et al.
-        2023 (In prep.) in a straightforward matter.
+        model in this work could be extended to the spline-based method,
+        allowing for a joint astrometric and photometric model than can be
+        rapidly fit to the stream of interest.
 
@@
         rise to their density.
+
+    % sub: comparison (end)
+
+    \subsection{Combining Information from Present and Future Surveys} \label{sub:future_surveys}
+
+        Streams have been primarily discovered and characterized using
+        photometric searches and matched filter methods (e.g.,
+        \citealt{Rockosi+2002, Grillmair2014, Bonaca+2012, Jethwa+2018,
+        Shipp+2018}).  \Gaia{} has enabled a more precise localization of
+        streams, thanks to their  compact kinematic distribution relative to a
+        field of background stars.  On the other hand, \Gaia{} is not
+        photometrically deep ($G\lesssim 21$) and therefore is less sensitive to
+        diffuse streams in the outer Milky Way halo.  Current and upcoming
+        surveys --- e.g., DES \citep{Abbott+2018, Abbott+2021}, \textit{Euclid}
+        \citep{Laureijs+2011}, Rubin \citep{Ivezic+2019}, \textit{Roman}
+        \citep{Spergel+2013} --- do and will probe much deeper photometrically
+        than \Gaia{} can detect.  From the more distant stellar halo
+        \citep{Shipp+2018} to extragalactic systems
+        \citep{Martinez-Delgado+2008, Demirjian+2020, Roman+2023}, these
+        missions will reveal many new tidal features. Since \Gaia{} cannot be
+        used for these streams, kinematic information will be rare, requiring
+        dedicated followup observations.
+
+        In this work we build mixture models (specifically MDNs) to characterize
+        streams using all of the existing photometric and astrometric data for a
+        given field. Looking to \autoref{fig:gd1-results-full} and
+        \autoref{fig:pal5-results-full}, the proper motion components of the
+        model are among the most information-rich and contribute significantly
+        to the model. What then are the prospects for using this work with
+        streams discovered with data from DES, \textit{Euclid}, Rubin, etc?
+        There are two categories of streams these surveys will observe. The
+        first is streams that partially appear in \Gaia{} but are deeper in
+        these surveys; \stream{Pal\,5} is an example, with its main sequence
+        below the \Gaia{} observation limit. Our method permits missing
+        phase-space dimensions, therefore allowing ``outer''-joined catalogues
+        mixing \Gaia{} and photometrically deeper surveys. In this scenario the
+        stream track in proper motions and parallaxes (and possibly radial
+        velocities) communicate and are mutually constrained with the
+        photometric tracks. The second category is streams entirely missing from
+        \Gaia{}, where the data is on-sky positions ($\phi_1$, $\phi_2$),
+        photometry ($\mbs{m}$), and potentially metallicities. Even in this
+        limited data regime,  our stream characterization framework is
+        applicable. The  normalizing flow background model with a tightly
+        constrained stream isochrone model can be flexibly applied to any
+        stream, allowing for a characterization of the tidal feature insofar as
+        the available data allows.
+
+        The ability to simultaneously model the on-sky and photometric
+        distribution of a stream makes this approach a quantitative and Bayesian
+        form of a matched filter analysis. For this reason, our method is
+        readily applicable to the wealth of data expected from upcoming surveys,
+        including both streams discovered in the Milky Way and extragalactic
+        tidal features. While the present work is concerned with the former
+        case, similar methods to the approach developed here may be applied to
+        extragalactic tidal features, 1000s of which are expected to be
+        discovered with Rubin \citep{Ivezic+2019} and \textit{Roman}
+        \citep{Spergel+2013}. With a density model of an extragalactic tidal
+        feature, the gravitational potential of external galaxies can be
+        constrained (e.g., \citealt{Fardal+2013, Pearson+2022, Nibauer+2023}).
+        We leave an extension of our method to extragalactic streams to future
+        work.
+
+    % sub: future_surveys (end)
 
@@
     relies on a combination of analytic densities and normalizing flows, each of
-    which are modular in our code-base and readily adaptable to a given field.
+    which are modular in \package{StreamMapper} and readily adaptable to a given
+    field.
 
@@
     \stream{GD-1} and the tidal tails of \stream{Palomar 5}, generating
-    membership catalogs for both streams that are publicly available
-    \JN{reference link or footnote}. Our characterization of \stream{GD-1}
-    reveals a significant detection of the stream's main component as well as
-    the ``spur" component, which represents a bifurcation from the main stream.
-    We also recover density variations and gaps along the stream that have been
-    previously observed. Our fit to \stream{Pal\,5} demonstrates the performance
-    of our model on a more diffuse stream with low signal-to-noise measurements.
-    The inclusion of deeper photometric data for \stream{Pal\,5} will enable a
-    more extended view of the stream.
+    membership catalogs for both streams that are publicly available at
+    \href{https://zenodo.org/doi/10.5281/zenodo.10903751}{DOI 10.5281/zenodo.10211409}. Our
+    characterization of \stream{GD-1} reveals a significant detection of the
+    stream's main component as well as the ``spur" component, which represents a
+    bifurcation from the main stream.  We also recover density variations and
+    gaps along the stream that have been previously observed. Our fit to
+    \stream{Pal\,5} demonstrates the performance of our model on a more diffuse
+    stream with low signal-to-noise measurements.  The inclusion of deeper
+    photometric data for \stream{Pal\,5} will enable a more extended view of the
+    stream.
 
@@
     stellar streams and stellar membership probabilities will therefore
-    represent a substantial step forward for galactic dynamics, since both the
+    represent a substantial step forward for modeling the Galaxy, since both the
     global track of a stream and its small-scale density distribution are
@@
 
+\newpage
 \section{acknowledgements}
@@
     JN is supported by a National Science Foundation Graduate Research
-    Fellowship, Grant No. \JN{fill in}.
+    Fellowship, Grant No. DGE-2039656. Any opinions, findings, and conclusions
+    or recommendations expressed in this material are those of the author(s) and
+    do not necessarily reflect the views of the National Science Foundation.
 
@@
     Streams 2022} conference for starting the discussions that led to this work.
+    We thank Joshua Speagle for conversations and suggestions that were crucial
+    to the development of the photometric model. We also thank Shirley Ho and
+    Miles Cranmer for insightful discussions and comments.
 
@@
 
+    We would also like to thank the anonymous reviewer, whose suggestions regarding the realistic mock datasets helped us better show the efficacy of the model on real(istic) data.
+
     The data availability statement is modified from one provided to
@@
         \package{brutus} \citep{brutus}, %
+        \package{equinox} \citep{equinox}, %
+        \package{flowjax} \citep{ward2023flowjax}, %
+        \package{gala} \citep{gala}, %
+        \package{galpy} \citep{galpy}, %
+        \package{jax} \citep{jax2018github}, %
         \package{Matplotlib} \citep{Hunter2007}, %
@@
         \package{SciPy} \citep{Scipy2020}, %
-        \package{ShowYourWork} \citep{Luger+2021} %
-        \package{zuko} \citep{zuko}, %
-
+        \package{seaborn} \citep{seaborn}, %
+        \package{ShowYourWork} \citep{Luger+2021}, %
+        \package{zuko} \citep{zuko}. %
+
+\newpage
 \section*{Data Availability} \label{sec:data_availability}
@@
     in the corresponding figure, and the other to the script used to make the
-    figure. The datasets are stored at \todo[inline]{zenodo url}. The git
+    figure. The datasets are stored at
+    \href{https://zenodo.org/doi/10.5281/zenodo.10903751}{DOI 10.5281/zenodo.10211409}. The git
     repository associated with this study is publicly available at
-    \package{\url{https://github.com/nstarman/stellar_stream_density_ml_paper}}.
+    \href{https://github.com/nstarman/stellar_stream_density_ml_paper}{nstarman/stellar\_stream\_density\_ml\_paper}.
+    The open-source code base developed for this project is
+    \href{https://github.com/GalOrrery/stream_mapper-pytorch}{\package{StreamMapper}}.
 
@@
 
+\newpage
 \bibliography{bib}
@@
         \begin{equation}
-            P_X(x; \mu, \sigma) = \mcal{N}(\mu, \sigma).
+            P_X(x; \mu, \sigma) = \mcal{N}(x; \mu, \sigma).
         \end{equation}
@@
         \begin{equation}
-            P_{\mcal{N}\cdot\mcal{N}}(x; \mu, \sigma, \sigobs) = \mcal{N}(\mu, \sqrt{\sigma^2 + \sigobs^2}).
+            P_{\mcal{N}\cdot\mcal{N}}(x; \mu, \sigma, \sigobs) = \mcal{N}(x; \mu, \sqrt{\sigma^2 + \sigobs^2}).
         \end{equation}
@@
 
+\newpage
+\section{Pairing Neural Networks with Priors} \label{app:nns_and_priors}
+
+    In modeling, the choices of priors are important, not only for the
+    information they adds to a model, but also for how optimizers explore
+    parameter spaces. Simple optimizers, like MCMC, propose a parameter vector
+    then compute its likelihood given the data \citep{HoggForeman-Mackey2018}.
+    Priors with compact support  $\theta \sim \mcal{D}((a, b])$, e.g.
+    $\mcal{U}(a, b)$, may be very dangerous as the optimizer can be initialized
+    in a region with zero probability and has no means but blind luck to find
+    the region of support -- the region with non-zero likelihood. More
+    sophisticated optimizers, like gradient-based descent \citep{cauchy_2009},
+    are susceptible to a similar initialization problem, allowing
+    zero-probability regions, but requiring at least a non-zero gradient to make
+    informed updates to the optimizers state.  Outside the support the gradient
+    can be zero.  With MDNs, model parameters are neural network outputs. Unlike
+    for conventional models where an informed initial parameter state may be
+    chosen by hand, it is impractical and undesirable to initialize by hand a
+    neural network's output by setting all its internal weights. One might
+    imagine accomplishing a desired initial output by pre-training the network
+    with a toy model that forces convergence on a set output vector.  However,
+    neural networks are highly non-linear in their response to internal state
+    changes (a desirable property). It is quite possible that when switching
+    from the toy to real model's loss function the pre-trained network is in a
+    local probability island from which the global optimum is unreachable.  
+    Therefore, with the MDN neural networks, initialization is mostly
+    for checking the dependence of the results on the initial state --
+    though even this dependence may instead be done using parameter
+    dropout. Rather than focusing on initializing to a particular
+    parameter vector, for neural networks it is instead important that
+    the initial state, whatever it is, has non-zero probability (or
+    non-zero gradient, depending on the optimizer).  Neural networks
+    have some intrinsic phase-space range that depends on the
+    architecture of the network. Therefore the network architecture must
+    be chosen such that the outputs match well with the priors. For
+    example, with a uniform prior $\theta \sim \mcal{U}(a,b)$, the
+    network should be restricted such that $\theta \in (a, b]$, e.g. by
+    ending the network's $\theta$ channel with a scaled logistic
+    function.
+
+\newpage
+\section{Tailored Mock}\label{app:tailored_mock}
+
+    In this example we construct a tailored dataset on which our model should perform excellently.
+The stream accounts for approximately 10 percent of the total number of stars and is distributed along a $\phi_1$-conditional multivariate Gaussian distribution.
+The background is composed of simple analytic distributions.
+Applying out method to this simple mock dataset provides a useful baseline for expectations.
+As will be shown, the baseline is high.
+
+    \subsection{Data Simulation} \label{app:mock:data}
+
+        We generate synthetic stream observations by sampling from simple
+        algebraic forms.  In $\phi_1$ we sample from a uniform distribution.
+        Non-Poissonian density variations, like gaps, are introduced by adding
+        to the uniform distribution two Gaussian distributions centered at
+        different values of $\phi_1$ with negative amplitudes and random widths.
+        Stream stars are then sampled from this uniform-plus-gaps mixture
+        distribution.  In $\phi_2$ we sample from a quadratic in $\phi_1$ with
+        normally-distributed $0.15^{\degree}$ scatter.  The distances are
+        uniformly sampled from $7$ to $15$ kpc in a linear function in $\phi_1$
+        with normally-distributed $0.25 \ \rm{kpc}$ scatter, then transformed to
+        the parallax $\parallax$. Even though the stream width is constant in
+        the distance the width in parallax is not, which will be used to
+        demonstrate that we can recover $\phi_1$ dependent distributions.  The
+        number of stream stars is $\variable{output/mock/nstream_variable.txt}$.
+        $\variable{output/mock/nbackground_variable.txt}$ background astrometric
+        points are generated by sampling from uniform distributions in each
+        coordinate.
+
+        The synthetic stream's photometry is also simulated using a
+        \variable{output/mock/isochrone_age_variable.txt}\unskip, [Fe/H] =
+        \variable{output/mock/isochrone_feh_variable.txt} MIST isochrone
+        \citep[using][]{brutus}. The isochrone is truncated just short of the
+        giant branch, and is sampled from assuming a stream mass function
+        similar to \stream{Pal\,5} \citep{GrillmairSmith2001} as well as with an
+        intrinsic uniform 0.2~dex scatter orthogonal to the isochrone track.
+
+        The isochrone is shifted by the stream's distance modulus, which is
+        derived from the astrometric distance track.  The background photometric
+        coordinates are generated as a 2-dimensional Gaussian with non-zero
+        covariance. The background is illustrative, if not realistic, in that it
+        is a distribution about which we care very little beyond our ability to
+        fit with a model.  Thus, the synthetic data scenario described here, and
+        presented in \autoref{fig:other_mock_data_result},
+        generates a mock stream in astrometric coordinates and photometric
+        coordinates, with density variations, a distance gradient which is
+        consistent in parallax and distance modulus (i.e., magnitudes), all
+        superimposed over a $\sim 10$ times larger noisy field of background
+        points in each astrometric and photometric dimension.
+
+    % sub: data_simulation (end)
+
+    \subsection{Modeling and Results} \label{app:mock:results}
+
+        To model the stream we use a similar model as was applied in \autoref{sec:results_mock}.
+The primary difference between this and the other model is the exclusion of any proper motion information, making this a simpler model with only $\phi_2, \varpi, g, r$ components.
+
+        The result of applying our density model to the synthetic data is
+        illustrated in \autoref{fig:mock_data_result}. The top panel shows the
+        weight parameter that controls membership probability as a function of
+        $\phi_1$. The dashed curve represents the output of our data-driven
+        model, while the histogram is the ground truth. The second panel shows
+        the stream and background in the $(\phi_1,\phi_2)$ plane, and the third
+        panel shows the stream and background in the $(\phi_1,\parallax)$ plane.
+        Points are color-coded according to their membership probability
+        \autoref{eq:membership_prob}. The weight parameter clearly shows that
+        the model has captured the two prominent density variations along the
+        stream.  There are additional variations, mostly around the edges of the
+        stream, though re-sampling the neural network weights with dropout
+        reveals that these variations represent regions of higher model
+        uncertainty.
+
+        We find that the stream is successfully recovered in both astrometric
+        and photometric coordinates, with
+        $\variable{output/mock/ncorrect_variable.txt}\%$ 
+        of stream stars being recovered with membership probability greater than
+        $80\%$.  In the bottom two rows of \autoref{fig:mock_data_result} we
+        illustrate the synthetic data color-coded by stream membership
+        probability (top) and background membership probability (background) for
+        different $\phi_1$ slices. Importantly, the photometric portion of the
+        mixture model successfully identifies the stream in magnitude space,
+        showing a high stream membership probability where the stream is
+        present, and a low probability ($\sim 0$) where the stream is absent.
+        The false positive rate (i.e., stars misidentified as stream members)
+        for this test is found to be $<0.1\%$ (3 stars) when cutting on the 80\%
+        membership probability threshold.
+
+        \begin{figure*}[!ht]
+            \script{mock/plot/results.py}
+            \centering
+            \includegraphics[width=0.9\linewidth]{figures/mock/results.pdf}
+            \caption{%
+                Illustration of the model's performance in recovering a stream
+                from synthetic observations. The \textbf{top panel} shows the
+                stream mixture coefficient $f(\phi_1)$ (dashed red line)
+                predicted by the model, overplotted on the true stream fraction
+                (black-outlined histogram).
+                %
+                In the \textbf{middle two rows} we also show the $\phi_2$ and
+                parallax, $\parallax$, tracks as a function of $\phi_1$ and
+                their associated widths (labeled as $\sigma_{\phi_2}$ and
+                $\sigma_{\parallax}$, respectively). The true values for these
+                quantities are shown in gray, while our model prediction and
+                uncertainty is show by the dashed red curve and red band, and by
+                the color of the data points (color-coded by membership
+                probability). The model does an excellent job at identifying the
+                ground truth stream stars.
+                %
+                In the \textbf{bottom three rows} we demonstrate our ability to
+                separate the stream from the background both astrometrically and
+                photometrically. Histograms are shown for each model component
+                (black for the ground truth, blue for the background, red for
+                the stream), in 4 $\phi_1$ ranges across the data set.  The
+                height of the histogram is the probability-weighted density for
+                the collection of stars in each bin. There is nearly perfect
+                agreement for the number of stars belonging to each model
+                component as a function of $\phi_1$. In the bottom row we show
+                photometric plots for each model component in the same 4
+                $\phi_1$ ranges across the data set. Points are color-coded by
+                stream membership probability. 
+                %
+            }
+            \label{fig:other_mock_data_result}
+        \end{figure*}
+
+    % sub: results (end)
+
 \end{document}

### 2024-04-21 src/scripts/gd1/models/4-train_model.py

@@ -34,7 +34,7 @@ try:
     snkmk = dict(snakemake.params)
 except NameError:
     snkmk = {
-        "load_from_static": False,
+        "load_from_static": True,
         "save_to_static": False,
         "diagnostic_plots": True,
         # training

### 2024-04-21 src/scripts/gd1/plot/member_probabilities.py

@@ -23,7 +23,6 @@ lik_tbl = QTable.read(paths.data / "gd1" / "membership_likelhoods.ecsv")
 liks = lik_tbl["allstream (MLE)"]
 prob_arr = np.linspace(0.01, liks.max(), num=100)
 num_gtr = np.array([np.sum(liks >= p) for p in prob_arr], dtype=int)
-num_gtr = num_gtr[0] - num_gtr
 
 # =============================================================================
 # Plot

### 2024-04-21 src/scripts/mock2/data/0-query-sim.py

@@ -33,7 +33,7 @@ try:
 except NameError:
     snkmk = {
         "diagnostic_plots": True,
-        "load_from_static": False,
+        "load_from_static": True,
         "save_to_static": True,
     }
 
@@ -45,6 +45,9 @@ diagnostic_plots.mkdir(parents=True, exist_ok=True)
 
 
 ##############################################################################
+
+names = ("ra", "dec", "parallax", "pmra", "pmdec", "G", "G-R")
+dims = len(names)
 
 if snkmk["load_from_static"]:
     shutil.copyfile(
@@ -69,9 +72,6 @@ else:
     # Define the distance range in parsecs
     max_plx = Distance(3 * u.kpc).parallax
     min_plx = Distance(15 * u.kpc).parallax
-
-    dims = 5 + 2  # 5D position, 2D photometry
-    names = ("ra", "dec", "parallax", "pmra", "pmdec", "G", "G-R")
 
     # Construct the query
     ra_min = (coord.ra - ra_radius).to_value("deg")

### 2024-04-21 src/scripts/mock2/data/1-emulate-astro-error.py

@@ -98,15 +98,15 @@ else:
         ]
     )
 
-    # Save the flow info
-    eqx.tree_serialise_leaves(
-        paths.data / "mock2" / "astro_errors_preprocess.eqx", preprocess_errors
-    )
-
     if snkmk["save_to_static"]:
         eqx.tree_serialise_leaves(
             paths.static / "mock2" / "astro_errors_preprocess.eqx", preprocess_errors
         )
+
+# Save the flow info
+eqx.tree_serialise_leaves(
+    paths.data / "mock2" / "astro_errors_preprocess.eqx", preprocess_errors
+)
 
 
 # Transform the data
@@ -202,13 +202,13 @@ else:
         normalized_error_flow, fjxb.Invert(preprocess_errors)
     )
 
-    # Save the flow info
-    eqx.tree_serialise_leaves(paths.data / "mock2" / "astro_error_flow.eqx", error_flow)
-
     if snkmk["save_to_static"]:
         eqx.tree_serialise_leaves(
             paths.static / "mock2" / "astro_error_flow.eqx", error_flow
         )
+
+# Save the flow info
+eqx.tree_serialise_leaves(paths.data / "mock2" / "astro_error_flow.eqx", error_flow)
 
 
 # -------------------------------------------

### 2024-04-21 src/scripts/mock2/data/1-emulate-phot-data.py

@@ -84,15 +84,15 @@ else:
         ]
     )
 
-    # Save the flow info
-    eqx.tree_serialise_leaves(
-        paths.data / "mock2" / "phot_data_preprocess.eqx", preprocess_data
-    )
-
     if snkmk["save_to_static"]:
         eqx.tree_serialise_leaves(
             paths.static / "mock2" / "phot_data_preprocess.eqx", preprocess_data
         )
+
+# Save the flow info
+eqx.tree_serialise_leaves(
+    paths.data / "mock2" / "phot_data_preprocess.eqx", preprocess_data
+)
 
 # Transform the data
 Xp = jax.vmap(preprocess_data.transform)(X)
@@ -177,11 +177,12 @@ else:
     )
     flow = fjdist.Transformed(normalized_flow, fjxb.Invert(preprocess_data))
 
-    # Save the flow info
-    eqx.tree_serialise_leaves(paths.data / "mock2" / "phot_data_flow.eqx", flow)
-
     if snkmk["save_to_static"]:
         eqx.tree_serialise_leaves(paths.static / "mock2" / "phot_data_flow.eqx", flow)
+
+
+# Save the flow info
+eqx.tree_serialise_leaves(paths.data / "mock2" / "phot_data_flow.eqx", flow)
 
 
 # ---------------------------------

### 2024-04-21 src/scripts/mock2/data/1-emulate-phot-error.py

@@ -137,15 +137,16 @@ else:
         ]
     )
 
-    # Save the flow info
-    eqx.tree_serialise_leaves(
-        paths.data / "mock2" / "phot_errors_preprocess.eqx", preprocess_errors
-    )
-
     if snkmk["save_to_static"]:
         eqx.tree_serialise_leaves(
             paths.static / "mock2" / "phot_errors_preprocess.eqx", preprocess_errors
         )
+
+
+# Save the flow info
+eqx.tree_serialise_leaves(
+    paths.data / "mock2" / "phot_errors_preprocess.eqx", preprocess_errors
+)
 
 # Transform the data
 dXp = jax.vmap(preprocess_errors.transform)(dX)
@@ -228,15 +229,13 @@ else:
         normalized_phot_error_flow, fjxb.Invert(preprocess_errors)
     )
 
-    # Save the flow info
-    eqx.tree_serialise_leaves(
-        paths.data / "mock2" / "phot_error_flow.eqx", phot_error_flow
-    )
-
     if snkmk["save_to_static"]:
         eqx.tree_serialise_leaves(
             paths.static / "mock2" / "phot_error_flow.eqx", phot_error_flow
         )
+
+# Save the flow info
+eqx.tree_serialise_leaves(paths.data / "mock2" / "phot_error_flow.eqx", phot_error_flow)
 
 
 # ---------------------------------

### 2024-04-21 src/scripts/mock2/models/1-train_flow.py

@@ -31,7 +31,7 @@ try:
     snkmk = dict(snakemake.params)
 except NameError:
     snkmk = {
-        "load_from_static": False,
+        "load_from_static": True,
         "save_to_static": True,
         "diagnostic_plots": True,
         "epochs": 2_000,

### 2024-04-21 src/scripts/mock2/models/2-train_model.py

@@ -33,8 +33,8 @@ try:
     snkmk = dict(snakemake.params)
 except NameError:
     snkmk = {
-        "load_from_static": False,
-        "save_to_static": False,
+        "load_from_static": True,
+        "save_to_static": True,
         "diagnostic_plots": True,
         "T1": 2_100,
         "T2": 2_100,
@@ -45,7 +45,7 @@ except NameError:
 snkmk["epochs"] = snkmk["T1"] + snkmk["T2"] + snkmk["T3"]
 
 
-if snkmk["load_from_static"] and (paths.static / "mock2").exists():
+if snkmk["load_from_static"] and (paths.static / "mock2" / "model.pt").exists():
     model.load_state_dict(xp.load(paths.static / "mock2" / "model.pt"))
     xp.save(model.state_dict(), paths.data / "mock2" / "model.pt")
 

### 2024-04-21 src/scripts/mock2/plot/results.py

@@ -32,8 +32,7 @@ plt.style.use(paths.scripts / "paper.mplstyle")
 plt.rcParams["ytick.direction"] = "inout"
 
 # Load model
-# model.load_state_dict(xp.load(paths.data / "mock2" / "model.pt"))
-model.load_state_dict(xp.load(paths.data / "mock2" / "models" / "epoch_06200.pt"))
+model.load_state_dict(xp.load(paths.data / "mock2" / "model.pt"))
 
 # Load data
 with asdf.open(

### 2024-04-21 src/scripts/pal5/datasets.py

@@ -1,5 +1,7 @@
 """Pal-5 DataSets."""
 
+import pathlib
+
 import asdf
 import astropy.units as u
 import numpy as np
@@ -9,7 +11,7 @@ from showyourwork.paths import user as user_paths
 
 import stream_mapper.pytorch as sml
 
-paths = user_paths()
+paths = user_paths(pathlib.Path(__file__).parents[3])
 
 # =============================================================================
 # Load data table

### 2024-04-21 src/scripts/pal5/plot/data_selection.py

@@ -1,5 +1,6 @@
 """Train photometry background flow."""
 
+import sys
 from typing import Any
 
 import asdf
@@ -10,14 +11,24 @@ import matplotlib.pyplot as plt
 import numpy as np
 from astropy.table import QTable, Row
 from matplotlib.colors import LogNorm
+from scipy.stats import gaussian_kde
 from showyourwork.paths import user as user_paths
 
 import stream_mapper.pytorch as sml
 
 paths = user_paths()
 
+# Add the parent directory to the path
+sys.path.append(paths.scripts.parent.as_posix())
+# isort: split
+
+from scripts.pal5.datasets import data, off_stream
+
 ###############################################################################
-# Load stuff
+# Prep
+
+# Munge the data
+data = data.astype(np.ndarray)
 
 # Matplotlib style
 plt.style.use(paths.scripts / "paper.mplstyle")
@@ -62,7 +73,15 @@ allstreams = galstreams.MWStreams(implement_Off=True)
 pal5I21 = allstreams["Pal5-I21"].track
 pal5PW19 = allstreams["Pal5-PW19"].track
 
-###############################################################################
+
+# On/off stream selection
+bw_method = 0.05
+background_kde = gaussian_kde(
+    np.c_[data["g"][off_stream], data["r"][off_stream]].T,
+    bw_method=bw_method,
+)
+positions = np.c_[data["g"][~off_stream], data["r"][~off_stream]]
+stream_kde = gaussian_kde(positions.T, bw_method=bw_method)
 
 
 def _sel_patch(row: Row, k1: str, k2: str, **kwargs: Any) -> mpl.patches.Rectangle:
@@ -77,6 +96,8 @@ def _sel_patch(row: Row, k1: str, k2: str, **kwargs: Any) -> mpl.patches.Rectang
 
     return rec
 
+
+###############################################################################
 
 fig = plt.figure(layout="constrained", figsize=(11, 6))
 outer_grid = fig.add_gridspec(2, 1, wspace=0, hspace=0, height_ratios=[1, 1.75])
@@ -122,21 +143,22 @@ ax00.legend(loc="lower left", fontsize=8)
 
 ax10 = fig.add_subplot(
     gs0[0, 2],
[…]

### 2024-04-21 src/scripts/pal5/plot/member_probabilities.py

@@ -23,7 +23,6 @@ lik_tbl = QTable.read(paths.data / "pal5" / "membership_likelhoods.ecsv")
 liks = lik_tbl["stream (MLE)"]
 prob_arr = np.linspace(0.01, liks.max(), num=100)
 num_gtr = np.array([np.sum(liks >= p) for p in prob_arr], dtype=int)
-num_gtr = num_gtr[0] - num_gtr
 
 # =============================================================================
 # Plot
